%TODO: figure out how to get rid of extra page 

\documentclass[serif, mathserif, final]{beamer}
%\documentclass[serif,mathserif, final]{beamer} %values in brackets just adjust the text font 

\usetheme{Lankton}
%\mode<poster>{\usetheme{Lankton}} 
%\mode<poster>{\usetheme{RicePoster}} 
\usepackage{amsmath,amsfonts,amssymb,pxfonts,xspace}
%\usepackage{eulervm}
\usepackage{graphicx, ragged2e}
\usepackage{pgffor}
\setbeamertemplate{caption}[numbered]

%\usepackage{textbox} <-- use for aligning  text - get this from macports
 
%\graphicspath{{./figures/}}
\usepackage[orientation=landscape,size=a0,scale=1.6,debug]{beamerposter}

%-- Header and footer information ----------------------------------
\newcommand{\footleft}{Mgmt-WorkLife-Goalsplanning} % figure what this should be 
\newcommand{\footright}{August 2014}
\title{Goals Planning} 
\author{Vivek Kale$^1$}
\institute{$^1$ University of Illinois at Urbana-Champaign \quad}  

%------------------------------------------------------------------
%-- Main Document ------------------------------------------------- 

\begin{document}
\begin{frame}{}

  \begin{columns}
    %-- Column 1 ---------------------------------------------------
    \begin{column}{0.33\linewidth} 
      %-- Block 1-1 
      \begin{block}{ 3-year plan }
        \begin{itemize} 
        \item \small find someone 
        \item \small make 150K 
        \item \small network
        \end{itemize} 
      \end{block} 
    \end{column}%1 
    

%-- Column 2 ---------------------------------------------------  
\begin{column}{0.27\linewidth} 

%-- Block 2-1 
\begin{block}{ 6-month plan  } 
\begin{itemize} 
\small \item \small results + thesis
\item \small routine + worklife 
\item \small 
\end{itemize} 
\end{block} 

\begin{block}{ Month-by-month}
\begin{itemize}
\item \small March: 
\item \small April:
\item \small May: 
\item \small June: org thesis. Org Amanda's application, figure out outstanding system's issues. 
\item \small July: Finish integration in last chapter, data. Amanda's application. 
\item \small August: org thesis, data collection
\item \small September: Prep other paper for IPDPS
\item \small October: Get slides ready for defense 
\end{itemize}
\end{block}
\end{column} %2 

%-- Column 3 --------------------------------------------- 
%\begin{column}{0.27\linewidth} {\textbf{Month Plan for August 2014}} 
\begin{column}{0.27\linewidth}
%\begin{column}{0.33\linewidth} {\textbf{\underline{Month Plan for August 2014}}}
      %-- Block 1-1 
\begin{block}{\underline{\textbf{August goals}}}
\begin{enumerate}
\item \small Work: app results + papers.
\item \small Work: thesis completion.
\item \small Mgmt: Health: lose 10 pounds:  excercise butt, chest, wrists. Run without eating.
\item \small worklife: Habits + empathy
\item \small habits: lips relaxed, back straight, no teeth clicking/body noises, feet quiet.
\end{enumerate}
\end{block} 

\begin{block}{\small \underline{\textbf{Week of August $4^{th}$}}} 
\begin{enumerate}
\tiny \item \tiny Work: get app results for nbody
\item \tiny Work: get poster done + talk to Simplice.
\item \tiny worklife: experiences sheet fix
\item \tiny worklife: read habits and update
\item \tiny Comm: finish last part of emotional intelligence.
\end{enumerate}
\end{block}

\begin{block}{\small \underline{\textbf{Week of August $13^{th}$}}}
\begin{enumerate}
\tiny \item \tiny Work: Do additional results from HACC.
\item \tiny Work: Update library/code.  +  Work: add code structure for data collection. +  Work: Send message to Tanzima about PAPI. Find any other systems issues and take care of them.
\item \tiny Comm: read social intelligence to help with social life.
\item \tiny worklife: read habits.
\end{enumerate}
\end{block} 

\begin{block} {\small \underline{\textbf{Week of August $20^{th}$}} }
\begin{enumerate}
\tiny \item \tiny Work: additional results for other codes such as miniFE. 
\tiny \item \tiny Work: finish results for nbody. 
\item \tiny Work: library +  Work: integrate with slack-conscious +  Work: start integration of schedulers.
\item \tiny Comm: read social intelligence to help with social life.
\item \tiny worklife: read habits.
\end{enumerate}
\end{block}

%\begin{block}{ \small \underline{\textbf{Week 3: Aug 27- Sept 1st }}}
%\begin{block}{ \small \underline{\textbf{Week 4: Week of Aug. 27 }}}
\begin{block}{ \small \underline{\textbf{Week of Aug $27^{th}$ }}}
\begin{enumerate}
\tiny \item \tiny Work: poster for EuroMPI + revisions in that chapter to finish off
 \item \tiny netip:
\end{enumerate}
\end{block} 

\end{column}%3 

\end{columns} 

\end{frame} 

\end{document}
