%Note:  figure how to make items small automatically

\underline{\textbf{June goals}} \\
\begin{enumerate}
\item Mgmt: Health: lose 10 pounds:  excercise butt, chest, wrists. Run without eating. 
\item Mgmt: Spaces: finish spaces org, make spaces vuln and habits everyday. 

\item Work: get working version of runtime.
\item Work: thesis completion.
\item Work: setup for Amanda's code. 

\item Comm: worklife working version. 
\item habits: lips relaxed, back straight, no teeth clicking/body noises, feet quiet. 
\item Situation: plan for wedding, plan to increase network at wedding. 
\end{enumerate}

\underline{\textbf{Week of June $2^{nd}$}} \\

\begin{enumerate}
\item Comm: find tm 
\item Mgmt: Spaces: clean room, and bathroom
\item Mgmt: Spaces: clean desktop
\item Work: thesis structuring 
\end{enumerate}

\underline{\textbf{Week of June $9^{th}$}} \\
\begin{enumerate}

\item Work: Do related work structure and motivation. 

\item Work: add code structure for data collection. 
\item Work: Send message to Tanzima about PAPI. Find any other systems issues and take care of them. 

\item Mgmt: Spaces: money: check sw old stuff, get the lamp, find iPad. 
\item worklife: get cooking instructions down, get routine for running/excercise down. 

\item Comm: structure Atul's speech + read vocal variety speech lessons, look at speech inspiration. 
\item Comm: finish books and get infrastructure down for worklife, with practiced. 

\end{enumerate}

\underline{\textbf{Week of June $14^{th}$}} \\
\begin{enumerate} 

\item Work: Prof Gropp's comments on being more precise(modeling) + Work: do stuff on Related Work, and organization + Work: start writing last chapter. 
\item Work: finish any further systems issues, integrate with slack-conscious +  Work: start integration of schedulers. 
\item Work: get profiling and put up data, Do analysis + find additional results for different strategies, do some
experimentation. 
\item Work: work on Amanda's code for the icrev, check correctness, figure out Amanda's code integration and linking with library, add implementation of techniques to Amanda's code. 

\item Mgmt: Spaces: practice spaces maintenance. 
\item Comm: structure Atul's speech + Comm: put into practice the books. + Comm: read social intelligence. 

\end{enumerate}

\underline{\textbf{Week of June $23^{rd}$}} \\
\begin{enumerate}

\item Comm: Prep for Atul's wedding 

\item Work: 

\end{enumerate}

