\begin{columns}
  %-- Page 2: Column 1 --------------------------------------------------- 
  \begin{column}{0.20\linewidth}
    %{\textbf{\underline{Week Aspects(new name)}})
      %--- Page 2: Block 1-1 
    \begin{block}{Routines}
      { \tiny \underline{\bf Routines:} Morning: bfast, exercise/brush,
        floss, shower (hair, eyes, ears, underarms, feet), meds, belt,
        comb hair / dishes, clean kitchen floor. |  Night: running/ put
        away dishes, clean kitchen floor / brush teeth, charge phone,
        clothes for tomorrow, contacts off.}\\
      {\tiny \underline{\bf Sunday Routines:} Routines:
        Experiences,week plan.}\\ 
      {\tiny \underline{\bf Weekday Routines:}}\\
      %TODO: check if weekday routines overlaps into daily routines.
    \end{block} 
      %--- Page 2: Block 1-3
    \begin{block}{Local Happiness}
      % howto:Recognize emotions / recognize (precisely) what you're
      % worried about -> methods for eliminating worry. 
      % clean out old worries, put them in pastWorries doc.  
      % remember to define precisely 
      % order from top-to bottom
      \begin{itemize} 
        \tiny \item \tiny -
      \item \tiny Worrying about gal: think about talking to others.
      \end{itemize} 
    \end{block}
    %--- Page 2: Block 1-4 
    \begin{block}{AngersAndAnxieties}
      % howto:Recognize emotions / recognize (precisely) what you're worried about -> methods for eliminating worry. 
      % clean out old worries, put them in pastWorries doc.  
      % remember to define precisely 
      % order from top-to bottom
      \begin{itemize}
        \item \tiny Issue with USC : $\rightarrow$ things get better. 
        \tiny \item \tiny Anger about UP $\rightarrow$ think about the positive
        perspective, and the original
      \item \tiny Anger about Mr. Kapoor $\rightarrow$  leave it
      \item \tiny Anger about a b  $\rightarrow$ ...
      \end{itemize}
    \end{block}
      %-- Block 1-5
      \begin{block}{Life notes}
        \begin{itemize}
          \tiny \item \tiny Social Intelligence: 
        \end{itemize}
      \end{block}
      % howto:
      \begin{block}
        {\tiny {\bf Week lessons:}}
        \begin{enumerate}
%          \tiny \item \tiny Win Friends/ Influence People
%        \item \tiny Go through 7 habits.
        \item \tiny tm tips.
        \item \tiny Coding problem: 
        \item \tiny Chess tips: 
        \end{enumerate}
            {{\tiny {\tiny \bf  News:}} {\tiny  M: Uber board | S:
                Tony Award's| E: Fallon:  Kimmel:  Colbert: SNL:}}
            {{\tiny {\tiny \bf  Weather:}} {\tiny M: 1100 T: 1100 W:
                0110 R: 0100 F: 0110 Sa: 0110 Su: }}
      \end{block}
  \end{column}
  %-- Column 2 ---------------------------------------------
  \begin{column}{0.6\linewidth}
    \begin{block}{Week Summary} 
      {\underline {\bf Week Plan:} 
        Work: finish writeup, Work: talk about HiVE, Work: talk to
        Youssef, Work: do outline for OpenMPCon, 
        Mgmt:Spaces: flights,  Mgmt:Spaces: look for apartment
        elsewhere, Mgmt:Spaces: car rental, 
        Work:rel: email to Renata} \\
      {\underline{\bf Weekend Plan:} Meet Puja, Meet Srushti }\\
    \end{block}

      \begin{block}{Running ToDo} % find a better name 
        \begin{enumerate} 
    \doneTask{Mgmt:wp(fbf): update featured photos on profile. =
        Mgmt:wp(fbf): decide which photos to add = Mgmt:wp(fbf): add picture of
        basement winning + Mgmt:wp(fbf): add photo of Vivek and Atul +
        Mgmt:wp(fbf): add photo of Vivek and Anu in backward hat + Mgmt:wp(fbf):
        add photo of wimping + Mgmt:wp(fbf): fb}. 
    
  \item \tiny Mgmt:wp(fbg): add post for golden state 
    \doneTask{Work(ltr): get information for Stephen about work =
      Work(ltr):Find work from Julia language + Work(ltr): Discuss 
      Work from Stanford + Work(ltr):Find work on Mendel Rosenblum +
      Work(ltr): Find work from person related to Stanford. \te{1
     hour}.} 

 \doneTask{Work: send message to Youssef about question about
   \texttt{nvprof}.} \te{1 hour}
 \doneTask{ Mgmt:Spaces: book flight for bmm in July} \te{1 hour}
 \doneTask{Comm: reply to Anisha from Coffee meets Bagel. } 
 \doneTask{ Work: PRISMA tool specification. }\te{2 hours}. 
 \doneTask{Mgmt:Spaces: return car .} \te{1 hour}.
 \doneTask{Mgmt:Health: do dentist appointment.}    
 \doneTask{ Comm: message to Rohina.}   
\item \tiny Mgmt:Health: get USC card for dental.
\doneTask{Mgmt:Spaces: call National for car. \te{10 minutes}.}
\doneTask{Work(opc:dpg): Discuss the abstract with Prof. Gropp. }  
\doneTask{Work: do outline for OpenMPCon \te{20 minutes}.}
\doneTask{Work(opc:adddiagram): add diagrams.} 
\doneTask{Work(opc:ex): write about example.}
\doneTask{Work(opc:rev): do revisions.}

\item \tiny \textbf{Curr} $\rightarrow$ 

\item \tiny Work:rel: email to Abid \te{1 hour}. 
\item \tiny Work: update paper .tex file with dot prod.  \te{30
   minutes}. 

 \item \tiny Work(psm): install CUDA driver. \te{10 minutes} 

 \item \tiny Work(psm): message to talk to V. Adve. \te{20 minutes}. 

 \item \tiny Work(psm): book flight for Chicago. \te{20 minutes}.
 \item \tiny Work(psm): prep for meeting. \te{1 hour}. 

 \item \tiny  Work: admin: accept DSL re-imbursement. 
 
 \item \tiny Work: do writeup for paper. \te{1 hour}. 
 \item \tiny Mgmt:Spaces: book flight for trip in December. \te{1
   hour}. 

 \item \tiny Work(iwp:dp): add results from dot product. 
 \item \tiny Work(iwp:pap): change formatting for paper. 
   \doneTask{Work(opc:addcitations): add citations.} 

   
 \item \tiny Comm: message to Shalaka? 
   
 \item \tiny Comm: message to Mamta, 
   Here's my number: 217-369-7996. I'm working for USC. I work in an
   office in the D.C. Area. I'm in Los Angeles this week. 
   
 \item \tiny Work:rel: email to Renata. \te{10 minutes}.
 \item \tiny Work: send message about optimizations to do for CkLoop. \te{1 hour} \dl{20 minutes}. 

 \item \tiny worklife: read social intelligence. \te{2 hour}.

 \item \tiny Comm: do review for Liberty Towers.

 \item \tiny Comm: message to Srushti.
   Ok. I plan to be in New York next weekend. Let me know if you and
   Ruddhi around and free next Saturday at 7:00 PM. 

      \item \tiny \textbf{ <-- End Curr } 
        
      \item \tiny Work: IM system for LLNL.
        \end{enumerate}
      \end{block}
      
      % howto: the below is a routine based on the job I'm doing and the
      % circumstances I'm in. Note that this is different from routines
      % above, which is true for a long-term period of over 10 years. 
      \begin{block}{Weekly Meetings}
        \begin{itemize}
          \tiny \item \tiny IWOMP affinity meeting Thursday 7 AM PDT / 9 AM
          CDT call in: 805-639-779 pswd: places. \url{https://llnl.webex.com/llnl/j.php?MTID=m33950b76befb72c0cbc31ea2e3be720c}
        \item \tiny DEG group meeting.  
        \end{itemize}
      \end{block} 
      \begin{block}{Week Daily Schedule}
        % howto: arrange items from running todo into the below
        % sheet management document. 
        %NOTE: we don't use the table format because of fittting
        \begin{columns}
          \begin{column}{0.14\textwidth}{\small \underline{\bf Mon}}
            {\tiny \bf {\tiny weather:} } {\tiny 11/1 s} \\ 
            {\tiny \bf {\tiny todo}}\\ 
            \begin{itemize}
              \tiny \item \tiny Work: do experiments with multiple nodes. 
            \item \tiny Work: get experiments using real data.  
            \item \tiny 
            \end{itemize}
                {\small  \bf schedule}\\
                \begin{enumerate} 
                  \tiny \item \tiny 8-9AM: Regular Routines 
                \end{enumerate}
          \end{column}

          \begin{column}{0.14\textwidth}{\small \underline{\bf Tues}}
            {\bf {\tiny  weather:} } {\tiny 3/1 r} \\ 
            {\bf {\tiny todo}}\\ 
            \begin{itemize}
              \tiny \item \tiny Work: do write-up 
            \end{itemize} 
                {{\bf {\tiny  schedule}}}
                \begin{enumerate} 
                  \tiny \item \tiny 8-9AM: Regular Routines 
                \end{enumerate} 
          \end{column}
          \begin{column}{0.14\textwidth}{\small \underline{\bf Wed}}
            {\tiny \bf weather: } {\tiny 3/1 r} \\ 
            {\tiny {\bf todo}}\\
            \begin{itemize}
              \tiny \item \tiny Work: send email to Prof. Gropp. 
            \item \tiny 
            \item \tiny Comm: message to Anita. 
            \end{itemize}
                {\tiny \bf schedule}\\
                \begin{enumerate} 
                  \tiny \item \tiny 8-9AM: Regular Routines 
                \end{enumerate} 
          \end{column}

          \begin{column}{0.14\textwidth}{\small \underline{\bf Thurs}}
            {\tiny \bf weather: } {\tiny 1/-1 r }\\ 
            {\tiny \bf todo} \\ 
            \begin{itemize}
              \tiny \item \tiny Add in schedule
            \item \tiny 
            \end{itemize} 
                {\tiny {\bf schedule}} \\
                \begin{enumerate} 
                  \tiny \item \tiny 8-9AM: Regular Routines 
                \end{enumerate}
          \end{column} 
          
          \begin{column}{0.14\textwidth}{\small \underline{\bf Fri}}
            {\tiny \bf weather: } {\tiny 3/1 r} \\ 
            {\tiny \bf todo} \\ 
            \begin{itemize}
              \tiny \item \tiny Add in schedule
            \item \tiny 
            \end{itemize} 
                {\tiny \bf schedule} \\
                \begin{enumerate} 
                  \tiny \item \tiny 8-9AM: Regular Routines 
                \end{enumerate}
          \end{column}

          \begin{column}{0.15\textwidth}{\small \underline{\bf Sat}}
            {\tiny \bf weather: } {\tiny 11/1 .2r} \\ 
            { \tiny \bf todo} \\ 
            \begin{itemize}
              \tiny \item \tiny Add in schedule
            \item \tiny 
            \end{itemize} 
                {\tiny \bf schedule} \\
                \begin{enumerate} 
                  \tiny \item \tiny 8-9AM: Regular Routines 
                \end{enumerate}
          \end{column}
         
          \begin{column}{0.15\textwidth}{\small \underline{\bf Sun}}
            {\tiny {\bf weather:} } {\tiny 11/2 r} \\ 
            {\tiny {\bf todo}}\\
            \begin{itemize}
              \tiny \item \tiny Add in schedule
            \end{itemize} 
                {\tiny \bf schedule}\\
                \begin{enumerate} 
                  \tiny \item \tiny 8-9AM: Regular Routines 
                \end{enumerate}
          \end{column}
        \end{columns}
      \end{block}
\end{column}
    
    % ------ Page 2: Column 3
    \begin{column}{0.20\linewidth}
      % ------ Block 2.3.1 
      \begin{block}{Food Plan} 
        \begin{itemize}
          \tiny \item \tiny Google Express: DHDQQJQDRFTXDM95B
        \end{itemize}
      \end{block} 
      \begin{block}{Clothes plan} 
        \begin{itemize}
          \tiny \item \tiny Monday: 
        \item \tiny Tuesday
        \item \tiny Wednesday
        \item \tiny Thursday
        \item \tiny Friday
        \item \tiny Saturday
        \end{itemize} 
      \end{block} 
      
      %-- Block 3-3 
      \begin{block}{Situations}
        % Summary: the below are the situations that define one
        % another.
        % Howto: Put post notes of each situation from list of previous
        % week. Put high importance situations in situationslist. 
        % Put list of upcoming situations on Sunday morning with Pre. 
        \begin{itemize}
          \tiny \item \tiny 
        \item \tiny 
        \end{itemize}
      \end{block}
      % contingincies: 
      % Summary:
    \end{column}
\end{columns}



\comments{

\begin{minipage}{0.5\textwidth}
\begin{itemize}
\tiny \item \tiny do scheduling strategies.
\item \tiny work on job talk.
\item \tiny do travel.
\item \tiny social on facebook, catch up with Rishi.
\end{itemize}
\begin{itemize}
\item \tiny 2-month plan: May: finish documents.  June:  finish paper.
\item \tiny 2-month plan: July: paper, meet people  August: paper, meet people.
\item \tiny 2-month plan: September: paper, meet people  October:
  paper, meet people.
\end{itemize}
\end{minipage}

\begin{multicols}{4}
\begin{minipage}{\columnwidth}
\underline{\bf \tiny {Work:code: PRISMA}}
\begin{enumerate}
\item \tiny Work: fix Youssef's code.
\item \tiny Work: download ptychoLib from Kaushik and copy to git repo.
\item \tiny Work: run for Ptypy.
\item \tiny Work: figure out time to talk with Youssef.
\item \tiny Work: download ptychoLib from Kaushik and copy to git repo.
\item \tiny Work: discuss work with A rittenbach + Work: download
  driver on GPU4.
\item \tiny work: integrate.
\item \tiny Work: do OpenMP 4.5 for ptypy and OpenACC.
\item \tiny Work: run with dataset from PSI.
\item \tiny Work: send message about research paper.
\item \tiny Work: get profiles for PtychoLib code.
\item \tiny Work: write report for spec.
\item \tiny Work: ask for an increase in size for HPCC system.
\end{enumerate}
\end{minipage}

\begin{minipage}{\columnwidth}
\underline{\bf \tiny {Work: PRISMA pubs}}
\begin{enumerate}
\tiny \item \tiny Work: create a latex git repo for paper.
\item \tiny Work: find a conference.
\item \tiny Work: create an outline.
\item \tiny Work: get information about JIT compilation.
\end{enumerate}
\end{minipage}

\begin{minipage}{\columnwidth}
\underline{\bf \tiny {Work: Other work at ISI}}
\begin{enumerate}
\item \tiny Work: get information about JIT compilation.
\end{enumerate}
\end{minipage}

\begin{minipage}{\columnwidth}
\underline{\bf \tiny {Work: OpenMPCon submission}}
\begin{enumerate}
\tiny \item \tiny Work: create a latex git repo for paper.
\item \tiny Work: send Prof. Gropp a message.
\item \tiny Work: make notes on static/dynamic scheduling.
\item \tiny Work: make notes on user-defined scheduling.
\end{enumerate}
\end{minipage}

\begin{minipage}{\columnwidth}
\underline{\bf \tiny {Work: Charm++ +OpenMP}}
\begin{enumerate}
\tiny \item \tiny Work: send notes/tasks todo.
\item \tiny Work: do documentation of implementation.
\item \tiny Do Charm++ + OpenMP implementation.
\item \tiny Get GPU implementation of dotProd in Charm++.
\item \tiny Work: get access to Cori machine.
\item \tiny Work: Add notes about OpenMP.
\item \tiny Work: add explanation of dotProduct on OpenMP.
\end{enumerate}
\end{minipage}


\begin{minipage}{\columnwidth} 
\underline{\bf \tiny {Work: Charm++ +OpenMP}}
\begin{enumerate}
\item \tiny Mgmt:wp: post with friends from college. 
\item \tiny Mgmt:wp: update description. 
\item \tiny Mgmt:wp: post about Queen.   
\item \tiny Comm:rel: update pictures. \te{30 minutes}.
\end{enumerate}
\end{minipage}

\begin{minipage}{\columnwidth}
\begin{enumerate} 
 \item \tiny Mgmt:Spaces: look for apartment elsewhere. \te{1 hour}. 
\end{enumerate}
\end{minipage} 
\end{multicols}

} 


