\begin{columns}  %-- Page 2: Column 1 ---------------------------------------------------

\begin{column}{0.10\linewidth}

\begin{block}{Projects}


%Project superspace: mental health

% Project superspace: work 

% Project: Fundamental knowledge. 

% Project space: applications 

\underline{Computational Reqs} 
\underline{\textbf{Deadline:} September $22^{nd}$, 2017} 
\begin{enumerate}
\pitem 
\pitem 
\end{enumerate}

\underline{Tomography Code} 
\underline{\textbf{Deadline:} September $22^{nd}$, 2017} 
\begin{enumerate}
\pitem 
\pitem 
\end{enumerate}

\underline{Networking Infrastructure} 
\underline{\textbf{Deadline:} September $22^{nd}$, 2017} 
\begin{enumerate}
\pitem 
\pitem 
\end{enumerate}

\underline{Publication} 
\underline{\textbf{Deadline:} September $22^{nd}$, 2017} 
\begin{enumerate}
\pitem 
\pitem 
\end{enumerate}

% Project space: programming and systems

% -- Project: OpenMP 
\underline{OMP proposal} 
\underline{\textbf{Deadline:} September $22^{nd}$, 2017} 
\begin{enumerate}
\pitem 
\pitem 
\end{enumerate} 

% -- Project: CkLoopHyb paper 
\underline{CkLoopHyb paper}
\underline{\textbf{Deadline:} September $22^{nd}$, 2017}
\begin{enumerate}
\pitem Add template to git repository.
\pitem Add writeup for dot product results on Cori.
\pitem Get PIC results with Charm++-everywhere for BW.
\pitem Need a new application.
\ptask Update the paper technique to be consistent with experiments.

\ptask Work: update paper .tex file with dot prod. \te{30
          minutes}.
\ptask Add PAPI cache misses for problem statement.
\ptask Fix diagrams.
\ptask Figure out what to put at the top block of first quadrant.
\ptask Add content in extended paper.
\ptask Add code for PIC in bottom left quadrant.
\ptask Add projections results.
\ptask Add to related work.
\ptask Get PIC results with Charm++-everywhere, Charm++ + CkLoop for Cori.
\ptask Get results for Charm++ + CkLoop for missing data points.
\ptask Show results for dot product using Charm++ + OpenMP, and for
dot product with Charm++ + CkLoop.
\doneTask{ Show code with Charm++ + OpenMP.}
\pitem Merge with git repository.
\pitem Send message to meet for results.
\pitem Work: message to Kathryn about poster.
\end{enumerate}

\underline{Schedule} \\ 
\begin{enumerate}
\pitem 
\end{enumerate} 
\end{block} 

%Project: interviewing 
\underline{Interviewing} 
\underline{\textbf{Deadline:}    }  
\begin{enumerate}
\pitem 
\pitem 
\end{enumerate} 

%Project: extra-curricular 

\begin{block}{Month Plan}

\end{block}

\end{column}
  \begin{column}{0.10\linewidth}
    %{\textbf{\underline{Week Aspects(new name)}})
      %--- Page 2: Block 1-1 
    \begin{block}{Routines}
      { \tiny \underline{\bf Routines:} Morning: bfast, exercise/brush,
        floss, shower (hair, eyes, ears, underarms, feet), meds, belt,
        comb hair / dishes, clean kitchen floor. |  Night: running/ put
        away dishes, clean kitchen floor / brush teeth, charge phone,
        clothes for tomorrow, contacts off.}\\
      {\tiny \underline{\bf Sunday Routines:} Routines:
        Experiences,week plan.}\\ 
      {\tiny \underline{\bf Weekday Routines:}}\\
      %TODO: check if weekday routines overlaps into daily routines.
    \end{block} 
      %--- Page 2: Block 1-3
    \begin{block}{Local Happiness}
      % howto:Recognize emotions / recognize (precisely) what you're
      % worried about -> methods for eliminating worry. 
      % clean out old worries, put them in pastWorries doc.  
      % remember to define precisely 
      % order from top-to bottom
      \begin{itemize} 
        \tiny \item \tiny -
      \item \tiny Worrying about gal: think about talking to others.
      \end{itemize} 
    \end{block}
    %--- Page 2: Block 1-4 
    \begin{block}{AngersAndAnxieties}
      % howto:Recognize emotions / recognize (precisely) what you're worried about -> methods for eliminating worry. 
      % clean out old worries, put them in pastWorries doc.  
      % remember to define precisely 
      % order from top-to bottom
      \begin{itemize}
        \item \tiny Issue with USC : $\rightarrow$ things get better. 
        \tiny \item \tiny Anger about UP $\rightarrow$ think about the positive
        perspective, and the original
      \item \tiny Anger about Mr. Kapoor $\rightarrow$  leave it
      \item \tiny Anger about a b  $\rightarrow$ ...
      \end{itemize}
    \end{block}
      %-- Block 1-5
      \begin{block}{Life notes}
        \begin{itemize}
          \tiny \item \tiny Social Intelligence: 
        \end{itemize}
      \end{block}
      % howto:
      \begin{block}
        {\tiny {\bf Week lessons:}}
        \begin{enumerate}
        \item \tiny tm tips.
        \item \tiny Coding problem: 
        \item \tiny Chess tips: 
        \end{enumerate}
            {{\tiny {\tiny \bf  News:}} {\tiny  M:  | S: 
                | E: Fallon:  Kimmel:  Colbert: SNL:}}
            {{\tiny {\tiny \bf  Weather:}} {\tiny M: 1100 T: 1100 W: 41/34 .1r 
                 R: 51/46 .60r F: 62/36 .7r a Sa: 42/20 .10r Su: 31/17 }} 

           % \input{weather} 
      \end{block}
  \end{column}
  %-- Column 2 ---------------------------------------------
  \begin{column}{0.6\linewidth}
    \begin{block}{Week Summary} 

      {\underline {\bf Week Plan:}  Comm: photo upload, Work:admin:
        finish re-imbursements, Mgmt:Spaces: get dl, Work: contact for
        UDS, Work:rel: send out the LLNL application + Work:rel:
        message to Nathan, Work:rel: send out cover letter, Work:
        slides for meeting, Comm: upload pictures, Comm: upload
        photos, }\\ 


{\underline{\bf Weekend Plan:} Move out of apartment. } \\

    \end{block}
    \begin{block}{Running ToDo} % find a better name 
      
      \begin{enumerate}
      \doneTask{ Work: contact for UDS} 
      \item \tiny Work: send e-mail to Michael Klemm. 

Hi Michael,
        
I'm working towards finishing my portion of the presentation of the user-defined schedule, which involves the implementation of the user-defined schedule.

I saw the updates that you made to the first several slides of the
presentation on Google Slides. I agree with them and they look
good. I'm integrating my portion of the presentation with the
changes. 

I'd like to go through the slides for the presentation for the
proposal for user-defined scheduling for OpenMP that you'll present
next Wednesday. Will you be free to meet with me this week on
Wednesday at 5:00 PM CET by Skype to do so? 

Vivek

      \item \tiny Work: work on slides to present this week =
        Work:(psm): slides present to JP + Work:(psm): slides
        discussion with graph  + Work:(psm): connect to schedule +
        Work:(psm): practice presentation.
      \item \tiny Comm: photo upload. 
      \item \tiny worklife: make projects list
        \doneTask{Work: message to Nathan. }

      \doneTask{ Work: send e-mail to JP and Steve about
        publications.}

Hi JP and Steve,

I'd like to note in next Friday's CS&T's 'What's Going On?' Breakfast
series the following publications from ISI. 

1. A User-defined schedule for OpenMP. --> Paper at OpenMPCon 2017.

2. Using Adaptive Loop Scheduling with Charm++ to Improve Performance
of Scientific Applications. --> Poster at SC 2017 and nomination for Best
Poster at SC 2017. 

I didn't think that I should bring them up in previous CS&T meetings
and thought it best to keep the success to myself and both of you
then. With more experience (and my understanding of the organization and
priorities of ISI as a whole), I think that they should. 

Also, I'd be open to promoting the nomination for Best Poster
nomination at SC17 in other places such as a newsletter or Annual
Report for ISI. 

Let me know if we can promote them there and if we should 

My desire to promote this work is independent of the discussion of the
PRISMA program in this afternoon's PRISMA meeting. I'd been planning to send you this e-mail yesterday
afternoon (but didn't get time to do so) without the knowledge of
today's discussion of the PRISMA program in the PRISMA meeting today.

Vivek

\doneTask{Mgmt:Spaces:(mvo): give back Internet box.} 
\doneTask{Work: reply to Michael Klemm.} 

\item \tiny \textbf{Curr} $\rightarrow$ 

\item \tiny Work:admin: finish re-imbursements 
  
\item \tiny Work: admin: finish re-imbursements. 
\item \tiny Work:rel: send out LLNL application. \te{1 hour}
  \dl{Wednesday}. 

\item \tiny Mgmt:Spaces: get glasses. 

\doneTask{ Mgmt:Spaces: get Duloxotine medication. } 
\doneTask{Mgmt:Spaces: call Bhavesh about bed. } 

\item \tiny \textbf{Curr} $\rightarrow$ 
\item \tiny Work:(psm:up): send JP slides with updates. 
\item \tiny Work:update slides for PRISMA

\item \tiny Work:(uds:sld): do slides for UDS = \doneTaskNoItem{Work(uds:sld): send slides to Dad} + 
  Work(uds:sld): update the slide to clarify the UDS limitation + Work(uds:sld): add notes 
  for slides and send them  + Work(uds:sld): reply to Michael's
  latest e-mail + \doneTaskNoItem{Work(uds:sld): add static schedule} 
  + \doneTaskNoItem{Work(uds:sld): update dynamic schedule.} 

\item \tiny Work:rel:cvl:upd):  do cover letter for LLNL = Work: rel:
  explain reason for wanting to join LLNL + Work:rel:(cvl): explain
  your contributions + Work:rel:(cvl):  +  \doneTask{Work:rel:send
  e-mail to Nathan Tallent. }

\item \tiny Work:rel: do application for HLFF = Work:rel: get degree
  certificate + Work:rel: add research statement + Work:rel: write
  letter of motivation.

\item \tiny Work:admin: finish re-imbursements. 

\item \tiny Work: send e-mail. 

\item \tiny Mgmt:Spaces: get driver's license from VA. 
\item \tiny Work:admin: submit receipts for travel. 
\item \tiny Mgmt:Spaces: get glasses. 
\item \tiny Mgmt:wp: add Andy Schmidt on LinkedIn.  

\item \tiny Comm: upload pictures. 
\item \tiny Comm: upload photos. 

\item \tiny Work:admin: submit receipts for Bagel. 

  
\tiny \item[] \tiny \textbf{Curr} $\rightarrow$
  
\item \tiny Work: finish proposal slides. 

\item \tiny Work:rel: do cover letter for BNL + Mgmt:Spaces: talk with
  Martin Kong.
  
\item \tiny Work: send in application to PNNL.

\item \tiny Work: admin: send in receipts for SC17. 

\item \tiny Mgmt:wp: add profile.
\item \tiny Mgmt:wp: add about me. 
  
\item \tiny Mgmt:wp: add profile 
\item \tiny Work:rel: email to Renata. \te{10 minutes} 
\item \tiny Comm: message to Sateja. 
  Hey, I followed you on LinkedIn. I think your work is really good. 
  Let me know if you want to grab coffee sometime in the city. 
\item \tiny Comm:rel: talk to Shweta.
\item \tiny Comm: talk with Toni. 

\item \tiny \textbf{ <-- End Curr }
      \item \tiny Mgmt:wp: add photos from college. 
      \item \tiny Comm: message to Rishi and Mike about meeting. 
      \item \tiny worklife: read social intelligence. \te{2 hour} 
      \item \tiny Work(psm): do document with slides. \te{10 minutes}.
      \item \tiny Mgmt:Spaces: buy floor mats by BMW. 
      \item \tiny Mgmt:Spaces: get face scrub
      \item \tiny Mgmt:Spaces: ask Mom to get clothes.
      \item \tiny Mgmt:Spaces: get clothes. 
      \item \tiny worklife: practice posing in a picture.  
      \item \tiny Comm: message to girl. \te{10 minutes} \pr{Urgent}. 
      \item \tiny Mgmt:wp: add tags of photos from this past weekend.  
      \item \tiny Mgmt:Spaces: call about Admiral's Club Card.
      \item \tiny Work: IM system for LLNL. 
        
      \end{enumerate}
    \end{block}
  
  % howto: the below is a routine based on the job I'm doing and the
  % circumstances I'm in. Note that this is different from routines
  % above, which is true for a long-term period of over 10 years. 
  \begin{block}{Weekly Meetings}
    \begin{itemize}
      \tiny \item \tiny IWOMP affinity meeting Thursday 7 AM PDT / 9 AM
      CDT call in: 805-639-779 pswd: places. \url{https://llnl.webex.com/llnl/j.php?MTID=m33950b76befb72c0cbc31ea2e3be720c}
    \item \tiny DEG group meeting.          \end{itemize}
  \end{block} 
      \begin{block}{Week Daily Schedule}
        % howto: arrange items from running todo into the below
        % sheet management document. 
        %NOTE: we don't use the table format because of fittting
        \begin{columns}
          \begin{column}{0.14\textwidth}{\small \underline{\bf Mon}}
            {\tiny \bf {\tiny weather:} } {\tiny 11/1 s} \\ 
            {\tiny \bf {\tiny todo}}\\ 
            \begin{itemize}
              \tiny \item \tiny Work: do experiments with multiple nodes. 
            \item \tiny Work: get experiments using real data.  
            \item \tiny 
            \end{itemize}
                {\small  \bf schedule}\\
                \begin{enumerate} 
                  \tiny \item \tiny 8-9AM: Regular Routines 
                \end{enumerate}
          \end{column}

          \begin{column}{0.14\textwidth}{\small \underline{\bf Tues}}
            {\bf {\tiny  weather:} } {\tiny 3/1 r} \\ 
            {\bf {\tiny todo}}\\ 
            \begin{itemize}
              \tiny \item \tiny Work: do write-up 
            \end{itemize} 
                {{\bf {\tiny  schedule}}}
                \begin{enumerate} 
                  \tiny \item \tiny 8-9AM: Regular Routines 
                \end{enumerate} 
          \end{column}
          \begin{column}{0.14\textwidth}{\small \underline{\bf Wed}}
            {\tiny \bf weather: } {\tiny 3/1 r} \\ 
            {\tiny {\bf todo}}\\
            \begin{itemize}
              \tiny \item \tiny Work: send email to Prof. Gropp. 
            \item \tiny 
            \item \tiny Comm: message to Anita. 
            \end{itemize}
                {\tiny \bf schedule}\\
                \begin{enumerate} 
                  \tiny \item \tiny 8-9AM: Regular Routines 
                \end{enumerate} 
          \end{column}

          \begin{column}{0.14\textwidth}{\small \underline{\bf Thurs}}
            {\tiny \bf weather: } {\tiny 1/-1 r }\\ 
            {\tiny \bf todo} \\ 
            \begin{itemize}
              \tiny \item \tiny Add in schedule 
            \item \tiny Work:admin: get slide updated.  
              \item \tiny Work: admin: send cc statement. 

            \end{itemize} 
                {\tiny {\bf schedule}} \\
                \begin{enumerate} 
                  \tiny \item \tiny 8-9AM: Regular Routines 
                \end{enumerate}
          \end{column} 
          
          \begin{column}{0.14\textwidth}{\small \underline{\bf Fri}}
            {\tiny \bf weather: } {\tiny 3/1 r} \\ 
            {\tiny \bf todo} \\ 
            \begin{itemize} 
            \item \tiny Work:rel: cover letter for LLNL.
            \item \tiny Work: e-mail to JP and Steve about acheivements.
            \item \tiny Work: send e-mail. 
            \item \tiny Mgmt:Spaces: give back Internet box. 
            \item \tiny Mgmt:Spaces: get the Driver's License.  
      \item \tiny Mgmt:Spaces: cancel order from LinkedIn premium +
        Mgmt:Spaces:cancel order of Youtube Red. 
            \item \tiny Comm: reply on Coffee Meets Bagel.
            \item \tiny Comm: reply to Aishwarya
            \item \tiny Comm:rel: talk with Vinita. 
                
            \end{itemize} 
                {\tiny \bf schedule} \\
                \begin{enumerate} 
                  \tiny \item \tiny 8-9AM: Regular Routines 
                \end{enumerate}
          \end{column}

          \begin{column}{0.15\textwidth}{\small \underline{\bf Sat}}
            {\tiny \bf weather: } {\tiny 11/1 .2r} \\ 
            { \tiny \bf todo} \\ 
            \begin{itemize}
              \tiny \item \tiny Add in schedule
            \item \tiny 
            \end{itemize} 
                {\tiny \bf schedule} \\
                \begin{enumerate} 
                  \tiny \item \tiny 8-9AM: Regular Routines 
                \end{enumerate}
          \end{column}
         
          \begin{column}{0.15\textwidth}{\small \underline{\bf Sun}}
            {\tiny {\bf weather:} } {\tiny 11/2 r} \\ 
            {\tiny {\bf todo}}\\
            \begin{itemize}
              \tiny \item \tiny Add in schedule
            \end{itemize} 
                {\tiny \bf schedule}\\
                \begin{enumerate} 
                  \tiny \item \tiny 8-9AM: Regular Routines 
                \end{enumerate}
          \end{column}
        \end{columns}
      \end{block}
\end{column}
    
    % ------ Page 2: Column 3
    \begin{column}{0.20\linewidth}
      % ------ Block 2.3.1 
      \begin{block}{Food Plan} 
        \begin{itemize}
          \tiny \item \tiny Google Express: DHDQQJQDRFTXDM95B
        \end{itemize}
      \end{block} 
      \begin{block}{Clothes plan} 
        \begin{itemize}
          \tiny \item \tiny Monday: 
        \item \tiny Tuesday
        \item \tiny Wednesday
        \item \tiny Thursday
        \item \tiny Friday
        \item \tiny Saturday
        \end{itemize} 
      \end{block} 
      
      %-- Block 3-3 
      \begin{block}{Situations}
        % Summary: the below are the situations that define one
        % another.
        % Howto: Put post notes of each situation from list of previous
        % week. Put high importance situations in situationslist. 
        % Put list of upcoming situations on Sunday morning with Pre. 
        \begin{itemize}
          \tiny \item \tiny 
        \item \tiny 
        \end{itemize}
      \end{block}
      % contingincies: 
      % Summary:
    \end{column}
\end{columns}
