\begin{columns}
    %-- Page 2: Column 1 --------------------------------------------------- 
    \begin{column}{0.20\linewidth}
      %{\textbf{\underline{Week Aspects(new name)}})
      %--- Page 2: Block 1-1 
      \begin{block}{Routines}
        { \tiny \underline{\bf Routines:} Morning: bfast, exercise/brush,
          floss, shower (hair, eyes, ears, underarms, feet), meds, belt,
          comb hair / dishes, clean kitchen floor. |  Night: running/ put
          away dishes, clean kitchen floor / brush teeth, charge phone,
          clothes for tomorrow, contacts off.}\\
        {\tiny \underline{\bf Sunday Routines:} Routines:
          Experiences,week plan.}\\ 
        {\tiny \underline{\bf Weekday Routines:}}\\
        %TODO: check if weekday routines overlaps into daily routines.
      \end{block} 
      %--- Page 2: Block 1-3
      \begin{block}{Local Happiness}
        % howto:Recognize emotions / recognize (precisely) what you're
        % worried about -> methods for eliminating worry. 
        % clean out old worries, put them in pastWorries doc.  
        % remember to define precisely 
        % order from top-to bottom
        \begin{itemize} 
          \tiny \item \tiny
        \item \tiny Worrying about gal: think about talking to others.
        \end{itemize} 
      \end{block}
      %--- Page 2: Block 1-4 
      \begin{block}{AngersAndAnxieties}
        % howto:Recognize emotions / recognize (precisely) what you're worried about -> methods for eliminating worry. 
        % clean out old worries, put them in pastWorries doc.  
        % remember to define precisely 
        % order from top-to bottom
        \begin{itemize}
          \tiny \item \tiny Anger about UP -> think about the positive
          perspective, and the original
        \item \tiny Anger about Mr. Kapoor ->  leave it
        \item \tiny Anger about a b  -> ...
        \item \tiny Issue with USC : --> things get better. 
        \end{itemize}
      \end{block}
      %-- Block 1-5
      \begin{block}{Life notes}
        \begin{itemize}
          \tiny \item \tiny Social Intelligence: 
        \end{itemize}
      \end{block}

      % howto:
      \begin{block}
        {\tiny {\bf Week lessons:}}
        \begin{enumerate}
          \tiny \item \tiny Win Friends/ Influence People
        \item \tiny Go through 7 habits.
        \item \tiny Coding problem: 
        \item \tiny Chess tips: 
        \item \tiny tm tips.
        \end{enumerate}
            {{\tiny {\tiny \bf  News:}} {\tiny  M: | S: France's election | E:
              Fallon:   Kimmel:  Colbert: SNL:}}
      \end{block}
    \end{column}
  %-- Column 2 ---------------------------------------------
  \begin{column}{0.6\linewidth}
    \begin{block}{Week Summary} 
      {\underline {\bf Week Plan:}
        Work: run dataset to scale on HPC cluster, Work: make slide
        for ptycholib, Comm: send message to Nitin Mama, Comm: reply
        on  WhatsApp group, Comm: message to Sonali + Comm: message to
      Arch. } \\

      {\underline{\bf Weekend Plan:} }\\
    \end{block}
      \begin{block}{Running ToDo} % find a better name 
        \begin{enumerate} 
          \item \tiny \textbf{Curr} $\rightarrow$
          \item \tiny Work: fix Youssef's code.
          \item \tiny Work: do \texttt{ ln -s} for paper subdirectory
            in bitbucket git repository.
          \item \tiny Work: download ptychoLib from Kaushik and copy
            to git repo.
          \item \tiny Work: discuss work with A rittenbach + Work:
            download driver on GPU4. 
          \doneTask{ Work: kakadu software. }
          \item \tiny Work: run with real dataset if possible. 

          \item \tiny Work: message to meet with Youssef.  

          \item \tiny Work: figure out time to talk with Youssef. 
          \item \tiny Mgmt:Spaces: get car check engine light updated
            + Mgmt:Spaces: do car's registration + Mgmt:Spaces: get
            reimbursements done.
          \item \tiny Mgmt:Spaces: plan trip  to California. = 
            Mgmt:Spaces: get rental car + Mgmt:Spaces: buy ticket from
            D.C. to Baltimore 
            \doneTaskNoItem{Mgmt:Spaces: talk to Ashwin saying that
              works.}  + Mgmt:Spaces: send message to Gopi + 
            \doneTaskNoItem{Mgmt:Spaces: ask Dad for getting miles} +
            Mgmt:Spaces: message to Nitin Mama. 

           \item \tiny Mgmt:wp: post about Tesla's. 
            \item \tiny Mgmt:wp: post about net neutrality. 
            The Internet was incepted with the assumption of network
            neutrality. Let's stick to tradition and keep the Internet
            that way. Support the cause.
            TODO:L4: assumption of network neutrality VS assuming net
            net neutrality.  -done 
            TODO:L4: stick to v VS maintain  -done 
            TODO:L4: and keep the internet that way. 
            TODO:L3: website VS full
            %http://time.com/4770205/john-oliver-fcc-net-neutrality/
            The Internet was incepted with the assumption of network neutrality. Let's stick to tradition and keep the Internet that way. Support the
            cause. \url{http://time.com/4770205/john-oliver-fcc-net-neutrality/} for network neutrality. 
            I support network neutrality.
            Support the cause. 
            Let's make sure that it stick to  I understand that
            companies need to make money, but there's absolutely no
            argument against blocking out smaller tradition.  Net
            neutrality. exactly what we need to fight for.
            
          \item \tiny Mgmt:wp: post about science on FB. 
          \item \tiny Mgmt:wp: post about Queen. 
          \item \tiny Mgmt:wp: Write up on facebook.
           \item \tiny Mgmt:wp: I like Tesla cars and support the company's
             disruption to its industry. At the same time, I don’t think
             that the company will devalue instantaneously the engineering
             accumulated over 8 decades in a BMW.
             {I like cars by Tesla and am supportive of the company’s
               disruptiveness to industry. However, I can’t imagine
               that the company’s cars will make the eight decades of
               engineering that’s in my BMW engine become worthless.
               Tesla technology
               TODO:L3: intent: explain supportiveness of disruptve
               TODO:L3: outcome: people see what I’m about 
               TODO: L4: disruptiveness to industry VS disruption to industry 
               TODO: L4: I have a hard time VS I can’t imagine VS I don’t think  VS 
               TODO:L4: At the same time, VS However, 
               TODO:L4: truly VS [OMIT] 
               TODO:L4: I like VS I love} 
             
           \item \tiny Comm: message to Nitin Mama about meeting his
             father with a picture. 

           \item \tiny Mgmt:wp: update fb with queen's picture. \te{10
             minutes}. 

             \item \tiny Mgmt:wp: send fb like to Deeptha
             \item \tiny Comm: message to Sonali \te{20 minutes}. 

               Hi, This is Vivek from Bharatmatrimony.com. You'd sent
               me a message through the website a few months ago. I'd
               been busy with a job that I started in
               January at University of Southern California and was working in
               Washington, D.C. the last three months for it.
               I'm wondering if you'd like to talk with me by
               phone this weekend, say Saturday at 6:00 PM, for
               fifteen minutes.

               Let me know if you are interested 


             \item \tiny Comm: message to Renata \te{10 minutes}. 

             \item \tiny Comm: send message to meet to Darlene. \te{10
               minutes} 


          \item \tiny Comm: do review for Liberty Towers. 
          \item \tiny \textbf{ <-- End Curr } 
          \item \tiny Work: IM system for LLNL.
        \end{enumerate}
      \end{block}
 
      % howto: the below is a routine based on the job I'm doing and the
      % circumstances I'm in. Note that this is different from routines
      % above, which is true for a long-term period of over 10 years. 

      \begin{block}{Weekly Meetings}
        \begin{itemize}
          \tiny \item \tiny IWOMP affinity meeting Thursday 7 AM PDT / 9 AM
          CDT call in: 805-639-779 pswd: places. \url{https://llnl.webex.com/llnl/j.php?MTID=m33950b76befb72c0cbc31ea2e3be720c}
        \item \tiny DEG group meeting.  
        \end{itemize}
      \end{block} 
      \begin{block}{Week Daily Schedule}
        % howto: arrange items from running todo into the below
        % sheet management document. 
        %NOTE: we don't use the table format because of fittting
        \begin{columns}
          \begin{column}{0.14\textwidth}{\small \underline{\bf Mon}}
            {\tiny \bf {\tiny weather:} } {\tiny 11/1 s} \\ 
            {\tiny \bf {\tiny todo}}\\ 
            \begin{itemize}
              \tiny \item \tiny Work: do experiments with multiple nodes. 
            \item \tiny Work: get experiments using real data.  
            \item \tiny 
            \end{itemize}
                {\small  \bf schedule}\\
                \begin{enumerate} 
                  \tiny \item \tiny 8-9AM: Regular Routines 
                \end{enumerate}
          \end{column}

          \begin{column}{0.14\textwidth}{\small \underline{\bf Tues}}
            {\bf {\tiny  weather:} } {\tiny 3/1 r} \\ 
            {\bf {\tiny todo}}\\ 
            \begin{itemize}
              \tiny \item \tiny Work: do write-up  
            \end{itemize} 
                {{\bf {\tiny  schedule}}}
                \begin{enumerate} 
                  \tiny \item \tiny 8-9AM: Regular Routines 
                \end{enumerate} 
          \end{column}
          \begin{column}{0.14\textwidth}{\small \underline{\bf Wed}}
            {\tiny \bf weather: } {\tiny 3/1 r} \\ 
            {\tiny {\bf todo}}\\
            \begin{itemize}
              \tiny \item \tiny Add in schedule
            \item \tiny -
            \end{itemize} 
                {\tiny \bf schedule}\\
                \begin{enumerate} 
                  \tiny \item \tiny 8-9AM: Regular Routines 
                \end{enumerate} 
          \end{column}

          \begin{column}{0.14\textwidth}{\small \underline{\bf Thurs}}
            {\tiny \bf weather: } {\tiny 1/-1 r }\\ 
            {\tiny \bf todo} \\ 
            \begin{itemize}
              \tiny \item \tiny Add in schedule
            \item \tiny 
            \end{itemize} 
                {\tiny {\bf schedule}} \\
                \begin{enumerate} 
                  \tiny \item \tiny 8-9AM: Regular Routines 
                \end{enumerate}
          \end{column} 
          
          \begin{column}{0.14\textwidth}{\small \underline{\bf Fri}}
            {\tiny \bf weather: } {\tiny 3/1 r} \\ 
            {\tiny \bf todo} \\ 
            \begin{itemize}
              \tiny \item \tiny Add in schedule
            \item \tiny 
            \end{itemize} 
                {\tiny \bf schedule} \\
                \begin{enumerate} 
                  \tiny \item \tiny 8-9AM: Regular Routines 
                \end{enumerate}
          \end{column}

          \begin{column}{0.15\textwidth}{\small \underline{\bf Sat}}
            {\tiny \bf weather: } {\tiny 11/1 .2r} \\ 
            { \tiny \bf todo} \\ 
            \begin{itemize}
              \tiny \item \tiny Add in schedule
            \item \tiny 
            \end{itemize} 
                {\tiny \bf schedule} \\
                \begin{enumerate} 
                  \tiny \item \tiny 8-9AM: Regular Routines 
                \end{enumerate}
          \end{column}
         
          \begin{column}{0.15\textwidth}{\small \underline{\bf Sun}}
            {\tiny {\bf weather:} } {\tiny 11/2 r} \\ 
            {\tiny {\bf todo}}\\
            \begin{itemize}
              \tiny \item \tiny Add in schedule
            \end{itemize} 
                {\tiny \bf schedule}\\
                \begin{enumerate} 
                  \tiny \item \tiny 8-9AM: Regular Routines 
                \end{enumerate}
          \end{column}
        \end{columns}
      \end{block}
\end{column}
    
    % ------ Page 2: Column 3
    \begin{column}{0.20\linewidth}
      % ------ Block 2.3.1 
      \begin{block}{Food Plan} 
        \begin{itemize}
          \tiny \item \tiny Google Express: DHDQQJQDRFTXDM95B
        \end{itemize}
      \end{block} 
      \begin{block}{Clothes plan} 
        \begin{itemize}
          \tiny \item \tiny Monday: 
        \item \tiny Tuesday
        \item \tiny Wednesday
        \item \tiny Thursday
        \item \tiny Friday
        \item \tiny Saturday
        \end{itemize} 
      \end{block} 
      
      %-- Block 3-3 
      \begin{block}{Situations}
        % Summary: the below are the situations that define one
        % another.
        % Howto: Put post notes of each situation from list of previous
        % week. Put high importance situations in situationslist. 
        % Put list of upcoming situations on Sunday morning with Pre. 
        \begin{itemize}
          \tiny \item \tiny Meet with Ashwin. Pre-: dress red, talk
          about life. Post-:

          \tiny \item \tiny Go for Salsa Pre-:  Post-: 

        \item \tiny Meet with Karthik: Pre-:  Post-: 
        \end{itemize}
      \end{block}
      % contingincies: 
      % Summary:
    \end{column}
\end{columns}
