\begin{minipage}{0.5\textwidth}
\begin{itemize}
\tiny \item \tiny do scheduling strategies.
\item \tiny work on job talk.
\item \tiny do travel.
\item \tiny social on facebook, catch up with Rishi.
\end{itemize}
\begin{itemize}
\item \tiny 2-month plan: May: finish documents.  June:  finish paper.
\item \tiny 2-month plan: July: paper, meet people  August: paper, meet people.
\item \tiny 2-month plan: September: paper, meet people  October:
  paper, meet people.
\end{itemize}
\end{minipage}

\begin{multicols}{4}
\begin{minipage}{\columnwidth}
\underline{\bf \tiny {Work:code: PRISMA}}
\begin{enumerate}
\item \tiny Work: fix Youssef's code.
\item \tiny Work: download ptychoLib from Kaushik and copy to git repo.
\item \tiny Work: run for Ptypy.
\item \tiny Work: figure out time to talk with Youssef.
\item \tiny Work: download ptychoLib from Kaushik and copy to git repo.

\item \tiny Work: discuss work with A rittenbach + Work: download
  driver on GPU4.

\item \tiny work: integrate.
\item \tiny Work: do OpenMP 4.5 for ptypy and OpenACC.
\item \tiny Work: run with dataset from PSI.
\item \tiny Work: send message about research paper.
\item \tiny Work: get profiles for PtychoLib code.
\item \tiny Work: write report for spec.
\item \tiny Work: ask for an increase in size for HPCC system.
\end{enumerate}
\end{minipage}

\begin{minipage}{\columnwidth}
\underline{\bf \tiny {Work: PRISMA pubs}}
\begin{enumerate}
\tiny \item \tiny Work: create a latex git repo for paper.
\item \tiny Work: find a conference.
\item \tiny Work: create an outline.
\item \tiny Work: get information about JIT compilation.
\end{enumerate}
\end{minipage}

\begin{minipage}{\columnwidth}
\underline{\bf \tiny {Work: Other work at ISI}}
\begin{enumerate}
\item \tiny Work: get information about JIT compilation.
\end{enumerate}
\end{minipage}

\begin{minipage}{\columnwidth}
\underline{\bf \tiny {Work: OpenMPCon submission}}
\begin{enumerate}
\tiny \item \tiny Work: create a latex git repo for paper.
\item \tiny Work: send Prof. Gropp a message.
\item \tiny Work: make notes on static/dynamic scheduling.
\item \tiny Work: make notes on user-defined scheduling.
\end{enumerate}
\end{minipage}

\begin{minipage}{\columnwidth}
\underline{\bf \tiny {Work: Charm++ +OpenMP}}
\begin{enumerate}
\tiny \item \tiny Work: send notes/tasks todo.
\item \tiny Work: do documentation of implementation.
\item \tiny Do Charm++ + OpenMP implementation.
\item \tiny Get GPU implementation of dotProd in Charm++.
\item \tiny Work: get access to Cori machine.
\item \tiny Work: Add notes about OpenMP.
\item \tiny Work: add explanation of dotProduct on OpenMP.
\end{enumerate}
\end{minipage}

\begin{minipage}{\columnwidth} 
\underline{\bf \tiny {Work: Charm++ +OpenMP}}
\begin{enumerate}
\item \tiny Mgmt:wp: post with friends from college. 
\item \tiny Mgmt:wp: update description.
\item \tiny Mgmt:wp: post about Queen.
\item \tiny Comm:rel: update pictures. \te{30 minutes}.
\end{enumerate}
\end{minipage}

\ifdefined\POSTER
  \begin{columns}
    %-- Column 1 ---------------------------------------------------  
   \begin{column}{0.22\columnwidth}
      \begin{block}{Happiness Generation - must maintain every week.}
\else
 \underline{\bf Happiness Generation - must maintain every week.}
\fi
        % explain happiness: show gratitude   

\begin{itemize}
          \tiny \item \tiny happy that I have Atul to show me.
        %\item \tiny Happy that I have normal life up to this point.                                                   
        %\item \tiny Think about dad saying, I understand, and want     
          %you to be happy.                                                                   
          \item \tiny T
            \end{itemize}
\ifdefined\POSTER
      \end{block}
\fi

\ifdefined\POSTER
    \begin{block}{Habits}
\else
 \underline{\bf \it Habits}
\fi
      \begin{itemize}
        \tiny \item \tiny back straight + eye contact.
      \item \tiny lips relaxed.
      \item \tiny watch what happens when a hot girl talks to you.
      \end{itemize}
\ifdefined\POSTER
    \end{block}
  \end{column} %1 
\fi

\ifdefined\POSTER
  \begin{column}{0.5\columnwidth}
    \begin{block}{10-year plan}   %-- Block 2-1   
\else
 \underline{\bf 10-year plan}
\fi
      \begin{itemize}
      \item \small Make someone and dad proud.
      \end{itemize}
\ifdefined\POSTER
    \end{block}
\fi

\ifdefined\POSTER
    \begin{block}{3-year plan}
\else
\underline{\bf 3-year plan}
\fi
      \begin{itemize}
      \item \small find someone
      \item \small make 150K
      \item \small network
      \end{itemize}
\ifdefined\POSTER
   \end{block}
      \item \tiny watch what happens when a hot girl talks to you.
      \end{itemize}
\ifdefined\POSTER
    \end{block}
  \end{column} %1                                                                                           
\fi

\ifdefined\POSTER
  \begin{column}{0.5\columnwidth}
    \begin{block}{10-year plan}   %-- Block 2-1         
\else
 \underline{\bf 10-year plan}
\fi
      \begin{itemize}
      \item \small Make someone and dad proud.
      \end{itemize}
\ifdefined\POSTER
    \end{block}
\fi

\ifdefined\POSTER
    \begin{block}{3-year plan}
\else
\underline{\bf 3-year plan}
\fi
      \begin{itemize}
      \item \small find someone
      \item \small make 150K
      \item \small network
      \end{itemize}
\ifdefined\POSTER
    \end{block}
\fi

\ifdefined\POSTER
    \begin{block}{6-month plan}
\else
\underline{\bf 6-month plan}
\fi
        \begin{itemize}
          \small \item \small results + thesis
          \item \small routine + worklife
          \item \small
          \end{itemize}
\ifdefined\POSTER
    \end{block}
\fi

\ifdefined\POSTER
    \begin{block}{Month-by-month}
\else
\underline{\bf Month-by-month}
\fi
      %howto: This is most important, and should be re-visited every                          
      %month and definitely every three months(have fixed time within                
      %4 times in the year to do this).                                                                               
      \begin{itemize}
      %\item \small \textit{May:} Work: finish paper  + Work: comm:                                
      %  finish resume and cover letter. 

\ifdefined\POSTER
\begin{block}{May goals}
\else
\underline{\bf May goals}\\
\fi

\begin{enumerate}
\item \small Work: finish writing goals
  \small \item \small Mgmt:Spaces: clean room
\item \small worklife: practice implemented work to form habits
\item \small Comm: meet people
\end{enumerate}

\ifdefined\POSTER
\end{block}
\fi

\ifdefined\POSTER
\begin{block}{\small \bf Week of September $31^{st}$: job search}
\else
\underline{\bf Week of September $31^{st}$: job search}\\
\fi

\begin{enumerate}
\tiny \item \tiny Work: finish connecting with people regarding implementation.
\item \tiny Mgmt:Spaces: take care of driver's license.
\item \tiny
\item \tiny Comm: meet people
\end{enumerate}

\ifdefined\POSTER
\end{block}
\fi

\ifdefined\POSTER
\begin{block}{Weekend Plans - March $15^{th}$, 2017 to May $1^{st}$,2017}
\else
{\underline{\bf Weekend Plans - March $15^{th}$, 2017 to May $1^{st}$,2017}}\\
\fi
\begin{itemize}
\item \tiny Weekend of March $17^{th}$: Visit New York City. Details:
\item \tiny Weekend of March $24^{th}$: Visit San Francisco. Details:
\item \tiny Weekend of March $31^{st}$: Visit San Francisco. Details:
\item \tiny Weekend of April $6^{th}$:  Dad is coming, cherry
  blossoms.
\item \tiny Weekend of April $13^{th}$: Visit India.
\item \tiny Weekend of April $20^{th}$: Go to New York.
\item \tiny Weekend of April $26^{th}$: Go to Los Angeles.
\end{itemize}

{\underline{\bf  Weekend plans for weekends between May $1^{st}$, 2017 and June$1^{st}$, 2017}}\\
\begin{itemize}
\item \tiny Weekend of May $5^{th}$: Visit New York.
\item \tiny Weekend of May $12^{th}$:
\item \tiny Weekend of May $19^{th}$:
\item \tiny Weekend of May $27^{th}$:
\end{itemize}

\ifdefined\POSTER
\end{block}
\fi 

\begin{minipage}{\columnwidth}
\begin{enumerate} 
 \item \tiny Mgmt:Spaces: look for apartment elsewhere. \te{1 hour}. 
\end{enumerate}
\end{minipage} 
\end{multicols}

\begin{columns}
  %-- Page 2: Column 1 --------------------------------------------------- 
  \begin{column}{0.20\linewidth}
    %{\textbf{\underline{Week Aspects(new name)}})
      %--- Page 2: Block 1-1 
    \begin{block}{Routines}
      { \tiny \underline{\bf Routines:} Morning: bfast, exercise/brush,
        floss, shower (hair, eyes, ears, underarms, feet), meds, belt,
        comb hair / dishes, clean kitchen floor. |  Night: running/ put
        away dishes, clean kitchen floor / brush teeth, charge phone,
        clothes for tomorrow, contacts off.}\\
      {\tiny \underline{\bf Sunday Routines:} Routines:
        Experiences,week plan.}\\ 
      {\tiny \underline{\bf Weekday Routines:}}\\
      %TODO: check if weekday routines overlaps into daily routines.
    \end{block} 
      %--- Page 2: Block 1-3
    \begin{block}{Local Happiness}
      % howto:Recognize emotions / recognize (precisely) what you're
      % worried about -> methods for eliminating worry. 
      % clean out old worries, put them in pastWorries doc.  
      % remember to define precisely 
      % order from top-to bottom
      \begin{itemize} 
        \tiny \item \tiny -
      \item \tiny Worrying about gal: think about talking to others.
      \end{itemize} 
    \end{block}
    %--- Page 2: Block 1-4 
    \begin{block}{AngersAndAnxieties}
      % howto:Recognize emotions / recognize (precisely) what you're worried about -> methods for eliminating worry. 
      % clean out old worries, put them in pastWorries doc.  
      % remember to define precisely 
      % order from top-to bottom
      \begin{itemize}
        \item \tiny Issue with USC : $\rightarrow$ things get better. 
        \tiny \item \tiny Anger about UP $\rightarrow$ think about the positive
        perspective, and the original
      \item \tiny Anger about Mr. Kapoor $\rightarrow$  leave it
      \item \tiny Anger about a b  $\rightarrow$ ...
      \end{itemize}
    \end{block}
      %-- Block 1-5
      \begin{block}{Life notes}
        \begin{itemize}
          \tiny \item \tiny Social Intelligence: 
        \end{itemize}
      \end{block}
      % howto:
      \begin{block}
        {\tiny {\bf Week lessons:}}
        \begin{enumerate}
%          \tiny \item \tiny Win Friends/ Influence People
%        \item \tiny Go through 7 habits.
        \item \tiny tm tips.
        \item \tiny Coding problem: 
        \item \tiny Chess tips: 
        \end{enumerate}
            {{\tiny {\tiny \bf  News:}} {\tiny  M: Uber board | S:
                Tony Award's| E: Fallon:  Kimmel:  Colbert: SNL:}}
            {{\tiny {\tiny \bf  Weather:}} {\tiny M: 1100 T: 1100 W:
                0110 R: 0100 F: 0110 Sa: 0110 Su: }}
      \end{block}
  \end{column}
  %-- Column 2 ---------------------------------------------
  \begin{column}{0.6\linewidth}
    \begin{block}{Week Summary} 
      {\underline {\bf Week Plan:} 
        Work: finish writeup, Work: talk about HiVE, Work: talk to
        Youssef, Work: do outline for OpenMPCon, 
        Mgmt:Spaces: flights,  Mgmt:Spaces: look for apartment
        elsewhere, Mgmt:Spaces: car rental, 
        Work:rel: email to Renata, } \\
      {\underline{\bf Weekend Plan:} Meet Puja, Meet Srushti }\\
    \end{block}

      \begin{block}{Running ToDo} % find a better name 
        \begin{enumerate} 
        \tiny \item \tiny \textbf{Curr} $\rightarrow$ 
        \item \tiny Work: send out email for HiPC.
        \item \tiny Work:admin: tell about reimbursements 
        \item \tiny  Mgmt:Spaces: look for apartment elsewhere. 

      \item \tiny Work: do outline for OpenMPCon.
        The presentation will discuss the addition of low-overhead loop scheduling to OpenMP and more generally, user-defined scheduling. We will discuss tips and tricks to use OpenMP loop scheduling in this way, particularly loop transformations for implementing hybrid static/dynamic scheduling through loop transformations.  
As applications and architectures are changing, new methods of distributing work ot cores are needed.  
By using a user-defined schedule in an application program, one can develop new schedules for OpenMP loop scheduling. A user-defined scheduling scheme aprovides flexibility to users and not just developers to allow OpenMP scheduling to be easily developed.
Finally, implementations are difficult to change. 
The following code shows how the user-defined scheduler is used for scheduling loop iterations of a threaded computation region to cores of a node. 
\begin{verbatim}
#pragma omp parallel
{
#pragma omp for schedule(usersched, params, history)
for (int i = 0; i < n; i++)
    sum += a[i]*b[i];
}
\end{verbatim}

The history variable can be used to adjust loop parameters.
The params variable contains a list of parameters that defines the scheduling strategy. 
The usersched function pointer defines the next iteration to dequeue and the queueing variable. 

\begin{verbatim} 

usersched(loop_next, loop_curr)
loop_next( current)
{ 
} 

\end{verbatim} 

Here is an example of the user-defined scheduling to use static/dynamic scheduling, usched as explained in V. Kale et al\cite{}.

\begin{verbatim}
#pragma omp parallel
{
#pragma omp for schedule(usersched:cyclic:fc, params, history)
for (int i = 0; i < n; i++)
    sum += a[i]*b[i];
}
\end{verbatim} 

\begin{verbatim}
#pragma omp parallel
{
#pragma omp for schedule(usersched, params, history)
for (int i = 0; i < n; i++)
    sum += a[i]*b[i];
}
\end{verbatim} 

WRite loop\_next 

Write enqueueue function. 

These two functions are all that is needed to write a scheduler. 
 \item \tiny Work:rel: email to Abid \te{1 hour}. 
 \item \tiny Mgmt:Spaces: return car \te{1 hour}. 

\item \tiny Work: PRISMA tool specification. \te{2 hours}. 
 \item \tiny Work: do outline for OpenMPCon \te{20 minutes}. 
 \item \tiny Work: update paper .tex file with dot prod.  \te{30
   minutes}. 
 \item \tiny Work: do writeup for paper. \te{1 hour}. 
 \item \tiny Work: send message to Youssef about question about
   \texttt{nvprof}. \te{1 hour}. 

 \item \tiny Mgmt:Spaces: book flight for bmm in July \te{1 hour}
 \item \tiny Mgmt:Spaces: book flight for trip in December. \te{1 hour}.
 \item \tiny Mgmt:Spaces: call National for car. \te{10 minutes}. 
 \item \tiny Comm: message to Shalaka? 

 \item \tiny Comm: message to Mamta, 
   Here's my number: 217-369-7996. I'm working for USC. I work in an
   office in the D.C. Area. I'm in Los Angeles this week. 
 \item \tiny Comm: message to Rohina.

 \item \tiny Work:rel: email to Renata. \te{10 minutes}. 
 \item \tiny Work: send message about optimizations to do for
   CkLoop. \te{1 hour} \dl{20 minutes}. 

 \item \tiny Work:rel: email to Renata. \te{10 minutes}.
 \item \tiny worklife: read social intelligence. \te{2 hour}. 

 \item \tiny Mgmt:Health: do dentist appointment. 

 \item \tiny Comm: do review for Liberty Towers.

 \item \tiny Comm: message to Srushti. Ok. I plan to be in New York next weekend. Let me know if you and Ruddhi around and free next Saturday at 7:00 PM. 
   
 \item \tiny \textbf{ <-- End Curr } 
   
 \item \tiny Work: IM system for LLNL.
        \end{enumerate}
      \end{block}
      
      % howto: the below is a routine based on the job I'm doing and the
      % circumstances I'm in. Note that this is different from routines
      % above, which is true for a long-term period of over 10 years. 
      \begin{block}{Weekly Meetings}
        \begin{itemize}
          \tiny \item \tiny IWOMP affinity meeting Thursday 7 AM PDT / 9 AM
          CDT call in: 805-639-779 pswd: places. \url{https://llnl.webex.com/llnl/j.php?MTID=m33950b76befb72c0cbc31ea2e3be720c}
        \item \tiny DEG group meeting.  
        \end{itemize}
      \end{block} 
      \begin{block}{Week Daily Schedule}
        % howto: arrange items from running todo into the below
        % sheet management document. 
        %NOTE: we don't use the table format because of fittting
        \begin{columns}
          \begin{column}{0.14\textwidth}{\small \underline{\bf Mon}}
            {\tiny \bf {\tiny weather:} } {\tiny 11/1 s} \\ 
            {\tiny \bf {\tiny todo}}\\ 
            \begin{itemize}
              \tiny \item \tiny Work: do experiments with multiple nodes. 
            \item \tiny Work: get experiments using real data.  
            \item \tiny 
            \end{itemize}
                {\small  \bf schedule}\\
                \begin{enumerate} 
                  \tiny \item \tiny 8-9AM: Regular Routines 
                \end{enumerate}
          \end{column}

          \begin{column}{0.14\textwidth}{\small \underline{\bf Tues}}
            {\bf {\tiny  weather:} } {\tiny 3/1 r} \\ 
            {\bf {\tiny todo}}\\ 
            \begin{itemize}
              \tiny \item \tiny Work: do write-up 
            \end{itemize} 
                {{\bf {\tiny  schedule}}}
                \begin{enumerate} 
                  \tiny \item \tiny 8-9AM: Regular Routines 
                \end{enumerate} 
          \end{column}
          \begin{column}{0.14\textwidth}{\small \underline{\bf Wed}}
            {\tiny \bf weather: } {\tiny 3/1 r} \\ 
            {\tiny {\bf todo}}\\
            \begin{itemize}
              \tiny \item \tiny Work: send email to Prof. Gropp. 
            \item \tiny 
            \item \tiny Comm: message to Anita. 
            \end{itemize}
                {\tiny \bf schedule}\\
                \begin{enumerate} 
                  \tiny \item \tiny 8-9AM: Regular Routines 
                \end{enumerate} 
          \end{column}

          \begin{column}{0.14\textwidth}{\small \underline{\bf Thurs}}
            {\tiny \bf weather: } {\tiny 1/-1 r }\\ 
            {\tiny \bf todo} \\ 
            \begin{itemize}
              \tiny \item \tiny Add in schedule
            \item \tiny 
            \end{itemize} 
                {\tiny {\bf schedule}} \\
                \begin{enumerate} 
                  \tiny \item \tiny 8-9AM: Regular Routines 
                \end{enumerate}
          \end{column} 
          
          \begin{column}{0.14\textwidth}{\small \underline{\bf Fri}}
            {\tiny \bf weather: } {\tiny 3/1 r} \\ 
            {\tiny \bf todo} \\ 
            \begin{itemize}
              \tiny \item \tiny Add in schedule
            \item \tiny 
            \end{itemize} 
                {\tiny \bf schedule} \\
                \begin{enumerate} 
                  \tiny \item \tiny 8-9AM: Regular Routines 
                \end{enumerate}
          \end{column}

          \begin{column}{0.15\textwidth}{\small \underline{\bf Sat}}
            {\tiny \bf weather: } {\tiny 11/1 .2r} \\ 
            { \tiny \bf todo} \\ 
            \begin{itemize}
              \tiny \item \tiny Add in schedule
            \item \tiny 
            \end{itemize} 
                {\tiny \bf schedule} \\
                \begin{enumerate} 
                  \tiny \item \tiny 8-9AM: Regular Routines 
                \end{enumerate}
          \end{column}
         
          \begin{column}{0.15\textwidth}{\small \underline{\bf Sun}}
            {\tiny {\bf weather:} } {\tiny 11/2 r} \\ 
            {\tiny {\bf todo}}\\
            \begin{itemize}
              \tiny \item \tiny Add in schedule
            \end{itemize} 
                {\tiny \bf schedule}\\
                \begin{enumerate} 
                  \tiny \item \tiny 8-9AM: Regular Routines 
                \end{enumerate}
          \end{column}
        \end{columns}
      \end{block}
\end{column}
    
    % ------ Page 2: Column 3
    \begin{column}{0.20\linewidth}
      % ------ Block 2.3.1 
      \begin{block}{Food Plan} 
        \begin{itemize}
          \tiny \item \tiny Google Express: DHDQQJQDRFTXDM95B
        \end{itemize}
      \end{block} 
      \begin{block}{Clothes plan} 
        \begin{itemize}
          \tiny \item \tiny Monday: 
        \item \tiny Tuesday
        \item \tiny Wednesday
        \item \tiny Thursday
        \item \tiny Friday
        \item \tiny Saturday
        \end{itemize} 
      \end{block} 
      
      %-- Block 3-3 
      \begin{block}{Situations}
        % Summary: the below are the situations that define one
        % another.
        % Howto: Put post notes of each situation from list of previous
        % week. Put high importance situations in situationslist. 
        % Put list of upcoming situations on Sunday morning with Pre. 
        \begin{itemize}
          \tiny \item \tiny 
        \item \tiny 
        \end{itemize}
      \end{block}
      % contingincies: 
      % Summary:
    \end{column}
\end{columns}
