\begin{columns}  %-- Page 2: Column 1 ---------------------------------------------------

\begin{column}{0.10\linewidth}

\begin{block}{Projects}
%Project superspace: mental health

% Project superspace: work 

% Project: Fundamental knowledge. 

% Project space: applications 

\underline{Computational Reqs} 
\underline{\textbf{Deadline:} January $29^{th}$, 2017} 
\begin{enumerate}
\pitem 
\pitem 
\end{enumerate}

\underline{Tomography Code} 
\underline{\textbf{Deadline:} February $4^{th}$, 2017} 
\begin{enumerate}
\pitem 
\pitem 
\end{enumerate}

\underline{Networking Infrastructure} 
\underline{\textbf{Deadline:} September $22^{nd}$, 2017} 
\begin{enumerate}
\pitem 
\pitem 
\end{enumerate}

\underline{Publication} 
\underline{\textbf{Deadline:} September $22^{nd}$, 2017} 
\begin{enumerate}
\pitem 
\pitem 
\end{enumerate}

% Project space: programming and systems

% -- Project: OpenMP 
\underline{OMP proposal} 
\underline{\textbf{Deadline:} September $22^{nd}$, 2017} 
\begin{enumerate}
\pitem 
\pitem 
\end{enumerate} 

% -- Project: CkLoopHyb paper 
\underline{CkLoopHyb paper}
\underline{\textbf{Deadline:} September $22^{nd}$, 2017}
\begin{enumerate}
\pitem Add template to git repository.
\pitem Add writeup for dot product results on Cori.
\pitem Get PIC results with Charm++-everywhere for BW.
\pitem Need a new application.
\ptask Update the paper technique to be consistent with experiments.

\ptask Work: update paper .tex file with dot prod. \te{30
          minutes}.
\ptask Add PAPI cache misses for problem statement.
\ptask Fix diagrams.
\ptask Figure out what to put at the top block of first quadrant.
\ptask Add content in extended paper.
\ptask Add code for PIC in bottom left quadrant.
\ptask Add projections results.
\ptask Add to related work.
\ptask Get PIC results with Charm++-everywhere, Charm++ + CkLoop for Cori.
\ptask Get results for Charm++ + CkLoop for missing data points.
\ptask Show results for dot product using Charm++ + OpenMP, and for
dot product with Charm++ + CkLoop.
\doneTask{ Show code with Charm++ + OpenMP.}
\pitem Merge with git repository.
\pitem Send message to meet for results.
\pitem Work: message to Kathryn about poster.
\end{enumerate}

\underline{Schedule} \\ 
\begin{enumerate}
\pitem 
\end{enumerate} 
\end{block} 

%Project: interviewing 
\underline{Interviewing} 
\underline{\textbf{Deadline:}    }  
\begin{enumerate}
\pitem 
\pitem 
\end{enumerate} 

%Project: extra-curricular 


\begin{block}{Year Plan}
\begin{itemize}
\tiny \item \tiny January: Work: interview, application. , Mgmt:Spaces: get dl , Mgmt:Spaces: get cc, Comm: 
\item \tiny February: Work: proposal, Work: implementation, Mgmt:Spaces: 
\item \tiny March: Work: paper for IWOMP, Work: job talk prep.
\item \tiny April: Work: paper for IWOMP, Work: implementation  
\item \tiny May: Work: do paper, Work: Comm: 
\item \tiny June: Work: work on implementation with UDS 
\item \tiny July: Work: work on implementation with UDS Comm:  
\item \tiny August: Work: paper for IPDPS, 
\item \tiny September: Work: paper for IPDPS 
\item \tiny October: Work: paper for IPDPS  
\item \tiny November: Work: SC stuff, 
\item \tiny December: 
\end{itemize} 
\end{block}


\begin{block}{Month Plan}
\underline{Week of January $31^{st}$, 2018}
\begin{itemize}
\tiny \item \tiny Work: 
\item \tiny Mgmt:Spaces: 
\item \tiny Comm: 
\end{itemize}

\underline{Week of February $4^{th}$, 2018}
\begin{itemize}
\tiny \item \tiny Work: send in cover letter + Work: finish application.  
\item \tiny Mgmt:Spaces: 
\item \tiny Comm: 
\end{itemize}


\underline{Week of February $9^{th}$, 2018}
\begin{itemize}
\tiny \item \tiny Work: 
\item \tiny
\end{itemize}

\underline{Week of February $16^{th}$, 2018}
\begin{itemize}
\tiny \item \tiny 
\item \tiny
\end{itemize}
\end{block}

\end{column}
  \begin{column}{0.10\linewidth}
    %{\textbf{\underline{Week Aspects(new name)}})
      %--- Page 2: Block 1-1 
    \begin{block}{Routines}
      { \tiny \underline{\bf Routines:} Morning: bfast, exercise/brush,
        floss, shower (hair, eyes, ears, underarms, feet), meds, belt,
        comb hair / dishes, clean kitchen floor. |  Night: running/ put
        away dishes, clean kitchen floor / brush teeth, charge phone,
        clothes for tomorrow, contacts off.}\\
      {\tiny \underline{\bf Sunday Routines:} Routines:
        Experiences,week plan.}\\ 
      {\tiny \underline{\bf Weekday Routines:}}\\
      %TODO: check if weekday routines overlaps into daily routines.
    \end{block} 
      %--- Page 2: Block 1-3
    \begin{block}{Local Happiness}
      % howto:Recognize emotions / recognize (precisely) what you're
      % worried about -> methods for eliminating worry. 
      % clean out old worries, put them in pastWorries doc.  
      % remember to define precisely 
      % order from top-to bottom
      \begin{itemize} 
        \tiny \item \tiny -
      \item \tiny Worrying about gal: think about talking to others.
      \end{itemize} 
    \end{block}
    %--- Page 2: Block 1-4 
    \begin{block}{AngersAndAnxieties}
      % howto:Recognize emotions / recognize (precisely) what you're worried about -> methods for eliminating worry. 
      % clean out old worries, put them in pastWorries doc.  
      % remember to define precisely 
      % order from top-to bottom
      \begin{itemize}
        \item \tiny Issue with USC : $\rightarrow$ things get better. 
        \tiny \item \tiny Anger about UP $\rightarrow$ think about the positive
        perspective, and the original
      \item \tiny Anger about Mr. Kapoor $\rightarrow$  leave it
      \item \tiny Anger about a b  $\rightarrow$ ...
      \end{itemize}
    \end{block}
      %-- Block 1-5
      \begin{block}{Life notes}
        \begin{itemize}
          \tiny \item \tiny Social Intelligence: 
        \end{itemize}
      \end{block}
      % howto:
      \begin{block}
        {\tiny {\bf Week lessons:}}
        \begin{enumerate}
        \item \tiny tm tips.
        \item \tiny Coding problem: 
        \item \tiny Chess tips: 
        \end{enumerate}
            {{\tiny {\tiny \bf  News:}} {\tiny  M:  | S: 
                | E: Fallon:  Kimmel:  Colbert: SNL:}}
            {{\tiny {\tiny \bf  Weather:}} {\tiny M: 1100 T: 1100 W: 41/34 .1r 
                 R: 51/46 .60r F: 62/36 .7r a Sa: 42/20 .10r Su: 31/17 }} 

           % \input{weather} 
      \end{block}
  \end{column}
  %-- Column 2 ---------------------------------------------
  \begin{column}{0.6\linewidth}
    \begin{block}{Week Summary}
      {\underline {\bf Week Plan:}  Work:admin: business cards, Work:admin:
        finish re-imbursements, Mgmt:Spaces: get dl, Work: contact for
        UDS, Work:rel: send out the LLNL application + Work:rel:
        message to Nathan, Work:rel: send out cover letter, 
        Work:  , Comm: upload pictures,
 }\\


{\underline{\bf Weekend Plan:} Meet Dhanashree. } \\

    \end{block}
    \begin{block}{Running ToDo} % find a better name 
      \begin{enumerate}
        \doneTask{ Work: talk with JP about travel. } 
        \doneTask{ Work:rel: add name to TWiki  OpenMP. }
        \doneTask{Comm: message to Aishwarya.} 
        \doneTask{ Work: admin: send e-mail to Tom Gioconda. }

      \doneTask{ Work:(uds:sld): do slides for UDS = Work(uds:sld):
        update the slide to clarify the UDS limitation +
        Work(uds:sld): add static/dynamic schedule + Work(uds:sld):
        add results to slide + Work(uds:sld): compress certain
        slides.} 
      \doneTask{ Comm: text message to Rathi := 'I'm in Baustin.'}
        \te{20 minutes} \pr{IU }
      \doneTask{ Work: admin: send message to Claire.} \te{20 minutes}. 
        
      \item \tiny \textbf{Curr} $\rightarrow$ 
      \item \tiny worklife: make projects list.


      \item \tiny Work:rel:cvl:upd):  do cover letter for LLNL = Work: rel:
        explain reason for wanting to join LLNL + Work:rel:(cvl):
        explain your contributions.  \te{1 hour} 
      \item \tiny Work:rel: send out LLNL application. \te{1 hour}
        \dl{Wednesday}. 
      \item \tiny Work: send slides to Nathan. \te{30 minutes}. 

      \item \tiny Mgmt:wp: add people to LinkedIn =  Mgmt:wp: add Andy Schmidt on LinkedIn. +  Mgmt:wp: add Mike Kumbera to LinkedIn +  Mgmt:wp: add Olga to LinkedIn + Mgmt:wp: add Ignacio to LLinkedIN. + Mgmt:wp: add Marty. 

      \item \tiny Work: send information on publication to Steve and JP.  \te{20 minutes}. 
        
      \item \tiny Work:rel: do application for HLFF = Work:rel: get degree
        certificate + Work:rel: add research statement + Work:rel: write
        letter of motivation. 



      \item \tiny Work: admin: finish re-imbursements for Denver =
        Work:admin: get flight to DC. 
        



      \item \tiny Mgmt:Spaces: get glasses. 
      \item \tiny Mgmt:Spaces: get driver's license from VA. 
        

        \item \tiny Comm: upload pictures. 
        \item \tiny Comm: upload photos. 
          
        \item \tiny Work:admin: submit receipts for Bagel. 
          
          
          \tiny \item[] \tiny \textbf{Curr} $\rightarrow$
          
        \item \tiny Work: finish proposal slides. 
        \item \tiny Work:rel: do cover letter for BNL + Mgmt:Spaces: talk with
          Martin Kong.
    
      \item \tiny Comm: photo upload. 
                
        \item \tiny Work: send in application to PNNL.
          
        \item \tiny Mgmt:wp: add profile.
        \item \tiny Mgmt:wp: add about me. 
          
        \item \tiny Mgmt:wp: add profile 
        \item \tiny Work:rel: email to Renata. \te{10 minutes} 
        \item \tiny Comm: message to Sateja. 
          Hey, I followed you on LinkedIn. I think your work is really good. 
          Let me know if you want to grab coffee sometime in the city. 
        \item \tiny Comm:rel: talk to Shweta.
        \item \tiny Comm: talk with Toni. 
          
\item \tiny \textbf{ <-- End Curr }
      \item \tiny Mgmt:wp: add photos from college. 
      \item \tiny Comm: message to Rishi and Mike about meeting. 
      \item \tiny worklife: read social intelligence. \te{2 hour} 
      \item \tiny Mgmt:Spaces: get face scrub. 
      \item \tiny worklife: practice posing in a picture.  
      \item \tiny Work: IM system for LLNL.  
      \end{enumerate}
    \end{block} 

\begin{block}{DayPlans} 

  Sunday:   
  | Monday:  
  | Tuesday:  
  | Wednesday: 

  | Thursday: Work:admin: send Claire message,
  Work: send message to Steve about poster,  
  Work: send e-mail to Nathan, 
  Work: send application to LLNL, 
  Work:rel: send LinkedIn - Olga, Ignacio, Andy Schmidt, 
  Comm: send Rathi a message, 

| Friday: 
| Saturday:  
\end{block}

\begin{block}{Alg for Mgmt}
Alg for Mgmt:Alg for Comm   L0:  L1:  L2:  L3:  Maps L4: L5: -> L0
TODO:  and prioritize . Use colors for levels Howto:  
\end{block} 

\begin{block}{Meeting Information}
BlueJeans meeting ID: 8562450706.
Webex MeetingID: 805639779  
\end{block} 

\begin{block}{Situations} 
\begin{enumerate}
\item Meet Rathi: 
\item Meet Dhanashree:
\end{block}

\begin{block}{Rel}
Rel-chat-short: Toni, Mamta S., Bhakti J., Shalaka K , Sonia B., 
Rel-chat:  cat1  Toni,, S Van., Bhakti, Shalaka/Rucha, Sateja P, Anuja
D. ,  Divya, cat2: sonal mukhi, Mamta, sapana/india, Avani, cat 3:
Shilpa Ghate, Renuka, Renata, 
\end{block}

  
  % howto: the below is a routine based on the job I'm doing and the
  % circumstances I'm in. Note that this is different from routines
  % above, which is true for a long-term period of over 10 years. 
  \begin{block}{Weekly Meetings}
    \begin{itemize}
      \tiny \item \tiny IWOMP affinity meeting Thursday 7 AM PDT / 9 AM
      CDT call in: 805-639-779 pswd: places. \url{https://llnl.webex.com/llnl/j.php?MTID=m33950b76befb72c0cbc31ea2e3be720c}
    \item \tiny DEG group meeting.          \end{itemize}
  \end{block} 

      \begin{block}{Week Daily Schedule}
        % howto: arrange items from running todo into the below
        % sheet management document. 
        %NOTE: we don't use the table format because of fittting
        \begin{columns}
          \begin{column}{0.14\textwidth}{\small \underline{\bf Mon}}
            {\tiny \bf {\tiny weather:} } {\tiny 11/1 s} \\ 
            {\tiny \bf {\tiny todo}}\\ 
            \begin{itemize}
              \tiny \item \tiny Work: do experiments with multiple nodes. 
            \item \tiny Work: get experiments using real data.  
            \item \tiny 
            \end{itemize}
                {\small  \bf schedule}\\
                \begin{enumerate} 
                  \tiny \item \tiny 8-9AM: Regular Routines 
                \end{enumerate}
          \end{column}

          \begin{column}{0.14\textwidth}{\small \underline{\bf Tues}}
            {\bf {\tiny  weather:} } {\tiny 3/1 r} \\ 
            {\bf {\tiny todo}}\\ 
            \begin{itemize}
              \tiny \item \tiny Work: do write-up 
            \end{itemize} 
                {{\bf {\tiny  schedule}}}
                \begin{enumerate} 
                  \tiny \item \tiny 8-9AM: Regular Routines 
                \end{enumerate} 
          \end{column}
          \begin{column}{0.14\textwidth}{\small \underline{\bf Wed}}
            {\tiny \bf weather: } {\tiny 3/1 r} \\ 
            {\tiny {\bf todo}}\\
            \begin{itemize}
              \tiny \item \tiny Work: send email to Prof. Gropp. 
            \item \tiny 
            \item \tiny Comm: message to Anita. 
            \end{itemize}
                {\tiny \bf schedule}\\
                \begin{enumerate} 
                  \tiny \item \tiny 8-9AM: Regular Routines 
                \end{enumerate} 
          \end{column}

          \begin{column}{0.14\textwidth}{\small \underline{\bf Thurs}}
            {\tiny \bf weather: } {\tiny 1/-1 r }\\ 
            {\tiny \bf todo} \\ 
            \begin{itemize}
              \tiny \item \tiny Add in schedule 
            \item \tiny Work:admin: get slide updated.  
              \item \tiny Work: admin: send cc statement. 

            \end{itemize} 
                {\tiny {\bf schedule}} \\
                \begin{enumerate} 
                  \tiny \item \tiny 8-9AM: Regular Routines 
                \end{enumerate}
          \end{column} 
          
          \begin{column}{0.14\textwidth}{\small \underline{\bf Fri}}
            {\tiny \bf weather: } {\tiny 3/1 r} \\ 
            {\tiny \bf todo} \\ 
            \begin{itemize} 
            \item \tiny Work:rel: cover letter for LLNL.
            \item \tiny Work: e-mail to JP and Steve about acheivements.
            \item \tiny Work: send e-mail. 
            \item \tiny Mgmt:Spaces: give back Internet box. 
            \item \tiny Mgmt:Spaces: get the Driver's License.  
      \item \tiny Mgmt:Spaces: cancel order from LinkedIn premium +
        Mgmt:Spaces:cancel order of Youtube Red. 
            \item \tiny Comm: reply on Coffee Meets Bagel.
            \item \tiny Comm: reply to Aishwarya
            \item \tiny Comm:rel: talk with Vinita. 
                
            \end{itemize} 
                {\tiny \bf schedule} \\
                \begin{enumerate} 
                  \tiny \item \tiny 8-9AM: Regular Routines 
                \end{enumerate}
          \end{column}

          \begin{column}{0.15\textwidth}{\small \underline{\bf Sat}}
            {\tiny \bf weather: } {\tiny 11/1 .2r} \\ 
            { \tiny \bf todo} \\ 
            \begin{itemize}
              \tiny \item \tiny Add in schedule
            \item \tiny 
            \end{itemize} 
                {\tiny \bf schedule} \\
                \begin{enumerate} 
                  \tiny \item \tiny 8-9AM: Regular Routines 
                \end{enumerate}
          \end{column}
         
          \begin{column}{0.15\textwidth}{\small \underline{\bf Sun}}
            {\tiny {\bf weather:} } {\tiny 11/2 r} \\ 
            {\tiny {\bf todo}}\\
            \begin{itemize}
              \tiny \item \tiny Add in schedule
            \end{itemize} 
                {\tiny \bf schedule}\\
                \begin{enumerate} 
                  \tiny \item \tiny 8-9AM: Regular Routines 
                \end{enumerate}
          \end{column}
        \end{columns}
      \end{block}
\end{column}
    
    % ------ Page 2: Column 3
    \begin{column}{0.20\linewidth}
      % ------ Block 2.3.1 
      \begin{block}{Food Plan} 
        \begin{itemize}
          \tiny \item \tiny Google Express: DHDQQJQDRFTXDM95B
        \end{itemize}
      \end{block} 
      \begin{block}{Clothes plan} 
        \begin{itemize}
          \tiny \item \tiny Monday: 
        \item \tiny Tuesday
        \item \tiny Wednesday
        \item \tiny Thursday
        \item \tiny Friday
        \item \tiny Saturday
        \end{itemize} 
      \end{block} 
      
      %-- Block 3-3 
      \begin{block}{Situations}
        % Summary: the below are the situations that define one
        % another.
        % Howto: Put post notes of each situation from list of previous
        % week. Put high importance situations in situationslist. 
        % Put list of upcoming situations on Sunday morning with Pre. 
        \begin{itemize}
          \tiny \item \tiny 
        \item \tiny 
        \end{itemize}
      \end{block}
      % contingincies: 
      % Summary:
    \end{column}
\end{columns}
