\begin{frame}
  \begin{columns}
    %-- Column 1 --------------------------------------------------- 
    \begin{column}{0.25\linewidth} %{\textbf{\underline{Week Aspects(new name)}}}
      \begin{block}{Local Happiness}
        % howto:Recognize emotions / recognize (precisely) what you're worried about -> methods for eliminating worry. 
        % clean out old worries, put them in pastWorries doc.  
        % remember to define precisely 
        % order from top-to bottom 
        \begin{itemize}
          \tiny \item \tiny Work: worrying about interviewing: just focus on the work. 
        \item \tiny Worrying about gal: think about talking to others. 
        \end{itemize}
      \end{block}
      \begin{block}{Stresses}
        % howto:Recognize emotions / recognize (precisely) what you're worried about -> methods for eliminating worry. 
        % clean out old worries, put them in pastWorries doc.  
        % remember to define precisely 
        % order from top-to bottom
        \begin{itemize}
          \tiny \item \tiny Work(
          \item \tiny Anger about a b  -> ...
          \item \tiny Anger about UP -> think about the positive
            perspective, and the original
          \item \tiny Anger about dad saying things 
        \end{itemize}
      \end{block}    
      %-- Block 1-3 
      \begin{block}{Life notes}
        \begin{itemize}
        \item \tiny TM: look at last chapter of emotional
          intelligence.  
        \item \tiny Problem: implement game of mastermind. 
        \end{itemize}
      \end{block}
    \end{column} %2

    %-- Column 2 --------------------------------------------- 
    \begin{column}{0.50\linewidth}
      %--- Block 2-1

      \begin{block}{Routines}
        Morning: exercise, brush, floss, shower (hair, eyes, ears,
        underarms, feet), meds,  belt, comb hair,  Night: brush teeth, charge
        phone, clothes for tomorrow, contacts off. 
      \end{block}

      \begin{block}{Week Summary}
        {\tiny \textbf{Week Plan:} Work: do postdoc work, Work:rel:
          prep for fb, Work: do slides, Comm: experience writing}

        {\tiny \textbf{Weekend Plan:} Mgmt:Spaces: check hotel} 
          Mgmt:Spaces: car wash for camry, worklife: car wash notes, 
          Work: slides, Work: code for Simon}  
      \end{block}


      \begin{block}{Running TODO} % find a better name 
        \begin{enumerate}
 
          \doneTask{Work:admin(at): Aachen travel = Work:admin(at): send
            message to Jill Peckham + Work:admin(at): book flight +
            Work:admin(at): book hotel} 

      \small \item \small Work(sa): send MPI+OpenACC code
     \doneTask{ Comm(apmsg): send Anita message about
      leaving}

      \small \item \small Mgmt:Spaces (meds): get meds done = 
      \doneTaskNoItem{Mgmt:Spaces(meds): fill out sheet} +
      Mgmt:Spaces(meds): call for appt. 

    \item \small Work:rel(jobs): follow-up from jobs = Work:rel(jobs):
      follow-up from jobs for fb + (Work:rel(jobs): send times that
      work). 
      
    \item \small Work:rel:  follow-up from HLF = Work:rel: message to
      Fred Brooks + Work:rel: talk to Alessandro. 


    \doneTask{ Work:rel:(wl): respond to Cray. }
     \doneTask{ Mgmt:Spaces: netip registration}  \te{30 minutes}  
    \item \small Mgmt:Spaces(pk): Packing = 
      Mgmt:Spaces(pk): charger +Mgmt:Spaces(pk): adapter 
      + Mgmt:Spaces(pk): shoes  + 
      Mgmt:Spaces(pk): belt + 
      Mgmt:Spaces(pk):undershirts  =
      (Mgmt:Spaces(pk):two black + Mgmt:Spaces(pk):two white) 
      \doneTaskNoItem{Mgmt:Spaces(pk): Passport}
      + \doneTaskNoItem{Mgmt:Spaces(pk): 6 underwear} +
      \doneTaskNoItem{Mgmt:Spaces(pk): 8 socks} +
      \doneTaskNoItem{Mgmt:Spaces: 4 shirts} + Mgmt:Spaces(pk): 4 


      \doneTask{ Work:rel(ora): respond to Oracle \te{1 hour} 
      Work:rel(ora): Here is my resume + Work:rel(ora): don't
      distribute + Work:rel(ora): busy for the next couple of days and
      am going to Europe. }

      \doneTask{ Work:comm(fresp): respond to Jon Freund =
      Work:comm(fresp): Say title of "Low-overhead Loop Scheduling" +
      Work:comm(fresp): Say that the content makes sense + 
      Work:comm(fresp): I'll actually be presenting work at IWOMP this
      week. I can get a better picture afterwards. I'm making some
      slides and can provide a description later.} 

    \doneTask{ Mgmt:Spaces(pk): netip registration } \te{1 hour}
      \dl{10 minutes} \pr{U}

    \item \small Comm: add Toastmaster's roles \te{1 hour}.
    \item \small Comm: add TM roles \te{1 hour}  
      
      \small \item \small Work: send MPI+OpenACC code to Simon = Work: write
      MPI+OpenACC code + Work: send MPI+OpenACC code + Work(oac):  add
      MPI assignment + Work(oac): put MPI reduction stuff + Work(oac):
      put MPI into code. 

      \doneTask{ Work(jlarson): reply to John} 


      \tiny \item \tiny Work(iwoSldwrite): write Iwomp slides =
      Work(iwompSldWrite): organize based on outline + 
      Work(iwompSldWrite): expand on the composition. 
       \item \tiny Work(iwoSld): send slides to Prof. Gropp =  
       \item \tiny Work(iwoprep): send question to Christian = 

         % curr --> 

       \item \tiny Work(simon): reply to Simon 

       \item \small Work(jl): send message to everyone that the 
         data transfer isn't big. 


       \item \tiny Comm: send message to Anita. \te{10 minutes}
         \dl{Saturday afternoon} \p{UandabitImportant}

       \item \tiny Mgmt:Spaces: 
       \item \tiny Comm: facebook picture. \t{10 minutes}  \d{ Sunday}
         \p{UI}. 


       \item \tiny Work:rel: add on linked in Ashif
       \item \tiny Work: send message to Professor Gropp for meeting. 

       \item \tiny Mgmt:Spaces: get appointment for meds. \t{10 mins}
         \d{Sunday} \p{UI},

       \item \tiny Mgmt:Spaces: 

        \end{enumerate}
      \end{block} 

      \begin{block}{Week Daily Schedule} 


        % howto: arrange items from running todo into the below
        % sheet management document. 

\comments{
        \begin{columns} 
          \column{0.14\textwidth}{\textbf{\small \underline{Mon}}}
          \textbf{\small todo} \\ 
          \begin{itemize}
            \tiny \item \tiny 
          \item \tiny 
          \end{itemize} 
          \textbf{\small schedule} \\
          \begin{enumerate} 
            \tiny \item \tiny 8-9AM: Regular Routines 
          \end{enumerate} 
          
          \column{0.14\textwidth}{\textbf{\small \underline{Tue}}}
          \textbf{\small todo} \\
          \begin{itemize}
            \tiny \item \tiny Work: make project sheet \te{10 minutes} 
          \item \tiny Mgmt:Spaces: check for diploma \te{10 minutes} 
          \end{itemize}  
          \textbf{\small schedule} 
          \begin{enumerate}
            \tiny \item \tiny 10AM - 11AM = 
          \item \tiny 11AM - 12AM = make long-term goals 
          \item \tiny 12PM - 2PM = 
            \tiny \item \tiny 2PM -3PM = 
          \item \tiny 6PM - 10PM = 
          \end{enumerate}  
          
          \column{0.14\textwidth}{\textbf{\small {\underline{Wed}}}}
          \textbf{\small todo} \\
          \begin{itemize}
           \tiny \item \tiny Work: finish slides for tomorrow. 
           \item \tiny Mgmt: Spaces: update fb 
         \item \tiny Comm: fb update 
          \end{itemize}
          \textbf{\small schedule} \\
          \begin{enumerate}
            \tiny \item \tiny 8-9AM: Regular Routines 
          \item \tiny 9AM - 10AM: Send message 
            \item \tiny 6:30PM - 7:30PM = 
          \end{enumerate} 
          \column{0.14\textwidth}{\textbf{\small{\underline{Thu}}}}
          \textbf{\small todo}\\
          \begin{itemize}  
            \tiny \item \tiny 
          \item \tiny 
          \end{itemize} 

          \textbf{\small schedule}\\
          \begin{enumerate} 
            \tiny \item \tiny 8-9AM = Regular Routines 
            \item \tiny 12-1PM = gather notes about job org. during
              session 
            \item \tiny 3:30PM - 4:30PM = meeting 
            \item \tiny 6PM - 9PM = revise emot. int. chapter and
              structure wl-cheat based on it 
          \end{enumerate} 
          
          \column{0.14\textwidth}{\textbf{\small{\underline{Fri}}}}
          \textbf{\small todo}\\ 
          \begin{itemize}
            \tiny \item \tiny Work: updates on GPU \dl{} \te{} \prio{}
          \item \tiny \te{1 hour} 
          \end{itemize}
          \textbf{\small schedule}\\
          \begin{enumerate}
            \tiny \item \tiny 8-9AM: Regular Routines 
          \end{enumerate}
          
          \column{0.14\textwidth}{\textbf{\small \underline{Sat}}}
          \textbf{\small todo}\\
          \begin{itemize} 
            \tiny \item \tiny
          \end{itemize}
          \textbf{\small schedule}\\ 
          \begin{enumerate}
            \tiny \item \tiny 7-7:30PM = food + organize.  
            \tiny \item \tiny 7:30PM -8PM = 
            \tiny \item \tiny 8PM -9PM = 
            \tiny \item \tiny 9:45PM - 10:30PM = go out 
            \tiny \item \tiny 2AM -3AM =  message Samir + add people
          \end{enumerate}
          
          \column{0.14\textwidth}{\textbf{\small \underline{Sun}}}
          \textbf{\small todo}\\
          \begin{itemize} 
           \tiny \item \tiny 
          \end{itemize}

          \textbf{\small schedule}\\
          \begin{enumerate} 
            \tiny \item \tiny 3PM - 4PM  =
          \item \tiny 5-7PM = Comm work 
          \item \tiny 8PM - 10PM = worklife work. 
          \end{enumerate} 
        \end{columns}
      \end{block}
    \end{column}%2
    
}

    %-- Column 3 --------------------------------------------------- 
    \begin{column}{0.20\linewidth}
      %-- Block 3-1 
      % On Sunday morn, put a quick synopsis of top news items           
      % here.  Categorize as Comm and Money.      
      \begin{block}{News}
        \begin{itemize} 
          \tiny \item \tiny 
        \item \tiny Debates
        \end{itemize}
      \end{block}
      
      \begin{block}{Weather} 
        \begin{itemize}
          \tiny \item \tiny 
        \item \tiny 
        \end{itemize}
      \end{block} 

      \begin{block}{Clothes plan} 
        \begin{itemize}
          \tiny \item \tiny Monday
        \item \tiny Tuesday 
        \item \tiny Wednesday
        \item \tiny Thursday
        \item \tiny Friday
        \end{itemize} 
      \end{block}
      %-- Block 3-2 
      
      %-- Block 3-3
      \begin{block}{Situations}
        % Howto: the below are the situations that define one another

        \begin{itemize} 

        \item \tiny \item 

          \tiny \item \tiny \comments{Main} \textit{Pandharipande
            meet} Pre-: 

          clothes: 
          topics: exp: hlf meeting with vint cerf L0: talk about pandharipande  L1:    L2:     L3:  L4:   L5: 

           Post-: 
          
           \tiny \item \tiny \textit{breakfast} Pre-: Post-: use knife and
           fork to avoid bread pieces, use both utensils to avoid
           getting hands dirty, don't eat while standing 
          \tiny \item \tiny \textit{meet with advisor} Pre-: check
          email periodically when sent. Post-: 
        \item \tiny \textit{Group meeting} Pre-: don't get
          distracted. 
        \end{itemize} 

      \end{block}
      
\begin{block}{Rel}
  \begin{itemize} 
    \small \item \small Girl from SF 
    \small \item \small Girl from L.A. 
    \small \item \small Mamta 

    %\small \item \small Ruchi 
    %\small \item \small Neha Jambhekar 
    %\small \item \small Meghan Joshi 
    %\small \item \small Vinita Ghate 
  \end{itemize} 
\end{block} 
\end{column}%3 

\end{columns}

\end{frame}

