%TODO: make outer file containing this file for compilation 
\begin{frame}
  \begin{columns}
    %-- Column 1 --------------------------------------------------- 
    \begin{column}{0.25\linewidth} %{\textbf{\underline{Week Aspects(new name)}}}
      \begin{block}{Local Happiness}
        % howto:Recognize emotions / recognize (precisely) what you're worried about -> methods for eliminating worry. 
        % clean out old worries, put them in pastWorries doc.  
        % remember to define precisely 
        % order from top-to bottom 
        \begin{itemize}
          \tiny \item \tiny Work: worrying about interviewing: just focus on the work. 
        \item \tiny Worrying about gal: think about talking to others. 
        \end{itemize}
      \end{block}
      \begin{block}{Stresses}
        % howto:Recognize emotions / recognize (precisely) what you're worried about -> methods for eliminating worry. 
        % clean out old worries, put them in pastWorries doc.  
        % remember to define precisely 
        % order from top-to bottom
        \begin{itemize}
          \tiny \item \tiny Work 
          \item \tiny Anger about a b  -> ...
          \item \tiny Anger about UP -> think about the positive
            perspective, and the original
          \item \tiny Anger about dad saying things 
        \end{itemize}
      \end{block} 
      %-- Block 1-3 
      \begin{block}{Life notes}
        \begin{itemize}
        \item \tiny TM: look at last chapter of emotional
          intelligence.  
        \item \tiny Problem: implement game of mastermind. 
        \end{itemize}
      \end{block}
    \end{column} %2 

    %-- Column 2 --------------------------------------------- 
    \begin{column}{0.50\linewidth}
      %--- Block 2-1

      \begin{block}{Routines}
        Morning: exercise, brush, \underline{floss}, shower (hair, eyes, ears,
        underarms, feet), meds,  belt, comb hair, Night: brush teeth, charge
        phone, clothes for tomorrow, contacts off.  
      \end{block}

      \begin{block}{Week Summary}
        {\tiny \textbf{Week Plan:} 

          Work: finish code for job submission for GPU 
          Work: admin: finish re-imbursements, 
          Work: rel: send message to LBL, 
          Work: do practice problems for interviews, 
          Mgmt:Spaces: pay ptickets, 
          Comm: --, 
          
        } 

        {\tiny \textbf{Weekend Plan:}  Mgmt:Spaces: pay tickets, Work:
          finish code, Comm: catch up with people, 
      }

      \end{block}

          %infiniti / mercedes / acura / lexus 

      \begin{block}{Running TODO} % find a better name 
        \begin{enumerate}

        %\item \tiny Work: finish time planning = Mgmt:Time(tp): do
        %  weekend plans through December 15th  + Mgmt:Time(tp): do
        %  planning through December 15th.
        \tiny \item \small Work:rel: follow-up from HLF = Work:rel: message to
          Fred Brooks + Work:rel: talk to Alessandro. 

          % --> curr  

        \item \tiny Work(SCemails): send message to Heidi about Cray
         MPI+OpenACC (PGI) compiler on BlueWaters +
         Work(SCemails): send message to Amanda to meet. 

       \item \tiny Work(WorkEmail): send message to Luke about
         meeting. 

       \doneTask{Work(WorkEmail): send message to Prof. Gropp
         about 2-week notice.} 
         \doneTask{Work(amanda): message to Amanda} 

       \doneTask{ Mgmt:Spaces: call for doctor's appt.} \te{10
         minutes} 
  
     \item \tiny Work(IntelEmails): send message to Jeff Hammond. 

     \doneTask{ Work: comm:(msgToGropp):  send message to Gropp about
       leaving }
     
   \item \tiny Comm: message to dp \te{10 minutes}
   \item \tiny Comm: message to Shikha \te{10 minutes} - Hi Shikha,
     Happy Holidays! Hope things are well with you. 
     Yes! Love the new facebook pic. 
     Love the new profile picture!!! VS  Love the new Facebook pic!!
     VS.  Love the new facebook pic!! VS  Love the new facebook pic!!!
     VS. Love the new Facebook pic!!! vs. Yes! I like the new facebook
     pic. 

   \item \tiny Comm: message to Shikha \te{10 minutes} - 

     Things are good. I will be in either Minneapolis or California 
     starting Feb to start work. 

I got a couple of job offers recently. 

     Things are good. I'm finishing postdoc work in the next 2 weeks
     and then taking a break for the next couple of months before
     working (I may be going to California, but I have to finish
     figuring things out).

     I'm with Atul in Champaign and we just now finished watching the
     movie Inside Out.

     \item \tiny Work(GPUcodepres): add in slides . \te{1 hour} 

   \item \tiny Work(GPUCodeCollab): put up code on git . \te{1 hour} 
 
     \item \tiny Work(stencilCode): finish stencil code =
       Work(stencilCode): put stencil code on git + Work(stencilCode):
       fix bug with stencil with MPI\_Isend/MPI\_Irecv/MPI\_Waitall
       {\tt MPI\_Isend()}  + Work: figure out MPI stuff + Work: fix
       data transfer issues with re-use of the code.  + Work: test
       code through job submission+ 

        Work(stencilCode): add script for experimentation 

     \item \tiny Work(GPUcode): get code done for OpenACC =
       Work(GPUcode): do Euler + Work(GPUcode): finish {\tt ModDeriv.fpp}
       + Work(GPUCode): get code to compile on bluewaters using
       {\tt mpipgf90} + 

       \doneTask{Work(GPUcode): get problem size done} 
       \doneTask{Work(GPUcode): write down compilation in the slides} +
       \doneTask{Work(GPUcode): figure out how to assign GPU to MPI process}  +
       Work: Test code for PlasComCM + Work(GPUcode): run code on
       xpacc cluster 


     \item \tiny Work(documentation): add documentation 
     \item \tiny Work(Slides): add slides with explanation.

         % Work: get results for GPU + Work: make projections about
         % performance as you increase number of operations. 
         
       \doneTask{ Work(Jobs): get pres done for Sandia + Work(Jobs):
           talk to Jeff Hammond + Work(Jobs):} 
       \item \tiny \doneTaskNoItem{Work(SCJobs): reply to nvidia} +
         Work(SCJobs): talk to BNL + Work(SCJobs): 
         \tiny \item \tiny Work: call for suit \te{30 minutes} 
       \item \tiny Mgmt:Spaces: pay tickets \te{10 minutes}
        \end{enumerate}
      \end{block} 

      \begin{block}{Work:rel}
        \begin{itemize} 
        \item \tiny Intel 
        \item \tiny Facebook
        \item \tiny Oracle
          \tiny \item \tiny Sandia, LLNL, Postdoc at UIUC  
        \end{itemize}
      \end{block}

      \begin{block}{Week Daily Schedule} 
        % howto: arrange items from running todo into the below
        % sheet management document. 
        {\small \textbf{Sun:} Work on code, worklife: experiences  }
        {\small \textbf{Mon:} Prep for presentation. \small
          \textbf{Tues:} experiences sheet\small
          \textbf{Wed:} Work: ... , Work: work on code, Work:rel: send in things for
          LBL,  Work:rel: send message to catch up on phone, Work:
          revise the presentation for technical stuff, Work: send
          message about 
          \small \textbf{Thur:}
          \small \textbf{Fri:}  Work: put up
          code on git, Work: fix MPI code, Mgmt:Spaces: shopping,
          Mgmt:Spaces: get tickets, Mgmt:webpresence: put up fb likes
          for Avani ,  Comm: message to Sarah,  Comm: look up Shaadi +
          Comm: talk about mamta.

          \textbf{Sat:} \small Work: put code on git, Work: fix
          stencil before putting it up, Work: update code, Work:
          organize pcomm, 
          Mgmt:Spaces: tickets,  
          Comm: send message to fb, Comm: talk to ppl  }


    %-- Column 3 --------------------------------------------------- 
    \begin{column}{0.20\linewidth}
      %-- Block 3-1 
      % On Sunday morn, put a quick synopsis of top news items           
      % here.  Categorize as Comm and Money.      
      \begin{block}{News}
        \begin{itemize} 
          \tiny \item \tiny Bomb from Egypt aircraft 
        \item \tiny Debates 
        \item \tiny Donald Trump on SNL 
        \item \tiny VW 
        \item \tiny Lufthansa strike  
        \end{itemize}
      \end{block}
      
      \begin{block}{Weather} 
        \begin{itemize}
          \tiny \item \tiny 
        \item \tiny 
        \end{itemize}
      \end{block}  

      \begin{block}{Clothes plan} 
        \begin{itemize}
          \tiny \item \tiny Monday
        \item \tiny Tuesday 
        \item \tiny Wednesday
        \item \tiny Thursday
        \item \tiny Friday 
        \end{itemize} 
      \end{block}

      %-- Block 3-3
      \begin{block}{Situations}
        % Howto: the below are the situations that define one another 
        %WeeklySunTimeEst: 10 minutes
        \begin{itemize} 
          \tiny \item \tiny \textit{Situation: SC}  
          Pre-:   Post-:  good job with Thursday party, but stick to
          same person throughout. 

        \item \tiny \textit{Situation: Sandia Interview} 

          \item \tiny \textit{Situation: Atul coming over} Pre-:
            Post-:  

        \end{itemize} 
      \end{block}
 

\begin{block}{Rel}
  \begin{itemize} 
    \small \item \small Girl from SF 

    %\small \item \small Meghan Joshi 
    \small \item \small Mamta 

    \small \item \small Girl from L.A.     
    \small \item \small Girl coming to SF. 
    
  \item \small Australian girl
    \small \item \small Chicago girl 
    \small \item \small Girl you got the number from 
    \small \item \small Rekha 

    \small \item Girl teaching 2nd grade     
  \item \small Smita kammath 
    
  \item \small Girl doing dentistry 

  %\small \item \small Ruchi 
  %\small \item \small Neha Jambhekar 

  %\small \item \small Vinita Ghate 
  \end{itemize} 
\end{block} 
\end{column}%3 
      \end{columns}


\comments{
        \begin{columns} 
          \column{0.14\textwidth}{\textbf{\small \underline{Mon}}}
          \textbf{\small todo} \\ 
          \begin{itemize}
            \tiny \item \tiny Work: finish coding for GPGPU to ask
            Wen-mei. \te{20 minutes}. 
          \item \tiny Work: send mails for meetings. 
          \item \tiny Work: prep for this week. 
          \item \tiny Work: make slides for next week and this week 

            \tiny \item \tiny Work:rel: send message to IBM 

          \item \tiny worklife: experience writing 

          \item \tiny Pay tickets 
          \item \tiny 

          \end{itemize} 

          \textbf{\small schedule} \\
          \begin{enumerate} 
            \tiny \item \tiny 8-9AM: Regular Routines 

            \tiny \item \tiny 10AM - 11AM =  letter to wdg
          \item \tiny 11AM - 12PM = IBM 
              \tiny \item \tiny 1PM - 4PM = prep for presentation + finish code + Makefile 
              \tiny \item \tiny 4PM - 5PM = experience sheet +
              planning 
              \tiny \item \tiny 5 PM - 9 PM = meet people at exhibit hall 
          \end{enumerate} 
          
          \column{0.14\textwidth}{\textbf{\small \underline{Tue}}}
          \textbf{\small todo} \\
          \begin{itemize}
            \tiny \item \tiny Work: make project sheet \te{10 minutes} 
          \item \tiny  \te{10 minutes} 
          \end{itemize}  
          \textbf{\small schedule} 
          \begin{enumerate}
            \tiny \item \tiny 11AM - 12PM = IBM letter 

          \item \tiny 12 PM - 1 PM = prep for presentation 
          \item \tiny 1 PM - 2 PM = 
            \tiny \item \tiny 2PM - 3PM = 
          \item \tiny 6PM - 10PM = 
          \end{enumerate}  
          
          \column{0.14\textwidth}{\textbf{\small {\underline{Wed}}}}
          \textbf{\small todo} \\
          \begin{itemize}
            \tiny \item \tiny Work: finish slides   
          \item \tiny Mgmt: Spaces: update fb 
          \item \tiny Comm: 
          \end{itemize}
          \textbf{\small schedule} \\
          \begin{enumerate}
            \tiny \item \tiny 8-9AM: Regular Routines 
          \item \tiny 9AM - 10AM: Send message 
            \item \tiny 6:30PM - 7:30PM = 
          \end{enumerate} 
          \column{0.14\textwidth}{\textbf{\small{\underline{Thu}}}}
          \textbf{\small todo}\\
          \begin{itemize}  
            \tiny \item \tiny Work: finish slides 
            \item \tiny Mgmt:Spaces: 
            \item \tiny Comm: 

          \end{itemize} 

          \textbf{\small schedule}\\
          \begin{enumerate} 
            \tiny \item \tiny 8-9AM = Regular Routines 
            \item \tiny 12-1PM = 
            \item \tiny 3:30PM - 4:30PM = group meeting 
            \item \tiny 6PM - 9PM = revise emot. int. chapter and
              structure wl-cheat based on it 
          \end{enumerate} 
          
          \column{0.14\textwidth}{\textbf{\small{\underline{Fri}}}}
          \textbf{\small todo}\\ 
          \begin{itemize}
            \tiny \item \tiny Work: updates on GPU \dl{} \te{} \prio{}

            \tiny \item \tiny Mgmt:Spaces: Haircut \te{10 minutes} 

            
          \item \tiny \te{1 hour} 
          \end{itemize}
          \textbf{\small schedule}\\
          \begin{enumerate}
            \tiny \item \tiny 8-9AM: Regular Routines            
          \item \tiny 10AM - 11AM  = haircut 
            \tiny \item \tiny 11AM - 12PM = meet with Prof. Gropp at
            SC 4313  
          \item \tiny 5:30 PM - 7:00 PM = meet with Ruchi at 106
            N. Walnut Street (Esquire Lounge) 
          
          \end{enumerate}
          
          \column{0.14\textwidth}{\textbf{\small \underline{Sat}}}
          \textbf{\small todo}\\
          \begin{itemize} 
            \tiny \item \tiny
          \end{itemize}
          \textbf{\small schedule}\\ 
          \begin{enumerate}
            \tiny \item \tiny 7-7:30PM = food + organize.  
            \tiny \item \tiny 7:30PM -8PM = 
            \tiny \item \tiny 8PM -9PM = 
            \tiny \item \tiny 9:45PM - 10:30PM = go out 
            \tiny \item \tiny 2AM -3AM =  message Samir + add people
          \end{enumerate}
          
          \column{0.14\textwidth}{\textbf{\small \underline{Sun}}}
          \textbf{\small todo}\\
          \begin{itemize} 
           \tiny \item \tiny 
          \end{itemize}

          \textbf{\small schedule}\\
          \begin{enumerate} 
            \tiny \item \tiny 3PM - 4PM  =
          \item \tiny 5-7PM = Comm work 
          \item \tiny 8PM - 10PM = worklife work. 
          \end{enumerate} 
        \end{columns}
      \end{block}
    \end{column}%2     
}
\end{frame}


%    \item \small Mgmt:Spaces(pk): Packing = 
%      Mgmt:Spaces(pk): charger +Mgmt:Spaces(pk): adapter 
%      + Mgmt:Spaces(pk): shoes  + 
%      Mgmt:Spaces(pk): belt + 
%      Mgmt:Spaces(pk):undershirts  =
%      (Mgmt:Spaces(pk):two black + Mgmt:Spaces(pk):two white) 
%      \doneTaskNoItem{Mgmt:Spaces(pk): Passport}
%      + \doneTaskNoItem{Mgmt:Spaces(pk): 6 underwear} +
%      \doneTaskNoItem{Mgmt:Spaces(pk): 8 socks} +
%      \doneTaskNoItem{Mgmt:Spaces: 4 shirts} + Mgmt:Spaces(pk): 4 

%   print boarding pass ,  print bus pass  

%   at airport:  

%  find the terminal to go to  

%  at security: 


% show boarding pass and get ID out 

% Put wallet in left compartment, and ID in right compartment. 

% Laptop in separate case 

% belt off, put in case with other things 

% shoes off 

% go into security 

% put laptop in case, and then in backpack.

% grab shoes and belt. 

% put cases away. 



% put backpack on. 
% grab other bag. 

% put shoes and belt on off to side 


% check gate on phone and go to gate

% check with flight staff about window, find a place to sit 

% email 
