%\def\PRES{1}
%\ifx{\PRES}
%\iftoggle{\PRES}

\begin{frame}{Week Plan}
Work: coding problems, Work: do work for cworks, Work: update job talk, Work: talk to LLNL, Mgmt:Spaces: take care health insurance, Mgmt:Spaces: call for flight change, Comm: message to Teja,
\end{frame} 
\begin{frame}{Running To Do - 1}
%\else 
  %\fi
  
  
  
\begin{enumerate}
  \tiny \item[] \tiny \textbf{Curr} $\rightarrow$ 
\item \tiny Work: send message to Tony to get access to HPC facilities. - 
\item \tiny Work: coding problems. 
\item \tiny Work: job talk update = Work: update task locality slides
  + Work: add PRISMA slides + Work: add Work: add locality-sensitive
  scheduling to thesis part + Work: add cloud computing to thesis +
  Work: update the charm++ stuff + Work: read papers on Charm++ +
  OpenMP + Work: update the Charm++ stuff and send.
\item \tiny Work: find person that can help with Google slides. 
 \item \tiny Work: coding practice update.
\doneTask{Work: update github and send to Todd G.}
\doneTask{Work: send message to LBNL, Krishna }
\doneTask{Work: send e-mail to Krishna. }

\item \tiny Work: send message to Prof Chapman.
\item \tiny Mgmt:spaces: book hotels for England Trip.

\item \tiny Mgmt:wp: post about github on LinkedIn. 
\item \tiny Mgmt:wp: add people to LinkedIn =  Mgmt:wp: add Andy
  Schmidt on LinkedIn. +  Mgmt:wp: add Mike Kumbera t  LinkedIn +
  Mgmt:wp: add Marty.
  
\item \tiny Mgmt:Spaces: unemployment.
\item \tiny Mgmt:Spaces: payment for garage.

\item \tiny Comm: message to Teja :=

  
\item \tiny Comm: e-mail to Rucha. 
\item \tiny Work: coding practice update. 
\item \tiny Work: job talk update = Work: update task locality slides
  + Work: add PRISMA slides + Work: add Work: add locality-sensitive 
  scheduling to thesis part + Work: add cloud computing to thesis.
  
\item \tiny Work: send e-mail for OpenMP. 
\item \tiny Work: update the charm++ stuff + Work: read papers on 
 Charm++ + OpenMP + Work: update the Charm++ stuff and send. 
\item \tiny Work: send message to Todd and Torsten. 
\item \tiny Work:admin: ask about unemployment. 
\item \tiny Mgmt:Spaces: get dentist appointment check. 
\item \tiny Mgmt:Spaces:(bst): update basement =  Mgmt:Spaces(bst): clean boxes in room  
    \seti
\end{enumerate}
% \ifx{\PRES}{1}
\end{frame}
% \else 
% \fi

% \ifx{\PRES}{1}
\begin{frame}{Running To Do (2)} 
%  \fi 
  \begin{enumerate}
    \conti
\item \tiny Work:rel: apply to other LLNL position for LC. \te{1 hour}
  \dl{}
\item Work: send e-mail to Cliff Stein.
\item Mgmt:Spaces: get the reimbursement for car's warranty. 
\item Comm: message to Renata.
\item Comm:rel: email to Bhakti. 
\item \tiny Mgmt:wp: add people to LinkedIn =  Mgmt:wp: add
  Andy Schmidt on LinkedIn + Mgmt:wp: add Marty.
\item Mgmt:Spaces: get new bank. 
\item Comm:rel: reply for Rathi? 
\item \tiny Comm:rel: send dilmil message to Anushya = Hi, how are you doing? What's the picture. 
  \item[] \tiny  $\leftarrow$ \textbf{End Curr}
  \item \tiny Mgmt:Spaces: get citi bank account + Mgmt:Spaces: get refund from AA  + Mgmt:Spaces: get the bumper bully
   
  \item \tiny Mgmt:Spaces: update software in car\te{ 1 hour}. 
  \item \tiny  Mgmt:Spaces: consider new wheels. 
  \item \tiny EI: Study materials from CBT.  \te{2 hours} \dl{Monday}. 
  \item \tiny Work:comm: figure out whether to add Anshu \te{1 hr}.
  \item \tiny Work: update book summary. 
  \item \tiny Work: update movie summary.
  \item \tiny Work: update website.
    
  \end{enumerate}
  %\ifx{\PRES}{1}
\end{frame}


\begin{frame}{Day Plans}

  
  \underline{\bf{Monday}:}
  \underline{\bf{Thursday}:} Work: send e-mail to Prof. Chapman  , Mgmt:Spaces: get hotels figured out for England, 
  , Comm: send message to Teja 
 
\end{frame} 
\begin{block}{Planning} 
\comments{
{\underline{\textit{2-month plans}}}
{\underline{\textit{January and February:}}}
{\underline{\textit{March and April:}} }
{\underline{\textit{May and June:}}}
}

\begin{itemize}
\tiny \item \tiny do scheduling strategies. 
\item \tiny work on job talk. 
\item \tiny do travel. 
\item \tiny social on facebook, catch up with Rishi. 
\end{itemize} 
\begin{itemize} 
\item \tiny 2-month plan: May:  June:  
\item \tiny 2-month plan: August:  prep September: interview. 
\end{itemize}
\end{block}

\begin{columns}
\begin{column}{0.333\columnwidth}
\begin{block}{Project1}
%\underline{\bf Work:code: Project , Coding practice: p for interview.}
\begin{enumerate}
\tiny \item \tiny Work:code (cp.): go through C++, Work:code (cp.): go
through Java + Work:code (cp.): go through OOP. 
\item \tiny Work:code (cp.): code up problems.  – 1 week.
\item \tiny Work:code (cp.): integer problems + numerics   -- 1 week.
\item \tiny Work:code (cp.): practice mock interview problems. – 1 week.
\end{enumerate}
{\tiny {\it {\tiny Schedule:}} Work:code (cp.): finish bit
  manipulation, Work(cp.): review brain teasers in book, Work(cp.):
  Work(cp.): go through C++.} \\
{\underline{\bf Project: job talk prep}} 
{\tiny {\it {\tiny Schedule:}} Work:code (cp.): finish bit manipulation,
Work(cp.): review brain teasers in book, Work(cp.): Work(cp.): go
through C++.} \\

{\underline{\bf Work:code: Project}}
\begin{enumerate}
\tiny \item \tiny Work: download ptychoLib from Kaushik and copy to git repo.
\item \tiny Work: discuss work with A rittenbach + Work: download driver on GPU4.
\item \tiny work: integrate.
\item \tiny Work: do OpenMP 4.5 for ptypy and OpenACC.
\item \tiny Work: run with dataset from PSI.
\item \tiny Work: send message about research paper. 
\end{enumerate}

{\underline{\bf Work:code: Project - Research Paper:}}
\begin{enumerate}
\tiny \item \tiny \url{http://mpp2016.ime.uerj.br}. 
\item \tiny \url{http://sbac-pad}  - registration is  500.

\item \tiny Work: add 
\item \tiny Put up latex.  
\item \tiny Gather all research. 
\item \tiny Gather project work. 
\item \tiny Write down introduction.
\item \tiny Gather data for OpenACC. 
\item \tiny Explain other details of setup. 
\item \tiny Note data for OpenMP. 
\item \tiny Work: discuss ideas with Michael Klemm. 
\end{enumerate}
{\tiny {\textit{Schedule:} March 24th: do latex, March 2}}\\

%\underline{\bf Work:rel: Project – interview with Berkeley/MIT/industry}
\begin{enumerate}
\tiny \item \tiny Business cards:  - use latex  -- 40 minutes. 
\item \tiny Cover letter. 
\item \tiny Jobs categorization for real jobs opportunities: Suny sb /
  suny sb / LLNL /  |  Intel, NVIDIA, Apple  Google/ms / software
  companies, Database companies/Oracle, $\rightarrow$ real companies. 
\item \tiny CV: + Research Summary:  -- 1 week.  - Talking about your research.
\item \tiny Work:rel: message to Yavatkar Kaka about VMWare +
  Work:rel: gather friends in network from friends about Google +
  Work:rel: message to contacts about Microsoft \te{} \dl{} \pr{}. 
\item \tiny Behavioral questions answers:    -- 1 week. 
\item \tiny Send emails – 1 day. 
\item \tiny Structure in latex. 
\end{enumerate}
%{\small {\it Schedule:} Behavioral answers – 1 week, CV prep - 1 day,
%business cards, cover letter -1 hour. }\\
%\underline{\bf Project: awards}
\begin{enumerate} 
\tiny \item \tiny Figure out write-up for Fulbright. 
\item \tiny Attend Fulbright : 
\item \tiny Stay in touch with HLF 
\item \tiny Do energy econ work with convergence. 
\item \tiny Go to whitehouse thing. 
\item \tiny Plan to be on Program Committee of .. 
\end{enumerate}
%{ \small \it Schedule:} April 15th: message to Stephen – 1 hour,
%Work:rel:Project – Awards: 
%\underline{\bf Mgmt:Spaces: settle on your own}
\begin{enumerate}
\tiny \item \tiny Dentist + Get dentist appointment.
\item \tiny Doctor / Counselor + CBT.
%TODO: organize and group the below
\item \tiny Reimbursements.
\item \tiny Work pay and holidays / hours.
\item \tiny 401k+retirement  + fidelity + bank (money owing).
\item \tiny apartment + apartment sublease + apartment rent.
\item \tiny Flights: update flight information, e.g., credit card,
  emergency contact, passport number.
\item \tiny Flights: finish flight decision making notes, e.g.,
  justification for travel, money/airfare rules, award travel rules. 
\item \tiny apartment sublease. 
\item \tiny Car city sticker.
\item \tiny Car: Get windows side checked + Get windows marking
  checked + Get tailpipe checked + Ask about warranty. 
\item \tiny Mgmt:Spaces(crp): check car tailpipe +
  Mgmt:Spaces(crp):Window \te{1 hour}.
\item \tiny Mgmt:Spaces(bfa): buy things for apartment =
  Mgmt:Spaces(bfa): buy a whiteboard + Mgmt:Spaces(bfa): get a chair
  that adjusts height and folds \te{} \dl{} \pr{}. 
\end{enumerate}
\end{enumerate}

{\underline{\textbf{Worklife - Project – Comm:rel:}}}
\begin{enumerate} 
  \tiny \item \tiny Worklife: link management together.  
\item \tiny Worklife: link habits comm and Toastmasters. - done
\item \tiny Worklife: latex viewpoint. 
\item \tiny Comm: read social intelligence first four chapters.
\item \tiny Comm: link all comm together.
\item \tiny Worklife: get emails and texts to analyze. 
\item \tiny Worklife: figure out how to book flights and trips
  quickly. 
\textit{Schedule:} Comm: read social intelligence first four chapters
and get a method to take in information – 5 hours. Comm: link comm
together, worklife: latex viewpoint. Looking ahead:  \\

{\underline{\bf Project: Comm}}
\begin{enumerate}
\item \tiny Comm: consider view of girl on Shaadi. 
\item \tiny Comm: consider talking to Illina.
\item \tiny Comm: talk to friends from high school.
\item \tiny Mgmt:Spaces: plan trips. \te{-}.
\item \tiny Mgmt:webpresence: cancel FB friend request of
  Jocelyn + Mgmt:webpresence: check other friend requests
  sent requests. \te{-}. 
\item \tiny Mgmt:Spaces(GetThingsSpring2016): get Things =
  Mgmt:Spaces(getThings): get suit.
  \doneTask{Mgmt:webpresence: delete Anil Taneja from LinkedIn. \te{1
      hour} \dl{Monday} \pr{UI}. - not needed since we met with Rishi
    + Comm: may have not accepted + Mgmt:webpresence: bad to do so}
\end{enumerate}
{\it Schedule:} meet others over summer, meet girl over summer.\\
%TODO: figure out why this was the issue

{\underline{\bf Project: Comm:rel}}
\begin{enumerate} 
  \tiny \item \tiny Comm: consider what to do about Bhavna.
\item \tiny Comm: get caught up with Matrimony and Shaadi, Use match,
  make system for meeting. 
\item \tiny Comm:rel: discuss with Mom and Dad. 
\end{enumerate} 

{\underline{\bf Mgmt:Spaces}}\\
\begin{enumerate} 
\item \tiny Mgmt:Spaces(GetThingsSpring2016): get Things = Mgmt:spaces: get suit
+ Mgmt:Spaces: buy calendar 
\item \tiny Mgmt:Spaces: get voicemail fixed  - ‘Hi, you have reached Vivek’s
phone. I’ll call you back as soon as possible.’ + Mgmt:Spaces: delete
voicemails’ 
\item \tiny Mgmt:Spaces: get 1 TB disk drive. 
\item \tiny Mgmt:Spaces: finish transferring pictures + Mgmt:Spaces: figure out
how to delete photos from iPhoto + Mgmt:Spaces: figure out why size of
photo booth stays the same  Mgmt:Spaces: Figure out airplane photos
and put in proper album folder. Mgmt:Spaces: Organize photos in
folders + Mgmt:Spaces: Confirm pictures are placed properly and delete
from photos + Mgmt:Spaces: Compress photos into zip drive. +
Mgmt:Spaces: Move photos from folders into temporary disk / USB stick 
+ Mgmt:Spaces:Delete photos from iPhone.
\end{enumerate} 

{\underline{\bf Work:comm: (can impact work):}}
\begin{enumerate}
\item \tiny Work:rel: add Shikha.
\item \tiny Mgmt:webpresence: fb like to Lagha. 
\end{enumerate}

\underline{\bf Work:rel: -  Project – Comm: rel:} 
\begin{itemize} 
\item \tiny Comm:rel: meet others:  Sweta Kambaskadwar. + Mgmt:webpresence: fb
like of Shalaka’s. L3:past: she liked and suggested to come, lots of
time delayed. I didn’t like back.  Intent: show interest. Outcome:
stay alive with Rucha?
\item \tiny Mgmt:webpresence: fb like to Tanuja
\item \tiny Mgmt:webpresence: take Xin Zhao off and remove anyone else that you
don’t want from work.
\item \tiny Mgmt:webpresence: update location on linkedIn +  Mgmt:webpresence: update.
\item \tiny Mgmt:webpresence: consider deleting asdfjkl;  and making parts of facebook bmm 2006 public. 
\end{itemize}

\end{block}
\ifdefined\POSTER
  \begin{columns}
    %-- Column 1 --------------------------------------------------- 
    \begin{column}{0.22\linewidth}
      \begin{block}{Happiness Generation - must maintain every week.} 
\else
 \underline{\bf Happiness Generation - must maintain every week.}
\fi
        % explain happiness: show gratitude
        \begin{itemize}
          \tiny \item \tiny happy that I have Atul to show me.  
        %\item \tiny Happy that I have normal life up to this point.  
        %\item \tiny Think about dad saying, I understand, and want
        %you to be happy.
          \item \tiny Th
        \end{itemize}
\ifdefined\POSTER
      \end{block}
\fi

\ifdefined\POSTER
    \begin{block}{Habits}
\else
 \underline{\bf \it Habits} 
\fi 
      \begin{itemize} 
        \tiny \item \tiny back straight + eye contact. 
      \item \tiny lips relaxed. 
      \item \tiny watch what happens when a hot girl talks to you. 
      \end{itemize}

\ifdefined\POSTER
    \end{block} 
  \end{column} %1
\fi

\ifdefined\POSTER
  \begin{column}{0.5\linewidth}
    \begin{block}{10-year plan}   %-- Block 2-1 
\else 
 \underline{\bf 10-year plan}

\fi
      \begin{itemize}
      \item \small Make someone and dad proud.
      \end{itemize}
\ifdefined\POSTER
    \end{block}
\fi

\ifdefined\POSTER 
    \begin{block}{3-year plan}
\else
\underline{\bf 3-year plan} 
\fi
      \begin{itemize}
      \item \small find someone
      \item \small make 150K
      \item \small network
      \end{itemize}
\ifdefined\POSTER
    \end{block} 
\fi


\ifdefined\POSTER
    \begin{block}{6-month plan}
\else 
\underline{\bf 6-month plan}
\fi
      \begin{itemize}
        \small \item \small results + thesis
      \item \small routine + worklife
      \item \small 
      \end{itemize}
\ifdefined\POSTER
    \end{block} 
\fi

\ifdefined\POSTER  
    \begin{block}{Month-by-month}
\else
\underline{\bf Month-by-month} 
\fi 
      %howto: This is most important, and should be re-visited every
      %month and definitely every three months(have fixed time within
      %4 times in the year to do this). 
      \begin{itemize} 
      %\item \small \textit{May:} Work: finish paper  + Work: comm:
      %  finish resume and cover letter.  
      %\item \small \textit{June:} Work: code org and plan + Work:
      %  finish code + worklife: org + worklife: finish emotional int +
      %  Comm: experiences + Comm: TM. 
      \item \small \textit{July:} Work: library, Work:comm: job
        introductions, Comm: meet people.
      \item \small \textit{August:} Work: library documentation and
        experimentation, Work: comm: resume prep + Work:comm:linkedIn
        + Work:comm: interviewing skills + Work:rel: get headstart on
        jobs (fb and dshaw) + Comm: stay in touch with girls. 
      \item \small \textit{September:} Work:library + Work: paper
        writing + Work:comm: interviewing. 
      \item \small \textit{October:} Work:paper +
        Work:rel:interviewing + Comm: dating 
      \item \small \textit{November:} worklife: review , Work:paper, Comm: dating 
 %     \item \small \textit{December:} 

      \end{itemize}
\ifdefined\POSTER 
    \end{block}
\fi

\ifdefined\POSTER
\begin{block}{March goals}
\else
\underline{\bf March goals}\\
\fi 

\begin{enumerate} 
\item \small Work: finish writing goals
  \small \item \small Mgmt:Spaces: clean room 
\item \small worklife: practice implemented work to form habits 
\item \small Comm: meet people 
\end{enumerate}
\ifdefined\POSTER
\end{block}
\fi

\ifdefined\POSTER
\begin{block}{\small \bf Week of September $31^{st}$: job search}
\else
\underline{\bf Week of September $31^{st}$: job search}\\
\fi

\begin{enumerate}
\tiny \item \tiny Work: finish connecting with people regarding
implementation. 
\item \tiny Mgmt:Spaces: take care of driver's license. 
\item \tiny 
\item \tiny 
\item \tiny Comm: meet people 
\end{enumerate}

\ifdefined\POSTER
\end{block}
\fi

\ifdefined\POSTER
\begin{block}
\fi

{\underline{\bf Weekend Plans - March $15^{th}$, 2017 to May $1^{st}$,
2017}}\\

\begin{itemize}
\item \tiny Weekend of March $17^{th}$: Visit New York City. Details:
\item \tiny Weekend of March $24^{th}$: Visit San Francisco. Details:
\item \tiny Weekend of March $31^{st}$: Visit San Francisco. Details:
\item \tiny Weekend of April $6^{th}$:  Dad is coming, cherry
  blossoms.
\item \tiny Weekend of April $13^{th}$: Visit India.
\item \tiny Weekend of April $20^{th}$: Go to New York.
\item \tiny Weekend of April $26^{th}$: Go to Los Angeles.
\end{itemize}

{\underline{\bf  Weekend plans for weekends between May $1^{st}$, 2017
    and June$1^{st}$, 2017}}\\
\begin{itemize}
\item \tiny Weekend of May $5^{th}$: Visit New York.
\item \tiny Weekend of May $12^{th}$:
\item \tiny Weekend of May $19^{th}$:
\item \tiny Weekend of May $27^{th}$:
\end{itemize}


\ifdefined\POSTER
\end{block}
\fi

\ifdefined\POSTER
\end{column}
\fi


%-- Column 3 --------------------------------------------- 

\ifdefined\POSTER
\begin{column}{0.28\linewidth}
\begin{block}{\small \bf Regular Routines}
\else
\underline{\bf Regular Routines}\\ 
\fi 

%\input{../../../ViveksLaptop2/life/workLifeMgr/regularRoutines}
\input{./content_regularRoutines_plan}

\ifdefined\POSTER
\end{block}
\end{column}%3
\fi

\ifdefined\POSTER
\end{columns}
\fi
\underline{\bf Morning}
\begin{itemize}
\tiny \item \tiny Brush Teeth \timeEst{4 mins}.
\item \tiny Mouthwash, Clean tongue - it helps with breath\timeEst{1mins}
\item \tiny Eating small breakfast.
\item \tiny Check your schedule for meetings / appointments for that
day: Is anything urgent? \timeEst{5 mins}.
\item \tiny Excercise: 1 hour ( Stretch for 10 mins, Treadmill for 30
mins , Lift weights or Yoga 1 hour, Meditation for 10 mins).
\item \tiny Shave (at least every other day) \timeEst{5 mins}.
\item \tiny Shower : (shampoo+conditioner, acne wash,  soap on
underarms/underbody) \timeEst{10 mins}
\item \tiny dry hair, dry face, arms, legs, back, stomach \timeEst{3
mins}
\item \tiny Clothing: belt, check collar, shirt not half-tucked,
matching socks \timeEst{5 mins}
\item \tiny Comb hair, hair gel optional \timeEst{ 1 min}
\item \tiny Check Keys/Wallet/Cell/Badge (get a bucket) \timeEst{1
min}
\item \tiny Open meds cabinet, get water, take medicines \timeEst{1
min}
\item \tiny Wear lenses and rinse out case \timeEst{ 2 mins}
\item \tiny Deodorant or cologne depending on the day \timeEst{1 min}
\item \tiny Wash your face with a face wash - it helps with
acne \timeEst{3 mins}
\item \tiny Moisturize - apply lotion \timeEst{ 2 min}
\item \tiny Neti pot / clean out sinuses - if you’re feeling
congested \timeEst{5 min}
\item \tiny clean out ears, nose \timeEst{5 mins}
\item \tiny Remember to lock door \timeEst{1 mins}
\end{itemize}

\underline{\bf Evening}
\begin{itemize}
\tiny \item \tiny Call family: 30 mins
\item \tiny meet friends: 20 mins
\item \tiny Cleaning dishes / cleaning house: 10 mins
\item \tiny Lay out clothes for the next day, iron if necessary
\item \tiny start laundry if needed: 10 mins,
\item \tiny Collect anything you’ll need for the next day (e.g. dry
cleaning to drop off): 5 mins,
\item \tiny Check Facebook/linkedin/google+: 10 mins, matrimony stuff:10 mins,
\item \tiny Food for lunch/dinner the next day: 10 mins
\end{itemize}
\underline{\bf Night before bed}
%TODO: why isn't enumerate working???
\begin{itemize}
\tiny \item \tiny Finish computer stuff \timeEst{5 mins}
\item \tiny Get into sleeping clothes \timeEst{1 mins}
\item \tiny Before sleeping: brush teeth, floss \timeEst{2 min} 
\item \tiny Properly wash and put away contacts \timeEst{2 mins}
\item \tiny Review the days good things \timeEst{10 min} 
\item \tiny Light Reading \timeEst{ 10 min}
\item \tiny Prayer \timeEst{10 mins}
\end{itemize}



%          \item \tiny Work: talk to Prem about an office in SF
  \begin{columns}
    %-- Page 2: Column 1 --------------------------------------------------- 
    \begin{column}{0.20\linewidth}
      %{\textbf{\underline{Week Aspects(new name)}})
      %--- Page 2: Block 1-1 
      \begin{block}{Routines}
        { \tiny \underline{\bf Routines:} Morning: bfast, exercise/brush,
          floss, shower (hair, eyes, ears, underarms, feet), meds, belt,
          comb hair / dishes, clean kitchen floor. |  Night: running/ put
          away dishes, clean kitchen floor / brush teeth, charge phone,
          clothes for tomorrow, contacts off.}\\
        {\tiny \underline{\bf Sunday Routines:} Routines:
          Experiences,week plan.}\\ 
        {\tiny \underline{\bf Weekday Routines:}}\\
        %TODO: check if weekday routines overlaps into daily routines.
      \end{block} 
      %--- Page 2: Block 1-3
      \begin{block}{Local Happiness}
        % howto:Recognize emotions / recognize (precisely) what you're
        % worried about -> methods for eliminating worry. 
        % clean out old worries, put them in pastWorries doc.  
        % remember to define precisely 
        % order from top-to bottom
        \begin{itemize} 
          \tiny \item \tiny
        \item \tiny Worrying about gal: think about talking to others.
        \end{itemize} 
      \end{block}
      %--- Page 2: Block 1-4 
      \begin{block}{AngersAndAnxieties}
        % howto:Recognize emotions / recognize (precisely) what you're worried about -> methods for eliminating worry. 
        % clean out old worries, put them in pastWorries doc.  
        % remember to define precisely 
        % order from top-to bottom
        \begin{itemize}
          \tiny \item \tiny Anger about UP -> think about the positive
          perspective, and the original
        \item \tiny Anger about Mr. Kapoor ->  leave it
        \item \tiny Anger about a b  -> ...
        \item \tiny Issue with USC : --> things get better. 
        \end{itemize}
      \end{block}
      %-- Block 1-5
      \begin{block}{Life notes}
        \begin{itemize}
          \tiny \item \tiny Social Intelligence: 
        \end{itemize}
      \end{block}

      % howto:
      \begin{block}
        {\tiny {\bf Week lessons:}}
        \begin{enumerate}
          \tiny \item \tiny Win Friends/ Influence People
        \item \tiny Go through 7 habits.
        \item \tiny Coding problem: 
        \item \tiny Chess tips: 
        \item \tiny tm tips.
        \end{enumerate}
            {{\tiny {\tiny \bf  News:}} {\tiny  M: | S: France's election | E:
              Fallon:   Kimmel:  Colbert: SNL:}}
      \end{block}
    \end{column}
  %-- Column 2 ---------------------------------------------
  \begin{column}{0.6\linewidth}
    \begin{block}{Week Summary} 
      {\underline {\bf Week Plan:}
        Work: run dataset to scale on HPC cluster, Work: make slide
        for ptycholib, Comm: send message to Nitin Mama, Comm: reply
        on  WhatsApp group. } \\

      {\underline{\bf Weekend Plan:} }\\
    \end{block}

      \begin{block}{Running ToDo} % find a better name 
        \begin{enumerate} 
          \item \tiny \textbf{Curr} $\rightarrow$
          \item \tiny Work: fix Youssef's code.
          \item \tiny Work: do \texttt{ ln -s} for paper subdirectory
            in bitbucket git repository.
          \item \tiny Work: download ptychoLib from Kaushik and copy
            to git repo.
          \item \tiny Work: discuss work with A rittenbach + Work: download driver on GPU4. 
           
          \item \tiny Work: kakadu software. 

          \item \tiny Work: run with real dataset if possible. 
          \item \tiny Work: figure out time to talk with Youssef.

          \item \tiny Mgmt:Spaces: get car check engine light updated
            + Mgmt:Spaces: do car's registration + Mgmt:Spaces: get
            reimbursements done. 

          \item \tiny Mgmt:Spaces: plan trip  to California. =
            Mgmt:Spaces: talk to Ashwin saying that works.  +
            Mgmt:Spaces: send message to Gopi + 
            Mgmt:Spaces: ask Dad for getting miles + Mgmt:Spaces:
            message to Nitin Mama.

           \item \tiny Mgmt:wp: post about Tesla's. 

            \item \tiny Mgmt:wp: post about net neutrality. 

            The Internet was incepted with the assumption of network
            neutrality. Let's stick to tradition and keep the Internet
            that way. Support the cause.

            TODO:L4: assumption of network neutrality VS assuming net
            net neutrality.  -done 
            TODO:L4: stick to v VS maintain  -done 

            TODO:L4: and keep the internet that way. 

            TODO:L3: website VS full


%http://time.com/4770205/john-oliver-fcc-net-neutrality/


The Internet was incepted with the assumption of network neutrality. Let's
stick to tradition and keep the Internet that way. Support the cause.

http://time.com/4770205/john-oliver-fcc-net-neutrality/


for network  neutrality.

I support network neutrality.

Support the cause. 


Let's make sure that it stick to 

            I understand that companies need to make money, but
            there's absolutely no argument against blocking out
            smaller 
            tradition.  Net neutrality. exactly what we need to fight
            for.
 
           \item \tiny Mgmt:wp: post about science on FB. 
           \item \tiny Mgmt:wp: post about Queen. 

           \item \tiny Mgmt:wp: Write up on facebook.
           \item \tiny Mgmt:wp: I like Tesla cars and support the company's
            disruption to its industry. At the same time, I don’t think
            that the company will devalue instantaneously the engineering
            accumulated over 8 decades in a BMW.
            {I like cars by Tesla and am supportive of the company’s
              disruptiveness to industry. However, I can’t imagine
              that the company’s cars will make the eight decades of
              engineering that’s in my BMW engine become worthless.
             Tesla technology
             TODO:L3: intent: explain supportiveness of disruptve
             TODO:L3: outcome: people see what I’m about 
             TODO: L4: disruptiveness to industry VS disruption to industry 
             TODO: L4: I have a hard time VS I can’t imagine VS I don’t think  VS 
             TODO:L4: At the same time, VS However, 
             TODO:L4: truly VS [OMIT] 
             TODO:L4: I like VS I love} 

           \item \tiny Comm: message to Nitin Mama about meeting his
             father with a picture.

          \item \tiny Comm: do review for Liberty Towers. 
          \item \tiny \textbf{ <-- End Curr } 
          \item \tiny Work: IM system for LLNL.
        \end{enumerate}
      \end{block}
 
      % howto: the below is a routine based on the job I'm doing and the
      % circumstances I'm in. Note that this is different from routines
      % above, which is true for a long-term period of over 10 years. 

      \begin{block}{Weekly Meetings}
        \begin{itemize}
          \tiny \item \tiny IWOMP affinity meeting Thursday 7 AM PDT / 9 AM
          CDT call in: 805-639-779 pswd: places. \url{https://llnl.webex.com/llnl/j.php?MTID=m33950b76befb72c0cbc31ea2e3be720c}
        \item \tiny DEG group meeting.  
        \end{itemize}
      \end{block} 

\comments{
\begin{block}
\begin{table}[ht!]
\label{fig:calendar}
\begin{center}
\begin{tabular}
{ | c || c | c | c | c | c | c | c |}
\hline
  \textbf{\small content} & {\small \bf M} & {\small \bf T} & {\small
    \bf W} & \
{\small \bf R} & {\small \bf F} & {\small \bf Sa} & {\small \bf Su} \\
  \hline
  \small weat  &\tiny 2/3 r &\tiny 2/1 r &\tiny 2/-1 r &\tiny 11/2 s
  &\tiny 11/4 s   &\tiny  11/4 s &\tiny 11/5 s \\
  \hline
  \small todo  &\small exps on a node &\small &\small &\small &\small &\small
  &\small  \\
  \small       &\small &\small &\small &\small &\small &\small
  &\small  \\
  \small       &\small &\small &\small &\small &\small &\small
  &\small  \\
  \small       &\small &\small &\small &\small &\small &\small
  &\small  \\
  \small       &\small &\small &\small &\small &\small &\small
  &\small  \\
  \hline
  \small schd  &\small &\small &\small &\small &\small &\small
  &\small  \\
  \small     &\small &\small &\small &\small &\small &\small  &\small
  \\
  \small      &\small &\small &\small &\small &\small &\small  &\small
  \\
  \small    &\small &\small &\small &\small &\small &\small  &\small
  \\
  \small     &\small &\small &\small &\small &\small &\small &\small
  \\
  \hline
%\bottomrule                                                                    
\end{tabular}
\end{center}
\end{table}

\end{block}
}

      \begin{block}{Week Daily Schedule}
        % howto: arrange items from running todo into the below
        % sheet management document. 
        %NOTE: we don't use the table format because of fittting

        \begin{columns}
          \begin{column}{0.14\textwidth}{\small \underline{\bf Mon}}
            {\tiny \bf {\tiny weather:} } {\tiny 11/1 s} \\ 
            {\tiny \bf {\tiny todo}}\\ 
            \begin{itemize}
              \tiny \item \tiny Work: do experiments with multiple
              nodes. 
            \item \tiny Work: get experiments using real data.  
            \item \tiny 
            \end{itemize}
                {\small  \bf schedule}\\
                \begin{enumerate} 
                  \tiny \item \tiny 8-9AM: Regular Routines 
                \end{enumerate}
          \end{column}

          \begin{column}{0.14\textwidth}{\small \underline{\bf Tues}}
            {\bf {\tiny  weather:} } {\tiny 3/1 r} \\ 
            {\bf {\tiny todo}}\\ 
            \begin{itemize}
              \tiny \item \tiny Work: do write-up  
            \end{itemize} 
                {{\bf {\tiny  schedule}}}
                \begin{enumerate} 
                  \tiny \item \tiny 8-9AM: Regular Routines 
                \end{enumerate} 
          \end{column}

          \begin{column}{0.14\textwidth}{\small \underline{\bf Wed}}
            {\tiny \bf weather: } {\tiny 3/1 r} \\ 
            {\tiny {\bf todo}}\\
            \begin{itemize}
              \tiny \item \tiny Add in schedule
            \item \tiny -
            \end{itemize} 
                {\tiny \bf schedule}\\
                \begin{enumerate} 
                  \tiny \item \tiny 8-9AM: Regular Routines 
                \end{enumerate} 
          \end{column}

          \begin{column}{0.14\textwidth}{\small \underline{\bf Thurs}}
            {\tiny \bf weather: } {\tiny 1/-1 r }\\ 
            {\tiny \bf todo} \\ 
            \begin{itemize}
              \tiny \item \tiny Add in schedule
            \item \tiny 
            \end{itemize} 
                {\tiny {\bf schedule}} \\
                \begin{enumerate} 
                  \tiny \item \tiny 8-9AM: Regular Routines 
                \end{enumerate}
          \end{column} 
          
          \begin{column}{0.14\textwidth}{\small \underline{\bf Fri}}
            {\tiny \bf weather: } {\tiny 3/1 r} \\ 
            {\tiny \bf todo} \\ 
            \begin{itemize}
              \tiny \item \tiny Add in schedule
            \item \tiny 
            \end{itemize} 
                {\tiny \bf schedule} \\
                \begin{enumerate} 
                  \tiny \item \tiny 8-9AM: Regular Routines 
                \end{enumerate}
          \end{column}

          \begin{column}{0.15\textwidth}{\small \underline{\bf Sat}}
            {\tiny \bf weather: } {\tiny 11/1 .2r} \\ 
            { \tiny \bf todo} \\ 
            \begin{itemize}
              \tiny \item \tiny Add in schedule
            \item \tiny 
            \end{itemize} 
                {\tiny \bf schedule} \\
                \begin{enumerate} 
                  \tiny \item \tiny 8-9AM: Regular Routines 
                \end{enumerate}
          \end{column}
          
          \begin{column}{0.15\textwidth}{\small \underline{\bf Sun}}
            {\tiny {\bf weather:} } {\tiny 11/2 r} \\ 
            {\tiny {\bf todo}}\\
            \begin{itemize}
              \tiny \item \tiny Add in schedule
            \end{itemize} 
                {\tiny \bf schedule}\\
                \begin{enumerate} 
                  \tiny \item \tiny 8-9AM: Regular Routines 
                \end{enumerate}
          \end{column}
        \end{columns}
      \end{block}

\end{column}
    
    % ------ Page 2: Column 3
    \begin{column}{0.20\linewidth}
      % ------ Block 2.3.1 
      \begin{block}{Food Plan} 
        \begin{itemize}
          \tiny \item \tiny Google Express: DHDQQJQDRFTXDM95B
        \end{itemize}
      \end{block} 
      \begin{block}{Clothes plan} 
        \begin{itemize}
          \tiny \item \tiny Monday: 
        \item \tiny Tuesday
        \item \tiny Wednesday
        \item \tiny Thursday
        \item \tiny Friday
        \item \tiny Saturday
        \end{itemize} 
      \end{block} 
      
      %-- Block 3-3 
      \begin{block}{Situations}
        % Summary: the below are the situations that define one
        % another.
        % Howto: Put post notes of each situation from list of previous
        % week. Put high importance situations in situationslist. 
        % Put list of upcoming situations on Sunday morning with Pre. 
        \begin{itemize}
          \tiny \item \tiny Meet with Ashwin. Pre-: dress red, talk
          about life. Post-:
        \end{itemize}
      \end{block}
      % contingincies: 
      % Summary:
    \end{column}
\end{columns}
  \begin{block}{Jobs}
    \begin{itemize}
      \tiny \item \tiny cat1: D.E. Shaw | SUNY/BNL: applying . | IBM:
      applied,interviews.  | Sandia: applied and failed, Cray: applied and got offer, USC. 
    \item \tiny cat2: Intel: Applied and failed. Intel: re-application  completed, AMD: applied, Samsung, VMWare: Contacting Yavatkar Kaka. 
    \item \tiny cat3: Google. MongoDB: applied and failed, Facebook. 
    \item \tiny cat4: LLNL. 
    \end{itemize} 
  \end{block} 


%TODO: check if below is needed. 
      %\item Friends: Amit, Sangita, Anchit, Kevin. 
      %Networking: 
  \begin{block}{Comm:friends} 
    \begin{itemize} 
    \item Palekar’s:  
      \begin{itemize}
      \item UP: 
      \item Rohun: 
      \end{itemize} 
    \item Bhagwat’s: 
    \item Kapoor’s: 
      \begin{itemize}
        \tiny \item \tiny Anchit: Interaction. Atul is smart. 
      \item \tiny Shuchi: 
      \end{itemize}
    \item Sudharshan’s: 
      \begin{itemize} 
        \tiny \item \tiny Amit:  
      \item \tiny Sangita:  
      \end{itemize}
    \item Kumar’s:
      \begin{itemize}
        \tiny \item \tiny Ashwin: 
      \item \tiny Shilpa: 
      \end{itemize}
    \item Saied’s: 
      \begin{itemize}
        \tiny \item \tiny Laila 
      \item \tiny Faisal 
      \item \tiny Ayesha
      \end{itemize} 
    \item Kukreti’s:
    \item Kumar’s:
    \item UIUC friends: 
      \begin{itemize} 
        \tiny \item \tiny Sadhna: 
      \item \tiny Rishi: 
      \item \tiny Amaeya: 
      \item \tiny Chris: 
      \item \tiny Brian: 
      \item \tiny Arif 
      \end{itemize}
    \item grad school friends 
      \begin{itemize} 
        \tiny \item \tiny  Karan: 
      \item \tiny Gopi: 
      \item \tiny Amanda:  
      \end{itemize}
    \end{itemize} 
  \end{block}
  
  \begin{block}{Rel} 
    \begin{itemize} 
      \small \item \small Shwetha K/r
    \item \small Shalaka 
    \item \tiny DCK girl 
    \item \tiny  Shikha Singhvi: initiated.  
    \item \small Mamta
    \item \small Avani 
    \item \small SH05702678 Palo Alto - 
    \item \small Sheila G -Sh93522198  
    \item \small sonalisinha  s: 5103658167 and my email address is: \url{2sonalisinha@gmail.com}
    \item \small Nandini  - 
    \item \small Archana from San Jose. 
    \item \small Im from DC  - B475435: parents initiated. 
    \item \small Sruthi 
    \item \small SH12825009 New York, New York - Finance Professional 
    \item \small Navneet K  - 29 5'8" - SH88263211 
    \item \small Girl from New York  -27 years
    \item \small Shwetha Ravi 
    \item \small Ruchira K ( SH34021888 )2-Way           
    \item \small SH11680694 from San Francisco. 
    \item \small Sandhya N. 22 Jun 2016 
    \item \small Aarti S - 27 - 5' 9'' Charlotte.  
    \item \small Anu M from Chicago, IL 
    \item \small Pranati A from Cleveland, OH - 
    \item \small Meghana K from New York - 
    \item \small Ssd S - 28 , 5 5 , Boston, MA 
    \item \small Anj B. - 30 yrs - SH13882555.
    \end{itemize}
  \end{block} 
%IfFileExists 

\begin{frame}{\today}{Daily Plan}
\underline{\bf todo}\\
\begin{itemize}
\tiny \item \tiny Work: 
\item \tiny Work:
\item \tiny Work: 
\item \tiny
\end{itemize}

\underline{\bf schedule:}\\
\begin{enumerate}
\tiny \item \tiny 11:00 AM - 12:00 PM = attend conf. call
\end{enumerate}
\end{frame}
\begin{frame}{Job Search}


%switch to deal with overleaf inconsistency. 
\IfFileExists{../thePast/situations/jobsList.csv}{../thePast/situations/jobsList.csv}{\tiny\csvautotabular{./thePast/situations/jobsList.csv}}


\end{frame}
\ifdefined\POSTER
  \begin{columns}
    %-- Column 1 --------------------------------------------------- 
   \begin{column}{0.22\columnwidth}
      \begin{block}{Happiness Generation - must maintain every week.}
\else
 \underline{\bf Happiness Generation - must maintain every week.} 
\fi
        % explain happiness: show gratitude 
        \begin{itemize}
          \tiny \item \tiny happy that I have Atul to show me.  
        %\item \tiny Happy that I have normal life up to this point.  
        %\item \tiny Think about dad saying, I understand, and want
        %you to be happy.
          \item \tiny T 
        \end{itemize}
\ifdefined\POSTER
      \end{block}
\fi

\ifdefined\POSTER
    \begin{block}{Habits}
\else
 \underline{\bf \it Habits} 
\fi 
      \begin{itemize} 
        \tiny \item \tiny back straight + eye contact. 
      \item \tiny lips relaxed. 
      \item \tiny watch what happens when a hot girl talks to you. 
      \end{itemize}
\ifdefined\POSTER
    \end{block} 
  \end{column} %1
\fi

\ifdefined\POSTER
  \begin{column}{0.5\columnwidth}
    \begin{block}{10-year plan}   %-- Block 2-1 
\else 
 \underline{\bf 10-year plan}
\fi
      \begin{itemize}
      \item \small Make someone and dad proud.
      \end{itemize}
\ifdefined\POSTER
    \end{block}
\fi

\ifdefined\POSTER 
    \begin{block}{3-year plan}
\else
\underline{\bf 3-year plan} 
\fi
      \begin{itemize}
      \item \small find someone
      \item \small make 150K
      \item \small network
      \end{itemize}
\ifdefined\POSTER
    \end{block} 
\fi

\ifdefined\POSTER
    \begin{block}{6-month plan}
\else
\underline{\bf 6-month plan}
\fi
        \begin{itemize}
          \small \item \small results + thesis
          \item \small routine + worklife
          \item \small             
          \end{itemize}
\ifdefined\POSTER
    \end{block} 
\fi


\ifdefined\POSTER  
    \begin{block}{Month-by-month}
\else
\underline{\bf Month-by-month} 
\fi 
      %howto: This is most important, and should be re-visited every
      %month and definitely every three months(have fixed time within
      %4 times in the year to do this). 
      \begin{itemize} 
      %\item \small \textit{May:} Work: finish paper  + Work: comm:
      %  finish resume and cover letter.  
      %\item \small \textit{June:} Work: code org and plan + Work:
      %  finish code + worklife: org + worklife: finish emotional int +
      %  Comm: experiences + Comm: TM. 
      \item \small \textit{July:} Work: library, Work:comm: job
        introductions, Comm: meet people.
      \item \small \textit{August:} Work: library documentation and
      experimentation, Work: comm: resume prep + Work:comm:linkedIn +
      Work:comm: interviewing skills + Work:rel: get headstart o jobs (fb and dshaw) + Comm: stay in touch with girls. 
      \item \small \textit{September:} Work:library + Work: paper writing + Work:comm: interviewing. 
      \item \small \textit{October:} Work:paper +  Work:rel:interviewing + Comm: dating 
      \item \small \textit{November:} worklife: review , Work:paper, Comm: dating 
      \end{itemize}
\ifdefined\POSTER 
    \end{block}
\fi

\ifdefined\POSTER
\begin{block}{May goals}
\else
\underline{\bf May goals}\\
\fi 

\begin{enumerate} 
\item \small Work: finish writing goals
  \small \item \small Mgmt:Spaces: clean room 
\item \small worklife: practice implemented work to form habits 
\item \small Comm: meet people 
\end{enumerate}

\ifdefined\POSTER
\end{block}
\fi

\ifdefined\POSTER
\begin{block}{\small \bf Week of September $31^{st}$: job search}
\else
\underline{\bf Week of September $31^{st}$: job search}\\
\fi

\begin{enumerate}
\tiny \item \tiny Work: finish connecting with people regarding implementation. 
\item \tiny Mgmt:Spaces: take care of driver's license. 
\item \tiny 
\item \tiny Comm: meet people 
\end{enumerate}

\ifdefined\POSTER
\end{block}
\fi

\ifdefined\POSTER
\begin{block}{Weekend Plans - March $15^{th}$, 2017 to May $1^{st}$,2017} 
\else
{\underline{\bf Weekend Plans - March $15^{th}$, 2017 to May $1^{st}$,2017}}\\ 
\fi
\begin{itemize}
\item \tiny Weekend of March $17^{th}$: Visit New York City. Details:
\item \tiny Weekend of March $24^{th}$: Visit San Francisco. Details:
\item \tiny Weekend of March $31^{st}$: Visit San Francisco. Details:
\item \tiny Weekend of April $6^{th}$:  Dad is coming, cherry
  blossoms.
\item \tiny Weekend of April $13^{th}$: Visit India.
\item \tiny Weekend of April $20^{th}$: Go to New York.
\item \tiny Weekend of April $26^{th}$: Go to Los Angeles.
\end{itemize}

{\underline{\bf  Weekend plans for weekends between May $1^{st}$, 2017
    and June$1^{st}$, 2017}}\\
\begin{itemize}
\item \tiny Weekend of May $5^{th}$: Visit New York.
\item \tiny Weekend of May $12^{th}$:
\item \tiny Weekend of May $19^{th}$:
\item \tiny Weekend of May $27^{th}$:
\end{itemize}

\ifdefined\POSTER
\end{block}
\end{column}
\fi

%-- Column 3 --------------------------------------------- 

\ifdefined\POSTER
\begin{column}{0.28\linewidth}
\begin{block}{\small \bf Regular Routines}
\else
\underline{\bf Regular Routines}\\ 
\fi 

%\input{../../../ViveksLaptop2/life/workLifeMgr/regularRoutines}
\input{./content_regularRoutines_plan}

\ifdefined\POSTER
\end{block}
\end{column}%3
\fi

\ifdefined\POSTER
\end{columns}
\fi
\begin{columns}
\begin{column}{0.5\columnwidth}
\ifdefined\POSTER
\begin{block}{\small \bf Week of May $25^{st}$}
  \else  
\underline{\bf Week of May $25^{st}$}\\ 
\fi 
\begin{framed}
\begin{enumerate} 
\mpitem Work: coding practice. 
\mpitem Work: finish off job talk. 
\mpitem Mgmt:Spaces: finish health stuff. 
\mpitem Comm: 
\end{enumerate}
\end{framed}

\ifdefined\POSTER
\end{block}
\fi

\ifdefined\POSTER
\begin{block}{\small \bf Week of June $1^{st}$}
\else
\underline{\bf Week of June $1^{st}$}\\
\fi

\begin{framed}
\begin{enumerate}
\mpitem Work: coding practice
\mpitem Mgmt:Spaces: find apartment. 
\mpitem Mgmt:Spaces: look up unemployment. 
\mpitem Mgmt:Spaces: update basement. 
\mpitem Comm: talk to Aditi? 
\end{enumerate}
\end{framed}
\ifdefined\POSTER
\end{block}
\fi


\end{column}


\begin{column}{0.5\columnwidth}

\ifdefined\POSTER
\begin{block}{\small \bf Week of June $15^{th}$}
\else
\underline{\bf Week of June $15^{th}$}\\
\fi
\begin{framed}
\begin{enumerate}
\mpitem Work: openmp work.
\mpitem Work: coding practice
\mpitem Mgmt:Spaces: sell car? 
\mpitem Comm: 
\end{enumerate}

\end{framed}
\ifdefined\POSTER 
\end{block}
\fi


\ifdefined\POSTER
\begin{block}{\small \bf Week of June $23^{rd}$}
\else
\underline{\bf Week of June $23^{rd}$}\\
\fi
\begin{framed}
\begin{enumerate}
\mpitem Work: openmp work.
\mpitem Work: coding practice
\mpitem Work: consider TM. 
\mpitem Mgmt:Spaces: meds, running. 
\mpitem Comm: consider tm.
\end{enumerate}
\end{framed}
\ifdefined\POSTER 
\end{block}
\fi



\end{column}

\end{columns}
\begin{columns}  %-- Page 2: Column 1 ---------------------------------------------------
\begin{column}{0.10\linewidth}

\begin{block}{Year Plan}
\begin{itemize}
\tiny \item \tiny January: Work: interview, application. , Mgmt:Spaces: get dl , Mgmt:Spaces: get cc, Comm: 
\item \tiny February: Work: proposal, Work: implementation, Mgmt:Spaces: 
\item \tiny March: Work: paper for IWOMP, Work: job talk prep.
\item \tiny April: Work: paper for IWOMP, Work: implementation  
\item \tiny May: Work: do paper, Work: Comm: 
\item \tiny June: Work: work on implementation with UDS 
\item \tiny July: Work: work on implementation with UDS Comm:  
\item \tiny August: Work: paper for IPDPS, 
\item \tiny September: Work: paper for IPDPS 
\item \tiny October: Work: paper for IPDPS  
\item \tiny November: Work: SC stuff, 
\item \tiny December: 
\end{itemize} 
\end{block}

\begin{block}{Month Plan} 

\underline{Week of January $31^{st}$, 2018} 
\begin{itemize}
\tiny \item \tiny Work: 
\item \tiny Mgmt:Spaces: 
\item \tiny Comm: 
\end{itemize}

\underline{Week of February $4^{th}$, 2018}
\begin{itemize}
\tiny \item \tiny Work: send in cover letter + Work: finish application.  
\item \tiny Mgmt:Spaces: 
\item \tiny Comm: 
\end{itemize}

\underline{Week of February $9^{th}$, 2018}
\begin{itemize}
\tiny \item \tiny Work: 
\item \tiny
\end{itemize}

\underline{Week of February $16^{th}$, 2018}
\begin{itemize}
\tiny \item \tiny 
\item \tiny
\end{itemize}


\underline{Week of February $16^{th}$, 2018}
\begin{itemize}
\tiny \item \tiny 
\item \tiny
\end{itemize} 
\end{block}
\end{column}

\end{column}
\end{columns}
\begin{minipage}{0.5\textwidth}
\begin{itemize}
\tiny \item \tiny do scheduling strategies.
\item \tiny work on job talk.
\item \tiny do travel.
\item \tiny social on facebook, catch up with Rishi.
\end{itemize}
\begin{itemize}
\item \tiny 2-month plan: May: finish documents.  June:  finish paper.
\item \tiny 2-month plan: July: paper, meet people  August: paper, meet people.
\item \tiny 2-month plan: September: paper, meet people  October: paper, meet people.
\end{itemize}
\end{minipage}

\begin{multicols}{4}
\begin{minipage}{\columnwidth}
\input{content_projects_psm}
\end{minipage}

%\begin{minipage}{\columnwidth} 
%\input{content_projects_sdh}
%\end{minipage}

\begin{minipage}{\columnwidth}
\input{content_projects_ocn}
\end{minipage}


\begin{minipage}{\columnwidth}
\input{content_projects_ckh} 
\end{minipage}

\begin{minipage}{\columnwidth}
\input{content_projects_ckhp}
\end{minipage}

\begin{minipage}{\columnwidth}
\input{content_projects_scp}
\end{minipage}

\begin{minipage}{\columnwidth}
\underline{\bf \tiny {Mgmt:Spaces: settle on your own}}
\begin{enumerate}
  \tiny \item \tiny Dentist + Get dentist appointment.
\item \tiny Doctor / Counselor + CBT.
  %TODO: organize and group the below. 
\item \tiny Work pay and holidays / hours. 
\item \tiny Flights: finish flight decision making notes, e.g.,
  justification for travel, money/airfare rules, award travel rules. 
\item \tiny Car city sticker.
\item \tiny Car: Get windows side checked + Get windows marking
  checked Ask about warranty.
\item \tiny Mgmt:Spaces(crp): check car tailpipe +
  Mgmt:Spaces(crp):Window \te{1 hour}.
\item \tiny Mgmt:Spaces(bfa): buy things for apartment =
Mgmt:Spaces(bfa): buy a whiteboard + Mgmt:Spaces(bfa): get a chair 
that adjusts height and folds \te{} \dl{} \pr{}.
\end{enumerate}
\end{minipage}

\samepage
\begin{minipage}{\columnwidth}
\underline{\bf \tiny {Project: awards}}\\
\begin{enumerate} 
\item \tiny Stay in touch with HLF - talk to Peter email:  \url{typos^@aol.com}
\item \tiny Do energy econ work with convergence. 
\item \tiny Go to whitehouse thing. 
\item \tiny Plan to be on Program Committee of .. 
\end{enumerate}
\tiny \textit{Schedule:} Looking ahead:\\ 
\end{minipage}
\samepage
\begin{minipage}{\columnwidth}
\underline{\bf \tiny {Worklife:read social intelligence}}
\begin{enumerate} 
\tiny \item \tiny -
\end{enumerate} 
{{\bf  \tiny {Schedule:}} Comm: read social intelligence first four chapters
and get a method to take in information ???? 5 hours. Comm: link comm
together, worklife: latex viewpoint. Looking ahead:} \\
\end{minipage}

\begin{minipage}{\columnwidth}
\underline{\bf Work:code: Project , Coding practice: p for interview.}
\begin{enumerate}
\tiny \item \tiny Work:code (cp.): go through C++, Work:code (cp.): go
through Java + Work:code (cp.): go through OOP. 
\item \tiny Work:code (cp.): code up problems.  ???? 1 week.
\item \tiny Work:code (cp.): integer problems + numerics   -- 1 week.
\item \tiny Work:code (cp.): practice mock interview problems. ???? 1  week.
\end{enumerate}
{{\bf \tiny {Schedule:}} Work:code (cp.): finish bit
  manipulation, Work(cp.): review brain teasers in book, Work(cp.):
  Work(cp.): go through C++.}\\
\end{minipage}
\end{multicols}


\comments{
\begin{columns}
\begin{column}{0.5\columnwidth}
%{\underline{\bf Work:code: Project for running ptychoLib }}
\begin{block}{Work:code: Project for running ptychoLib}
\begin{enumerate}
\tiny \item \tiny Work: download ptychoLib from Kaushik and copy to git repo.
\item \tiny Work: discuss work with A rittenbach + Work: download driver on GPU4.
\item \tiny work: integrate.
\item \tiny Work: do OpenMP 4.5 for ptypy and OpenACC.
\item \tiny Work: run with dataset from PSI.
\item \tiny Work: send message about research paper.
\item \tiny Work: get profiles for PtychoLib code.  
\end{enumerate}
\end{block}

\begin{block}{Worklife:read social intelligence } 
\begin{enumerate} 
\tiny \item \tiny -
\end{enumerate} 
\fbox{\tiny \textit{Schedule:} Comm: read social intelligence first four chapters
and get a method to take in information ???? 5 hours. Comm: link comm
together, worklife: latex viewpoint. Looking ahead:}\\ 
\end{block}

\begin{block}{Mgmt:Spaces: settle on your own}
\begin{enumerate}
  \tiny \item \tiny Dentist + Get dentist appointment.
\item \tiny Doctor / Counselor + CBT.
  %TODO: organize and group the below. 
\item \tiny Work pay and holidays / hours. 
\item \tiny 401k+retirement  + fidelity + bank (money owing).
\item \tiny Flights: finish flight decision making notes, e.g.,
  justification for travel, money/airfare rules, award travel rules.
\item \tiny Car city sticker.
\item \tiny Car: Get windows side checked + Get windows marking
  checked + Get tailpipe checked + Ask about warranty. 
\item \tiny Mgmt:Spaces(crp): check car tailpipe +
  Mgmt:Spaces(crp):Window \te{1 hour}.
\item \tiny Mgmt:Spaces(bfa): buy things for apartment =
  Mgmt:Spaces(bfa): buy a whiteboard + Mgmt:Spaces(bfa): get a chair
  that adjusts height and folds \te{} \dl{} \pr{}. 
\end{enumerate}
\end{block} 

\begin{block}{Mgmt:wp}
\begin{enumerate}
\item \tiny Mgmt:wp: I like Tesla cars and support the company's
  disruption to its industry. At the same time, I don????t think
  that the company will devalue instantaneously the engineering
  accumulated over 8 decades in a BMW.
  {I like cars by Tesla and am supportive of the company????s
    disruptiveness to industry. However, I can????t imagine
    that the company????s cars will make the eight decades of
    engineering that????s in my BMW engine become worthless.
    Tesla technology
    TODO:L3: intent: explain supportiveness of disruptve
    TODO:L3: outcome: people see what I????m about 
    TODO: L4: disruptiveness to industry VS disruption to industry 
    TODO: L4: I have a hard time VS I can????t imagine VS I
    don????t think VS
    TODO:L4: At the same time, VS However, 
    TODO:L4: truly VS [OMIT] 
    TODO:L4: I like VS I love}. 
\item \tiny Mgmt:Spaces: get car check engine light updated
  + Mgmt:Spaces: do car's registration. 
\item \tiny Mgmt:wp: post about Queen.
\item \tiny Mgmt:wp: post about Beckham. 

\item \tiny Mgmt:wp: post about Tesla's. 
\item \tiny Mgmt:wp: post about science on FB. 
\item \tiny Mgmt:wp: post about Queen.
\item \tiny Mgmt:wp: update fb with queen's picture. \te{10
  minutes}. 
\item \tiny Mgmt:wp: Write up on facebook.  
\end{enumerate}           
\end{block} 

\begin{block}{Worklife - Project ???? Comm:rel:}
\begin{enumerate} 
  \tiny \item \tiny Worklife: link management together.  
\item \tiny Worklife: link habits comm and Toastmasters. - done
\item \tiny Worklife: latex viewpoint. 
\item \tiny Comm: read social intelligence first four chapters.
\item \tiny Comm: link all comm together.
\item \tiny Worklife: get emails and texts to analyze.
\item \tiny Worklife: figure out how to book flights and trips quickly. 
\end{enumerate}
\fbox{\tiny \textit{Schedule:} Comm: read social intelligence first
  four chapters and get a method to take in information ???? 5
  hours. Comm: link comm together, worklife: latex viewpoint. Looking ahead:  }
\end{block} 

\begin{block}{Project: Comm}
\begin{enumerate}
\tiny \item \tiny Comm: consider view of girl on Shaadi. 
\item \tiny Comm: consider talking to Illina.
\item \tiny Comm: talk to friends from high school.
\item \tiny Mgmt:Spaces: plan trips. \te{-}.
\item \tiny Mgmt:webpresence: cancel FB friend request of Jocelyn + Mgmt:webpresence: check other friend requests
  sent requests. \te{-}. 
\item \tiny Mgmt:Spaces(GetThingsSpring2016): get Things =
  Mgmt:Spaces(getThings): get suit. \doneTask{Mgmt:webpresence: delete
    Anil Taneja from LinkedIn. \te{1 hour} \dl{Monday} \pr{UI}. - not
    needed since we met with Rishi+ Comm: may have not accepted + Mgmt:webpresence: bad to do so}
\end{enumerate}
{\fbox{\tiny {\it Schedule:} meet others over summer, meet girl over summer.}}\\
%TODO: figure out why this was the issue
\end{block}

\begin{block}{Project: Comm:rel}
\begin{enumerate} 
  \tiny \item \tiny Comm: consider what to do about Bhavna.
\item \tiny Comm: get caught up with Matrimony and Shaadi, Use match,
  make system for meeting. -done
\item \tiny Comm:rel: discuss with Mom and Dad. 
\end{enumerate}
\end{block}

\begin{block}{Work:rel: Project ???? interview with  Berkeley/MIT/industry} 
  \begin{enumerate}
    \tiny \item \tiny Business cards:  - use latex  -- 40 minutes. 
  \item \tiny Cover letter. 
  \item \tiny CV: + Research Summary:  -- 1 week.  - Talking about your
    research. 
  \item \tiny Work:rel: message to contacts about Microsoft \te{} \dl{} \pr{}. 
  \item \tiny Behavioral questions answers:    -- 1 week. 
  \item \tiny Structure in latex. 
  \end{enumerate}
{\small {\it Schedule:} Behavioral answers ???? 1 week, CV prep - 1 day,
  business cards, cover letter -1 hour. }\\ 
\end{block}
\end{column}

\begin{column}{0.5\columnwidth}
\begin{block}{Mgmt:Spaces}
\begin{enumerate} 
\item \tiny Mgmt:Spaces(GetThingsSpring2016): get Things = Mgmt:spaces: get suit
\item \tiny Mgmt:Spaces: get 1 TB disk drive. 
\item \tiny Mgmt:Spaces: finish transferring pictures + Mgmt:Spaces: figure out
how to delete photos from iPhoto + Mgmt:Spaces: figure out why size of
photo booth stays the same  Mgmt:Spaces: Figure out airplane photos
and put in proper album folder. Mgmt:Spaces: Organize photos in
folders + Mgmt:Spaces: Confirm pictures are placed properly and delete
from photos + Mgmt:Spaces: Compress photos into zip drive. +
Mgmt:Spaces: Move photos from folders into temporary disk / USB stick 
+ Mgmt:Spaces:Delete photos from iPhone.
\end{enumerate} 
\end{block}

\begin{block}{Work:comm: (can impact work):}
\begin{enumerate}
\tiny \item \tiny Work:rel: add Shikha.
\item \tiny Mgmt:webpresence: fb like to Lagha. 
\end{enumerate}
\end{block} 

\begin{block}{Work:rel: -  Project ???? Comm: rel:}
\begin{itemize} 
\item \tiny Comm:rel: meet others:  Sweta Kambaskadwar. + Mgmt:webpresence: fb
like of Shalaka????s. L3:past: she liked and suggested to come, lots of
time delayed. I didn????t like back.  Intent: show interest. Outcome:
stay alive with Rucha?
\item \tiny Mgmt:webpresence: take Xin Zhao off and remove anyone else that you
don????t want from work.
\item \tiny Mgmt:webpresence: consider deleting asdfjkl;  and making parts of facebook bmm 2006 public. 
\end{itemize}
\end{block}

\begin{block}{Interview preparing}
%\underline{\bf Work:code: Project , Coding practice: p for interview.}
\begin{enumerate}
\tiny \item \tiny Work:code (cp.): go through C++, Work:code (cp.): go
through Java + Work:code (cp.): go through OOP. 
\item \tiny Work:code (cp.): code up problems.  ???? 1 week.
\item \tiny Work:code (cp.): integer problems + numerics   -- 1 week.
\item \tiny Work:code (cp.): practice mock interview problems. ???? 1  week.
\end{enumerate}
{\tiny {\it {\tiny Schedule:}} Work:code (cp.): finish bit
  manipulation, Work(cp.): review brain teasers in book, Work(cp.):
  Work(cp.): go through C++.} \\
%{\underline{\bf Project: job talk prep}} 
{\tiny {\it {\tiny Schedule:}} Work:code (cp.): finish bit manipulation, Work(cp.): review brain teasers in book, Work(cp.): Work(cp.): go through C++.}\\
\end{block}

\end{column}

\end{columns}
}
\underline{\bf Morning}
\begin{itemize}
\tiny \item \tiny Brush Teeth \timeEst{4 mins}.
\item \tiny Mouthwash, Clean tongue - it helps with breath\timeEst{1mins}
\item \tiny Eating small breakfast.
\item \tiny Check your schedule for meetings / appointments for that
day: Is anything urgent? \timeEst{5 mins}.
\item \tiny Excercise: 1 hour ( Stretch for 10 mins, Treadmill for 30
mins , Lift weights or Yoga 1 hour, Meditation for 10 mins).
\item \tiny Shave (at least every other day) \timeEst{5 mins}.
\item \tiny Shower : (shampoo+conditioner, acne wash,  soap on
underarms/underbody) \timeEst{10 mins}
\item \tiny dry hair, dry face, arms, legs, back, stomach \timeEst{3
mins}
\item \tiny Clothing: belt, check collar, shirt not half-tucked,
matching socks \timeEst{5 mins}
\item \tiny Comb hair, hair gel optional \timeEst{ 1 min}
\item \tiny Check Keys/Wallet/Cell/Badge (get a bucket) \timeEst{1
min}
\item \tiny Open meds cabinet, get water, take medicines \timeEst{1
min}
\item \tiny Wear lenses and rinse out case \timeEst{ 2 mins}
\item \tiny Deodorant or cologne depending on the day \timeEst{1 min}
\item \tiny Wash your face with a face wash - it helps with
acne \timeEst{3 mins}
\item \tiny Moisturize - apply lotion \timeEst{ 2 min}
\item \tiny Neti pot / clean out sinuses - if you’re feeling
congested \timeEst{5 min}
\item \tiny clean out ears, nose \timeEst{5 mins}
\item \tiny Remember to lock door \timeEst{1 mins}
\end{itemize}

\underline{\bf Evening}
\begin{itemize}
\tiny \item \tiny Call family: 30 mins
\item \tiny meet friends: 20 mins
\item \tiny Cleaning dishes / cleaning house: 10 mins
\item \tiny Lay out clothes for the next day, iron if necessary
\item \tiny start laundry if needed: 10 mins,
\item \tiny Collect anything you’ll need for the next day (e.g. dry
cleaning to drop off): 5 mins,
\item \tiny Check Facebook/linkedin/google+: 10 mins, matrimony stuff:10 mins,
\item \tiny Food for lunch/dinner the next day: 10 mins
\end{itemize}
\underline{\bf Night before bed}
%TODO: why isn't enumerate working???
\begin{itemize}
\tiny \item \tiny Finish computer stuff \timeEst{5 mins}
\item \tiny Get into sleeping clothes \timeEst{1 mins}
\item \tiny Before sleeping: brush teeth, floss \timeEst{2 min} 
\item \tiny Properly wash and put away contacts \timeEst{2 mins}
\item \tiny Review the days good things \timeEst{10 min} 
\item \tiny Light Reading \timeEst{ 10 min}
\item \tiny Prayer \timeEst{10 mins}
\end{itemize}
\begin{frame}{Rel Plan}{\today}
\IfFileExists{../thePast/situations/girlsList.csv}{\tiny\csvautotabular{../thePast/situations/girlsList.csv}}{\tiny\csvautotabular{./thePast/situations/girlsList.csv}}
\end{frame}
\begin{frame}{Situations}


\begin{enumerate}

\item Bhaskar's wedding
\item Meet Aditi 


\end{enumerate}

\end{frame}
\begin{block}{Jobs}
  \begin{itemize}
    \tiny \item \tiny cat1: D.E. Shaw | SUNY/BNL: applying . | IBM:
    applied,interviews.  | Sandia: applied and failed, Cray: applied and got offer, USC. 
  \item \tiny cat2: Intel: Applied and failed. Intel: re-application  completed, AMD: applied, Samsung, VMWare: Contacting Yavatkar Kaka. 
  \item \tiny cat3: Google. MongoDB: applied and failed, Facebook. 
  \item \tiny cat4: LLNL. 
  \end{itemize} 
\end{block} 

%TODO: check if below is needed. 
      %\item Friends: Amit, Sangita, Anchit, Kevin. 
      %Networking: 
  \begin{block}{Comm:friends} 
    \begin{itemize} 
    \item Palekar’s:  
      \begin{itemize}
      \item UP: 
      \item Rohun: 
      \end{itemize} 
    \item Bhagwat’s: 
    \item Kapoor’s: 
      \begin{itemize}
        \tiny \item \tiny Anchit: Interaction. Atul is smart. 
      \item \tiny Shuchi: 
      \end{itemize}
    \item Sudharshan’s: 
      \begin{itemize} 
        \tiny \item \tiny Amit:  
      \item \tiny Sangita:  
      \end{itemize}
    \item Kumar’s:
      \begin{itemize}
        \tiny \item \tiny Ashwin: 
      \item \tiny Shilpa: 
      \end{itemize}
    \item Saied’s: 
      \begin{itemize}
        \tiny \item \tiny Laila 
      \item \tiny Faisal 
      \item \tiny Ayesha
      \end{itemize} 
    \item Kukreti’s:
    \item Kumar’s:
    \item UIUC friends: 
      \begin{itemize} 
        \tiny \item \tiny Sadhna: 
      \item \tiny Rishi: 
      \item \tiny Amaeya: 
      \item \tiny Chris: 
      \item \tiny Brian: 
      \item \tiny Arif 
      \end{itemize}
    \item grad school friends 
      \begin{itemize} 
        \tiny \item \tiny  Karan: 
      \item \tiny Gopi: 
      \item \tiny Amanda:  
      \end{itemize}
    \end{itemize} 
  \end{block}
  
%  \begin{block}{Rel} 
%    \begin{itemize} 
%      \small \item \small Shwetha K/r
%    \item \small Shalaka 
%    \item \tiny DCK girl 
%    \item \tiny  Shikha Singhvi: initiated.  
%    \item \small Mamta
%    \item \small Avani 
%    \item \small SH05702678 Palo Alto - 
%    \item \small Sheila G -Sh93522198  
%    \item \small sonalisinha  s: 5103658167 and my email address is: \url{2sonalisinha@gmail.com}
%    \item \small Nandini  - 
%    \item \small Archana from San Jose. 
%    \item \small Im from DC  - B475435: parents initiated. 
%    \item \small Sruthi 
%    \item \small SH12825009 New York, New York - Finance Professional 
%    \item \small Navneet K  - 29 5'8" - SH88263211 
%    \item \small Girl from New York  -27 years
%    \item \small Shwetha Ravi 
%    \item \small Ruchira K ( SH34021888 )2-Way           
%    \item \small SH11680694 from San Francisco. 
%    \item \small Sandhya N. 22 Jun 2016 
%    \item \small Aarti S - 27 - 5' 9'' Charlotte.  
%    \item \small Anu M from Chicago, IL 
%    \item \small Pranati A from Cleveland, OH - 
%    \item \small Meghana K from New York - 
%    \item \small Ssd S - 28 , 5 5 , Boston, MA 
%    \item \small Anj B. - 30 yrs - SH13882555.
%    \end{itemize}
%  \end{block}
\begin{itemize}
          \tiny \item \tiny Monday: 
        \item \tiny Tuesday
        \item \tiny Wednesday
        \item \tiny Thursday
        \item \tiny Friday
        \item \tiny Saturday
        \end{itemize} 

{\underline{\bf Week Plan}  Work: send message to Prof. Gropp, Work: finish getting data set to work,
        Work: talk to Kristina, Mgmt:Spaces: take care of license
        plant + Mgmt:Spaces: take care of Virginia parking ticket,
        Comm: message to Kavita to send pictures}\\ 
      {\underline{\bf Weekend Plan:} Go to NYC, meet Ranjit, see BNL.}\\

%--- Page 2: Block 1-4 
      % howto:Recognize emotions / recognize (precisely) what you're worried about -> methods for eliminating worry. 
      % clean out old worries, put them in pastWorries doc.  
      % remember to define precisely 
      % order from top-to bottom
      \begin{itemize}
        \tiny \item \tiny Anger about UP -> think about the positive
        perspective, and the original
      \item \tiny Anger about Mr. Kapoor ->  leave it
      \item \tiny Anger about a b  -> ...
      \item \tiny Issue with USC : --> things get better. 
      \end{itemize}
\begin{minipage}{0.5\textwidth}
\begin{itemize}
\tiny \item \tiny do scheduling strategies.
\item \tiny work on job talk.
\item \tiny do travel.
\item \tiny social on facebook, catch up with Rishi.
\end{itemize}
\begin{itemize}
\item \tiny 2-month plan: May: finish documents.  June:  finish paper.
\item \tiny 2-month plan: July: paper, meet people  August: paper, meet people.
\item \tiny 2-month plan: September: paper, meet people  October:
  paper, meet people.
\end{itemize}
\end{minipage}

\begin{multicols}{4}
\begin{minipage}{\columnwidth}
\underline{\bf \tiny {Work:code: PRISMA}}
\begin{enumerate}
\item \tiny Work: fix Youssef's code.
\item \tiny Work: download ptychoLib from Kaushik and copy to git repo.
\item \tiny Work: run for Ptypy.
\item \tiny Work: figure out time to talk with Youssef.
\item \tiny Work: download ptychoLib from Kaushik and copy to git repo.

\item \tiny Work: discuss work with A rittenbach + Work: download
  driver on GPU4.

\item \tiny work: integrate.
\item \tiny Work: do OpenMP 4.5 for ptypy and OpenACC.
\item \tiny Work: run with dataset from PSI.
\item \tiny Work: send message about research paper.
\item \tiny Work: get profiles for PtychoLib code.
\item \tiny Work: write report for spec.
\item \tiny Work: ask for an increase in size for HPCC system.
\end{enumerate}
\end{minipage}

\begin{minipage}{\columnwidth}
\underline{\bf \tiny {Work: PRISMA pubs}}
\begin{enumerate}
\tiny \item \tiny Work: create a latex git repo for paper.
\item \tiny Work: find a conference.
\item \tiny Work: create an outline.
\item \tiny Work: get information about JIT compilation.
\end{enumerate}
\end{minipage}

\begin{minipage}{\columnwidth}
\underline{\bf \tiny {Work: Other work at ISI}}
\begin{enumerate}
\item \tiny Work: get information about JIT compilation.
\end{enumerate}
\end{minipage}

\begin{minipage}{\columnwidth}
\underline{\bf \tiny {Work: OpenMPCon submission}}
\begin{enumerate}
\tiny \item \tiny Work: create a latex git repo for paper.
\item \tiny Work: send Prof. Gropp a message.
\item \tiny Work: make notes on static/dynamic scheduling.
\item \tiny Work: make notes on user-defined scheduling.
\end{enumerate}
\end{minipage}

\begin{minipage}{\columnwidth}
\underline{\bf \tiny {Work: Charm++ +OpenMP}}
\begin{enumerate}
\tiny \item \tiny Work: send notes/tasks todo.
\item \tiny Work: do documentation of implementation.
\item \tiny Do Charm++ + OpenMP implementation.
\item \tiny Get GPU implementation of dotProd in Charm++.
\item \tiny Work: get access to Cori machine.
\item \tiny Work: Add notes about OpenMP.
\item \tiny Work: add explanation of dotProduct on OpenMP.
\end{enumerate}
\end{minipage}

\begin{minipage}{\columnwidth} 
\underline{\bf \tiny {Work: Charm++ +OpenMP}}
\begin{enumerate}
\item \tiny Mgmt:wp: post with friends from college. 
\item \tiny Mgmt:wp: update description.
\item \tiny Mgmt:wp: post about Queen.
\item \tiny Comm:rel: update pictures. \te{30 minutes}.
\end{enumerate}
\end{minipage}

\ifdefined\POSTER
  \begin{columns}
    %-- Column 1 ---------------------------------------------------  
   \begin{column}{0.22\columnwidth}
      \begin{block}{Happiness Generation - must maintain every week.}
\else
 \underline{\bf Happiness Generation - must maintain every week.}
\fi
        % explain happiness: show gratitude
\begin{itemize}
          \tiny \item \tiny happy that I have Atul to show me.
        %\item \tiny Happy that I have normal life up to this point. 
       %\item \tiny Think about dad saying, I understand, and want     
          %you to be happy.                             
          \item \tiny T
            \end{itemize}
\ifdefined\POSTER
      \end{block}
\fi

\ifdefined\POSTER
    \begin{block}{Habits}
\else
 \underline{\bf \it Habits}
\fi
      \begin{itemize}
        \tiny \item \tiny back straight + eye contact.
      \item \tiny lips relaxed.
      \item \tiny watch what happens when a hot girl talks to you.
      \end{itemize}
\ifdefined\POSTER
    \end{block}
  \end{column} %1 
\fi

\ifdefined\POSTER
  \begin{column}{0.5\columnwidth}
    \begin{block}{10-year plan}   %-- Block 2-1   
\else
 \underline{\bf 10-year plan}
\fi
      \begin{itemize}
      \item \small Make someone and dad proud.
      \end{itemize}
\ifdefined\POSTER
    \end{block}
\fi

\ifdefined\POSTER
    \begin{block}{3-year plan}
\else
\underline{\bf 3-year plan}
\fi
      \begin{itemize}
      \item \small find someone
      \item \small make 150K
      \item \small network
      \end{itemize}
\ifdefined\POSTER
   \end{block}
      \item \tiny watch what happens when a hot girl talks to you.
      \end{itemize}
\ifdefined\POSTER
    \end{block}
  \end{column} %1                                                                                           
\fi

\ifdefined\POSTER
  \begin{column}{0.5\columnwidth}
    \begin{block}{10-year plan}   %-- Block 2-1         
\else
 \underline{\bf 10-year plan}
\fi
      \begin{itemize}
      \item \small Make someone and dad proud.
      \end{itemize}
\ifdefined\POSTER
    \end{block}
\fi

\ifdefined\POSTER
    \begin{block}{3-year plan}
\else
\underline{\bf 3-year plan}
\fi
      \begin{itemize}
      \item \small find someone
      \item \small make 150K
      \item \small network
      \end{itemize}
\ifdefined\POSTER
    \end{block}
\fi

\ifdefined\POSTER
    \begin{block}{6-month plan}
\else
\underline{\bf 6-month plan}
\fi
        \begin{itemize}
          \small \item \small results + thesis
          \item \small routine + worklife
          \item \small
          \end{itemize}
\ifdefined\POSTER
    \end{block}
\fi

\ifdefined\POSTER
    \begin{block}{Month-by-month}
\else
\underline{\bf Month-by-month}
\fi
      %howto: This is most important, and should be re-visited every  
      %month and definitely every three months(have fixed time within  
      %4 times in the year to do this).     
      \begin{itemize}
      %\item \small \textit{May:} Work: finish paper  + Work: comm: 
      %  finish resume and cover letter. 

\ifdefined\POSTER
\begin{block}{May goals}
\else
\underline{\bf May goals}\\
\fi

\begin{enumerate}
\item \small Work: finish writing goals
  \small \item \small Mgmt:Spaces: clean room
\item \small worklife: practice implemented work to form habits
\item \small Comm: meet people
\end{enumerate}

\ifdefined\POSTER
\end{block}
\fi

\ifdefined\POSTER
\begin{block}{\small \bf Week of September $31^{st}$, 2017:}
\else
\underline{\bf Week of July $31^{st}$: }\\
\fi

\begin{enumerate}
\tiny \item \tiny Work: finish connecting with people regarding implementation.
\item \tiny Mgmt:Spaces: take care of driver's license.
\item \tiny Comm: meet people.
\end{enumerate}

\ifdefined\POSTER
\end{block}
\fi

\ifdefined\POSTER
\begin{block}{Weekend Plans - March $15^{th}$, 2017 to May $1^{st}$,2017}
\else
{\underline{\bf Weekend Plans - March $15^{th}$, 2017 to May $1^{st}$,2017}}\\
\fi

\input{plansForWeekend}

\begin{itemize}
\item \tiny Weekend of July $21^{st}$: Get car fixed. Visit NYC . Details: 
\item \tiny Weekend of July $28^{th}$: Visit Champaign  . Details:
\item \tiny Weekend of August $6^{th}$: Visit NYC Details:
\item \tiny Weekend of August $12^{th}$: Visit SFO?
\item \tiny Weekend of August $19^{th}$: Stay in D.C. - work on weekend.
\item \tiny Weekend of August $26^{th}$: Stay in D.C. - work on weekend.

\item \tiny Weekend of September $3^rd$: Go to San Francisco.

\item \tiny Weekend of September $26^{th}$: Go to New York City.
\item \tiny Weekend of September 
\end{itemize}

\end{itemize}

\ifdefined\POSTER
\end{block}
\fi 

\begin{minipage}{\columnwidth}
\begin{enumerate} 
 \item \tiny Mgmt:Spaces: look for apartment elsewhere. \te{1 hour}. 
\end{enumerate}
\end{minipage} 
\end{multicols}

\begin{columns}
  %-- Page 2: Column 1 --------------------------------------------------- 
  \begin{column}{0.20\linewidth}
    %{\textbf{\underline{Week Aspects(new name)}})
      %--- Page 2: Block 1-1 
    \begin{block}{Routines}
      { \tiny \underline{\bf Routines:} Morning: bfast, exercise/brush,
        floss, shower (hair, eyes, ears, underarms, feet), meds, belt,
        comb hair / dishes, clean kitchen floor. |  Night: running/ put
        away dishes, clean kitchen floor / brush teeth, charge phone,
        clothes for tomorrow, contacts off.}\\
      {\tiny \underline{\bf Sunday Routines:} Routines:
        Experiences,week plan.}\\ 
      {\tiny \underline{\bf Weekday Routines:}}\\
      %TODO: check if weekday routines overlaps into daily routines.
    \end{block} 
      %--- Page 2: Block 1-3
    \begin{block}{Local Happiness}
      % howto:Recognize emotions / recognize (precisely) what you're
      % worried about -> methods for eliminating worry. 
      % clean out old worries, put them in pastWorries doc.  
      % remember to define precisely 
      % order from top-to bottom
      \begin{itemize} 
        \tiny \item \tiny -
      \item \tiny Worrying about gal: think about talking to others.
      \end{itemize} 
    \end{block}
    %--- Page 2: Block 1-4 
    \begin{block}{AngersAndAnxieties}
      % howto:Recognize emotions / recognize (precisely) what you're worried about -> methods for eliminating worry. 
      % clean out old worries, put them in pastWorries doc.  
      % remember to define precisely 
      % order from top-to bottom
      \begin{itemize}
        \item \tiny Issue with USC : $\rightarrow$ things get better. 
        \tiny \item \tiny Anger about UP $\rightarrow$ think about the positive
        perspective, and the original
      \item \tiny Anger about Mr. Kapoor $\rightarrow$  leave it
      \item \tiny Anger about a b  $\rightarrow$ ...
      \end{itemize}
    \end{block}
      %-- Block 1-5
      \begin{block}{Life notes}
        \begin{itemize}
          \tiny \item \tiny Social Intelligence: 
        \end{itemize}
      \end{block}
      % howto:
      \begin{block}
        {\tiny {\bf Week lessons:}}
        \begin{enumerate}
%          \tiny \item \tiny Win Friends/ Influence People
%        \item \tiny Go through 7 habits.
        \item \tiny tm tips.
        \item \tiny Coding problem: 
        \item \tiny Chess tips: 
        \end{enumerate}
            {{\tiny {\tiny \bf  News:}} {\tiny  M: Uber board | S:
                Tony Award's| E: Fallon:  Kimmel:  Colbert: SNL:}}
            {{\tiny {\tiny \bf  Weather:}} {\tiny M: 1100 T: 1100 W:
                0110 R: 0100 F: 0110 Sa: 0110 Su: }}
      \end{block}
  \end{column}
  %-- Column 2 ---------------------------------------------
  \begin{column}{0.6\linewidth}
    \begin{block}{Week Summary} 
      {\underline {\bf Week Plan:} 
        Work: message to Youssef,
        Work: send out write up for git repo, Work: make plan for diffraction patterns, 
        Mgmt:Health: get dentist appointment, Mgmt:Spaces: xcel card,
        Mgmt:Spaces: call doctor for medicine appointment,
        Mgmt:Spaces: fix car tires, Mgmt:Spaces: flight for July,
        Mgmt:Spaces: look for apartment elsewhere,} \\

      {\underline{\bf Weekend Plan:} Meet Puja, Meet Srushti }\\
    \end{block} 
      \begin{block}{Running ToDo} % find a better name 
        \begin{enumerate} 
        \tiny \item \tiny \textbf{Curr} $\rightarrow$ 
      
     \item \tiny Work: put information on installing PtychoLib for Kaushik. 
     \item \tiny Mgmt:Health: get x-rays. 
     \item \tiny Mgmt:Health: call for dentist appointment at Virginia
       dental.
     \item \tiny Mgmt:Health: call about the counselor. 
     \item \tiny Work: run Youssef’s code with params.
     \item \tiny Mgmt:Spaces: book flight to California.
     \item \tiny Mgmt:Spaces: put up apartment for rent.
     \item \tiny Mgmt:Spaces: buy Kitchen magnet.
     \item \tiny Comm: message to Renata.
     \item \tiny EI: get the counselors taken care of in D.C. area. 
     \item \tiny Mgmt:Spaces: look for apartment elsewhere. 
     \item \tiny Work: do writeup for paper. \te{1 hour}. 
     \item \tiny Work: send message to Youssef about question about
       \texttt{nvprof}. \te{1 hour}.
     \item \tiny Mgmt:Spaces: book flight for trip in December. \te{1
       hour}.
     \item \tiny Comm: message to Rohina. 
     \item \tiny Work:rel: email to Renata. \te{10 minutes}. 
     \item \tiny worklife: read social intelligence. \te{2 hour}. 
     \item \tiny Comm: do review for Liberty Towers.
     \item \tiny \textbf{ <-- End Curr } 

     \item \tiny Work: IM system for LLNL.
=======

        \doneTask{Mgmt:Spaces: fix car tires.}


        \tiny \item \tiny \textbf{Curr} $\rightarrow$ 
        \item \tiny Work:admin: tell about reimbursements 
        \item \tiny  Mgmt:Spaces: look for apartment elsewhere. 

        \item \tiny Work: message to Youssef.   

        \item \tiny Work: email about schedule for work. 
        \item \tiny Work: email about git repository. 
        \item \tiny 

        \item \tiny Work: send out write up for git repo 
        \item \tiny Work: make plan for diffraction patterns
        \item \tiny Work: send message about optimizations to do for
          CkLoop. \te{1 hour} \dl{20 minutes}.
         
        \item \tiny Work:rel: email to Abid \te{1 hour}. 

        \item \tiny Mgmt:Health: get dentist appointment. 

        \item \tiny Mgmt:Spaces: flight for September. 
        \item \tiny Mgmt:Spaces: book flight for trip in July to Chicago . \te{1 hour}  
          
        \item \tiny Mgmt:Spaces: xcel card. 
        \item \tiny Mgmt:Spaces: call doctor for medicine appointment.

        \item \tiny Mgmt:Spaces: look for apartment elsewhere          

        \item \tiny Mgmt:Spaces: book flight for trip in December. \te{1 hour}.

        \item \tiny  Comm: prep to meet with Rohina. 
        \item \tiny Comm: message to Shalaka?
        \item \tiny Work:rel: email to Renata. \te{10 minutes}.
        \item \tiny worklife: read social intelligence. \te{2 hour}.           
          
        \item \tiny \textbf{ <-- End Curr } 
          
        \item \tiny Work: IM system for LLNL.
>>>>>>> f99874ec2397c111e47d40225e53c07d5693f7fd
        \end{enumerate}
      \end{block}
      
      % howto: the below is a routine based on the job I'm doing and the
      % circumstances I'm in. Note that this is different from routines
      % above, which is true for a long-term period of over 10 years. 
      \begin{block}{Weekly Meetings}
        \begin{itemize}
          \tiny \item \tiny IWOMP affinity meeting Thursday 7 AM PDT / 9 AM
          CDT call in: 805-639-779 pswd: places. \url{https://llnl.webex.com/llnl/j.php?MTID=m33950b76befb72c0cbc31ea2e3be720c}
        \item \tiny DEG group meeting.  
        \end{itemize}
      \end{block} 
      \begin{block}{Week Daily Schedule}
        % howto: arrange items from running todo into the below
        % sheet management document. 
        %NOTE: we don't use the table format because of fittting
        \begin{columns}
          \begin{column}{0.14\textwidth}{\small \underline{\bf Mon}}
            {\tiny \bf {\tiny weather:} } {\tiny 11/1 s} \\ 
            {\tiny \bf {\tiny todo}}\\ 
            \begin{itemize}
              \tiny \item \tiny Work: do experiments with multiple nodes. 
            \item \tiny Work: get experiments using real data.  
            \item \tiny 
            \end{itemize}
                {\small  \bf schedule}\\
                \begin{enumerate} 
                  \tiny \item \tiny 8-9AM: Regular Routines 
                \end{enumerate}
          \end{column}

          \begin{column}{0.14\textwidth}{\small \underline{\bf Tues}}
            {\bf {\tiny  weather:} } {\tiny 3/1 r} \\ 
            {\bf {\tiny todo}}\\ 
            \begin{itemize}
              \tiny \item \tiny Work: do write-up 
            \end{itemize} 
                {{\bf {\tiny  schedule}}}
                \begin{enumerate} 
                  \tiny \item \tiny 8-9AM: Regular Routines 
                \end{enumerate} 
          \end{column}
          \begin{column}{0.14\textwidth}{\small \underline{\bf Wed}}
            {\tiny \bf weather: } {\tiny 3/1 r} \\ 
            {\tiny {\bf todo}}\\
            \begin{itemize}
              \tiny \item \tiny Work: send email to Prof. Gropp. 
            \item \tiny 
            \item \tiny Comm: message to Anita. 
            \end{itemize}
                {\tiny \bf schedule}\\
                \begin{enumerate} 
                  \tiny \item \tiny 8-9AM: Regular Routines 
                \end{enumerate} 
          \end{column}

          \begin{column}{0.14\textwidth}{\small \underline{\bf Thurs}}
            {\tiny \bf weather: } {\tiny 1/-1 r }\\ 
            {\tiny \bf todo} \\ 
            \begin{itemize}
              \tiny \item \tiny Add in schedule
            \item \tiny 
            \end{itemize} 
                {\tiny {\bf schedule}} \\
                \begin{enumerate} 
                  \tiny \item \tiny 8-9AM: Regular Routines 
                \end{enumerate}
          \end{column} 
          
          \begin{column}{0.14\textwidth}{\small \underline{\bf Fri}}
            {\tiny \bf weather: } {\tiny 3/1 r} \\ 
            {\tiny \bf todo} \\ 
            \begin{itemize}
              \tiny \item \tiny Add in schedule
            \item \tiny 
            \end{itemize} 
                {\tiny \bf schedule} \\
                \begin{enumerate} 
                  \tiny \item \tiny 8-9AM: Regular Routines 
                \end{enumerate}
          \end{column}

          \begin{column}{0.15\textwidth}{\small \underline{\bf Sat}}
            {\tiny \bf weather: } {\tiny 11/1 .2r} \\ 
            { \tiny \bf todo} \\ 
            \begin{itemize}
              \tiny \item \tiny Add in schedule
            \item \tiny 
            \end{itemize} 
                {\tiny \bf schedule} \\
                \begin{enumerate} 
                  \tiny \item \tiny 8-9AM: Regular Routines 
                \end{enumerate}
          \end{column}
         
          \begin{column}{0.15\textwidth}{\small \underline{\bf Sun}}
            {\tiny {\bf weather:} } {\tiny 11/2 r} \\ 
            {\tiny {\bf todo}}\\
            \begin{itemize}
              \tiny \item \tiny Add in schedule
            \end{itemize} 
                {\tiny \bf schedule}\\
                \begin{enumerate} 
                  \tiny \item \tiny 8-9AM: Regular Routines 
                \end{enumerate}
          \end{column}
        \end{columns}
      \end{block}
\end{column}
    
    % ------ Page 2: Column 3
    \begin{column}{0.20\linewidth}
      % ------ Block 2.3.1 
      \begin{block}{Food Plan} 
        \begin{itemize}
          \tiny \item \tiny Google Express: DHDQQJQDRFTXDM95B
        \end{itemize}
      \end{block} 
      \begin{block}{Clothes plan} 
        \begin{itemize}
          \tiny \item \tiny Monday: 
        \item \tiny Tuesday
        \item \tiny Wednesday
        \item \tiny Thursday
        \item \tiny Friday
        \item \tiny Saturday
        \end{itemize} 
      \end{block} 
      
      %-- Block 3-3 
      \begin{block}{Situations}
        % Summary: the below are the situations that define one
        % another.
        % Howto: Put post notes of each situation from list of previous
        % week. Put high importance situations in situationslist. 
        % Put list of upcoming situations on Sunday morning with Pre. 
        \begin{itemize}
          \tiny \item \tiny 
        \item \tiny 
        \end{itemize}
      \end{block}
      % contingincies: 
      % Summary:
    \end{column}
\end{columns}
\ifdefined\POSTER
\begin{block}{Weekend Plans - June $1^{st}$, 2018 to July $15^{th}$, 2018} 
\else
{\underline{\bf Weekend Plans - June $1^{st}$, 2018 to July $15^{th}$, 2018}}\\ 
\fi
\begin{itemize}
\tiny \item \tiny \underline{Weekend of June $1^{st}$:}     {\it Details:}
\item \tiny \underline{Weekend of June  $8^{th}$:} Meet Aditi? {\it Details:}
\item \tiny \underline{Weekend of June $15^{th}$:} Go to SF?  {\it Details:} 
\item \tiny \underline{Weekend of June $22^{nd}$:} Bhaskar's wedding.  {\it Details:} 
\item \tiny \underline{Weekend of June $29^{th}$:} {\it Details:} 
\item \tiny \underline{Weekend of July $8^{th}$:}  Go to
England? \textit{Details:}

\item \tiny \underline{Weekend of July $15^{th}$:}  \textit{Details:}
\end{itemize}

\ifdefined\POSTER
\end{block}
\end{column}
\fi

\ifdefined\POSTER
\begin{block}{Weekend Plans - July $15^{th}$, 2018 to September $1^{st}$, 2018} 
\else
{\underline{\bf Weekend Plans - July $15^{th}$, 2018 to September $1^{st}$, 2018}}\\ 

\begin{itemize}
\tiny \item \tiny \underline{Weekend of July $15^{th}$:}     {\it Details:}
\item \tiny \underline{Weekend of July $22^{nd}$:}  Atul comes to
Illinois {\it Details:}
\item \tiny \underline{Weekend of August $1^{st}$:} Chicago {\it Details:} 
\item \tiny \underline{Weekend of August $9^{th}$:} Chicago {\it Details:} 
\item \tiny \underline{Weekend of August $16^{th}$:} \textit{Details:}

\item \tiny \underline{Weekend of August $23^{rd}$:}  \textit{Details:}

\end{itemize}

\ifdefined\POSTER
\end{block}
\end{column}
\fi
\begin{frame}
\frametitle{Routines}

\input{routines}
\end{frame}

\begin{frame}
\frametitle{Local Happiness}
\end{frame}


\begin{frame} 
\frametitle{AngersAndAnxieties}
\input{angersAndAnxieties-curr}
\end{frame}

\begin{frame}
\frametitle{Life Notes}
\end{frame}

\begin{frame}
\frametitle{Week lessons} 
\end{frame}

\begin{frame}
\frametitle{Week Summary}
\end{frame}


\begin{frame}
\frametitle{Running ToDo}
\end{frame}

\begin{frame} 
\frametitle{Running ToDo} 
\end{frame}

\underline{\textbf{Deadline:} September $31^{st}$, 2017} 
\begin{enumerate}

\item jobs $\rightarrow$ we'll find something , we'll look for something on east. 

\item RS $\rightarrow$ forget her 

\end{enumerate} 

\begin{columns}  %-- Page 2: Column 1 ---------------------------------------------------

\begin{column}{0.10\linewidth}

\begin{block}{Projects}
%Project superspace: mental health

% Project superspace: work 

% Project: Fundamental knowledge. 

% Project space: applications 

\underline{Computational Reqs} 
\underline{\textbf{Deadline:} January $29^{th}$, 2017} 
\begin{enumerate}
\pitem 
\pitem 
\end{enumerate} 

\underline{Tomography Code} 
\underline{\textbf{Deadline:} February $4^{th}$, 2017} 
\begin{enumerate}
\pitem 
\pitem 
\end{enumerate} 

\underline{Networking Infrastructure} 
\underline{\textbf{Deadline:} September $22^{nd}$, 2017} 
\begin{enumerate}
\pitem 
\pitem 
\end{enumerate} 

\underline{Publication} 
\underline{\textbf{Deadline:} September $22^{nd}$, 2017} 
\begin{enumerate}
\pitem 
\pitem 
\end{enumerate}

% Project space: programming and systems

% -- Project: OpenMP 
\underline{OMP proposal} 
\underline{\textbf{Deadline:} September $22^{nd}$, 2017} 
\begin{enumerate}
\pitem 
\pitem 
\end{enumerate} 

% -- Project: CkLoopHyb paper 
\underline{CkLoopHyb paper}
\underline{\textbf{Deadline:} September $22^{nd}$, 2017}
\begin{enumerate}
\pitem Add template to git repository.
\pitem Add writeup for dot product results on Cori.
\pitem Get PIC results with Charm++-everywhere for BW.
\pitem Need a new application. 

\ptask Update the paper technique to be consistent with experiments.  
\ptask Work: update paper .tex file with dot prod. \te{30 minutes}.
\ptask Add PAPI cache misses for problem statement.
\ptask Fix diagrams.
\ptask Figure out what to put at the top block of first quadrant.
\ptask Add content in extended paper.
\ptask Add code for PIC in bottom left quadrant.
\ptask Add projections results.
\ptask Add to related work.
\ptask Get PIC results with Charm++-everywhere, Charm++ + CkLoop for Cori.
\ptask Get results for Charm++ + CkLoop for missing data points.
\ptask Show results for dot product using Charm++ + OpenMP, and for
dot product with Charm++ + CkLoop.
%\doneTask{ Show code with Charm++ + OpenMP.}
\pitem Merge with git repository.
\pitem Send message to meet for results.
\pitem Work: message to Kathryn about poster.
\end{enumerate}

\underline{Schedule} \\ 
\begin{enumerate}
\pitem 
\end{enumerate} 
\end{block} 

%Project: interviewing 
\underline{Interviewing} 
\underline{\textbf{Deadline:}} 
\begin{enumerate}
\pitem 
\pitem 
\end{enumerate} 


%Project: extra-curricular

\begin{block}{Year Plan}
\begin{itemize}
\tiny \item \tiny January: Work: interview, application. , Mgmt:Spaces: get dl , Mgmt:Spaces: get cc, Comm: 
\item \tiny February: Work: proposal, Work: implementation, Mgmt:Spaces: 
\item \tiny March: Work: paper for IWOMP, Work: job talk prep.
\item \tiny April: Work: paper for IWOMP, Work: implementation  
\item \tiny May: Work: do paper, Work: Comm: 
\item \tiny June: Work: work on implementation with UDS 
\item \tiny July: Work: work on implementation with UDS Comm:  
\item \tiny August: Work: paper for IPDPS, 
\item \tiny September: Work: paper for IPDPS 
\item \tiny October: Work: paper for IPDPS  
\item \tiny November: Work: SC stuff, 
\item \tiny December: 
\end{itemize} 
\end{block}

\begin{block}{Month Plan}
\underline{Week of January $31^{st}$, 2018}
\begin{itemize}
\tiny \item \tiny Work: 
\item \tiny Mgmt:Spaces: 
\item \tiny Comm: 
\end{itemize}

\underline{Week of February $4^{th}$, 2018}
\begin{itemize}
\tiny \item \tiny Work: send in cover letter + Work: finish application.  
\item \tiny Mgmt:Spaces: 
\item \tiny Comm: 
\end{itemize}

\underline{Week of February $9^{th}$, 2018}
\begin{itemize}
\tiny \item \tiny Work: 
\item \tiny
\end{itemize}

\underline{Week of February $16^{th}$, 2018}
\begin{itemize}
\tiny \item \tiny 
\item \tiny
\end{itemize}

\underline{Week of February $16^{th}$, 2018}
\begin{itemize}
\tiny \item \tiny 
\item \tiny
\end{itemize}

\end{block}

\end{column}
  \begin{column}{0.10\linewidth}
    %{\textbf{\underline{Week Aspects(new name)}})
      %--- Page 2: Block 1-1 
    \begin{block}{Routines}
      { \tiny \underline{\bf Routines:} Morning: bfast, exercise/brush,
        floss, shower (hair, eyes, ears, underarms, feet), meds, belt,
        comb hair / dishes, clean kitchen floor. |  Night: running/ put
        away dishes, clean kitchen floor / brush teeth, charge phone,
        clothes for tomorrow, contacts off.}\\
      {\tiny \underline{\bf Sunday Routines:} Routines:
        Experiences,week plan.}\\ 
      {\tiny \underline{\bf Weekday Routines:}}\\
      %TODO: check if weekday routines overlaps into daily routines.
    \end{block} 
      %--- Page 2: Block 1-3
    \begin{block}{Local Happiness}
      % howto:Recognize emotions / recognize (precisely) what you're
      % worried about -> methods for eliminating worry. 
      % clean out old worries, put them in pastWorries doc.  
      % remember to define precisely 
      % order from top-to bottom
      \begin{itemize} 
        \tiny \item \tiny -
      \item \tiny Worrying about gal: think about talking to others.
      \end{itemize} 
    \end{block}
    %--- Page 2: Block 1-4 
    \begin{block}{AngersAndAnxieties}
      % howto:Recognize emotions / recognize (precisely) what you're worried about -> methods for eliminating worry. 
      % clean out old worries, put them in pastWorries doc.  
      % remember to define precisely 
      % order from top-to bottom
      \begin{itemize}
      \item \tiny Problem with Rathi: $\rightarrow$ do what she
        says. it's ok. 

        \item \tiny Issue with job: $\rightarrow$ we'll find
          something.  

%        \tiny \item \tiny Anger about UP $\rightarrow$ think about the positive
%        perspective, and the original
%      \item \tiny Anger about Mr. Kapoor $\rightarrow$  leave it
%      \item \tiny Anger about a b  $\rightarrow$ ...
      \end{itemize}
    \end{block}
      %-- Block 1-5
      \begin{block}{Life notes}
        \begin{itemize}
          \tiny \item \tiny Social Intelligence: 
        \end{itemize}
      \end{block}
      % howto:
      \begin{block}
        {\tiny {\bf Week lessons:}}
        \begin{enumerate}
        \item \tiny tm tips. 
        \item \tiny Coding problem:
        \item \tiny Chess tips: 
        \end{enumerate}
            {{\tiny {\tiny \bf  News:}} {\tiny  M:  | S: 
                | E: Fallon:  Kimmel:  Colbert: SNL:}}
            {{\tiny {\tiny \bf  Weather:}} {\tiny M: 1100 T: 1100 W: 41/34 .1r 
                 R: 51/46 .60r F: 62/36 .7r a Sa: 42/20 .10r Su: 31/17 }}
           % \input{weather} 
      \end{block}
  \end{column}
  %-- Column 2 ---------------------------------------------
  \begin{column}{0.6\linewidth}
    \begin{block}{Week Summary} 
      {\underline {\bf Week Plan:} 
        Work: send e-mail to Sam Williams, 
        Work: send updates to Harshitha, Work: message to , 
        Work: apply to other places, 
        Mgmt:Spaces: update MetroMile, Comm: e-mail to Rathi? 
      }\\ 
      {\underline{\bf Weekend Plan:} Celebrate Mother's Day. } \\
  
    \end{block}
    \begin{block}{Running ToDo} % find a better name 
      \item \tiny Work: apply to other places, 
        
      \doneTask{Mgmt:Spaces: get credit card. }
      \doneTask{Work: message about OpenMP stuff.}

      \begin{enumerate}

        
      \item \tiny \textbf{Curr} $\rightarrow$ 
        
      \item \tiny Work: coding practice. 
      \item \tiny Work: job talk.

      \item \tiny Mgmt:Spaces: get dentist appt.
 
      \item \tiny Comm: e-mail to Rathi?  := 
        
        Hi Rathi, 
        
        I'm in Illinois at home right now receiving severance payments from my
        previous employer. I'm working for my father's company at Charmworks
        this summer while in the Bay Area through the summer. I'll be
        at BNL most likely in September.
        
        Vivek

      %\item \tiny Work: do slides for UDS. 
      %\item \tiny Work:rel: send out cover letter. 
      
      \item \tiny Comm: upload photos.
        
      \item \tiny \textbf{Curr} $\rightarrow$ 

      \item \tiny Mgmt:Spaces: get glasses. 
  
      \item \tiny Comm: talk with Toni. 
      \item \tiny Work:rel: email to Renata. \te{10 minutes} 
      \item \tiny Comm: message to Sateja.
        
        Hey, I followed you on LinkedIn. I think your work is really good. 
        Let me know if you want to grab coffee sometime in the city. 
        
      \item \tiny \textbf{ <-- End Curr }
      \item \tiny Mgmt:wp: add photos from college.           
      \item \tiny Mgmt:Spaces: post apartment on craigslist. \te{1
        hour}.
      \item \tiny Comm: message to Rishi and Mike about meeting. 
      \item \tiny worklife: read social intelligence. \te{2 hour} 
      \item \tiny Work(psm): do document with slides. \te{10 minutes}.
      \item \tiny Mgmt:Spaces: buy floor mats by BMW. 
      \item \tiny Mgmt:Spaces: get face scrub
      \item \tiny Mgmt:Spaces: ask Mom to get clothes.
      \item \tiny Mgmt:Spaces: get clothes. 
      \item \tiny worklife: practice posing in a picture.  
      \item \tiny Comm: message to girl. \te{10 minutes} \pr{Urgent}. 
      \item \tiny Mgmt:wp: add tags of photos from this past weekend.  
      \item \tiny Mgmt:Spaces: call about Admiral's Club Card.
      \item \tiny Work: IM system for LLNL. 
      \item \tiny Work: get results for n-body. 
      \item \tiny Comm: message to Rupali Gr. 
        Hi Rupali, I hope that you're doing well. -Vivek


      \end{enumerate}
    \end{block} 


\begin{block}{DayPlans} 

  Sunday:   
  | Monday: 
  | Tuesday: 

  - Work: questions for letter. 
  - Work: prep for Todd. 

1. Talk about ISI situation.
2. Tell about other places interviewing. 
3. Talk about past work with LLNL, current work. 
4. Talk about meeting times. 
5. Talk about trip timings available to talk more if interested. 


  - Work: reply to NERSC. 

  - Work: reply to Sam Williams with information. 
  - Work: reply for Apple interview.

  - Mgmt:Spaces: book trip back. 
  - Mgmt:Spaces: 


  - Comm: message to 
  - Comm: message to Madhura.  

  | Wednesday: 
  | Thursday: 
| Friday: 
| Saturday:  
\end{block}

\begin{block}{Alg for Mgmt}
Alg for Mgmt:Alg for Comm   L0:  L1:  L2:  L3:  Maps L4: L5: -> L0
TODO:  and prioritize . Use colors for levels Howto:  
\end{block} 

\begin{block}{Meeting Information}
BlueJeans meeting ID: 8562450706.
Webex MeetingID: 805639779  
\end{block} 

\begin{block}{Situations} 
\begin{enumerate}
\item Meet Steve: 
\end{enumerate} 
\end{block}

\begin{block}{Rel}
\underline{Rel-chat-short}: Bhakti J., Rath S, Vinita G. , Aishwarya ,
Madhura, Anushya, Aditi 

\underline{Rel-chat-like-toinitiate}: Sateja P. , Anuja D., Shilpa G., Sneha from NJ. 

\underline{Rel-chat}:  cat1:  Toni,, S Van., Bhakti, Shalaka/Rucha, Sateja P, Anuja
D. ,  Divya, cat2: sonal mukhi, Mamta, sapana/india, Avani, cat 3:
Shilpa Ghate, Renuka, Renata, 
\end{block}
  
  % howto: the below is a routine based on the job I'm doing and the
  % circumstances I'm in. Note that this is different from routines
  % above, which is true for a long-term period of over 10 years. 
  \begin{block}{Weekly Meetings}
    \begin{itemize}
      \tiny \item \tiny IWOMP affinity meeting Thursday 7 AM PDT / 9 AM
      CDT call in: 805-639-779 pswd: places. \url{https://llnl.webex.com/llnl/j.php?MTID=m33950b76befb72c0cbc31ea2e3be720c}
    \item \tiny DEG group meeting.          \end{itemize}
  \end{block} 

      \begin{block}{Week Daily Schedule}
        % howto: arrange items from running todo into the below
        % sheet management document. 
        %NOTE: we don't use the table format because of fittting
        \begin{columns}
          \begin{column}{0.14\textwidth}{\small \underline{\bf Mon}}
            {\tiny \bf {\tiny weather:} } {\tiny 11/1 s} \\ 
            {\tiny \bf {\tiny todo}}\\ 
            \begin{itemize}
              \tiny \item \tiny Work: do experiments with multiple nodes. 
            \item \tiny Work: get experiments using real data. 
          \item \tiny Mgmt:Spaces: get the Driver's License.  
      \item \tiny Mgmt:Spaces: cancel order from LinkedIn premium +
        Mgmt:Spaces:cancel order of Youtube Red.  
            \end{itemize}
                {\small  \bf schedule}\\
                \begin{enumerate} 
                  \tiny \item \tiny 8-9AM: Regular Routines 
                \end{enumerate}
          \end{column}

          \begin{column}{0.14\textwidth}{\small \underline{\bf Tues}}
            {\bf {\tiny  weather:} } {\tiny 3/1 r} \\ 
            {\bf {\tiny todo}}\\ 
            \begin{itemize}
              \tiny \item \tiny Work: do write-up 
            \end{itemize} 
                {{\bf {\tiny  schedule}}}
                \begin{enumerate} 
                  \tiny \item \tiny 8-9AM: Regular Routines 
                \end{enumerate} 
          \end{column}
          \begin{column}{0.14\textwidth}{\small \underline{\bf Wed}}
            {\tiny \bf weather: } {\tiny 3/1 r} \\ 
            {\tiny {\bf todo}}\\
            \begin{itemize}
              \tiny \item \tiny Work: send email to Prof. Gropp. 
            \item \tiny 
            \item \tiny Comm: message to Anita. 
            \end{itemize}
                {\tiny \bf schedule}\\
                \begin{enumerate} 
                  \tiny \item \tiny 8-9AM: Regular Routines 
                \end{enumerate} 
          \end{column}

          \begin{column}{0.14\textwidth}{\small \underline{\bf Thurs}}
            {\tiny \bf weather: } {\tiny 1/-1 r }\\ 
            {\tiny \bf todo} \\ 
            \begin{itemize}
              \tiny \item \tiny Add in schedule 
            \item \tiny Work:admin: get slide updated.  
              \item \tiny Work: admin: send cc statement. 

            \end{itemize} 
                {\tiny {\bf schedule}} \\
                \begin{enumerate} 
                  \tiny \item \tiny 8-9AM: Regular Routines 
                \end{enumerate}
          \end{column} 
          
          \begin{column}{0.14\textwidth}{\small \underline{\bf Fri}}
            {\tiny \bf weather: } {\tiny 3/1 r} \\ 
            {\tiny \bf todo} \\ 
            \begin{itemize} 
            \item \tiny Work:rel: cover letter for LLNL.
            \item \tiny Work: e-mail to JP and Steve about acheivements.
            \item \tiny Work: send e-mail. 
            \item \tiny Mgmt:Spaces: give back Internet box. 
            \item \tiny Mgmt:Spaces: get the Driver's License.  
      \item \tiny Mgmt:Spaces: cancel order from LinkedIn premium +
        Mgmt:Spaces:cancel order of Youtube Red. 
            \item \tiny Comm: reply on Coffee Meets Bagel.
            \item \tiny Comm: reply to Aishwarya
            \item \tiny Comm:rel: talk with Vinita. 
                
            \end{itemize} 
                {\tiny \bf schedule} \\
                \begin{enumerate} 
                  \tiny \item \tiny 8-9AM: Regular Routines 
                \end{enumerate}
          \end{column}

          \begin{column}{0.15\textwidth}{\small \underline{\bf Sat}}
            {\tiny \bf weather: } {\tiny 11/1 .2r} \\ 
            { \tiny \bf todo} \\ 
            \begin{itemize}
              \tiny \item \tiny Add in schedule
            \item \tiny 
            \end{itemize} 
                {\tiny \bf schedule} \\
                \begin{enumerate} 
                  \tiny \item \tiny 8-9AM: Regular Routines 
                \end{enumerate}
          \end{column}
         
          \begin{column}{0.15\textwidth}{\small \underline{\bf Sun}}
            {\tiny {\bf weather:} } {\tiny 11/2 r} \\ 
            {\tiny {\bf todo}}\\
            \begin{itemize}
              \tiny \item \tiny Add in schedule
            \end{itemize} 
                {\tiny \bf schedule}\\
                \begin{enumerate} 
                  \tiny \item \tiny 8-9AM: Regular Routines 
                \end{enumerate}
          \end{column}
        \end{columns}
      \end{block}
\end{column}
    
    % ------ Page 2: Column 3
    \begin{column}{0.20\linewidth}
      % ------ Block 2.3.1 
      \begin{block}{Food Plan} 
        \begin{itemize}
          \tiny \item \tiny Google Express: DHDQQJQDRFTXDM95B
        \end{itemize}
      \end{block} 
      \begin{block}{Clothes plan} 
        \begin{itemize}
          \tiny \item \tiny Monday: 
        \item \tiny Tuesday
        \item \tiny Wednesday
        \item \tiny Thursday
        \item \tiny Friday
        \item \tiny Saturday
        \end{itemize} 
      \end{block} 
      
      %-- Block 3-3 
      \begin{block}{Situations}
        % Summary: the below are the situations that define one
        % another.
        % Howto: Put post notes of each situation from list of previous
        % week. Put high importance situations in situationslist. 
        % Put list of upcoming situations on Sunday morning with Pre. 
        \begin{itemize}
          \tiny \item \tiny 
        \item \tiny 
        \end{itemize}
      \end{block}
      % contingincies: 
      % Summary:
    \end{column}
\end{columns}
\begin{frame}{Year Plan}

\end{frame}
