\begin{columns}  %-- Page 2: Column 1 ---------------------------------------------------


\begin{column}{0.10\linewidth}


\begin{block}{Projects}

\end{block}


\begin{block}{Month Plan}

\end{block}

\end{column}
  \begin{column}{0.10\linewidth}
    %{\textbf{\underline{Week Aspects(new name)}})
      %--- Page 2: Block 1-1 
    \begin{block}{Routines}
      { \tiny \underline{\bf Routines:} Morning: bfast, exercise/brush,
        floss, shower (hair, eyes, ears, underarms, feet), meds, belt,
        comb hair / dishes, clean kitchen floor. |  Night: running/ put
        away dishes, clean kitchen floor / brush teeth, charge phone,
        clothes for tomorrow, contacts off.}\\
      {\tiny \underline{\bf Sunday Routines:} Routines:
        Experiences,week plan.}\\ 
      {\tiny \underline{\bf Weekday Routines:}}\\
      %TODO: check if weekday routines overlaps into daily routines.
    \end{block} 
      %--- Page 2: Block 1-3
    \begin{block}{Local Happiness}
      % howto:Recognize emotions / recognize (precisely) what you're
      % worried about -> methods for eliminating worry. 
      % clean out old worries, put them in pastWorries doc.  
      % remember to define precisely 
      % order from top-to bottom
      \begin{itemize} 
        \tiny \item \tiny -
      \item \tiny Worrying about gal: think about talking to others.
      \end{itemize} 
    \end{block}
    %--- Page 2: Block 1-4 
    \begin{block}{AngersAndAnxieties}
      % howto:Recognize emotions / recognize (precisely) what you're worried about -> methods for eliminating worry. 
      % clean out old worries, put them in pastWorries doc.  
      % remember to define precisely 
      % order from top-to bottom
      \begin{itemize}
        \item \tiny Issue with USC : $\rightarrow$ things get better. 
        \tiny \item \tiny Anger about UP $\rightarrow$ think about the positive
        perspective, and the original
      \item \tiny Anger about Mr. Kapoor $\rightarrow$  leave it
      \item \tiny Anger about a b  $\rightarrow$ ...
      \end{itemize}
    \end{block}
      %-- Block 1-5
      \begin{block}{Life notes}
        \begin{itemize}
          \tiny \item \tiny Social Intelligence: 
        \end{itemize}
      \end{block}
      % howto:
      \begin{block}
        {\tiny {\bf Week lessons:}}
        \begin{enumerate}
        \item \tiny tm tips.
        \item \tiny Coding problem: 
        \item \tiny Chess tips: 
        \end{enumerate}
            {{\tiny {\tiny \bf  News:}} {\tiny  M:  | S: 
                | E: Fallon:  Kimmel:  Colbert: SNL:}}
            {{\tiny {\tiny \bf  Weather:}} {\tiny M: 1100 T: 1100 W: 41/34 .1r 
                 R: 51/46 .60r F: 62/36 .7r a Sa: 42/20 .10r Su: 31/17 }} 

           % \input{weather} 
      \end{block}
  \end{column}
  %-- Column 2 ---------------------------------------------
  \begin{column}{0.6\linewidth}
    \begin{block}{Week Summary} 

      {\underline {\bf Week Plan:}  Work:admin: finish re-imbursements,
        Work: send out review, Work: do slides for UDS, Work:rel:
        finish resume upload, Work:rel: send out cover letter, Comm: upload pictures, Comm: upload
        photos, Comm: message to Arif, }\\ 

      {\underline{\bf Weekend Plan:} Move out of apartment. } \\

    \end{block}
    \begin{block}{Running ToDo} % find a better name 
      
      \begin{enumerate}
      \item \tiny \textbf{Curr} $\rightarrow$ 
      \item \tiny Comm: message to Arif. 
      \item \tiny Work: go through IPDPS paper.  
      \item \tiny Mgmt:Spaces: get glasses. 
        \doneTask{Work(psm:nt): reply for journal.}
        \doneTask{Work: ask about LLVM compiler to Michael Klemm.}
        \doneTask{ Mgmt:Spaces: get points on Southwest back.}
        \doneTask{Mgmt:Spaces: finalize dinner with Bhavesh.}
        \doneTask{Mgmt:Spaces: flight to LAX. } 
        \doneTask{Work:admin: update resume}.
        \doneTask{Work: prep for discussion with OpenMP.}
        \doneTask{Mgmt:Spaces: finalize travel for Boston. }
      \doneTask{ Work: talk with Michael Klemm,}
      \doneTask{Work:(ckl:hms): send e-mail to Harshitha. } 
     
      \item \tiny \textbf{Curr} $\rightarrow$ 
      \item \tiny Work:(psm:up): send JP slides with updates. 
      \item \tiny Work:(uds:sld): do slides for UDS. 
      \item \tiny Work: send e-mail about 
        
        \tiny \item \tiny Work:admin: finish re-imbursements. 
        
      \item \tiny Work:rel:cvl:upd):  do cover letter for LLNL = Work: rel: explain reason for wanting to join LLNL + Work:rel:(cvl): explain your
        contributions + Work:rel:(cvl):  +       \item \tiny Work:rel: send e-mail to Nathan Tallent 
       
      \item \tiny Work:rel: do application for HLFF = Work:rel: get degree
        certificate + Work:rel: add research statement + Work:rel: write letter of motivation.  

      \item \tiny Mgmt:Spaces: get driver's license from VA.        
 
      \item \tiny Mgmt:Spaces:(mvo): Move out of apartment  =
        \doneTaskNoItem{Mgmt:Spaces:(mvo): move tv} + \doneTaskNoItem{Mgmt:Spaces:(mvo): take out small
        things} + \doneTaskNoItem{Mgmt:Spaces:(mvo): clean up} + \doneTaskNoItem{Mgmt:Spaces:(mvo): give keys} + \doneTaskNoItem{Mgmt:Spaces:(mvo): xcel Dominion Power} + Mgmt:Spaces:(mvo): give back Internet box.  

      \item \tiny Mgmt:Spaces: get glasses. 

      \item \tiny Mgmt:wp: add Andy Schmidt
      \item \tiny Mgmt:wp: reply to Sam Skalicky. 

      \item \tiny Comm: upload pictures
      \item \tiny Comm: upload photos. 
  
      \item \tiny Work:admin: submit receipts for travel. 
      \item \tiny Work:admin: submit receipts for Bagel. 
        \tiny \item[] \tiny \textbf{Curr} $\rightarrow$

      \item \tiny {\bf Curr} $\rightarrow$
      \item \tiny Work: finish proposal slides. 
      \item \tiny WOrk:rel: do cover letter for BNL.
      \item \tiny Mgmt:Spaces: talk with Martin Kong.
        
      \item \tiny Work: admin: send in receipts for SC17.
  
      \item \tiny Work: send in application to PNNL. 
        
      \item \tiny Mgmt:wp: add profile.
      \item \tiny Mgmt:wp: add about me. 
        
      \item \tiny Mgmt:wp: add profile 
      \item \tiny Work:rel: email to Renata. \te{10 minutes} 
      \item \tiny Comm: message to Sateja. 
        Hey, I followed you on LinkedIn. I think your work is really good. 
        Let me know if you want to grab coffee sometime in the city. 
      \item \tiny Comm:rel: talk to Shweta.
      \item \tiny Comm: talk with Toni. 

      \item \tiny \textbf{ <-- End Curr }
      \item \tiny Mgmt:wp: add photos from college. 
      \item \tiny Comm: message to Rishi and Mike about meeting. 
      \item \tiny worklife: read social intelligence. \te{2 hour} 
      \item \tiny Work(psm): do document with slides. \te{10 minutes}.
      \item \tiny Mgmt:Spaces: buy floor mats by BMW. 
      \item \tiny Mgmt:Spaces: get face scrub
      \item \tiny Mgmt:Spaces: ask Mom to get clothes.
      \item \tiny Mgmt:Spaces: get clothes. 
      \item \tiny worklife: practice posing in a picture.  
      \item \tiny Comm: message to girl. \te{10 minutes} \pr{Urgent}. 
      \item \tiny Mgmt:wp: add tags of photos from this past weekend.  
      \item \tiny Mgmt:Spaces: call about Admiral's Club Card.
      \item \tiny Work: IM system for LLNL. 
        
      \end{enumerate}
    \end{block}
  
  % howto: the below is a routine based on the job I'm doing and the
  % circumstances I'm in. Note that this is different from routines
  % above, which is true for a long-term period of over 10 years. 
  \begin{block}{Weekly Meetings}
    \begin{itemize}
      \tiny \item \tiny IWOMP affinity meeting Thursday 7 AM PDT / 9 AM
      CDT call in: 805-639-779 pswd: places. \url{https://llnl.webex.com/llnl/j.php?MTID=m33950b76befb72c0cbc31ea2e3be720c}
    \item \tiny DEG group meeting.          \end{itemize}
  \end{block} 
      \begin{block}{Week Daily Schedule}
        % howto: arrange items from running todo into the below
        % sheet management document. 
        %NOTE: we don't use the table format because of fittting
        \begin{columns}
          \begin{column}{0.14\textwidth}{\small \underline{\bf Mon}}
            {\tiny \bf {\tiny weather:} } {\tiny 11/1 s} \\ 
            {\tiny \bf {\tiny todo}}\\ 
            \begin{itemize}
              \tiny \item \tiny Work: do experiments with multiple nodes. 
            \item \tiny Work: get experiments using real data.  
            \item \tiny 
            \end{itemize}
                {\small  \bf schedule}\\
                \begin{enumerate} 
                  \tiny \item \tiny 8-9AM: Regular Routines 
                \end{enumerate}
          \end{column}

          \begin{column}{0.14\textwidth}{\small \underline{\bf Tues}}
            {\bf {\tiny  weather:} } {\tiny 3/1 r} \\ 
            {\bf {\tiny todo}}\\ 
            \begin{itemize}
              \tiny \item \tiny Work: do write-up 
            \end{itemize} 
                {{\bf {\tiny  schedule}}}
                \begin{enumerate} 
                  \tiny \item \tiny 8-9AM: Regular Routines 
                \end{enumerate} 
          \end{column}
          \begin{column}{0.14\textwidth}{\small \underline{\bf Wed}}
            {\tiny \bf weather: } {\tiny 3/1 r} \\ 
            {\tiny {\bf todo}}\\
            \begin{itemize}
              \tiny \item \tiny Work: send email to Prof. Gropp. 
            \item \tiny 
            \item \tiny Comm: message to Anita. 
            \end{itemize}
                {\tiny \bf schedule}\\
                \begin{enumerate} 
                  \tiny \item \tiny 8-9AM: Regular Routines 
                \end{enumerate} 
          \end{column}

          \begin{column}{0.14\textwidth}{\small \underline{\bf Thurs}}
            {\tiny \bf weather: } {\tiny 1/-1 r }\\ 
            {\tiny \bf todo} \\ 
            \begin{itemize}
              \tiny \item \tiny Add in schedule 
            \item \tiny Work:admin: get slide updated.  
              \item \tiny Work: admin: send cc statement. 

            \end{itemize} 
                {\tiny {\bf schedule}} \\
                \begin{enumerate} 
                  \tiny \item \tiny 8-9AM: Regular Routines 
                \end{enumerate}
          \end{column} 
          
          \begin{column}{0.14\textwidth}{\small \underline{\bf Fri}}
            {\tiny \bf weather: } {\tiny 3/1 r} \\ 
            {\tiny \bf todo} \\ 
            \begin{itemize} 
            \item \tiny Work:rel: cover letter for LLNL.
            \item \tiny Work: e-mail to JP and Steve about acheivements.
            \item \tiny Work: send e-mail. 
            \item \tiny Mgmt:Spaces: give back Internet box. 
            \item \tiny Mgmt:Spaces: get the Driver's License.  
      \item \tiny Mgmt:Spaces: cancel order from LinkedIn premium +
        Mgmt:Spaces:cancel order of Youtube Red. 
            \item \tiny Comm: reply on Coffee Meets Bagel.
            \item \tiny Comm: reply to Aishwarya
            \item \tiny Comm:rel: talk with Vinita. 
                
            \end{itemize} 
                {\tiny \bf schedule} \\
                \begin{enumerate} 
                  \tiny \item \tiny 8-9AM: Regular Routines 
                \end{enumerate}
          \end{column}

          \begin{column}{0.15\textwidth}{\small \underline{\bf Sat}}
            {\tiny \bf weather: } {\tiny 11/1 .2r} \\ 
            { \tiny \bf todo} \\ 
            \begin{itemize}
              \tiny \item \tiny Add in schedule
            \item \tiny 
            \end{itemize} 
                {\tiny \bf schedule} \\
                \begin{enumerate} 
                  \tiny \item \tiny 8-9AM: Regular Routines 
                \end{enumerate}
          \end{column}
         
          \begin{column}{0.15\textwidth}{\small \underline{\bf Sun}}
            {\tiny {\bf weather:} } {\tiny 11/2 r} \\ 
            {\tiny {\bf todo}}\\
            \begin{itemize}
              \tiny \item \tiny Add in schedule
            \end{itemize} 
                {\tiny \bf schedule}\\
                \begin{enumerate} 
                  \tiny \item \tiny 8-9AM: Regular Routines 
                \end{enumerate}
          \end{column}
        \end{columns}
      \end{block}
\end{column}
    
    % ------ Page 2: Column 3
    \begin{column}{0.20\linewidth}
      % ------ Block 2.3.1 
      \begin{block}{Food Plan} 
        \begin{itemize}
          \tiny \item \tiny Google Express: DHDQQJQDRFTXDM95B
        \end{itemize}
      \end{block} 
      \begin{block}{Clothes plan} 
        \begin{itemize}
          \tiny \item \tiny Monday: 
        \item \tiny Tuesday
        \item \tiny Wednesday
        \item \tiny Thursday
        \item \tiny Friday
        \item \tiny Saturday
        \end{itemize} 
      \end{block} 
      
      %-- Block 3-3 
      \begin{block}{Situations}
        % Summary: the below are the situations that define one
        % another.
        % Howto: Put post notes of each situation from list of previous
        % week. Put high importance situations in situationslist. 
        % Put list of upcoming situations on Sunday morning with Pre. 
        \begin{itemize}
          \tiny \item \tiny 
        \item \tiny 
        \end{itemize}
      \end{block}
      % contingincies: 
      % Summary:
    \end{column}
\end{columns}
