% Howto: 
\underline{Weekend Plans} 
2-Month Plan: December: code + worklife, January: study for
interviews. 

2-Month Plan: February:  code  

% Howto: 
Week of February $1^{st}$: 
\begin{itemize} 
\tiny \item \tiny 
\item \tiny 
\end{itemize} 

Week of February $8^{th}$: 
\begin{itemize} 
\tiny \item \tiny  
\item \tiny 
\end{itemize} 

Week of February $15^{th}$:
\begin{itemize} 
\tiny \item \tiny 
\item \tiny 
\end{itemize} 

% Howto:  

\underline{\textbf{Sunday Routines}}: Experiences, week plan 
\underline{\bf Routines}: Morning: exercise/brush, floss, shower
(hair, eyes, ears, underarms, feet), meds, belt, comb hair / dishes,
clean kitchen floor. |  Night: running/ put away dishes, clean
kitchen floor brush teeth, charge phone, clothes for tomorrow,
contacts off. 

% Howto: 
\underline{\textbf{AngerAndWorries:}} 

\underline{\textbf{Week lessons:}} 

\underline{\bf{News:}} 
\underline{\bf{Week Plan: }}: Work:comm: experiences, Work:comm: , 
worklife, work:rel: send message to companies, Comm: message to
Manj., Work: message to Prof. Gropp, Work: do coding practice,  Work:
finish Win Friends Influence People. 

\underline{\textbf{Running TODO}} 
\begin{enumerate} 
\tiny \item \tiny Work: prepare notes for Prof Gropp. \pr{} 
\item \tiny Work: 
\tiny \item \tiny Work: rel: send nvidia message. \te{}  
\tiny \item \tiny Work: comm: send note to Blaise.  
\tiny \item \tiny Work: rel: send intel message. 
\end{enumerate} 




And, hope you're having a good week. -Vivek 

\textbf{Project: Comm} 
\begin{itemize} 
\item \tiny 
\item \tiny 
\item \tiny 
\item \tiny 
\end{itemize}  

\underline{\textbf{Project: Interview}}
\begin{itemize} 
\item \tiny 
\item \tiny
\end{itemize} 


Monday 

Tuesday 

Wednesday 

Thursday:  
