%\def\PRES{1}
%\ifx{\PRES}

%\iftoggle{\PRES}
\begin{frame}{Running to do}
%\else 
%\fi 
\begin{enumerate}
  \item \tiny Work(psm:nt): reply for journal.
  

    \tiny \item[] \tiny \textbf{Curr} $\rightarrow$ 
         \item \tiny Work:admin: update resume.
 
    \item \tiny Work: prep for discussion with OpenMP. 
    
	\item \tiny Mgmt:Spaces: get Virginia license and registration \pr{Urgent}.
    \item \tiny Mgmt:Spaces: pay parking ticket from VA \te{1hour} \pr{U}. 
    \item \tiny Mgmt:Spaces: pay parking ticket from VA \te{1hour} \pr{U}.  
\item \tiny Work:rel:(ecp): follow-up from ECP  = Work:rel(ecp:f):
  e-mail to Mary Ann Leung for volunteering + Work:rel:(ecp:f): e-mail
  to Julie + Work:rel(ecp:f): message to Xeushen + Work(ecp:f): linkedIn to Costin.  

\item \tiny Work: create slide for Hormozd.

   \item \tiny Work: finish slide. 
  \item \tiny Work:admin: submit receipts for Bagel.
  \item \tiny Work:admin: ask for vacation.\te{10 minutes} \dl{TuesNight} \pr{high}    
    \item \tiny Work: update slides for OpenMPCon. 
    \item \tiny Work: update website for  \url{bit.ly/udsomp}. 
    \item \tiny Work:admin: fill out questionnaire for Health assessment.
    \item \tiny Mgmt:Spaces: pay Mai T. Phan. 
\seti
\end{enumerate}
  
 % \ifx{\PRES}{1}
\end{frame}
 % \else 
 % \fi
  
 % \ifx{\PRES}{1}
\begin{frame}{Running To Do (2)} 
%  \fi 
  \begin{enumerate}
\conti    
         \item[] \tiny  $\leftarrow$ \textbf{End Curr}
         \item \tiny Mgmt:Spaces: get citi bank account + Mgmt:Spaces: get refund from AA  + Mgmt:Spaces: get the bumper bully 
          \item \tiny Mgmt:Spaces: update software  in car\te{ 1 hour}. 
        \item \tiny  Mgmt:Spaces: consider new wheels 
        \item \tiny EI: Study materials from CBT.  \te{2 hours} \dl{Monday}.
        \item \tiny Work:comm: figure out whether to add Anshu \te{1 hr}.
    \end{enumerate}
    
%\ifx{\PRES}{1}
 \end{frame}
%\fi
