\documentclass[serif, mathserif, final]{beamer}
\mode<presentation>{\usetheme{Lankton}} 
\usepackage[orientation=landscape,size=a0,scale=1.6, debug]{beamerposter}
%\usepackage[orientation=landscape,size=a0,scale=1.4,debug]{beamerposter}
%\usepackage[absolute,overlay]{textpos} % <-- can  use this to position text (solves problem of earlier yesterday with poster placement). 

%\documentclass[serif,mathserif,final]{beamer}
%\mode<poster>{\usetheme{RicePoster}}
\usepackage{amsmath,amsfonts,amssymb,pxfonts,xspace}

\usepackage{graphicx, ragged2e}
\usepackage{pgffor}
\usepackage{ulem}
\usepackage{caption}
\usepackage{courier}

\usepackage{verbatim}

%\usepackage[usenames,dvipsnames]{xcolor}                                                                                                                            
\usepackage{listings}

\usepackage{float}
\usepackage{subfig}
\setbeamertemplate{caption}[numbered] 

%\graphicspath{{./figures/}}                                                                                              
%\usepackage{beamerposter}
%\graphicspath{{./figures/}} 
\newcommand{\bllt}{\item \small}
\newcommand{\doneTaskNoItem}[1]{\sout{#1}}
\newcommand{\doneTask}[1]{\item \sout{#1}}
\newcommand{\doneTaskHyp}[1]{\item \textcolor{blue} {\sout{#1}}}
\newcommand{\optTask}[1]{\item  \textcolor{green}{#1}}
\newcommand{\prioTask}[1]{\item  \textcolor{red}{#1}}
\newcommand{\timeEst}[1]{\textit{Time:} \textit{#1}}
\newcommand{\priority}[1]{\textit{Priority:} \textit{#1}}
\newcommand{\prio}[1]{\textit{Priority:} \textit{#1}}
\newcommand{\dueBy}[1]{\textit{Deadline:} \textit{#1}}
\newcommand{\MyName}{Vivek~Kale}
\newcommand{\fixme}[1]{\textcolor{blue}{[FIXME: #1]}}
\newcommand{\revision}[1]{\textcolor{blue}{[FIXME comment : #1]}}
\newcommand{\regItem}[1]{\item \textcolor{cyan}{#1}}
\newcommand{\regRoutineItem}[1]{\item \textcolor{green}{\textit{Reg. Routine:} #1}}
\newcommand{\situationItem}[1]{\item \textcolor{magenta}{\textit{Situation:} #1}}
\newcommand{\deadline}[1]{#1}
\newcommand{\comments}[1]{}

%\graphicspath{{./figures/}}
%\usepackage[orientation=landscape,size=a0,scale=1.6,debug]{beamerposter}

%-- Header and footer information ----------------------------------
\newcommand{\footleft}{Mgmt-WorkLife-weekPlan} % figure what this should be 
\newcommand{\footright}{October 2014}

%------------------------------------------------------------------
%-- Main Document ------------------------------------------------- 
\title{Month-Week-Day Plan} 
\author{Vivek Kale$^1$}
\institute{$^1$ University of Illinois at Urbana-Champaign}  
\date{\today}

% TODO: make the below document neater 
% TODO: consider stretching center column 
% TODO: check how to fit week daily plan together .  
\begin{document} 
\begin{frame}{} 
  \begin{columns}
%-- Column 1 ---------------------------------------------------  
\begin{column}{0.25\linewidth} %{\textbf{\underline{Week Aspects(new name)}}}
  %-- Block 1-1
\begin{block} {Happiness Generation - must maintain every day}
\begin{itemize}
  \tiny \item \tiny happy that I have Atul to show me . 
\item \tiny Happy that I have normal life up to this point . 
\end{itemize} 
\end{block} 
  \begin{block}{ Stresses} 
    % Recognize emotions / recognize what you're worried about -> eliminate worry
    \begin{itemize}
     % \tiny \item \tiny EuroMPI paper: 
     % \small \item \tiny Ridhima saying stuff about me. 
    %\item \tiny related work:   
      % \item \tiny Atul saying let's talk about this some other time. 
      % \item \small friends of Atul's better(?): 
      % \item \small email -done : 
      % \item \small anger that you are below parents 
      % \item \small [ find others ]
    %\item \tiny others at work. 
    %\item \tiny Comm: Talking to Amit - can bounce back, just close
    %  friends.
      %\item \tiny Comm: restricted profile - take it for face
      % value, probably because I'd get angry. 
%    \tiny \item \tiny Comm: Frustration about Sneha - you still are you.
  %\item \tiny Comm: thinking about how Sat. went /general worries:
   %   don't worry and be conscious. 
  %  \item \tiny Comm: putting extra fb update - just did it for fun
  %    and whatever, if anything just local anxiety. 
%    \item \tiny Comm: brother getting upset about laptop: 
 %   \item \tiny Comm: fb message to everyone: will go with time, was stressed about something, said Kaw later
%    \item \tiny Comm: angry about weekend: she was too shy anyways. 

    \item \tiny Comm: remembering ab : it didn't work out for a reason - 
%    \item \tiny Comm: Worrying about Sadhna's sis: Pre-: Post-: 
    \item \tiny Comm: Worrying about not losing it (check this/ define this better) : work on sheet.  

    \item \tiny Worrying about thesis finish. Be sincere and work, we make mistakes with time. 
    \item \tiny Worrying about whether we should have done something earlier. Don't look at past. 

    \item \tiny Worrying about deep: forget her, because there's much more to be done.  She may not be interested because it's a brother. 
    \end{itemize} 
  \end{block} 
  %-- Block 1-2 

  %-- Block 1-3
  \begin{block}{ Habits } 
    \begin{itemize} 
      %\tiny \item \tiny move feet less, don't scrub on floor. 
      \item \tiny Reduce things. 
      \tiny \item \tiny back straight. 
    \item \tiny lips relaxed. 
    \item \tiny watch what happens when a hot girl talks to you. 
    \end{itemize} 
  \end{block} 

  %-- Block 1-4
  \begin{block}{Clothes plan} 
    \begin{itemize} 
      \tiny \item \tiny Saturday: wear polo shirt. 
    \item \tiny Saturday night: wear light blue dress shirt and jeans. (or maybe khakis and polo shirt). 
    \item \tiny Sunday: business casual shirt. 
    \item \tiny Wednesday : 
    \item \tiny Thursday: 
    \item \tiny Friday : 
    \item \tiny Saturday : Blue full shirt . 
    \item \tiny Sunday : Red shirt .
    \end{itemize} 
  \end{block} 
  %-- Block 1-5
  \begin{block}{ Food plan } 
    \begin{itemize} 
      \tiny \item \tiny Skip meals this week to take out fat from weekend. 
    \item \tiny Be very careful about food for Saturday night, along with Brunch for Sunday and dinner for Sunday. 
    \end{itemize} 
  \end{block} 
  
  \begin{block}{ Situations} 
    \begin{itemize} 

\item \tiny \textit{Meet with Prof. Gropp:}  Pre-:  Post-: 

\item \tiny \textit{Meet with friends} Pre-: Clothes, new fb pic.  Post-: 

\item \tiny \textit{FB picture update} : Pre-:  Post-: 

\item \tiny \textit{Engagement Party} Pre-: clothes: black pant, belt, red tie, beige shirt, stay quiet, practice talking for short amounts of time like an adult,  Post-: be less drunk, have a plan. 

\item \tiny \textit{Meet with Prof Gropp: } Pre- : Have results ready, make plan to discuss thesis, Post-: plan out time before meeting, so there is time to plan. 

\item \tiny \textit{Meet with Prof Garzaran: Friday 2pm} Pre-: get notes/slides sent, discuss basics and focus on questions she should answer for you (rather than just showing). 
\item \tiny \texttt{fb post} : Pre-: Another reason to have a fourth branch of government, where real people with real problems spontaneously scream and shout when Congressmen start arguing
about nonsense.

    \end{itemize}
  \end{block} 

  
  \begin{block} {Life notes} 
    \begin{itemize} 
      \tiny \item \tiny Level 0+1: focus on finding Happiness. 
    \item \tiny Level 2: 
    \item \tiny Level 4.1: Writing: prefer standard to offbeat 
    \item \tiny Level 4.2: Body Language: lips relaxed
    \item \tiny Level 4.3: Vocal Variety: shout. 
    \item \tiny TM: work on speech for submission to blog, increasing intentionality. 
    \item \tiny Mgmt/habits: finish chapter 1 reading notes and habits. 
    \end{itemize} 
    
  \end{block} 
\end{column} %2 
%-- Column 2 --------------------------------------------- 
\begin{column}{0.50\linewidth}
%{\textbf{\underline{Week TODO}}} 
% NOTE: Current policy is to comment out days as they come. 
  % TODO: put in the regular routines here for each day, in the schedule box. 
  %--- Block 2-1
  
  \begin{block}{Week TODO} 
    \begin{enumerate} 
    \item \tiny Work: finish research questions and write defense. \timeEst{2 hours}.  

    \item \tiny Work: do snap results weak scaling on BW. \timeEst{2 hours}. 

    \item \tiny Work: do nbody BG/Q results + Work: do
      timings. \timeEst{6 hours}. 

    \item \tiny Work: add weighted locality-sensitive scheduling to
      each of the 18 graphs + 9 graphs + Work: focus on explaining
      reasoning for weighted locality-sensitive scheduling in n-body. 
      \timeEst{30 mins}. 

    \item \tiny Work: show differences between fine-grained,
      coarse-grained, etc. 

    \item \tiny Work: finish the results for tradeoffs between load
      imbalance and locality \timeEst{20 mins}. Need this for each of
      the strategies, for each app. Then, need this for each arch.
      (Discuss PAPI results). 

    \item \tiny Work: finish results on weak scaling for cab on SNAP on cab. \timeEst{20 mins}.

    \item \tiny Work: get implementation done for weak scaling for 
      SNAP on BG/Q. \priority{UrgentAndImportant} \timeEst{1 hour}.       

    \item \tiny Work: add results for NAS for different problem sizes
      on BG/Q  \timeEst{30 mins } \priority{ImportantButOkToPushOffNextWeek}.

    \item \tiny Work: add results for NAS for different problem sizes
      on cab. \timeEst{30 mins } \priority{ImportantButOkToPushOffNextWeek} 

    \item \tiny Work: get implementation done for
      n-body on BG/Q. \priority{UrgentAndImportant} \timeEst{1 hour}.       

    \item \tiny Work: finish results for weak scaling for SNAP on
      BG/Q. \timeEst{1 hour}. \priority{UrgentAndImportant}. 

    \item \tiny Work: finish results for miniFE on BG/Q. 
    \item \tiny Work: finish results for miniFE on BW.         
    \item \tiny Work: get histograms for 20 runs. 

    \item \tiny Work: organize thesis. \timeEst{30 mins}.   
    \item \tiny Work: schedule defense write-up. 

    \item \tiny Work: fix timings on all results + graphs. \timeEst{10 mins}. 
    \item \tiny Work: get excel spreadsheet set up. \timeEst{20 mins} \priority{ImportantToSpeedupOtherParts}. 

    \item \tiny Work: make diagrams, and do properly. \timeEst{2 hours}.  
    \item \tiny Work: finish coding + org of results scripts.
      \tiny \item \tiny Work: submit runs / get distribution \timeEst{4-5 hours}
    \item \tiny Mgmt: Money: do re-imbursements \timeEst{30 mins} \priority{30 mins}. 
    \item \tiny Mgmt: Spaces: get screen replaced. \priority{UI} \timeEst{30 mins}. 
    \item \tiny Mgmt: Spaces: return Honda taillight . \timeEst{10 mins} \priority{U}. 
    \item \tiny Comm: send message to dp+sh+rd   + dp \timeEst{30 mins} \priority{U}. 
    \item \tiny Work: check for sending paper to cloud computing
      conference/workshop. +  Work: (planning): look up conference for
      slack-conscious  - could do this later afterwards. 
    \item \tiny Mgmt: Spaces: Graduation: send messages on Post-doc to
      Prof. Gropp about Princeton / other places + check graduation info 
\end{enumerate}
\end{block} 

%\begin{columns}
%\begin{column}{0.5\columnwidth} 

\begin{block}{Week Daily Schedule} 
\textbf{\small \underline{Mon}}
\begin{enumerate} 
\tiny \item \tiny -
\end{enumerate} 

\textbf{\small \underline{Tue}}
\begin{enumerate}
\tiny \item \tiny Comm: Finish speech, integrate points into it + Comm: add in todos  \timeEst{20 mins} \priority{UI}. 
\item \tiny Work: finish graph for SNAP. 
\end{enumerate} 

\textbf{\small {\underline{Wed}}}
\begin{enumerate} 
\tiny \item \tiny  
\item \tiny Work: Finish abstract. 
\item \tiny Work: .
\end{enumerate} 

\textbf{\small{\underline{Thu}}}
\begin{enumerate} 
\item \tiny Work: send chapter 1 to Prof Gropp.  
\item \tiny Comm: send message to Ashwini.
\item \tiny worklife: update situations.
\item \tiny Poster submission. 

\begin{itemize} 
\tiny \item \tiny Work: put together graph on static execution time and dynamic execution. 
\item \tiny Work: put together graph on overheads with increasing threads,  dynamic - static. 
\end{itemize} 

\begin{itemize} 
\item \tiny Work: put together graph on static execution time and dynamic execution. 
\item \tiny Work: put together graph on overheads with increasing threads,  dynamic - static. 
\item \tiny Work: put together a graph on dynamic - static - dynamic.  
\item \tiny Work: get graphs on load imbalance. 
\item \tiny Work: send message about the overheads.
\end{itemize} 
\item \tiny Comm: TM body language.
\item \tiny Mgmt: spaces: get travel for SC. 
\item \tiny Comm: send message to Renuka.
\end{enumerate}
%\end{column} 
%\begin{column}{0.5\columnwidth} 

\textbf{\small {\underline{Fri}}} 
\begin{enumerate} 
\tiny \item \tiny Work: do results for baseline to support the argument. NAS static, dynamic, guided - cache misses.  \timeEst{1 hour}. 
\item \tiny Work: finish problem statements, send to Prof Gropp \timeEst{20 mins}. 
\item \tiny Work: add in result for BG/Q on n-body \timeEst{30 mins}. 
\item \tiny Work: add in result for SNAP on BW  weak scaling. \timeEst{1 hour}. 
\begin{itemize} 
\item \tiny Work: get static timing for SNAP on BW weak scaling \timeEst{20 mins}.
\item \tiny Work: get dynamic and guided timing for SNAP on BW weak scaling \timeEst{5 mins}.
\item \tiny Work: get uSched timing for SNAP on BW weak scaling \timeEst{10 mins}. 
\item \tiny Work: get \texttt{callsite\_fd} timing for SNAP on BW weak scaling \timeEst{5 mins}. 
\item \tiny Work: get \texttt{vSched} timing for SNAP on BW weak scaling \timeEst{10 mins}. 
\end{itemize} 

\item \tiny Work: get static timing for BG/Q for nbody. 
\item \tiny Work: add in result for nbody weighted locality-sensitive scheduling \timeEst{45 mins}.
\item \tiny Work: get schedule for Prof Gropp \timeEst{10 mins}. 
\item \tiny Comm: let Atul know timing. 
\end{enumerate}

\textbf{\small \underline{Sat}} 
\begin{enumerate} 
\tiny \item \tiny Work: get results done \priority{UI} \timeEst{2 hours} 
\tiny \item \tiny Work: get the writing done. 
\item \tiny Comm: get speech done \priority{UrgentAndJustUpload} \timeEst{2 hour}
\item \tiny Mgmt: Spaces: clean up iPhone and install latest software update 
\item \tiny Work:
\item \tiny Comm: 
\end{enumerate} 

\textbf{\small \underline{Sun}}
\begin{enumerate} 
\tiny \item \tiny Work: finish thesis research questions to add 
problem statement. \timeEst{20 mins} + Work: finish research questions connect with 
techniques.  \timeEst{30 mins}  +  Work: add in graphs labels + Work: add in explanations 
for results. 

\item \tiny Work: add graphs.
\item \tiny Work: send Bronis message about thesis. 
\item \tiny Comm: respond to Ashwini. 
\item \tiny Mgmt:Spaces: re-imbursements. 
\item \tiny Mgmt: Spaces: finish re-imbursements. 

\end{enumerate} 

\end{block} 
\end{column}%2 

\begin{column}{0.20\linewidth} 
%Block 3-1
\begin{block}{\small \textbf{\underline{Regular Routines}} }
\underline{\textbf{Morning}}
\begin{itemize}
\tiny \item \tiny Brush Teeth \timeEst{4 mins}
\item \tiny Mouthwash, Clean tongue - it helps with breath\timeEst{1mins} 
\item \tiny Eating small breakfast
\item \tiny Check your schedule for meetings / appointments for that day: Is anything urgent? \timeEst{5 mins}
\item \tiny Excercise: 1 hour ( Stretch for 10 mins, Treadmill for 30 mins , Lift weights or Yoga 1 hour, Meditation for 10 mins)
\item \tiny Shave (at least every other day) \timeEst{5 mins}
\item \tiny Shower : (shampoo+conditioner, acne wash,  soap on underarms/underbody)
\timeEst{10 mins}
\item \tiny dry hair, dry face, arms, legs, back, stomach \timeEst{3 mins}
\item \tiny Clothing: belt, check collar, shirt not half-tucked, matching socks \timeEst{5 mins}
\item \tiny Comb hair, hair gel optional \timeEst{ 1 min}
\item \tiny Check Keys/Wallet/Cell/Badge (get a bucket) \timeEst{1 min}
\item \tiny Open meds cabinet, get water, take medicines \timeEst{1 min}
\item \tiny Wear lenses and rinse out case \timeEst{ 2 mins}
\item \tiny Deodorant or cologne depending on the day \timeEst{1 min}
\item \tiny Wash your face with a face wash - it helps with acne \timeEst{3 mins}
\item \tiny Moisturize - apply lotion \timeEst{ 2 min}
\item \tiny Neti pot / clean out sinuses - if you’re feeling congested \timeEst{5 min}
\item \tiny clean out ears, nose \timeEst{5 mins}
\item \tiny Remember to lock door \timeEst{1 mins}
\end{itemize}

\underline{\textbf{Evening}}

\begin{itemize}
\tiny \item \tiny Call family: 30 mins
\item \tiny meet friends: 20 mins
\item \tiny Cleaning dishes / cleaning house: 10 mins
\item \tiny Lay out clothes for the next day, iron if necessary
\item \tiny start laundry if needed: 10 mins,
\item \tiny Collect anything you’ll need for the next day (e.g. dry cleaning to drop off): 5 mins,
\item \tiny Check Facebook/linkedin/google+: 10 mins, matrimony stuff: 10 mins,
\item \tiny Food for lunch/dinner the next day: 10 mins
\end{itemize}

\underline{\textbf{Night before bed}}
%TODO: why isn't enumerate working???
%\begin{enumerate}
\begin{itemize}
\tiny \item \tiny Finish computer stuff \timeEst{5 mins}
\item \tiny Get into sleeping clothes \timeEst{1 mins}
\item \tiny Before sleeping: brush teeth, floss \timeEst{ 2 min}
\item \tiny Properly wash and put away contacts \timeEst{ 2 mins}
\item \tiny Review the days good things \timeEst{ 10 min}
\item \tiny Light Reading \timeEst{ 10 min}
\item \tiny Prayer \timeEst{10 mins}
%\end{enumerate} 
\end{itemize}
\end{block}

\end{column}%3 

\end{columns} 

\end{frame} 

\end{document}
