\documentclass[serif, mathserif, final]{beamer}
\mode<presentation>{\usetheme{Lankton}}
\usepackage[orientation=landscape,size=a0,scale=1.6, debug]{beamerposter}
\usepackage{amsmath,amsfonts,amssymb,pxfonts,xspace}
\usepackage{graphicx,ragged2e,pgffor}
\usepackage{hyperref}
\usepackage{ulem}
\usepackage{courier}
\usepackage{caption,verbatim,listings,float,subfig} %TODO: order these 
\setbeamertemplate{caption}[numbered] 
\usepackage{calendar}
\usepackage{geometry}

%TODO: remove unneeded items 
\newcommand{\bllt}{\item \small}
\newcommand{\doneTaskNoItem}[1]{\sout{#1}}
\newcommand{\doneTask}[1]{\tiny \item \tiny \sout{#1}}
\newcommand{\doneTaskHyp}[1]{\tiny \item \tiny \textcolor{blue} {\sout{#1}}}
\newcommand{\optTask}[1]{\tiny \item \tiny \textcolor{green}{#1}}
\newcommand{\prioTask}[1]{\tiny \item \tiny \textcolor{red}{#1}}

\newcommand{\timeEst}[1]{\textit{TimeEst:}\textit{#1}}
\newcommand{\te}[1]{\textit{TimeEst:}\textit{#1}}
\newcommand{\deadline}[1]{\textit{Deadline:}\textit{#1}}
\newcommand{\dueBy}[1]{\textit{Deadline:}\textit{#1}}
\newcommand{\dl}[1]{\textit{Deadline:}\textit{#1}}
\newcommand{\priority}[1]{\textit{Priority:}\textit{#1}}
\newcommand{\prio}[1]{\textit{Priority:}\textit{#1}}
\newcommand{\pr}[1]{\textit{Priority:}\textit{#1}}

\newcommand{\MyName}{Vivek~Kale}
\newcommand{\fixme}[1]{\textcolor{blue}{[FIXME: #1]}}
\newcommand{\revision}[1]{\textcolor{blue}{[FIXME comment : #1]}}
\newcommand{\regItem}[1]{\item \textcolor{cyan}{#1}}
\newcommand{\regRoutineItem}[1]{\item \textcolor{green}{\textit{Reg. Routine:} #1}}
\newcommand{\situationItem}[1]{\item \textcolor{magenta}{\textit{Situation:} #1}}

\newcommand{\comments}[1]{}

%TODO: consider changing the below so you only use the text in the
%document 


%TODO: change Week plans 

\newcommand{\footleft}{Mgmt-WorkLife-weekPlan} % figure what this should be 
\newcommand{\footright}{July 2016}
%-- Main Document ------------------------------------------------- 
\title{Month-Week-Day Plan}\author{Vivek Kale$^1$}\institute{$^1$ 
University of Illinois at Urbana-Champaign}\date{\today}

\begin{document}
\begin{frame}


\begin{columns}
\column{1.0\linewidth}

\begin{block}{Projects}

Work:code: Project - Research Paper:
\begin{enumerate} 
\item \tiny \url{http://mpp2016.ime.uerj.br} 
\item \tiny \url {http://sbac-pad}  - registration is  \$ 500 . 

\item \tiny Put up latex.  
\item \tiny Gather all research. 
\item \tiny Gather project work. 
\item \tiny Write down introduction.     
\item \tiny Gather data for OpenACC. 
\item \tiny Explain other details of setup.
\item \tiny Note data for OpenMP.  
\end{enumerate} 

\textit{Schedule:} March 24th: do latex, March 25th, March 26th
Work:code: - Project - Coding practice: p for interview. 
\begin{enumerate} 
\tiny \item \tiny Work:code(cp.bm): finish bit manip:  
\item \tiny Work:code(cp.bm): finish bit manip:  finish problem 5 from book 
\item \tiny Work:code(cp.bm): finish bit manip:  finish problem 6 from book 
\item \tiny Work:code(cp.bm): finish bit manip:  finish problem 7 from book
\item \tiny Work:code(cp.bm): finish bit manip:  finish problem 8 from book  
\item \tiny Work:code(cp.bm): finish bit manip:  finish problem 9 from book 
\item \tiny Work:code(cp.bm): finish bit manip:  finish problem on
\item \tiny Work:code(cp.bt): review brainteasers – 1 day. 
\item \tiny Work:code(cp.bmpie): do graphics problem from bit manip:
  rectangular overlap. 
\item \tiny Work:code(cp.bmpie): do big endian vs. little endian := 
\item \tiny Work:code(cp.bmpie): number of ones  := 
\item \tiny Work:code(cp.bmpie): code up bit manip problems :=  
\item \tiny Work:code(cp.bt): finish brain teasers:  finish problem on
  egg drop from book.  
\item\tiny Work: code(cp.bt): talk about and write 100 lockers . 
\item \tiny Work: code(cp.bt):  finish brain teasers: finish problem on heavy
pill . 
\item \tiny Work:code(cp.btpie): finish brain teaser problems from programming
interviews exposed. 
\item \tiny Work:code (cp.): go through C++, Work:code (cp.): go through Java +
Work:code (cp.): go through OOP. 
\item \tiny Work:code (cp.): code up problems.  – 1 week. 
\item \tiny Work:code (cp.): integer problems + numerics   -- 1 week. 
\item \tiny Work:code (cp.): practice mock interview problems. – 1 week.   
\item \tiny Work:code (cp.): finish recursion + BFS/DFS – 1 week. 
Work:code(cp.): finish recursion, Work:code(cp. ): code up problems,
Work(cp.): practice mock interview problems. 
\item \tiny Work: comm: Project –general,  Work:comm: talk to Stephen. 
\end{enumerate} 
\textit{Schedule:} Work:code (cp.): finish bit manipulation, Work(cp.): review
brain teasers in book, Work(cp.): Work(cp.): go through C++.  \\ 

\begin{enumerate} 
\tiny \item \tiny Figure out write-up for Fulbright.
\item \tiny Attend Fulbright : 
\end{enumerate} 
\textit{Schedule:} April 15th: message to Stephen – 1 hour, Work:rel:
Project – Awards:,  Work:rel: Project – interview with
Berkeley/MIT/industry: 

\begin{enumerate}
\tiny \item \tiny cover letter:
\tiny \item \tiny CV: + Research Summary:  -- 1 week.  
\item \tiny Business cards:  - use latex  -- 40 minutes. 
\item \tiny Behavioral questions answers:    -- 1 week. 
\item \tiny Send emails – 1 day. 
\item \tiny Structure in latex. 
\end{enumerate}

\textit{Schedule:} Behavioral answers – 1 week, CV prep - 1 day, business cards.

Worklife: - Project: – Comm:rel: 



\begin{enumerate} 
\tiny \item \tiny Worklife: link management together. 
\item \tiny  Worklife: link habits comm and Toastmasters.
\item \tiny Worklife: latex viewpoint. 
\item \tiny Comm: read social intelligence first four chapters.
\item \tiny  Comm: link all comm together.
\item \tiny Worklife: get emails and texts to analyze. 
\item \tiny  Worklife: figure out how to book flights and trips quickly. 
\end{enumerate}
\textit{Schedule:}  Comm: read social intelligence first four chapters and get a
method to take in information – 5 hours, 

Comm: link comm together, worklife: latex viewpoint.

Weekend Plans: 

Looking ahead: 

GenKnowledge: 
House of cards: 

Mgmt:Spaces: 
1.Cars. 

Work:rel: -  Project – Comm: rel: 
4. Comm:rel: meet others:  Sweta K. 
{\it Schedule:} meet others over summer, meet girl over summer. 

Friends: Amit, Sangita, Anchit, Kevin, 

\end{block}

\end{columns}
\end{frame}  




\begin{frame}
  \begin{columns}
    %-- Page 2: Column 1 --------------------------------------------------- 
    \begin{column}{0.25\linewidth} %{\textbf{\underline{Week Aspects(new name)}}}
      %TODO: check where this should go. -done
      %--- Page 2: Block 1-1
     
      \begin{block}{Routines} 
        \textbf{\underline{Sunday Routines:}} Experiences, week plan. \\ 
        \textbf{\underline{Routines:}} Morning: bfast, exercise/brush, floss, shower (hair, eyes,
        ears, underarms, feet), meds, belt, comb hair / dishes, clean kitchen
        floor. |  Night: running/ put away dishes, clean kitchen floor / brush
        teeth, charge phone, clothes for tomorrow, contacts off. \\
        
        Cover letter: 
        
        Resume: 
        
        Reference Letters:  

      \end{block} 
    

      %--- Page 2: Block 1-2
\begin{block}{Map} 

        VIN:  License plate: ill e61 2444   other cars: lexus:  VIN:  license:
        Hyundai: 
        Audi: VIN:  License: P84 
        Day trip packing list: charger for iPhone, charger for laptop, car
        keys, underwear, black socks, shoes, meds, halls meds, greyhound,
        boarding pass, flight pass. 
        
        Atul’s FightingIllini  wifi pass:  2173900374 WPA  \\
        Amtrak  eVoucher numbers. \\
        Southwest credit:
        BT code for BMW:
        
        When tank light on, filling 13.3 gallons.



Local space: 

Local map: 

\textbf{\underline{Urbana-Champaign:}}


Campustown: 
  North: Engineering: 
  Main campus: 
  Southside of campus: 
Urbana: 
Champaign: 
Savoy: 
\textbf{CMI} 
\textbf{Illini Terminal} 
Decatur/Springfield: 
Tuscola/Mattoon: 
Rantoul/Paxton: 
\end{block}
  
      %--- Page 2: Block 1-3
      \begin{block}{Local Happiness}
        % howto:Recognize emotions / recognize (precisely) what you're
        % worried about -> methods for eliminating worry. 
        % clean out old worries, put them in pastWorries doc.  
        % remember to define precisely 
        % order from top-to bottom
        \begin{itemize}
          \tiny \item \tiny Work: worrying about interviewing: just focus on the work. 
        \item \tiny Worrying about gal: think about talking to others. 
        \end{itemize}
      \end{block}

      %--- Page 2: Block 1-4
      \begin{block}{Stresses}
        % howto:Recognize emotions / recognize (precisely) what you're worried about -> methods for eliminating worry. 
        % clean out old worries, put them in pastWorries doc.  
        % remember to define precisely 
        % order from top-to bottom
        \begin{itemize}
          \tiny \item \tiny Work: worrying about interviewing: just focus on the work. 
        \item \tiny Worrying abt Dp thinking you are stupid -->  think
            about Todd saying you're smart, you don't apply yourself; 
            think about Atul saying they aren't doing that
            intentionally. 
          \item \tiny Anger about a b  -> ...
          \item \tiny Anger about UP -> think about the positive
            perspective, and the original
        \end{itemize}
      \end{block}    
      %-- Block 1-5
      \begin{block}{Life notes}
        \begin{itemize}
        \item \tiny 
        \item \tiny 
        \end{itemize}
      \end{block} 
% howto: 

\end{column} 


%-- Column 2 --------------------------------------------- 


\begin{column}{0.5\linewidth}

      \begin{block}{Week Summary}
        {\tiny \textbf{Week Plan:}   }
        {\tiny \textbf{Weekend Plan:}  }   
      \end{block}

      \begin{block}{Running TODO} % find a better name 
        \begin{enumerate} 

        \item \tiny \doneTask{Work:comm:rel: message to Barbara Chapman +
          Work:comm: message to BNL +  Work:comm: cover letter for BNL job. \te{1 hour}
          \dl{July 12th} \pr{UI} + Work:comm: email for BNL job \te{1hour} \dl{July 11th}
          \pr{IU}. }

        \item \tiny \doneTask{Mgmt:Spaces: cancel CLEAR membership. }

        \item \tiny \doneTask{Mgmt:webpresence: respond to Ayo's
          LinkedIn request.} 

        \item \tiny \doneTask{Comm: respond to Labonee.}

\textbf{Curr} $\rightarrow$
          
        \item \tiny Work(cp): coding problem := Work(cp): coding problem on
          bits and arrays and hash table. 
        \item \tiny Work(cp): MIT lecture := Work(cp): MIT lecture on
          hashing Karp-Rabin \te{1.5 hours} \dl{before Wed}
          \pr{reasonable}. 

        \item \tiny Work(res): write journal paper. 
        \item \tiny Work(pappub): look up conference papers - SBAC pad in Los
          Angeles \te{1 hour}. 

        \item \tiny Work(pappub): look up papers and understand
          architectures/trends, applications. 

        \item \tiny worklife: read 7 habits summary. 
        \item \tiny Worklife: plan out 7 habits + social
          intelligence. 

        \item \tiny Work:rel: watch Fulbright scholar video
          =: Work:rel(fulb): watch video + Work: rel(fulb): figure out whether there are fellowships
          that do not require postdocs 

          conclusion: do this next year because we will still be
          eligible and it is possible as an early career. (Con: may
          not be eligible ) 

        \item \tiny Mgmt:webpresence: take video. 

        \item \tiny Mgmt:webpresence: delete Anil Taneja from
          LinkedIn.

        \item \tiny Work: Create CV from Resume 


        \item \tiny Comm: send message about a 10-year re-union. 
        \item \tiny Comm: send matrimony requests. \te{1 hour}
          \dl{Sunday afternoon}

        \item \tiny Comm: consider a view of girl on Shaadi. 
        \item \tiny Comm: consider what to do about Bhavna. 

        \item \tiny Comm: consider talking to Illina. 
        \item \tiny Comm: talk to friends from school. 


        \item \tiny Mgmt:webpresence: cancel FB friend request of
          Jocelyn.  
        \item \tiny Mgmt:webpresence: FB like Amaeya's post for
          Bhangra. 
        \item \tiny Mgmt:Spaces(GetThingsSpring2016): get Things =
          Mgmt:Spaces(getThings): get suit. 
        \end{enumerate}
      \end{block}

      \begin{block}{Week Daily Schedule} 
        % howto: arrange items from running todo into the below
        % sheet management document. 
        \begin{columns} 
          \column{0.14\textwidth}{\textbf{\small \underline{Mon}}}
          \textbf{\small todo} \\ 
          \begin{itemize}
            \tiny \item \tiny Add in schedule
          \item \tiny 
          \end{itemize} 
          \textbf{\small schedule} \\
          \begin{enumerate} 
            \tiny \item \tiny 8-9AM: Regular Routines 
          \end{enumerate} 
          
          \column{0.14\textwidth}{\textbf{\small \underline{Tue}}}
          \textbf{\small todo} \\
          \begin{itemize}
            \tiny \item \tiny Work: make project sheet \te{10 minutes} 
          \item \tiny Mgmt:Spaces: check for diploma \te{10 minutes} 
          \end{itemize}  
          \textbf{\small schedule} 
          \begin{enumerate}
            \tiny \item \tiny 10AM - 11AM = 
          \item \tiny 11AM - 12AM = make long-term goals 
          \item \tiny 12PM - 2PM = 
            \tiny \item \tiny 2PM -3PM = 
          \item \tiny 6PM - 10PM = 
          \end{enumerate} 
          
          \column{0.14\textwidth}{\textbf{\small {\underline{Wed}}}}
          \textbf{\small todo} \\
          \begin{itemize}
           \tiny \item \tiny Work: finish slides for tomorrow. 
           \item \tiny Mgmt: Spaces: update fb 
         \item \tiny Comm: fb update 
          \end{itemize}
          \textbf{\small schedule} \\
          \begin{enumerate}
            \tiny \item \tiny 8-9AM: Regular Routines 
          \item \tiny 9AM - 10AM: Send message 
            \item \tiny 6:30PM - 7:30PM = 
          \end{enumerate} 
          \column{0.14\textwidth}{\textbf{\small{\underline{Thu}}}}
          \textbf{\small todo}\\
          \begin{itemize}  
            \tiny \item \tiny 
          \item \tiny 
          \end{itemize} 

          \textbf{\small schedule}\\
          \begin{enumerate} 
            \tiny \item \tiny 8-9AM = Regular Routines 
            \item \tiny 12-1PM = gather notes about job org. during
              session 
            \item \tiny 3:30PM - 4:30PM = meeting 
            \item \tiny 6PM - 9PM = revise emot. int. chapter and
              structure wl-cheat based on it 
          \end{enumerate}  
          
          \column{0.14\textwidth}{\textbf{\small{\underline{Fri}}}}
          \textbf{\small todo}\\ 
          \begin{itemize}
          \item \tiny Work: code review. 
          \item \tiny Work: finish work. 
          \item \tiny Mgmt:Spaces: Haircut \te{10 minutes}. 
          \item \tiny Comm: check messages 
          \end{itemize}
          \textbf{\small schedule}\\
          \begin{enumerate}
            \tiny \item \tiny 8-9AM: Regular Routines 
          \end{enumerate}
          
          \column{0.14\textwidth}{\textbf{\small \underline{Sat}}}
          \textbf{\small todo}\\
          \begin{itemize} 
            \tiny \item \tiny
          \end{itemize}
          \textbf{\small schedule}\\ 
          \begin{enumerate}
            \tiny \item \tiny 7-7:30PM = food + organize.  
            \tiny \item \tiny 7:30 PM - 8 PM = 
            \tiny \item \tiny 8 PM - 9 PM = 
            \tiny \item \tiny 9:45 PM - 10:30 PM = go out 
            \tiny \item \tiny 2AM -3AM =  message Samir + add people
          \end{enumerate}
         

          \column{0.14\textwidth}{\textbf{\small \underline{Sun}}}
          \textbf{\small todo}\\
          \begin{itemize} 
           \tiny \item \tiny 
          \end{itemize}

          \textbf{\small schedule}\\
          \begin{enumerate} 
            \tiny \item \tiny 3PM - 4PM =  . 
          \item \tiny 5-7PM = Comm work. 
          \item \tiny 8PM - 10PM = worklife work. 
          \end{enumerate} 
        \end{columns}
      \end{block}
    \end{column}%2



% ------ Page 2: Column 3
\begin{column}{0.25\linewidth}

% ------ Block 2.3.1

      \begin{block}{Weather}
        \begin{itemize}
          \tiny \item \tiny Rain early in the week,Pollen, 60s.
          \tiny \item \tiny Heavy rain on Wednesday 
        \end{itemize}
      \end{block}

      \begin{block}{Clothes plan} 
        \begin{itemize}
          \tiny \item \tiny Monday
        \item \tiny Tuesday
        \item \tiny Wednesday
        \item \tiny Thursday
        \item \tiny Friday
        \end{itemize} 
      \end{block}
      %-- Block 3-2 

      %-- Block 3-3 
      \begin{block}{Situations}
        % Summary: the below are the situations that define one
        % another.        
        % Howto: Put post notes of each situation from list of previous
        % week. Put high importance situations in situationslist. 
        % Put list of upcoming situations on Sunday morning with Pre. 
        \begin{itemize}
        \tiny \item \tiny \textit{meet with girl in SF} Pre-: avoid talking much.
      \item \tiny \textit{Meet Atul} Pre-:  don't talk too much    /  Post-: 
        \end{itemize} 
      \end{block} 
%Summary:  

\begin{block}{Spaces}
\begin{itemize} 
\tiny \item \tiny 
\item \tiny 
\item \tiny 
\end{itemize} 
\end{block} 

\begin{block}{Rel}

  \begin{itemize} 
    \small \item \small  from SF. 
    \item \small Shwetha K 
    \item \small Mamta       
    \item \small SH11680694 from San Francisco. 
    \item \small Sandhya N. 22 Jun 2016 
    \item \small Aarti S - 27 - 5' 9'' Charlotte.       
    \item \small Anu M from Chicago, IL 
    \item \small Pranati A from Cleveland, OH - 
    \item \small Meghana K from New York - 
    \item \small Ssd S - 28 , 5 5 , Boston, MA 
    \item \small Anj B. - 30 yrs - SH13882555.
  \end{itemize} 
    %\small \item \small Meghan Joshi 

% Accept our apologies for the delayed response. We spoke to our son
% about your daughter and we are interested also. When is a good time for us to
% call you? 


\begin{itemize}
    \item \small
      \url{http://profile.marathimatrimony.com/profiledetail/viewprofile.php?id=K658342&osa=dbos&memval=3&listtype=1&msgId=&rq=&loadPage=12&listtype=1&tabtype=16&filtertype=1&filtered=0&viewed=2&TotCnt=367&Show=Y&Module=}

\item \small \url{http://profile.marathimatrimony.com/profiledetail/viewprofile.php?id=M3730924&osa=dbos&memval=1&listtype=1&msgId=&rq=&loadPage=13&listtype=1&tabtype=16&filtertype=1&filtered=0&viewed=0&TotCnt=367&Show=Y&Module=}

\item \small \url{http://profile.marathimatrimony.com/profiledetail/viewprofile.php?id=R1194547&osa=dbos&memval=4&listtype=1&msgId=&rq=&loadPage=11&listtype=1&tabtype=16&filtertype=1&filtered=0&viewed=3&TotCnt=367&Show=Y&Module=}

\item \small \url{http://profile.marathimatrimony.com/profiledetail/viewprofile.php?id=R1762507&osa=dbos&memval=6&listtype=1&msgId=&rq=&loadPage=1&listtype=1&tabtype=16&filtertype=1&filtered=0&viewed=5&TotCnt=367&Show=Y&Module=}

\item \small \url{http://profile.marathimatrimony.com/profiledetail/viewprofile.php?id=R1194547&osa=dbos&memval=4&listtype=1&msgId=&rq=&loadPage=11&listtype=1&tabtype=16&filtertype=1&filtered=0&viewed=3&TotCnt=367&Show=Y&Module=}

\item \small \url{http://www.shaadi.com/profile?profileid=SH13882555&ubt=L2luYm94L3BlbmRpbmcvcmVjZW50LWludGVyZXN0c3xpbmJveDo1YjhmMGM0ZTViMTM4YmU2ZjUxNDAzMTVlM2M4OWJhMnw4NDI3ZGVlYjMzMTg2MmUzMDc1N2E5Mjg0OGEyZjc2OQ\%3D\%3D&source=unified&evt_ref=aW5ib3gtaW50ZXJlc3Rz&datasrc=api}

\item \small \url{http://www.shaadi.com/profile?profileid=bSH74851794&ubt=L2luYm94L3BlbmRpbmcvcmVjZW50LWludGVyZXN0c3xpbmJveDo1YjhmMGM0ZTViMTM4YmU2ZjUxNDAzMTVlM2M4OWJhMnxlNzMxMWM0NmM2ODNjZmRhM2JlODY0NTQzMzIxODg5Mw\%3D\%3D&source=unified\&evt_ref=aW5ib3gtaW50ZXJlc3Rz&datasrc=api}

\item \small
  \url{http://www.shaadi.com/profile?profileid=ISH08025255&ubt=L2luYm94L3BlbmRpbmcvcmVjZW50LWludGVyZXN0c3xpbmJveDo1YjhmMGM0ZTViMTM4YmU2ZjUxNDAzMTVlM2M4OWJhMnwyMDJhNGVlNzk5NGI0MjlmZTliMTkwODQzMDQ5NDRmYg\%3D\%3D&source=unified&evt_ref=aW5ib3gtaW50ZXJlc3Rz&datasrc=api}
\end{itemize} 


\end{block} 
\end{column}%3 

\end{columns}
\end{frame}

    
\end{document}


% -- Attic -- % 

%        \begin{itemize}
%          \tiny \item \tiny If you do something sloppy, don't
%          think about it and don't say sorry. 
%        \item \tiny don't think someone is trying to hurt you if
%          they say something.
%        \item \tiny know the paths of least stress. 
%        \item \tiny if mom does something, don't let that bite you. 
%        \end{itemize}
