\documentclass[serif, mathserif, final]{beamer}
\mode<presentation>{\usetheme{Lankton}} 
\usepackage[orientation=landscape,size=a0,scale=1.6, debug]{beamerposter}
%\usepackage[orientation=landscape,size=a0,scale=1.4,debug]{beamerposter}
%\usepackage[absolute,overlay]{textpos} % <-- can  use this to position text (solves problem of earlier yesterday with poster placement). 

%\documentclass[serif,mathserif,final]{beamer}
%\mode<poster>{\usetheme{RicePoster}}
\usepackage{amsmath,amsfonts,amssymb,pxfonts,xspace}

\usepackage{graphicx, ragged2e}
\usepackage{pgffor}
\usepackage{ulem}
\usepackage{caption}
\usepackage{courier}

\usepackage{verbatim}

%\usepackage[usenames,dvipsnames]{xcolor}    
\usepackage{listings}

\usepackage{float}
\usepackage{subfig}
\setbeamertemplate{caption}[numbered] 

\usepackage{calendar}
\usepackage{geometry}

%\graphicspath{{./figures/}}                                                   
%\usepackage{beamerposter}
%\graphicspath{{./figures/}} 
\newcommand{\bllt}{\item \small}
\newcommand{\doneTaskNoItem}[1]{\sout{#1}}
\newcommand{\doneTask}[1]{\tiny \item \tiny \sout{#1}}
\newcommand{\doneTaskHyp}[1]{\tiny \item \tiny \textcolor{blue} {\sout{#1}}}
\newcommand{\optTask}[1]{\tiny \item \tiny \textcolor{green}{#1}}
\newcommand{\prioTask}[1]{\tiny \item \tiny \textcolor{red}{#1}}
\newcommand{\timeEst}[1]{\textit{Time:} \textit{#1}}
\newcommand{\te}[1]{\textit{TimeEst:} \textit{#1}}
\newcommand{\priority}[1]{\textit{Priority:} \textit{#1}}
\newcommand{\pr}[1]{\textit{Priority:} \textit{#1}}
\newcommand{\prio}[1]{\textit{Priority:} \textit{#1}}
\newcommand{\dueBy}[1]{\textit{Deadline:} \textit{#1}}
\newcommand{\MyName}{Vivek~Kale}
\newcommand{\fixme}[1]{\textcolor{blue}{[FIXME: #1]}}
\newcommand{\revision}[1]{\textcolor{blue}{[FIXME comment : #1]}}
\newcommand{\regItem}[1]{\item \textcolor{cyan}{#1}}
\newcommand{\regRoutineItem}[1]{\item \textcolor{green}{\textit{Reg. Routine:} #1}}
\newcommand{\situationItem}[1]{\item \textcolor{magenta}{\textit{Situation:} #1}}
\newcommand{\deadline}[1]{#1}
\newcommand{\dl}[1]{#1}
\newcommand{\comments}[1]{}

%\graphicspath{{./figures/}}
%\usepackage[orientation=landscape,size=a0,scale=1.6,debug]{beamerposter}

%-- Header and footer information ----------------------------------
\newcommand{\footleft}{Mgmt-WorkLife-weekPlan} % figure what this should be 
\newcommand{\footright}{April 2015}

%------------------------------------------------------------------
%-- Main Document ------------------------------------------------- 
\title{Month-Week-Day Plan} 
\author{Vivek Kale$^1$}
\institute{$^1$ University of Illinois at Urbana-Champaign}  
\date{\today}

% TODO: make the below document neater 
% TODO: consider stretching center column 
% TODO: check how to fit week daily plan together .  

\begin{document}  

\comments{
\begin{frame}{} 
  \begin{columns}
    %-- Column 1 --------------------------------------------------- 
    \begin{column}{0.22\linewidth}
      \begin{block}{Happiness Generation - must maintain every week.} 
        % explain happiness: show gratitude
        % remember to show gratitude
        \begin{itemize}
          \tiny \item \tiny happy that I have Atul to show me.  
        \item \tiny Happy that I have normal life up to this point.  
        \item \tiny Thankful that I got a chance to do what I did on Saturday. 
        \item \tiny Think about Neha Jamb. 
        \item \tiny Think about dad saying, I understand, and want you to be happy. 
        \end{itemize}
      \end{block}

    \begin{block}{Habits} 
      \begin{itemize} 
        %\tiny \item \tiny move feet less, don't scrub on floor. 
        \tiny \item \tiny back straight + eye contact. 
      \item \tiny Reduce things. 
      \item \tiny lips relaxed. 
      \item \tiny watch what happens when a hot girl talks to you. 
      \end{itemize} 
    \end{block} 
  \end{column} %1

  \begin{column}{0.5\linewidth}
    %-- Block 2-1 
    \begin{block}{ 10-year plan }
      \begin{itemize}
      \item \small Make someone and dad proud.
      \end{itemize}
    \end{block}
    
    \begin{block}{ 3-year plan }
      \begin{itemize}
      \item \small find someone
      \item \small make 150K
      \item \small network
      \end{itemize}
    \end{block}

    \begin{block}{ 6-month plan}
      \begin{itemize}
        \small \item \small results + thesis
      \item \small routine + worklife
      \item \small 
      \end{itemize}
    \end{block} 

    \begin{block}{Month-by-month}
      \begin{itemize}
      \item \small Early December: finish slides for defense.
      \item \small Mid-december: put together things. 
      \item \small Late December: send out thesis to others 
      \item \small Late January: Defend.
      \item \small Mid-Feb: finish thesis, start looking for jobs. 
      \item \small Late feb: jobs+ and vacation. 
      \item \small March: 
      \item \small April: 
      \item \small May: finish paper. 
      \item \small June: review work from sem, library + worklife
        org. 
      \item \small July: social + jobs. 
      \item \small 
      \end{itemize}
    \end{block}

%TODO: prioritize 
%\begin{column}{0.33\linewidth} {\textbf{\underline{Month Plan for August 2014}}}      %-- Block 1-1   
\begin{block}{\underline{\textbf{April goals}}}
\begin{enumerate}
\small \item \small 
\item \small 
\end{enumerate}
\end{block}

\begin{block}{\small \underline{\textbf{Week of April $17^{th}$}}}
\begin{enumerate}
\tiny \item \tiny 
\item \tiny 
\item \tiny 
\end{enumerate}
\end{block}

\begin{block}{\small \underline{\textbf{Week of April $17^{th}$}}}
\begin{enumerate}
\tiny \item \tiny 
\item \tiny 
\item \tiny 
\end{enumerate}
\end{block}
\end{column}

%-- Column 3 ---------------------------------------------


\begin{column}{0.28\linewidth}
\begin{block}{\small \textbf{\underline{Regular Routines}} }
\underline{\textbf{Morning}}
\begin{itemize}
\tiny \item \tiny Brush Teeth \timeEst{4 mins}. 
\item \tiny Mouthwash, Clean tongue - it helps with breath\timeEst{1mins} 
\item \tiny Eating small breakfast. 
\item \tiny Check your schedule for meetings / appointments for that day: Is anything urgent? \timeEst{5 mins}. 
\item \tiny Excercise: 1 hour ( Stretch for 10 mins, Treadmill for 30 mins , Lift weights or Yoga 1 hour, Meditation for 10 mins). 
\item \tiny Shave (at least every other day) \timeEst{5 mins}. 
\item \tiny Shower : (shampoo+conditioner, acne wash,  soap on underarms/underbody)
\timeEst{10 mins}
\item \tiny dry hair, dry face, arms, legs, back, stomach \timeEst{3 mins}
\item \tiny Clothing: belt, check collar, shirt not half-tucked, matching socks \timeEst{5 mins}
\item \tiny Comb hair, hair gel optional \timeEst{ 1 min}
\item \tiny Check Keys/Wallet/Cell/Badge (get a bucket) \timeEst{1 min}
\item \tiny Open meds cabinet, get water, take medicines \timeEst{1 min}
\item \tiny Wear lenses and rinse out case \timeEst{ 2 mins}
\item \tiny Deodorant or cologne depending on the day \timeEst{1 min}
\item \tiny Wash your face with a face wash - it helps with acne \timeEst{3 mins}
\item \tiny Moisturize - apply lotion \timeEst{ 2 min}
\item \tiny Neti pot / clean out sinuses - if you’re feeling congested \timeEst{5 min}
\item \tiny clean out ears, nose \timeEst{5 mins}
\item \tiny Remember to lock door \timeEst{1 mins}
\end{itemize} 

\underline{\textbf{Evening}}
\begin{itemize}
\tiny \item \tiny Call family: 30 mins
\item \tiny meet friends: 20 mins
\item \tiny Cleaning dishes / cleaning house: 10 mins
\item \tiny Lay out clothes for the next day, iron if necessary
\item \tiny start laundry if needed: 10 mins,
\item \tiny Collect anything you’ll need for the next day (e.g. dry cleaning to drop off): 5 mins,
\item \tiny Check Facebook/linkedin/google+: 10 mins, matrimony stuff: 10 mins,
\item \tiny Food for lunch/dinner the next day: 10 mins
\end{itemize}

\underline{\textbf{Night before bed}}
%TODO: why isn't enumerate working???
%\begin{enumerate}
\begin{itemize}
\tiny \item \tiny Finish computer stuff \timeEst{5 mins}
\item \tiny Get into sleeping clothes \timeEst{1 mins}
\item \tiny Before sleeping: brush teeth, floss \timeEst{ 2 min}
\item \tiny Properly wash and put away contacts \timeEst{ 2 mins}
\item \tiny Review the days good things \timeEst{ 10 min}
\item \tiny Light Reading \timeEst{ 10 min}
\item \tiny Prayer \timeEst{10 mins}
%\end{enumerate} 
\end{itemize}
\end{block} 
\end{column}%3 
\end{columns} 
\end{frame}
}


\begin{frame}{} 
  \begin{columns}
    %-- Column 1 --------------------------------------------------- 
    \begin{column}{0.25\linewidth} %{\textbf{\underline{Week
      %Aspects(new name)}}}
      \begin{block}{Habits}
        \begin{itemize}
          \tiny \item \tiny 
        \item \tiny 
        \item \tiny 
        \item \tiny 
        \end{itemize}
      \end{block}
      %-- Block 1-1 

      \begin{block}{Happiness}  
        \begin{enumerate}
        \tiny \item \tiny Think about happy thoughts about meeting
        someone else.  
      \item \tiny 
        \end{enumerate}
      \end{block} 

      \begin{block}{Stresses}
        % Recognize emotions / recognize (precisely) what you're worried about -> methods for eliminating worry. 
        % clean out old worries, put them in pastWorries doc.  
        % remember to define precisely 
        % order from top-to bottom
        \begin{itemize}
          \tiny \item \tiny Worrying about thesis finish. Be sincere
          and work, we make mistakes with time. Get the facts about
          completion. Go find the path. If I can't get it done, then we'll do
          something else. 
          \item \tiny Work: worrying about interviewing: just
            focus on the work. 
          \item \tiny Worrying about gal: think about talking to
            others 

            % \item \tiny Comm: Worrying about not losing it (check this/ define this better) : work on sheet.  
          % \item \tiny Worrying about deep: forget her, because
            % there's much more to be done.  She may not be interested
            % because it's a brother. 
        \end{itemize} 
      \end{block} 
      
      \begin{block}{Real-time Confidence}
        \begin{itemize}
          \tiny \item \tiny If you do something sloppy, don't
          think about it and don't say sorry. 
        \item \tiny don't think someone is trying to hurt you if
          they say something.
        \item \tiny know the paths of least stress. 
        \item \tiny if mom does something, don't let that bite you. 
        \end{itemize}
      \end{block}
      
     %-- Block 1-3
      \begin{block}{Life notes} 
        \begin{itemize} 
          \tiny \item \tiny Level 0+1: focus on finding Happiness. 
        \item \tiny Level 2: 
        \item \tiny Level 4.1: Writing: prefer standard to offbeat. 
        \item \tiny Level 4.2: Body Language: lips relaxed
        \item \tiny Level 4.3: Vocal Variety: shout. 
        \item \tiny TM: work on speech for submission to blog, increasing intentionality. 
        \item \tiny Mgmt/habits: finish chapter 1 reading notes and habits. 
        \end{itemize}     
      \end{block}
    \end{column} %2 
    
    %-- Column 2 --------------------------------------------- 
    \begin{column}{0.50\linewidth}
      %{\textbf{\underline{Week TODO}}} 
      % NOTE: Current policy is to comment out days as they come. 
      % TODO: put in the regular routines here for each day, in the schedule box. 
      %--- Block 2-1
      \begin{block}{Week Summary}
    {\tiny \textbf{Weekend Plan:} Work: write introduction + Work:
      finish techniques + Work: finish related work and conclusions +
      Work:comm: send message about introduction, Work:comm: send
      message about postdoc, Comm: send pics from graduation }\\
      \end{block}
      
      \begin{block}{Running TODO} % find a better name 
        \begin{enumerate}
          \small \item \small Work(ppr): IWOMP paper submissions  =  Work(ppr): get
          intro done and sent  + Work(ppr): send the outline + 
          Work(ppr): update techniques + Work(ppr): add related work \te{3
            hours}\prio{ImportantToHaveSomething}
          \dl{BeforeCrazinessStarts}. 
          %   \item \small Work (ppr): problem statement and techniques and
          %   implementation = 
        \item \small Work(ppr): update implementation to have better
          introduction  = Work(ppr): do this + Work(ppr): check this 
        \item \small Work(ppr): update techniques to have better
          introduction = Work(ppr):do this  +  Work(ppr): check 
        \item \small  Work(ppr): fix problem statement metrics
          description. 
        \item \small Work(ppr): update related work. 
        \item \small Work(ppr): update conclusions. 
        \item \small \doneTask{Work: send Prof Gropp a message.}           
        \item \small Work(ppr): intro+abstract+related work+ conclusions: 
        \item \small Work(ppr): results. 
        \item \small Work(ppr): check for L4: 
        \item \small Work(ppr): grammar errors. 
        \item \small how to say it, and make figures neat. 
        \item \small Work: check with Christian about submission (adding
          message about Bronis not being on the submission). 
        \item \small Comm: send message to Bronis. 

        \item \small Work: job talk slides. 
        \item \small Work: comm: meet for dinner with udatta kaka. 
          
        \item \small worklife: update car sheet 
        \item \small worklife: make more metrics 
        \item \small worklife: add more to T.M. 
        \item \small worklife: experiences documentation.  
        \item \small worklife: figure out ways to be more efficient
        \item \small worklife: find how to use full Levels
      simultaneously.
    \item \small worklife: read books frequently . 
      
    \item \small Mgmt:Spaces: put gift money in bank.  

    \item \small \doneTask{Work:Comm: send reply to Jon Freund.} \te{1 hour}

    \item \small Comm: have Atul send message to PRof. Gropp = Comm:
      write the message  + Comm: send message to Atul to send.  \te{20
        mins}.

    \item \small worklife: get worklife stuff done

    \item \small mgmt:spaces: get passport stuff done. 

    \item \small Work:comm: talk to Tripti and send message. +
      Work:comm: send message for Google survey. 

    \item \small Comm: meet Atul in Chicago. 
    \item \small Comm: BMM registration \te{1 hour} 
    \item \small Mgmt: webpresence: update cover photo. \te{1 hour} 

    \item \small  Comm: TM managment = COmm:  sign up for TM roles +

    \item \small  Comm: plan meeting with ...  \te{1 hour} 

    \item \tiny Comm: send Rishi a message about BMM.
    \item \tiny Comm: send Chris a message about meeting up 
    \end{enumerate}
  \end{block} 

  \begin{block}{Week Daily Schedule}
    \begin{columns} 
      \column{0.14\textwidth}{\textbf{\small \underline{Mon}}}
      \textbf{\small todo} \\ 
      \begin{itemize}
        \tiny \item \tiny Work(hw): homework 1  + homework 2 

        \tiny \item \tiny 
      \item \tiny Work: management of problems.
      \item \tiny Work: comm: send message about fellowship.
      \end{itemize} 
  \textbf{\small schedule} \\
  \begin{enumerate} 
    \tiny \item \tiny 8-9AM: Regular Routines 
  \end{enumerate} 

  \column{0.14\textwidth}{\textbf{\small \underline{Tue}}}
  \textbf{\small todo} \\
  \begin{itemize} 
  \tiny \item \tiny worklife: update pages \te{20 mins} 
    \item \tiny Work: comm: send message to Prof Gropp \te{5 mins} 
      \tiny \item \tiny Work: comm: finish working on funding \te{1 hour} 
    \item \tiny Work: IWOMP paper  \te {2 hours}. 
  \end{itemize}  
  \textbf{\small schedule}\\ 
  \begin{enumerate} 
    \tiny \item \tiny 8-9AM: Regular Routines 
  \end{enumerate} 

  \column{0.14\textwidth}{\textbf{\small {\underline{Wed}}}}
  \textbf{\small todo} \\
  \begin{itemize}
\tiny \item \tiny 

  \end{itemize}
  \textbf{\small schedule} \\
  \begin{enumerate}
    \tiny \item \tiny 8-9AM: Regular Routines 
  \end{enumerate}
  
  \column{0.14\textwidth}{\textbf{\small{\underline{Thu}}}}
  \textbf{\small todo}\\
  \begin{itemize} 
    \tiny \item \tiny Work: finish slides  = Work: finish  slides +
    Work: finish meeting prep\te{3 hours} 

  \item \tiny Work: comm: send message to Jonathan Freund  = Work:
    talk to dad + Work: figure out what to say to Prof gropp +
    Work:comm: send message to Jon Freund  \te{3 hours}
  \item \tiny Work: comm: send out resume = Work:comm: send out resume
  to dropbox + ...  \te{1 hour}  

  \item \tiny Work: comm: send thanks to Christian Terboven. \te{1
    hour} \dl{} 

  \item \tiny Comm: send message to Atul about the photos \te{20 mins}
    \dl{Before9PM} 

  \item \tiny Comm: find joke for TM, practice \te {30 mins} \dl
    {JustBeforeTM}

  \item \tiny Comm: update TM 
  \item \tiny Work: comm: send message to Rajesh Nishtala
  \end{itemize}
  \textbf{\small schedule}\\
  \begin{enumerate} 
    \tiny \item \tiny 8-9AM: Regular Routines 
    \tiny \item 6:30PM - 7:15PM: TM 
    \tiny \item 7:15PM: Jump Labs 
  \end{enumerate} 
  
  \column{0.14\textwidth}{\textbf{\small{\underline{Fri}}}}
  \textbf{\small todo}\\ 
  \begin{itemize}
    \tiny \item \tiny -  \deadline{ }   \timeEst{}  \priority{} 
  \end{itemize}
  \textbf{\small schedule}\\
  \begin{enumerate}
    \tiny \item \tiny 8-9AM: Regular Routines 
  \end{enumerate}
  
  \column{0.14\textwidth}{\textbf{\small \underline{Sat}}}
  \textbf{\small todo}\\
  \begin{itemize}
    \tiny \item \tiny Work:  
  \item \tiny 
  \item \tiny 
  \item \tiny Comm: 
  \end{itemize}
  \textbf{\small schedule}\\ 
  \begin{enumerate}
    \tiny \item \tiny 8-9AM: Regular Routines 
  \end{enumerate}
  
  \column{0.14\textwidth}{\textbf{\small \underline{Sun}}}
  \textbf{\small todo}\\
  \begin{itemize}
  \item \tiny Work: 
    \item \tiny Work: make schedule for paper and send 
    \item \tiny Comm: talk to Atul about life
    \item \tiny Mgmt: webpresence: update on whatsapp  
    \item \tiny Mgmt: webpresence: message on fb 

    \item \tiny Mgmt: spaces: vuln: check key. 
  \end{itemize}
  \textbf{\small schedule}\\
  \begin{enumerate} 
    \tiny \item \tiny 
  \end{enumerate} 
    \end{columns}
  \end{block}
\end{column}%2

%-- Column 3 --------------------------------------------------- 
\begin{column}{0.20\linewidth}
  %-- Block 3-1 
  % On Sunday morn, put a quick synopsis of top news items                  
  % here.  Categorize as Comm and Money.      
  \begin{block}{News}
    \begin{itemize} 
      \tiny \item \tiny French Open
    \end{itemize}
  \end{block}
  \begin{block}{Weather} 
    \begin{itemize}
      \tiny \item \tiny Watch for Pollen.
    \item \tiny Rainy 
    \end{itemize}
  \end{block} 
  \begin{block}{Clothes plan} 
    \begin{itemize} 
      \tiny \item \tiny Saturday: wear polo 
    \item \tiny Saturday night: wear light blue dress shirt and jeans. (or maybe khakis and polo shirt). 
    \item \tiny Sunday: business casual shirt. 
    \item \tiny Wednesday : 
    \item \tiny Thursday: 
    \item \tiny Friday : 
    \item \tiny Saturday : Blue full shirt . 
    \item \tiny Sunday : Red shirt .
    \end{itemize} 
  \end{block}
  %-- Block 3-2

  %-- Block 3-3
  \begin{block}{Situations}
    \begin{itemize}
    

\tiny \item \tiny \textit{Sitting at Union} Pre-: don't make
        sudden movements with girl.
      \item \tiny \textit{Meetup from Conference} Pre-: don't make
        sudden movements with girl.  
        \item \tiny \textit{Talking to SiriusXM} Pre-:  Post-: don't
          talk more after they ask questions.  

        \item \tiny \textit{Mem. Day Atul and Ridhima} Pre-: 
      \item \tiny \textit{Graduation:} Pre-:   Post-: 
      \item \tiny \textit{Party } Pre-:  Post-:

      \item \tiny \textit{Message to Rohun} Pre-: think about intent,
        and goal Post-: 
        \item \tiny \textit{PostGrad-Thanks}: Pre-: thanks to
          everyone. Experience wouldn't have been the same without
          you. Much to be thankful for. Post-: %Mgmt:webpresence: if
                                %going onto facebook to check if you
                                %need to respond to something, don't
                                %check FB likes (those can be
                                %delayed).                                                                                    
          \item \tiny \textit{Talk to Anu about Money}: Pre-:   Post-:
            say ``Hi Anu,  [newline] No problem at all.`` 
    \end{itemize}
  \end{block}
\end{column}%3 
\end{columns}

\end{frame}
\end{document}
