\documentclass[serif, mathserif, final]{beamer}
\mode<presentation>{\usetheme{Lankton}}
\usepackage[orientation=landscape,size=a0,scale=1.6, debug]{beamerposter}
\usepackage{amsmath,amsfonts,amssymb,pxfonts,xspace}
\usepackage{graphicx,ragged2e,pgffor}
\usepackage{hyperref}
\usepackage{ulem}
\usepackage{courier}
\usepackage{caption,verbatim,listings,float,subfig} %TODO: order these 
\setbeamertemplate{caption}[numbered] 
\usepackage{calendar}
\usepackage{geometry}

%TODO: remove unneeded items 
\newcommand{\bllt}{\item \small}
\newcommand{\doneTaskNoItem}[1]{\sout{#1}}
\newcommand{\doneTask}[1]{\tiny \item \tiny \sout{#1}}
\newcommand{\doneTaskHyp}[1]{\tiny \item \tiny \textcolor{blue} {\sout{#1}}}
\newcommand{\optTask}[1]{\tiny \item \tiny \textcolor{green}{#1}}
\newcommand{\prioTask}[1]{\tiny \item \tiny \textcolor{red}{#1}}

\newcommand{\timeEst}[1]{\textit{TimeEst:}\textit{#1}}
\newcommand{\te}[1]{\textit{TimeEst:}\textit{#1}}
\newcommand{\deadline}[1]{\textit{Deadline:}\textit{#1}}
\newcommand{\dueBy}[1]{\textit{Deadline:}\textit{#1}}
\newcommand{\dl}[1]{\textit{Deadline:}\textit{#1}}
\newcommand{\priority}[1]{\textit{Priority:}\textit{#1}}
\newcommand{\prio}[1]{\textit{Priority:}\textit{#1}}
\newcommand{\pr}[1]{\textit{Priority:}\textit{#1}}

\newcommand{\MyName}{Vivek~Kale}
\newcommand{\fixme}[1]{\textcolor{blue}{[FIXME: #1]}}
\newcommand{\revision}[1]{\textcolor{blue}{[FIXME comment : #1]}}
\newcommand{\regItem}[1]{\item \textcolor{cyan}{#1}}
\newcommand{\regRoutineItem}[1]{\item \textcolor{green}{\textit{Reg. Routine:} #1}}
\newcommand{\situationItem}[1]{\item \textcolor{magenta}{\textit{Situation:} #1}}

\newcommand{\comments}[1]{}

%TODO: consider changing the below so you only use the text in the
%document 


%TODO: change Week plans 

\newcommand{\footleft}{Mgmt-WorkLife-weekPlan} % figure what this should be 
\newcommand{\footright}{May 2016}
%-- Main Document ------------------------------------------------- 
\title{Month-Week-Day Plan}\author{Vivek Kale$^1$}\institute{$^1$ 
University of Illinois at Urbana-Champaign}\date{\today}

\begin{document}
\begin{frame}
  \begin{columns}
    %-- Column 1 --------------------------------------------------- 
    \begin{column}{0.25\linewidth} %{\textbf{\underline{Week Aspects(new name)}}}
      \begin{block}{Local Happiness}
        % howto:Recognize emotions / recognize (precisely) what you're
        % worried about -> methods for eliminating worry. 
        % clean out old worries, put them in pastWorries doc.  
        % remember to define precisely 
        % order from top-to bottom
        \begin{itemize}
          \tiny \item \tiny Work: worrying about interviewing: just focus on the work. 
        \item \tiny Worrying about gal: think about talking to others. 
        \end{itemize}
      \end{block}
      \begin{block}{Stresses}
        % howto:Recognize emotions / recognize (precisely) what you're worried about -> methods for eliminating worry. 
        % clean out old worries, put them in pastWorries doc.  
        % remember to define precisely 
        % order from top-to bottom
        \begin{itemize}
          \tiny \item \tiny Work: worrying about interviewing: just focus on the work. 
        \item \tiny Worrying abt Dp thinking you are stupid -->  think
            about Todd saying you're smart, you don't apply yourself; 
            think about Atul saying they aren't doing that
            intentionally. 
          \item \tiny Anger about a b  -> ...
          \item \tiny Anger about UP -> think about the positive
            perspective, and the original
          \item \tiny Anger about dad saying things 
        \end{itemize}
      \end{block}    
      %-- Block 1-3 
      \begin{block}{Life notes}
        \begin{itemize}
        \item \tiny 
        \item \tiny 
        \end{itemize}
      \end{block}
    \end{column} %2
    %-- Column 2 --------------------------------------------- 

%howto:
    
    Atul’s FightingIllini  wifi pass:  2173900374 WPA  
    
    Amtrak  eVoucher numbers 
    
    Southwest credit: 
    
    BT code for BMW: 

    \begin{column}{0.50\linewidth}
      %--- Block 2-1
      \begin{block}{Week Summary}
        {\tiny \textbf{Week Plan:} }
        {\tiny \textbf{Weekend Plan:}  }   
      \end{block} 
      \begin{block}{Running TODO} % find a better name 
        \begin{enumerate} 


      % curr --> 
        \item \tiny \doneTask{ Mgmt:webpresence: FB like Prem's post. }

        \doneTask{Comm: respond to Tope.} \te{30 minutes} \dl{} \pr{IU}
         \doneTask{Comm: message to Laila Saied} \te{1 hour}
          \d{Monday} \pr{UI}. 

          Hi,
          
          I'm not sure that you remember me, but I want to let you know
          it's nice to be connected with you on Facebook.
          

          
          Hi, 
          
          I'm not sure you remember me, but it's nice to be connected with you
          on Facebook.
          

          -----------------------           
          
          Hi,
          
          I'm not sure that you remember me, but it's nice to be connected with
          you on Facebook. 

          I'm unsure that you remember me. It's nice to be connected with
          you on Facebook. 
          
          TODO: L3: I want to let you know VS [OMIT] 
          TODO: L4: I'm not sure v VS I don't know  -done
          TODO: L5: Hi VS __ VS OMIT -done          
          TODO: L4: that VS [OMIT] - just 
          TODO: L4: that VS [OMIT] 


        \item \tiny Mgmt:webpresence: FB like Mamta's NYC post.  

          Pro: 
          - knows I like her - could do this elsewhere? but
          where? 
          - knows I'm still alive. 
          - do it now - later in summer may not have opportunities

         
          Con: 

          - can be overdone - but not true, two months since. 
          
          outcome: reciprocate - no need, just know I like her. I'm
          just annoyed a bit. 

          L5: good to meet people.  
          

        \item \tiny Mgmt:webpresence: add to Mukta.

          Pros: 
          1. good to connect. 
          2. Don't do it now, she might cancel.
          3. shouldn't not have connection - bad. 

          Cons: 
          -  deleted before, may delete. 
          -  Late. 
          -  Annoying to have.           

        \item \tiny Comm: message to Ayo Adesida on Facebook. 
          

        \item \tiny Mgmt:webpresence: FB like Mona and Leena's. Pro:
          they appreciate, show appreciation also. Con: could get
          involved. 

        \item \tiny Mgmt:webpresnce: FB like Amaeya's post for
          Bhangra.  



        \item \tiny Work: send message about Intel opportunity. 

        \item \tiny  Comm: send message about a 10-year re-union.


Laugh 
Think 
Emotions moved to tears 



Hi,

I heard through word of mouth from Professor Josep Torrellas about
an opportunity at Intel-Hudson related to HPC and Data Analytics. I'm
interested in the position.

To give you background about me, 

I did a PhD under Professor Bill Gropp at the University of Illinois,
with a fellowship at Lawrence Livermore National Laboratory. I
graduated in May 2015. My dissertation was on low-overhead OpenMP scheduling schemes to
improve performance of scientific application programs run on clusters
of multicore nodes. My fellowship which required one to do their
dissertation work at Lawrence Livermore Lab in California. 

I believe I can contribute well in a team that is focused on HPC software
development and research. 

If you would like to contact me by phone to talk further, please feel
free to contact my cell phone number at 217-369-7996.

Vivek
                   
        \item \tiny Mgmt:webpresence:(addMuk): add Mukta on LinkedIn =
          \te{20 minutes} 
          Mgmt:webpresence(addMuk): add Mukta on LinkedIn +
          Mgmt:webpresence:(addMuk): add mukta on LinkedIn. 

        \item \tiny Work: watch Fulbright scholar video. 
          

        \item \tiny Work:comm:rel: message to Barbara Chapman. 
        \item \tiny Work: write journal paper.  

        \item \tiny Work(cp): coding problem := Work(cp): coding problem on
          bits and arrays and hash tables.
          
        \item \tiny Work(cp): MIT lecture := Work(cp): MIT lecture on
          hashing Karp-Rabin \te{1.5 hours} \dl{before Wed}
          \pr{reasonable}. 

        \item \tiny Comm: consider talking to Illina 

        \item \tiny 

        \item \tiny worklife: read 7 habits summary. 
        \item \tiny Worklife: plan out 7 habits + social
          intelligence. 

        \item \tiny Mgmt:Spaces: cancel clear membership.  

        \item \tiny Mgmt:Spaces(GetThingsSpring2016): get Things =
          \doneTaskNoItem{Mgmt:Spaces(getThings): get iPad} + Mgmt:Spaces(getThings):
          get suit + \doneTaskNoItem{Mgmt:Spaces(getThings): get
            muffler tips}

        \end{enumerate}
      \end{block} 

      \begin{block}{Week Daily Schedule} 
        % howto: arrange items from running todo into the below
        % sheet management document. 
        \begin{columns} 
          \column{0.14\textwidth}{\textbf{\small \underline{Mon}}}
          \textbf{\small todo} \\ 
          \begin{itemize}
            \tiny \item \tiny Add in schedule
          \item \tiny 
          \end{itemize} 
          \textbf{\small schedule} \\
          \begin{enumerate} 
            \tiny \item \tiny 8-9AM: Regular Routines 
          \end{enumerate} 
          
          \column{0.14\textwidth}{\textbf{\small \underline{Tue}}}
          \textbf{\small todo} \\
          \begin{itemize}
            \tiny \item \tiny Work: make project sheet \te{10 minutes} 
          \item \tiny Mgmt:Spaces: check for diploma \te{10 minutes} 
          \end{itemize}  
          \textbf{\small schedule} 
          \begin{enumerate}
            \tiny \item \tiny 10AM - 11AM = 
          \item \tiny 11AM - 12AM = make long-term goals 
          \item \tiny 12PM - 2PM = 
            \tiny \item \tiny 2PM -3PM = 
          \item \tiny 6PM - 10PM = 
          \end{enumerate} 
          
          \column{0.14\textwidth}{\textbf{\small {\underline{Wed}}}}
          \textbf{\small todo} \\
          \begin{itemize}
           \tiny \item \tiny Work: finish slides for tomorrow. 
           \item \tiny Mgmt: Spaces: update fb 
         \item \tiny Comm: fb update 
          \end{itemize}
          \textbf{\small schedule} \\
          \begin{enumerate}
            \tiny \item \tiny 8-9AM: Regular Routines 
          \item \tiny 9AM - 10AM: Send message 
            \item \tiny 6:30PM - 7:30PM = 
          \end{enumerate} 
          \column{0.14\textwidth}{\textbf{\small{\underline{Thu}}}}
          \textbf{\small todo}\\
          \begin{itemize}  
            \tiny \item \tiny 
          \item \tiny 
          \end{itemize} 

          \textbf{\small schedule}\\
          \begin{enumerate} 
            \tiny \item \tiny 8-9AM = Regular Routines 
            \item \tiny 12-1PM = gather notes about job org. during
              session 
            \item \tiny 3:30PM - 4:30PM = meeting 
            \item \tiny 6PM - 9PM = revise emot. int. chapter and
              structure wl-cheat based on it 
          \end{enumerate}  
          
          \column{0.14\textwidth}{\textbf{\small{\underline{Fri}}}}
          \textbf{\small todo}\\ 
          \begin{itemize}
          \item \tiny Work: code review. 
          \item \tiny Work: finish work. 
          \item \tiny Mgmt:Spaces: Haircut \te{10 minutes}. 
          \item \tiny Comm: check messages 
          \end{itemize}
          \textbf{\small schedule}\\
          \begin{enumerate}
            \tiny \item \tiny 8-9AM: Regular Routines 
          \end{enumerate}
          
          \column{0.14\textwidth}{\textbf{\small \underline{Sat}}}
          \textbf{\small todo}\\
          \begin{itemize} 
            \tiny \item \tiny
          \end{itemize}
          \textbf{\small schedule}\\ 
          \begin{enumerate}
            \tiny \item \tiny 7-7:30PM = food + organize.  
            \tiny \item \tiny 7:30PM -8PM = 
            \tiny \item \tiny 8PM -9PM = 
            \tiny \item \tiny 9:45PM - 10:30PM = go out 
            \tiny \item \tiny 2AM -3AM =  message Samir + add people
          \end{enumerate}
          
          \column{0.14\textwidth}{\textbf{\small \underline{Sun}}}
          \textbf{\small todo}\\
          \begin{itemize} 
           \tiny \item \tiny 
          \end{itemize}

          \textbf{\small schedule}\\
          \begin{enumerate} 
            \tiny \item \tiny 3PM - 4PM  =
          \item \tiny 5-7PM = Comm work 
          \item \tiny 8PM - 10PM = worklife work. 
          \end{enumerate} 
        \end{columns}
      \end{block}
    \end{column}%2
    
    %-- Column 3 --------------------------------------------------- 
    \begin{column}{0.20\linewidth}
      %-- Block 3-1 
      % On Sunday morn, put a quick synopsis of top news items                  
      % here.  Categorize as Comm and Money.      
      \begin{block}{News}
        \begin{itemize} 
          \tiny \item \tiny M: IBM/Intel job cuts 
          \tiny \item \tiny S: Trump  wins nomination
        \end{itemize}
      \end{block}
      

      \begin{block}{Weather} 
        \begin{itemize}
          \tiny \item \tiny Rain early in the week,Pollen, 60s. 
        \end{itemize}
      \end{block} 

      \begin{block}{Clothes plan} 
        \begin{itemize}
          \tiny \item \tiny Monday
        \item \tiny Tuesday
        \item \tiny Wednesday
        \item \tiny Thursday
        \item \tiny Friday
        \end{itemize} 
      \end{block}
      %-- Block 3-2 

      %-- Block 3-3
      \begin{block}{Situations}
        % Summary: the below are the situations that define one
        % another.        
        % Howto: Put post notes of each situation from list of previous
        % week. Put high importance situations in situationslist. 
        % Put list of upcoming situations on Sunday morning with Pre. 

        \begin{itemize}
        \tiny \item \tiny \textit{meet with girl in SF} Pre-: avoid
        talking much.
      \item \tiny 
        \end{itemize} 
      \end{block} 
%Summary:  

\begin{block}{Rel}
  \begin{itemize} 
    \small \item \small Girl from SF 
    \small \item \small Mamta 
    %\small \item \small Ruchi 
    %\small \item \small Neha Jambhekar 
    %\small \item \small Meghan Joshi 
    %\small \item \small Vinita Ghate 
  \end{itemize} 
\end{block} 
\end{column}%3 
    %%`
\end{columns}
\end{frame}


\end{document}












% -- Attic -- % 

%        \begin{itemize}
%          \tiny \item \tiny If you do something sloppy, don't
%          think about it and don't say sorry. 
%        \item \tiny don't think someone is trying to hurt you if
%          they say something.
%        \item \tiny know the paths of least stress. 
%        \item \tiny if mom does something, don't let that bite you. 
%        \end{itemize}
