\documentclass[serif,mathserif,final]{beamer}

\mode<presentation>{\usetheme{Lankton}} 
%\mode<presentation>{\usetheme{I6pd2}} 
%\mode<presentation>{\usetheme{RicePoster}} 
%%\mode<presentation>{\usetheme{ConfPoster}} 
\usepackage{amsmath,amsfonts,amssymb}
%\usepackage{eulervm}

\usepackage{pxfonts}
\usepackage{graphicx, ragged2e}
\usepackage{pgffor}
\setbeamertemplate{caption}[numbered]

%\documentclass[11pt]{article}

\usepackage{ulem}
\usepackage{color}
\usepackage{xspace}
\newcommand{\bllt}{\item \small}
\newcommand{\doneTaskNoItem}[1]{\sout{#1}}
\newcommand{\doneTask}[1]{\item \sout{#1}}
\newcommand{\doneTaskHyp}[1]{\item \textcolor{blue} {\sout{#1}}}
\newcommand{\optTask}[1]{\item  \textcolor{green}{#1}}
\newcommand{\prioTask}[1]{\item  \textcolor{red}{#1}}
\newcommand{\timeEst}[1]{\textit{Time:} \textit{#1}}
\newcommand{\priority}[1]{\textit{Priority:} \textit{#1}}
\newcommand{\prio}[1]{\textit{Priority:} \textit{#1}}
\newcommand{\dueBy}[1]{\textit{Deadline:} \textit{#1}}
\newcommand{\MyName}{Vivek~Kale}
\newcommand{\fixme}[1]{\textcolor{blue}{[FIXME: #1]}}
\newcommand{\revision}[1]{\textcolor{blue}{[FIXME comment : #1]}}
\newcommand{\regItem}[1]{\item \textcolor{cyan}{#1}}
\newcommand{\regRoutineItem}[1]{\item \textcolor{green}{\textit{Reg. Routine:} #1}}
\newcommand{\situationItem}[1]{\item \textcolor{magenta}{\textit{Situation:} #1}}
\newcommand{\deadline}[1]{#1}
\newcommand{\comments}[1]{}

\graphicspath{{./figures/}}
\usepackage[orientation=landscape,size=a0,scale=1.6,debug]{beamerposter}

%-- Header and footer information ----------------------------------
\newcommand{\footleft}{Mgmt-WorkLife-weekPlan} % figure what this should be 
\newcommand{\footright}{June 2014}
\title{Month-Week-Day Plan} 
\author{Vivek Kale$^1$$^2$}
\institute{$^1$ University of Illinois at Urbana-Champaign \quad}  

%------------------------------------------------------------------
%-- Main Document ------------------------------------------------- 

\begin{document} 
\begin{frame}{}
  
  \begin{columns}[t]
    
%-- Column 1 ---------------------------------------------------  
\begin{column}{0.30\linewidth} {\textbf{\underline{Week Aspects(new name)}}} 
  %-- Block 1-1
  \begin{block}{\textit Stresses} 
    % Recognize emotions / recognize what you're worried about -> eliminate worry
    \begin{itemize}
    \item \tiny EuroMPI paper : 
      \small \item \tiny Ridhima saying stuff about me. 
    \item \tiny related work:   
    \item \tiny Atul saying let's talk about this some other time. 
      % \item \small friends of Atul's better(?): 
      % \item \small email -done : 
      % \item \small anger that you are below parents 
      % \item \small [ find others ]
    \end{itemize} 
  \end{block} 
  %-- Block 1-2 

  %-- Block 1-3
  \begin{block}{\textit Habits } 
    \begin{itemize} 
      \tiny \item \tiny move feet less, don't scrub on floor. 
    \item \tiny back straight. 
    \item \tiny lips relaxed. 
    \end{itemize} 
  \end{block} 

  %-- Block 1-4
  \begin{block}{\textit Clothes plan } 
    \begin{itemize} 
      \small \item \tiny - 
    \item \tiny Saturday: wear polo shirt. 
    \item \tiny Saturday night: wear light blue dress shirt and jeans. (or maybe khakis and polo shirt ). 
    \item \tiny Sunday: business casual shirt. 
    \end{itemize} 
  \end{block} 

  %-- Block 1-5
  \begin{block}{\textit Food plan } 
    \begin{itemize} 
      \small \item \tiny Skip meals this week to take out fat from weekend. 
    \item \tiny Be very careful about food for Saturday night, along with Brunch for Sunday and dinner for Sunday. 
    \end{itemize} 
  \end{block} 

  \begin{block}{\textit Situations} 
    \begin{itemize} 
    \item \tiny Meeting with Prof Gropp: Pre-: get updates in early, think about what to say Post-:  Think about what to say earlier, watch for stresses during the meeting(don't overthink), go through possible stress points earlier, 
      
    \item \tiny Toastmaster's : Pre-:    Post-: 

    \item \tiny Driving to Chicago with Atul/Ridhima/Joe : Pre-:  Post-: 
    \item \tiny Moving with Atul/Ridhima/Gary : Pre-:      Post-: 
    \item \tiny Driving back with Joe : Pre-:      Post-: 

    \end{itemize} 
  \end{block} 

\end{column} %2 
%-- Column 2 --------------------------------------------- 

\begin{column}{0.33\linewidth}{\textbf{\underline{Week TODO}}} 

% NOTE: Current policy is to comment out days as they come. 
% TODO: put in the regular routines here for each day, in the schedule box. 
  %--- Block 2-1

\begin{block}

%{\small weekTODO} 

\begin{enumerate}

\item \tiny Work: Do related work structure and motivation. 
\item \tiny Work: update picture and chapter on combo. 
\item \tiny Work: add code structure for data collection + Send
  message to Tanzima about PAPI + Find any other systems issues and
  take care of them + integrate the slack-conscious runtime/ MPI dot
  prod. 
\item \tiny Mgmt: time: plan out thesis for mid-October grad date. 

\item \tiny Comm: send Sneha message 
\item \tiny Comm: structure Atul's speech + read vocal variety speech lessons, look at speech inspiration + sign up for week-after-next speech. 

\item \tiny Mgmt: Spaces:webpresence: choose and update matrimony pic
  + change website pic based on matrimony pic (or choose a separate
  one) + update linkedIN/website pic.


\item \tiny Mgmt: Spaces: money: check sw old stuff; get the lamp;
  find iPad; update money; check money in bank. 

\item \tiny \textbf{Mgmt: Spaces: Graduation: check for credit hours
  for the summer, get new ones if needed + check grad deadlines.  -
  got 6 hours,  need to register in fall for 1 S/U 500-level.  -
  checked the graduation/defense page, make sure your committee is in
  aggreement about the thesis. + Schedule defense in October / Do it
  early with checking Bronis's schedule / Be sure to go on
  Self-Service to apply for graduation before then. } 

\item \tiny Mgmt: Spaces: Graduation: send messages on Post-docs. Princeton. / SUNY. / MIT. / Livermore. 

\item \tiny Mgmt: Spaces: get the taillight fixed, by buying this online. \timeEst{30 mins} 

\item \tiny \doneTask{workLife: Finish monthPlanCurr.} 
\item \tiny \doneTask{workLife: put situations in correct place.}  
\item \tiny workLife: finish emotional intelligence book, style guide, and winfriends. 
\item \tiny \doneTask{worklife: get cooking instructions down, get routine for running/excercise down, integrate other sheets.} 



\item \tiny \doneTask{Work: check with others about accounts at LLNL. }
\item \tiny \doneTask{Work: get environment setup, worklife: add in notes into environment}. 
\item \tiny Work: Figure out computer (cs-grad131), and check for files/images from CS525. 
\item \tiny GenKnowledge: get book on genKnowledge. 
\end{enumerate}

\end{block} 

\end{column}%2 



\begin{column}{0.27\linewidth} {\textbf{\underline{Reg. Routines}}}

%Block 3-1
\begin{block}{\small \textbf{\underline{Regular Routines}} }
\underline{\textbf{Morning}}
\begin{itemize}
\item \tiny Brush Teeth \timeEst{4 mins}
\item \tiny Mouthwash, Clean tongue - it helps with breath\timeEst{1mins} 
\item \tiny Eating small breakfast
\item \tiny Check your schedule for meetings / appointments for that day: Is anything urgent? \timeEst{5 mins}
\item \tiny Excercise: 1 hour ( Stretch for 10 mins, Treadmill for 30 mins , Lift weights or Yoga 1 hour, Meditation for 10 mins)
\item \tiny Shave (at least every other day) \timeEst{5 mins}
\item \tiny Shower : (shampoo+conditioner, acne wash,  soap on underarms/underbody)
\timeEst{10 mins}
\item \tiny dry hair, dry face, arms, legs, back, stomach \timeEst{3 mins}
\item \tiny Clothing: belt, check collar, shirt not half-tucked, matching socks \timeEst{5 mins}
\item \tiny Comb hair, hair gel optional \timeEst{ 1 min}
\item \tiny Check Keys/Wallet/Cell/Badge (get a bucket) \timeEst{1 min}
\item \tiny Open meds cabinet, get water, take medicines \timeEst{1 min}
\item \tiny Wear lenses and rinse out case \timeEst{ 2 mins}
\item \tiny Deodorant or cologne depending on the day \timeEst{1 min}
\item \tiny Wash your face with a face wash - it helps with acne \timeEst{3 mins}
\item \tiny Moisturize - apply lotion \timeEst{ 2 min}
\item \tiny Neti pot / clean out sinuses - if you’re feeling congested \timeEst{5 min}
\item \tiny clean out ears, nose \timeEst{5 mins}
\item \tiny Remember to lock door \timeEst{1 mins}
\end{itemize}

\underline{\textbf{Evening}}

\begin{itemize}
\item \tiny Call family: 30 mins
\item \tiny meet friends: 20 mins
\item \tiny Cleaning dishes / cleaning house: 10 mins
\item \tiny Lay out clothes for the next day, iron if necessary
\item \tiny start laundry if needed: 10 mins,
\item \tiny Collect anything you’ll need for the next day (e.g. dry cleaning to drop off): 5 mins,
\item \tiny Check Facebook/linkedin/google+: 10 mins, matrimony stuff: 10 mins,
\item \tiny Food for lunch/dinner the next day: 10 mins
\end{itemize}

\underline{\textbf{Night before bed}}
%TODO: why isn't enumerate working???
%\begin{enumerate}
\begin{itemize}
\item \tiny Finish computer stuff \timeEst{5 mins}
\item \tiny Get into sleeping clothes \timeEst{1 mins}
\item \tiny Before sleeping: brush teeth, floss \timeEst{ 2 min}
\item \tiny Properly wash and put away contacts \timeEst{ 2 mins}
\item \tiny Review the days good things \timeEst{ 10 min}
\item \tiny Light Reading \timeEst{ 10 min}
\item \tiny Prayer \timeEst{10 mins}
%\end{enumerate} 
\end{itemize}
\end{block}

\end{column}%3 

\end{columns} 

\end{frame} 

\end{document}
