\\documentclass[11pt]{article}

\usepackage{ulem}
\usepackage{color}
\usepackage{xspace}
\newcommand{\bllt}{\item \small}
\newcommand{\doneTask}[1]{\item \sout{#1}}
\newcommand{\doneTaskHyp}[1]{\item \textcolor{blue} {\sout{#1}}}
\newcommand{\optTask}[1]{\item  \textcolor{green}{#1}}
\newcommand{\prioTask}[1]{\item  \textcolor{red}{#1}}
\newcommand{\timeEst}[1]{\textit{#1}}
\newcommand{\dueBy}[1]{\textit{#1}}
\newcommand{\MyName}{Vivek~Kale}
\newcommand{\fixme}[1]{\textcolor{blue}{[FIXME: #1]}}
\newcommand{\revision}[1]{\textcolor{blue}{[FIXME comment : #1]}}
%Note:  consider weekly schedule template

\begin{document}
\underline{\textbf{Week of Dec. 20th}}
\textbf{\textit{Sunday}}
\begin{enumerate}
\item
\item
\item
\end{enumerate}

\textbf{\textit{Monday}}
\textbf{todo}
\begin{enumerate}
\item Implementation for variation of task sizes \timeEst{1 hour}
\item Dequeue overhead in static fraction variation graph - implementation \timeEst{30 mins}
\item Dequeue overhead in static fraction variation graph - data \timeEst{30 mins}
\end{enumerate}

\textbf{schedule}
\begin{itemize}
\item 10:00AM - 11:00AM : apt stuff
\item 11AM - 4PM : sched org, make to do
\item 5-6PM: finish status updates for everyone \timeEst { 1hour}
\item 6-10PM: work on graphs
\end{itemize}
\textbf{\textit{Tuesday}}
\textbf{todo}
\begin{enumerate}
\item finish receipts and reimbursement stuff \timeEst{2 hours}
\item send Prof Gropp email about quitting \timeEst{20 mins}
\item send everyone email about project ideas \timeEst {10 mins}
\item finish dequeue overhead code \timeEst{1 hour}
\item Add plot of dequeue overhead in graph \timeEst{1 hour}
\item Get histogram of slack timings \timeEst{1 hour}
\item Get histogram of iteration timings \timeEst{ 1 hour}
\end{enumerate}

\textbf{schedule}
\begin{itemize}
\item 9:00AM - 10:00AM : meeting
\item 1PM - 2PM :
\item 7:30PM - 8:30PM : toastmasters berkeley
\item 4:30 - 6:00PM :  go to party
\item 10:00PM - 10:30PM : go back to Livermore, get rental
\end{itemize}

\textbf{\textit{Wednesday}}
\begin{enumerate}
\item fix Amanda's pthread code to assign values into the variables \timeEst{1hour}
\item add in code
\item finish situations list
\item finish work org
\end{enumerate}

\textbf{schedule}
\begin{itemize}
\item 9AM - 10AM :  pack
\item 10AM -11AM : figure out getting back to Chicago, plan getting to
airport
\item 3PM - 4PM: work with Amanda
\item 4:30PM - 5:30PM :  meet with people
\item 5:30PM -6:30PM :  look at email
\item 6:30PM -7:30PM :  yoga and possibly work
\item 7:30PM - 8:30PM : make fixes to code/data for static fraction,  get model done
\item 8:30PM - 9:30PM : send updates on fixes
\item 9:30PM - 10:30PM : fix code of Amanda's
\end{itemize}

\textbf{\textit{Thursday}}
\begin{enumerate}
\item add in runs for 1024 nodes.
\item add in data for percentage outliers as we increase scale for static, dynamic,
uSched and slack-conscious.
\item Put in model into slides.
\item Add in the slack-conscious scheduling label.
\end{enumerate}

\textbf{schedule}
\begin{itemize}
\item 9AM - 10AM :  pack
\item 10AM -11AM : figure out getting back to Chicago ,  plan getting to
airport
\item 3PM - 4PM : work with Amanda.
\item 4:30PM - 5:30PM: meet with people.
\item 5:30PM -6:30PM:  look at email.
\item 6:30PM -7:30PM:  yoga and possibly work.
\item 7:30PM - 8:30PM: make fixes to code/data for static fraction, get model done
\item 8:30PM - 9:30PM : send updates on fixes
\item 9:30PM - 10:30PM : fix code of Amanda's
\end{itemize}
\textbf{\textit{Friday}}
\begin{enumerate}
\item send Prof Gropp an email  \timeEst{1.5 hours}
\item fix slack stuff, add histogram
\item go through code,  send Amanda an email \timeEst{2 hours}
\item
\item
\end{enumerate}

\textbf{\textit{Saturday}}
\begin{enumerate}
\item put shared memory extensions of dot product  \timeEst{1 day}
\item excercise
\item Additional graphs in paper (dequeue overheads, noise histograms)
\item
\end{enumerate}
\newpage
\textbf{schedule}
\begin{itemize}
\item 10AM -11AM : figure out getting back to Chicago, plan getting to airport
\item 2PM - 3PM : work out
\item 3-3:30PM : get library books on Organization,
\item 3PM - 6PM: get additional graphs added (go through paper)
\item 6PM - 8:30PM: work on Amanda's code, add shared mem. extensions
\item 8:30PM - 9:30PM : dinner
\item 9:30PM - 10:30PM : plan out weekend, tomorrow's sched.
\item 10:30PM - 11PM : emails (Varada Bal)
\end{itemize}

\end{document}
