%Note:  consider weekly schedule template

%TODO : figure out how to schedule urgent and important tasks


{\huge{\underline{\textbf{Week of March 12th}}}} \\

\textbf{Summary:} This is the weekly planning document. To create
this, first look at weekly routines and make sure they are here. Then,
look at the yearWeekPlan doc, along with project plan doc, and iPhone
todo list, and divide tasks across days of the week. Then, put this
into the schedule.

After this is done, these items should be checked in the work and
work+life calendar, and verified through email.
Then, they should be put in the work + life
calendars. \\

\textbf{Clothing Prep: } \\
Note: think about making dress code for situations
\begin{enumerate}
\item \textbf{Monday}: standard tshirt + jeans
\item \textbf{Tuesday}: standard red polo shirt + jeans
\item \textbf{Wednesday}: simple  blue shirt + jeans
\item \textbf{Thursday}: Regular red + jeans
\item \textbf{Friday}: Full blue shirt , jeans
\item \textbf{Saturday}: formal wear
\item \textbf{Sunday}: lounging around wear
\end{enumerate}

\textbf{Worries to watch for} \\
\begin{enumerate}
\item seeing another person
\item ex-
\item New Years text
\item email to Vk
\item what will bronis say
\item stress about worklife
\end{enumerate}

\textbf{Current habits}\\
\begin{itemize}
%\item dinner etiquette
%\item make sure eye contact not shifty
%\item avoid facebook / social media urge
%\item no cell phone
\item avoid bodily noises
%\item walk in straight line without feet scrubbing floor
%\item get reg routines down
\item back straight
\item lips relaxed
\end{itemize}

\textbf{Practice Points}\\
\begin{itemize}
\item \textit{\textbf{Note:}} figure out how to organize and do this
\item go through goals from top down to get schedule
\end{itemize}

\textbf{Spaces Org: do this every Saturday }
\begin{itemize}
\item code folder
\item organization folder
\item email folder
\item iPhone items
\item desktop
\item backpack
\end{itemize}

\underline{\textbf{situations}} \\
\begin{enumerate}
\item Flight from SF to Chicago: Pre- : Wear nice shirt with sweater, estimates of time, print boarding pass,  Post-: pay attention at important points during trip, don't have to lie to attendant.

\item Talk to Natasha:  Pre-:    Post-:  good on connecting to Doonya,
iAmSoNervous showed that you listened to her and it got to the point
concisely along with adding humour(note that she didn't laugh a lot,
indicating that this might be somewhat normal back-and-forth that
people already are somewhat skilled at - ).


\item  Flight to New York : Pre-: check-in early, print boarding passes, plan trip after you land, figure out where to stay Post: good to keep others updated, don't get so bothered by other stuff, get laptop out and plan what you're going to do 

\item Flight back from New york: Post-: can explain better the plan to Atul, watch out for people's space, don't bump into them , eat less 

\item Talk to Divya : Pre-:  talk about new york plans, tell her craziness that's been going on, talk about running and marathon interest, and whether you can go backwards in marathon, running marathon in bikini ,  Post-: 

\item Meet with Divya: Pre-: send plan   Post-: don't have to talk about BMW too much, make sure timing is good in morning, read signals to get closer, good to try different versions out of Vivek (european), good to talk about life, think about texts to send. , have good time estimates, don't have to say to come with, good to talk about marathon, try to fit in running sometime

\item Talk to Sneha: Pre-:   Post:  can get timings right better, talk about scary movies less, be sure to have a plan on what to talk about.

\item Meet with Prof Gropp on Tuesday:  Pre-: dress properly, write down plan  Post-:  explained first part well, could explain second idea well so you don't get confused in the discussion later on (practice explaining the idea, come prepared) , good facial expressions and vocal variety.

\item Meet with Maria on Wednesday:

\end{enumerate}

\underline{\textbf{\textit{Monday}}}\\
\underline{\textbf{todo}}\\
\begin{enumerate}
\item Finish writing the essay \timeEst{1 hour per day }
\end{enumerate}

\underline{\textbf{schedule}}\\
\begin{itemize}
\regItem{7:00AM - 8:00AM: running}
\regItem{9:00AM - 10:00AM : regular routines for morning}
\regItem{5:00PM - 6:00PM : send out email to everyone on notes for meeting}
\regItem{9:00PM - 10:00PM : regular routines for night}
\end{itemize}

End goal: Bronis should not bother me, Todd should not bother me. We should have bi-weekly meetings.
I should work every week towards a goal of EuroMPI paper. Torsten should no longer be involved.
Bill should guide me towards a November graduation.

\underline{\textbf{\textit{Tuesday}}}\\
\underline{\textbf{todo}}\\
\begin{enumerate}
\item finish all minor revisions

\item write up cost function, write up engineering design  \priority{I}
\item write code for Amanda
\item
\item check for VPN account access \timeEst{10 mins}

\end{enumerate}

\textbf{Tuesday facebook post: } The actual innovation has already been done in Computer Science.
This doesn't solve an imminent problem in society. This generates controversy.
Controversy brings up attention. Attention makes people interested in trying it out.
And generating controversy is exactly how tech startups can be important again.

\underline{\textbf{schedule}}\\
\begin{itemize}
\regItem{7:00AM - 8:00AM: weights}
\regItem {8:00AM - 9:00AM: regular routines for morning}
\regItem {9:00AM - 10:00AM: meeting}
\item 11-12AM :  summarize meeting, make plan for paper , prep for TM

\item 1:30PM-6PM: work on code, to get codes
\item 4PM - 5PM : meet with Prof Gropp
\item 8-8:40PM :  do win friends influence people reviews
\item 8:45PM - 9:30PM:
\item 9:30PM -10PM : weekend planning
\regItem {9:30-10PM: fb social, linkedIn social}
\regItem {10:00PM - 10:30PM: regular routines for night}
\end{itemize}

\underline{\textbf{\textit{Wednesday}}}\\
\underline{\textbf{todo}}\\
\begin{enumerate}
\item write up reasons for leaving livermore to Bronis \timeEst{10 mins} \priority{IU}
\item send Prof Gropp email about planning on how to do things \timeEst{10 mins} \priority{UI}
\item look at Amanda's code briefly, fix the icrev part  \timeEst{10 mins}  \priority{I}
\item make long-term definition for the next four weeks.
\item think about work life application (weekPlan curr)
\item think about work life application (how to write a letter)
\item putting worklife together \timeEst{}
\item work on revising writup for Prof Gropp
\end{enumerate}

\underline{\textbf{schedule}}\\
\begin{itemize}
\regItem{7:00AM - 8:00AM: running}
\regItem{8:00AM - 9:00AM: regular routines for morning}
\situationItem {1:30PM -2PM : meet with Maria Garzaran}
\regItem{10:00PM - 10:30PM: regular routines for night}
\end{itemize}

\underline{\textbf{\textit{Thursday}}}\\

\underline{\textbf{todo}}\\
\begin{enumerate}
\item talk to Bronis about post-doc opportunities, plan to graduate \priority{UI-high}
\item review Heidelberg essay \priority{U}
\end{enumerate}

\underline{\textbf{schedule}}\\
\begin{itemize}
\regItem{7:00AM - 8:00AM: weights}
\regItem{8:00AM - 9:00AM: regular routines for morning}
\regItem {10AM -11AM : DEG meeting}
\regItem {11AM - 11:30AM : work admin stuff}
\item 11AM - 12PM :
\item 1PM - 4PM: Amanda's code lookover
\item 11PM - 12PM: packing , checkin to flight
\regItem{10:00PM - 11:00PM: regular routines for night}
\end{itemize}

\underline{\textbf{\textit{Friday}}}\\
\underline{\textbf{todo}}\\
\begin{enumerate}
\item add in code for pthreads in Amanda's code for stream \timeEst{2 hours} \priority{I}
\item work on locality in static section \timeEst{10 mins}
\item do analysis of win friends and influence people, remaining chapters section 3 \timeEst{10 mins}  \priority{UI}
\item summarize first chapter of emotional intelligence book \timeEst{10 mins}
\item conversation analysis book \timeEst{10 mins each day}
\item time management book, go through time management tips \timeEst{10 mins}
\item get glasses
\item get meeting with Prof Gropp
\end{enumerate}

\underline{\textbf{schedule}}\\
\begin{itemize}
\regItem{7:00AM - 8:00AM: running}
\regRoutineItem {8:00AM - 9:00AM: regular routines for morning}
\regItem{10AM - 11AM : HPC group meeting}
\item 6PM - 7PM : talk to Sneha
\regItem{9PM - 9:30PM :  situations analysis}
\regItem{9:30PM - 10PM :  lookup clothes for next week}
\regRoutineItem{10:00PM - 11:00PM: regular routines for night}
\end{itemize}

\underline{\textbf{\textit{Saturday}}}\\
\underline{\textbf{todo}}\\
\begin{enumerate}
\item excercise
\item do re-imbursements
\item summarize the style guide, last part \timeEst{10 mins}
\item do analysis of win friends and influence people 2 chapters \timeEst{10 mins}
\end{enumerate}

\underline{\textbf{schedule}}\\
\begin{itemize}
\regItem{7:00AM - 8:00AM: yoga sculpt}
\regRoutineItem {8:30AM - 9:30AM: regular routines for morning}
\regItem{9:30AM - 10:30AM: Spaces maintenance}
\situationItem 12PM - 1PM:
\item 6PM - 8:30PM:
\item 8:30PM - 9:30PM : dinner
\item 9:30PM - 10:30PM :
\regItem{10:00PM - 11:00PM: regular routines for night}
\end{itemize}

\underline{\textbf{\textit{Sunday}}}\\
\underline{\textbf{todo}}\\
\begin{enumerate}
\item summarize the style guide \timeEst{10 mins}
\item do analysis of win friends and influence people 2 chapters \timeEst{10 mins}
\end{enumerate}

\underline{\textbf{schedule}}\\
\begin{itemize}
\regItem{7:00AM - 8:00AM: weights + running + meditation }
\regRoutineItem {8:00AM - 9:00AM: regular routines for morning}
\item
\item 7-8PM: plan out refine yearweeksPlan for the next month
\regItem{8-9PM:  plan out week in week Plan curr}
\regRoutineItem{10:00PM - 11:00PM: regular routines for night}
\end{itemize}

\newpage

