\documentclass[serif, mathserif, final]{beamer}
\mode<presentation>{\usetheme{Lankton}}
\usepackage[orientation=landscape,size=a0,scale=1.6, debug]{beamerposter}
\usepackage{amsmath,amsfonts,amssymb,pxfonts,xspace}
\usepackage{graphicx,ragged2e,pgffor}
\usepackage{hyperref}
\usepackage{ulem}
\usepackage{courier}
\usepackage{caption,verbatim,listings,float,subfig} %TODO: order these 
\setbeamertemplate{caption}[numbered] 
\usepackage{calendar}
\usepackage{geometry}

%TODO: remove unneeded items 
\newcommand{\bllt}{\item \small}
\newcommand{\doneTaskNoItem}[1]{\sout{#1}}
\newcommand{\doneTask}[1]{\tiny \item \tiny \sout{#1}}
\newcommand{\doneTaskHyp}[1]{\tiny \item \tiny \textcolor{blue} {\sout{#1}}}
\newcommand{\optTask}[1]{\tiny \item \tiny \textcolor{green}{#1}}
\newcommand{\prioTask}[1]{\tiny \item \tiny \textcolor{red}{#1}}

\newcommand{\timeEst}[1]{\textit{TimeEst:}\textit{#1}}
\newcommand{\te}[1]{\textit{TimeEst:}\textit{#1}}
\newcommand{\deadline}[1]{\textit{Deadline:}\textit{#1}}
\newcommand{\dueBy}[1]{\textit{Deadline:}\textit{#1}}
\newcommand{\dl}[1]{\textit{Deadline:}\textit{#1}}
\newcommand{\priority}[1]{\textit{Priority:}\textit{#1}}
\newcommand{\prio}[1]{\textit{Priority:}\textit{#1}}
\newcommand{\pr}[1]{\textit{Priority:}\textit{#1}}

\newcommand{\MyName}{Vivek~Kale}
\newcommand{\fixme}[1]{\textcolor{blue}{[FIXME: #1]}}
\newcommand{\revision}[1]{\textcolor{blue}{[FIXME comment : #1]}}
\newcommand{\regItem}[1]{\item \textcolor{cyan}{#1}}
\newcommand{\regRoutineItem}[1]{\item \textcolor{green}{\textit{Reg. Routine:} #1}}
\newcommand{\situationItem}[1]{\item \textcolor{magenta}{\textit{Situation:} #1}}
\newcommand{\comments}[1]{}

%TODO: consider changing the below so you only use the text in the
%document 


%TODO: change Week plans 

\newcommand{\footleft}{Mgmt-WorkLife-weekPlan} % figure what this should be 
\newcommand{\footright}{August 2016}
%-- Main Document ------------------------------------------------- 
\title{Month-Week-Day Plan}\author{Vivek Kale$^1$}\institute{$^1$ 
University of Illinois at Urbana-Champaign}\date{\today}
%TODO: get rid of extra numbers below

\begin{document}
\begin{frame}
\begin{columns}
\column{1.0\linewidth} 

\begin{block}{Projects}
{\bf Work:code: Project - Coding practice: p for interview.}
\begin{enumerate}
\tiny \item \tiny Work:code(cp.bm): finish bit manipulation from book
+ Work:code(cp.bm): finish bit manipulation: finish problem 5 from
book + Work:code(cp.bm): finish bit manip: fk 
\doneTask{Work:code(cp.bt): review brainteasers – 1 day} 
\tiny \item \tiny Work:code(cp.bm): finish bit manip +
Work:code(cp.bm): finish bit manip: finish problem 5 from book +
Work:code(cp.bm): finish bit manip: finish problem 6 from book +
Work:code(cp.bm): finish bit manip: finish problem 7 from book +
Work:code(cp.bm): finish bit manip: finish problem 8 from book + 
Work:code(cp.bm): finish bit manip: finish problem 9 from book + 
Work:code(cp.bm): finish bit manip: finish problem on 
\item \tiny Work:code(cp.bmpie): do graphics problem from bit manip: rectangular overlap. 
\item \tiny Work:code(cp.bmpie): do big endian vs. little endian := 
\item \tiny Work:code(cp.bmpie): number of ones := 
\item \tiny Work:code(cp.bmpie): code up bit manip problems :=  
\item \tiny Work:code(cp.bt): finish brain teasers:  finish problem on
  egg drop from book.
\item\tiny Work: code(cp.bt): talk about and write 100 lockers. 
\item \tiny Work: code(cp.bt): finish brain teasers: finish problem on heavy pill. 
\item \tiny Work:code(cp.btpie): finish brain teaser problems from programming interviews exposed. 
\item \tiny Work:code (cp.): go through C++, Work:code (cp.): go
  through Java + Work:code (cp.): go through OOP. 
\item \tiny Work:code (cp.): code up problems.  – 1 week.
\item \tiny Work:code (cp.): integer problems + numerics   -- 1 week. 
\item \tiny Work:code (cp.): practice mock interview problems. – 1 week. 
\doneTask{ Work:code (cp.): finish recursion + BFS/DFS – 1 week. 
Work:code(cp.): finish recursion, Work:code(cp. ): code up problems,
Work(cp.): practice mock interview problems.}
\end{enumerate}
\textit{Schedule:} Work:code (cp.): finish bit manipulation, Work(cp.): review
brain teasers in book, Work(cp.): Work(cp.): go through C++.\\
{ \bf Project: job talk prep} 
\begin{enumerate} 
\tiny \item \tiny 
\item \tiny 
\end{enumerate} 


{\bf Work:code: Project - Research Paper:}  
\begin{enumerate} 
\item \tiny \url{http://mpp2016.ime.uerj.br}. 
\item \tiny \url {http://sbac-pad}  - registration is  \$ 500. 
\item \tiny Put up latex.  
\item \tiny Gather all research. 
\item \tiny Gather project work. 
\item \tiny Write down introduction.
\item \tiny Gather data for OpenACC. 
\item \tiny Explain other details of setup. 
\item \tiny Note data for OpenMP. 
\end{enumerate} 
\textit{Schedule:} March 24th: do latex, March 2

{\bf Work:rel: Project – interview with Berkeley/MIT/industry} 
\begin{enumerate} 
\tiny \item \tiny Business cards:  - use latex  -- 40 minutes. 
\tiny \item \tiny Cover letter 
\tiny \item \tiny Jobs categorization for real jobs opportunities: 
Suny sb / suny sb / LLNL /  |  Intel, NVIDIA, Apple  Google/ms /
software companies, Database companies/Oracle,  --> real companies 
\tiny \item \tiny CV: + Research Summary:  -- 1 week.  - Talking about
  your research.
\item \tiny Work:rel: message to Yavatkar Kaka about VMWare +
  Work:rel: gather friends in network from friends about Google +
  Work:rel: message to contacts about Microsoft \te{} \dl{} \pr{}. 
\item \tiny Behavioral questions answers:    -- 1 week. 
\item \tiny Send emails – 1 day. 
\item \tiny Structure in latex. 
\end{enumerate}  
\textit{Schedule:} Behavioral answers – 1 week, CV prep - 1 day,
business cards, cover letter -1 hour. 


{\bf Project: awards}
\begin{enumerate} 
\tiny \item \tiny Figure out write-up for Fulbright. 
\item \tiny Attend Fulbright : 
\item \tiny Stay in touch with HLF 
\item \tiny Do energy econ work with convergence. 
\item \tiny Go to whitehouse thing. 
\item \tiny Plan to be on Program Committee of .. 
\end{enumerate} 
\textit{Schedule:} April 15th: message to Stephen – 1 hour,
Work:rel:Project – Awards: 

{\bf Mgmt:Spaces: settle on your own} 
\begin{enumerate}
\item \tiny Dentist + Get dentist appointment.
\item \tiny Doctor / Counselor + CBT.
\item \tiny Health insurance.
%TODO: organize and group the below 
\item \tiny Reimbursements.
\item \tiny Work pay and holidays / hours. 
\item \tiny 401k+retirement  + fidelity + bank (money owing). 
\item \tiny apartment + apartment sublease + apartment rent.
\item \tiny Flights: update flight information, e.g., credit card,
  emergency contact, passport number.
\item \tiny Flights: finish flight decision making notes, e.g.,
  justification for travel, money/airfare rules, award travel rules. 

\item \tiny Change Chase address. 
\item \tiny apartment sublease. 
\item \tiny renter's insurance. 
\item \tiny xfinity and wifi accounts. 
\item \tiny ComEd. 
\item \tiny car insurance 
\doneTask{car parking} 
\item \tiny Car city sticker. 
\doneTask{Ventra card.}
\item \tiny Car: Get windows side checked + Get windows marking checked + Get tailpipe checked + Ask about warranty. 
\end{enumerate} 

{\bf Worklife - Project – Comm:rel: } 
\begin{enumerate} 
\tiny \item \tiny Worklife: link management together.  
\item \tiny Worklife: link habits comm and Toastmasters. - done
\item \tiny Worklife: latex viewpoint. 
\item \tiny Comm: read social intelligence first four chapters.
\item \tiny Comm: link all comm together.
\item \tiny Worklife: get emails and texts to analyze. 
\item \tiny Worklife: figure out how to book flights and trips quickly. 
\end{enumerate}
\textit{Schedule:} Comm: read social intelligence first four chapters
and get a method to take in information – 5 hours. 
Comm: link comm together, worklife: latex viewpoint. Looking ahead:  


{\bf Project: GenKnowledge:}
House of cards:
Mgmt:Spaces:
1. Cars.  Work:rel: -  Project – Comm: rel: 
\doneTask{Comm:rel: meet others:  Sweta K. 
{\it Schedule:} meet others over summer, meet girl over summer.

{\bf Project: Comm} 
\begin{enumerate} 
\item \tiny Comm: message to Mona and Leena \te{10 minutes}  := 
\item \tiny Comm: consider view of girl on Shaadi. 
\item \tiny Comm(ren): message to Michael :=  Comm(ren): message to
  Rishi and Chris and Amaeya about meeting. 
\item \tiny Comm: meet Gary and KD \te{10 minutes}.  
\doneTask{Comm: message to Kavita}  \te{1 hour} \dl{Thursday} \pr{} 
\end{enumerate}

{\bf Project: Comm:rel} 
\begin{enumerate} 
\item \tiny Comm: get caught up with Matrimony and Shaadi, Use match, make system
  for meeting. 
\item \tiny Comm:rel: discuss with Mom and Dad. 
\end{enumerate} 
\end{block} 

\begin{block}{Planning} 
\underline{\textit{2-month plans}}
\underline{\textit{January and February:}}
\underline{\textit{March and April:}} 
\underline{\textit{May and June:}}
\begin{itemize}
\tiny \item \tiny do scheduling strategies. 
\item \tiny work on job talk. 
\item \tiny do travel. 
\item \tiny social on facebook, catch up with Rishi. 
\end{itemize} 

2-Month Plan: December: code + worklife, January: study for interviews,  \\
2-Month Plan: February: code | March:  code + interview review + finish coding work.    \\ 
2-Month Plan: April: code, May: code paper review. \\
2-month plan: June: relax July: adjust \\ 
2-month plan: August:  prep September: interview \\
\end{block} 

\bf{Week of August $1^{st}$, 2016:} \\
\begin{itemize} 
\tiny \item \tiny Work: write up SBAC. 
\item \tiny Work: write up  cover letter. 
\item \tiny Work: finish lectures up to BFS, DFS. 
\item \tiny Work: finish coding problems on C++. 
\end{itemize} 

\bf{Week of August $7^{th}$, 2016:} \\
\begin{itemize} 
\tiny \item \tiny Work: write up SBAC. 
\item \tiny Work: write up  cover letter. 
\item \tiny Work: finish lectures up to BFS, DFS. 
\item \tiny Work: finish coding problems on C++. 
\item \tiny Comm: review win friends Inf people review + Comm: do one
  lesson with Social Intelligence thoroghly. 
\end{itemize} 

\bf{Week of August $14^{th}$, 2016:} \\ 
\begin{itemize} 
\tiny \item \tiny Work: review lectures for shortest path. 
\item \tiny Mgmt:Spaces: 
\tiny \item \tiny Work: review lectures + Work: do practice problems.
\end{itemize}

\bf{Week of August $24^{th}$, 2016:} \\
\begin{itemize} 
\tiny \item \tiny Work: review lectures. 
\item \tiny Comm: review win friends Inf people. 
\item \tiny Comm: read social intelligence chapter 2 
\item \tiny Comm: read social intelligence Chapter 4. 
\end{itemize} 

\underline{\textbf{Weekend Plans:}}
\textbf{Weekend of August $5^{th}$ -$7^{th}$ : } Meet mom and Dad.
\textbf{Weekend of August $12^{th}$ - $13^{th}$:} Go to San Francisco.
\textbf{Weekend of August $20^{th}$ - August $22^{nd}$:} Mom  and Dad
Visit, send message to Mona and Leena 
\textbf{Weekend of August $31^{st}$  to September $2^{nd}$ } Chicago summer. 

\underline{\textbf{Upcoming situations:}} re-union, Sangita's
wedding. 

\underline{\textit{Month Plan}:}  Work: do writing of papers, Work: do
coding problems on databases and software engineering, Work: do social
intelligence notes}

\end{block}
\end{columns}
\end{frame}


\begin{frame}
  \begin{columns}
    %-- Page 2: Column 1 --------------------------------------------------- 
    \begin{column}{0.25\linewidth} %{\textbf{\underline{Week Aspects(new name)}}}
      %TODO: check where this should go. -done
      %--- Page 2: Block 1-1
      \begin{block}{Routines}
        
      \textbf{\underline{Sunday Routines:}} Experiences, week plan. \\ 
      \textbf{\underline{Routines:}} Morning: bfast, exercise/brush,
      floss, shower (hair, eyes, ears, underarms, feet), meds, belt,
      comb hair / dishes, clean kitchen floor. |  Night: running/ put
      away dishes, clean kitchen floor / brushy teeth, charge phone,
      clothes for tomorrow, contacts off. \\
  
      \begin{itemize}
      \item \tiny ppn:028361799  exp: driver's license:K400-8728-4051  exp:2-20-18 
      \item \tiny CC1 num: CC2 num: Dbtnum:  bank acct num:  
      \item \tiny VIN:    License Plate:  E61 2444    Atul's lic: P84  
      \item \tiny Parking location codes:   Parking signs: 
      \item \tiny VivekInternet’s FightingIllini  wifi pass: 2173900374 WPA 
      \item \tiny xfinity account number: 0149024144. 
      \item \tiny AAdvantage number: 847JJP0.
      \item \tiny Dad's AAdvantage number: BRU6630 Password: polarwind.
      \item \tiny Emerald Club number :  140294615   pass:  
      \item \tiny Netflix use
        r:  lvk2408@gmail.com  Netflix password: chitrapat. 
      \end{itemize}
      \end{block}

      \end{block} 
%--- Page 2: Block 1-3
      \begin{block}{Local Happiness}
        % howto:Recognize emotions / recognize (precisely) what you're
        % worried about -> methods for eliminating worry. 
        % clean out old worries, put them in pastWorries doc.  
        % remember to define precisely 
        % order from top-to bottom
        \begin{itemize} 
          \tiny \item \tiny Work: worrying about interviewing: just focus on the work. 
        \item \tiny Worrying about gal: think about talking to others. 
        \end{itemize}
      \end{block} 
      %--- Page 2: Block 1-4 
      \begin{block}{AngersAndAnxieties}
        % howto:Recognize emotions / recognize (precisely) what you're worried about -> methods for eliminating worry. 
        % clean out old worries, put them in pastWorries doc.  
        % remember to define precisely 
        % order from top-to bottom
        \begin{itemize}
          \tiny \item \tiny Anger about UP -> think about the positive
            perspective, and the original
          \item \tiny Anger about Mr. Kapoor ->  
          \item \tiny Work: worrying about interviewing: just
          focus on the work. 
          \item \tiny Anger about a b  -> ...
        \end{itemize}
      \end{block}
      %-- Block 1-5
      \begin{block}{Life notes}
        \begin{itemize}
        \tiny \item \tiny Social Intelligence: 
        \end{itemize}
      \end{block}
% howto: 
\end{column}

  %-- Column 2 ---------------------------------------------

\begin{column}{0.5\linewidth} 
      \begin{block}{Week Summary} 
        {\tiny \underline{\textbf{Week Plan}: } \tiny } 

Work: finish review of BFS and DFS 
Work: finish paper? 

Work: apply for jobs 
Work: cover letter
Work: write job talk  
COmm: message to Mona + Comm: message to Rishi 

        {\tiny \underline{\textbf{Weekend Plan:}} see Mom and Dad}

        {\tiny {\bf Week lessons:}}
        \begin{enumerate}
          \tiny \item \tiny Win Friends/ Influence People – no one
          likes to take direct orders.
        \item \tiny Go through 7 habits.
        \item \tiny Coding problem: 
        \item \tiny Chess tips: 
        \item \tiny tm tips.
        \end{enumerate} 

        
        {{\tiny \bf News:} M: iPhone, galaxy, Salesforce | S: bombings, emmy's | E: Fallon:  w:  }
        
      \begin{block}{Running TODO} % find a better name 
        \begin{enumerate} 
          
          \textbf{Curr} $\rightarrow$

      \item \tiny Work: review material you know already \te{2 hours}. 

      \item \tiny Work: how to organize a project \te{30
        minutes}\te{}\dl{}\pr{}. 
        
      \item \tiny Work: rel(cl): integrate vision document with goals
        document + Work:rel: gather Lawrence Scholar +  Work:rel:
        finish cover letter. 

      \item \tiny Work:rel: respond to EPFL \te{20 minutes}
        \dl{Saturday night}. 

      \item \tiny Work:rel: message to Professor Chapman \te{30 minutes} \dl{Wednesday} \pr{IU} 

        Dear Professor Chapman, 
        
        I'd like to add more about myself regarding the position. 
        Do you know if and when other positions open up?

        I have 3 or 4 research ideas that I'd like to
        publish. Ideally, I'd like to work elsewhere, e.g., 

        I have thought about Lawrence Berkeley Laboratory or Oak
        Ridge. Brookhaven is appealing to me because I can set my own goals
        and push them forward. 

        My goals is to push forward research ideas that Professor
        Gropp suggested during my postdoc position with him. 
 
        Long term, I'd like to become a software 
        engineer that can publish in conferences.

        Please give me a chance to interview again and to give a job
        talk for the other positions.

        Vivek 

    \item \tiny Mgmt:webpresence(webpage): update webpage front page =
      Mgmt:webpresence(wpg.lw): update the text lightweight self-adaptive
      loop = ( Mgmt:webpresence(wpg.lw): decide multicore +
      Mgmt:webpresence(wpg.lw): name for lightweight loop) +
      Mgmt:webpresence(wpg): omit PDF  + \doneTask{Mgmt:webpresence(wpg): take
      out global} +  Mgmt:webpresence(wpg): see if we should use a different term
      than scalability  + \doneTask{Mgmt:webpresence(wpg): change the word
      optimize to improve}  + Mgmt:webpresence(wbpg): change from 'I am
      interested' to 'I use' 
    \item \tiny Mgmt:webpresence(wbpg): add [Personal] and put in hobbies and interests there  + 
      Mgmt:webpresence(wsu): update description of work based on cover
      letter. 
      \item \tiny Mgmt:webpresence: update LinkedIn cover photo to
        picture of the globe \te{}\pr{}\dl{}. 
      \item \tiny Work:rel: make job landscape.  
      \item \tiny Work:rel: apply for companies.
      \item \tiny Work:rel: networking summary \te{10 minutes}. 
      \item \tiny Work:rel: review of interview \te{1 hour} \dl{}. 
      \item \tiny Work:rel: add in experiences \te{} \dl{}
      \item \tiny Mgmt:Spaces: check hair from \url{http://restorehair.com/contact-us/}. 
      \item \tiny Comm(soc): send message to Dad about social. 

      \item \tiny Work:rel(trp): make a template for replies to
        companies \te{1 hour} = Work:rel(trp): respond for times that
        work + Work:rel(trp): confirm timings for interview +
        Work:rel(trp): Thank You notes. 

      \item \tiny Comm: message to Labonee \te{1 hour} \dl{Sat. night}
        \pr{ImportantToMaintainContacts}.
        
      \item \tiny Mgmt:Spaces(crp): check car tailpipe +
        Mgmt:Spaces(crp): Window 

      \item \tiny Mgmt:Spaces(bfa): buy things for apartment =
        Mgmt:Spaces(bfa): buy a whiteboard. 

      \item \tiny Mgmt:Spaces(afx): tell about the closet door. \te{}
        \dl{}. 

        
      \item \tiny Mgmt:Spaces(grc): get groceries =
        Mgmt:Spaces(grc):Malt-O-meal + Mgmt:Spaces(grc): matches for
        candles + Mgmt:Spaces(grc): labels for organization of kitchen
        cabinets + Mgmt:Spaces(grc): labels for organization of fridge and freezer +
        Mgmt:Spaces(grc): labels for organization of bathroom. 
        \doneTaskNoItem{Mgmt:Spaces: explain wifi password.} 
        Mgmt:Spaces(grc): sheet for explaining where to come. 

      \item \tiny  Mgmt:Spaces(car): get halogen lights for fog lights
        \te{1 hour}. 
          
      \item \tiny Comm: consider a view of girl on Shaadi. 

      \item \tiny Mgmt:webpresence: update LinkedIn cover photo to picture
        of the globe \te{}\pr{}\dl{} 

      \item \tiny Comm: consider what to do about Bhavna. 
      \item \tiny Comm: consider talking to Illina. 
      \item \tiny Comm: talk to friends from high school.
      \item \tiny Mgmt:Spaces: plan trips. \te{}. 

      \item \tiny Mgmt:webpresence: cancel FB friend request of
        Jocelyn + Mgmt:webpresence: check other friend requests
        sent. \te{}. 

      \item \tiny Mgmt:Spaces(GetThingsSpring2016): get Things =
        Mgmt:Spaces(getThings): get suit. \te{}
 
      \doneTask{Mgmt:webpresence: delete Anil Taneja from
        LinkedIn. \te{1 hour} \dl{Monday} \pr{UI}. - not needed since
        we met with Rishi  + Comm: may have not accepted +
        Mgmt:webpresence: bad to do so} 


        \end{enumerate}
      \end{block}

      % howto: the below is a routine based on the job I'm doing and the
      % circumstances I'm in. Note that this is different from routines
      % above, which is true for a long-term period of over 10 years.  
      
      \begin{block}{Weekly routines} 
        \begin{itemize}
          \tiny \item \tiny 630 am: wake up, turn off alarm clock, brush teeth
        \item \tiny 645 am: eat breakfast
          715 am: lift weights
          730 am: look up weather, read emails
          800 am: watch algorithms lectures, review programming problems
          11 am : research stuff
          12 pm : eat lunch
          1 pm - 3 pm : programming
          3 pm - 5 pm : applications/emails/meetings/phone calls
          5 pm  - 6 pm : running
          6 pm  - 7:30 pm : dinner
          8 pm - 9 pm : talk to you and mom
          9 pm - 10:30 pm : finish emails
          10:30 pm - 11:30 pm : read books / articles on meditation or self-help.
        \end{itemize}         
        On weekends, I take care of chores and things I didn't finish during
        the weekday. 
      \end{block} 
      
      \begin{block}{Weekly Meetings}
        \begin{itemize} 
        \item \tiny IWOMP affinity meeting Thursday 7 AM PDT / 9 AM
          CDT call in: 805-639-779 pswd: places. 
          https://llnl.webex.com/llnl/j.php?MTID=m33950b76befb72c0cbc31ea2e3be720c  
        \item \tiny DEG group meeting.  
        \end{itemize}



\end{block} 
      
      \begin{block}{Week Daily Schedule} 
        {\bf Sun:} WOrk: finish summary,   WOrk: do paper ,
        Mgmt:Spaces: book flight, Comm: message about re-union ? 
        \newline {\bf Mon:}
        \newline {\bf Tues:}
        \newline {\bf Wed:}
        \newline {\bf Thur:} 
        \newline {\bf Fri:} 
        \newline {\bf Sat:} 
      \end{block} 
      
      % ------ Page 2: Column 3
      \begin{column}{0.25\linewidth}
        % ------ Block 2.3.1 
        
        \begin{block}{Food Plan} 
          \begin{itemize}
            \tiny \item \tiny 
          \item \tiny 
          \item \tiny 
          \end{itemize}
        \end{block} 
        
        \begin{block}{Weather}
          \begin{itemize}
            \tiny \item \tiny 
          \item \tiny
          \end{itemize}
        \end{block} 

      \begin{block}{Clothes plan} 
        \begin{itemize}
          \tiny \item \tiny Monday
        \item \tiny Tuesday
        \item \tiny Wednesday
        \item \tiny Thursday
        \item \tiny Friday
          \item \tiny Saturday
        \end{itemize} 
      \end{block}


      %-- Block 3-2 

%TODO: check where this goes: 
      \textbf{\underline{Day trip packing list:}} charger for iPhone, charger for laptop,
      car keys, underwear, black socks, shoes, meds, halls meds, greyhound,
      boarding pass, flight pass, directions to venue? \\ 

      \begin{block} {Birthdays}       
        \begin{itemize} 
        \tiny  \item \tiny Situation: wish Shalaka? 
        \item \tiny Situation: wish Avani 
        \end{itemize} 
      \end{block} 

        %-- Block 3-3 
      \begin{block}{Situations}
        % Summary: the below are the situations that define one
        % another.        
        % Howto: Put post notes of each situation from list of previous
        % week. Put high importance situations in situationslist. 
        % Put list of upcoming situations on Sunday morning with Pre. 

        \begin{itemize}
          \tiny \item \tiny Situation: Meet Mom and Dad:  coord:
          Pre-:  Post-: have topics to discuss, talk about plan
          beforehand- see time comittment, mention the work you need to do.  
      
          
        \item \tiny Situation: Talk to Anu:  Pre-:   Post-:  talk less
          about you, don't have to make statements that are logical 
 
        \end{itemize} 
      \end{block}
%Summary:  


\begin{block}
  Mgmt:webpresence:
  Researchgate, linkedIn, twitter, website, facebook
  Friends: Amit, Sangita, Anchit, Kevin.
  Rel: Sruthi
\end{block}

\begin{block}{Rel} 
  \begin{itemize} 
    \small \item \small  from SF. 
    \item \small Shwetha K 
    \item \small Mamta       
    \item \small SH11680694 from San Francisco. 
    \item \small Sandhya N. 22 Jun 2016 
    \item \small Aarti S - 27 - 5' 9'' Charlotte.       
    \item \small Anu M from Chicago, IL 
    \item \small Pranati A from Cleveland, OH - 
    \item \small Meghana K from New York - 
    \item \small Ssd S - 28 , 5 5 , Boston, MA 
    \item \small Anj B. - 30 yrs - SH13882555.
  \end{itemize} 
    %\small \item \small Meghan Joshi 

% Accept our apologies for the delayed response. We spoke to our son
% about your daughter and we are interested also. When is a good time
% for us to call you? 

\begin{itemize}
\item \small
  \url{http://profile.marathimatrimony.com/profiledetail/viewprofile.php?id=K658342&osa=dbos&memval=3&listtype=1&msgId=&rq=&loadPage=12&listtype=1&tabtype=16&filtertype=1&filtered=0&viewed=2&TotCnt=367&Show=Y&Module=} 
\item \small \url{http://profile.marathimatrimony.com/profiledetail/viewprofile.php?id=M3730924&osa=dbos&memval=1&listtype=1&msgId=&rq=&loadPage=13&listtype=1&tabtype=16&filtertype=1&filtered=0&viewed=0&TotCnt=367&Show=Y&Module=}
  
\item \small \url{http://profile.marathimatrimony.com/profiledetail/viewprofile.php?id=R1194547&osa=dbos&memval=4&listtype=1&msgId=&rq=&loadPage=11&listtype=1&tabtype=16&filtertype=1&filtered=0&viewed=3&TotCnt=367&Show=Y&Module=}
  
\item \small \url{http://profile.marathimatrimony.com/profiledetail/viewprofile.php?id=R1762507&osa=dbos&memval=6&listtype=1&msgId=&rq=&loadPage=1&listtype=1&tabtype=16&filtertype=1&filtered=0&viewed=5&TotCnt=367&Show=Y&Module=}

\item \small \url{http://profile.marathimatrimony.com/profiledetail/viewprofile.php?id=R1194547&osa=dbos&memval=4&listtype=1&msgId=&rq=&loadPage=11&listtype=1&tabtype=16&filtertype=1&filtered=0&viewed=3&TotCnt=367&Show=Y&Module=}

\item \small \url{http://www.shaadi.com/profile?profileid=SH13882555&ubt=L2luYm94L3BlbmRpbmcvcmVjZW50LWludGVyZXN0c3xpbmJveDo1YjhmMGM0ZTViMTM4YmU2ZjUxNDAzMTVlM2M4OWJhMnw4NDI3ZGVlYjMzMTg2MmUzMDc1N2E5Mjg0OGEyZjc2OQ\%3D\%3D&source=unified&evt_ref=aW5ib3gtaW50ZXJlc3Rz&datasrc=api}

\item \small \url{http://www.shaadi.com/profile?profileid=bSH74851794&ubt=L2luYm94L3BlbmRpbmcvcmVjZW50LWludGVyZXN0c3xpbmJveDo1YjhmMGM0ZTViMTM4YmU2ZjUxNDAzMTVlM2M4OWJhMnxlNzMxMWM0NmM2ODNjZmRhM2JlODY0NTQzMzIxODg5Mw\%3D\%3D&source=unified\&evt_ref=aW5ib3gtaW50ZXJlc3Rz&datasrc=api}

\item \small \url{http://www.shaadi.com/profile?profileid=ISH08025255&ubt=L2luYm94L3BlbmRpbmcvcmVjZW50LWludGVyZXN0c3xpbmJveDo1YjhmMGM0ZTViMTM4YmU2ZjUxNDAzMTVlM2M4OWJhMnwyMDJhNGVlNzk5NGI0MjlmZTliMTkwODQzMDQ5NDRmYg\%3D\%3D&source=unified&evt_ref=aW5ib3gtaW50ZXJlc3Rz&datasrc=api} 
\end{itemize} 
\end{block} 

\begin{block} 
Mgmt:webpresence: 
Researchgate, linkedIn, twitter, website, facebook 
Friends: Amit, Sangita, Anchit, Kevin. 
Rel: Sruthi 
\end{block} 
\end{column}%3 


%\begin{block}{Spaces}
%\begin{itemize} 
%\tiny \item \tiny 
%\item \tiny 
%\item \tiny 
%\end{itemize} 
%\end{block} 




\comments{
      \begin{block}{Week Daily Schedule} 
        % howto: arrange items from running todo into the below
        % sheet management document. 
        \begin{columns} 
          \column{0.14\textwidth}{\textbf{\small \underline{Mon}}}
          \textbf{\small todo} \\ 
          \begin{itemize}
            \tiny \item \tiny Add in schedule
          \item \tiny 
          \end{itemize} 
          \textbf{\small schedule} \\
          \begin{enumerate} 
            \tiny \item \tiny 8-9AM: Regular Routines 
          \end{enumerate} 
          
          \column{0.14\textwidth}{\textbf{\small \underline{Tue}}}
          \textbf{\small todo} \\
          \begin{itemize}
            \tiny \item \tiny Work: make project sheet \te{10 minutes} 
          \item \tiny Mgmt:Spaces: check for diploma \te{10 minutes} 
          \end{itemize}  
          \textbf{\small schedule} 
          \begin{enumerate}
            \tiny \item \tiny 10AM - 11AM = 
          \item \tiny 11AM - 12AM = make long-term goals 
          \item \tiny 12PM - 2PM = 
            \tiny \item \tiny 2PM -3PM = 
          \item \tiny 6PM - 10PM = 
          \end{enumerate} 
          
          \column{0.14\textwidth}{\textbf{\small {\underline{Wed}}}}
          \textbf{\small todo} \\
          \begin{itemize}
           \tiny \item \tiny Work: finish slides for tomorrow. 
           \item \tiny Mgmt: Spaces: update fb 
         \item \tiny Comm: fb update 
          \end{itemize}
          \textbf{\small schedule} \\
          \begin{enumerate}
            \tiny \item \tiny 8-9AM: Regular Routines 
          \item \tiny 9AM - 10AM: Send message 
            \item \tiny 6:30PM - 7:30PM = 
          \end{enumerate} 
          \column{0.14\textwidth}{\textbf{\small{\underline{Thu}}}}
          \textbf{\small todo}\\
          \begin{itemize}  
            \tiny \item \tiny 
          \item \tiny 
          \end{itemize} 

          \textbf{\small schedule}\\
          \begin{enumerate} 
            \tiny \item \tiny 8-9AM = Regular Routines 
            \item \tiny 12-1PM = gather notes about job org. during
              session 
            \item \tiny 3:30PM - 4:30PM = meeting 
            \item \tiny 6PM - 9PM = revise emot. int. chapter and
              structure wl-cheat based on it 
          \end{enumerate}  
          
          \column{0.14\textwidth}{\textbf{\small{\underline{Fri}}}}
          \textbf{\small todo}\\ 
          \begin{itemize}
          \item \tiny Work: code review. 
          \item \tiny Work: finish work. 
          \item \tiny Mgmt:Spaces: Haircut \te{10 minutes}. 
          \item \tiny Comm: check messages 
          \end{itemize}
          \textbf{\small schedule}\\
          \begin{enumerate}
            \tiny \item \tiny 8-9AM: Regular Routines 
          \end{enumerate}
           
          \column{0.14\textwidth}{\textbf{\small \underline{Sat}}}
          \textbf{\small todo}\\
          \begin{itemize} 
            \tiny \item \tiny
          \end{itemize}
          \textbf{\small schedule}\\ 
          \begin{enumerate}
            \tiny \item \tiny 7-7:30PM = food + organize.  
            \tiny \item \tiny 7:30 PM - 8 PM = 
            \tiny \item \tiny 8 PM - 9 PM = 
            \tiny \item \tiny 9:45 PM - 10:30 PM = go out 
            \tiny \item \tiny 2AM -3AM =  message Samir + add people
          \end{enumerate}
          \column{0.14\textwidth}{\textbf{\small \underline{Sun}}}
          \textbf{\small todo}\\
          \begin{itemize} 
           \tiny \item \tiny 
          \end{itemize}
          \textbf{\small schedule}\\
          \begin{enumerate} 
            \tiny \item \tiny 3PM - 4PM =  . 
          \item \tiny 5-7PM = Comm work. 
          \item \tiny 8PM - 10PM = worklife work. 
          \end{enumerate} 
        \end{columns}
      \end{block}
    \end{column}%2
}


\end{columns}
\end{frame}

    
\end{document}


% -- Attic -- % 

%        \begin{itemize}
%          \tiny \item \tiny If you do something sloppy, don't
%          think about it and don't say sorry. 
%        \item \tiny don't think someone is trying to hurt you if
%          they say something.
%        \item \tiny know the paths of least stress. 
%        \item \tiny if mom does something, don't let that bite you. 
%        \end{itemize}

\comments{

    %--- Page 2: Block 1-2
    \begin{block}{Map} 
      \begin{itemize} 
      \item \tiny driver's license  exp. date .  Number. 
      \item \tiny ppt number  exp. date.  
      \end{itemize}
      
      \begin{itemize} 
      \item \tiny bank account num 
      \item \tiny cc num 
      \end{itemize} 
      
      \begin{itemize} 
        \tiny \item \tiny Amtrak  eVoucher numbers. \\
      \item \tiny  Southwest credit:  \\   
      \item \tiny  Mileage number: \\ 
      \end{itemize} 
      
      \begin{itemize}
        \tiny \item \tiny VIN:  License plate: ill e61 2444  
      \item \tiny BT code for BMW:
      \end{itemize} 
      
      \begin{itemize} 
        \tiny \item \tiny other cars: lexus:  VIN:  license:
      \item \tiny Hyundai: 
      \item \tiny Audi: VIN:  License: P84  
      \end{itemize} 
      
      \begin{itemize} 
        \tiny \item \tiny Vivek's wifi:   wifi pass: 
        \item \tiny Atul’s FightingIllini  wifi pass:  2173900374 WPA  \\
        \item \tiny When tank light on, filling 13.3 gallons. 
      \end{itemize} 
      
      Local space: 
      Local map: 

      \textbf{\underline{Urbana-Champaign:}} 
        Campustown: 
        North: Engineering: 
        Main campus: 
        Southside of campus:         
        Urbana: 
        Champaign: 
        Savoy: 
        \textbf{CMI} 
        \textbf{Illini Terminal} 
        Decatur/Springfield: 
        Tuscola/Mattoon: 
        Rantoul/Paxton:  
        
        Cover letter / Resume : 5 hours .
        Behavioral questions : 
        Review what you know : 
    \end{block}

\underline{\textit{July and August:}} 
\begin{itemize}
\tiny \item \tiny Settle with interviews. 
\item \tiny Move-in to apartment.
\item \tiny Do papers.
\item \tiny Finish social intelligence 1 chapter. 
\item \tiny Finish 7 habits. 
\end{itemize} 

}
