%Note:  consider weekly schedule template

%TODO : figure out how to schedule urgent and important tasks

{\huge{\underline{\textbf{Week of April 14th}}}} \\
\textbf{Summary:} {\small This is the weekly planning document. To create
this, first look at weekly routines and make sure they are here. Then,
look at the yearWeekPlan doc, along with project plan doc, and iPhone
todo list, and divide tasks across days of the week. Then, put this
into the schedule.

After this is done, these items should be checked in the work and
work+life calendar, and verified through email.
Then, they should be put in the work + life
calendars.}\\

\textbf{Worries to watch for: }
{\small seeing another person,
ex-,
% New Years text,
email to Vk,
% what will bronis say,
stress about worklife, stress about women, stress about PACT paper rebuttal
}
%stress about Divya
\\
\textbf{Current habits: monthly}
% dinner etiquette
% make sure eye contact not shifty
% avoid facebook / social media urge
% no cell phone
%avoid bodily noises
% walk in straight line without feet scrubbing floor
% get reg routines down
{\small \textit{back straight}}
{\small \textit  lips relaxed }
% avoid butt-dials.
% no teeth clicks
\\
%\textit{\textbf{Note:}} figure out how to organize and do this
\textbf{Practice Points:} {\small go through goals from top down to get schedule, prioritization and time management,
comparisons to general people (students), comparisons to others, practice unwinding by playing chess, making goals and meeting deadlines}. \\

\textbf{Spaces Org: do this every Saturday } {\small code folder, paper folder, organization folder,  email folder, iPhone items, clean laptop surface and desk,
\doneTaskNoItem{desktop}, \doneTaskNoItem{backpack}, clean up home directory, car : tires change, detailing, clean outside, clean up downloads directory}\\

% figure out what to do about the list

%Note: think about making dress code for situations
\textbf{Clothing Prep: }
{\small (\textit{Monday}: standard tshirt + jean, \textit{Tuesday}: standard red polo shirt + jeans, \textit{Wednesday}: simple blue shirt + jeans,
 \textit{Thursday}: Regular red + jeans, \textit{Friday}: Full blue shirt , jeans, \textit{Saturday}: formal wear,  \textit{Sunday}: lounging around wear
 }\\

\textbf{Calories planning}
{\small (
\textit{Monday}: -
\textit{Tuesday}: -
\textit{Wednesday}: -
\textit{Thursday}: -
\textit{Friday}: biryani, gilebi, pastries, lemonade, cheese 2 slices of Pizza,
\textit{Saturday}: -  Watch for dinner
\textit{Sunday}: -
 }\\

\underline{\textbf{situations}}\\
\begin{enumerate}
\item \small meet with Prof Gropp: Pre-:  send email in advance

\item \small charm workshop :  Pre-: dress well, find place to sit, know who is coming when Post- :

\item \small Comm: Writing email to Vk: Pre-:  organize Post: make
better plan, be more mature about it.

\item \small Mgmt: flight to Boston:  Pre-: get flight booking done 2
weeks in advance. (ZW9TFA, 7BRGRD). 180 on expedia, 242 on southwest,
wednesday 141, Sunday coming back: (United 126, Delta 141
Flight booked from southwest return:  MO4HXS )  , check about the
travel funds from ISP flight.  Post-:

\item \small Group lunch :  Pre-:  casual dress  Post-:

\end{enumerate}
\newpage

\underline{\textbf{\textit{Monday}}}\\
\underline{\textbf{todo:}}
\begin{itemize}

\item code: fix Barnes-hut implementation for
\item code: get timing for dequeue overheads to work

\item paper: intro: get intro problem clarified, to bring people into context of what we are talking about.
\item paper: intro: explain that there are many dimensions to improve locality.
\item paper: intro: send paper to dad.
\item paper: intro: get intro contributions revised.
\item paper: intro: fix shortcoming of prior work.

\item paper: problem statement: explain the problem with dynamic scheduling.
\item paper: problem statement: explain static/dynamic scheduling.
\item paper: techniques: explain basic static/dynamic scheme.
\item paper: techniques: explain technique of staggering. \priority{UI}
\item paper: techniques: add in code for staggering
\item paper: techniques: explain private work queue
\item paper: techniques: explain idea of which thread to steal from
\item paper: techniques: explain the constraining function in stealing
\item paper: techniques: draw figure for staggered iterations \priority{UI}
\item paper: results: put in explanation of changing threads
\doneTask{paper: results: explain why the results are good for large problem sizes}
\item paper: results: add in data for OpenMP tuning compared with my scheduling scheme
\item paper: intro: add in contributions.
\item relatedWork: add in relevant citations (clarify this).
\item paper: clean up graphs, clean up grammar and weird things \priority{UI}.
\item paper: revise for clarity, revise graphs.
\doneTask{paper: get the access to Easychair}
\end{itemize}

\underline{\textbf{schedule}}\\
\begin{itemize}
\regItem{7:00AM - 8:00AM: running}
\regItem{9:00AM - 10:00AM : regular routines for morning}
\regItem{5:00PM - 6:00PM : send out email to everyone on notes for meeting}
\item
\item
\item
\item 7PM -8PM: yoga
\regItem{9:00PM - 10:00PM : regular routines for night}
\end{itemize}

\underline{\textbf{\textit{Tuesday}}}\\
\underline{\textbf{todo}}: write down elements of style 1 chapter, read emotional intelligence, get chapter's notes down \timeEst{10 mins}
\textbf{Tuesday facebook post: (every other week -not needed this week), be clear, remember someone else's name, reduce anxiety} \\
\begin{itemize}
\item mgmt: spaces: get groceries of ..
\doneTask{ mgmt: call and cancel CLEARME  }
\item check for rebuttal stuff and plan time for this.
\item code: get bw access done
\end{itemize}

\underline{\textbf{schedule}}\\
\begin{itemize}
\regItem{7:00AM - 8:00AM: weights}
\regItem{8:00AM - 9:00AM: regular routines for morning}
\regItem{9:00AM - 10:00AM: meeting}
\item
\item paper: figure out what to do with Amanda
\item
\regItem{9:30-10PM: fb social, linkedIn social, read self-improvement/comm books}
\regItem{10:00PM - 10:30PM: regular routines for night}
\end{itemize}

\underline{\textbf{\textit{Wednesday}}}\\
%NOTE: consider putting this back, due to doneTask issue
%\begin{enumerate}
%\item
%\end{enumerate}
\underline{\textbf{todo}}:
\begin{itemize}
\item mgmt: call Nitin mama and tell about car
\end{itemize}

\underline{\textbf{schedule}}\\
\begin{itemize}
\regItem{7:00AM - 8:00AM: running}
\regItem{8:00AM - 9:00AM: regular routines for morning}
\item 5PM - 6PM : excercise
\item 6:00PM - 6:30PM :
\regItem{10:00PM - 10:30PM: regular routines for night}
\end{itemize}

\underline{\textbf{\textit{Thursday}}}\\
\underline{\textbf{todo}}:
\begin{itemize}
\item send Prof Gropp update
\item
\item revise email to Vk \timeEst{30 mins} \priority{U}
\end{itemize}

\underline{\textbf{schedule}}\\
\begin{itemize}
\regItem{7:00AM - 8:00AM: weights}
\regItem{8:00AM - 9:00AM: regular routines for morning}
\regItem {11AM - 11:30AM : work admin stuff}
\item
\item
\item
\regItem{10:00PM - 11:00PM: regular routines for night}
\end{itemize}

\underline{\textbf{\textit{Friday}}}\\
\underline{\textbf{todo}}:
\begin{itemize}

\item paper: related work: add Amanda's citation and talk about it \timeEst{10 mins}
\item email Amanda about related work and give update \timeEst{10 mins}
\item send revised paper version throughout the day.

\doneTask{ combine point about percent gain in paper, with BG/Q}  \priority{}  \timeEst{10 mins}

\doneTask{ check about fixed duration of noise
events}   \priority{} \timeEst{4 mins}   \priority{I}

\item make a more compelling argument that other events are important
in the work, not just floating-point exceptions. \timeEst{10 mins}

\doneTask{fix wording that says p=1 doesn't make sense - fixed by adding word uni-processor} \timeEst{10 mins}
\item fix wording for bulk-synchronous programming model, this should be in the tone of explanation  \timeEst{10 mins}.
\item make clear that noise and slack are identified clearly already, but that we'll further clarify it \timeEst{5 mins}.
\doneTask{ go through reviewer 1's text to see what to add - just makeclear the presentation.} \timeEst{10 mins}
\doneTask{ delay signature of a parallel process} \timeEst{10 mins}
\doneTask{ address point about adding text for the code} \timeEst{10 mins} \priority{UI}
\doneTask{ take out co-scheduling is not available on all machines} \timeEst{10 mins}
\doneTask{fix point about locality being orthogonal to this work -
fixed by saying locality is separate from this work} \timeEst{10 mins}

\item check reviewer 3's questions again about chunksize, and ensure
that we have answered them properly \timeEst{10 mins}

\doneTask{ make sure tasking model says something about the novelty of this paper } \timeEst{10 mins}
\item update point about exploiting slack  \priority{UI}  \timeEst{20
mins} \deadline{5PM}.

\doneTask{ discuss task and directionality clauses from figure  - not
efficient and mature at the time, we will make a comparison to other
schemes, but we believe ours is unique and novel (no other framework
has what we have done)}  \timeEst{10 mins}  \priority{UI}.
\doneTask{ fix ``delay signature of parallel process'' }
\doneTask{ check this sentence ``Noise is identified through an initial reading in MPI\_Init()''}

\item  fix the locality point rearrangement
\item think about taking out co-scheduling may not be available on all machines

\item check for style \timeEst{30 mins}.
\item check for social intelligence , inspirational \timeEst{10 mins}.

\item final check to make sure that all other review points to be added \timeEst{10 mins}.

\item mgmt: call Nitin mama and tell about car.

\end{itemize}

\underline{\textbf{schedule}}\\
\begin{itemize}
\regItem{7:00AM - 8:00AM: running}
\regRoutineItem {8:00AM - 9:00AM: regular routines for morning}
\regItem{10AM - 11AM : HPC group meeting}
\item Figure out bug in code  for uSched, vSchedLib, and uSchedLib
\item organize code \timeEst{30 mins}
\item send message to Sneha \timeEst{30 mins}
\regItem{9PM - 9:30PM :  situations analysis}
\regItem{9:30PM - 10PM :  lookup clothes for next week}
\regRoutineItem{10:00PM - 11:00PM: regular routines for night}
\end{itemize}

\underline{\textbf{\textit{Saturday}}}\\
\underline{\textbf{todo}}:
\begin{itemize}
\item read Emotional Intelligence \timeEst{10 mins} , summarize the style guide, analyze situations
\item spaces: book flight to Boston, clean up folders in git and in paper.

\textbf{after paper}

\item do tests with different constraints ,  add in to the paper on the theoretical analysis, and cost model
\item software dev., integrate with \texttt{basicPthreads-handTuned.C}
\item results: add in data collection scheme for barnes-hut and any application(add printf's in it)
\item results/experimentation: finish plotting scripts for dat file
\item results/experimentation: find out PAPI information , talk to Tanzima
\item results/experimentation: figure out application data grabbing for Amanda's code , or any other code.  (figure out gen. method).
\end{itemize}

\begin{itemize}
\item write up to Vk \timeEst{2 hours}
\end{enumerate}
\item work on sched code
\begin{enumerate}
\item get the dequeue overhead function fixed \timeEst{2 hours}
\item fix how the nextIter\_CLA is working
\item add in code
\item fix code
\end{enumerate}

\end{itemize}

\underline{\textbf{schedule}}\\
\begin{itemize}
\regItem{7:00AM - 8:00AM: yoga sculpt}
\regRoutineItem {8:30AM - 9:30AM: regular routines for morning}
\regItem{9:30AM - 10:30AM: Spaces maintenance}
\item
\item
\item
\item 8:30PM - 9:30PM : dinner
\item 9:30PM - 10:30PM :
\regItem{10:00PM - 11:00PM: regular routines for night}
\end{itemize}

\underline{\textbf{\textit{Sunday}}}\\
\underline{\textbf{todo:}}\\
\\
\\
\\

\begin{itemize}
\item intro
\item results
\end{itemize}

\underline{\textbf{schedule}}\\
\begin{itemize}
\regItem{7:00AM - 8:00AM: weights + running + meditation }
\regRoutineItem {8:00AM - 9:00AM: regular routines for morning}



\item mgmt: call Nitin mama and tell about car
\item 7-8PM: plan out refine yearweeksPlan for the next month
\regItem{8-9PM:  plan out week in week Plan curr}
\regRoutineItem{10:00PM - 11:00PM: regular routines for night}
\end{itemize}
\newpage

