\documentclass[serif,mathserif,final]{beamer}

\mode<presentation>{\usetheme{Lankton}} 
%\mode<presentation>{\usetheme{I6pd2}} 
%\mode<presentation>{\usetheme{RicePoster}} 
%%\mode<presentation>{\usetheme{ConfPoster}} 
\usepackage{amsmath,amsfonts,amssymb}
\usepackage{eulervm}

\usepackage{pxfonts}
\usepackage{graphicx, ragged2e}
\usepackage{pgffor}
\setbeamertemplate{caption}[numbered]

%\documentclass[11pt]{article}

\usepackage{ulem}
\usepackage{color}
\usepackage{xspace}
\newcommand{\bllt}{\item \small}
\newcommand{\doneTaskNoItem}[1]{\sout{#1}}
\newcommand{\doneTask}[1]{\item \sout{#1}}
\newcommand{\doneTaskHyp}[1]{\item \textcolor{blue} {\sout{#1}}}
\newcommand{\optTask}[1]{\item  \textcolor{green}{#1}}
\newcommand{\prioTask}[1]{\item  \textcolor{red}{#1}}
\newcommand{\timeEst}[1]{\textit{Time:} \textit{#1}}
\newcommand{\priority}[1]{\textit{Priority:} \textit{#1}}
\newcommand{\prio}[1]{\textit{Priority:} \textit{#1}}
\newcommand{\dueBy}[1]{\textit{Deadline:} \textit{#1}}
\newcommand{\MyName}{Vivek~Kale}
\newcommand{\fixme}[1]{\textcolor{blue}{[FIXME: #1]}}
\newcommand{\revision}[1]{\textcolor{blue}{[FIXME comment : #1]}}
\newcommand{\regItem}[1]{\item \textcolor{cyan}{#1}}
\newcommand{\regRoutineItem}[1]{\item \textcolor{green}{\textit{Reg. Routine:} #1}}
\newcommand{\situationItem}[1]{\item \textcolor{magenta}{\textit{Situation:} #1}}
\newcommand{\deadline}[1]{#1}
\newcommand{\comments}[1]{}

\graphicspath{{./figures/}}
\usepackage[orientation=landscape,size=a0,scale=1.6,debug]{beamerposter}

%-- Header and footer information ----------------------------------
\newcommand{\footleft}{Mgmt-WorkLife-weekPlan} % figure what this should be 
\newcommand{\footright}{June 2014}
\title{Month-Week-Day Plan} 
\author{Vivek Kale$^1$$^2$}
\institute{$^1$ University of Illinois at Urbana-Champaign \quad}  

%------------------------------------------------------------------
%-- Main Document ------------------------------------------------- 

\begin{document} 
\begin{frame}{} 

  \begin{columns}[t]
%-- Column 1 ---------------------------------------------------  
\begin{column}{0.30\linewidth} {\textbf{\underline{Week Aspects(new name)}}}
  %-- Block 1-1
  \begin{block}{\textit Stresses} 
    % Recognize emotions / recognize what you're worried about -> eliminate worry
    \begin{itemize}
     % \tiny \item \tiny EuroMPI paper: 
     % \small \item \tiny Ridhima saying stuff about me. 
    %\item \tiny related work:   
      % \item \tiny Atul saying let's talk about this some other time. 
      % \item \small friends of Atul's better(?): 
      % \item \small email -done : 
      % \item \small anger that you are below parents 
      % \item \small [ find others ]
    %\item \tiny others at work. 
    \item \tiny Comm: Talking to Amit - can bounce back. just close friends. 
     \item \tiny Comm:  thinking about how Sat. went /general worries : don't worry and be conscious. 
       \item \tiny Comm: restricted profile - take it for face value. probably because I'd get angry. 
    \end{itemize} 
  \end{block} 
  %-- Block 1-2 
  
  %-- Block 1-3
  \begin{block}{\textit Habits } 
    \begin{itemize} 
      \tiny \item \tiny move feet less, don't scrub on floor. 
    \item \tiny back straight. 
    \item \tiny lips relaxed. 
    \end{itemize} 
  \end{block} 

  %-- Block 1-4
  \begin{block}{\textit Clothes plan } 
    \begin{itemize} 
    \tiny \item \tiny Saturday: wear polo shirt. 
    \item \tiny Saturday night: wear light blue dress shirt and jeans. (or maybe khakis and polo shirt). 
    \item \tiny Sunday: business casual shirt. 
    \item \tiny Wednesday : 
    \item \tiny Thursday: 
    \item \tiny Friday : 
    \item \tiny Saturday : 
    \item \tiny Sunday : 
    \item \tiny   
    \end{itemize} 
  \end{block} 

  %-- Block 1-5
  \begin{block}{\textit Food plan } 
    \begin{itemize} 
      \small \item \tiny Skip meals this week to take out fat from weekend. 
    \item \tiny Be very careful about food for Saturday night, along with Brunch for Sunday and dinner for Sunday. 
    \end{itemize} 
  \end{block} 

  \begin{block}{\textit Situations} 
    \begin{itemize} 
    \item \tiny Meeting with Prof Gropp: Pre-: get updates in early,
      think about what to say Post-:  Think about what to say earlier,
      watch for stresses during the meeting(don't overthink), go
      through possible stress points earlier.  
    \item \tiny Meeting with Prof Gropp: Pre-:  get updates earlier, make
      better plans to do so. Post-: don't be hesitant when saying ``yea I
      should do that now``
\item \tiny Udatta kaka dinner: 
\item \tiny Toastmaster's : Pre-:    Post-: 
\item \tiny meeting everyone Wednesday/Thurs/Friday: Pre-: Post-: watch for over-stressing about Rishi being friend. 
\item \tiny cleanup : pre- : post-:  note mom's biases towards clean house. 
\item \tiny meet Rishi for bday : Pre-: check clothes, get wine bottle, find cover-up,  Post-: 
  
%\item \tiny Driving to Chicago with Atul/Ridhima/Joe : Pre-: 
%      Post-: be sure to tell plans in advance. 
    \end{itemize}
  \end{block} 
\end{column} %2 
%-- Column 2 --------------------------------------------- 

\begin{column}{0.33\linewidth}{\textbf{\underline{Week TODO}}}

% NOTE: Current policy is to comment out days as they come. 
% TODO: put in the regular routines here for each day, in the schedule box. 
  %--- Block 2-1

\begin{block}

%{\small weekTODO} 

\begin{enumerate} 

\item \tiny \doneTask{ Comm: get summary finished for Emo. Intelligence. } 

\item \tiny \doneTask{ Work: Try Tanzima's work. Send Tanzima a message about
  doing the PAPI code. }

\item \tiny figure out the work to send to Prof Gropp for next week. 
item \tiny Mgmt: Spaces: call Dr. Garrick's office for meds. 
\item \tiny Comm: structure Atul's speech + read vocal variety speech
  lessons, look at speech inspiration + sign up for week-after-next
  speech. 

\item \tiny Work: send message about workshop paper from PACT; think
  about best option here. \priority{UI} 

\item \tiny Comm: send Shyunti message. 

\item \tiny \doneTask{Work: send Prof. Gropp message about meeting for
  additional chapter, }\priority{U}.
\item \tiny \doneTask{Work: send message about poster paper for PACT.}
  \priority{U}. 
\item \tiny \doneTask{Work: send Prof. Gropp message about management of time
  next week.} 
\item \tiny Work: refine schedule for summer, communicate with Prof
  Gropp. \timeEst{2 hours} \priority{IU}. 

\item \tiny Work: Do related work structure and motivation \timeEst{2
  hours}. 

\item \tiny Work: update picture and chapter on combo. - check with
  Prof Gropp about this. 

\item \tiny Mgmt: Spaces: get rugs. 

\item \tiny Mgmt: Spaces: money: check sw old stuff; find iPad; update money; check money in bank. 

\item \tiny Mgmt: Spaces: get watch done. 

\item \tiny \textbf{Mgmt: Spaces: Graduation: check for credit hours 
for the summer, get new ones if needed + check grad deadlines.} 

\item \tiny Add code structure for data collection + Find
  any other systems issues and take care of them + integrate the
  slack-conscious runtime/MPI dot prod. 

\item \tiny Mgmt: Spaces: Graduation: send messages on Post-doc to
  Prof. Gropp about Princeton / other places. 
\item \tiny \doneTask{worklife: get cooking instructions down, get
  routine for running/excercise down, integrate other sheets.}

\item \tiny GenKnowledge: get book on genKnowledge. 
\item \tiny Work: check with Prof Gropp about the Princeton post-doc. 
\item \tiny Work: Figure out computer (cs-grad131), and check for files/images from CS525. 

\end{enumerate}
\end{block} 

\begin{block} 

\textbf{\underline{Mon}}
\begin{enumerate} 
\tiny \item \tiny 
\item \tiny 
\item \tiny 
\end{enumerate} 


\textbf{\underline{Tue}}
\begin{enumerate} 
\tiny \item \tiny 
\item \tiny 
\item \tiny 
\end{enumerate} 


\textbf{\underline{Wed}}
\begin{enumerate} 
\tiny \item \tiny 
\item \tiny 
\item \tiny 
\end{enumerate} 

\textbf{\underline{Thu}}
\begin{enumerate} 
\tiny \item \tiny Work: finish related work, other stuff. 
\item \tiny Work: send message to Prof. Gropp about schedule for next
  week, schedule for later. 
\item \tiny Work: send message to Tanzima 

\item \tiny Comm: Toastmasters, do speech, work on emo. intelligence
  work. 

\end{enumerate} 

\textbf{\underline{Fri}}

\begin{enumerate} 
\tiny \item \tiny finish emo intelligence notes 
\item \tiny send message to Tanzima 
\item \tiny call Dr. Garrick's office 
\item \tiny plan Atul's speech. 
\end{enumerate} 

\textbf{\underline{Sat}}

\begin{enumerate} 
\tiny \item \tiny 
\item \tiny 
\item \tiny 
\end{enumerate} 


\textbf{\underline{Sun}}

\begin{enumerate} 
\tiny \item \tiny 
\item \tiny 
\item \tiny 
\end{enumerate} 

\end{block} 

\end{column}%2 

\begin{column}{0.27\linewidth} {\textbf{\underline{Reg. Routines}}}

%Block 3-1
\begin{block}{\small \textbf{\underline{Regular Routines}} }
\underline{\textbf{Morning}}
\begin{itemize}
\item \tiny Brush Teeth \timeEst{4 mins}
\item \tiny Mouthwash, Clean tongue - it helps with breath\timeEst{1mins} 
\item \tiny Eating small breakfast
\item \tiny Check your schedule for meetings / appointments for that day: Is anything urgent? \timeEst{5 mins}
\item \tiny Excercise: 1 hour ( Stretch for 10 mins, Treadmill for 30 mins , Lift weights or Yoga 1 hour, Meditation for 10 mins)
\item \tiny Shave (at least every other day) \timeEst{5 mins}
\item \tiny Shower : (shampoo+conditioner, acne wash,  soap on underarms/underbody)
\timeEst{10 mins}
\item \tiny dry hair, dry face, arms, legs, back, stomach \timeEst{3 mins}
\item \tiny Clothing: belt, check collar, shirt not half-tucked, matching socks \timeEst{5 mins}
\item \tiny Comb hair, hair gel optional \timeEst{ 1 min}
\item \tiny Check Keys/Wallet/Cell/Badge (get a bucket) \timeEst{1 min}
\item \tiny Open meds cabinet, get water, take medicines \timeEst{1 min}
\item \tiny Wear lenses and rinse out case \timeEst{ 2 mins}
\item \tiny Deodorant or cologne depending on the day \timeEst{1 min}
\item \tiny Wash your face with a face wash - it helps with acne \timeEst{3 mins}
\item \tiny Moisturize - apply lotion \timeEst{ 2 min}
\item \tiny Neti pot / clean out sinuses - if you’re feeling congested \timeEst{5 min}
\item \tiny clean out ears, nose \timeEst{5 mins}
\item \tiny Remember to lock door \timeEst{1 mins}
\end{itemize}

\underline{\textbf{Evening}}

\begin{itemize}
\item \tiny Call family: 30 mins
\item \tiny meet friends: 20 mins
\item \tiny Cleaning dishes / cleaning house: 10 mins
\item \tiny Lay out clothes for the next day, iron if necessary
\item \tiny start laundry if needed: 10 mins,
\item \tiny Collect anything you’ll need for the next day (e.g. dry cleaning to drop off): 5 mins,
\item \tiny Check Facebook/linkedin/google+: 10 mins, matrimony stuff: 10 mins,
\item \tiny Food for lunch/dinner the next day: 10 mins
\end{itemize}

\underline{\textbf{Night before bed}}
%TODO: why isn't enumerate working???
%\begin{enumerate}
\begin{itemize}
\item \tiny Finish computer stuff \timeEst{5 mins}
\item \tiny Get into sleeping clothes \timeEst{1 mins}
\item \tiny Before sleeping: brush teeth, floss \timeEst{ 2 min}
\item \tiny Properly wash and put away contacts \timeEst{ 2 mins}
\item \tiny Review the days good things \timeEst{ 10 min}
\item \tiny Light Reading \timeEst{ 10 min}
\item \tiny Prayer \timeEst{10 mins}
%\end{enumerate} 
\end{itemize}
\end{block}

\end{column}%3 

\end{columns} 

\end{frame} 

\end{document}
