\documentclass[serif, mathserif, final]{beamer}
\mode<presentation>{\usetheme{Lankton}} 
\usepackage[orientation=landscape,size=a0,scale=1.6, debug]{beamerposter}
%\usepackage[orientation=landscape,size=a0,scale=1.4,debug]{beamerposter}
%\usepackage[absolute,overlay]{textpos} % <-- can  use this to position text (solves problem of earlier yesterday with poster placement). 

%\documentclass[serif,mathserif,final]{beamer}
%\mode<poster>{\usetheme{RicePoster}}
\usepackage{amsmath,amsfonts,amssymb,pxfonts,xspace}

\usepackage{graphicx, ragged2e}
\usepackage{pgffor}
\usepackage{ulem}
\usepackage{caption}
\usepackage{courier}

\usepackage{verbatim}

%\usepackage[usenames,dvipsnames]{xcolor}                                                                                                                            
\usepackage{listings}

\usepackage{float}
\usepackage{subfig}
\setbeamertemplate{caption}[numbered] 

%\graphicspath{{./figures/}}                                                                                              
%\usepackage{beamerposter}
%\graphicspath{{./figures/}} 
\newcommand{\bllt}{\item \small}
\newcommand{\doneTaskNoItem}[1]{\sout{#1}}
\newcommand{\doneTask}[1]{\item \sout{#1}}
\newcommand{\doneTaskHyp}[1]{\item \textcolor{blue} {\sout{#1}}}
\newcommand{\optTask}[1]{\item  \textcolor{green}{#1}}
\newcommand{\prioTask}[1]{\item  \textcolor{red}{#1}}
\newcommand{\timeEst}[1]{\textit{Time:} \textit{#1}}
\newcommand{\priority}[1]{\textit{Priority:} \textit{#1}}
\newcommand{\prio}[1]{\textit{Priority:} \textit{#1}}
\newcommand{\dueBy}[1]{\textit{Deadline:} \textit{#1}}
\newcommand{\MyName}{Vivek~Kale}
\newcommand{\fixme}[1]{\textcolor{blue}{[FIXME: #1]}}
\newcommand{\revision}[1]{\textcolor{blue}{[FIXME comment : #1]}}
\newcommand{\regItem}[1]{\item \textcolor{cyan}{#1}}
\newcommand{\regRoutineItem}[1]{\item \textcolor{green}{\textit{Reg. Routine:} #1}}
\newcommand{\situationItem}[1]{\item \textcolor{magenta}{\textit{Situation:} #1}}
\newcommand{\deadline}[1]{#1}
\newcommand{\comments}[1]{}

%\graphicspath{{./figures/}}
%\usepackage[orientation=landscape,size=a0,scale=1.6,debug]{beamerposter}

%-- Header and footer information ----------------------------------
\newcommand{\footleft}{Mgmt-WorkLife-weekPlan} % figure what this should be 
\newcommand{\footright}{November 2014}

%------------------------------------------------------------------
%-- Main Document ------------------------------------------------- 
\title{Month-Week-Day Plan} 
\author{Vivek Kale$^1$}
\institute{$^1$ University of Illinois at Urbana-Champaign}  
\date{\today}

% TODO: make the below document neater 
% TODO: consider stretching center column 
% TODO: check how to fit week daily plan together .  

\begin{document}  


\comments{
\begin{frame}{} 
  \begin{columns}
    %-- Column 1 --------------------------------------------------- 
    \begin{column}{0.22\linewidth}
      \begin{block}{Happiness Generation - must maintain every week.}                                          
        % explain happiness: show gratitude
        % remember to show gratitude
        \begin{itemize}
          \tiny \item \tiny happy that I have Atul to show me.  
        \item \tiny Happy that I have normal life up to this point.  
        \item \tiny Thankful that I got a chance to do what I did on Saturday. 
        \item \tiny Think about Neha Jamb. 
        \item \tiny Think about dad saying, I understand, and want you to be happy. 
        \end{itemize}
      \end{block} 

    \begin{block}{Habits} 
      \begin{itemize} 
        %\tiny \item \tiny move feet less, don't scrub on floor. 
        \tiny \item \tiny back straight + eye contact. 
      \item \tiny Reduce things. 
      \item \tiny lips relaxed. 
      \item \tiny watch what happens when a hot girl talks to you. 
      \end{itemize} 
    \end{block} 
  \end{column} %1 

  \begin{column}{0.5\linewidth}
    %-- Block 2-1 
    \begin{block}{ 10-year plan }
      \begin{itemize}
      \item \small Make someone and dad proud.
      \end{itemize}
    \end{block}
    
    \begin{block}{ 3-year plan }
      \begin{itemize}
      \item \small find someone
      \item \small make 150K
      \item \small network
      \end{itemize}
    \end{block}

    \begin{block}{ 6-month plan}
      \begin{itemize}
        \small \item \small results + thesis
      \item \small routine + worklife
      \item \small 
      \end{itemize}
    \end{block} 

    \begin{block}{Month-by-month}
      \begin{itemize}
      \item \small March:
      \item \small April:
      \item \small May:
      \item \small June: org thesis. Org Amanda's application, figure out outstanding system's issues.
      \item \small July: Finish integration in last chapter, data. Amanda's application.
      \item \small August: org thesis, data collection
      \item \small September: Prep other paper for IPDPS
      \item \small October: Get slides ready for defense
      \item \small November: get slides ready for defense 
      \end{itemize}
    \end{block}

    
%\begin{column}{0.33\linewidth} {\textbf{\underline{Month Plan for August 2014}}}      %-- Block 1-1   
\begin{block}{\underline{\textbf{November goals}}}
\begin{enumerate}
\item \small Work: thesis defense. 
\item \small Work: finish code. 
\item \small Comm: practice body language. + Comm: practice vocal variety. 
\item \small Comm: finish the reading for empathy and social intelligence. 
\item \small Comm: take notes. 
\item \small Worklife: integrate all. 
\item \small Worklife: practice with integration of all. 
\item \small Mgmt: dentist appt. 
\end{enumerate}
\end{block}

\begin{block}{\small \underline{\textbf{Week of Nov. $1^{st}$}}}
\begin{enumerate}
\tiny \item \tiny Work: finish poster. 
\item \tiny Work: finish results. 
\item \tiny Comm: finish notes on empathy. \timeEst{2 hours} 
\item \tiny Comm: finish notes on social intelligence. \timeEst{2 hours} 
\end{enumerate}
\end{block}

\begin{block}{\small \underline{\textbf{Week of November $8^{th}$}}}
\begin{enumerate}
\tiny \item \tiny Work: finish the writing . Coordinate for thesis. 
\item \tiny  Work: finish thesis writing. 
\item \tiny  Comm: practice situations.
\end{enumerate}
\end{block}

\begin{block} {\small \underline{\textbf{Week of November $16^{th}$}} }
\begin{enumerate}
\tiny \item \tiny Work: 
\tiny \item \tiny Work: send poster into printing \timeEst{1 hour}. 
\item \tiny Work: get slides ready to present \timeEst{3 hours} \priority{Important}. 
\item \tiny Work: talk to Kathy Yelick. 
\item \tiny Mgmt: Spaces: SC flight. 
\item \tiny Work: 
\item \tiny Work: 
\item \tiny Comm: 
\item \tiny Comm: 
\item \tiny worklife: get cheatsheet ready \timeEst{4 hours}. 
\item \tiny Mgmt: Spaces: Have flight info done, along with hotels \timeEst{1 hour}. 
\end{enumerate}
\end{block} 


\begin{block} {\small \underline{\textbf{Week of November $24^{th}$}} }
\begin{enumerate}
\tiny \item \tiny Work: get slides sent to Prof Gropp \timeEst{30 mins} 
\tiny \item \tiny Work: Comm: talk to Garzaran and Padua. 

\tiny \item \tiny Worklife: get practiced. 
\tiny \item \tiny Worklife: focus on being precise, and defining based on experience. 
\tiny \item \tiny worklife: reliability addition. 
\tiny \item \tiny worklife: add in text for each section, so that it's easy to read and understand when dumb (at level 0).
\item \tiny Mgmt: Spaces: 
\item \tiny Mgmt: Money: re-imbursements for SC and for travel. 
\item \tiny Mgmt: Health: dentist appt. 

\item \tiny Comm: Sateja 
\item \tiny Comm: Rupali 
\end{enumerate}
\end{block} 

\end{column}%2

%-- Column 3 ---------------------------------------------
\begin{column}{0.28\linewidth}
\begin{block}{\small \textbf{\underline{Regular Routines}} }
\underline{\textbf{Morning}}
\begin{itemize}
\tiny \item \tiny Brush Teeth \timeEst{4 mins}. 
\item \tiny Mouthwash, Clean tongue - it helps with breath\timeEst{1mins} 
\item \tiny Eating small breakfast. 
\item \tiny Check your schedule for meetings / appointments for that day: Is anything urgent? \timeEst{5 mins}. 
\item \tiny Excercise: 1 hour ( Stretch for 10 mins, Treadmill for 30 mins , Lift weights or Yoga 1 hour, Meditation for 10 mins). 
\item \tiny Shave (at least every other day) \timeEst{5 mins}. 
\item \tiny Shower : (shampoo+conditioner, acne wash,  soap on underarms/underbody)
\timeEst{10 mins}
\item \tiny dry hair, dry face, arms, legs, back, stomach \timeEst{3 mins}
\item \tiny Clothing: belt, check collar, shirt not half-tucked, matching socks \timeEst{5 mins}
\item \tiny Comb hair, hair gel optional \timeEst{ 1 min}
\item \tiny Check Keys/Wallet/Cell/Badge (get a bucket) \timeEst{1 min}
\item \tiny Open meds cabinet, get water, take medicines \timeEst{1 min}
\item \tiny Wear lenses and rinse out case \timeEst{ 2 mins}
\item \tiny Deodorant or cologne depending on the day \timeEst{1 min}
\item \tiny Wash your face with a face wash - it helps with acne \timeEst{3 mins}
\item \tiny Moisturize - apply lotion \timeEst{ 2 min}
\item \tiny Neti pot / clean out sinuses - if you’re feeling congested \timeEst{5 min}
\item \tiny clean out ears, nose \timeEst{5 mins}
\item \tiny Remember to lock door \timeEst{1 mins}
\end{itemize} 

\underline{\textbf{Evening}}
\begin{itemize}
\tiny \item \tiny Call family: 30 mins
\item \tiny meet friends: 20 mins
\item \tiny Cleaning dishes / cleaning house: 10 mins
\item \tiny Lay out clothes for the next day, iron if necessary
\item \tiny start laundry if needed: 10 mins,
\item \tiny Collect anything you’ll need for the next day (e.g. dry cleaning to drop off): 5 mins,
\item \tiny Check Facebook/linkedin/google+: 10 mins, matrimony stuff: 10 mins,
\item \tiny Food for lunch/dinner the next day: 10 mins
\end{itemize}

\underline{\textbf{Night before bed}}
%TODO: why isn't enumerate working???
%\begin{enumerate}
\begin{itemize}
\tiny \item \tiny Finish computer stuff \timeEst{5 mins}
\item \tiny Get into sleeping clothes \timeEst{1 mins}
\item \tiny Before sleeping: brush teeth, floss \timeEst{ 2 min}
\item \tiny Properly wash and put away contacts \timeEst{ 2 mins}
\item \tiny Review the days good things \timeEst{ 10 min}
\item \tiny Light Reading \timeEst{ 10 min}
\item \tiny Prayer \timeEst{10 mins}
%\end{enumerate} 
\end{itemize}
\end{block} 
\end{column}%3 
\end{columns} 
\end{frame} 
}

\begin{frame}{} 
  \begin{columns}
    %-- Column 1 --------------------------------------------------- 
    \begin{column}{0.25\linewidth} %{\textbf{\underline{Week Aspects(new name)}}}
      %-- Block 1-1 
      \begin{block}{Stresses}
        % Recognize emotions / recognize (precisely) what you're worried about -> methods for eliminating worry. 
        % clean out old worries, put them in pastWorries doc.  
        % remember to define precisely 
        % order from top-to bottom
        \begin{itemize} 
        \item \tiny Worrying about thesis finish. Be sincere and work, we
          make mistakes with time. Get the facts about completion.  Go
          find the path. If I can't get it done, then we'll do something
          else. 
          % \item \tiny Comm: Worrying about not losing it (check this/ define this better) : work on sheet.  
          %    \item \tiny Worrying about deep: forget her, because there's much more to be done.  She may not be interested because it's a brother. 
        \end{itemize} 
      \end{block} 

  %-- Block 1-2 
  \begin{block}{Real-time confidence}
    \begin{itemize} 
      \tiny \item \tiny if you do something sloppy, don't think about it and don't say sorry. 
    \item \tiny don't think someone is trying to hurt you if they say something.       
    \item \tiny know the paths of least stress. 
    \item \tiny if mom does something, don't let that bite you 
    \end{itemize} 
  \end{block} 

  %-- Block 1-3
  \begin{block} {Life notes} 
    \begin{itemize} 
      \tiny \item \tiny Level 0+1: focus on finding Happiness. 
    \item \tiny Level 2: 
    \item \tiny Level 4.1: Writing: prefer standard to offbeat 
    \item \tiny Level 4.2: Body Language: lips relaxed
    \item \tiny Level 4.3: Vocal Variety: shout. 
    \item \tiny TM: work on speech for submission to blog, increasing intentionality. 
    \item \tiny Mgmt/habits: finish chapter 1 reading notes and habits. 
    \end{itemize}     
  \end{block} 
\end{column} %2 

%-- Column 2 --------------------------------------------- 
\begin{column}{0.50\linewidth}
%{\textbf{\underline{Week TODO}}} 
% NOTE: Current policy is to comment out days as they come. 
  % TODO: put in the regular routines here for each day, in the schedule box. 
  %--- Block 2-1 
  \begin{block}{Week TODO} 
    \begin{enumerate} 
    \item Work: finish thesis 
    \item Mgmt: finish flight booking. 
    \end{enumerate}
  \end{block} 
  
  \begin{block}{Week Daily Schedule} 
    \textbf{\small \underline{Mon}} \\
  \textbf{\small todo} \\
  \begin{itemize} 
    \tiny \item \tiny Work: finish data  \deadline{ }   \timeEst{}  \priority{} 
    \tiny \item \tiny Work: finish graphing results  \deadline{ }   \timeEst{}  \priority{} 
    \tiny \item \tiny Work: finish graphing slides  \deadline{ }   \timeEst{}  \priority{} 
    \tiny \item \tiny Work: finish sending results to Prof Gropp.  \deadline{ }   \timeEst{}  \priority{} 

  \end{itemize}  
  \textbf{\small schedule} \\
  \begin{enumerate} 
    \tiny \item \tiny 8-9AM: Regular Routines 
  \end{enumerate} 



  \textbf{\small \underline{Tue}} \\ 
  \textbf{\small todo} \\
  \begin{itemize} 
    \tiny  add in situations  
    \tiny \item \tiny worklife: update worklife  with reliability 
    \tiny \item \tiny worklife: update usage notes. 
    \tiny \item \tiny Work: finish data  \deadline{ }   \timeEst{}  \priority{} 
    \tiny \item \tiny Work: finish graphing results  \deadline{ }   \timeEst{}  \priority{} 
    \tiny \item \tiny Work: finish graphing slides  \deadline{ }   \timeEst{}  \priority{} 
    \tiny \item \tiny Work: finish sending results to Prof Gropp.  \deadline{ }   \timeEst{}  \priority{}               
    \tiny \item \tiny comm: send message to labonee about sateja  \d{   } \t{   }  \p{ } 
  \end{itemize}  
  \textbf{\small schedule}\\ 
  \begin{enumerate} 
    \tiny \item \tiny 8-9AM: Regular Routines 
  \end{enumerate}  

  \textbf{\small {\underline{Wed}}}
  \textbf{\small todo} \\
  \begin{itemize} 
    \tiny \item \tiny Work: finish cache miss results.  + Work: put results in slides  \deadline{}  \timeEst{}  \priority{} 
    \tiny \item Mgmt: Spaces: book flight  \deadline{  }  \timeEst{30 mins} \priority{UI}. 
    \tiny \item worklife: put situations in + worklife: draw full model. 
    \tiny \item Comm: party at mellanox. 
    \tiny \item Comm: prep for Rupali. 
  \end{itemize}  
  \textbf{\small schedule} \\  
  \begin{enumerate} 
    \tiny \item \tiny 8-9AM: Regular Routines 
  \end{enumerate}  


  \textbf{\small{\underline{Thu}}} \\
  \textbf{\small todo} 
  \begin{itemize} 
    \tiny \item \tiny Work: add in data for cache  misses for other kernels. \timeEst{30 mins} 
  \item \tiny Work: put together info for cache  misses in thesis.  \timeEst{30 mins}  \priority{UI} \deadline{Friday} 
  \item \tiny Work: write up slides. + Work: send message to Prof Gropp on slides.  \timeEst{1 hour} \deadline{Sunday}
  \item \tiny Work: send message to Prof. Gropp on work. 
  \item \tiny \doneTask{Mgmt: Spaces: xcel marriot} \deadline{3PM}   \timeEst{}  \priority{} 
  \item \tiny \doneTask{add new sheraton} \deadline{Friday}   \timeEst{}  \priority{} 
  \item \tiny \doneTask{add rental} \deadline{Thursday} \timeEst{10 mins} \priority{UI} 
  \end{itemize}  
  \textbf{\small schedule}
  \begin{enumerate} 
    \tiny \item \tiny 8-9AM: Regular Routines 
  \end{enumerate}  



  \textbf{\small {\underline{Fri}}}\\
  \textbf{\small todo} 
  \begin{itemize} 
    \tiny \item \tiny -  \deadline{ }   \timeEst{}  \priority{} 
  \end{itemize} 
  \textbf{\small schedule} 
  \begin{enumerate} 
    \tiny \item \tiny 8-9AM: Regular Routines 
  \end{enumerate} 

\textbf{\small \underline{Sat}} 
\begin{itemize} 
\item \tiny Work: poster  \deadline{  }  \timeEst{   }  \priority{ } 
\item \tiny Work: comm:  send emails  to Amanda + Work: comm: send email to Tanzima  + Work:plan out 
\item \tiny Mgmt: Spaces: dentist appt  + Mgmt: Spaces: 
\item \tiny worklife: write todos for worklife sheet 
\item \tiny worklife: fix weekPlanDoc.tex 
\item \tiny worklife: start writing step by step instructions for worklife maturity. 

\item \tiny worklife: write instructions on new ideas.  + worklife: note techniques to build ideas.  

\item \tiny worklife: know hwo to use stress skills in real-time 

\item \tiny worklife: define where you are at, and where you want to be. 

\item \tiny worklife: have cross-link down  
\item \tiny worklife: logic 
\item \tiny worklife: have cache ready 
\end{itemize} 

\textbf{\small schedule} 
\begin{enumerate} 
  \tiny \item \tiny 8-9AM: Regular Routines 
\end{enumerate}  

\textbf{\small \underline{Sun}}
\begin{enumerate} 
\tiny \item \tiny Work: finish slides \timeEst{1 hour 30 mins} 
\item \tiny Work: go through slides with dad \timeEst{1 hour} 
\item \tiny Comm: talk to Ashwini \timeEst{20 mins}. 
\item \tiny Mgmt: dentist appt .
\item \tiny Mgmt: clean room 
\item \tiny Mgmt: nails 
\end{enumerate} 
\end{block} 

\end{column}%2 
%-- Column 3 --------------------------------------------------- 
\begin{column}{0.20\linewidth}
  %-- Block 3-1
  \begin{block}{Clothes plan} 
    \begin{itemize} 
      \tiny \item \tiny Saturday: wear polo shirt. 
    \item \tiny Saturday night: wear light blue dress shirt and jeans. (or maybe khakis and polo shirt). 
    \item \tiny Sunday: business casual shirt. 
    \item \tiny Wednesday : 
    \item \tiny Thursday: 
    \item \tiny Friday : 
    \item \tiny Saturday : Blue full shirt . 
    \item \tiny Sunday : Red shirt .
    \end{itemize} 
  \end{block}
  %-- Block 3-2

  %-- Block 3-3
  \begin{block}{Situations} 
    \begin{itemize} 
    \item \tiny \textit{Meet with Prof Gropp: } Pre- : Have results ready, make plan to discuss thesis, don't say too much about thesis completion, feel good about working more, be sure to take criticism, avoid going on tangents when he says something.   
      Post-: plan out time before meeting, so there is time to plan. 
    \item \tiny \textit{SC} : Pre-: clothes   Post-:  
    \item \tiny \textit{Group Lunch}:  Pre-: Send Email.  Post-: 
    \end{itemize}
  \end{block}
\end{column}%3 

\end{columns}

\end{frame}

\end{document}
