%Note:  consider weekly schedule template

%TODO : figure out how to schedule urgent and important tasks

{\huge{\underline{\textbf{Week of March 12th}}}} \\

\textbf{Summary:} This is the weekly planning document. To create
this, first look at weekly routines and make sure they are here. Then,
look at the yearWeekPlan doc, along with project plan doc, and iPhone
todo list, and divide tasks across days of the week. Then, put this
into the schedule.

After this is done, these items should be checked in the work and
work+life calendar, and verified through email.
Then, they should be put in the work + life
calendars. \\

\textbf{Clothing Prep: } \\
Note: think about making dress code for situations
\begin{enumerate}
\item \textbf{Monday}: standard tshirt + jeans
\item \textbf{Tuesday}: standard red polo shirt + jeans
\item \textbf{Wednesday}: simple  blue shirt + jeans
\item \textbf{Thursday}: Regular red + jeans
\item \textbf{Friday}: Full blue shirt , jeans
\item \textbf{Saturday}: formal wear
\item \textbf{Sunday}: lounging around wear
\end{enumerate}

\textbf{Worries to watch for} \\
\begin{enumerate}
\item seeing another person
\item ex-
\item New Years text
\item email to Vk
\item what will bronis say
\item stress about worklife
\end{enumerate}

\textbf{Current habits}\\
\begin{itemize}
%\item dinner etiquette
%\item make sure eye contact not shifty
%\item avoid facebook / social media urge
%\item no cell phone
\item avoid bodily noises
%\item walk in straight line without feet scrubbing floor
%\item get reg routines down
%\item back straight.
%\item lips relaxed.
\item avoid butt-dials.
\end{itemize}

\textbf{Practice Points}\\
\begin{itemize}
\item \textit{\textbf{Note:}} figure out how to organize and do this
\item go through goals from top down to get schedule
\end{itemize}

\textbf{Spaces Org: do this every Saturday }
\begin{itemize}
\item code folder
\item organization folder
\item email folder
\item iPhone items
\item desktop
\item backpack
\end{itemize}

\underline{\textbf{situations}} \\
\begin{enumerate}

\item Flight back from New York: Post-: can explain better the plan to Atul, watch out for people's space, don't bump into them , eat less, don't open the cabin door just as others are getting out.

\item Meet with Maria on Wednesday: Pre-: locality-aware dyn sched., locality-aware static sched, writing schedule and when to graduate,  Post-:

\item Meet with Prof Gropp later: Pre-:  Post-:

\item Talk to Sanjay and Nirupaa: Pre-:    Post-: 
\item Talk to Sneha : Pre-: Post-:
\item Talk to Divya : Pre-: Post-:
\item Talk to Bronis and Todd about work stuff:  Pre-:  Post-:

\end{enumerate}

\underline{\textbf{\textit{Monday}}}\\
\underline{\textbf{todo}}\\
\begin{enumerate}
\item Finish writing the essay \timeEst{1 hour per day}
\item make quick notes on conversation skills \timeEst{10 mins}
\end{enumerate}

\underline{\textbf{schedule}}\\
\begin{itemize}
\regItem{7:00AM - 8:00AM: running}
\regItem{9:00AM - 10:00AM : regular routines for morning}
\regItem{5:00PM - 6:00PM : send out email to everyone on notes for meeting}
\regItem{9:00PM - 10:00PM : regular routines for night}
\end{itemize}

End goal: Bronis should not bother me, Todd should not bother me. We should have bi-weekly meetings.
I should work every week towards a goal of EuroMPI paper. Torsten should no longer be involved.
Bill should guide me towards a November graduation.

\underline{\textbf{\textit{Tuesday}}}\\
\underline{\textbf{todo}}\\
\begin{enumerate}
\item write up cost function, write up engineering design  \priority{I}
\item write code for Amanda
\doneTask {check for VPN account access \timeEst{10 mins}}
\end{enumerate}

\textbf{Tuesday facebook post: } The actual innovation has already been done in Computer Science.
This doesn't solve an imminent problem in society. This generates controversy.
Controversy brings up attention. Attention makes people interested in trying it out.
And generating controversy is exactly how tech startups can stand tall in the face of tech giants.

\underline{\textbf{schedule}}\\
\begin{itemize}
\regItem{7:00AM - 8:00AM: weights}
\regItem {8:00AM - 9:00AM: regular routines for morning}
\regItem {9:00AM - 10:00AM: meeting}
\item 11-12AM :  summarize meeting, make plan for paper , prep for TM
\item 1:30PM-6PM : work on code, to get codes
\item 4PM - 5PM : meet with Prof Gropp
\item 8-8:40PM :  do win friends influence people reviews
\item 8:45PM - 9:30PM:
\item 9:30PM -10PM : weekend planning
\regItem {9:30-10PM: fb social, linkedIn social}
\regItem {10:00PM - 10:30PM: regular routines for night}
\end{itemize}

\underline{\textbf{\textit{Wednesday}}}\\
\underline{\textbf{todo}}\\
\begin{enumerate}
\item putting worklife together, (remember to save!) \timeEst{1 hour}
\item integrate/unify long-term goals together \timeEst{10 mins}

\end{enumerate}

\underline{\textbf{schedule}}\\
\begin{itemize}
\regItem{7:00AM - 8:00AM: running}
\regItem{8:00AM - 9:00AM: regular routines for morning}
\situationItem {1:30PM -2PM : meet with Maria Garzaran}
\item 2PM - 5PM: coding for tests, make project diagram as needed.
\regItem{10:00PM - 10:30PM: regular routines for night}
\end{itemize}

\underline{\textbf{\textit{Thursday}}}\\
\underline{\textbf{todo}}\\
\begin{enumerate}
\item talk to Bronis about post-doc opportunities, plan to graduate \priority{UI-high}
\item review Heidelberg essay \priority{U}
\end{enumerate}

\underline{\textbf{schedule}}\\
\begin{itemize}
\regItem{7:00AM - 8:00AM: weights}
\regItem{8:00AM - 9:00AM: regular routines for morning}
\regItem {10AM -11AM : DEG meeting}
\regItem {11AM - 11:30AM : work admin stuff}
\item 11AM - 12PM :
\item 1PM - 4PM: Amanda's code lookover
\item 11PM - 12PM: packing, checkin to flight
\regItem{10:00PM - 11:00PM: regular routines for night}
\end{itemize}

\underline{\textbf{\textit{Friday}}}\\
\underline{\textbf{todo}}\\
\begin{enumerate}

\item write down elements of style 1 chapter \timeEst{10 mins}
\item read emotional intelligence, get chapter's notes down \timeEst{10 mins}

\item look at Amanda's code briefly, fix the icrev part  \timeEst{10 mins}  \priority{I}
\item do code implementation for meeting \timeEst{20 mins}
\item organize locality-conscious scheduling library \timeEst{1 hour}
\item add in calendar event \timeEst{10 mins}
\item do code cleanup \timeEst{30 mins}
\item write up to Vk \timeEst{2 hours}
\item situations analysis \timeEst{20 mins}

\item read intros of different books and integrate them into worklife doc

\end{enumerate}

\underline{\textbf{schedule}}\\
\begin{itemize}
\regItem{7:00AM - 8:00AM: running}
\regRoutineItem {8:00AM - 9:00AM: regular routines for morning}
\regItem{10AM - 11AM : HPC group meeting}
\item 6PM - 7PM : talk to Sneha
\regItem{9PM - 9:30PM :  situations analysis}
\regItem{9:30PM - 10PM :  lookup clothes for next week}
\regRoutineItem{10:00PM - 11:00PM: regular routines for night}
\end{itemize}

\underline{\textbf{\textit{Saturday}}}\\
\underline{\textbf{todo}}\\
\begin{enumerate}
\item excercise
\item do re-imbursements
\item summarize the style guide, last part \timeEst{10 mins}
\item do analysis of win friends and influence people 2 chapters \timeEst{10 mins}
\end{enumerate}

\underline{\textbf{schedule}}\\
\begin{itemize}
\regItem{7:00AM - 8:00AM: yoga sculpt}
\regRoutineItem {8:30AM - 9:30AM: regular routines for morning}
\regItem{9:30AM - 10:30AM: Spaces maintenance}
\situationItem 12PM - 1PM:
\item 6PM - 8:30PM:
\item 8:30PM - 9:30PM : dinner
\item 9:30PM - 10:30PM :
\regItem{10:00PM - 11:00PM: regular routines for night}
\end{itemize}

\underline{\textbf{\textit{Sunday}}}\\
\underline{\textbf{todo}}\\
\begin{enumerate}
\item summarize the style guide \timeEst{10 mins}
\item do analysis of win friends and influence people 2 chapters \timeEst{10 mins}
\end{enumerate}

\underline{\textbf{schedule}}\\
\begin{itemize}
\regItem{7:00AM - 8:00AM: weights + running + meditation }
\regRoutineItem {8:00AM - 9:00AM: regular routines for morning}
\item
\item 7-8PM: plan out refine yearweeksPlan for the next month
\regItem{8-9PM:  plan out week in week Plan curr}
\regRoutineItem{10:00PM - 11:00PM: regular routines for night}
\end{itemize}

\newpage

