\documentclass[serif,mathserif,final]{beamer}

\mode<presentation>{\usetheme{Lankton}} 
%\mode<presentation>{\usetheme{I6pd2}} 
%\mode<presentation>{\usetheme{RicePoster}} 
%%\mode<presentation>{\usetheme{ConfPoster}} 
\usepackage{amsmath,amsfonts,amssymb}
\usepackage{eulervm}

\usepackage{pxfonts}
\usepackage{graphicx, ragged2e}
\usepackage{pgffor}
\setbeamertemplate{caption}[numbered]

%\documentclass[11pt]{article}

\usepackage{ulem}
\usepackage{color}
\usepackage{xspace}
\newcommand{\bllt}{\item \small}
\newcommand{\doneTaskNoItem}[1]{\sout{#1}}
\newcommand{\doneTask}[1]{\item \sout{#1}}
\newcommand{\doneTaskHyp}[1]{\item \textcolor{blue} {\sout{#1}}}
\newcommand{\optTask}[1]{\item  \textcolor{green}{#1}}
\newcommand{\prioTask}[1]{\item  \textcolor{red}{#1}}
\newcommand{\timeEst}[1]{\textit{Time:} \textit{#1}}
\newcommand{\priority}[1]{\textit{Priority:} \textit{#1}}
\newcommand{\prio}[1]{\textit{Priority:} \textit{#1}}
\newcommand{\dueBy}[1]{\textit{Deadline:} \textit{#1}}
\newcommand{\MyName}{Vivek~Kale}
\newcommand{\fixme}[1]{\textcolor{blue}{[FIXME: #1]}}
\newcommand{\revision}[1]{\textcolor{blue}{[FIXME comment : #1]}}
\newcommand{\regItem}[1]{\item \textcolor{cyan}{#1}}
\newcommand{\regRoutineItem}[1]{\item \textcolor{green}{\textit{Reg. Routine:} #1}}
\newcommand{\situationItem}[1]{\item \textcolor{magenta}{\textit{Situation:} #1}}
\newcommand{\deadline}[1]{#1}
\newcommand{\comments}[1]{}

\graphicspath{{./figures/}}
\usepackage[orientation=landscape,size=a0,scale=1.6,debug]{beamerposter}

%-- Header and footer information ----------------------------------
\newcommand{\footleft}{Mgmt-WorkLife-weekPlan} % figure what this should be 
\newcommand{\footright}{June 2014}
\title{Month-Week-Day Plan} 
\author{Vivek Kale$^1$$^2$}
\institute{$^1$ University of Illinois at Urbana-Champaign \quad}  

%------------------------------------------------------------------
%-- Main Document ------------------------------------------------- 

\begin{document} 
\begin{frame}{} 

  \begin{columns}[t]
%-- Column 1 ---------------------------------------------------  
\begin{column}{0.30\linewidth} {\textbf{\underline{Week Aspects(new name)}}}
  %-- Block 1-1
  \begin{block}{\textit Stresses} 
    % Recognize emotions / recognize what you're worried about -> eliminate worry
    \begin{itemize}
     % \tiny \item \tiny EuroMPI paper: 
     % \small \item \tiny Ridhima saying stuff about me. 
    %\item \tiny related work:   
      % \item \tiny Atul saying let's talk about this some other time. 
      % \item \small friends of Atul's better(?): 
      % \item \small email -done : 
      % \item \small anger that you are below parents 
      % \item \small [ find others ]
    %\item \tiny others at work. 
    \item \tiny Comm: Talking to Amit - can bounce back. just close friends. 
     \item \tiny Comm:  thinking about how Sat. went /general worries : don't worry and be conscious. 
       \item \tiny Comm: restricted profile - take it for face value. probably because I'd get angry. 
    \end{itemize} 
  \end{block} 
  %-- Block 1-2 
  
  %-- Block 1-3
  \begin{block}{\textit Habits } 
    \begin{itemize} 
      \tiny \item \tiny move feet less, don't scrub on floor. 
    \item \tiny back straight. 
    \item \tiny lips relaxed. 
    \end{itemize} 
  \end{block} 

  %-- Block 1-4
  \begin{block}{\textit Clothes plan } 
    \begin{itemize} 
    \tiny \item \tiny Saturday: wear polo shirt. 
    \item \tiny Saturday night: wear light blue dress shirt and jeans. (or maybe khakis and polo shirt). 
    \item \tiny Sunday: business casual shirt. 
    \item \tiny Wednesday : 
    \item \tiny Thursday: 
    \item \tiny Friday : 
    \item \tiny Saturday : 
    \item \tiny Sunday : 
    \item \tiny   
    \end{itemize} 
  \end{block} 

  %-- Block 1-5
  \begin{block}{\textit Food plan } 
    \begin{itemize} 
      \small \item \tiny Skip meals this week to take out fat from weekend. 
    \item \tiny Be very careful about food for Saturday night, along with Brunch for Sunday and dinner for Sunday. 
    \end{itemize} 
  \end{block} 

  \begin{block}{\textit Situations} 
    \begin{itemize} 
    \item \tiny  Rishi's party: Pre-: Check fb updates frequently, get wine early, look at dress code,  Post-: Careful with pictures, Good talking to Gargi, don't let out too much to Traci Schmidt, plan out money before dancing, it's ok to be talking in the side group, have topics to talk about with each person you don't know that well (e.g. Sadhna) , think about what to say when meeting a nice girl (can't remember what happened).

    \item \tiny
      a. Saturday at our house: Pre-:   Post-: Check clothes ahead of time, Know rough schedule and what is happening (not just when) to get context, Don't stand around like you are lost, be direct about what you want, don't laugh if you don't know what you want,  don't get stressed about camera with Rashmi aunty, pay attention when in a groupb (dancing) \\
      
      b. Saturday at Amit's house: Pre-: Post-: don't have to tell dad about when I first met Atul and Ridhima \\

\item \tiny 
  a. Sunday:  Post-: watch for asking about ``is this your car'' to Shruti ,  be ok with silence, good to relate about indian school, good to talk about the current courses at UIUC. \\

  \item \tiny  b. Sunday: Pre-: Post-: don't talk too much in car about wedding stuff, Etiquette: don't drink two drinks (take the same drink from glass), talk less with Amit (shut your mouth when not needed).\\

\item \tiny 
  
  a. Dinner Monday: Pre-:  \\ 
  b. Dinner Tuesday:   \\
  c. Dinner Wednesday:  \\

\item \tiny Sangeet Thursday: Pre-: know who is coming , don't get excited about others saying things Post-: 
\item \tiny Saturday Wedding: Pre- :   Post-: 
\item \tiny  Saturday Reception: Pre-:    Post-: 
\item \tiny  Sunday dinner:  Pre-:   Post-:  
      %\item \tiny Driving to Chicago with Atul/Ridhima/Joe : Pre-: 
      %      Post-: be sure to tell plans in advance. 
    \end{itemize}
  \end{block} 
\end{column} %2 
%-- Column 2 --------------------------------------------- 

\begin{column}{0.33\linewidth}{\textbf{\underline{Week TODO}}} 
% NOTE: Current policy is to comment out days as they come. 
% TODO: put in the regular routines here for each day, in the schedule box. 
  %--- Block 2-1

\begin{block}
%{\small weekTODO} 

\begin{enumerate} 
\item \tiny Comm: delete ak from fb \priority{UI}  
\item \tiny Comm: add limited profile \priority{U} 

\item \tiny Comm: add Mufasa to deeptha pic. \priority{}
\item \tiny \doneTask{Mgmt: Spaces: send email about insurance} \priority{U} 
\item \tiny \doneTask{Comm: send Deeptha message abt. when you are coming, and that Ridhima's dad is giving watch} \priority{UI}  

\item \tiny 
%\item \tiny Comm: add deeptha pic, change to  Mufasa \priority{} 

\item \tiny Comm: talk to Mrinal Kaku about d \priority{UI}  
\item \tiny Comm: add pic with Srushti on fb   
\item \tiny Comm: add pic with Ritika on fb 
\item \tiny Comm: delete mufasa pic \priority{UI} 

\item \tiny Work: prep to meet with Prof Gropp  \priority{I} . 
\item \tiny Work: clean up thesis tex file. 
\item \tiny Work: fix intro: add intro paragraph, fix contributions . 
\item \tiny Work: fix related work  .
\item \tiny Work: conferences updates .

\item \tiny Mgmt: Spaces: money: check sw old stuff; find iPad; update money; check money in bank. 

\item \tiny Comm: update worklife 
\item \tiny Comm: fix work-life cheatsheet \priority{UI} 
\item \tiny Comm: integrate howtosayit, EI, winfriends, SI, 7habits \priority{UI} 
\item \tiny Comm: do situations planning 

\item \tiny Comm: week planning : \priority{U} 
\item \tiny Work: reply to Tanzima 
\item \tiny Work: figure out the work to send to Prof Gropp for next week + 
send quick update to Prof. Gropp \priority{U}
\item \tiny Work: check for sending paper to workshop on DataFlow. 
\item \tiny Work: send message about workshop paper from PACT; think about best option here. \priority{UI}  

\item \tiny Work: refine schedule for summer, communicate with Prof. Gropp. \timeEst{2 hours} \priority{IU} 
\item \tiny Work: Do related work structure and motivation \timeEst{2 hours}. 
\item \tiny Work: update picture and chapter on combo, based on discussion with Prof. Gropp. 
\item \tiny Mgmt: Spaces: get rugs. 

\item \tiny \textbf{Mgmt: Spaces: Graduation: check for credit hours for the summer, get new ones if needed + check grad deadlines, get the Neur course checked} 

\item \tiny Work: Add code structure for data collection + Find any other systems issues and take care of them + integrate the
  slack-conscious runtime/MPI dot prod.  

\item \tiny Comm: 

\item \tiny Mgmt: Spaces: Graduation: send messages on Post-doc to Prof. Gropp about Princeton / other places + 
  Work: check with Prof Gropp about the Princeton post-doc. 

\item \tiny \doneTask{worklife: get cooking instructions down, get
  routine for running/excercise down, integrate other sheets}. 

\item \tiny GenKnowledge: get book on genKnowledge. 
\item \tiny Work: Figure out computer (cs-grad131), and check for files/images from CS525. 
\end{enumerate}
\end{block} 

\begin{block} 

\textbf{\underline{Mon}}
\begin{enumerate} 
\tiny \item \tiny 
\item \tiny 
\item \tiny 
\end{enumerate} 


\textbf{\underline{Tue}}
\begin{enumerate} 
\tiny \item \tiny 
\item \tiny 
\item \tiny 
\end{enumerate} 


\textbf{\underline{Wed}}
\begin{enumerate} 
\item \tiny Work: Make schedule for work 
\item \tiny Work: Finish intro, update with Prof. Gropp 
\item \tiny Work: go through PAPI code 
\item \tiny Work: make plan to go through apps. 

\item \tiny Comm: delete ak from fb \priority{UI}  
\item \tiny Comm: add limited profile \priority{U} 

\item \tiny Comm: plan out meetup with others. 
\item \tiny Comm: Make schedule for Life 
\item \tiny Comm: Situations 

\end{enumerate} 

\textbf{\underline{Thu}}
\begin{enumerate} 
\tiny \item \tiny Work: finish related work, other stuff + Work: finish writing stuff for intro and related work 
\item \tiny Work: Summarize meeting. 

\item \tiny Work: do stuff for conference submissions copyright form  
\item \tiny Work: submit EuroMPI by July 18th, using sigalternate style. Add in doi. Add in copyright block. 

\item \tiny Mgmt: Spaces: finish packing 
\item \tiny Mgmt: Spaces: 

\item \tiny Comm: situations review 
\item \tiny Comm: Social Intelligence reading. 

\item \tiny Comm: get speech for vocal variety written up 

\end{enumerate} 

\textbf{\underline{Fri}}

\begin{enumerate} 

\tiny \item \tiny Work: finish related work, other stuff + Work: finish writing stuff for intro and related work 
\item \tiny Work: Summarize meeting. 

\item \tiny Work: do stuff for conference submissions 

\item \tiny Work: travel planning 

\item \tiny Comm: get speech for vocal variety written up 

\tiny \item \tiny finish emo intelligence notes 
\item \tiny send message to Tanzima 
\item \tiny call Dr. Garrick's office 
\item \tiny plan Atul's speech. 
\end{enumerate} 

\textbf{\underline{Sat}} 
\begin{enumerate} 
\tiny \item \tiny 
\item \tiny Mgmt: money: travel planning: edmonton, Japan, California 
\item \tiny 
\end{enumerate} 


\textbf{\underline{Sun}}

\begin{enumerate} 
\tiny \item \tiny 
\item \tiny 
\item \tiny 
\end{enumerate} 

\end{block} 

\end{column}%2 

\begin{column}{0.27\linewidth} {\textbf{\underline{Reg. Routines}}}

%Block 3-1
\begin{block}{\small \textbf{\underline{Regular Routines}} }
\underline{\textbf{Morning}}
\begin{itemize}
\item \tiny Brush Teeth \timeEst{4 mins}
\item \tiny Mouthwash, Clean tongue - it helps with breath\timeEst{1mins} 
\item \tiny Eating small breakfast
\item \tiny Check your schedule for meetings / appointments for that day: Is anything urgent? \timeEst{5 mins}
\item \tiny Excercise: 1 hour ( Stretch for 10 mins, Treadmill for 30 mins , Lift weights or Yoga 1 hour, Meditation for 10 mins)
\item \tiny Shave (at least every other day) \timeEst{5 mins}
\item \tiny Shower : (shampoo+conditioner, acne wash,  soap on underarms/underbody)
\timeEst{10 mins}
\item \tiny dry hair, dry face, arms, legs, back, stomach \timeEst{3 mins}
\item \tiny Clothing: belt, check collar, shirt not half-tucked, matching socks \timeEst{5 mins}
\item \tiny Comb hair, hair gel optional \timeEst{ 1 min}
\item \tiny Check Keys/Wallet/Cell/Badge (get a bucket) \timeEst{1 min}
\item \tiny Open meds cabinet, get water, take medicines \timeEst{1 min}
\item \tiny Wear lenses and rinse out case \timeEst{ 2 mins}
\item \tiny Deodorant or cologne depending on the day \timeEst{1 min}
\item \tiny Wash your face with a face wash - it helps with acne \timeEst{3 mins}
\item \tiny Moisturize - apply lotion \timeEst{ 2 min}
\item \tiny Neti pot / clean out sinuses - if you’re feeling congested \timeEst{5 min}
\item \tiny clean out ears, nose \timeEst{5 mins}
\item \tiny Remember to lock door \timeEst{1 mins}
\end{itemize}

\underline{\textbf{Evening}}

\begin{itemize}
\item \tiny Call family: 30 mins
\item \tiny meet friends: 20 mins
\item \tiny Cleaning dishes / cleaning house: 10 mins
\item \tiny Lay out clothes for the next day, iron if necessary
\item \tiny start laundry if needed: 10 mins,
\item \tiny Collect anything you’ll need for the next day (e.g. dry cleaning to drop off): 5 mins,
\item \tiny Check Facebook/linkedin/google+: 10 mins, matrimony stuff: 10 mins,
\item \tiny Food for lunch/dinner the next day: 10 mins
\end{itemize}

\underline{\textbf{Night before bed}}
%TODO: why isn't enumerate working???
%\begin{enumerate}
\begin{itemize}
\item \tiny Finish computer stuff \timeEst{5 mins}
\item \tiny Get into sleeping clothes \timeEst{1 mins}
\item \tiny Before sleeping: brush teeth, floss \timeEst{ 2 min}
\item \tiny Properly wash and put away contacts \timeEst{ 2 mins}
\item \tiny Review the days good things \timeEst{ 10 min}
\item \tiny Light Reading \timeEst{ 10 min}
\item \tiny Prayer \timeEst{10 mins}
%\end{enumerate} 
\end{itemize}
\end{block}

\end{column}%3 

\end{columns} 

\end{frame} 

\end{document}
