\begin{frame}
  \begin{columns}
    %-- Column 1 --------------------------------------------------- 
    \begin{column}{0.25\linewidth} %{\textbf{\underline{Week Aspects(new name)}}}
      \begin{block}{Local Happiness}
        % howto:Recognize emotions / recognize (precisely) what you're worried about -> methods for eliminating worry. 
        % clean out old worries, put them in pastWorries doc.  
        % remember to define precisely 
        % order from top-to bottom 
        \begin{itemize}
          \tiny \item \tiny Work: worrying about interviewing: just focus on the work. 
        \item \tiny Worrying about gal: think about talking to others. 
        \end{itemize}
      \end{block}
      \begin{block}{Stresses}
        % howto:Recognize emotions / recognize (precisely) what you're worried about -> methods for eliminating worry. 
        % clean out old worries, put them in pastWorries doc.  
        % remember to define precisely 
        % order from top-to bottom
        \begin{itemize}
          \tiny \item \tiny Work 
          \item \tiny Anger about a b  -> ...
          \item \tiny Anger about UP -> think about the positive
            perspective, and the original
          \item \tiny Anger about dad saying things 
        \end{itemize}
      \end{block}    
      %-- Block 1-3 
      \begin{block}{Life notes}
        \begin{itemize}
        \item \tiny TM: look at last chapter of emotional
          intelligence.  
        \item \tiny Problem: implement game of mastermind. 
        \end{itemize}
      \end{block}
    \end{column} %2

    %-- Column 2 --------------------------------------------- 
    \begin{column}{0.50\linewidth}
      %--- Block 2-1

      \begin{block}{Routines}
        Morning: exercise, brush, floss, shower (hair, eyes, ears,
        underarms, feet), meds,  belt, comb hair, Night: brush teeth, charge
        phone, clothes for tomorrow, contacts off.  
      \end{block}
      
      \begin{block}{Week Summary}
        {\tiny \textbf{Week Plan:} Work: finish code, Mgmt:Spaces:
          take care of Aer Lingus, Work:rel: talk to Sandia = (work:
          send resume + Work: send message about meeting time)  +
          Work:rel: talk to qumulo + Work:rel: talk to FB, Work: do
          coding problems  } 
        {\tiny \textbf{Weekend Plan:} Work: finish coding, Work: do 
          coding practice problems, Mgmt:Spaces: get contacts/glasses,
          Comm: respond to Saroj } 

      \end{block}

      \begin{block}{Running TODO} % find a better name 
        \begin{enumerate}
        \item \small Work:rel: follow-up from HLF = Work:rel: message to
          Fred Brooks + Work:rel: talk to Alessandro. 
        \item \tiny Comm(tmP): prep for TM \te{10 minutes}  = Comm(tmP): get
          introductions \te{10 minutes} + Comm(tmP): prepare sequence
          for TM \te{20 minutes}

        \item \tiny Comm(netipfollowUP): message to NetIP friends  = 
          Comm(netIPfollowUP): send message to Vanessa \te{10
            minutes} + Comm(netIPFollowUp): message to Natasha about
          the gold dress. + Comm: shalini message + Comm(netipfollow): 
          \doneTask{Work: send message to Shikha} \te{10 minutes}  

        \item \tiny Work:admin(scTravel): plan travel for SC =
          Work:admin(scTravel):send Jill the info for flight for hold
          \te{10 minutes} + \doneTaskNoItem{Work:admin(scTr): send
            Jill the hotel} + Work:admin(scTr): confirm other parts of
          travel + Work:admin(scTravel): Justifications ( extra day by saying
          to meet friend in Austin +
          \doneTaskNoItem{Work:admin(scTravel): travel to/from Champaign} +
          \doneTaskNoItem{Work:admin(scTr): check whether we should do
            flight on our own} +  Work:admin(scTr): decide whether to go + 
          Work:admin(scTr): decide whether to leave on Sunday or
          Monday +
          Work:admin(scTr): decide how early to leave + 
         Work:admin(scTr): decide whether to go from Austin or
          elsewhere 
          + Work:admin(scTr): decide whether to do southwest or not
          $yes because it's generally cheaper, and because you can
          cancel$ 

          Work:admin(scTr): figure out when and how to come back + 
          Work:admin(scTr): decide whether to do conference
          registration or not 


          \doneTask{Work: rel: send Resume to Sandia} \te{20 minutes} 
          
          \doneTask{ Work:comm: send Prof. Gropp slides for
            presentation next week \te{10 minutes}}

          % --> curr 

          %infiniti / mercedes / acura / lexus 

        \item \tiny Work: call for suit \te{30 minutes} 

        \item \tiny Comm(spdt): speed dating follow-up \te{45 minutes} =
          Comm(spdt): send message to Saroj + Comm(spdt): message to
          girl from Hvhd 

        \item \tiny Work(GPUcode): get code done for OpenACC +
          Work: get results for GPU + Work: make projections about
          performance as you          increase number of operations 

        \item \tiny Work: finish time planning = Mgmt:Time(tp): do
          weekend plans through December 15th  + Mgmt:Time(tp): do
          planning through December 15th. 

% later 

        \item \tiny Mgmt:Spaces (meds): get meds done =
          \doneTaskNoItem{Mgmt:Spaces(meds): fill out sheet} +
          Mgmt:Spaces(meds): call for appt. 

        \item \tiny Mgmt:Spaces: pay missed toll \te{10 minutes} 

        \end{enumerate}        
      \end{block} 
      
      \begin{block}{Work:rel}
        \begin{itemize} 
          
          \tiny \item \tiny Sandia 
        \item \tiny Cray  
        \item \tiny Facebook 
        \item \tiny Oracle  

        \item \tiny Intel 
        \end{itemize}

\end{block}       


      \begin{block}{Week Daily Schedule} 

        % howto: arrange items from running todo into the below
        % sheet management document. 



\comments{
        \begin{columns} 
          \column{0.14\textwidth}{\textbf{\small \underline{Mon}}}
          \textbf{\small todo} \\ 
          \begin{itemize}
            \tiny \item \tiny 
          \item \tiny 
          \end{itemize} 
          \textbf{\small schedule} \\
          \begin{enumerate} 
            \tiny \item \tiny 8-9AM: Regular Routines 
          \end{enumerate} 
          
          \column{0.14\textwidth}{\textbf{\small \underline{Tue}}}
          \textbf{\small todo} \\
          \begin{itemize}
            \tiny \item \tiny Work: make project sheet \te{10 minutes} 
          \item \tiny Mgmt:Spaces: check for diploma \te{10 minutes} 
          \end{itemize}  
          \textbf{\small schedule} 
          \begin{enumerate}
            \tiny \item \tiny 10AM - 11AM = 
          \item \tiny 11AM - 12AM = make long-term goals 
          \item \tiny 12PM - 2PM = 
            \tiny \item \tiny 2PM -3PM = 
          \item \tiny 6PM - 10PM = 
          \end{enumerate}  
          
          \column{0.14\textwidth}{\textbf{\small {\underline{Wed}}}}
          \textbf{\small todo} \\
          \begin{itemize}
            \tiny \item \tiny Work: finish slides   
          \item \tiny Mgmt: Spaces: update fb 
          \item \tiny Comm: 
          \end{itemize}
          \textbf{\small schedule} \\
          \begin{enumerate}
            \tiny \item \tiny 8-9AM: Regular Routines 
          \item \tiny 9AM - 10AM: Send message 
            \item \tiny 6:30PM - 7:30PM = 
          \end{enumerate} 
          \column{0.14\textwidth}{\textbf{\small{\underline{Thu}}}}
          \textbf{\small todo}\\
          \begin{itemize}  
            \tiny \item \tiny Work: finish slides 
            \item \tiny Mgmt:Spaces: 
            \item \tiny Comm: 

          \end{itemize} 

          \textbf{\small schedule}\\
          \begin{enumerate} 
            \tiny \item \tiny 8-9AM = Regular Routines 
            \item \tiny 12-1PM = 
            \item \tiny 3:30PM - 4:30PM = group meeting 
            \item \tiny 6PM - 9PM = revise emot. int. chapter and
              structure wl-cheat based on it 
          \end{enumerate} 
          
          \column{0.14\textwidth}{\textbf{\small{\underline{Fri}}}}
          \textbf{\small todo}\\ 
          \begin{itemize}
            \tiny \item \tiny Work: updates on GPU \dl{} \te{} \prio{}

            \tiny \item \tiny Mgmt:Spaces: Haircut \te{10 minutes} 

            
          \item \tiny \te{1 hour} 
          \end{itemize}
          \textbf{\small schedule}\\
          \begin{enumerate}
            \tiny \item \tiny 8-9AM: Regular Routines 
            
          \item \tiny 10AM - 11AM  = haircut 
            \tiny \item \tiny 11AM - 12PM = meet with Prof. Gropp at
            SC 4313  
          \item \tiny 5:30 PM - 7:00 PM = meet with Ruchi at 106
            N. Walnut Street (Esquire Lounge) 
          
          \end{enumerate}
          
          \column{0.14\textwidth}{\textbf{\small \underline{Sat}}}
          \textbf{\small todo}\\
          \begin{itemize} 
            \tiny \item \tiny
          \end{itemize}
          \textbf{\small schedule}\\ 
          \begin{enumerate}
            \tiny \item \tiny 7-7:30PM = food + organize.  
            \tiny \item \tiny 7:30PM -8PM = 
            \tiny \item \tiny 8PM -9PM = 
            \tiny \item \tiny 9:45PM - 10:30PM = go out 
            \tiny \item \tiny 2AM -3AM =  message Samir + add people
          \end{enumerate}
          
          \column{0.14\textwidth}{\textbf{\small \underline{Sun}}}
          \textbf{\small todo}\\
          \begin{itemize} 
           \tiny \item \tiny 
          \end{itemize}

          \textbf{\small schedule}\\
          \begin{enumerate} 
            \tiny \item \tiny 3PM - 4PM  =
          \item \tiny 5-7PM = Comm work 
          \item \tiny 8PM - 10PM = worklife work. 
          \end{enumerate} 
        \end{columns}
      \end{block}
    \end{column}%2
    
}

    %-- Column 3 --------------------------------------------------- 
    \begin{column}{0.20\linewidth}
      %-- Block 3-1 
      % On Sunday morn, put a quick synopsis of top news items           
      % here.  Categorize as Comm and Money.      
      \begin{block}{News}
        \begin{itemize} 
          \tiny \item \tiny 
        \item \tiny Debates
        \end{itemize}
      \end{block}
      
      \begin{block}{Weather} 
        \begin{itemize}
          \tiny \item \tiny 
        \item \tiny 
        \end{itemize}
      \end{block} 

      \begin{block}{Clothes plan} 
        \begin{itemize}
          \tiny \item \tiny Monday
        \item \tiny Tuesday 
        \item \tiny Wednesday
        \item \tiny Thursday
        \item \tiny Friday
        \end{itemize} 
      \end{block}
      %-- Block 3-2 
      
      %-- Block 3-3
      \begin{block}{Situations}
        % Howto: the below are the situations that define one another 

        \begin{itemize} 

        \item \tiny \item 
          \tiny \item \tiny \comments{Main} \textit{Pandharipande
            meet} Pre-: 

          clothes: 
          topics: exp: hlf meeting with vint cerf L0: talk about pandharipande  L1:    L2:     L3:  L4:   L5: 

           Post-: 
          
           \tiny \item \tiny \textit{breakfast} Pre-: Post-: use knife and
           fork to avoid bread pieces, use both utensils to avoid
           getting hands dirty, don't eat while standing 
          \tiny \item \tiny \textit{meet with advisor} Pre-: check
          email periodically when sent. Post-: 
        \item \tiny \textit{Group meeting} Pre-: don't get
          distracted. 
        \end{itemize} 

      \end{block}


%    \item \small Mgmt:Spaces(pk): Packing = 
%      Mgmt:Spaces(pk): charger +Mgmt:Spaces(pk): adapter 
%      + Mgmt:Spaces(pk): shoes  + 
%      Mgmt:Spaces(pk): belt + 
%      Mgmt:Spaces(pk):undershirts  =
%      (Mgmt:Spaces(pk):two black + Mgmt:Spaces(pk):two white) 
%      \doneTaskNoItem{Mgmt:Spaces(pk): Passport}
%      + \doneTaskNoItem{Mgmt:Spaces(pk): 6 underwear} +
%      \doneTaskNoItem{Mgmt:Spaces(pk): 8 socks} +
%      \doneTaskNoItem{Mgmt:Spaces: 4 shirts} + Mgmt:Spaces(pk): 4 




\begin{block}{Rel}
  \begin{itemize} 
    \small \item \small Girl from SF 
    \small \item \small Girl from L.A. 
    \small \item \small Mamta 
\small \item \small Girl coming from SF 

    \item \small Australian girl
    \small \item \small Chicago girl 
    \small \item \small Girl you got the number from 
    \small \item \small Rekha

\small \item Girl teaching 2nd grade 

  \item \small Smita kammath 

      \item \small Girl doing dentistry

    %\small \item \small Ruchi 
    %\small \item \small Neha Jambhekar 
    %\small \item \small Meghan Joshi 
    %\small \item \small Vinita Ghate 
  \end{itemize} 
\end{block} 
\end{column}%3 
\end{columns}

\end{frame}






