\documentclass[serif, mathserif, final]{beamer}
\mode<presentation>{\usetheme{Lankton}}
\usepackage[orientation=landscape,size=a0,scale=1.6, debug]{beamerposter}
\usepackage{amsmath,amsfonts,amssymb,pxfonts,xspace}
\usepackage{graphicx,ragged2e,pgffor}
\usepackage{hyperref}
\usepackage{ulem}
\usepackage{courier}
\usepackage{caption,verbatim,listings,float,subfig} %TODO: order these 
\setbeamertemplate{caption}[numbered] 
\usepackage{calendar}
\usepackage{geometry}

%TODO: remove unneeded items 
\newcommand{\bllt}{\item \small}
\newcommand{\doneTaskNoItem}[1]{\sout{#1}}
\newcommand{\doneTask}[1]{\tiny \item \tiny \sout{#1}}
\newcommand{\doneTaskHyp}[1]{\tiny \item \tiny \textcolor{blue} {\sout{#1}}}
\newcommand{\optTask}[1]{\tiny \item \tiny \textcolor{green}{#1}}
\newcommand{\prioTask}[1]{\tiny \item \tiny \textcolor{red}{#1}}

\newcommand{\timeEst}[1]{\textit{TimeEst:}\textit{#1}}
\newcommand{\te}[1]{\textit{TimeEst:}\textit{#1}}
\newcommand{\deadline}[1]{\textit{Deadline:}\textit{#1}}
\newcommand{\dueBy}[1]{\textit{Deadline:}\textit{#1}}
\newcommand{\dl}[1]{\textit{Deadline:}\textit{#1}}
\newcommand{\priority}[1]{\textit{Priority:}\textit{#1}}
\newcommand{\prio}[1]{\textit{Priority:}\textit{#1}}
\newcommand{\pr}[1]{\textit{Priority:}\textit{#1}}

\newcommand{\MyName}{Vivek~Kale}
\newcommand{\fixme}[1]{\textcolor{blue}{[FIXME: #1]}}
\newcommand{\revision}[1]{\textcolor{blue}{[FIXME comment : #1]}}
\newcommand{\regItem}[1]{\item \textcolor{cyan}{#1}}
\newcommand{\regRoutineItem}[1]{\item \textcolor{green}{\textit{Reg. Routine:} #1}}
\newcommand{\situationItem}[1]{\item \textcolor{magenta}{\textit{Situation:} #1}}
\newcommand{\comments}[1]{}

%TODO: think of document as adding around ...
%TODO: consider changing the below so you only use the text in the
%document 
%TODO: change Week plans 

\newcommand{\footleft}{Mgmt-WorkLife-weekPlan} % figure what this should be 
\newcommand{\footright}{Sept 2016}
%-- Main Document -------------------------------------------------
\title{Month-Week-Day Plan}\author{Vivek Kale$^1$}\institute{$^1$ University of Illinois at Urbana-Champaign}\date{\today}
%TODO: get rid of extra numbers below
\begin{document}

\begin{frame}
\begin{columns}

\begin{column}{0.5\textwidth}
\begin{block}{Projects}
%\underline{\bf Work:code: Project , Coding practice: p for interview.}
\begin{enumerate}
\tiny \item \tiny Work:code (cp.): go through C++, Work:code (cp.): go through Java + Work:code (cp.): go through OOP. 
\item \tiny Work:code (cp.): code up problems.  – 1 week.
\item \tiny Work:code (cp.): integer problems + numerics   -- 1 week. 
\item \tiny Work:code (cp.): practice mock interview problems. – 1 week. 
\end{enumerate}
{\it Schedule:} Work:code (cp.): finish bit manipulation,
%Work(cp.): review brain teasers in book, Work(cp.): Work(cp.): go through C++.\\


{\underline{\bf Project: job talk prep}}
\begin{enumerate} 
\tiny \item \tiny 
\item \tiny 
\item \tiny Mgmt:Spaces(crp): check car tailpipe +
  Mgmt:Spaces(crp):Window \te{1 hour}.
\item \tiny Mgmt:Spaces(bfa): buy things for apartment =
  Mgmt:Spaces(bfa): buy a whiteboard + Mgmt:Spaces(bfa): get a chair
  that adjusts height and folds \t{} \d{} \p{}. 

\end{enumerate}

{\underline{\bf Work:code: Project - Research Paper:}}
\begin{enumerate}
\tiny \item \tiny \url{http://mpp2016.ime.uerj.br}. 
\item \tiny \url{http://sbac-pad}  - registration is  500.
\item \tiny Put up latex.  
\item \tiny Gather all research. 
\item \tiny Gather project work. 
\item \tiny Write down introduction.
\item \tiny Gather data for OpenACC. 
\item \tiny Explain other details of setup. 
\item \tiny Note data for OpenMP. 
\end{enumerate} 
\textit{Schedule:} March 24th: do latex, March 2 \\
%\underline{\bf Work:rel: Project – interview with Berkeley/MIT/industry}
\begin{enumerate} 
\tiny \item \tiny Business cards:  - use latex  -- 40 minutes. 
\item \tiny Cover letter 
\item \tiny Jobs categorization for real jobs opportunities: 
Suny sb / suny sb / LLNL /  |  Intel, NVIDIA, Apple  Google/ms /
software companies, Database companies/Oracle, $\rightarrow$ real companies 
\item \tiny CV: + Research Summary:  -- 1 week.  - Talking about
  your research.
\item \tiny Work:rel: message to Yavatkar Kaka about VMWare +
  Work:rel: gather friends in network from friends about Google +
  Work:rel: message to contacts about Microsoft \te{} \dl{} \pr{}. 
\item \tiny Behavioral questions answers:    -- 1 week. 
\item \tiny Send emails – 1 day. 
\item \tiny Structure in latex. 
\end{enumerate}
%{\small {\it Schedule:} Behavioral answers – 1 week, CV prep - 1 day,
%business cards, cover letter -1 hour. }\\
%\underline{\bf Project: awards}
\begin{enumerate} 
\tiny \item \tiny Figure out write-up for Fulbright. 
\item \tiny Attend Fulbright : 
\item \tiny Stay in touch with HLF 
\item \tiny Do energy econ work with convergence. 
\item \tiny Go to whitehouse thing. 
\item \tiny Plan to be on Program Committee of .. 
\end{enumerate}
%{ \small \it Schedule:} April 15th: message to Stephen – 1 hour,
%Work:rel:Project – Awards: 
%\underline{\bf Mgmt:Spaces: settle on your own}
\begin{enumerate}
\tiny \item \tiny Dentist + Get dentist appointment.
\item \tiny Doctor / Counselor + CBT.
%TODO: organize and group the below 
\item \tiny Reimbursements.
\item \tiny Work pay and holidays / hours. 
\item \tiny 401k+retirement  + fidelity + bank (money owing). 
\item \tiny apartment + apartment sublease + apartment rent.
\item \tiny Flights: update flight information, e.g., credit card,
  emergency contact, passport number.
\item \tiny Flights: finish flight decision making notes, e.g.,
  justification for travel, money/airfare rules, award travel rules.
\item \tiny Change Chase address. 
\item \tiny apartment sublease. 
\item \tiny renter's insurance. 
\item \tiny xfinity and wifi accounts. 
\item \tiny ComEd. 
\item \tiny car insurance \doneTask{car parking} 
\item \tiny Car city sticker. \doneTask{Ventra card.}
\item \tiny Car: Get windows side checked + Get windows marking checked + Get tailpipe checked + Ask about warranty. 
\end{enumerate}

{\underline{\textbf{Worklife - Project – Comm:rel:}}}
\begin{enumerate} 
\tiny \item \tiny Worklife: link management together.  
\item \tiny Worklife: link habits comm and Toastmasters. - done
\item \tiny Worklife: latex viewpoint. 
\item \tiny Comm: read social intelligence first four chapters.
\item \tiny Comm: link all comm together.
\item \tiny Worklife: get emails and texts to analyze. 
\item \tiny Worklife: figure out how to book flights and trips quickly. 
\end{enumerate}
\textit{Schedule:} Comm: read social intelligence first four chapters
and get a method to take in information – 5 hours. Comm: link comm together, worklife: latex viewpoint. Looking ahead:  \\
{\underline{\textbf{ Project: Comm}}}
\begin{enumerate}
\tiny \item \tiny Comm: message to Mona and Leena \te{10 minutes}  := 
\item \tiny Comm: consider view of girl on Shaadi. 
\item \tiny Comm(ren): message to Michael :=  Comm(ren): message to Rishi and Chris and Amaeya about meeting. 
\item \tiny Comm: meet Gary and KD \te{10 minutes}. 
\doneTask{Comm: message to Kavita} 
\te{1 hour} \dl{Thursday} \pr{-}
      \item \tiny Comm: consider talking to Illina.
      \item \tiny Comm: talk to friends from high school.
      \item \tiny Mgmt:Spaces: plan trips. \te{-}.
      \item \tiny Mgmt:webpresence: cancel FB friend request of
        Jocelyn + Mgmt:webpresence: check other friend requests
        sent. \te{-}.
      \item \tiny Mgmt:Spaces(GetThingsSpring2016): get Things =
        Mgmt:Spaces(getThings): get suit. 
      \doneTask{Mgmt:webpresence: delete Anil Taneja from
        LinkedIn. \te{1 hour} \dl{Monday} \pr{UI}. - not needed since
        we met with Rishi  + Comm: may have not accepted +
        Mgmt:webpresence: bad to do so}
\end{enumerate}
{\it Schedule:} meet others over summer, meet girl over summer.\\
%TODO: figure out why this was the issue

{\underline{\textbf{Project: Comm:rel}}}
\begin{enumerate} 
  \tiny \item \tiny Comm: consider what to do about Bhavna.
\item \tiny Comm: get caught up with Matrimony and Shaadi, Use match, make system
  for meeting. 
\item \tiny Comm:rel: discuss with Mom and Dad. 
\end{enumerate} 
\end{block} 
\end{column}

\begin{column}{0.5\textwidth}
\begin{block}{Planning} 
\comments{
{\underline{\textit{2-month plans}}}
{\underline{\textit{January and February:}}}
{\underline{\textit{March and April:}} }
{\underline{\textit{May and June:}}}
}

\begin{itemize}
\tiny \item \tiny do scheduling strategies. 
\item \tiny work on job talk. 
\item \tiny do travel. 
\item \tiny social on facebook, catch up with Rishi. 
\end{itemize} 
\begin{itemize} 
\tiny \item \tiny 2-Month Plan: December: code + worklife, January: study for interviews
\item \tiny 2-Month Plan: February: code | March:  code + interview review + finish coding work. 
\item \tiny 2-Month Plan: April: code, May: code paper review.
\item \tiny 2-month plan: June: relax July: adjust 
\item \tiny 2-month plan: August:  prep September: interview 
\end{itemize}
\end{block}

\begin{block}{} 
{\underline{\textbf{Week of September $1^{st}$, 2016:}}}
\begin{itemize} 
\tiny \item \tiny Work: 
\item \tiny Work:
\item \tiny Work:
\item \tiny Work:
\end{itemize}
{\underline{\textbf{Week of September $7^{th}$, 2016:}}}
\begin{itemize} 
\tiny \item \tiny
\item \tiny 
\item \tiny 
\item \tiny 
\item \tiny Comm:
\end{itemize} 
{\underline{\textbf{Week of September $19^{th}$, 2016:}}}
\begin{itemize} 
\tiny \item \tiny Work: take care of app +  Work: finish review of cs
+ Work: do research work. 
\item \tiny Mgmt:Spaces: dentist 
\item \tiny Comm: hbd to Renuka  
\end{itemize}
{\underline{\textbf{Week of September $24^{th}$ 2016:}}}
\begin{itemize}
\tiny \item \tiny Work: 
\item \tiny Comm: 
\item \tiny Comm: 
\item \tiny Comm: 
\end{itemize}
{\underline{\textbf{Weekend Plans:}}}
\end{block}

\end{column} % end column f1 column 1 
\end{columns}

% \item \tiny Mgmt:Spaces(afx): tell about the closet door.\te{}\dl{}
%   + Mgmt:Spaces(afx): tell about the bathroom. 
\end{frame}

\begin{frame}
  \begin{columns}
    %-- Page 2: Column 1 --------------------------------------------------- 
    \begin{column}{0.25\linewidth} %{\textbf{\underline{Week Aspects(new name)}}}
      %TODO: check where this should go. -done  
      %--- Page 2: Block 1-1 
      \begin{block}{Routines}
      { \tiny\underline{ \bf Routines:} Morning: bfast, exercise/brush,
      floss, shower (hair, eyes, ears, underarms, feet), meds, belt,
      comb hair / dishes, clean kitchen floor. |  Night: running/ put
      away dishes, clean kitchen floor / brushy teeth, charge phone,
      clothes for tomorrow, contacts off.} \\ 
      {\tiny \underline{\bf Sunday Routines:} Routines: Experiences,week plan.} \\ 
      {\tiny \underline{\bf Weekday Routines:}}  
      %TODO: check if weekday routines overlaps into daily routines.
      \end{block} 
%--- Page 2: Block 1-3
      \begin{block}{Local Happiness}
        % howto:Recognize emotions / recognize (precisely) what you're
        % worried about -> methods for eliminating worry. 
        % clean out old worries, put them in pastWorries doc.  
        % remember to define precisely 
        % order from top-to bottom
        \begin{itemize} 
          \tiny \item \tiny Work: worrying about interviewing: just focus on the work. 
        \item \tiny Worrying about gal: think about talking to others. 
        \end{itemize}
      \end{block} 
      %--- Page 2: Block 1-4 
      \begin{block}{AngersAndAnxieties}
        % howto:Recognize emotions / recognize (precisely) what you're worried about -> methods for eliminating worry. 
        % clean out old worries, put them in pastWorries doc.  
        % remember to define precisely 
        % order from top-to bottom
        \begin{itemize}
          \tiny \item \tiny Anger about UP -> think about the positive
            perspective, and the original
          \item \tiny Anger about Mr. Kapoor ->  
          \item \tiny Work: worrying about interviewing: just
          focus on the work. 
          \item \tiny Anger about a b  -> ...
        \end{itemize}
      \end{block}
      %-- Block 1-5
      \begin{block}{Life notes}
        \begin{itemize}
        \tiny \item \tiny Social Intelligence: 
        \end{itemize}
      \end{block}
% howto: 
\end{column}

  %-- Column 2 --------------------------------------------- 
\begin{column}{0.5\linewidth} 
  \begin{block}{Week Summary} 
    {\tiny \underline{\textbf{Week Plan}:  Work: CV updates, Work:
        prep for interview, Work: talk to JP, Work: do cworks, Comm:
        meet Kavita, Comm: plan out wedding} \tiny }
    {\tiny \underline{\textbf{Weekend Plan:}}}
    {\underline{\bf Day trip packing list:} charger for iPhone,
      charger for laptop, car keys, underwear, black socks, shoes, meds, halls
    meds, greyhound, boarding pass, flight pass, directions to venue?}

    {\tiny {\bf Week lessons:}}
    \begin{enumerate}
      \tiny \item \tiny Win Friends/ Influence People – no one
          likes to take direct orders.
        \item \tiny Go through 7 habits.
        \item \tiny Coding problem: 
        \item \tiny Chess tips: 
        \item \tiny tm tips.
    \end{enumerate}

    {{\tiny \bf News:} M: iPhone, galaxy, | S: obama speech, 
      sex misconduct | E: Fallon:  w: {m: {60s r a}}  t:{60s s a}
      {w: {70s s a}} {r: {70s s a}} {f: {70s s a   } } {a :{70s
          s a} }  {u: {  }  } }
  \end{block} 

  \begin{block}{Running ToDo} % find a better name 
    \begin{enumerate}
    \item \tiny Work:comm: update CV.
    \item \tiny Work:rel: discuss salary 
    \item \tiny Work:comm: prep for interview. 

    \item \tiny Work:comm: 
I'd been working on a startup since the
beginning of this year to July in Champaign-Urbana. I've been doing the same
since July in Chicago. I'm deciding between two offers for positions
that I received recently. One is in the Los Angeles area and the other
is in the New York City area.

I actually didn't know about your dinner until I spoke to Atul about 
it during this past weekend.

Please let me know the next time that you visit the US. My phone
number is 217-369-7996. My email address is vivek.lkale@gmail.com. 
Thanks for the invitation to visit you in the UK - I'll let you know.

Vivek


TODO:L3: intent: 

TODO:L4: searching for jobs VS looking for jobs -done 
TODO:L4->L2.5: I'm deciding between VS I received  VS. I'll move soon 
TODO:L4: Thanks again VS Thanks [OMIT] -done



TODO:L4->L2.5: in Champaign 


TODO:L4: place in England - I'll see if I can come in the next couple of
months. Visiting you is on my list.


TODO:L5: I haven't told many people yet about this. 


\item \tiny Message to Kavita 

Hi Kavita and Ashish, 

Thanks for the good time tonight. 

Vivek


TODO:L2: 

TODO:L4: enjoyable VS memorable VS good 

TODO:L5:Kavita and Ashish VS Ashish and Kavita  : ladies first  

TODO:L5: 


Hi Kavita and Ashish,

Thanks for the nice time tonight.

Vivek

Hi Kavita and Ashish,

Thanks for the enjoyable time this evening. 

Vivek

 Let me know when you come again. 

Vivek

    \item \tiny Mgmt:Spaces: check credit card statement.
    \item \tiny Mgmt:Spaces: check for automatic renewal - WSJ,
      Sirius XM, linkedIn, Google Express , Hello Fresh. 


\item \tiny Mgmt:webpresence: fb likes to Mona and Leena's post about
  Cubs. 

\item \tiny Mgmt:webpresence: fb like for Vegas post. 

    \item \tiny Mgmt:Health: dental records \te{1 hour}\dl{}
    \item \tiny Comm: message to Kavita.
    \item \tiny Comm: prep for wedding. 

    \end{enumerate}
  \end{block}

  % howto: the below is a routine based on the job I'm doing and the
  % circumstances I'm in. Note that this is different from routines
  % above, which is true for a long-term period of over 10 years. 

  \begin{block}{Weekly Meetings}
    \begin{itemize} 
    \item \tiny IWOMP affinity meeting Thursday 7 AM PDT / 9 AM
      CDT call in: 805-639-779 pswd: places. 
      \url{https://llnl.webex.com/llnl/j.php?MTID=m33950b76befb72c0cbc31ea2e3be720c}  
    \item \tiny DEG group meeting.  
    \end{itemize}
  \end{block} 
      
  \begin{block}{Week Daily Schedule} 
    {\bf Sun:} Work: ref letters,  Work: update latest in CV  Comm: message to Shalaka, 
    \newline {\bf Mon:} Work: install charm++, Work: CV updates,
    Work: move files from LLNL, Mgmt:Spaces: dental records,  Comm: add 
    \newline {\bf Tues:}
    \newline {\bf Wed:}
    \newline {\bf Thur:} 
    \newline {\bf Fri:} 
    \newline {\bf Sat:} 
  \end{block}
      
  \begin{block}{Week Daily Schedule} 
    % howto: arrange items from running todo into the below
        % sheet management document. 
    \begin{columns}
      \column{0.14\textwidth}{\textbf{\small \underline{Mon}}}
      \textbf{\small todo} \\ 
      \begin{itemize}
        \tiny \item \tiny Add in schedule
      \item \tiny 
      \end{itemize} 
      \textbf{\small schedule} \\
      \begin{enumerate} 
        \tiny \item \tiny 8-9AM: Regular Routines 
      \end{enumerate} 
    \end{columns} 
  \end{block} 
\end{column}

% ------ Page 2: Column 3
\begin{column}{0.25\linewidth}
  % ------ Block 2.3.1 
  
  \begin{block}{Food Plan} 
    \begin{itemize}
      \tiny \item \tiny Google Express: DHDQQJQDRFTXDM95B
    \item \tiny 
    \item \tiny 
    \end{itemize}
  \end{block} 
  
  \begin{block}{Weather}
    \begin{itemize}
      \tiny \item \tiny 
    \item \tiny
    \end{itemize}
  \end{block}
  
  \begin{block}{Clothes plan} 
    \begin{itemize}
      \tiny \item \tiny Monday: 
    \item \tiny Tuesday
    \item \tiny Wednesday
    \item \tiny Thursday
    \item \tiny Friday
    \item \tiny Saturday
    \end{itemize} 
  \end{block}

  %-- Block 3-3 
      \begin{block}{Situations}
        % Summary: the below are the situations that define one
        % another.    
        % Howto: Put post notes of each situation from list of previous
        % week. Put high importance situations in situationslist. 
        % Put list of upcoming situations on Sunday morning with Pre. 
        \begin{itemize}
          \tiny \item \tiny Situation: Meet for Sangita's wedding. Pre-: Post-: 

          %\tiny \item \tiny Situation: Meet Mom and Dad:  coord:
          %Pre-:  Post-: have topics to discuss, talk about plan
          %beforehand- see time comittment, mention the work you need
          %to do.

          % \item \tiny Situation: Talk to Anu:  Pre-:   Post-:  talk less
          %  about you, don't have to make statements that are logical

        \end{itemize} 
      \end{block} 
      % contingincies: 
%Summary: 

\begin{block}{Rel} 
  \begin{itemize} 
  \small \item \small Shwetha K /r
    \item \small Mamta
    \item \small Avani 
    \item \small Sruthi 
    \item \small SH11680694 from San Francisco. 
    \item \small Sandhya N. 22 Jun 2016 
    \item \small Aarti S - 27 - 5' 9'' Charlotte.       
    \item \small Anu M from Chicago, IL 
    \item \small Pranati A from Cleveland, OH - 
    \item \small Meghana K from New York - 
    \item \small Ssd S - 28 , 5 5 , Boston, MA 
    \item \small Anj B. - 30 yrs - SH13882555.
  \end{itemize}
\end{block}

\begin{block}{Comm:friends} 
\begin{itemize}
\item Mgmt:webpresence: 
\item Researchgate, linkedIn, twitter, website, facebook 
\item Friends: Amit, Sangita, Anchit, Kevin. 
\item Rel: Sruthi 
\end{itemize} 
\end{block} 


\end{column}%3 
\end{columns}
\end{frame}
%}
\end{document}
