%Note:  consider weekly schedule template

%TODO : figure out how to schedule urgent and important tasks

{\huge{\underline{\textbf{Week of April 14th}}}} \\
\textbf{Summary:} {\small This is the weekly planning document. To create
this, first look at weekly routines and make sure they are here. Then,
look at the yearWeekPlan doc, along with project plan doc, and iPhone
todo list, and divide tasks across days of the week. Then, put this
into the schedule.

After this is done, these items should be checked in the work and
work+life calendar, and verified through email.
Then, they should be put in the work + life
calendars.}\\

\textbf{Worries to watch for: }
{\small seeing another person,
ex-,
% New Years text,
email to Vk,
% what will bronis say,
stress about worklife , stress about women
}
%stress about Divya
\\
\textbf{Current habits: monthly}
% dinner etiquette
% make sure eye contact not shifty
% avoid facebook / social media urge
% no cell phone
%avoid bodily noises
% walk in straight line without feet scrubbing floor
% get reg routines down
{\small \textit{back straight}}
{\small \textit  lips relaxed }
% avoid butt-dials.
% no teeth clicks
\\
%\textit{\textbf{Note:}} figure out how to organize and do this
\textbf{Practice Points:} {\small go through goals from top down to get schedule, prioritization and time management,
comparisons to general people (students), comparisons to others, practice unwinding by playing chess, making goals and meeting deadlines}. \\

\textbf{Spaces Org: do this every Saturday } {\small code folder, paper folder, organization folder,  email folder, iPhone items, clean laptop surface and desk,
\doneTaskNoItem{desktop}, \doneTaskNoItem{backpack}, clean up home directory, car : tires change, detailing, clean outside, clean up downloads directory}\\

% figure out what to do about the list

%Note: think about making dress code for situations
\textbf{Clothing Prep: }
{\small (\textit{Monday}: standard tshirt + jean, \textit{Tuesday}: standard red polo shirt + jeans, \textit{Wednesday}: simple blue shirt + jeans,
 \textit{Thursday}: Regular red + jeans, \textit{Friday}: Full blue shirt , jeans, \textit{Saturday}: formal wear,  \textit{Sunday}: lounging around wear
 }\\

\textbf{Calories planning}
{\small (
\textit{Monday}: -
\textit{Tuesday}: -
\textit{Wednesday}: -
\textit{Thursday}: -
\textit{Friday}: biryani, gilebi, pastries, lemonade, cheese 2 slices of Pizza,
\textit{Saturday}: -  Watch for dinner
\textit{Sunday}: -
 }\\

\underline{\textbf{situations}}\\
\begin{enumerate}

\item \small Comm: talk with Sneha Gurjar: Pre-: Dress well, shave
Post-:  make sure not to take things personally, good to not laugh too much,
know how to start the conversation on the chat. 

\item \small Comm: text to Sneha Narayan : Pre-: Send message
about being in Boston on Friday. Post-: be understanding
and assume the best in people. Think more quickly about this.

\item \small Talk with Amanda:  Pre-: Post-: Good to be assertive,
good to plan out what you are going to say.
\item \small Talk with Todd:  Pre-: run through slides and practice
for 15 mins, know what to say about where you are, send notes to Todd
before meeting. Post-: expect unexpected with logistics of Torsten
(don't assume he'll not come), send out slide updates much earlier.

\item \small Comm: Writing email to Vk: Pre-:  organize Post: make
better plan, be more mature about it.

\item \small Mgmt: flight to Boston:  Pre-: get flight booking done 2
weeks in advance. (ZW9TFA, 7BRGRD). 180 on expedia, 242 on southwest,
wednesday 141, Sunday coming back: (United 126, Delta 141
Flight booked from southwest return:  MO4HXS )  , check about the
travel funds from ISP flight.  Post-:

\item \small

\end{enumerate}
\newpage

\underline{\textbf{\textit{Monday}}}\\
\underline{\textbf{todo:}}
\begin{itemize}

\doneTask{send out slides}
\item  finish off spaces org (get credit card, photos of items to
sell), finish week planning,  do situation analysis, prioritize the
day
\item book flight for SF, figure out Boston flight  \timeEst{10 mins}

\item fix vSchedLib dyn sched  \timeEst{1hr 10 mins}
\item add in constrained locality
\item explain data sets to Prof Gropp

\item send email to Vk \timeEst{1hr 30 mins}

\end{itemize}

\underline{\textbf{schedule}}\\
\begin{itemize}
\regItem{7:00AM - 8:00AM: running}
\regItem{9:00AM - 10:00AM : regular routines for morning}
\regItem{5:00PM - 6:00PM : send out email to everyone on notes for meeting}
\item
\item
\item
\item 7PM -8PM: yoga
\regItem{9:00PM - 10:00PM : regular routines for night}
\end{itemize}

\underline{\textbf{\textit{Tuesday}}}\\
\underline{\textbf{todo}}: write down elements of style 1 chapter, read emotional intelligence, get chapter's notes down \timeEst{10 mins},

\textbf{Tuesday facebook post: (every other week -not needed this week)}
\\
\underline{\textbf{schedule}}\\
\begin{itemize}
\regItem{7:00AM - 8:00AM: weights}
\regItem{8:00AM - 9:00AM: regular routines for morning}
\regItem{9:00AM - 10:00AM: meeting}
\item
\item
\item
\regItem{9:30-10PM: fb social, linkedIn social, read self-improvement/comm books}
\regItem{10:00PM - 10:30PM: regular routines for night}
\end{itemize}

\underline{\textbf{\textit{Wednesday}}}\\

%NOTE: consider putting this back, due to doneTask issue
%\begin{enumerate}
%\item
%\end{enumerate}
\underline{\textbf{todo}}:
\begin{itemize}
\item do perf. modeling and cost model  \priority{UI}
\item fix vSched dyn sched  \timeEst{1hr 10 mins}  \priority{UI} \deadline{Thursday}
\item send Prof Gropp message about code explanation \priority{UI}
\item read self-improv. book \timeEst{1 hr 30 mins}
\end{itemize}

\underline{\textbf{schedule}}\\
\begin{itemize}
\regItem{7:00AM - 8:00AM: running}
\regItem{8:00AM - 9:00AM: regular routines for morning}
\item 5PM - 6PM : excercise
\item 6:00PM - 6:30PM :
\regItem{10:00PM - 10:30PM: regular routines for night}
\end{itemize}

\underline{\textbf{\textit{Thursday}}}\\
\underline{\textbf{todo}}:
\begin{itemize}

\item add in locality tags \timeEst{1 hr 30 mins}
\item explain data sets to Prof Gropp
\doneTask{add in constrained locality}
\item add in load imbalance numbers for Barnes-Hut
\item write up strategy for load imbalance for moving static section across threads.
\item implement uSched in Barnes-Hut


\item add in data for OpenMP tuning compared with my scheduling scheme
\item software dev., integrate with \texttt{basicPthreads-handTuned.C}
\item write email to Vk \timeEst{30 mins} \priority{U}
\item
\end{itemize}

\underline{\textbf{schedule}}\\
\begin{itemize}
\regItem{7:00AM - 8:00AM: weights}
\regItem{8:00AM - 9:00AM: regular routines for morning}
\regItem {11AM - 11:30AM : work admin stuff}
\item
\item
\item
\regItem{10:00PM - 11:00PM: regular routines for night}
\end{itemize}

\underline{\textbf{\textit{Friday}}}\\
\underline{\textbf{todo}}:
\begin{itemize}
\item add in data collection scheme for barnes-hut
\end{itemize}

\underline{\textbf{schedule}}\\
\begin{itemize}
\regItem{7:00AM - 8:00AM: running}
\regRoutineItem {8:00AM - 9:00AM: regular routines for morning}
\regItem{10AM - 11AM : HPC group meeting}
\item Figure out bug in code  for uSched, vSchedLib, and uSchedLib
\item organize code \timeEst{30 mins}
\item send message to Sneha \timeEst{30 mins}
\regItem{9PM - 9:30PM :  situations analysis}
\regItem{9:30PM - 10PM :  lookup clothes for next week}
\regRoutineItem{10:00PM - 11:00PM: regular routines for night}
\end{itemize}

\underline{\textbf{\textit{Saturday}}}\\
\underline{\textbf{todo}}:
\begin{itemize}
\item read Emotional Intelligence \timeEst{10 mins} , summarize the style guide, analyze situations
\item spaces: cancel southwest, book flight for SF, book flight to Boston, clean up folders in git and in paper.
\item send Prof. Gropp a message on update , add in stuff to the implementation
\item do tests with different constraints ,  add in to the paper on the theoretical analysis .

\end{itemize}

\begin{itemize}
\item write up to Vk \timeEst{2 hours}
\end{enumerate}
\item work on sched code
\begin{enumerate}
\item get the dequeue overhead function fixed \timeEst{2 hours}
\item fix how the nextIter\_CLA is working
\item add in code
\item fix code
\end{enumerate}

\end{itemize}

\underline{\textbf{schedule}}\\
\begin{itemize}
\regItem{7:00AM - 8:00AM: yoga sculpt}
\regRoutineItem {8:30AM - 9:30AM: regular routines for morning}
\regItem{9:30AM - 10:30AM: Spaces maintenance}
\item
\item
\item
\item 8:30PM - 9:30PM : dinner
\item 9:30PM - 10:30PM :
\regItem{10:00PM - 11:00PM: regular routines for night}
\end{itemize}

\underline{\textbf{\textit{Sunday}}}\\
\underline{\textbf{todo:}}\\
\\
\\
\\

\begin{itemize}
\item intro
\item results
\end{itemize}

\underline{\textbf{schedule}}\\
\begin{itemize}
\regItem{7:00AM - 8:00AM: weights + running + meditation }
\regRoutineItem {8:00AM - 9:00AM: regular routines for morning}
\item
\item
\item
\item
\item 7-8PM: plan out refine yearweeksPlan for the next month
\regItem{8-9PM:  plan out week in week Plan curr}
\regRoutineItem{10:00PM - 11:00PM: regular routines for night}
\end{itemize}

\newpage

