\begin{columns}  %-- Page 2: Column 1 ---------------------------------------------------
  \begin{column}{0.20\linewidth}
    %{\textbf{\underline{Week Aspects(new name)}})
      %--- Page 2: Block 1-1 
    \begin{block}{Routines}
      { \tiny \underline{\bf Routines:} Morning: bfast, exercise/brush,
        floss, shower (hair, eyes, ears, underarms, feet), meds, belt,
        comb hair / dishes, clean kitchen floor. |  Night: running/ put
v        away dishes, clean kitchen floor / brush teeth, charge phone,
        clothes for tomorrow, contacts off.}\\
      {\tiny \underline{\bf Sunday Routines:} Routines:
        Experiences,week plan.}\\ 
      {\tiny \underline{\bf Weekday Routines:}}\\
      %TODO: check if weekday routines overlaps into daily routines.
    \end{block} 
      %--- Page 2: Block 1-3
    \begin{block}{Local Happiness}
      % howto:Recognize emotions / recognize (precisely) what you're
      % worried about -> methods for eliminating worry. 
      % clean out old worries, put them in pastWorries doc.  
      % remember to define precisely 
      % order from top-to bottom
      \begin{itemize} 
        \tiny \item \tiny -
      \item \tiny Worrying about gal: think about talking to others.
      \end{itemize} 
    \end{block}
    %--- Page 2: Block 1-4 
    \begin{block}{AngersAndAnxieties}
      % howto:Recognize emotions / recognize (precisely) what you're worried about -> methods for eliminating worry. 
      % clean out old worries, put them in pastWorries doc.  
      % remember to define precisely 
      % order from top-to bottom
      \begin{itemize}
        \item \tiny Issue with USC : $\rightarrow$ things get better. 
        \tiny \item \tiny Anger about UP $\rightarrow$ think about the positive
        perspective, and the original
      \item \tiny Anger about Mr. Kapoor $\rightarrow$  leave it
      \item \tiny Anger about a b  $\rightarrow$ ...
      \end{itemize}
    \end{block}
      %-- Block 1-5
      \begin{block}{Life notes}
        \begin{itemize}
          \tiny \item \tiny Social Intelligence: 
        \end{itemize}
      \end{block}
      % howto:
      \begin{block}
        {\tiny {\bf Week lessons:}}
        \begin{enumerate}
        \item \tiny tm tips.
        \item \tiny Coding problem: 
        \item \tiny Chess tips: 
        \end{enumerate}
            {{\tiny {\tiny \bf  News:}} {\tiny  M:  | S: 
                | E: Fallon:  Kimmel:  Colbert: SNL:}}

            {{\tiny {\tiny \bf  Weather:}} {\tiny M: 1100 T: 1100 W:
                0110 R: 0100 F: 0110 Sa: 0110 r Su: r }}

            \input{weather} 
      \end{block}
  \end{column}
  %-- Column 2 ---------------------------------------------
  \begin{column}{0.6\linewidth}
    \begin{block}{Week Summary}
      {\underline {\bf Week Plan:} Work: send e-mail to Abid + Work:
        OpenMP, Work: update poster diagrams + Work:update poster text
     + Work: update poster abstract, Work: have ready for submission, 

} \\
      {\underline{\bf Weekend Plan:} Meet with Amanda: } \\
    \end{block}
      \begin{block}{Running ToDo} % find a better name 
        \begin{enumerate} 
      
     \item \tiny \textbf{Curr} $\rightarrow$ 
     
       
     \item \tiny Work(psm:): call USC for networking information. 
     \item \tiny Work(psm:): talk to Argonne National Laboratory for
       information about detector. 
       
     \donetTask{ Work: send agenda for two tasks to JP.}
   \doneTask{ Work: get git repositories updated to have Youssef  =
       Work: reply to Youssef + 
       Work: talk with JP about access + Work: tell Youssef he has
       access to it. }

     \item \tiny Work: 

     \item \tiny Work(psc:): update abstract for poster. 
     \item \tiny Work(psc:): get results for 128 nodes on BlueWaters
       for PIC. 

     \item \tiny Work(psc): get results for dot product on 128 nodes
       of BlueWaters.


     \item \tiny Work(psc): add latex generated diagrams for Figure
         1 of poster. 
     \item \tiny Work(psc:): finish poster plots cleanup for Figure 1
       in poster. 

     \item \tiny Work(psc:): update text in poster paper.

       \item \tiny Work(psc): upload poster paper to submissions
         webpage. 

     \item \tiny Work(psc:):  message to everyone on CklExp for
       biography and picture.

     \item \tiny Work(psc:):  message to everyone on CklExp for
       biography. 

     \item \tiny Mgmt:Spaces: pay bill for counseling sessions. 
     \item \tiny Mgmt:Spaces: get parking spot. 

     \item \tiny Comm: message on Facebook messenger to Kavita. 

     \item \tiny Comm: talk with Mom and Dad about Sonia.
       
     \item \tiny Comm: answer e-mails from others. 

     \item \tiny Mgmt:wp: hbd to Steve Kane. 
     \item \tiny Mgmt:wp: hbd to Andrea Jeffries. 

     \item \tiny Mgmt:wp: hbd to Omkar Bhate. 

     \item \tiny Mgmt:wp: Happy birthday to Rama on WhatsApp. 

     \item \tiny Mgmt:wp: hbd to Neha Gupta \te{September 29} 
     \item \tiny Mgmt:wp: hbd to Ritika Chopra \te{September 29} 
     \item \tiny Mgmt:wp: hbd to Sangram PRadhan \dl{September 30} 
     \item \tiny Mgmt:wp: hbd to Abha Khisty \dl{September 30} 

     \item \tiny Work:rel:  send e-mail to Todd. 
       
       I'm writing to tell you that I want to work at LLNL. I
       believe that I can do the job there if offered one. 

       Here are my credentials: 

        I'd like to work with Bronis  
        Based on an e-mail exchange with Blaise, 
        I'm thinking of talking to Martin Schulz on  OpenMP-T for
        profiling in the parallel systems group at LLNL. 
        I think that this will make sense given my Scholar experience. 
        
        I'd also like to work with Bronis if that's possible.
        
        After consulting with Blaise Barney. It would be really
        good to work with Bronis again, if that's possible. 

        I'm not asking for advice as to how I should proceed. 

        Vivek 

        I'd like to get in on the scene and be better than the
        competition of undergrads 

        I think that you ought to know this 

        I don't know whether there is an opening, but I'd like 

      \item \tiny Work:rel: talk to Andy Schmidt. \te{10 minutes}

      \item \tiny Mgmt:Spaces: check that medical records were
        transferred.

        \item \tiny Comm: message to Rupali Gr. 
          Hi Rupali, I hope that you're doing well. -Vivek
 
        \item \tiny Comm: send Rishi a message to talk by phone. 
          Hi Rishi, I don't know when your wedding is. Don't hesitate
          to call me once before whenever it is. -Vivek.

       \item \tiny Mgmt:Spaces: find departure flight for weekend
         after Labor day. \te{10 minutes}  \pr{IU} \dl{Friday}. 
         
      \item \tiny Mgmt:Spaces: post the apartment on
        craigslist. \pr{UI} \dl{Saturday}.

      \item \tiny Mgmt:Spaces: buy floor mats by BMW. 

     \item \tiny Work:rel: send message to John Damoulakis.  \te{1 hour}. 
     \item \tiny Work:rel: talk to Andy Schmidt. \te{10 minutes} 

      \doneTask{ Mgmt:Spaces: get appointment for BMW service}  +
        Mgmt:Spaces: take car for service. 

      \item \tiny Mgmt:Spaces: get face scrub
        \item \tiny Mgmt:Spaces: ask Mom to get clothes.
        \item \tiny Mgmt:Spaces: get clothes. 

        \item \tiny \textbf{ <-- End Curr }

        \item \tiny Mgmt:wp: add photos from college.           
        \item \tiny Mgmt:wp: happy bd to Sneha Borikar. 
        \item \tiny Mgmt:wp: hbd to Sneha. 
          
        \item \tiny Comm: message to Rishi and Mike about meeting. 
        \item \tiny Work:rel: email to Renata. \te{10 minutes}. 
        \item \tiny worklife: read social intelligence. \te{2 hour} 
        \item \tiny Work(psm): do document with slides. \te{10 minutes}.    
        \item \tiny Work(psm): add Overleaf.            
        \item \tiny Mgmt:Spaces: get contact lenses.
        \item \tiny Mgmt:Spaces: get glasses. 


        \item \tiny worklife: practice posing in a picture.  
        \item \tiny Mgmt:Spaces: get flight for labor day weekend. 
        \item \tiny Mgmt:Spaces: post the apartment on craigslist. 

        \item \tiny Comm: message to girl. \te{10 minutes} \pr{Urgent}. 

        \item \tiny Mgmt:wp: add tags of photos from this past weekend. 
        \item \tiny Mgmt:wp: add photos from college. 
        \item \tiny Comm: message to Rishi.
        \item \tiny Comm: message to Rishi and Mike about meeting.
        \item \tiny Work:rel: email to Renata. \te{10 minutes}. 

         
        \item \tiny worklife: read social intelligence. \te{2 hour}. 

        \item \tiny Mgmt:wp: add tags of photos from this past weekend.  
        \item \tiny Mgmt:wp: add fb picture with Atul. \dl{}. 
        \item \tiny Comm: do review for Liberty Towers.
        \item \tiny Mgmt:Spaces: call about Admiral's Club Card.
        \item \tiny Work: IM system for LLNL.
        \item \tiny Mgmt:Spaces: post apartment on craigslist. \te{1
          hour}.

        \item \tiny Comm: reply to girl. 
        \item \tiny Comm: e-mail to Saloni.
        \item \tiny Comm: e-mail to Bhakti. 
        \item \tiny Comm: message to Rishi and Mike about
          meeting. \te{1 hour}. 
        \item \tiny Work:rel: email to Renata. \te{10 minutes}. 
        \item \tiny Work: send message about optimizations to do for
          CkLoop. \te{1 hour} \dl{20 minutes}. 
        \item \tiny worklife: read social intelligence. \te{2 hour}. 

        \item \tiny \textbf{ <-- End Curr } 

        \item \tiny Work:rel: meet for coffee. \te{1 hour}. 
        \item \tiny Work: get results for n-body.
        \item \tiny Work(iwp:dp): add results from dot product.    
        \item \tiny Work(psm): prep for meeting. \te{1 hour}. 
        \end{enumerate}
      \end{block}
      
      % howto: the below is a routine based on the job I'm doing and the
      % circumstances I'm in. Note that this is different from routines
      % above, which is true for a long-term period of over 10 years. 
      \begin{block}{Weekly Meetings}
        \begin{itemize}
          \tiny \item \tiny IWOMP affinity meeting Thursday 7 AM PDT / 9 AM
          CDT call in: 805-639-779 pswd: places. \url{https://llnl.webex.com/llnl/j.php?MTID=m33950b76befb72c0cbc31ea2e3be720c}
        \item \tiny DEG group meeting.  
        \end{itemize}
      \end{block} 
      \begin{block}{Week Daily Schedule}
        % howto: arrange items from running todo into the below
        % sheet management document. 
        %NOTE: we don't use the table format because of fittting
        \begin{columns}
          \begin{column}{0.14\textwidth}{\small \underline{\bf Mon}}
            {\tiny \bf {\tiny weather:} } {\tiny 11/1 s} \\ 
            {\tiny \bf {\tiny todo}}\\ 
            \begin{itemize}
              \tiny \item \tiny Work: do experiments with multiple nodes. 
            \item \tiny Work: get experiments using real data.  
            \item \tiny 
            \end{itemize}
                {\small  \bf schedule}\\
                \begin{enumerate} 
                  \tiny \item \tiny 8-9AM: Regular Routines 
                \end{enumerate}
          \end{column}

          \begin{column}{0.14\textwidth}{\small \underline{\bf Tues}}
            {\bf {\tiny  weather:} } {\tiny 3/1 r} \\ 
            {\bf {\tiny todo}}\\ 
            \begin{itemize}
              \tiny \item \tiny Work: do write-up 
            \end{itemize} 
                {{\bf {\tiny  schedule}}}
                \begin{enumerate} 
                  \tiny \item \tiny 8-9AM: Regular Routines 
                \end{enumerate} 
          \end{column}
          \begin{column}{0.14\textwidth}{\small \underline{\bf Wed}}
            {\tiny \bf weather: } {\tiny 3/1 r} \\ 
            {\tiny {\bf todo}}\\
            \begin{itemize}
              \tiny \item \tiny Work: send email to Prof. Gropp. 
            \item \tiny 
            \item \tiny Comm: message to Anita. 
            \end{itemize}
                {\tiny \bf schedule}\\
                \begin{enumerate} 
                  \tiny \item \tiny 8-9AM: Regular Routines 
                \end{enumerate} 
          \end{column}

          \begin{column}{0.14\textwidth}{\small \underline{\bf Thurs}}
            {\tiny \bf weather: } {\tiny 1/-1 r }\\ 
            {\tiny \bf todo} \\ 
            \begin{itemize}
              \tiny \item \tiny Add in schedule 
            \item \tiny Work:admin: get slide updated.  
              \item \tiny Work: admin: send cc statement 
              \item \tiny Work: admin: 
                \item \tiny Comm: message to Shikha
                  \item \tiny Comm: talk to Namrata. 
                    \item \tiny Comm: message to Shalaka. 

            \end{itemize} 
                {\tiny {\bf schedule}} \\
                \begin{enumerate} 
                  \tiny \item \tiny 8-9AM: Regular Routines 
                \end{enumerate}
          \end{column} 
          
          \begin{column}{0.14\textwidth}{\small \underline{\bf Fri}}
            {\tiny \bf weather: } {\tiny 3/1 r} \\ 
            {\tiny \bf todo} \\ 
            \begin{itemize}
              \tiny \item \tiny Add in schedule
            \item \tiny 
            \end{itemize} 
                {\tiny \bf schedule} \\
                \begin{enumerate} 
                  \tiny \item \tiny 8-9AM: Regular Routines 
                \end{enumerate}
          \end{column}

          \begin{column}{0.15\textwidth}{\small \underline{\bf Sat}}
            {\tiny \bf weather: } {\tiny 11/1 .2r} \\ 
            { \tiny \bf todo} \\ 
            \begin{itemize}
              \tiny \item \tiny Add in schedule
            \item \tiny 
            \end{itemize} 
                {\tiny \bf schedule} \\
                \begin{enumerate} 
                  \tiny \item \tiny 8-9AM: Regular Routines 
                \end{enumerate}
          \end{column}
         
          \begin{column}{0.15\textwidth}{\small \underline{\bf Sun}}
            {\tiny {\bf weather:} } {\tiny 11/2 r} \\ 
            {\tiny {\bf todo}}\\
            \begin{itemize}
              \tiny \item \tiny Add in schedule
            \end{itemize} 
                {\tiny \bf schedule}\\
                \begin{enumerate} 
                  \tiny \item \tiny 8-9AM: Regular Routines 
                \end{enumerate}
          \end{column}
        \end{columns}
      \end{block}
\end{column}
    
    % ------ Page 2: Column 3
    \begin{column}{0.20\linewidth}
      % ------ Block 2.3.1 
      \begin{block}{Food Plan} 
        \begin{itemize}
          \tiny \item \tiny Google Express: DHDQQJQDRFTXDM95B
        \end{itemize}
      \end{block} 
      \begin{block}{Clothes plan} 
        \begin{itemize}
          \tiny \item \tiny Monday: 
        \item \tiny Tuesday
        \item \tiny Wednesday
        \item \tiny Thursday
        \item \tiny Friday
        \item \tiny Saturday
        \end{itemize} 
      \end{block} 
      
      %-- Block 3-3 
      \begin{block}{Situations}
        % Summary: the below are the situations that define one
        % another.
        % Howto: Put post notes of each situation from list of previous
        % week. Put high importance situations in situationslist. 
        % Put list of upcoming situations on Sunday morning with Pre. 
        \begin{itemize}
          \tiny \item \tiny 
        \item \tiny 
        \end{itemize}
      \end{block}
      % contingincies: 
      % Summary:
    \end{column}
\end{columns}


\comments{

\begin{minipage}{0.5\textwidth}
\begin{itemize}
\tiny \item \tiny do scheduling strategies.
\item \tiny work on job talk.
\item \tiny do travel.
\item \tiny social on facebook, catch up with Rishi.
\end{itemize}
\begin{itemize}
\item \tiny 2-month plan: May: finish documents.  June:  finish paper.
\item \tiny 2-month plan: July: paper, meet people  August: paper, meet people.
\item \tiny 2-month plan: September: paper, meet people  October:
  paper, meet people.
\end{itemize}
\end{minipage}

\begin{multicols}{4}
\begin{minipage}{\columnwidth}
\underline{\bf \tiny {Work:code: PRISMA}}
\begin{enumerate}
\item \tiny Work: fix Youssef's code.
\item \tiny Work: download ptychoLib from Kaushik and copy to git repo.
\item \tiny Work: run for Ptypy.
\item \tiny Work: figure out time to talk with Youssef.
\item \tiny Work: download ptychoLib from Kaushik and copy to git repo.
\item \tiny Work: discuss work with A rittenbach + Work: download
  driver on GPU4.
\item \tiny work: integrate.
\item \tiny Work: do OpenMP 4.5 for ptypy and OpenACC.
\item \tiny Work: run with dataset from PSI.
\item \tiny Work: send message about research paper.
\item \tiny Work: get profiles for PtychoLib code.
\item \tiny Work: write report for spec.
\item \tiny Work: ask for an increase in size for HPCC system.
\end{enumerate}
\end{minipage}

\begin{minipage}{\columnwidth}
\underline{\bf \tiny {Work: PRISMA pubs}}
\begin{enumerate}
\tiny \item \tiny Work: create a latex git repo for paper.
\item \tiny Work: find a conference.
\item \tiny Work: create an outline.
\item \tiny Work: get information about JIT compilation.
\end{enumerate}
\end{minipage}

\begin{minipage}{\columnwidth}
\underline{\bf \tiny {Work: Other work at ISI}}
\begin{enumerate}
\item \tiny Work: get information about JIT compilation.
\end{enumerate}
\end{minipage}

\begin{minipage}{\columnwidth}
\underline{\bf \tiny {Work: OpenMPCon submission}}
\begin{enumerate}
\tiny \item \tiny Work: create a latex git repo for paper.
\item \tiny Work: send Prof. Gropp a message.
\item \tiny Work: make notes on static/dynamic scheduling.
\item \tiny Work: make notes on user-defined scheduling.
\end{enumerate}
\end{minipage}

\begin{minipage}{\columnwidth}
\underline{\bf \tiny {Work: Charm++ +OpenMP}}
\begin{enumerate}
\tiny \item \tiny Work: send notes/tasks todo.
\item \tiny Work: do documentation of implementation.
\item \tiny Do Charm++ + OpenMP implementation.
\item \tiny Get GPU implementation of dotProd in Charm++.
\item \tiny Work: get access to Cori machine.
\item \tiny Work: Add notes about OpenMP.
\item \tiny Work: add explanation of dotProduct on OpenMP.
\end{enumerate}
\end{minipage}


\begin{minipage}{\columnwidth} 
\underline{\bf \tiny {Work: Charm++ +OpenMP}}
\begin{enumerate}
\item \tiny Mgmt:wp: post with friends from college. 
\item \tiny Mgmt:wp: update description. 
\item \tiny Mgmt:wp: post about Queen.   
\item \tiny Comm:rel: update pictures. \te{30 minutes}.
\end{enumerate}
\end{minipage}

\begin{minipage}{\columnwidth}
\begin{enumerate} 
 \item \tiny Mgmt:Spaces: look for apartment elsewhere. \te{1 hour}. 
\end{enumerate}
\end{minipage} 
\end{multicols}

} 


