\documentclass[serif, mathserif, final]{beamer}
\mode<presentation>{\usetheme{Lankton}}
\usepackage[orientation=landscape,size=a0,scale=1.6, debug]{beamerposter}
\usepackage{amsmath,amsfonts,amssymb,pxfonts,xspace}
\usepackage{graphicx,ragged2e,pgffor}
\usepackage{hyperref}
\usepackage{ulem}
\usepackage{courier}
\usepackage{caption,verbatim,listings,float,subfig} %TODO: order these 
\setbeamertemplate{caption}[numbered] 
\usepackage{calendar}
\usepackage{geometry}

%TODO: remove unneeded items 
\newcommand{\bllt}{\item \small}
\newcommand{\doneTaskNoItem}[1]{\sout{#1}}
\newcommand{\doneTask}[1]{\tiny \item \tiny \sout{#1}}
\newcommand{\doneTaskHyp}[1]{\tiny \item \tiny \textcolor{blue} {\sout{#1}}}
\newcommand{\optTask}[1]{\tiny \item \tiny \textcolor{green}{#1}}
\newcommand{\prioTask}[1]{\tiny \item \tiny \textcolor{red}{#1}}

\newcommand{\timeEst}[1]{\textit{TimeEst:}\textit{#1}}
\newcommand{\te}[1]{\textit{TimeEst:}\textit{#1}}
\newcommand{\deadline}[1]{\textit{Deadline:}\textit{#1}}
\newcommand{\dueBy}[1]{\textit{Deadline:}\textit{#1}}
\newcommand{\dl}[1]{\textit{Deadline:}\textit{#1}}
\newcommand{\priority}[1]{\textit{Priority:}\textit{#1}}
\newcommand{\prio}[1]{\textit{Priority:}\textit{#1}}
\newcommand{\pr}[1]{\textit{Priority:}\textit{#1}}

\newcommand{\MyName}{Vivek~Kale}
\newcommand{\fixme}[1]{\textcolor{blue}{[FIXME: #1]}}
\newcommand{\revision}[1]{\textcolor{blue}{[FIXME comment : #1]}}
\newcommand{\regItem}[1]{\item \textcolor{cyan}{#1}}
\newcommand{\regRoutineItem}[1]{\item \textcolor{green}{\textit{Reg. Routine:} #1}}
\newcommand{\situationItem}[1]{\item \textcolor{magenta}{\textit{Situation:} #1}}

\newcommand{\comments}[1]{}

\newcommand{\footleft}{Mgmt-WorkLife-weekPlan} % figure what this should be 
\newcommand{\footright}{August 2015}
%-- Main Document ------------------------------------------------- 
\title{Month-Week-Day Plan}\author{Vivek Kale$^1$}\institute{$^1$ University of Illinois at Urbana-Champaign}\date{\today}

\begin{document}
\begin{frame}
  \begin{columns}
    %-- Column 1 --------------------------------------------------- 
    \begin{column}{0.25\linewidth} %{\textbf{\underline{Week Aspects(new name)}}}
      \begin{block}{Local Happiness}
        % howto:Recognize emotions / recognize (precisely) what you're worried about -> methods for eliminating worry. 
        % clean out old worries, put them in pastWorries doc.  
        % remember to define precisely 
        % order from top-to bottom
        \begin{itemize}
        \tiny \item \tiny Work: worrying about interviewing: just focus on the work. 
        \item \tiny Worrying about gal: think about talking to others. 
        \end{itemize}
      \end{block}
      \begin{block}{Stresses}
        % howto:Recognize emotions / recognize (precisely) what you're worried about -> methods for eliminating worry. 
        % clean out old worries, put them in pastWorries doc.  
        % remember to define precisely 
        % order from top-to bottom
        \begin{itemize}
        \tiny \item \tiny Work: worrying about interviewing: just focus on the work. 
        \item \tiny Worrying abt Dp thinking you are stupid -->  think
            about Todd saying you're smart, you don't apply yourself; 
           think about Atul saying they aren't doing that
            intentionally. 
          \item \tiny Anger about a b  -> ...
          \item \tiny Anger about UP -> think about the positive
            perspective, and the original
        \end{itemize}
      \end{block}       
%      \begin{block}{Real-time Confidence}
%      \end{block}
      %-- Block 1-3
      \begin{block}{Life notes}
        \begin{itemize}
        \item \tiny TM: look at intelligence book. 
        \item \tiny Problem: implement game of mastermind. 
        \end{itemize}
      \end{block}
    \end{column} %2 

    %-- Column 2 --------------------------------------------- 
    \begin{column}{0.50\linewidth}
      %--- Block 2-1
      \begin{block}{Week Summary}
        {\tiny \textbf{Week Plan:} Work: do code for OpenMP, Work:rel:
          send message about fb to Mrinalini + Work:rel: talk to apple,
          Mgmt:Spaces: pack + Comm: prep for situations, Mgmt:Spaces:
          finish organization,  worklife: do organization, Comm: write
          out comm material in wl cheatsheet, } 

        {\tiny \textbf{Weekend Plan:} Comm: answer mails from
          matrimony, Mgmt:Spaces: update work directory.} 
      \end{block} 
      \begin{block}{Running TODO} % find a better name 
        \begin{enumerate} 
          \doneTask{ Work: comm: talk to Matt about meeting} 
          \doneTask{ Mgmt:Spaces: figure out trip to Germany +
            Work:admin: update wiki space = Work:admin: talk to
            someone + Work:admin: review wiki space parts.} 
          \doneTask{ Comm: message to Anita +  Comm: look at people
            and reply to them } \te{1 hour} \dl{Thursday} 
          \doneTask{ Mgmt:Spaces: Zoloft} \te{1 hour}
        \doneTask{ Mgmt:Spaces: apartment = Mgmt:Spaces: find
          Orchard downs apartments(45-day notice) + Mgmt:Spaces:(apt):
          talk to Kobuck and Prospect Pointe apts + Mgmt:Spaces: argue
          reasons for apartments + Mgmt:Spaces: ask about garage} \te{1 hour} 
        % putting hybrid static/dynamic scheduling into application
        % code. 
         \doneTask{Work:comm(meetGrp): send message about meeting to
          Prof. Gropp = Work:comm(meetGrp): go through meeting times +
          Work:comm(meetGrp): meet with him .. }

\comments{
        I've putting in theOpenMP shared memory into the XPACC code.

        Next week, I'llput in hybrid static/dynamic scheduling along
        with other OpenMP loop optimizations. 

        I'm putting aside the OpenACC code for right now.  
        General Goal: inform 
        Specific Goal: getting main work you wanted done done. (for
        OpenMP).  
        
        
        % Below is a follow-up from the earlier message. 
        
        To follow-up from the earlier message: 
        
        With help from John Larson, I am now applying OpenMP to the loops of all the functions of the 
        PlasComCM code, excluding the functions in the ModDeriv.fpp
        code file that are done already. 

        Also, later next week, I will apply hybrid static/dynamic scheduling to
        these OpenMP parallel loops and also try applying other OpenMP loop
        optimizations to these OpenMP loops. 

        I want to note that I am putting aside the OpenACC stencil code
        / OpenACC parallelization for the PlasComCM code for right
        now - the OpenACC parallelization for the PlasComCM code should
        follow from the OpenMP parallelization done in the code. 
        I will focus more on the OpenACC parallelization after I come back from Germany
        week after next, and I will keep Jon Freund posted on this. (Let
        me know if this is ok.) 

        % until after the OpenMP parallel loop optimizations
        % are done. 
        % Please let me know if this is a good idea, and I'll keep Jon
        % Freund posted on this during this week. 

        1. TODO: L3: Also, -done 
        2. TODO: L2: An additional update.  - done 
        3. TODO: L3: I will pick that up after I come back from - done 
        Germany. 
        
        4. TODO: L0: OpenACC code  -done 
        
        5. TODO: I'm putting aside ...b -done 

        6. TODO: L2: transformations follow from loop parallelization
        --- done

        7. TODO: L2: Germany next week  -done

        9. TODO: L2+ L4: PlasComCM should follow from the OPenMP
        parallelization 
        
        8. TODO: L3(1): working on my work = TODO:L3(1): check
        paragrpahs + TODO:L3(1): - let me know
        if this is ok. - done 

        10. TODO: L4: pick up OpenACC again - focus more on OpenACC
        -done  

        11. TODO: L5: Let me know if this is ok in parenthesis or not?
        -done 
        12. TODO: L5: the OpenACC parallelization - keep to show its
        importance , and that you want to do something
        different. -done 
        13. TODO: L5: try to apply --   try applying -done 

        14. TODO: for right now - , since  -- for right now, since 

        15. TODO(L1:,L4, L5): I'm putting aside  
        bring that back in, seeing if I can integrate it directly into the
        application code. 
        % after I come back from Germany. 

        While that is important, I've been putting in the OpenMP shared memory into
        the XPACC code. Next week, I'll put in hybrid static/dynamic
        scheduling into application code. I'm putting the OpenACC code
        on the side burner for the moment. 
}
        
         \doneTask{ worklife: toastmasters practice} \te{1 hour} 
         \doneTask{ Work:comm: send message to Prof. Gropp} \te{30 minutes} 

        \item \small worklife: finish slides for management =
          worklife: toastmasters + worklife: finish picture. \te{2
            hours} 
          % curr --> 

        %\item \small Work(opcm): get performance data for XPACC code =
        %  Work(opcm): apply PAPI counters to each routine in
        %  application. 
        %\item \small Work(opcm): Apply OpenCL to XPACC code \te{10
        %  hours} = Work(opcm): Apply OpenCL to each routine +
        %  Work(opcm): 
        %\item \small Work(opcm): Apply OpenMP to mini-miniApp \te{10
        %  hours} = Work(opcm): Apply OpenMP to each routine +
        %  Work(opcm):


        \item \small Mgmt:Spaces: Book airfare \te{30 minutes}
          \dl{Saturday} 

        \item \small Comm: Delete ka + Comm: Hide Ms. I + Comm: talk
          to Atul. \te {30 minutes} \prio{UI} \dl{Wed} +  Comm: hope I
          was a good brother. 

        \item \small Comm: gauge matrimony = Comm: message to
          \href{mailto:earthtopratima@gmail.com}{earthtopratima@gmail.com} + Comm: look at others \pr{UI}
          \te{1 hour}  

        \item \small worklife: finish emot. int. book  on Cecil =
          worklife: structure + worklife:integration into sheet and
          connection with other things +
          worklife:applications/examples\te{1 hour} 
        \item \small Work(gpuCode): apply OpenCL to stencil. \te{10
          hours} =  Work(gpuCode): code with OpenCL on stencil.
        \item \small Work(opcm): Apply OpenMP to XPACC code \te{10
          hours} = Work(opcm): Apply OpenMP to each routine +
          Work(opcm): 


        \item \small Comm: message to Anita = Comm: (text conv last
          night) +  Comm: talk to Anita on skype 
        \item \small Comm: send message to Rishi \te{30 mins}
          \dl{Saturday} \pr{IU} 

        \item \small Work: do coding practice planning \te{10 mins} 

       \item \small Mgmt:Spaces: fix the wall unit \te{1 hour} 
        \end{enumerate}
      \end{block} 
      \begin{block}{Week Daily Schedule} 
        % howto: arrange items from running todo into the below
        % sheet management document. 
        \begin{columns} 
          \column{0.14\textwidth}{\textbf{\small \underline{Mon}}}
          \textbf{\small todo} \\ 
          \begin{itemize}
            \tiny \item \tiny 
          \item \tiny 
          \end{itemize} 
          \textbf{\small schedule} \\
          \begin{enumerate} 
            \tiny \item \tiny 8-9AM: Regular Routines 
          \end{enumerate} 
          
          \column{0.14\textwidth}{\textbf{\small \underline{Tue}}}
          \textbf{\small todo} \\
          \begin{itemize}
            \tiny \item \tiny Work: start writing code \te{2 hours} 
          \item \tiny Mgmt:Spaces: send package to Anu \te{15 minutes} 
          \item \tiny Comm: TM prep + Comm: message to Anita  \te{30
            minutes} 
          \end{itemize}  
          \textbf{\small schedule} 
          \begin{enumerate}
            \tiny \item \tiny 10AM - 11AM = update org 
          \item \tiny 11AM - 12AM = make long-term goals 
          \item \tiny 12PM - 2PM = start writing code and make the
            framework. 
            \tiny \item \tiny 2PM -3PM = meet for apartment showing
            and respond about apartment. 
          \item \tiny 6PM - 10PM = worklife + write code 
          \end{enumerate}  

          \column{0.14\textwidth}{\textbf{\small {\underline{Wed}}}}
          \textbf{\small todo} \\
          \begin{itemize}
           \tiny \item \tiny 
          \item \tiny 
          \end{itemize}
          \textbf{\small schedule} \\
          \begin{enumerate}
            \tiny \item \tiny 8-9AM: Regular Routines 
          \item \tiny 9AM - 10AM: Send message 
            \item \tiny 6:30PM - 7:30PM = 
          \end{enumerate} 
          \column{0.14\textwidth}{\textbf{\small{\underline{Thu}}}}
          \textbf{\small todo}\\
          \begin{itemize}  
            \tiny \item \tiny 
          \item \tiny 
          \end{itemize}
          
          \textbf{\small schedule}\\
          \begin{enumerate} 
            \tiny \item \tiny 8-9AM = Regular Routines 
            \item \tiny 12-1PM = gather notes about job org. during
              session 
            \item \tiny 3:30PM - 4:30PM = meeting 
            \item \tiny 6PM - 9PM = revise emot. int. chapter and
              structure wl-cheat based on it 
          \end{enumerate} 
          
          \column{0.14\textwidth}{\textbf{\small{\underline{Fri}}}}
          \textbf{\small todo}\\ 
          \begin{itemize}
            \tiny \item \tiny Work: updates on GPU \dl{} \te{} \prio{}
          \item \tiny \te{1 hour} 
          \end{itemize}
          \textbf{\small schedule}\\
          \begin{enumerate}
            \tiny \item \tiny 8-9AM: Regular Routines 
          \end{enumerate}
          
          \column{0.14\textwidth}{\textbf{\small \underline{Sat}}}
          \textbf{\small todo}\\
          \begin{itemize} 
            \tiny \item \tiny
          \end{itemize}
          \textbf{\small schedule}\\ 
          \begin{enumerate}
            \tiny \item \tiny 7-7:30PM = food + organize.  
            \tiny \item \tiny 7:30PM -8PM = 
            \tiny \item \tiny 8PM -9PM = 
            \tiny \item \tiny 9:45PM - 10:30PM = go out 
            \tiny \item \tiny 2AM -3AM =  message Samir + add people
          \end{enumerate}
          
          \column{0.14\textwidth}{\textbf{\small \underline{Sun}}}
          \textbf{\small todo}\\
          \begin{itemize} 
           \tiny \item \tiny 
          \end{itemize}

          \textbf{\small schedule}\\
          \begin{enumerate} 
            \tiny \item \tiny 3PM - 4PM  = think about weekend, any
            other tasks 
          \item \tiny 5-7PM = Comm work 
          \item \tiny 8PM - 10PM = worklife work. 
          \end{enumerate} 
        \end{columns}
      \end{block}
    \end{column}%2
    
    %-- Column 3 --------------------------------------------------- 
    \begin{column}{0.20\linewidth}
      %-- Block 3-1 
      % On Sunday morn, put a quick synopsis of top news items                  
      % here.  Categorize as Comm and Money.      
      \begin{block}{News}
        \begin{itemize} 
          \tiny \item \tiny Jon Stewart's last episode. 
        \item \tiny Mission Impossible 
        \item \tiny 
        \end{itemize}
      \end{block}
      
      \begin{block}{Weather} 
        \begin{itemize}
          \tiny \item \tiny 
        \item \tiny 
        \end{itemize}
      \end{block} 

      \begin{block}{Clothes plan} 
        \begin{itemize}
          \tiny \item \tiny Monday
        \item \tiny Tuesday
        \item \tiny Wednesday
        \item \tiny Thursday
        \item \tiny Friday
        \end{itemize} 
      \end{block}
      %-- Block 3-2 
      
      %-- Block 3-3
      \begin{block}{Situations}
        % Howto: the below are the situations that define one another

        \begin{itemize} 

          %\tiny \item \tiny \textit{Post-talk with Meghan}: Pre-: send
          %message to wait for a month. 
          %It's not going to move anywhere, like you were saying. 
          %I'm busy with interviewing - we should keep in touch
          %though. 
          %I will let you know once things are settled where I end up.  
          %Leaving for the airport soon. 
          %Post-: check time - see if we can get to what we want to say
          %more quickly   

          \tiny \item \tiny \textit{Toastmasters} Post-: L2: good to prep
          in advance, but prep even more. L1: Watch for changing at the last minute.  
          L3: good to stay consistent L4: say thank you instead of
          thanks. 

          \tiny \item \tiny \textit{Talk to Anita} Pre-: get ready for
          phone call by looking good. Post-: laugh less (watch for
          "interesting" diversions. 
        \item \tiny \item  \textit{Shwaytha dinner:} Pre-: 1. Talk to
          Udatta Palekar (distance yourself). 2. Talk to Shwaytha about
          how she has been doing

          Back straight/ lips relaxed (like
          TM) -  Keep it throughout if possible. 
          don't crumple napkin, 

          Post-:  

        \end{itemize} 

      \end{block}
      
\begin{block}{Rel}
  \begin{itemize} 
    \small \item \small Girl from SF 
    \small \item \small Girl from L.A. 
    \small \item \small Mamta 

    %\small \item \small Ruchi 
    %\small \item \small Neha Jambhekar 
    %\small \item \small Meghan Joshi 
    %\small \item \small Vinita Ghate 
  \end{itemize} 
\end{block} 
\end{column}%3 

\end{columns}

\end{frame}


\end{document}



% -- Attic -- % 

%        \begin{itemize}
%          \tiny \item \tiny If you do something sloppy, don't
%          think about it and don't say sorry. 
%        \item \tiny don't think someone is trying to hurt you if
%          they say something.
%        \item \tiny know the paths of least stress. 
%        \item \tiny if mom does something, don't let that bite you. 
%        \end{itemize}
