\documentclass[serif,mathserif,final]{beamer}

%\mode<presentation>{\usetheme{Lankton}} 
%\mode<presentation>{\usetheme{I6pd2}} 
\mode<presentation>{\usetheme{RicePoster}} 
%%\mode<presentation>{\usetheme{ConfPoster}} 
\usepackage{amsmath,amsfonts,amssymb}
\usepackage{eulervm}

\usepackage{pxfonts}
\usepackage{graphicx, ragged2e}
\usepackage{pgffor}
\setbeamertemplate{caption}[numbered]

%\documentclass[11pt]{article}

\usepackage{ulem}
\usepackage{color}
\usepackage{xspace}
\newcommand{\bllt}{\item \small}
\newcommand{\doneTaskNoItem}[1]{\sout{#1}}
\newcommand{\doneTask}[1]{\item \sout{#1}}
\newcommand{\doneTaskHyp}[1]{\item \textcolor{blue} {\sout{#1}}}
\newcommand{\optTask}[1]{\item  \textcolor{green}{#1}}
\newcommand{\prioTask}[1]{\item  \textcolor{red}{#1}}
\newcommand{\timeEst}[1]{\textit{Time:} \textit{#1}}
\newcommand{\priority}[1]{\textit{Priority:} \textit{#1}}
\newcommand{\prio}[1]{\textit{Priority:} \textit{#1}}
\newcommand{\dueBy}[1]{\textit{Deadline:} \textit{#1}}
\newcommand{\MyName}{Vivek~Kale}
\newcommand{\fixme}[1]{\textcolor{blue}{[FIXME: #1]}}
\newcommand{\revision}[1]{\textcolor{blue}{[FIXME comment : #1]}}
\newcommand{\regItem}[1]{\item \textcolor{cyan}{#1}}
\newcommand{\regRoutineItem}[1]{\item \textcolor{green}{\textit{Reg. Routine:} #1}}
\newcommand{\situationItem}[1]{\item \textcolor{magenta}{\textit{Situation:} #1}}
\newcommand{\deadline}[1]{#1}
\newcommand{\comments}[1]{}

\graphicspath{{./figures/}}
\usepackage[orientation=landscape,size=a0,scale=1.6,debug]{beamerposter}

%-- Header and footer information ----------------------------------
\newcommand{\footleft}{Mgmt-WorkLife-weekPlan} % figure what this should be 
\newcommand{\footright}{August 2014}
\title{Month-Week-Day Plan} 
\author{Vivek Kale$^1$}
\institute{$^1$ University of Illinois at Urbana-Champaign \quad}  

%------------------------------------------------------------------
%-- Main Document ------------------------------------------------- 

% TODO: make the below document neater 
% TODO: consider stretching center column 
% TODO: check how to fit week daily plan together 

\begin{document} 
\begin{frame}{} 

  \begin{columns}[t]
%-- Column 1 ---------------------------------------------------  
\begin{column}{0.25\linewidth} %{\textbf{\underline{Week Aspects(new name)}}}
  %-- Block 1-1
  \begin{block}{ Stresses} 
    % Recognize emotions / recognize what you're worried about -> eliminate worry
    \begin{itemize}
     % \tiny \item \tiny EuroMPI paper: 
     % \small \item \tiny Ridhima saying stuff about me. 
    %\item \tiny related work:   
      % \item \tiny Atul saying let's talk about this some other time. 
      % \item \small friends of Atul's better(?): 
      % \item \small email -done : 
      % \item \small anger that you are below parents 
      % \item \small [ find others ]
    %\item \tiny others at work. 
    %\item \tiny Comm: Talking to Amit - can bounce back, just close
    %  friends.
      %\item \tiny Comm: restricted profile - take it for face
      % value, probably because I'd get angry. 
    \tiny \item \tiny Comm: Frustration about Sneha - you still are you.
    \item \tiny Comm: thinking about how Sat. went /general worries:
      don't worry and be conscious. 
    \item \tiny Comm: putting extra fb update - just did it for fun
      and whatever, if anything just local anxiety. 
    \item \tiny Comm: brother getting upset about laptop: 
    \item \tiny Comm: fb message to everyone: will go with time, was stressed about something, said Kaw later
    \item \tiny Comm: angry about weekend: she was too shy anyways
    \end{itemize} 
  \end{block} 
  %-- Block 1-2 
  
  %-- Block 1-3
  \begin{block}{ Habits } 
    \begin{itemize} 
      %\tiny \item \tiny move feet less, don't scrub on floor. 
    \tiny \item \tiny back straight. 
    \item \tiny lips relaxed. 
    \item \tiny watch what happens when a hot girl talks to you. 
    \end{itemize} 
  \end{block} 

  %-- Block 1-4
  \begin{block}{ Clothes plan } 
    \begin{itemize} 
    \tiny \item \tiny Saturday: wear polo shirt. 
    \item \tiny Saturday night: wear light blue dress shirt and jeans. (or maybe khakis and polo shirt). 
    \item \tiny Sunday: business casual shirt. 
    \item \tiny Wednesday : 
    \item \tiny Thursday: 
    \item \tiny Friday : 
    \item \tiny Saturday : Blue full shirt . 
    \item \tiny Sunday : Red shirt .
    \end{itemize} 
  \end{block} 

  %-- Block 1-5
  \begin{block}{ Food plan } 
    \begin{itemize} 
      \tiny \item \tiny Skip meals this week to take out fat from weekend. 
    \item \tiny Be very careful about food for Saturday night, along with Brunch for Sunday and dinner for Sunday. 
    \end{itemize} 
  \end{block} 
  \begin{block}{ Situations} 
    \begin{itemize} 
    \item \tiny meet with Prof. Gropp: Pre-: have data ready Post-: work on not saying extra things (to generate extra work), prep the main points, esp. beginnning in advance, prioritize (like was done for last meeting), did good on ``not saying extra''  towards the end 
      \item \tiny Meet with Atul/Ridhima: 
        \item \tiny Meet at Kukretis: Pre-: dress well Post-: don't say ``neglected'', watch laughter, know what to do when Rakesh uncle comes (script) but is ok, 
    \end{itemize}
  \end{block} 
\end{column} %2 
%-- Column 2 --------------------------------------------- 
\begin{column}{0.50\linewidth}
%{\textbf{\underline{Week TODO}}} 
% NOTE: Current policy is to comment out days as they come. 
% TODO: put in the regular routines here for each day, in the schedule box. 
  %--- Block 2-1

\begin{block}{ Week TODO} 

\begin{enumerate} 
\tiny \item \tiny Work: clean up thesis tex file to have abstract/title.  
\item \tiny \doneTask{Work: make poster for SC, and send it to Prof Gropp.}

\item \tiny worklife: fix work-life cheatsheet to have updates 
\priority{UI} + Comm: integrate howtosayit, EI, winfriends, SI, 7habits \priority{UI}. 
\item \tiny worklife: do full habits/infrastructure 
\item \tiny worklife: do situations planning 
\item \tiny Mgmt: Spaces: month plan curr.  
\item \tiny Work: make todo for apps. 
\item \tiny Mgmt: Spaces: order 10 iPhone 5s chargers.
\item \tiny GenKnowledge: get book on genKnowledge OR read NYtimes, make habits to read . 
\item \tiny Mgmt: Spaces: get rugs . 
\item \tiny Mgmt: Spaces: return taillight . 
\item \tiny Mgmt: Spaces: money: check sw old stuff; find iPad; update
  money; check money in bank. 
\item \tiny \textbf{Mgmt: Spaces: Graduation: check for credit hours
  for the summer, get new ones if needed + check grad deadlines, get
  the Neur course checked}. 
\item \tiny Work: Figure out computer (cs-grad131), and check for files/images from CS525. 

\item \tiny Work: add error checks to code + Work: figure out timings
  for app, along with PAPI profile (dummy) and the dqIdle/time. + check flops. 
\item \tiny Work: get timestep times 

\item \tiny Work: Add code structure for data collection + Find any
  other systems issues and take care of them + integrate the
  slack-conscious runtime/MPI dot prod. 
\item \tiny Work: put in hypothesis for each of the applications. 
\item \tiny Work: app code fix the problem with the per-thread lock
  for stealing / write-up 

\item \tiny Work: check for sending paper to workshop on DataFlow,
  cloud computing conference/workshop. 
\item \tiny Work: reply to Tanzima telling her what she is saying does
  not make sense \priority{doItinAdayOrTwoButSoon} \timeEst{30 mins}.
\item \tiny Mgmt: Spaces: Graduation: send messages on Post-doc to
  Prof. Gropp about Princeton / other places + Work: check with Prof
  Gropp about the Princeton post-doc. 
\item \tiny Work: reply to Tanzima. 

\end{enumerate}
\end{block} 


%\begin{columns}
%\begin{column}{0.5\columnwidth} 

\begin{block}{Week Daily Schedule} 
\textbf{\small \underline{Mon}}
\begin{enumerate} 
\tiny \item \tiny worklife+Comm: situations review. 
\end{enumerate} 

\textbf{\small \underline{Tue}}
\begin{enumerate} 
\tiny \item \tiny email updates/ admin / send message to Simplice. 
\item \tiny Take care of poster confirmation for PACT + flight . 
\item \tiny worklife+Comm: situations review.
\item \tiny Work: apps todo (NAS + nbody + MCB). 
\item \tiny Work: make latex for poster. 
\item \tiny Comm: go through meeting 
\end{enumerate} 

\textbf{\small {\underline{Wed}}}
\begin{enumerate} 
\tiny \item \tiny 
\item \tiny Comm: Speech prep + habits. 
\end{enumerate} 

\textbf{\small{\underline{Thu}}}
\begin{enumerate} 

\tiny \item \tiny \doneTask{Mgmt:webpresence: check researchgate}
\item \tiny \doneTask{Mgmt:webpresence: update google+ profile to make sure nothing crazy is publicly viewed} 
\item \tiny \doneTask{Mgmt: webpresence: blog: where to put it. } 
\tiny \item \tiny \doneTask{Work: finish trying  HACC. }

\item \tiny WOrk: finish strong scaling for nbody  \priority{UI}. 
\item \tiny Work: make graph (static, guided, uSched, vSched, sSched). 
\item \tiny \doneTask{Work: create and update poster. }

\item \tiny send Simplice reply. 
\item \tiny send Prof Gropp message to meet again. 
\item \tiny \doneTask{send message to Amaral to confirm.}
\item \tiny register for PACT. 
\item \tiny Work: finish coding updates for nbody code. 
\item \tiny Comm: read 7 habits 1st chapter and summarize \timeEst{1 hour} . 
\end{enumerate}
%\end{column}

%\begin{column}{0.5\columnwidth}

\textbf{\small {\underline{Fri}}} 
\begin{enumerate} 
\tiny \item \tiny worklife: update spaces sheets.
\item \tiny worklife: add in practice points / go through full diagram. 
\item \tiny Mgmt:webpresence: check researchgate. 
\item \tiny Work: finish the code for NAS LU, CG
\item \tiny  Work: get it to work for HACC and other benchmarks. 
\item \tiny Work: finish related work, other stuff + Work: finish writing stuff for intro and related work. 
\end{enumerate}

\textbf{\small \underline{Sat}} 
\begin{enumerate} 
\tiny \item \tiny Comm: sned message to Shyunti. 
\item \tiny Comm: send message to Neha replying. 
\item \tiny Work: send Simplice the poster draft , and compose message to describe.   Send message to Laura Grigori. 
\item \tiny worklife: worklife cheat sheet update of experiences \timeEst{30 mins.} 
\item \tiny worklife: update practice points + worklife: update worklife implementation/habits. 
\item \tiny worklife: finish emo intelligence notes on Empathy, and add into last part. 
\item \tiny Mgmt: Spaces: get laptop screen fixed. \priority{UI} 
\end{enumerate} 

\textbf{\small \underline{Sun}}
\begin{enumerate}
\tiny \item \tiny  Time for next month 
\item \tiny figure out delete of ak from fb
\item \tiny poster
\item \tiny Mgmt: Money: California in mid-August. 
\item \tiny Mgmt: Money: figure out registration for NetIP.
\item \tiny Mgmt: webpresence: make final decision to delete ak from fb \timeEst{30 mins.} \priority{Urgent} 
\item \tiny Mgmt:webpresence: put blog post to blogger.com \timeEst{1 hr}. 
\item \tiny Comm: get speech for vocal variety written up - MBA vs PhD\timeEst{1 hour}. 

\end{enumerate} 

\end{block} 

%\end{column}
%\end{columns}

\end{column}%2 

\begin{column}{0.20\linewidth} 
%{\textbf{\underline{Reg. Routines}}} 

%Block 3-1
\begin{block}{\small \textbf{\underline{Regular Routines}} }
\underline{\textbf{Morning}}
\begin{itemize}
\tiny \item \tiny Brush Teeth \timeEst{4 mins}
\item \tiny Mouthwash, Clean tongue - it helps with breath\timeEst{1mins} 
\item \tiny Eating small breakfast
\item \tiny Check your schedule for meetings / appointments for that day: Is anything urgent? \timeEst{5 mins}
\item \tiny Excercise: 1 hour ( Stretch for 10 mins, Treadmill for 30 mins , Lift weights or Yoga 1 hour, Meditation for 10 mins)
\item \tiny Shave (at least every other day) \timeEst{5 mins}
\item \tiny Shower : (shampoo+conditioner, acne wash,  soap on underarms/underbody)
\timeEst{10 mins}
\item \tiny dry hair, dry face, arms, legs, back, stomach \timeEst{3 mins}
\item \tiny Clothing: belt, check collar, shirt not half-tucked, matching socks \timeEst{5 mins}
\item \tiny Comb hair, hair gel optional \timeEst{ 1 min}
\item \tiny Check Keys/Wallet/Cell/Badge (get a bucket) \timeEst{1 min}
\item \tiny Open meds cabinet, get water, take medicines \timeEst{1 min}
\item \tiny Wear lenses and rinse out case \timeEst{ 2 mins}
\item \tiny Deodorant or cologne depending on the day \timeEst{1 min}
\item \tiny Wash your face with a face wash - it helps with acne \timeEst{3 mins}
\item \tiny Moisturize - apply lotion \timeEst{ 2 min}
\item \tiny Neti pot / clean out sinuses - if you’re feeling congested \timeEst{5 min}
\item \tiny clean out ears, nose \timeEst{5 mins}
\item \tiny Remember to lock door \timeEst{1 mins}
\end{itemize}

\underline{\textbf{Evening}}

\begin{itemize}
\tiny \item \tiny Call family: 30 mins
\item \tiny meet friends: 20 mins
\item \tiny Cleaning dishes / cleaning house: 10 mins
\item \tiny Lay out clothes for the next day, iron if necessary
\item \tiny start laundry if needed: 10 mins,
\item \tiny Collect anything you’ll need for the next day (e.g. dry cleaning to drop off): 5 mins,
\item \tiny Check Facebook/linkedin/google+: 10 mins, matrimony stuff: 10 mins,
\item \tiny Food for lunch/dinner the next day: 10 mins
\end{itemize}

\underline{\textbf{Night before bed}}
%TODO: why isn't enumerate working???
%\begin{enumerate}
\begin{itemize}
\tiny \item \tiny Finish computer stuff \timeEst{5 mins}
\item \tiny Get into sleeping clothes \timeEst{1 mins}
\item \tiny Before sleeping: brush teeth, floss \timeEst{ 2 min}
\item \tiny Properly wash and put away contacts \timeEst{ 2 mins}
\item \tiny Review the days good things \timeEst{ 10 min}
\item \tiny Light Reading \timeEst{ 10 min}
\item \tiny Prayer \timeEst{10 mins}
%\end{enumerate} 
\end{itemize}
\end{block}

\end{column}%3 

\end{columns} 

\end{frame} 

\end{document}
