\documentclass[serif, mathserif, final]{beamer}
\mode<presentation>{\usetheme{Lankton}} 
\usepackage[orientation=landscape,size=a0,scale=1.6, debug]{beamerposter}

\usepackage{amsmath,amsfonts,amssymb,pxfonts,xspace}

\usepackage{graphicx, ragged2e}
\usepackage{pgffor}
\usepackage{ulem}
\usepackage{caption}
\usepackage{courier}

\usepackage{verbatim}
\usepackage{listings}

\usepackage{float}
\usepackage{subfig}
\setbeamertemplate{caption}[numbered] 

\usepackage{calendar}
\usepackage{geometry}

%TODO: remove unneeded items 
\newcommand{\bllt}{\item \small}
\newcommand{\doneTaskNoItem}[1]{\sout{#1}}
\newcommand{\doneTask}[1]{\tiny \item \tiny \sout{#1}}
\newcommand{\doneTaskHyp}[1]{\tiny \item \tiny \textcolor{blue} {\sout{#1}}}
\newcommand{\optTask}[1]{\tiny \item \tiny \textcolor{green}{#1}}
\newcommand{\prioTask}[1]{\tiny \item \tiny \textcolor{red}{#1}}
\newcommand{\timeEst}[1]{\textit{Time:} \textit{#1}}
\newcommand{\te}[1]{\textit{TimeEst:} \textit{#1}}
\newcommand{\priority}[1]{\textit{Priority:} \textit{#1}}
\newcommand{\pr}[1]{\textit{Priority:} \textit{#1}}
\newcommand{\prio}[1]{\textit{Priority:} \textit{#1}}
\newcommand{\dueBy}[1]{\textit{Deadline:} \textit{#1}}
\newcommand{\MyName}{Vivek~Kale}
\newcommand{\fixme}[1]{\textcolor{blue}{[FIXME: #1]}}
\newcommand{\revision}[1]{\textcolor{blue}{[FIXME comment : #1]}}
\newcommand{\regItem}[1]{\item \textcolor{cyan}{#1}}
\newcommand{\regRoutineItem}[1]{\item \textcolor{green}{\textit{Reg. Routine:} #1}}
\newcommand{\situationItem}[1]{\item \textcolor{magenta}{\textit{Situation:} #1}}
\newcommand{\deadline}[1]{#1}
\newcommand{\dl}[1]{#1}
\newcommand{\comments}[1]{}

\newcommand{\footleft}{Mgmt-WorkLife-weekPlan} % figure what this should be 
\newcommand{\footright}{August 2015}

%------------------------------------------------------------------
%-- Main Document ------------------------------------------------- 
\title{Month-Week-Day Plan} 
\author{Vivek Kale$^1$}
\institute{$^1$ University of Illinois at Urbana-Champaign}  
\date{\today}

\begin{document}
    
\begin{frame}
  \begin{columns}
    %-- Column 1 --------------------------------------------------- 
    \begin{column}{0.25\linewidth} %{\textbf{\underline{Week Aspects(new name)}}}

      \begin{block}{Stresses}
        % howto:Recognize emotions / recognize (precisely) what you're worried about -> methods for eliminating worry. 
        % clean out old worries, put them in pastWorries doc.  
        % remember to define precisely 
        % order from top-to bottom
        \begin{itemize}
        \item \tiny Work: worrying about interviewing: just
          focus on the work. 
        \item \tiny Worrying about gal: think about talking to
          others 
        \item \tiny 
          % \item \tiny Comm: Worrying about not losing it (check this/ define this better) : work on sheet.  
          % there's much more to be done.  She may not be interested
          % because it's a brother. 
        \end{itemize}
      \end{block}

      \begin{block}{Real-time Confidence}
%        \begin{itemize}
%          \tiny \item \tiny If you do something sloppy, don't
%          think about it and don't say sorry. 
%        \item \tiny don't think someone is trying to hurt you if
%          they say something.
%        \item \tiny know the paths of least stress. 
%        \item \tiny if mom does something, don't let that bite you. 
%        \end{itemize}
      \end{block}
      %-- Block 1-3
      \begin{block}{Life notes}
        \begin{itemize}
        \item \tiny TM: look at intelligence book. 
        \item \tiny Problem: implement game of mastermind. 
        \end{itemize}
      \end{block}
    \end{column} %2 

    %-- Column 2 --------------------------------------------- 
    \begin{column}{0.50\linewidth}
      %--- Block 2-1
      \begin{block}{Week Summary}
        {\tiny \textbf{Week Plan:}
          Work: do startup work with GPU, Work: figure out GPU mem
          usage, Comm: talk to people from matrimony}
        {\tiny \textbf{Weekend Plan:} Meet for date, finish
          sharpen different materials/parts, bring back real data} 
      \end{block}

      \begin{block}{Running TODO} % find a better name 
        \begin{enumerate}
          % curr -->
        \item \small Mgmt:Spaces: send out letters. \te{1 hour}           
        
        \item \small Work(gpuMem): find GPU memory used  =
          \doneTaskNoItem{ Work(gpumem): find variables allocated in
            NS\_Grid.fpp} + Work(gpuMem): find variables used in NS\_Grid.fpp = (talk to Tarun about this) +
          Work(gpuMem): go through the {\tt NS\_Grid.fpp} and
          {\tt ModDataStruct.fpp} to see what is being allocated + Work(gpuMem): come up with
          formulas in latex + Work(gpumem): check everything done with ModDeriv.fpp +
          Work(gpuMem): write for Prof. Gropp and Jon  + Work(gpuMem): check
          for other functions being added (talk to John Larson about
          this) + Work(gpumem): finish estimation  + Work(gpumem):
          check script 

        \item \small Work(gpuHybStatDyn): code XPACC functions using
          GPU memory = Work(gpuHybStatDyn): have dyn +
          Work(gpuHybStatDyn): note codelet0. 
          
          \doneTask{Work: comm: message to Prof. Gropp}  \te{20 minutes} 

        \item \small Mgmt:Spaces: get meds  = \doneTaskNoItem{Mgmt:Spaces: call for meds} \te{5 minutes}
          +  Mgmt:Spaces: get meds 

        \doneTask{ Comm: reply to Gopi about meeting = L0: figure
          out message + L1: shorten  + L2: make sure it flows properly
          + L3: } 
        \doneTask{Work: comm: message to Prof. Gropp}  \te{20 minutes}  
        \doneTask{Comm: send Atul a message to let him know that
          you'll be in Chicago this Saturday}


      
        \item \small worklife: finish emot. int. book  on Cecil =
          worklife: structure + worklife:integration into sheet and
          connection with other things +
          worklife:applications/examples \te{1 hour mins}
          
        \item \small Make slides for idea \te{1 hr }

        \item \small Mgmt:webpresence: update facebook with del \te{1 hr}
        \doneTask{Comm: send message to Vinita} - ok b/c you don't
        feel comfortable.  
      \item \small Comm: talk to Atul \te{} 

      \item \small Comm: check with mm \te{}. 

      \item \small Comm: geez I really didn't like that Savvy aka
        Survesh. Sorry for letting it out. \te{} \te{}. 

      \item \small Comm: look at people and reply to them \te{1 hour}



      \item \small worklife: finish slides for management =
        worklife: toastmasters + worklife: finish picture.  
        
      \item \small Work: do coding practice planning \te{10 mins}. \te{2 hours}. 
        
      \item \small Comm: message to Shilpa Talwalkar \dl{sat night} \te{1 hour} \prio{U}.
      
      \item \small Comm: message to Anita
          
        % future (check this- and if it should be added)   -->   
        \end{enumerate}
      \end{block} 
      
      \begin{block}{Week Daily Schedule} 
        % howto: arrange items from running todo into the below
        % sheet management document. 
        \begin{columns} 
          \column{0.14\textwidth}{\textbf{\small \underline{Mon}}}
          \textbf{\small todo} \\ 
          \begin{itemize}
            \tiny \item \tiny 
          \item \tiny 
          \end{itemize} 
          \textbf{\small schedule} \\
          \begin{enumerate} 
            \tiny \item \tiny 8-9AM: Regular Routines 
          \end{enumerate} 
          
          \column{0.14\textwidth}{\textbf{\small \underline{Tue}}}
          \textbf{\small todo} \\
          \begin{itemize}
            \tiny \item \tiny             
          \end{itemize}  
          \textbf{\small schedule}\\ 
          \begin{enumerate} 
            \tiny \item \tiny
          \end{enumerate}  

          \column{0.14\textwidth}{\textbf{\small {\underline{Wed}}}}
          \textbf{\small todo} \\
          \begin{itemize}
            \doneTask{Work: send message to Jon} 
          \item \tiny Work: write out the performance estimation.  
          \item \tiny Work: write out perf. estimate. \te{10 mins}
          \item \tiny Mgmt: Spaces: get meds + Mgmt:Spaces: update
            3-month plan 
            \doneTask{Comm: message to Vinita} 
         
          \end{itemize}
          \textbf{\small schedule} \\
          \begin{enumerate}
            \tiny \item \tiny 8-9AM: Regular Routines 
          \item \tiny 9AM - 10AM: Send message 
          \item \tiny 5PM - 6PM = 
          \item \tiny 6PM - 6:30PM = 
            \item \tiny 6:30PM - 7:30PM = 
          \end{enumerate} 
          \column{0.14\textwidth}{\textbf{\small{\underline{Thu}}}}
          \textbf{\small todo}\\
          \begin{itemize}  
          \item \tiny Work: do slides for updates, try script. 
          \item \tiny Work: create code 
          \item \tiny Mgmt: Spaces: send key 
          \item \tiny Comm : talk to Meghan 
            \item \tiny Comm: Anyways, need to go for another meeting
              soon - send me your address! 
          \item \tiny Comm: send message to others  
          \end{itemize}
          
          \textbf{\small schedule}\\
          \begin{enumerate} 
            \tiny \item \tiny 8-9AM = Regular Routines 
            \item \tiny 12-1PM = gather notes about job org. during
              session 
            \item \tiny 3:30PM - 4:30PM = meeting 
            \item \tiny 6PM - 9PM = revise emot. int. chapter and
              structure wl-cheat based on it 
          \end{enumerate} 
          
          \column{0.14\textwidth}{\textbf{\small{\underline{Fri}}}}
          \textbf{\small todo}\\ 
          \begin{itemize}
            \tiny \item \tiny Work: updates on GPU \dl{}
            \tiny \item \tiny Work: 
            \te{} \prio{}
            \tiny \item \tiny Mgmt:Spaces: clean up the ViveksLaptop
            directory Work to have the work stuff integrated. 
            \tiny \item \tiny Comm: gather people from matrimony site
            \te{1 hour}. 

          \end{itemize}
          \textbf{\small schedule}\\
          \begin{enumerate}
            \tiny \item \tiny 8-9AM: Regular Routines 
          \end{enumerate}
          
          \column{0.14\textwidth}{\textbf{\small \underline{Sat}}}
          \textbf{\small todo}\\
          \begin{itemize} 
            \tiny \item \tiny
          \end{itemize}
          \textbf{\small schedule}\\ 
          \begin{enumerate}
            \tiny \item \tiny 7-7:30PM = food + organize.  
            \tiny \item \tiny 7:30PM -8PM = 
            \tiny \item \tiny 8PM -9PM = 
            \tiny \item \tiny 9:45PM - 10:30PM = go out 
            \tiny \item \tiny 2AM -3AM =  message Samir + add people
          \end{enumerate}
          
          \column{0.14\textwidth}{\textbf{\small \underline{Sun}}}
          \textbf{\small todo}\\
          \begin{itemize} 
            \tiny \item \tiny Work: Organize stuff in work directory 
          \item \tiny Mgmt: Spaces: black socks  + Mgmt:Spaces: gray
            shirt. 
          \item \tiny Worklife: post of weekend   +  (worklife: update
            picture )  + worklife: update slides )  <-- clarify what
            we were doing this week 
          \item \tiny Comm: respond to girl. 
          \end{itemize}

          \textbf{\small schedule}\\
          \begin{enumerate} 
            \tiny \item \tiny 3PM - 4PM  = think about weekend, any
            other tasks 
          \item \tiny 5-7PM = Comm work 
          \item \tiny 8PM - 10PM = worklife work. 
          \end{enumerate} 
        \end{columns}
      \end{block}
    \end{column}%2
    
    %-- Column 3 --------------------------------------------------- 
    \begin{column}{0.20\linewidth}
      %-- Block 3-1 
      % On Sunday morn, put a quick synopsis of top news items                  
      % here.  Categorize as Comm and Money.      
      \begin{block}{News}
        \begin{itemize}   
          \tiny \item \tiny Jon Stewart's last episode. 
        \item \tiny  
        \end{itemize}
      \end{block}
      \begin{block}{Weather} 
        \begin{itemize}
          \tiny \item \tiny 
        \item \tiny 
        \end{itemize}
      \end{block} 

      \begin{block}{Clothes plan} 
        \begin{itemize}
          \tiny \item \tiny Monday
        \item \tiny Tuesday
        \item \tiny Wednesday
        \item \tiny Thursday
        \item \tiny Friday
        \end{itemize} 
      \end{block}
      %-- Block 3-2 
      
      %-- Block 3-3
      \begin{block}{Situations}
        % Howto: the below are the situations that define one another

        \begin{itemize}


          \tiny \item \tiny \textit{Talk to Anita} Pre-: get ready for
          phone call by looking good. Post-: laugh less (watch for
          "interesting" diversions. 

          \tiny \item \tiny \textit{Meet with Meghan} Pre-: get
          directions  Post-: good to keep mouth shut more, watch for
          management stuff (drunk less, close door).


          \tiny \item \tiny \textit{Post-talk with Meghan}: Pre-: send
          message to wait for a month. 
          It's not going to move anywhere, like you were saying. 
          I'm busy with interviewing - we should keep in touch
          though. 

          I will let you know once things are settled where I end up.  
          Leaving for the airport soon. 

          Post-: check time - see if we can get to what we want to say
          more quickly 

        \item \tiny \textit{Meet with Simon:} Post-: don't repeat too
          much before saying bye (have a closing and opening
          memorized). 

        \item \tiny \textit{XPACC group meeting:} Pre-: discuss code
          updates for GPU with Prof Gropp (talk about how much data
          can fit in GPU) + discuss Simon comm and translating it to
          XPACC code + discuss comm and translating it. 

        \item \tiny \textit{Comm: tell Mona that you hate:} 
    \end{itemize} 
        
      \end{block}
      
\begin{block}{Rel}
  \begin{itemize} 
    \small \item \small Girl from SF 
    \small \item \small Girl from L.A. 
    \small \item \small Mamta 


    \small \item \small Ruchi
    \small \item \small Neha Jambhekar 
    \small \item \small Meghan Joshi 
    \small \item \small Vinita Ghate 
  \end{itemize} 
\end{block} 
\end{column}%3 

\end{columns}

\end{frame}
\end{document}
