\documentclass[serif, mathserif, final]{beamer}
\mode<presentation>{\usetheme{Lankton}}
\usepackage[orientation=landscape,size=a0,scale=1.6, debug]{beamerposter}
\usepackage{amsmath,amsfonts,amssymb,pxfonts,xspace}
\usepackage{graphicx,ragged2e,pgffor}
\usepackage{hyperref}
\usepackage{ulem}
\usepackage{courier}
\usepackage{caption,verbatim,listings,float,subfig} %TODO: order these 
\setbeamertemplate{caption}[numbered] 
\usepackage{calendar}
\usepackage{geometry}

%TODO: remove unneeded items 
\newcommand{\bllt}{\item \small}
\newcommand{\doneTaskNoItem}[1]{\sout{#1}}
\newcommand{\doneTask}[1]{\tiny \item \tiny \sout{#1}}
\newcommand{\doneTaskHyp}[1]{\tiny \item \tiny \textcolor{blue} {\sout{#1}}}
\newcommand{\optTask}[1]{\tiny \item \tiny \textcolor{green}{#1}}
\newcommand{\prioTask}[1]{\tiny \item \tiny \textcolor{red}{#1}}

\newcommand{\timeEst}[1]{\textit{TimeEst:}\textit{#1}}
\newcommand{\te}[1]{\textit{TimeEst:}\textit{#1}}
\newcommand{\deadline}[1]{\textit{Deadline:}\textit{#1}}
\newcommand{\dueBy}[1]{\textit{Deadline:}\textit{#1}}
\newcommand{\dl}[1]{\textit{Deadline:}\textit{#1}}
\newcommand{\priority}[1]{\textit{Priority:}\textit{#1}}
\newcommand{\prio}[1]{\textit{Priority:}\textit{#1}}
\newcommand{\pr}[1]{\textit{Priority:}\textit{#1}}

\newcommand{\MyName}{Vivek~Kale}
\newcommand{\fixme}[1]{\textcolor{blue}{[FIXME: #1]}}
\newcommand{\revision}[1]{\textcolor{blue}{[FIXME comment : #1]}}
\newcommand{\regItem}[1]{\item \textcolor{cyan}{#1}}
\newcommand{\regRoutineItem}[1]{\item \textcolor{green}{\textit{Reg. Routine:} #1}}
\newcommand{\situationItem}[1]{\item \textcolor{magenta}{\textit{Situation:} #1}}
\newcommand{\comments}[1]{}

%TODO: consider changing the below so you only use the text in the
%document 


%TODO: change Week plans 

\newcommand{\footleft}{Mgmt-WorkLife-weekPlan} % figure what this should be 
\newcommand{\footright}{August 2016}
%-- Main Document ------------------------------------------------- 
\title{Month-Week-Day Plan}\author{Vivek Kale$^1$}\institute{$^1$ 
University of Illinois at Urbana-Champaign}\date{\today} 


\begin{document}
\begin{frame} 
\begin{columns}

\column{1.0\linewidth}

\begin{block}{Projects} 
Work:code: Project - Research Paper: 
\begin{enumerate} 
\item \tiny \url{http://mpp2016.ime.uerj.br}. 
\item \tiny \url {http://sbac-pad}  - registration is  \$ 500. 
\item \tiny Put up latex.  
\item \tiny Gather all research. 
\item \tiny Gather project work. 
\item \tiny Write down introduction.
\item \tiny Gather data for OpenACC. 
\item \tiny Explain other details of setup. 
\item \tiny Note data for OpenMP. 
\end{enumerate} 

\textit{Schedule:} March 24th: do latex, March 2
Work:code:

- Project - Coding practice: p for interview.
\begin{enumerate} 
\tiny \item \tiny Work:code(cp.bm): finish bit manip:  
\item \tiny Work:code(cp.bm): finish bit manip:  finish problem 5 from book 
\item \tiny Work:code(cp.bm): finish bit manip:  finish problem 6 from book 
\item \tiny Work:code(cp.bm): finish bit manip:  finish problem 7 from book
\item \tiny Work:code(cp.bm): finish bit manip:  finish problem 8 from book  
\item \tiny Work:code(cp.bm): finish bit manip:  finish problem 9 from book 
\item \tiny Work:code(cp.bm): finish bit manip:  finish problem on
\item \tiny Work:code(cp.bt): review brainteasers – 1 day. 
\item \tiny Work:code(cp.bmpie): do graphics problem from bit manip:
  rectangular overlap. 
\item \tiny Work:code(cp.bmpie): do big endian vs. little endian := 
\item \tiny Work:code(cp.bmpie): number of ones  := 
\item \tiny Work:code(cp.bmpie): code up bit manip problems :=  
\item \tiny Work:code(cp.bt): finish brain teasers:  finish problem on
  egg drop from book.  
\item\tiny Work: code(cp.bt): talk about and write 100 lockers . 
\item \tiny Work: code(cp.bt):  finish brain teasers: finish problem on heavy
pill. 
\item \tiny Work:code(cp.btpie): finish brain teaser problems from
  programming interviews exposed. 
\item \tiny Work:code (cp.): go through C++, Work:code (cp.): go through Java +
Work:code (cp.): go through OOP. 
\item \tiny Work:code (cp.): code up problems.  – 1 week. 
\item \tiny Work:code (cp.): integer problems + numerics   -- 1 week. 
\item \tiny Work:code (cp.): practice mock interview problems. – 1 week.   
\item \tiny Work:code (cp.): finish recursion + BFS/DFS – 1 week. 
Work:code(cp.): finish recursion, Work:code(cp. ): code up problems,
Work(cp.): practice mock interview problems. 
\item \tiny Work: comm: Project –general,  Work:comm: talk to Stephen.
\end{enumerate} 
\textit{Schedule:} Work:code (cp.): finish bit manipulation, Work(cp.): review
brain teasers in book, Work(cp.): Work(cp.): go through C++.  \\ 

Project: GenKnowledge:  
House of cards: Mgmt:Spaces: 
1. Cars.  Work:rel: -  Project – Comm: rel: 
2. Comm:rel: meet others:  Sweta K. 
{\it Schedule:} meet others over summer, meet girl over summer. 

{Project: awards }  
\begin{enumerate} 
\tiny \item \tiny Figure out write-up for Fulbright. 
\item \tiny Attend Fulbright : 
\end{enumerate} 
\textit{Schedule:} April 15th: message to Stephen – 1 hour, Work:rel:Project – Awards:,  Work:rel: Project – interview with
Berkeley/MIT/industry. 

\begin{enumerate} 
\tiny \item \tiny Suny sb / suny sb / LLNL / 
\item \tiny Intel, NVIDIA, Apple
\item \tiny Google/ms / software companies, Database companies/Oracle,
\tiny \item \tiny CV: + Research Summary:  -- 1 week.  - Talking about
your research.
\item \tiny Business cards:  - use latex  -- 40 minutes.
\item \tiny Behavioral questions answers:    -- 1 week. 
\item \tiny Send emails – 1 day. 
\item \tiny Structure in latex. 
\end{enumerate}  
\textit{Schedule:} Behavioral answers – 1 week, CV prep - 1 day,
business cards, cover letter -1 hour.  

{\bf Worklife: - Project: –Comm:rel: } 
\begin{enumerate} 
\tiny \item \tiny Worklife: link management together.  
\item \tiny  Worklife: link habits comm and Toastmasters.
\item \tiny Worklife: latex viewpoint. 
\item \tiny Comm: read social intelligence first four chapters.
\item \tiny  Comm: link all comm together.
\item \tiny Worklife: get emails and texts to analyze. 
\item \tiny  Worklife: figure out how to book flights and trips quickly. 
\end{enumerate}
\textit{Schedule:}  Comm: read social intelligence first four chapters
and get a method to take in information – 5 hours. 
Comm: link comm together, worklife: latex viewpoint. 
Looking ahead: 

\underline{\textit{2-month plans}}
\underline{\textit{January and February:}}
\underline{\textit{March and April:}} 
\underline{\textit{May and June:}}
\begin{itemize}
\tiny \item \tiny do scheduling strategies. 
\item \tiny work on job talk. 
\item \tiny do travel. 
\item \tiny social on facebook, catch up with Rishi. 
\end{itemize}

\begin{block}
2-Month Plan: December: code + worklife, January: study for interviews,  \\
2-Month Plan: February: code | March:  code + interview review + finish coding work.    \\ 
2-Month Plan: April: code, May: code paper review. \\
2-month plan: June:  July:  \\ 
2-month plan: August:  September: \\
\end{block} 

\bf{Week of August $1^{st}$, 2016:} \\
\begin{itemize} 
\tiny \item \tiny Work: write up SBAC. 
\item \tiny Work: write up  cover letter. 
\item \tiny Work: finish lectures up to BFS, DFS. 
\item \tiny Work: finish coding problems on C++. 
\end{itemize} 

\bf{Week of August $7^{th}$, 2016:} \\
\begin{itemize} 
\tiny \item \tiny Work: write up SBAC. 
\item \tiny Work: write up  cover letter. 
\item \tiny Work: finish lectures up to BFS, DFS. 
\item \tiny Work: finish coding problems on C++. 
\item \tiny Comm: review win friends Inf people review + Comm: do one lesson with Social Intelligence thoroghly. 
\end{itemize} 

\bf{Week of August $14^{th}$, 2016:} \\ 
\begin{itemize} 
\tiny \item \tiny Work: review lectures for shortest path. 
\item \tiny Mgmt:Spaces: 
\tiny \item \tiny Work: review lectures + Work: do practice problems.
\end{itemize}

\bf{Week of August $24^{th}$, 2016:} \\
\begin{itemize} 
\tiny \item \tiny Work: review lectures. 
\item \tiny Comm: review win friends Inf people
\item \tiny Comm: read social intelligence chapter 2 
\item \tiny Comm: read social intelligence Chapter 4. 
\end{itemize} 


\underline{\textit{July and August:}} 
\begin{itemize}
\tiny \item \tiny Settle with interviews. 
\item \tiny move-in to apartment.
\item \tiny do papers.
\item \tiny finish social intelligence.
\end{itemize}

\underline{\textbf{Weekend Plans:}}
\textbf{Weekend of August $5^{th}$ -$7^{th}$ : } Meet mom and Dad.
\textbf{Weekend of August $12^{th}$ - $13^{th}$:} Go to San Francisco.
\textbf{Weekend of August $20^{th}$ - August $22^{nd}$:} reunion.
\textbf{Weekend of August $31^{st}$  to September $2^{nd}$ } Chicago summer.

\underline{\textbf{Upcoming situations:}} re-union, Sangita's
wedding. 

\underline{\textit{Month Plan}:}  Work: do writing of papers, Work: do
coding problems on databases and software engineering, Work: do social
intelligence notes}.   

\underline{\textit{Week Plan}:} 
\textbf{Week of August 7:}
\begin{itemize}
\item \tiny Work: finish hashing
\item \tiny Work: go through lectures for BFS and DFS. 
\item \tiny Work: review prior material.+ Work: figure out weak points. 
\item \tiny Work:rel: combine job talk. 
\item \tiny Work: figure out method to create notes:= Work: read transcript + work: read book + work: read notes + work:read. 
\item \tiny Mgmt:Spaces: get car checked.  + Mgmt:Spaces: get rid of apartment + Mgmt:webpresence: take webpage text down. 
\item \tiny Comm: message to Mona- done + Comm: message to Rishi about re-union.+ Comm: message to Kavita. 
\item \tiny Comm: message to Mugdha. 
\item \tiny Comm: message to Dad about issues. 
\end{itemize}
\end{block}
\end{columns}
\end{frame}



\begin{frame}
  \begin{columns}
    %-- Page 2: Column 1 --------------------------------------------------- 
    \begin{column}{0.25\linewidth} %{\textbf{\underline{Week Aspects(new name)}}}
      %TODO: check where this should go. -done
      %--- Page 2: Block 1-1
      \begin{block}{Routines}
        {{\tiny \bf Weather:} Warm through the week} 
        {\tiny \bf Weekend Plan:}
        \begin{itemize}
        \item \tiny ppn:028361799  exp: driver's license:K400-8728-4051  exp:2-20-18 
        \item \tiny CC1 num: CC2 num: Dbtnum:  bank acct num:  
        \item \tiny VIN:        License Plate:  E61 2444 
        \item \tiny VivekInternet’s FightingIllini  wifi pass: 2173900374 WPA 
        \item \tiny xfinity account number: 0149024144. 
        \item \tiny AAdvantage number: 847JJP0.
        \item \tiny Dad's AAdvantage number: BRU6630 Password: polarwind.
        \item \tiny Emerald Club number :  140294615   pass: 
        \item \tiny Netflix user:  lvk2408@gmail.com  Netflix password: chitrapat. 
        \end{itemize}
      \end{block}
      
      \textbf{\underline{Sunday Routines:}} Experiences, week plan. \\ 
      \textbf{\underline{Routines:}} Morning: bfast, exercise/brush,
      floss, shower (hair, eyes, ears, underarms, feet), meds, belt,
      comb hair / dishes, clean kitchen floor. |  Night: running/ put away dishes, clean kitchen floor / brush
y      teeth, charge phone, clothes for tomorrow, contacts off. \\
      
      Day trip packing list: charger for iPhone, charger for laptop, car
      keys, underwear, black socks, shoes, meds, halls meds, greyhound,
      boarding pass, flight pass. \\ 
      
      Cover letter: 
      Resume: 
      Reference Letters: \\ 
      
      \end{block} 
    %--- Page 2: Block 1-2
    \begin{block}{Map} 
      \begin{itemize} 
      \item \tiny driver's license  exp. date .  Number. 
      \item \tiny ppt number  exp. date.  
      \end{itemize}
      
      \begin{itemize} 
      \item \tiny bank account num 
      \item \tiny cc num 
      \end{itemize} 
      
      \begin{itemize} 
        \tiny \item \tiny Amtrak  eVoucher numbers. \\
      \item \tiny  Southwest credit:  \\   
      \item \tiny  Mileage number: \\ 
      \end{itemize} 
      
      \begin{itemize}
        \tiny \item \tiny VIN:  License plate: ill e61 2444  
      \item \tiny BT code for BMW:
      \end{itemize} 
      
      \begin{itemize} 
        \tiny \item \tiny other cars: lexus:  VIN:  license:
      \item \tiny Hyundai: 
      \item \tiny Audi: VIN:  License: P84  
      \end{itemize} 
      
      \begin{itemize} 
        \tiny \item \tiny Vivek's wifi:   wifi pass: 
        \item \tiny Atul’s FightingIllini  wifi pass:  2173900374 WPA  \\
        \item \tiny When tank light on, filling 13.3 gallons. 
      \end{itemize} 
      
      Local space: 
      Local map: 

      \textbf{\underline{Urbana-Champaign:}} 
        Campustown: 
        North: Engineering: 
        Main campus: 
        Southside of campus:         
        Urbana: 
        Champaign: 
        Savoy: 
        \textbf{CMI} 
        \textbf{Illini Terminal} 
        Decatur/Springfield: 
        Tuscola/Mattoon: 
        Rantoul/Paxton: 
        
        Cover letter / Resume : 5 hours .
        Behavioral questions : 
        Review what you know : 
    \end{block}
    
%--- Page 2: Block 1-3
      \begin{block}{Local Happiness}
        % howto:Recognize emotions / recognize (precisely) what you're
        % worried about -> methods for eliminating worry. 
        % clean out old worries, put them in pastWorries doc.  
        % remember to define precisely 
        % order from top-to bottom
        \begin{itemize} 
          \tiny \item \tiny Work: worrying about interviewing: just focus on the work. 
        \item \tiny Worrying about gal: think about talking to others. 
        \end{itemize}
      \end{block} 
      %--- Page 2: Block 1-4 

      \begin{block}{AngersAndAnxieties}
        % howto:Recognize emotions / recognize (precisely) what you're worried about -> methods for eliminating worry. 
        % clean out old worries, put them in pastWorries doc.  
        % remember to define precisely 
        % order from top-to bottom
        \begin{itemize}
          \item \tiny Anger about UP -> think about the positive
            perspective, and the original.
          \tiny \item \tiny Work: worrying about interviewing: just
          focus on the work. 
          \item \tiny Anger about a b  -> ...
        \end{itemize}
      \end{block}
      %-- Block 1-5
      \begin{block}{Life notes}
        \begin{itemize}
        \tiny \item \tiny Social Intelligence: 
        \item \tiny Social Intelligence: 
        \end{itemize}
      \end{block}
% howto: 
\end{column}

%-- Column 2 ---------------------------------------------

\begin{column}{0.5\linewidth} 
      \begin{block}{Week Summary}
        {\tiny \textbf{Week Plan:}  }
        {\tiny \textbf{Weekend Plan:} see Mom and Dad}
        {\tiny {\bf Week lessons:}}
        \begin{enumerate}
          \tiny \item \tiny Win Friends/ Influence People – no one
          likes to take direct orders.
        \item \tiny Go through 7 habits.
        \item \tiny Coding problem: 
        \item \tiny Chess tips: 
        \item \tiny tm tips.
        \end{enumerate} 

        {{\tiny \bf News:} M: jobless rate, First Reprogrammable
          quantum computer created, Google driver car CEO leaves, | S:
          clinton leads, trump 2nd amdm,  Rio Opening Ceremony| E:
          Fallon: }

      \begin{block}{Running TODO} % find a better name 
        \begin{enumerate}

          \doneTask{Work:rel: reply to MongoDB} \te{20 minutes}
          \pr{UI} \dl{Thurs night}. 

                 \doneTask{Mgmt:Spaces: book flight to San Francisco} \te{20
          minutes} \dl{Friday}. 
        
        \doneTask{ Work(pappub): look up papers and understand
          architectures/trends, applications. \te{1 hr} \dl{} +
          Work(pappub): read articles from hpcwire \te{1 hr} + Knight's
          landing.}      
        Knight's landing. 
        GPU architecture. 
        
      \item \tiny Work:comm:(amrel): reply to Amanda's email :=
        \doneTaskNoItem{Work:comm(amrel): tell her what's going on} +
        Work:comm(amrel): consider going to Duke for meeting and
        possibly a lecture. \doneTask{Mgmt:Time: plan out trip to San
          Francisco} \te{1 hour} \dl{Sat night}
        \pr{UrgentImportantEnoughToMaintainContacts}. 

        \textbf{Curr} $\rightarrow$ 
      \item \tiny Work(res): write journal paper. \te{2 days} \dl{}
        \pr{IU}. 
        
      \item \tiny Work: Write paper for workshop here: 
        http://mpp2016.ime.uerj.br/important-dates.html - due date
        August $16^{th}$.  \te{20 hours} \dl{-}
        \pr{ImportantToKeepYourselfKnown} + \doneTask{Work: Register
          paper for workshop on accelerating mesh applications.} \te{1
          hour}. \pr{} \dl{}.
 
      \item \tiny Work: review material you know already \te{2 hours}.
 
        \doneTask{ Work: make notes on how to take notes for a lecture}
      \item \tiny Work(cp): review difference between book and
        lectures. \te{} \dl{} \pr{} \item \tiny go through Harvard lectures. 
        
      \item \tiny Work: how to organize a project \te{30 minutes}\te{} \dl{}
        \pr{}. 



http://www2.sbc.org.br/sbac/2016/
        

I don't have plans to be at SC this year. However, I may be at
SBAC-PAD 2016. Let me know if you'll be there.

Vivek




\item \tiny Mgmt:Spaces: check hair from
  \url{http://restorehair.com/contact-us/}. 


      \item \tiny Work(cp): coding problem := Work(cp): coding
        problem on bits and arrays and hash table.  \te{1 hour}. \dl{} \pr{} 
        
      \item \tiny Work: coding review on hash tables \te{1 hour} \dl{Friday}
        \pr{IU}. \doneTask{Work(cp): MIT lecture := Work(cp): MIT lecture on
          hashing Karp-Rabin} \te{1.5 hours} \dl{before Wed}
        \pr{reasonable}. 
        
      \item \tiny Work(cp): MIT ocw lecture on DFS \te{2 hour} + Work(cp):
        MIT ocw lecture on BFS \te{2 hour}.

      \item \tiny Mgmt:Spaces: post on craigslist the ad :=
       One bedroom for rent in south loop.        

       I'm subletting my 1 bedroom convertible apartment from Sept 1st through the
       end of the lease on October 24th. The apartment has a view of
       the Lake and a view of part of Chicago's skyline. Pictures are
       below. 

       A unique aspect of the apartments in the building are the high
       cement ceilings and full-glass windows. The apartment has
       24-hour security, fitness center, lounge, and outdoor bb       area. 
       
       Water and gas is included in the rent. 


       \te{1 hour} \dl{Thursday} \pr{}. 

      \item \tiny Comm: message to Kavita  \te{1 hour} \dl{Thursday}
        \pr{} 

        It's nice to hear from you. I'm in Chicago this month
        studying. I plan to have friends over towards the end of
        August at the place I'm staying at. I hope that you and
        Ashish can join when I do.


        TODO:L3: intent: past : meet up at Irazu 
        TODO:L3: intent: I like you guys
        TODO:L3: outcome: I'm still cool. 

        TODO:L4: for when I do v VS when I do. just: gets ambiguity
        out. 
        
        TODO:L4: can v VS will  just: not too imposing  
 
      \item \tiny Work: organize job talk. \te{} \dl{} \pr{}.

      \item \tiny Work:rel: finish cover letter + Work:rel:
        respond to EPFL \te{20 minutes} \dl{Saturday night}  +
        Work:rel: gather Lawrence Scholar.
        
      \item \tiny Work:rel(trp): make a template for replies to
        companies \te{1 hour} = Work:rel(trp): respond for times that work + 
        Work:rel(trp): confirm timings for interview + Work:rel(trp):
        Thank You notes. 
        
      \item \tiny Comm: send message about a 10-year re-union \te{1 hour}. 
  
      \item \tiny Work:rel: review of interview \te{1 hour} \dl{}. 
     
      \item \tiny Work:rel: add in experiences. \te{} \dl{}. 
        
      \item \tiny Mgmt:Spaces: put up craigslist ad for apartment 
        \te{} \pr{} \dl{}. 
        
        Hey Amanda, 
        
        I'm not going to SC this year, but I'm planning to go to SBAC-PAD in
        Los Angeles this year. 
        
        Vivek 
        
      \item \tiny Comm: message to Labonee \te{1 hour}
        \dl{Sat. night} \pr{ImportantToMaintainContacts}.
        Seeing your photos of your ..., I look up to your commitment to
        excellence in what you do. I don't think I'd find this
        spirits elsewhere. This is one of the reasons I can't leave
        the Bay Area. Getting to know you and others in the bay area, I think
        there's one thing that defines this place - it's the undying
        committment to excellence that's praised. 
        P.S. The above is based on conversations I've had with Neil,
        and he ought to be cited. It's that undying committment to
        excellence that makes me want to do whatever I might do with
        excellence rather than just getting the job done. This is
        what defines the Bay Area to me. Sorry if this is lame. I
        came up with it 10 minutes. I can't leave this place. This
        is based on conversations with. 

      \item \tiny Mgmt:webpresence: update LinkedIn cover photo to picture
        of the globe \te{}\pr{}\dl{}. 
        
      \item \tiny Mgmt:Spaces(bfa): buy things for apartment =
        Mgmt:Spaces(bfa): get a vaccuum cleaner + Mgmt:Spaces(bfa):
        buy sticky putty + Mgmt:Spaces(bfa): buy a whiteboard. 

      \item \tiny Mgmt:Spaces(afx): tell about the closet door. \te{} \dl{}.        
      \item \tiny Mgmt:Spaces(bfhm): bring hamper from home +
        \doneTaskNoItem{Mgmt:Spaces(bfhm): BMW key} +
        Mgmt:Spaces(bfhm): get cereal box container \te{1 hour} \dl{}
        \pr{} + Mgmt:Spaces(bfhm): 
 
      \item \tiny Mgmt:Spaces(grc): get groceries = Mgmt:Spaces:
        Malt-O-meal + Mgmt:Spaces: pasta + Mgmt:Spaces: pizza +
        Mgmt:Spaces: cereal + 

        Mgmt:Spaces: labels for organization of kitchen cabinets +
        Mgmt:Spaces: labels for organization of fridge and freezer +
        Mgmt:Spaces: labels for organization of bathroom +
        \doneTask{Mgmt:Spaces: cucumber air freshner.} \te{} \dl{}
        \pr{UI}. 
         
      \item \tiny Mgmt:Spaces(carwash): check car tailpipe + 
        Mgmt:Spaces(carwash): Window + Mgmt:Spaces(car): get halogen
        lights for fog lights \te{1 hour} 
  
      \item \tiny Mgmt:webpresence: update website(wsu) =
        \doneTaskNoItem{Mgmt:webpresence(wsu): update formatting on
          website} + Mgmt:webpresence(wsu): update description of work.
       
        
      \item \tiny Work:rel: message to Yavatkar Kaka about
        VMWare. \te{} \dl{} \pr{}. 
        
        
\item \tiny Comm: message to Rishi and Amaeya about reunion \te{ 1
  hour} \pr{UI}  \dl{aug15}  
          
\item \tiny Comm: meet Gary and KD \te{1 hour}. 
  
\item \tiny Comm: message to Dad and Atul about social stuff \dl{} \te{1 hour}.  
          
\item \tiny Comm: consider a view of girl on Shaadi. 
\item \tiny Comm: consider what to do about Bhavna. 
\item \tiny Comm: consider talking to Illina. 
\item \tiny Comm: talk to friends from school.
\item \tiny Mgmt:Spaces: plan trips. \te{}. 
\item \tiny Mgmt:webpresence: delete Anil Taneja from
  LinkedIn. \te{1 hour} \dl{Monday} \pr{UI}.
\item \tiny Mgmt:webpresence: cancel FB friend request of
  Jocelyn + Mgmt:webpresence: check other friend requests
  sent. \te{}.
\item \tiny Mgmt:Spaces(GetThingsSpring2016): get Things =
  Mgmt:Spaces(getThings): get suit. \te{}
        \end{enumerate}
      \end{block}
      
      % howto: the below is a routine based on the job I'm doing and the
      % circumstances I'm in. Note that this is different from routines
      % above, which is true for a long-term period of over 10 years.  


\begin{block}{Weekly routines} 
\begin{itemize}
\tiny \item \tiny 630 am: wake up, turn off alarm clock, brush teeth
\item \tiny 645 am: eat breakfast
715 am: lift weights
730 am: look up weather, read emails
800 am: watch algorithms lectures, review programming problems
11 am : research stuff
12 pm : eat lunch
1 pm - 3 pm : programming
3 pm - 5 pm : applications/emails/meetings/phone calls
5 pm  - 6 pm : running
6 pm  - 7:30 pm : dinner
8 pm - 9 pm : talk to you and mom
9 pm - 10:30 pm : finish emails
10:30 pm - 11:30 pm : read books / articles on meditation or self-help.
\end{itemize} 

On weekends, I take care of chores and things I didn't finish during
the weekday. 
On Saturday: 

\end{block} 

\begin{block}{Weekly Meetings}
  \begin{itemize} 
  \item \tiny IWOMP affinity meeting Thursday 7 AM PDT / 9 AM
    CDT call in: 805-639-779 pswd: places. 
    https://llnl.webex.com/llnl/j.php?MTID=m33950b76befb72c0cbc31ea2e3be720c  
  \item \tiny DEG group meeting. 
  \item \tiny 
  \end{itemize}
\end{block} 


\begin{block}{Week Daily Schedule} 
  {\bf Sun:} Work: write paper for waacpd, Mgmt:Spaces: , Mgmt:Time:
  organize weekPlanDoc, Mgmt:Time: make plan for doing different
  things, Comm: 
    \newline {\bf Mon:}
    \newline {\bf Tues:}
    \newline {\bf Wed:}
    \newline {\bf Thur:} Work: finish putting amplification paper
    together. Work: put paper on results for workshop. Work: do hash
    table implementation, Mgmt:Spaces: do flight for SF, Comm: send message to Labonee. 
    \newline {\bf Fri:} 
    \newline {\bf Sat:} 
\end{block} 

% ------ Page 2: Column 3
\begin{column}{0.25\linewidth}
% ------ Block 2.3.1 

      \begin{block}{Weather}
        \begin{itemize}
          \tiny \item \tiny Chicago: Cool throughout the week, Warm
          Thursday and Friday. 
          \item \tiny Champaign: Cool throughout the week. 
        \end{itemize}
      \end{block} 

      \begin{block}{Food Plan} 
        \begin{itemize}
          \tiny \item \tiny 
        \item \tiny 
        \item \tiny 
        \end{itemize}
      \end{block} 

      \begin{block}{Clothes plan} 
        \begin{itemize}
          \tiny \item \tiny Monday
        \item \tiny Tuesday
        \item \tiny Wednesday
        \item \tiny Thursday
        \item \tiny Friday
        \end{itemize} 
      \end{block}
      %-- Block 3-2 

      %-- Block 3-3 
      \begin{block}{Situations}
        % Summary: the below are the situations that define one
        % another.        
        % Howto: Put post notes of each situation from list of previous
        % week. Put high importance situations in situationslist. 
        % Put list of upcoming situations on Sunday morning with Pre. 
        \begin{itemize}

        \item \tiny \textit{Meet Mona and Leena} 
          Pre-: Confirm time, leave by 7PM, wear business clothes, rent a car? Discuss
          savv0ddude , talk about girl, explain what you are doing(rehearse),
          have closing for meeting next, take picture and put post on
          FB. 
          Post-:          
        \end{itemize} 
      \end{block} 
%Summary:  

\begin{block}{Spaces}
\begin{itemize} 
\tiny \item \tiny 
\item \tiny 
\item \tiny 
\end{itemize} 
\end{block} 

\begin{block}{Rel} 
  \begin{itemize} 
    \small \item \small  from SF. 
    \item \small Shwetha K 
    \item \small Mamta       
    \item \small SH11680694 from San Francisco. 
    \item \small Sandhya N. 22 Jun 2016 
    \item \small Aarti S - 27 - 5' 9'' Charlotte.       
    \item \small Anu M from Chicago, IL 
    \item \small Pranati A from Cleveland, OH - 
    \item \small Meghana K from New York - 
    \item \small Ssd S - 28 , 5 5 , Boston, MA 
    \item \small Anj B. - 30 yrs - SH13882555.
  \end{itemize} 
    %\small \item \small Meghan Joshi 

% Accept our apologies for the delayed response. We spoke to our son
% about your daughter and we are interested also. When is a good time
% for us to call you? 

\begin{itemize}
\item \small
  \url{http://profile.marathimatrimony.com/profiledetail/viewprofile.php?id=K658342&osa=dbos&memval=3&listtype=1&msgId=&rq=&loadPage=12&listtype=1&tabtype=16&filtertype=1&filtered=0&viewed=2&TotCnt=367&Show=Y&Module=} 
\item \small \url{http://profile.marathimatrimony.com/profiledetail/viewprofile.php?id=M3730924&osa=dbos&memval=1&listtype=1&msgId=&rq=&loadPage=13&listtype=1&tabtype=16&filtertype=1&filtered=0&viewed=0&TotCnt=367&Show=Y&Module=}
  
\item \small \url{http://profile.marathimatrimony.com/profiledetail/viewprofile.php?id=R1194547&osa=dbos&memval=4&listtype=1&msgId=&rq=&loadPage=11&listtype=1&tabtype=16&filtertype=1&filtered=0&viewed=3&TotCnt=367&Show=Y&Module=}
  
\item \small \url{http://profile.marathimatrimony.com/profiledetail/viewprofile.php?id=R1762507&osa=dbos&memval=6&listtype=1&msgId=&rq=&loadPage=1&listtype=1&tabtype=16&filtertype=1&filtered=0&viewed=5&TotCnt=367&Show=Y&Module=}

\item \small \url{http://profile.marathimatrimony.com/profiledetail/viewprofile.php?id=R1194547&osa=dbos&memval=4&listtype=1&msgId=&rq=&loadPage=11&listtype=1&tabtype=16&filtertype=1&filtered=0&viewed=3&TotCnt=367&Show=Y&Module=}

\item \small \url{http://www.shaadi.com/profile?profileid=SH13882555&ubt=L2luYm94L3BlbmRpbmcvcmVjZW50LWludGVyZXN0c3xpbmJveDo1YjhmMGM0ZTViMTM4YmU2ZjUxNDAzMTVlM2M4OWJhMnw4NDI3ZGVlYjMzMTg2MmUzMDc1N2E5Mjg0OGEyZjc2OQ\%3D\%3D&source=unified&evt_ref=aW5ib3gtaW50ZXJlc3Rz&datasrc=api}

\item \small \url{http://www.shaadi.com/profile?profileid=bSH74851794&ubt=L2luYm94L3BlbmRpbmcvcmVjZW50LWludGVyZXN0c3xpbmJveDo1YjhmMGM0ZTViMTM4YmU2ZjUxNDAzMTVlM2M4OWJhMnxlNzMxMWM0NmM2ODNjZmRhM2JlODY0NTQzMzIxODg5Mw\%3D\%3D&source=unified\&evt_ref=aW5ib3gtaW50ZXJlc3Rz&datasrc=api}

\item \small \url{http://www.shaadi.com/profile?profileid=ISH08025255&ubt=L2luYm94L3BlbmRpbmcvcmVjZW50LWludGVyZXN0c3xpbmJveDo1YjhmMGM0ZTViMTM4YmU2ZjUxNDAzMTVlM2M4OWJhMnwyMDJhNGVlNzk5NGI0MjlmZTliMTkwODQzMDQ5NDRmYg\%3D\%3D&source=unified&evt_ref=aW5ib3gtaW50ZXJlc3Rz&datasrc=api} 
\end{itemize} 
\end{block} 

\begin{block} 
Mgmt:webpresence: 
Researchgate, linkedIn, twitter, website, facebook 
Friends: Amit, Sangita, Anchit, Kevin. 
Rel: Sruthi 
\end{block} 

\end{column}%3 






\comments{
      \begin{block}{Week Daily Schedule} 
        % howto: arrange items from running todo into the below
        % sheet management document. 
        \begin{columns} 
          \column{0.14\textwidth}{\textbf{\small \underline{Mon}}}
          \textbf{\small todo} \\ 
          \begin{itemize}
            \tiny \item \tiny Add in schedule
          \item \tiny 
          \end{itemize} 
          \textbf{\small schedule} \\
          \begin{enumerate} 
            \tiny \item \tiny 8-9AM: Regular Routines 
          \end{enumerate} 
          
          \column{0.14\textwidth}{\textbf{\small \underline{Tue}}}
          \textbf{\small todo} \\
          \begin{itemize}
            \tiny \item \tiny Work: make project sheet \te{10 minutes} 
          \item \tiny Mgmt:Spaces: check for diploma \te{10 minutes} 
          \end{itemize}  
          \textbf{\small schedule} 
          \begin{enumerate}
            \tiny \item \tiny 10AM - 11AM = 
          \item \tiny 11AM - 12AM = make long-term goals 
          \item \tiny 12PM - 2PM = 
            \tiny \item \tiny 2PM -3PM = 
          \item \tiny 6PM - 10PM = 
          \end{enumerate} 
          
          \column{0.14\textwidth}{\textbf{\small {\underline{Wed}}}}
          \textbf{\small todo} \\
          \begin{itemize}
           \tiny \item \tiny Work: finish slides for tomorrow. 
           \item \tiny Mgmt: Spaces: update fb 
         \item \tiny Comm: fb update 
          \end{itemize}
          \textbf{\small schedule} \\
          \begin{enumerate}
            \tiny \item \tiny 8-9AM: Regular Routines 
          \item \tiny 9AM - 10AM: Send message 
            \item \tiny 6:30PM - 7:30PM = 
          \end{enumerate} 
          \column{0.14\textwidth}{\textbf{\small{\underline{Thu}}}}
          \textbf{\small todo}\\
          \begin{itemize}  
            \tiny \item \tiny 
          \item \tiny 
          \end{itemize} 

          \textbf{\small schedule}\\
          \begin{enumerate} 
            \tiny \item \tiny 8-9AM = Regular Routines 
            \item \tiny 12-1PM = gather notes about job org. during
              session 
            \item \tiny 3:30PM - 4:30PM = meeting 
            \item \tiny 6PM - 9PM = revise emot. int. chapter and
              structure wl-cheat based on it 
          \end{enumerate}  
          
          \column{0.14\textwidth}{\textbf{\small{\underline{Fri}}}}
          \textbf{\small todo}\\ 
          \begin{itemize}
          \item \tiny Work: code review. 
          \item \tiny Work: finish work. 
          \item \tiny Mgmt:Spaces: Haircut \te{10 minutes}. 
          \item \tiny Comm: check messages 
          \end{itemize}
          \textbf{\small schedule}\\
          \begin{enumerate}
            \tiny \item \tiny 8-9AM: Regular Routines 
          \end{enumerate}
           
          \column{0.14\textwidth}{\textbf{\small \underline{Sat}}}
          \textbf{\small todo}\\
          \begin{itemize} 
            \tiny \item \tiny
          \end{itemize}
          \textbf{\small schedule}\\ 
          \begin{enumerate}
            \tiny \item \tiny 7-7:30PM = food + organize.  
            \tiny \item \tiny 7:30 PM - 8 PM = 
            \tiny \item \tiny 8 PM - 9 PM = 
            \tiny \item \tiny 9:45 PM - 10:30 PM = go out 
            \tiny \item \tiny 2AM -3AM =  message Samir + add people
          \end{enumerate}
          \column{0.14\textwidth}{\textbf{\small \underline{Sun}}}
          \textbf{\small todo}\\
          \begin{itemize} 
           \tiny \item \tiny 
          \end{itemize}
          \textbf{\small schedule}\\
          \begin{enumerate} 
            \tiny \item \tiny 3PM - 4PM =  . 
          \item \tiny 5-7PM = Comm work. 
          \item \tiny 8PM - 10PM = worklife work. 
          \end{enumerate} 
        \end{columns}
      \end{block}
    \end{column}%2
}


\end{columns}
\end{frame}

    
\end{document}


% -- Attic -- % 

%        \begin{itemize}
%          \tiny \item \tiny If you do something sloppy, don't
%          think about it and don't say sorry. 
%        \item \tiny don't think someone is trying to hurt you if
%          they say something.
%        \item \tiny know the paths of least stress. 
%        \item \tiny if mom does something, don't let that bite you. 
%        \end{itemize}
