\documentclass[serif, mathserif, final]{beamer}
\mode<presentation>{\usetheme{Lankton}}
\usepackage[orientation=landscape,size=a0,scale=1.6, debug]{beamerposter}
\usepackage{amsmath,amsfonts,amssymb,pxfonts,xspace}
\usepackage{graphicx,ragged2e,pgffor}
\usepackage{hyperref}
\usepackage{ulem}
\usepackage{courier}
\usepackage{caption,verbatim,listings,float,subfig} %TODO: order these 
\setbeamertemplate{caption}[numbered] 
\usepackage{calendar}
\usepackage{geometry}

%TODO: remove unneeded items 
\newcommand{\bllt}{\item \small}
\newcommand{\doneTaskNoItem}[1]{\sout{#1}}
\newcommand{\doneTask}[1]{\tiny \item \tiny \sout{#1}}
\newcommand{\doneTaskHyp}[1]{\tiny \item \tiny \textcolor{blue} {\sout{#1}}}
\newcommand{\optTask}[1]{\tiny \item \tiny \textcolor{green}{#1}}
\newcommand{\prioTask}[1]{\tiny \item \tiny \textcolor{red}{#1}}

\newcommand{\timeEst}[1]{\textit{TimeEst:}\textit{#1}}
\newcommand{\te}[1]{\textit{TimeEst:}\textit{#1}}
\newcommand{\deadline}[1]{\textit{Deadline:}\textit{#1}}
\newcommand{\dueBy}[1]{\textit{Deadline:}\textit{#1}}
\newcommand{\dl}[1]{\textit{Deadline:}\textit{#1}}
\newcommand{\priority}[1]{\textit{Priority:}\textit{#1}}
\newcommand{\prio}[1]{\textit{Priority:}\textit{#1}}
\newcommand{\pr}[1]{\textit{Priority:}\textit{#1}}

\newcommand{\MyName}{Vivek~Kale}
\newcommand{\fixme}[1]{\textcolor{blue}{[FIXME: #1]}}
\newcommand{\revision}[1]{\textcolor{blue}{[FIXME comment : #1]}}
\newcommand{\regItem}[1]{\item \textcolor{cyan}{#1}}
\newcommand{\regRoutineItem}[1]{\item \textcolor{green}{\textit{Reg. Routine:} #1}}
\newcommand{\situationItem}[1]{\item \textcolor{magenta}{\textit{Situation:} #1}}

\newcommand{\comments}[1]{}

%TODO: consider changing the below so you only use the text in the
%document 


%TODO: change Week plans 

\newcommand{\footleft}{Mgmt-WorkLife-weekPlan} % figure what this should be 
\newcommand{\footright}{August 2016}
%-- Main Document ------------------------------------------------- 
\title{Month-Week-Day Plan}\author{Vivek Kale$^1$}\institute{$^1$ 
University of Illinois at Urbana-Champaign}\date{\today} 

\begin{document}
\begin{frame} 

\begin{columns}
\column{1.0\linewidth}

\begin{block}{Projects} 

Work:code: Project - Research Paper: 
\begin{enumerate} 
\item \tiny \url{http://mpp2016.ime.uerj.br} 
\item \tiny \url {http://sbac-pad}  - registration is  \$ 500 .   
\item \tiny Put up latex.  
\item \tiny Gather all research. 
\item \tiny Gather project work. 
\item \tiny Write down introduction.     
\item \tiny Gather data for OpenACC. 
\item \tiny Explain other details of setup.
\item \tiny Note data for OpenMP.  
\end{enumerate} 

\textit{Schedule:} March 24th: do latex, March 25th, March 26th
Work:code: - Project - Coding practice: p for interview. 
\begin{enumerate} 
\tiny \item \tiny Work:code(cp.bm): finish bit manip:  
\item \tiny Work:code(cp.bm): finish bit manip:  finish problem 5 from book 
\item \tiny Work:code(cp.bm): finish bit manip:  finish problem 6 from book 
\item \tiny Work:code(cp.bm): finish bit manip:  finish problem 7 from book
\item \tiny Work:code(cp.bm): finish bit manip:  finish problem 8 from book  
\item \tiny Work:code(cp.bm): finish bit manip:  finish problem 9 from book 
\item \tiny Work:code(cp.bm): finish bit manip:  finish problem on
\item \tiny Work:code(cp.bt): review brainteasers – 1 day. 
\item \tiny Work:code(cp.bmpie): do graphics problem from bit manip:
  rectangular overlap. 
\item \tiny Work:code(cp.bmpie): do big endian vs. little endian := 
\item \tiny Work:code(cp.bmpie): number of ones  := 
\item \tiny Work:code(cp.bmpie): code up bit manip problems :=  
\item \tiny Work:code(cp.bt): finish brain teasers:  finish problem on
  egg drop from book.  
\item\tiny Work: code(cp.bt): talk about and write 100 lockers . 
\item \tiny Work: code(cp.bt):  finish brain teasers: finish problem on heavy
pill . 
\item \tiny Work:code(cp.btpie): finish brain teaser problems from programming
interviews exposed. 
\item \tiny Work:code (cp.): go through C++, Work:code (cp.): go through Java +
Work:code (cp.): go through OOP. 
\item \tiny Work:code (cp.): code up problems.  – 1 week. 
\item \tiny Work:code (cp.): integer problems + numerics   -- 1 week. 
\item \tiny Work:code (cp.): practice mock interview problems. – 1 week.   
\item \tiny Work:code (cp.): finish recursion + BFS/DFS – 1 week. 
Work:code(cp.): finish recursion, Work:code(cp. ): code up problems,
Work(cp.): practice mock interview problems. 
\item \tiny Work: comm: Project –general,  Work:comm: talk to
  Stephen. 

\end{enumerate} 
\textit{Schedule:} Work:code (cp.): finish bit manipulation, Work(cp.): review
brain teasers in book, Work(cp.): Work(cp.): go through C++.  \\ 
\begin{enumerate} 
\tiny \item \tiny Figure out write-up for Fulbright.
\item \tiny Attend Fulbright : 
\end{enumerate} 
\textit{Schedule:} April 15th: message to Stephen – 1 hour,
Work:rel:Project – Awards:,  Work:rel: Project – interview with
Berkeley/MIT/industry: 

\tiny \item \tiny cover letters:  

\begin{enumerate} 
\tiny \item \tiny Suny sb / suny sb / LLNL / 
\item \tiny Intel, NVIDIA, Apple
\item \tiny Google/ms / software companies, Database companies/Oracle,

\tiny \item \tiny CV: + Research Summary:  -- 1 week.  - Talking about
your research.

\item \tiny Business cards:  - use latex  -- 40 minutes.
\item \tiny Behavioral questions answers:    -- 1 week. 
\item \tiny Send emails – 1 day. 
\item \tiny Structure in latex. 
\end{enumerate}

\textit{Schedule:} Behavioral answers – 1 week, CV prep - 1 day,
business cards. Worklife: - Project: – Comm:rel: 

\begin{enumerate} 
\tiny \item \tiny Worklife: link management together. 
\item \tiny  Worklife: link habits comm and Toastmasters.
\item \tiny Worklife: latex viewpoint. 
\item \tiny Comm: read social intelligence first four chapters.
\item \tiny  Comm: link all comm together.
\item \tiny Worklife: get emails and texts to analyze. 
\item \tiny  Worklife: figure out how to book flights and trips quickly. 
\end{enumerate}
\textit{Schedule:}  Comm: read social intelligence first four chapters
and get a method to take in information – 5 hours. 

Comm: link comm together, worklife: latex viewpoint. 

Looking ahead: 

\underline{\textit{2-month plans}}

\underline{\textit{January and February:}}

\underline{\textit{March and April:}} 

\underline{\textit{May and June:}}
\begin{itemize}
\tiny \item \tiny do scheduling strategies. 
\item \tiny work on job talk. 
\item \tiny do travel. 
\item \tiny social on facebook, catch up with Rishi. 
\end{itemize} 

\underline{\textit{July and August:}} 

\begin{itemize}
\tiny \item \tiny Settle with interviews. 
\item \tiny move-in to apartment.
\item \tiny do papers.
\item \tiny finish social intelligence.
\end{itemize} 

\underline{\textit{Month Plan}: Work: do writing of papers, Work: do
  coding problems on databases and software engineering, Work: do
  social intelligence notes} 

\underline{\textit{Week Plan}:} 

\textbf{Week of August 1: }  

\textbf{Week of August 4:} 

\underline{\textbf{Weekend Plans:}}
\textbf{Weekend of August $5^{th}$ -$7^{th}$ : } Meet mom and Dad.
\textbf{Weekend of August $12^{th}$ - $13^{th}$:} Go to San Francisco.
\textbf{Weekend of August $20^{th}$ - August $22^{nd}$:} reunion.
\textbf{Weekend of August $31^{st}$  to September $2^{nd}$ } Chicago
summer. 

GenKnowledge: 
House of cards: 

Mgmt:Spaces: 
1.Cars. 


Work:rel: -  Project – Comm: rel: 
4. Comm:rel: meet others:  Sweta K. 
{\it Schedule:} meet others over summer, meet girl over summer. 






\end{block}

\end{columns}
\end{frame} 
          Interested.
          Long-term: patterns, teaching, research. I'd like to teach. 
          I'm also interested in performance modeling and theoretical 
          analysis. I'm aware of several good researchers at 
          surrounding universities. This is why I'm inclined to take 
          the position or another position that comes up.
          Applying to other places. 
          Let me know if you have updates.

\begin{frame}
  \begin{columns}
    %-- Page 2: Column 1 --------------------------------------------------- 
    \begin{column}{0.25\linewidth} %{\textbf{\underline{Week Aspects(new name)}}}
      %TODO: check where this should go. -done
      %--- Page 2: Block 1-1 

      \begin{block}{Routines}
        \textbf{\underline{Sunday Routines:}} Experiences, week plan. \\ 
        \textbf{\underline{Routines:}} Morning: bfast, exercise/brush,
        floss, shower (hair, eyes, ears, underarms, feet), meds, belt,
        comb hair / dishes, clean kitchen floor. |  Night: running/ put away dishes, clean kitchen floor / brush
        teeth, charge phone, clothes for tomorrow, contacts off. \\
        Cover letter: 
        Resume: 
        Reference Letters:  
      \end{block} 

      %--- Page 2: Block 1-2
      \begin{block}{Map} 
        Day trip packing list: charger for iPhone, charger for laptop, car
        keys, underwear, black socks, shoes, meds, halls meds, greyhound,
        boarding pass, flight pass. 

        \begin{itemize} 
          \item \tiny driver's license  exp. date .  Number. 
          \item \tiny ppt number  exp. date.  
        \end{itemize}

        \begin{itemize} 
        \item \tiny bank account num 
        \item \tiny cc num 
        \end{itemize} 
        
        \begin{itemize} 
          \tiny \item \tiny Amtrak  eVoucher numbers. \\
         \item \tiny  Southwest credit:  \\   
         \item \tiny  Mileage number: \\ 
        \end{itemize} 

 
        \begin{itemize}
        \tiny \item \tiny VIN:  License plate: ill e61 2444  
          \item \tiny BT code for BMW:
        \end{itemize} 

        \begin{itemize} 
          \tiny \item \tiny other cars: lexus:  VIN:  license:
        \item \tiny  Hyundai: 
        \item \tiny  Audi: VIN:  License: P84  
        \end{itemize} 

        \begin{itemize} 
        \tiny \item \tiny Vivek's wifi:   wifi pass: 
        \item \tiny Atul’s FightingIllini  wifi pass:  2173900374 WPA  \\
        \item \tiny When tank light on, filling 13.3 gallons. 
        \end{itemize} 

        Local space: 
        Local map: 

        \textbf{\underline{Urbana-Champaign:}} 
        Campustown: 
        North: Engineering: 
        Main campus: 
        Southside of campus: 
        
        Urbana: 
        Champaign: 
        Savoy: 
        \textbf{CMI} 
        \textbf{Illini Terminal} 
        Decatur/Springfield: 
        Tuscola/Mattoon: 
        Rantoul/Paxton: 

\end{block}

%--- Page 2: Block 1-3
      \begin{block}{Local Happiness}
        % howto:Recognize emotions / recognize (precisely) what you're
        % worried about -> methods for eliminating worry. 
        % clean out old worries, put them in pastWorries doc.  
        % remember to define precisely 
        % order from top-to bottom
        \begin{itemize}
          \item \tiny 
          \tiny \item \tiny Work: worrying about interviewing: just focus on the work. 
        \item \tiny Worrying about gal: think about talking to others. 
        \end{itemize}
      \end{block}
      
      %--- Page 2: Block 1-4
      \begin{block}{AngersAndAnxieties}
        % howto:Recognize emotions / recognize (precisely) what you're worried about -> methods for eliminating worry. 
        % clean out old worries, put them in pastWorries doc.  
        % remember to define precisely 
        % order from top-to bottom
        \begin{itemize}
          \item \tiny Anger about UP -> think about the positive
            perspective, and the original.
          \tiny \item \tiny Work: worrying about interviewing: just
          focus on the work. 
          \item \tiny Anger about a b  -> ...
        \end{itemize}
      \end{block}
      %-- Block 1-5
      \begin{block}{Life notes}
        \begin{itemize}
        \tiny \item \tiny Life 
        \item \tiny 
        \end{itemize}
      \end{block} 
% howto: 
\end{column}

%-- Column 2 ---------------------------------------------

\begin{column}{0.5\linewidth} 
      \begin{block}{Week Summary}
        {\tiny \textbf{Week Plan:}  Work: rel: respond to interview,
          Mgmt:webpresence: update website, 
          Mgmt:Spaces: finish trip planning, 
          Work: finish interview preparation, 
          Mgmt:Spaces: do move-in, Work: finish writing papers}
        {\tiny \textbf{Weekend Plan:}  see Mom and Dad} 

        {\tiny {\bf Week lessons:}}

        \begin{enumerate}
          \tiny \item \tiny Win Friends/ Influence People – no one
          likes to take direct orders.
        \item \tiny Go through 7 habits.
        \item \tiny Coding problem: 
        \item \tiny Chess tips: 
        \item \tiny tm tips. 
        \end{enumerate} 

        { News: M: First Reprogrammable quantum computer created,
          jobless rate increases in July | S: Trump's non-endorsement
          of Ryan,  Rio Opening Ceremony|  E: Fallon:  Seinfeld} 

        {Weather:  }
        Weekend Plan: 
        \begin{itemize}
        \item \tiny ppn:028361799  exp: driver's
          license:K400-8728-4051  exp:2-20-18
        \item \tiny CC1 num: CC2 num: Dbtnum:  bank acct num: 
        \item \tiny VIN:  License Plate:  E61 2444
        \item \tiny VivekInternet’s FightingIllini  wifi pass:
          2173900374 WPA. 
        \item \tiny xfinity account number: 0149024144. 
        \item \tiny AAdvantage number: 847JJP0. 
        \item \tiny Dad's AAdvantage number: BRU6630 Password:
          polarwind. 
        \item \tiny Emerald Club number :  140294615   pass:   
        \item \tiny Netflix user:  lvk2408@gmail.com  Netflix 
          password: chitrapat. 
        \end{itemize} 
      \end{block}


      \begin{block}{Running TODO} % find a better name 
        \begin{enumerate} 
        \item \tiny \doneTask{worklife: read 7 habits summary. }
        \item \tiny \doneTask{Comm: rel: catch up on matrimony.} \te{1
          hour}.           
          \doneTask{Work:rel: apply to EPFL.}  
          \doneTask{Mgmt:Spaces: put shower curtain in apartment +
            Mgmt:Spaces: install coffee tables + Mgmt:Spaces: clean up}.
          \doneTask{Work:rel: reply to MongoDB.} 
          \doneTask{ Work: add title to technical report and put it on
            the web.} 
          \doneTask{Work(pappub): look up conference papers - SBAC pad
            in Los Angeles} \te{1 hour}.

        \item \tiny \doneTask{Comm: FB like of Amit's baby?}. 
          \doneTask{Work: rel: respond to MongoDB} \te{1 hour}
          \dl{Teusday} 

        \item \tiny \doneTask{ Work:admin: Create CV in latex from
          Resume.} 

        \doneTask{Mgmt:Spaces: get internet taken care of :=
          Mgmt:Spaces: call comcast for account number
        \item \tiny Mgmt:Spaces: get internet in backyard checked. }

        \item \tiny Mgmt:Spaces:(asp):  =
          \doneTaskNoItem{Mgmt:Spaces:(asp)get bar stools} +
          \doneTaskNoItem{Mgmt:Spaces:(asp): get broom for sweeping} +
          \doneTaskNoItem{Mgmt:Spaces:(asp): test laundry machine}  +
          \doneTaskNoItem{Mgmt:Spaces(asp):get sofa constructed}  +
          \doneTaskNoItem{Mgmt:Spaces(asp): get butter and syrup for
            pancakes.} 


        \doneTask{ Work:rel: message to Professor Chapman discussing
          whether they figured out the result} \te{1
            hour}. \dl{Thursday night / Friday morning}. 

          Interested. 

          Long-term: patterns, teaching, research. I'd like to teach. 
          I'm also interested in performance modeling and theoretical
          analysis. I'm aware of several good researchers at
          surrounding universities. This is why I'm inclined to take
          the position. 
          Applying to other places. 
          Let me know if you have updates.

          Dear Professor Chapman, 

          Please let me know the outcome of my interview when you
          have a chance. 

          Vivek


          Dear Professor Chapman, 
         
          Please let me know the outcome of my interview when you have a
          chance. 
      
          Dear Professor Chapman, 
          Can you please let me know the outcome of my interview when
          you have a chance? 
          Thanks,
             Vivek 
          TODO:L0+L1: 

          TODO:L2+L3: past: no response 
                      intent: let me know, I give up, I still want the
                      job if you have it. 
                      outcome: give a job if you still have it. 

          TODO:L3: Interview Outcome v VS Outcome of interview VS
          Interview's Outcome just: be casual, but formal - done 
          TODO:L4:  VS - 
          TODO:L5: please VS [OMIT] 
          TODO:L5:  Thanks VS [OMIT]
        \doneTask{ Mgmt:webpresence: update Twitter cover
          photo} \te{} \pr{} \dl{}. 

        \doneTask{Comm: send message to meet Mona and Leena } \te{1
          hour} 

        \doneTask{Comm: fb like of Atul's marathon picture} \te{1 hour} \dl{}. 
        \doneTask{Comm: respond to Kavita's message.} \te{1 hour}
        \dl{}.


          \textbf{Curr-->} $\rightarrow$. 

        \item \tiny Work: Write paper for workshop here:
          http://mpp2016.ime.uerj.br/important-dates.html - due date 
          August $16^{th}$.  \te{20 hours} \dl{-}
          \pr{ImportantToKeepYourselfKnown} + Work:Register paper for
          workshop on accelerating mesh applications. \te{1 hour}.

        \item \tiny Work(pappub): look up papers and understand
          architectures/trends, applications. \te{1 hr} \dl{} +
          Work(pappub): read articles from hpcwire \te{1 hr}.

        \item \tiny Work(ocw): Watch lectures on BFS and DFS. \te{10
          minutes}.
        \item \tiny Work: coding review on hash tables. \te{1 hour} 
        \item \tiny Work: coding review on databases.\te{1 hour} 
        \item \tiny Work(cp): coding problem := Work(cp): coding
          problem on bits and arrays and hash table. 


        \item \tiny Work(cp): MIT lecture := Work(cp): MIT lecture on
          hashing Karp-Rabin \te{1.5 hours} \dl{before Wed}
          \pr{reasonable}.
 
        \item \tiny Work:comm:(amrel): reply to Amanda's email :=
          \doneTaskNoItem{Work:comm(amrel): tell her what's going on}  +
          Work:comm(amrel): consider going to Duke for meeting and
          possibly a lecture.
         \doneTask{Mgmt:Time: plan out trip to San Francisco} \te{ 1
           hour} \dl{Sat night} \pr{UrgentImportantEnoughToMaintainContacts}. 
        \item \tiny Work:rel: reply to MongoDB \te{20 minutes} \pr{UI}
          \dl{Thurs night}. 
        \item \tiny Work:rel: respond to EPFL \te{20 minutes}
          \dl{Saturday night}. --------

        \item \tiny Work:rel: review of interview \te{1 hour} \dl{}.

        \item \tiny Mgmt:webpresence(wsu): update website = 
          Mgmt:webpresence(wsu): update picture on website  +
          Mgmt:webpresence(wsu): update formatting on website +
          Mgmt:webpresence(wsu): update courses on website +
          Mgmt:webpresence(wsu): update webpages := 
        \item \tiny Mgmt:webpresence: update website(wsu) :=
          \doneTaskNoItem{Mgmt:webpresence(wsu): update picture on website}  +
          \doneTaskNoItem{Mgmt:webpresence(wsu): update formatting on
            website} + \doneTaskNoItem{Mgmt:webpresence(wsu): update
            courses on website} + Mgmt:webpresence(wsu): update
          description of work. 


        \item \tiny Comm: message to Labonee \te{1 hour} 
          \dl{Sat. night} \pr{ImportantToMaintainContacts}. 

        Seeing your photos of your ..., I look up to your commitment to
        excellence in what you do.  I don't think I'd find this
        spirits elsewhere. This is one of the reasons I can't leave the Bay
        Area. 

        Getting to know you and others in the bay area, I think
        there's one thing that defines this place - it's the undying
        committment to excellence that's praised. 

        P.S. The above is based on conversations I've had with Neil,
        and he ought to be cited. 

        It's that undying committment to excellence that makes me
        want to do whatever I might do with excellence rather than
        just getting the job done. This is what defines the Bay Area
        to me. 
        
        Sorry if this is lame. I came up with it 10 minutes. I can't leave
        this place . This is based on conversations with.

        \item \tiny Comm: message to Rishi and Amaeya about reunion +
          Comm: message to Leena and Mona to meetup. 


        \item \tiny Comm: meet Gary and KD \te{1 hour}. \doneTask{Comm: add Cheryl Tymonko to FB} \te{10minutes}. \doneTask{Comm: fb like of Dhara's picture.}
          \te{1 minute}. 

        \item \tiny Mgmt:Spaces: book flight to San Francisco \te{20
          minutes} \dl{Friday}. 
        \item \tiny Mgmt:Spaces: put up craigslist ad for
          apartment \te{} \pr{} \dl{}. 
        \item \tiny Mgmt:webpresence: update LinkedIn cover photo to 
          picture of the globe \te{}\pr{}\dl{}. 

        \item \tiny \doneTaskNoItem{Mgmt:Spaces: parking} + \doneTaskNoItem{Mgmt:Spaces: rent for apartment} +
          Mgmt:Spaces: tell about the closet door. 

        \item \tiny Mgmt:Spaces(bfhm): bring hamper from home +
          Mgmt:Spaces(bfhm): BMW key + Mgmt:Spaces(bfhm): get cereal
          box + Mgmt:Spaces(bfhm): get 

        \item \tiny Mgmt:Spaces(carwash): check car tailpipe. +
          Mgmt:Spaces(carwash): Window + Mgmt:Spaces(car): get halogen
          lights for fog lights \te{1 hour}.
        \item \tiny Work: coding practice problem on arrays. \te{1
          hour}. 

        \item \tiny Work:rel: message to Yavatkar Kaka about VMWare.
        \item \tiny Work(res): write journal paper. 
        \item \tiny Work: make a template for replies to companies. 
        \item \tiny Comm: send message about a 10-year re-union. \te{1
          hour}. 

        \item \tiny Comm: message to Mona and Leena.  
        \item \tiny Comm: FB like Dhara's picture.
        \item \tiny Comm: consider a view of girl on Shaadi. 
        \item \tiny Comm: consider what to do about Bhavna. 
        \item \tiny Comm: consider talking to Illina. 
        \item \tiny Comm: talk to friends from school.           
        \item \tiny Mgmt:Spaces: plan trips.

        \item \tiny Mgmt:webpresence: delete Anil Taneja from
          LinkedIn. \te{1 hour} \dl{Monday} \pr{UI}. 

        \item \tiny Mgmt:webpresence: cancel FB friend request of
          Jocelyn + Mgmt:webpresence: check other friend requests
          sent. 

        \item \tiny Mgmt:Spaces(GetThingsSpring2016): get Things =
          Mgmt:Spaces(getThings): get suit. 

        \end{enumerate}        
      \end{block}

\begin{block} 

Mgmt:webpresence: 

Researchgate, linkedIn, twitter, website, facebook 

Friends: Amit, Sangita, Anchit, Kevin. 

Rel: 

- Sruthi 
- 

\end{block}

\begin{block}{Weekly Meetings} 
  \begin{itemize} 
  \item \tiny IWOMP affinity meeting Thursday 7 AM PDT / 9 AM
    CDT call in: 805-639-779 pswd: places. 
    https://llnl.webex.com/llnl/j.php?MTID=m33950b76befb72c0cbc31ea2e3be720c  
  \item \tiny DEG group meeting. 
  \item \tiny 
  \end{itemize}
  
  \begin{block} {Week Daily Schedule} 
    {\bf Sun:}
    \newline {\bf Mon:}
    \newline {\bf Tues:}
    \newline {\bf Wed:}
    \newline {\bf Thur:} Work: finish putting amplification paper
    together as tr 
    Work: put paper on results for workshop. 
    Work: do hash table implementation. 
    Mgmt:Spaces: do flight for SF. 
    Comm: send message to Labonee. 
    \newline {\bf Fri:} 
    \newline {\bf Sat:} 
\end{block} 

% ------ Page 2: Column 3
\begin{column}{0.25\linewidth}
% ------ Block 2.3.1

      \begin{block}{Weather}
        \begin{itemize}
          \tiny \item \tiny Chicago: Cool throughout the week.
          \item \tiny Champaign: Cool throughout the week. 
        \end{itemize}
      \end{block}

      \begin{block}{Clothes plan} 
        \begin{itemize}
          \tiny \item \tiny Monday
        \item \tiny Tuesday
        \item \tiny Wednesday
        \item \tiny Thursday
        \item \tiny Friday
        \end{itemize} 
      \end{block}
      %-- Block 3-2 

      %-- Block 3-3 
      \begin{block}{Situations}
        % Summary: the below are the situations that define one
        % another.        
        % Howto: Put post notes of each situation from list of previous
        % week. Put high importance situations in situationslist. 
        % Put list of upcoming situations on Sunday morning with Pre. 
        \begin{itemize}
        \item \tiny \textit{Meet Atul to fix}
          Pre-:  don't talk too much. 
          Post-: 
        \item \tiny \textit{Interview with MongoDB} 
          Pre-: Have headset, try out code. 
          Post-: 
        \item \tiny \textit{Meet parents:} 

        \end{itemize} 
      \end{block} 
%Summary:  

\begin{block}{Spaces}
\begin{itemize} 
\tiny \item \tiny 
\item \tiny 
\item \tiny 
\end{itemize} 
\end{block} 

\begin{block}{Rel}

  \begin{itemize} 
    \small \item \small  from SF. 
    \item \small Shwetha K 
    \item \small Mamta       
    \item \small SH11680694 from San Francisco. 
    \item \small Sandhya N. 22 Jun 2016 
    \item \small Aarti S - 27 - 5' 9'' Charlotte.       
    \item \small Anu M from Chicago, IL 
    \item \small Pranati A from Cleveland, OH - 
    \item \small Meghana K from New York - 
    \item \small Ssd S - 28 , 5 5 , Boston, MA 
    \item \small Anj B. - 30 yrs - SH13882555.
  \end{itemize} 
    %\small \item \small Meghan Joshi 

% Accept our apologies for the delayed response. We spoke to our son
% about your daughter and we are interested also. When is a good time for us to
% call you? 


\begin{itemize}
    \item \small
      \url{http://profile.marathimatrimony.com/profiledetail/viewprofile.php?id=K658342&osa=dbos&memval=3&listtype=1&msgId=&rq=&loadPage=12&listtype=1&tabtype=16&filtertype=1&filtered=0&viewed=2&TotCnt=367&Show=Y&Module=}

\item \small \url{http://profile.marathimatrimony.com/profiledetail/viewprofile.php?id=M3730924&osa=dbos&memval=1&listtype=1&msgId=&rq=&loadPage=13&listtype=1&tabtype=16&filtertype=1&filtered=0&viewed=0&TotCnt=367&Show=Y&Module=}

\item \small \url{http://profile.marathimatrimony.com/profiledetail/viewprofile.php?id=R1194547&osa=dbos&memval=4&listtype=1&msgId=&rq=&loadPage=11&listtype=1&tabtype=16&filtertype=1&filtered=0&viewed=3&TotCnt=367&Show=Y&Module=}

\item \small \url{http://profile.marathimatrimony.com/profiledetail/viewprofile.php?id=R1762507&osa=dbos&memval=6&listtype=1&msgId=&rq=&loadPage=1&listtype=1&tabtype=16&filtertype=1&filtered=0&viewed=5&TotCnt=367&Show=Y&Module=}

\item \small \url{http://profile.marathimatrimony.com/profiledetail/viewprofile.php?id=R1194547&osa=dbos&memval=4&listtype=1&msgId=&rq=&loadPage=11&listtype=1&tabtype=16&filtertype=1&filtered=0&viewed=3&TotCnt=367&Show=Y&Module=}

\item \small \url{http://www.shaadi.com/profile?profileid=SH13882555&ubt=L2luYm94L3BlbmRpbmcvcmVjZW50LWludGVyZXN0c3xpbmJveDo1YjhmMGM0ZTViMTM4YmU2ZjUxNDAzMTVlM2M4OWJhMnw4NDI3ZGVlYjMzMTg2MmUzMDc1N2E5Mjg0OGEyZjc2OQ\%3D\%3D&source=unified&evt_ref=aW5ib3gtaW50ZXJlc3Rz&datasrc=api}

\item \small \url{http://www.shaadi.com/profile?profileid=bSH74851794&ubt=L2luYm94L3BlbmRpbmcvcmVjZW50LWludGVyZXN0c3xpbmJveDo1YjhmMGM0ZTViMTM4YmU2ZjUxNDAzMTVlM2M4OWJhMnxlNzMxMWM0NmM2ODNjZmRhM2JlODY0NTQzMzIxODg5Mw\%3D\%3D&source=unified\&evt_ref=aW5ib3gtaW50ZXJlc3Rz&datasrc=api}

\item \small
  \url{http://www.shaadi.com/profile?profileid=ISH08025255&ubt=L2luYm94L3BlbmRpbmcvcmVjZW50LWludGVyZXN0c3xpbmJveDo1YjhmMGM0ZTViMTM4YmU2ZjUxNDAzMTVlM2M4OWJhMnwyMDJhNGVlNzk5NGI0MjlmZTliMTkwODQzMDQ5NDRmYg\%3D\%3D&source=unified&evt_ref=aW5ib3gtaW50ZXJlc3Rz&datasrc=api}
\end{itemize} 


\end{block} 
\end{column}%3 


\comments{
      \begin{block}{Week Daily Schedule} 
        % howto: arrange items from running todo into the below
        % sheet management document. 
        \begin{columns} 
          \column{0.14\textwidth}{\textbf{\small \underline{Mon}}}
          \textbf{\small todo} \\ 
          \begin{itemize}
            \tiny \item \tiny Add in schedule
          \item \tiny 
          \end{itemize} 
          \textbf{\small schedule} \\
          \begin{enumerate} 
            \tiny \item \tiny 8-9AM: Regular Routines 
          \end{enumerate} 
          
          \column{0.14\textwidth}{\textbf{\small \underline{Tue}}}
          \textbf{\small todo} \\
          \begin{itemize}
            \tiny \item \tiny Work: make project sheet \te{10 minutes} 
          \item \tiny Mgmt:Spaces: check for diploma \te{10 minutes} 
          \end{itemize}  
          \textbf{\small schedule} 
          \begin{enumerate}
            \tiny \item \tiny 10AM - 11AM = 
          \item \tiny 11AM - 12AM = make long-term goals 
          \item \tiny 12PM - 2PM = 
            \tiny \item \tiny 2PM -3PM = 
          \item \tiny 6PM - 10PM = 
          \end{enumerate} 
          
          \column{0.14\textwidth}{\textbf{\small {\underline{Wed}}}}
          \textbf{\small todo} \\
          \begin{itemize}
           \tiny \item \tiny Work: finish slides for tomorrow. 
           \item \tiny Mgmt: Spaces: update fb 
         \item \tiny Comm: fb update 
          \end{itemize}
          \textbf{\small schedule} \\
          \begin{enumerate}
            \tiny \item \tiny 8-9AM: Regular Routines 
          \item \tiny 9AM - 10AM: Send message 
            \item \tiny 6:30PM - 7:30PM = 
          \end{enumerate} 
          \column{0.14\textwidth}{\textbf{\small{\underline{Thu}}}}
          \textbf{\small todo}\\
          \begin{itemize}  
            \tiny \item \tiny 
          \item \tiny 
          \end{itemize} 

          \textbf{\small schedule}\\
          \begin{enumerate} 
            \tiny \item \tiny 8-9AM = Regular Routines 
            \item \tiny 12-1PM = gather notes about job org. during
              session 
            \item \tiny 3:30PM - 4:30PM = meeting 
            \item \tiny 6PM - 9PM = revise emot. int. chapter and
              structure wl-cheat based on it 
          \end{enumerate}  
          
          \column{0.14\textwidth}{\textbf{\small{\underline{Fri}}}}
          \textbf{\small todo}\\ 
          \begin{itemize}
          \item \tiny Work: code review. 
          \item \tiny Work: finish work. 
          \item \tiny Mgmt:Spaces: Haircut \te{10 minutes}. 
          \item \tiny Comm: check messages 
          \end{itemize}
          \textbf{\small schedule}\\
          \begin{enumerate}
            \tiny \item \tiny 8-9AM: Regular Routines 
          \end{enumerate}
           
          \column{0.14\textwidth}{\textbf{\small \underline{Sat}}}
          \textbf{\small todo}\\
          \begin{itemize} 
            \tiny \item \tiny
          \end{itemize}
          \textbf{\small schedule}\\ 
          \begin{enumerate}
            \tiny \item \tiny 7-7:30PM = food + organize.  
            \tiny \item \tiny 7:30 PM - 8 PM = 
            \tiny \item \tiny 8 PM - 9 PM = 
            \tiny \item \tiny 9:45 PM - 10:30 PM = go out 
            \tiny \item \tiny 2AM -3AM =  message Samir + add people
          \end{enumerate}
          \column{0.14\textwidth}{\textbf{\small \underline{Sun}}}
          \textbf{\small todo}\\
          \begin{itemize} 
           \tiny \item \tiny 
          \end{itemize}
          \textbf{\small schedule}\\
          \begin{enumerate} 
            \tiny \item \tiny 3PM - 4PM =  . 
          \item \tiny 5-7PM = Comm work. 
          \item \tiny 8PM - 10PM = worklife work. 
          \end{enumerate} 
        \end{columns}
      \end{block}
    \end{column}%2
}


\end{columns}
\end{frame}

    
\end{document}


% -- Attic -- % 

%        \begin{itemize}
%          \tiny \item \tiny If you do something sloppy, don't
%          think about it and don't say sorry. 
%        \item \tiny don't think someone is trying to hurt you if
%          they say something.
%        \item \tiny know the paths of least stress. 
%        \item \tiny if mom does something, don't let that bite you. 
%        \end{itemize}
