\documentclass[serif, mathserif, final]{beamer}
\mode<presentation>{\usetheme{Lankton}} 
\usepackage[orientation=landscape,size=a0,scale=1.6, debug]{beamerposter}
%\usepackage[orientation=landscape,size=a0,scale=1.4,debug]{beamerposter}
%\usepackage[absolute,overlay]{textpos} % <-- can  use this to position text (solves problem of earlier yesterday with poster placement). 

%\documentclass[serif,mathserif,final]{beamer}
%\mode<poster>{\usetheme{RicePoster}}
\usepackage{amsmath,amsfonts,amssymb,pxfonts,xspace}

\usepackage{graphicx, ragged2e}
\usepackage{pgffor}
\usepackage{ulem}
\usepackage{caption}
\usepackage{courier}

\usepackage{verbatim}

%\usepackage[usenames,dvipsnames]{xcolor}    
\usepackage{listings}

\usepackage{float}
\usepackage{subfig}
\setbeamertemplate{caption}[numbered] 

\usepackage{calendar}
\usepackage{geometry}

%\graphicspath{{./figures/}}                                                   
%\usepackage{beamerposter}
%\graphicspath{{./figures/}} 
\newcommand{\bllt}{\item \small}
\newcommand{\doneTaskNoItem}[1]{\sout{#1}}
\newcommand{\doneTask}[1]{\tiny \item \tiny \sout{#1}}
\newcommand{\doneTaskHyp}[1]{\tiny \item \tiny \textcolor{blue} {\sout{#1}}}
\newcommand{\optTask}[1]{\tiny \item \tiny \textcolor{green}{#1}}
\newcommand{\prioTask}[1]{\tiny \item \tiny \textcolor{red}{#1}}
\newcommand{\timeEst}[1]{\textit{Time:} \textit{#1}}
\newcommand{\te}[1]{\textit{TimeEst:} \textit{#1}}
\newcommand{\priority}[1]{\textit{Priority:} \textit{#1}}
\newcommand{\pr}[1]{\textit{Priority:} \textit{#1}}
\newcommand{\prio}[1]{\textit{Priority:} \textit{#1}}
\newcommand{\dueBy}[1]{\textit{Deadline:} \textit{#1}}
\newcommand{\MyName}{Vivek~Kale}
\newcommand{\fixme}[1]{\textcolor{blue}{[FIXME: #1]}}
\newcommand{\revision}[1]{\textcolor{blue}{[FIXME comment : #1]}}
\newcommand{\regItem}[1]{\item \textcolor{cyan}{#1}}
\newcommand{\regRoutineItem}[1]{\item \textcolor{green}{\textit{Reg. Routine:} #1}}
\newcommand{\situationItem}[1]{\item \textcolor{magenta}{\textit{Situation:} #1}}
\newcommand{\deadline}[1]{#1}
\newcommand{\dl}[1]{#1}
\newcommand{\comments}[1]{}

%\graphicspath{{./figures/}}
%\usepackage[orientation=landscape,size=a0,scale=1.6,debug]{beamerposter}

%-- Header and footer information ----------------------------------
\newcommand{\footleft}{Mgmt-WorkLife-weekPlan} % figure what this should be 
\newcommand{\footright}{April 2015}

%------------------------------------------------------------------
%-- Main Document ------------------------------------------------- 
\title{Month-Week-Day Plan} 
\author{Vivek Kale$^1$}
\institute{$^1$ University of Illinois at Urbana-Champaign}  
\date{\today}

% TODO: make the below document neater 
% TODO: consider stretching center column 
% TODO: check how to fit week daily plan together .  

\begin{document}  

\begin{frame}{} 
  \begin{columns}
    %-- Column 1 --------------------------------------------------- 
    \begin{column}{0.22\linewidth}
      \begin{block}{Happiness Generation - must maintain every week.} 
        % explain happiness: show gratitude
        % remember to show gratitude
        \begin{itemize}
          \tiny \item \tiny happy that I have Atul to show me.  
        \item \tiny Happy that I have normal life up to this point.  
        \item \tiny Thankful that I got a chance to do what I did on Saturday. 
        \item \tiny Think about Neha Jamb. 
        \item \tiny Think about dad saying, I understand, and want you to be happy. 
        \end{itemize}
      \end{block}

    \begin{block}{Habits} 
      \begin{itemize} 
        %\tiny \item \tiny move feet less, don't scrub on floor. 
        \tiny \item \tiny back straight + eye contact. 
      \item \tiny Reduce things. 
      \item \tiny lips relaxed. 
      \item \tiny watch what happens when a hot girl talks to you. 
      \end{itemize} 
    \end{block} 
  \end{column} %1

  \begin{column}{0.5\linewidth}
    %-- Block 2-1 
    \begin{block}{ 10-year plan }
      \begin{itemize}
      \item \small Make someone and dad proud.
      \end{itemize}
    \end{block}
    
    \begin{block}{ 3-year plan }
      \begin{itemize}
      \item \small find someone
      \item \small make 150K
      \item \small network
      \end{itemize}
    \end{block} 

    \begin{block}{6-month plan}
      \begin{itemize}
        \small \item \small results + thesis
      \item \small routine + worklife
      \item \small 
      \end{itemize}
    \end{block} 
    
    \begin{block}{Month-by-month}
      \begin{itemize}
%      \item \small Early December: finish slides for defense.
%      \item \small Mid-december: put together things. 
%      \item \small Late December: send out thesis to others 
%      \item \small Late January: Defend.
%      \item \small Mid-Feb: finish thesis, start looking for jobs. 
%      \item \small Late feb: jobs+ and vacation. 
%      \item \small March: 
%      \item \small \textit{April:}  

      \item \small \textit{May:} Work: finish paper  + Work: comm:
        finish resume and cover letter. 

      \item \small \textit{June:} Work: code org and plan + Work:
        finish code + worklife: org + worklife: finish emotional int +
        Comm: experiences + Comm: TM 

      \item \small \textit{July:} Work: library, Work:comm: job
        introductions, Comm: meet people. 
      
      \item \small \textit{August:} Work: library documentation and
        experimentation, Work: comm: resume prep + Work:comm:linkedIn
        + Work: comm: interviewing skills, Comm: stay in touch
        through phone ... 
      \item \small \textit{September:} Work: paper writing + Work:comm: interviewing + Comm: stay in touch - dating? -think
        about this ...
      \end{itemize}
    \end{block}

%TODO: prioritize 
%\begin{column}{0.33\linewidth} {\textbf{\underline{Month Plan for August 2014}}}      %-- Block 1-1   
\begin{block}{\underline{\textbf{June goals}}} 
\begin{enumerate} 
  \small \item \small Work: slides 
  \small \item \small Work: code plan. 
  \item \small worklife: org. 
  \item \small Comm: TM speech + worklife: finish emotional int. + Worklife: organize
    social intelligence. 
\end{enumerate}
\end{block}

\begin{block}{\small \underline{\textbf{Week of June $1^{st}$}}}
\begin{enumerate}
\tiny \item \tiny Work: slides 
\item \tiny Work:comm: send to Google + Work: comm: organize for interview.
\item \tiny Mgmt:Time: planning \te{1 day}. 
\item \tiny Comm: plan for TM meeting.
\item \tiny Comm: planning + Comm: read on last chapter of emotional intelligence. 
\end{enumerate}
\end{block}


\begin{block}{\small \underline{\textbf{Week of June $8^{th}$}}}
\begin{enumerate}
\tiny \item \tiny Work: slides + Work: take down feedback. 
\item \tiny Mgmt:Spaces: organization
\item \tiny Comm: TM org 
\end{enumerate}
\end{block}

\begin{block}{\small \underline{\textbf{Week of June $16^{th}$}}}
\begin{enumerate}
\tiny \item \tiny Work: code
\item \tiny Work:comm: finish email to Bronis
\item \tiny worklife: get worklife updated 

\end{enumerate}
\end{block}

\begin{block}{\small \underline{\textbf{Week of June $26^{th}$}}}
\begin{enumerate}
\tiny \item \tiny 
\item \tiny 
\item \tiny 
\end{enumerate}
\end{block}

\end{column}

%-- Column 3 ---------------------------------------------

\begin{column}{0.28\linewidth}
\begin{block}{\small \textbf{\underline{Regular Routines}} }
\input{../../../ViveksLaptop/Life/workLifeMgr/regularRoutines}
\end{block} 
\end{column}%3 
\end{columns} 
\end{frame}


\begin{frame}{} 
  \begin{columns}
    %-- Column 1 --------------------------------------------------- 
    \begin{column}{0.25\linewidth} %{\textbf{\underline{Week
      %Aspects(new name)}}}
      \begin{block}{Habits}
        \begin{itemize}
          \tiny \item \tiny 
        \item \tiny 
        \item \tiny 
        \item \tiny 
        \end{itemize}
      \end{block}
      %-- Block 1-1 
      \begin{block}{Happiness}  
        \begin{enumerate}
          \tiny \item \tiny Think about happy thoughts about meeting
          someone else.  
        \item \tiny 
        \end{enumerate}
      \end{block} 

      \begin{block}{Stresses}
        % Recognize emotions / recognize (precisely) what you're worried about -> methods for eliminating worry. 
        % clean out old worries, put them in pastWorries doc.  
        % remember to define precisely 
        % order from top-to bottom
        \begin{itemize}
          \tiny \item \tiny Worrying about thesis finish. Be sincere
          and work, we make mistakes with time. Get the facts about
          completion. Go find the path. If I can't get it done, then we'll do
          something else. 
        \item \tiny Work: worrying about interviewing: just
          focus on the work. 
        \item \tiny Worrying about gal: think about talking to
          others 
        \item \tiny 
          % \item \tiny Comm: Worrying about not losing it (check this/ define this better) : work on sheet.  
          % \item \tiny Worrying about deep: forget her, because
          % there's much more to be done.  She may not be interested
          % because it's a brother. 
        \end{itemize} 
      \end{block}
 
      \begin{block}{Real-time Confidence}
        \begin{itemize}
          \tiny \item \tiny If you do something sloppy, don't
          think about it and don't say sorry. 
        \item \tiny don't think someone is trying to hurt you if
          they say something.
        \item \tiny know the paths of least stress. 
        \item \tiny if mom does something, don't let that bite you. 
        \end{itemize}
      \end{block}
      
     %-- Block 1-3
      \begin{block}{Life notes} 
        \begin{itemize} 
          \tiny \item \tiny Level 0+1: focus on finding Happiness. 
        \item \tiny Level 2: 
        \item \tiny Level 4.1: Writing: prefer standard to offbeat. 
        \item \tiny Level 4.2: Body Language: lips relaxed
        \item \tiny Level 4.3: Vocal Variety: shout. 
        \item \tiny TM: work on speech for submission to blog, increasing intentionality. 
        \item \tiny Mgmt/habits: finish chapter 1 reading notes and habits. 
        \end{itemize}     
      \end{block}
    \end{column} %2 
    
    %-- Column 2 --------------------------------------------- 
    \begin{column}{0.50\linewidth}
      %{\textbf{\underline{Week TODO}}} 
      % NOTE: Current policy is to comment out days as they come. 
      % TODO: put in the regular routines here for each day, in the schedule box. 
      %--- Block 2-1
      \begin{block}{Week Summary}
%    {\tiny \textbf{Weekend Plan:} Work: write introduction + Work:
%      finish techniques + Work: finish related work and conclusions +
%      Work:comm: send message about introduction, Work:comm: send
%      message about postdoc, Comm: send pics from graduation }\\

        
%          \doneTask{Mgmt:Spaces:get passport stuff done +
%          Mgmt:Spaces:
%          disconnect service from lexus 
%          Work:admin:send talk title, Work:comm: Google survey +
%          Work:comm:applications, Mgmt:Time: planing for summer,
%          Comm: send message to plan for next week
%          Work: submit paper (send message to Prof. Gropp), prep. for
%          job talk, Work:comm: send message to Tripti, Comm: BMM
%          flight booking.}

          {\tiny \textbf{Weekend Plan:}  Meet with Atul and make plan,
            anger management, Send message to Bronis.}

        {\tiny \textbf{Week Plan:} Work:comm: finish offer stuff,
          Work: finish HiPC paper, Work: finish email to Bronis,
          worklife: finish relaxation methods + worklife: read
          emot.int., Mgmt:Spaces: xm radio cancellation}

%worklife: finish reading
%         Emot. Int. + worklife: spaces management + worklife: time
%          management. } 

      \end{block} 
      
      \begin{block}{Running TODO} % find a better name 
        \begin{enumerate} 
        \item \small worklife: get worklife stuff done =  worklife:
          update car sheet + worklife: make more metrics + worklife:
          add more to T.M. + worklife: experiences documentation +
          worklife: figure out ways to be more efficient + worklife:
          find how to use full levels simultaneously + worklife: read
          books frequently + Mgmt:Spaces: put gift money in bank. 

      \item \small Work: submit resume to companies  =
        Work:comm:submit to dropBox + Work:comm: submit resume to Facebook (talk
        to Rajesh Nishtala) + Work: submit
        resume to MS = (Work:comm: talk to Britney Bullis) +
        Work:comm: submit resume to Amazon. 

      \item \small Mgmt:Spaces: plane ticket to LA.  + Mgmt:Spaces:
        BMM registration + Mgmt:Spaces: consider hotel near the
        conference for July $3^{rd}$ and July $4^{th}$.  +
        Mgmt:Spaces: Talk to Dhanashree about this \te{1 hour}
        \dl{June $10^{th}$ and before prices go up}
        \prio{ImportantForSocial} 

      \doneTask{ Work: job talk slides. \te{30 mins} = Work(jb):
        update first piece of code  + Work(jb): shorten extreme-scale
        slides + Work(jb): put conclusions last part (take out first
        parts) + Work(jb): app add/update to app slides + Work(jb):
       remember other things to add + Work(jb): send to Prof. Gropp.}

    \item \small Work: finish review from the job talk  = Work:
      write in job talk summary + update slides necessary, with
      overview added. \priority{I} 
      
    \item \small Work: Talk to Prof. Gropp about paper to put as
      tech. report \te{1 hour}. 
        
    \item \small Work:comm: send message to Ashley and John . 
 
   \item \small Work:admin: prep = \doneTaskNoItem{registration} +
      flight + travel request from Prof. Gropp.  
    \item \small Work:comm: send message to Prof. Gropp about job
      talk. 

      \doneTask{Mgmt:Spaces: finish booking for travel} 

    \item \small Work: make plan for the next 3 months to handover
      \priority{IU} \dl{Thurs}.

    \item \small Work: send message to Schloss Dagstuhl \te{1 hour} 
    \item \small Comm: TM prep \te{1 hour} = Comm: TM prep + Comm:call
      for meeting + Comm: call

% curr --> 

    \item \small Work:comm: send message to Bronis \te{3  hour} \dl
      {beforeIWOMPThisWeekend} \priority{IU}

   \item \small Worklife: do planning for next 3 months. \te {1
      hour}. 
%    \item \small Work: + work:comm:  coding practice with Atul
     \item \small worklife: TM. 
     \item \small worklife: consider portrait of who you are now. 
     \item \small worklife: experiences sheet add
     \item \small worklife: make easier to maneuver with docs = get
       overview sheet - put in power point + make easier to navigate
       through docs + faster addition to experiences. 
     \item \small Mgmt:Spaces: Sirius XM  = cancel sirius XM + add
       sirius XM. 
     \item \small Mgmt:Spaces: get air freshner.
     \item \small worklife(cd): make car diagram = worklife(cd): diagram for
       cleanliness/smell + worklife(cd): diagram for interior washing +
       worklife(cd): diagram for organizing things + worklife(cd): diagram for
       exterior = worklife(cd): diagram for wheels + worklife(cd): diagram
       for windows + worklife(cd): diagram for exterior = (worklife(cd):diagram for bumpers + worklife(cd):diagram for metal). 

%      \item \small Mgmt:Spaces: put up BMW license plate =
%        Mgmt:Spaces: figure out correct color coord (social and what
%        looks good on car) 
      %\item \small Comm: talk to Udatta Palekar \te{1 hour} 
      \item \small Work: paper updates \te{2 hours}. 

      \item \small Comm: arrange time to meet for TM. 
      \item \small Comm: prep for TM speech.   
      \item \small Work:comm: send message to Bronis.
      \item \small Comm: send Rishi a message about BMM. \te{10 mins} 


        \end{enumerate}
      \end{block} 
     
      \begin{block}{Week Daily Schedule}
        \begin{columns} 
          \column{0.14\textwidth}{\textbf{\small \underline{Mon}}}
          \textbf{\small todo} \\ 
          \begin{itemize}
            \tiny \item \tiny Mgmt: Spaces: Passport
          \item \tiny Work: management of problems.
          \item \tiny Work: comm: send message about fellowship.
          \end{itemize} 
          \textbf{\small schedule} \\
          \begin{enumerate} 
            \tiny \item \tiny 8-9AM: Regular Routines 
          \end{enumerate} 
          
          \column{0.14\textwidth}{\textbf{\small \underline{Tue}}}
          \textbf{\small todo} \\
  \begin{itemize}
    \tiny \item \tiny worklife: update pages \te{20 mins}
    \item \tiny Work: comm: send message to Prof Gropp \te{5 mins} 
  \end{itemize}  
  \textbf{\small schedule}\\ 
  \begin{enumerate} 
    \tiny \item \tiny 8-9AM: Regular Routines 
  \end{enumerate} 

  \column{0.14\textwidth}{\textbf{\small {\underline{Wed}}}}
  \textbf{\small todo} \\
  \begin{itemize}
\tiny \item \tiny 

  \end{itemize}
  \textbf{\small schedule} \\
  \begin{enumerate}
    \tiny \item \tiny 8-9AM: Regular Routines 
  \end{enumerate}
  
  \column{0.14\textwidth}{\textbf{\small{\underline{Thu}}}}
  \textbf{\small todo}\\
  \begin{itemize} 
    \tiny \item \tiny Work: finish letter to Bronis
  \item \tiny Work: Finish admin for letter 
  \item \tiny Work:   
  \end{itemize}
  \textbf{\small schedule}\\
  \begin{enumerate} 
    \tiny \item \tiny 8-9AM: Regular Routines 
    \tiny \item 6:30PM - 7:15PM: TM 
    \tiny \item 7:15PM: Jump Labs 
  \end{enumerate} 
  
  \column{0.14\textwidth}{\textbf{\small{\underline{Fri}}}}
  \textbf{\small todo}\\ 
  \begin{itemize}
    \tiny \item \tiny -  \deadline{ }   \timeEst{}  \priority{} 
  \end{itemize}
  \textbf{\small schedule}\\
  \begin{enumerate}
    \tiny \item \tiny 8-9AM: Regular Routines 
  \end{enumerate}
  
  \column{0.14\textwidth}{\textbf{\small \underline{Sat}}}
  \textbf{\small todo}\\
  \begin{itemize}
    \tiny \item \tiny Work: finish writing slides 
  \item \tiny Work: comm: have Atul send pics  

  \item \tiny worklife: finish writing the comm + worklife: finish tm
    org \dl{wed} 
  \item \tiny Work: comm: finish writing to Bronish \dl{WedOrnextWed} 
  \item \tiny MGmt: Time: do planning draft for summer

  \end{itemize}
  \textbf{\small schedule}\\ 
  \begin{enumerate}
    \tiny \item \tiny 8-9AM: Regular Routines 
  \end{enumerate}
  
  \column{0.14\textwidth}{\textbf{\small \underline{Sun}}}
  \textbf{\small todo}\\
  \begin{itemize}
  \item \tiny 
  \item \tiny 
    
  \end{itemize}
  \textbf{\small schedule}\\
  \begin{enumerate} 
    \tiny \item \tiny 
  \end{enumerate} 
    \end{columns}
  \end{block}
\end{column}%2

%-- Column 3 --------------------------------------------------- 
\begin{column}{0.20\linewidth}
  %-- Block 3-1 
  % On Sunday morn, put a quick synopsis of top news items                  
  % here.  Categorize as Comm and Money.      
  \begin{block}{News}
    \begin{itemize} 
      \tiny \item \tiny French Open
    \end{itemize}
  \end{block}
  \begin{block}{Weather} 
    \begin{itemize}
      \tiny \item \tiny Watch for Pollen.
    \item \tiny Rainy 
    \end{itemize}
  \end{block} 
  \begin{block}{Clothes plan} 
    \begin{itemize} 
      \tiny \item \tiny Saturday: wear polo 
    \item \tiny Saturday night: wear light blue dress shirt and jeans. (or maybe khakis and polo shirt). 
    \item \tiny Sunday: business casual shirt. 
    \item \tiny Wednesday : 
    \item \tiny Thursday: 
    \item \tiny Friday : 
    \item \tiny Saturday : Blue full shirt . 
    \item \tiny Sunday : Red shirt .
    \end{itemize} 
  \end{block}
  %-- Block 3-2

  %-- Block 3-3
  \begin{block}{Situations}
    \begin{itemize}
\tiny \item \tiny \textit{Sitting at Union} Pre-: don't make
        sudden movements with girl.
      \item \tiny \textit{Meetup from Conference} Pre-: don't make
        sudden movements with girl.  
        \item \tiny \textit{Talking to SiriusXM} Pre-:  Post-: don't
          talk more after they ask questions.  

        \item \tiny \textit{Mem. Day Atul and Ridhima} Pre-: 
      \item \tiny \textit{Graduation:} Pre-:   Post-: 
      \item \tiny \textit{Party } Pre-:  Post-:

      \item \tiny \textit{Message to Rohun} Pre-: think about intent,
        and goal Post-: 
        \item \tiny \textit{PostGrad-Thanks}: Pre-: thanks to
          everyone. Experience wouldn't have been the same without
          you. Much to be thankful for. Post-: %Mgmt:webpresence: if
                                %going onto facebook to check if you
                                %need to respond to something, don't
                                %check FB likes (those can be
                                %delayed).                                                                                    
          \item \tiny \textit{Talk to Anu about Money}: Pre-:   Post-:
            say ``Hi Anu,  [newline] No problem at all.`` 

            \item \tiny \textit{Meet for Passport}
            \item \tiny \textit{Sirius XM Radio} 

            \item \tiny \textit{Change FB cover photo:} Pre-: L0: L1:
              L2: L3: Post-: think about the issues beforehand (say
              you post this up, would you re-think? and what thoughts
              might go in) 
              \item \tiny \textit{Meet with Atul at Dublin} Pre-: put
                concealer, add de-odorant, Post-: 

              \item \tiny \textit{Meet with Prof. Gropp} Pre-:  Post-:
                don't belabor any points like .. and the last part
                conclusion. , don't talk too much when asked about the
                intro... conclusion (?) ,
                Talk less about Amanda, Focus on points (stay on
                topic,be intentional about the diagram when asked,
                science: don't get too carried away),
              \item \tiny \textit{Talk with Meridee} Pre-:  Post-:
                good to stay on point.

              \item \tiny \textit{Dinner} Pre-: wear good clothes,
                decide time, Post-: avoid last minite decision and
                plan better, don't make ref to clinton awkward, Don't
                talk too much about food at home. 
                \item \tiny \textit{Meet with postdocs}
                \item \tiny \textit{Meet with Jon Freund:} Pre- 
                \item \tiny \textit{Presentation} 
                \item \tiny \textit{Meet with Dan Bodony} Pre-:
                  introduce by saying hi, I'm good , talk about your
                  work from paragraph, a little more code perspective 
                  discuss what work you might do  Post-: 

                \item \tiny \textit{Flight Booking} Pre-: -- analyze
                  this: options for
                  flight: leave sunday come back next Monday (good
                  because time to prep in LA for convention) OR leave
                  Tuesday, come back next Saturday OR leave next
                  Tuesday and come back next Thursday OR leave on
                  Sunday come back next Friday (leaving early gives
                  time, but late may not be right for work purpose -
                  and bad for work purpose) + bookmark on points, Post-: memorize travel ,
                  read on travel and gather stuff before starting
                  (have a place that you pull up just before you
                  start). 

                \item \tiny \textit{TM Speech} : Pre-:  practice a
                  couple times, do what Meridee says, Post-: Prep with
                 logistics, good job on giving time for practice,
                 memorize introduction,  TODO: make plan on how to
                 write a speech. 

               \item \tiny \textit{Movie}: 

               \item \tiny 
                 \textit{ Graduation party }:  J Kukreti: 51.00 ,
                 Rakesh Uncle : 101.00 
                 udatta kaka: 101.00
                 Kapoors: 31.00


               \item \tiny \textit{Meet with Prof. Gropp: } Post-:
                 don't get caught up with umm's, don't have to say tm
                 at the end, Could have a plan when meeting (even if
                 it's last minute, could recognize last minute and what to
                 do in that case). 

               \item \tiny \textit{Meet with Amy Pruitt} : Post-:
                 stay consistent, Good to just be relaxed, don't get
                 too caught up with start date explanation , but ok
                 because you were relaxed. 
    \end{itemize}
  \end{block}
\end{column}%3 
\end{columns}

\end{frame}
\end{document}
