\documentclass[serif,mathserif,final]{beamer}

\mode<presentation>{\usetheme{Lankton}} 
%\mode<presentation>{\usetheme{I6pd2}} 
%\mode<presentation>{\usetheme{RicePoster}} 
%%\mode<presentation>{\usetheme{ConfPoster}} 
\usepackage{amsmath,amsfonts,amssymb}
\usepackage{eulervm}

\usepackage{pxfonts}
\usepackage{graphicx, ragged2e}
\usepackage{pgffor}
\setbeamertemplate{caption}[numbered]

%\documentclass[11pt]{article}

\usepackage{ulem}
\usepackage{color}
\usepackage{xspace}
\newcommand{\bllt}{\item \small}
\newcommand{\doneTaskNoItem}[1]{\sout{#1}}
\newcommand{\doneTask}[1]{\item \sout{#1}}
\newcommand{\doneTaskHyp}[1]{\item \textcolor{blue} {\sout{#1}}}
\newcommand{\optTask}[1]{\item  \textcolor{green}{#1}}
\newcommand{\prioTask}[1]{\item  \textcolor{red}{#1}}
\newcommand{\timeEst}[1]{\textit{Time:} \textit{#1}}
\newcommand{\priority}[1]{\textit{Priority:} \textit{#1}}
\newcommand{\prio}[1]{\textit{Priority:} \textit{#1}}
\newcommand{\dueBy}[1]{\textit{Deadline:} \textit{#1}}
\newcommand{\MyName}{Vivek~Kale}
\newcommand{\fixme}[1]{\textcolor{blue}{[FIXME: #1]}}
\newcommand{\revision}[1]{\textcolor{blue}{[FIXME comment : #1]}}
\newcommand{\regItem}[1]{\item \textcolor{cyan}{#1}}
\newcommand{\regRoutineItem}[1]{\item \textcolor{green}{\textit{Reg. Routine:} #1}}
\newcommand{\situationItem}[1]{\item \textcolor{magenta}{\textit{Situation:} #1}}
\newcommand{\deadline}[1]{#1}
\newcommand{\comments}[1]{}

\graphicspath{{./figures/}}
\usepackage[orientation=landscape,size=a0,scale=1.6,debug]{beamerposter}

%-- Header and footer information ----------------------------------
\newcommand{\footleft}{Mgmt-WorkLife-weekPlan} % figure what this should be 
\newcommand{\footright}{June 2014}
\title{Month-Week-Day Plan} 
\author{Vivek Kale$^1$$^2$}
\institute{$^1$ University of Illinois at Urbana-Champaign \quad}  

%------------------------------------------------------------------
%-- Main Document ------------------------------------------------- 

\begin{document} 
\begin{frame}{} 

  \begin{columns}[t]
%-- Column 1 ---------------------------------------------------  
\begin{column}{0.30\linewidth} {\textbf{\underline{Week Aspects(new name)}}}
  %-- Block 1-1
  \begin{block}{\textit Stresses} 
    % Recognize emotions / recognize what you're worried about -> eliminate worry
    \begin{itemize}
     % \tiny \item \tiny EuroMPI paper: 
     % \small \item \tiny Ridhima saying stuff about me. 
    %\item \tiny related work:   
      % \item \tiny Atul saying let's talk about this some other time. 
      % \item \small friends of Atul's better(?): 
      % \item \small email -done : 
      % \item \small anger that you are below parents 
      % \item \small [ find others ]
    %\item \tiny others at work. 
    %\item \tiny Comm: Talking to Amit - can bounce back, just close
    %  friends.
      %\item \tiny Comm: restricted profile - take it for face
      % value, probably because I'd get angry. 
    \item \tiny Comm: Frustration about Sneha - you still are you.
    \item \tiny Comm: thinking about how Sat. went /general worries:
      don't worry and be conscious. 
    \item \tiny Comm: putting extra fb update - just did it for fun
      and whatever, if anything just local anxiety. 
       \item \tiny Comm: brother getting upset about laptop 

    \end{itemize} 
  \end{block} 
  %-- Block 1-2 
  
  %-- Block 1-3
  \begin{block}{\textit Habits } 
    \begin{itemize} 
      \tiny \item \tiny move feet less, don't scrub on floor. 
    \item \tiny back straight. 
    \item \tiny lips relaxed. 
    \item \tiny watch what happens when a lovely girl talks to you. 
    \end{itemize} 
  \end{block} 

  %-- Block 1-4
  \begin{block}{\textit Clothes plan } 
    \begin{itemize} 
    \tiny \item \tiny Saturday: wear polo shirt. 
    \item \tiny Saturday night: wear light blue dress shirt and jeans. (or maybe khakis and polo shirt). 
    \item \tiny Sunday: business casual shirt. 
    \item \tiny Wednesday : 
    \item \tiny Thursday: 
    \item \tiny Friday : 
    \item \tiny Saturday : 
    \item \tiny Sunday : 
    \end{itemize} 
  \end{block} 

  %-- Block 1-5
  \begin{block}{\textit Food plan } 
    \begin{itemize} 
      \small \item \tiny Skip meals this week to take out fat from weekend. 
    \item \tiny Be very careful about food for Saturday night, along with Brunch for Sunday and dinner for Sunday. 
    \end{itemize} 
  \end{block} 

  \begin{block}{\textit Situations} 
    \begin{itemize} 
 \item \tiny Comm: saying something online about the computer - 
      notes on mailing stuff : e.g. 4 pages is ounce,  \$2.30 for
      regular mailing takes 4 + 3  days to California ,  know exact
      shipping/return address ,  be ready to handwrite(practice), know
      where the return address should be.   
    \item \tiny text to Sneha:  
    \item \tiny meet with Amit + Ritika for dinner: 
    \item \tiny meet with Prof. Gropp: Pre-:  Post-: good to have
      notes, have things ``not to say'',  could rehearse going through
      different things possibly. 
    \item \tiny meet with Shyunti:  Pre-:  Post-: 
    \end{itemize}
  \end{block} 
\end{column} %2 
%-- Column 2 --------------------------------------------- 
\begin{column}{0.33\linewidth}{\textbf{\underline{Week TODO}}} 
% NOTE: Current policy is to comment out days as they come. 
% TODO: put in the regular routines here for each day, in the schedule box. 
  %--- Block 2-1

\begin{block}
%{\small weekTODO} 

\begin{enumerate} 
\item \tiny Work: prep to meet with Prof Gropp  \priority{I}. 
\item \tiny Work: make todo for apps + Work: clean up thesis tex file to have abstract/title. 

\item \tiny Work: reply to Tanzima + Work: send message to Simplice. 

\item \tiny \textbf{Mgmt: Spaces: Graduation: check for credit hours for the summer, get new ones if needed + check grad deadlines, get the Neur course checked}. 
\item \tiny Mgmt: Spaces: Graduation: send messages on Post-doc to Prof. Gropp about Princeton / other places + Work: check with Prof Gropp about the Princeton post-doc. 

\item \tiny Work: Add code structure for data collection + Find any other systems issues and take care of them + integrate the slack-conscious runtime/MPI dot prod. 
\item \tiny Work: check for sending paper to workshop on DataFlow, cloud computing conference/workshop. 
\item \tiny Work: update picture and chapter on combo, based on discussion with Prof. Gropp. 

\item \tiny Work: return book to Todd. 
\item \tiny Mgmt: Spaces: get laptop screen fixed. 

\item \tiny Mgmt: Spaces: money: check sw old stuff; find iPad; update money; check money in bank. 

\item \tiny Comm: update worklife 

\item \tiny Comm: fix work-life cheatsheet \priority{UI} +  Comm:
  integrate howtosayit, EI, winfriends, SI, 7habits \priority{UI} 

\item \tiny Comm: do situations planning. 

\item \tiny GenKnowledge: get book on genKnowledge OR read NYtimes. 
\item \tiny Mgmt: Spaces: get rugs 
\item \tiny Mgmt: Spaces: return taillight
\item \tiny Mgmt: Spaces: order 10 iPhone 5s chargers 
\item \tiny  Mgmt: webpresence: check fb profile info.
 
\item \tiny Work: Figure out computer (cs-grad131), and check for
  files/images from CS525. 

\end{enumerate}
\end{block} 

\begin{block} 

\textbf{\underline{Mon}}
\begin{enumerate} 
\tiny \item \tiny Work: finish write-up for camera-ready (specifically,
the ``constraint'') + add in thesis \priority{U}. Check for title of 
Improving Load Balancing vs. Load Balancing --> see what to do with 
the camera-ready version, and to upload it. 

\item \tiny \doneTask{worklife: finish situations review}
  \priority{I} 

\item \tiny Work: look through app code for MCB. + talk about software
  with dad + Work: prep for meeting with Prof. Gropp. 

\item \tiny Comm: send reply to Sneha saying 
``No problem. My parents told me to contact you yesterday. All the best.''  
+ Comm: send message to Neha  ``Hi Neha, this is Vivek. How are you
doing? My parents gave me your info. Let me know if you wanted to chat
sometime.'' 

\item \tiny Work: send book back to Todd \priority{U}. 
\item \tiny Mgmt:Spaces: call for Zoloft + call for appt. 
\item \tiny Mgmt:webpresence: check fb profile info +  Mgmt:webpresence: check fb profile info. 
\item \tiny Mgmt:Spaces: figure out laptop screen. 
\end{enumerate} 

\textbf{\underline{Tue}}
\begin{enumerate} 
\tiny \item \tiny 

\end{enumerate} 

\textbf{\underline{Wed}}
\begin{enumerate} 
\item \tiny Work: send Todd back the book + send email \priority{U}
  \priority{doItByThisEveningOrTomorrowMorning} \timeEst{30 mins} 
\item \tiny Mgmt: Spaces: Get the meds for zoloft: \timeEst{30 mins}
  \priority{U}. 

\end{enumerate} 

\textbf{\underline{Thu}}
\begin{enumerate} 
\tiny \item \tiny Work: think about EuroMPI camera-ready submission title
  change. \priority{ClocksTicking}. - either change the title or make Prof gropp , the person who signs the thesis, sligthly annoyed. 

\item \tiny Work: send meeting summary to Prof. Gropp.

\item \tiny Work: send Todd email saying sorry for the delay, but have
  the book now. \timeEst{10 mins} \priority{byTomorrowAndThisIsImportant}. 


\item \tiny Comm: add in TM prep tonight. 


\item \tiny Work: make plan to go through apps. 

\item \tiny Work: finish coding updates for nbody code. 

\item \tiny Work: fix problem with vSched, organize vSched. 

\item \tiny Comm: check for table topics sign-up around noon, sign up for table topics. 
\item \tiny Comm: prep table topics in speeches directory of folder. 
\item \tiny Comm: send Nitin Mama reply. 

\item \tiny Comm: read 7 habits 1st chapter and summarize. \timeEst{1 hour}.

\item \tiny Comm: get speech for vocal variety written up \timeEst{1 hour}. 

\item \tiny Work: submit EuroMPI by July 18th, using sigalternate style. Add in doi. Add in copyright block. figure out title \timeEst{45 mins}. 

\end{enumerate} 


\textbf{\underline{Fri}} 
\begin{enumerate} 
\item \tiny \doneTask{ Work: reply regarding EuroMPI registration and title }

\item \tiny Work: finish the code for NAS LU, CG , + Work: get it to work for MCB and other benchmarks. 

\item \tiny Work: add error checks to code + Work: figure out timings for app, along with PAPI profile (dummy) and the dqIdle/time. 

\item \tiny Work: app code fix the problem with the per-thread lock for stealing. 

\item \tiny Work: reply to Tanzima telling her what she is saying does not make sense \priority{doItinAdayOrTwoButSoon} \timeEst{30 mins}.

\item \tiny \doneTask{Work: reply regarding EuroMPI registration and title -can't do much about the doi}. 

\item \tiny Work: finish related work, other stuff + Work: finish 
  writing stuff for intro and related work. 

\item \tiny Comm: talk to Neha 


\item \tiny Comm: planning for Sunday

\item \tiny Comm: consider delete ak from fb \priority{UI}  
\item \tiny Comm: add limited profile \priority{U} 
\end{enumerate} 

\textbf{\underline{Sat}} 
\begin{enumerate} 

\item \tiny worklife: worklife cheat sheet update 
\item \tiny worklife: add notes on TM table topics 
\item \tiny worklife: add situation on meeting

\item \tiny finish emo intelligence notes on Empathy. 


\item \tiny Mgmt: Money: ask about Japan. 
\item \tiny Work: travel planning: Edmonton. 
\item \tiny Mgmt: Money: California in mid-August. 
\item \tiny Mgmt: Money: figure out registration for NetIP. 
\item \tiny Work/worklife: figure out time needed for EuroMPI camera-ready submission. 


\end{enumerate} 


\textbf{\underline{Sun}}

\begin{enumerate} 
\tiny \item \tiny 
\item \tiny 
\item \tiny 
\end{enumerate} 

\end{block} 

\end{column}%2 

\begin{column}{0.27\linewidth} {\textbf{\underline{Reg. Routines}}} 

%Block 3-1
\begin{block}{\small \textbf{\underline{Regular Routines}} }
\underline{\textbf{Morning}}
\begin{itemize}
\item \tiny Brush Teeth \timeEst{4 mins}
\item \tiny Mouthwash, Clean tongue - it helps with breath\timeEst{1mins} 
\item \tiny Eating small breakfast
\item \tiny Check your schedule for meetings / appointments for that day: Is anything urgent? \timeEst{5 mins}
\item \tiny Excercise: 1 hour ( Stretch for 10 mins, Treadmill for 30 mins , Lift weights or Yoga 1 hour, Meditation for 10 mins)
\item \tiny Shave (at least every other day) \timeEst{5 mins}
\item \tiny Shower : (shampoo+conditioner, acne wash,  soap on underarms/underbody)
\timeEst{10 mins}
\item \tiny dry hair, dry face, arms, legs, back, stomach \timeEst{3 mins}
\item \tiny Clothing: belt, check collar, shirt not half-tucked, matching socks \timeEst{5 mins}
\item \tiny Comb hair, hair gel optional \timeEst{ 1 min}
\item \tiny Check Keys/Wallet/Cell/Badge (get a bucket) \timeEst{1 min}
\item \tiny Open meds cabinet, get water, take medicines \timeEst{1 min}
\item \tiny Wear lenses and rinse out case \timeEst{ 2 mins}
\item \tiny Deodorant or cologne depending on the day \timeEst{1 min}
\item \tiny Wash your face with a face wash - it helps with acne \timeEst{3 mins}
\item \tiny Moisturize - apply lotion \timeEst{ 2 min}
\item \tiny Neti pot / clean out sinuses - if you’re feeling congested \timeEst{5 min}
\item \tiny clean out ears, nose \timeEst{5 mins}
\item \tiny Remember to lock door \timeEst{1 mins}
\end{itemize}

\underline{\textbf{Evening}}

\begin{itemize}
\item \tiny Call family: 30 mins
\item \tiny meet friends: 20 mins
\item \tiny Cleaning dishes / cleaning house: 10 mins
\item \tiny Lay out clothes for the next day, iron if necessary
\item \tiny start laundry if needed: 10 mins,
\item \tiny Collect anything you’ll need for the next day (e.g. dry cleaning to drop off): 5 mins,
\item \tiny Check Facebook/linkedin/google+: 10 mins, matrimony stuff: 10 mins,
\item \tiny Food for lunch/dinner the next day: 10 mins
\end{itemize}

\underline{\textbf{Night before bed}}
%TODO: why isn't enumerate working???
%\begin{enumerate}
\begin{itemize}
\item \tiny Finish computer stuff \timeEst{5 mins}
\item \tiny Get into sleeping clothes \timeEst{1 mins}
\item \tiny Before sleeping: brush teeth, floss \timeEst{ 2 min}
\item \tiny Properly wash and put away contacts \timeEst{ 2 mins}
\item \tiny Review the days good things \timeEst{ 10 min}
\item \tiny Light Reading \timeEst{ 10 min}
\item \tiny Prayer \timeEst{10 mins}
%\end{enumerate} 
\end{itemize}
\end{block}

\end{column}%3 

\end{columns} 

\end{frame} 

\end{document}
