\begin{columns}
    %-- Page 2: Column 1 --------------------------------------------------- 
    \begin{column}{0.25\linewidth}
      %{\textbf{\underline{Week Aspects(new name)}}}
      %TODO: check where this should go. -done  
      %--- Page 2: Block 1-1 
      \begin{block}{Routines}
        { \tiny \underline{\bf Routines:} Morning: bfast, exercise/brush,
          floss, shower (hair, eyes, ears, underarms, feet), meds, belt,
          comb hair / dishes, clean kitchen floor. |  Night: running/ put
          away dishes, clean kitchen floor / brush teeth, charge phone,
          clothes for tomorrow, contacts off.}\\
        {\tiny \underline{\bf Sunday Routines:} Routines:
          Experiences,week plan.}\\ 
        {\tiny \underline{\bf Weekday Routines:}}\\
        %TODO: check if weekday routines overlaps into daily routines.
      \end{block} 
      %--- Page 2: Block 1-3
      \begin{block}{Local Happiness}
        % howto:Recognize emotions / recognize (precisely) what you're
        % worried about -> methods for eliminating worry. 
        % clean out old worries, put them in pastWorries doc.  
        % remember to define precisely 
        % order from top-to bottom
        \begin{itemize} 
          \tiny \item \tiny Work: worrying about interviewing: just
          focus on the work.
        \item \tiny Worrying about gal: think about talking to others.
        \end{itemize} 
      \end{block}
      %--- Page 2: Block 1-4 
      \begin{block}{AngersAndAnxieties}
        % howto:Recognize emotions / recognize (precisely) what you're worried about -> methods for eliminating worry. 
        % clean out old worries, put them in pastWorries doc.  
        % remember to define precisely 
        % order from top-to bottom
        \begin{itemize}
          \tiny \item \tiny Anger about UP -> think about the positive
          perspective, and the original
        \item \tiny Anger about Mr. Kapoor ->  leave it
        \item \tiny Anger about a b  -> ...
        \item \tiny Issue with USC : --> things get better. 
        \end{itemize}
      \end{block}
      %-- Block 1-5
      \begin{block}{Life notes}
        \begin{itemize}
          \tiny \item \tiny Social Intelligence: 
        \end{itemize}
      \end{block}
      % howto:

      \begin{block}
      
      {\underline{\bf Day trip packing list:} charger for iPhone,
        charger for laptop, car keys, underwear, black socks, shoes,
        meds, halls meds, greyhound, boarding pass, flight pass, directions to
        venue?} \\ 
      {\tiny {\bf Week lessons:}} \\ 
      \begin{enumerate}
        \tiny \item \tiny Win Friends/ Influence People – no one
        likes to take direct orders.
      \item \tiny Go through 7 habits.
      \item \tiny Coding problem: 
      \item \tiny Chess tips: 
      \item \tiny tm tips.
      \end{enumerate}
          {{\tiny {\bf News:}} M: MS uses gmail | S:  Trump's govt shutdown | E:
            Fallon:   Kimmel:  Colbert: SNL:
            w: washdc: 
            {su: { s a}}
            {m:{54/41 r a}}
            {t: {59/56 r a}} 
            {w: {76/58 s a}} 
            {r: {84/66 s a}}
            {f :{86/68 s a} }
            {sa: {91/70 s a}}}
    \end{block} 

  \end{column}
  %-- Column 2 ---------------------------------------------
  \begin{column}{0.5\linewidth}
    \begin{block}{Week Summary} 
      {\underline {\bf Week Plan:} 

        Work: handle emails from Youssef,
        Work: message to Harshitha about prob statement+ Work: write
        paper, Mgmt:Spaces: get garage door opener, Comm: send Kishore
      Kaka a message, Comm: send message to Nitin Mama, Comm: reply on
      WhatsApp group.

} \\ 
      {\underline{\bf Weekend Plan:} Work on paper }\\
    \end{block}

      \begin{block}{Running ToDo} % find a better name 
        \begin{enumerate} 
          \doneTask{Work: respond to Doodle.}
          \doneTask{Mgmt:wp: fb HBD to Aniket.}
          \doneTask{Comm: message to Kishore Kaka.}
          \doneTask{Comm: send picture to Geeta Maushi.}
          \doneTask{Work: message to Harshitha about PAPI counters + Work:
            discuss problem statement.}
          \doneTask{Work: reply to Harshitha about PAPI counters.}
            \doneTask{ Mgmt:wp: fb HBD to Ryan Clasey.} 
            \doneTask{ Mgmt:wp: HBD to Kavita.} 
          \doneTask{Work: add Harshitha as corresponding author in
            paper.}
            \doneTask{Work: do abstract of paper.}
            \doneTask{Work: paper registration and information. = Work: add
            title + Work: add Harshitha to paper + Work: add
            abstract.}
            \doneTask{ Mgmt:wp: add Bariz to LinkedIn.}              
            \doneTask{ Work: add JIRA account.} 
            \doneTask{Mgmt:wp: add Hrishikesh to FB.} 

          \item \tiny \textbf{Curr} $\rightarrow$
          \item \tiny Work: fix Youssef's code. 
          \item \tiny Work: get PIC code to work on Stampede. 
          \item \tiny Work: ensure that CkLoop works on BG/Q. 
          \item \tiny Work: experimentation section. 
          \item \tiny Work: experimentation section message.
          \item \tiny Work: do \texttt{ ln -s} for paper subdirectory in bitbucket git repository.
          \item \tiny Work: download ptychoLib from Kaushik and copy to git repo.            
          \item \tiny Work: discuss script of paper. \te{1 hour}
            \dl{tonight} \pr{high}. 

          \item \tiny Work: add graph for problem statement in paper. 
          \item \tiny Work: update paper's techniques section. 
          \item \tiny Work: update paper's implementation section. 
          \item \tiny Mgmt:Spaces: find garage opener + Mgmt:Spaces:
            get car check engine light updated + Mgmt:Spaces: do car's
            registration + Mgmt:Spaces: get Navdy.

          \item \tiny Work: talk to Prem about an office in SF. 
          \item \tiny Work: figure out time to talk with Youssef.
          \item \tiny Mgmt:wp: add Hirve Kaka to LinkedIN?

          \item \tiny Comm: do review for Liberty Towers.

          \item \tiny Comm: respond to Sonali Sinha at 2song103658167
            and my email address is: 2sonalisinha@gmail.com.

            Dear Sonali,

            Sorry for my delayed reply. Thank you for your message. I had
            the privelage of coming across your profile too. Would
            you like to talk with me by phone next week or next weekend? 
            Please let me know when you can.
            
            Vivek

          \item \tiny Comm: message to Nitin Mama about meeting father.
          \item \tiny Comm: message saying thanks for a nice wedding.
          \item \tiny Mgmt:Spaces: get Virginia license and
            registration. \pr{Urgent}.
  
\item \tiny \textbf{ <-- End Curr } 

\item \tiny Work: IM system for LLNL. 

        \end{enumerate}
      \end{block}
 
      % howto: the below is a routine based on the job I'm doing and the
      % circumstances I'm in. Note that this is different from routines
      % above, which is true for a long-term period of over 10 years. 

      \begin{block}{Weekly Meetings}
        \begin{itemize}
          \tiny \item \tiny IWOMP affinity meeting Thursday 7 AM PDT / 9 AM
          CDT call in: 805-639-779 pswd: places. \url{https://llnl.webex.com/llnl/j.php?MTID=m33950b76befb72c0cbc31ea2e3be720c}
        \item \tiny DEG group meeting.  
        \end{itemize}
      \end{block} 


\begin{table}[ht!]
\label{fig:calendar}
\begin{center}
\begin{tabular}
{ | c || c | c | c | c | c | c | c |}
\hline
  \textbf{\small content} & {\small \bf M} & {\small \bf T} & {\small
    \bf W} & {\small \bf R} & {\small \bf F} & {\small \bf Sa} &
         {\small \bf Su} \\
  \hline
  \small weat  &\tiny 2/3 r &\tiny 2/1 r &\tiny 2/-1 r &\tiny 11/2 s  &\tiny 11/4 s   &\tiny  11/4 s &\tiny 11/5 s \\
  \hline
  \small todo  &\small &\small &\small &\small &\small &\small
  &\small  \\
  \small       &\small &\small &\small &\small &\small &\small
  &\small  \\
  \small       &\small &\small &\small &\small &\small &\small
  &\small  \\
  \small       &\small &\small &\small &\small &\small &\small
  &\small  \\
  \small       &\small &\small &\small &\small &\small &\small
  &\small  \\
  \hline
  \small schd  &\small &\small &\small &\small &\small &\small &\small  \\
  \small     &\small &\small &\small &\small &\small &\small  &\small
  \\
  \small      &\small &\small &\small &\small &\small &\small  &\small
  \\
  \small    &\small &\small &\small &\small &\small &\small  &\small
  \\
  \small     &\small &\small &\small &\small &\small &\small &\small
  \\
  \hline
  %\bottomrule
\end{tabular}
\end{center}
\end{table}

\end{column}
    
    % ------ Page 2: Column 3
    \begin{column}{0.25\linewidth}
      % ------ Block 2.3.1 
      \begin{block}{Food Plan} 
        \begin{itemize}
          \tiny \item \tiny Google Express: DHDQQJQDRFTXDM95B
        \end{itemize}
      \end{block} 
      \begin{block}{Clothes plan} 
        \begin{itemize}
          \tiny \item \tiny Monday: 
        \item \tiny Tuesday
        \item \tiny Wednesday
        \item \tiny Thursday
        \item \tiny Friday
        \item \tiny Saturday
        \end{itemize} 
      \end{block} 
      
      %-- Block 3-3 
      \begin{block}{Situations}
        % Summary: the below are the situations that define one
        % another.
        % Howto: Put post notes of each situation from list of previous
        % week. Put high importance situations in situationslist. 
        % Put list of upcoming situations on Sunday morning with Pre. 
        \begin{itemize}
          \tiny \item \tiny Situation: meet With Kavita  Post-: More
          social awareness. More planning.
        \end{itemize}
      \end{block}
      % contingincies: 
      % Summary:
    \end{column}
  \end{columns}

% ----- Attic --- 

\comments{ 
  
\item \tiny Work: do transformations for CUDA + Work: try to
  get to work on new data sets + Work: look up parallelization
  of algorithms + Work: show errors  graph TimeEst \te{1 hour}
  Work: do run for problem size. \te{1 hour} 
  
\item \tiny Work: do Cworks items = Get application with
  ckloop that’s load imbalanced Modify ckloop to ckloophybrid, where
  static section is not stolen by cores, i.e., cores do not steal
  work during execution of statically scheduled loop iterations +
  Consider additions: weighted static, locality-optimized. Bind
  cores, i.e., drone mode. Integrate with git.  \te{1 hour}
  \dl{tonight} \pr{high}.
 
\item \tiny Work: send message to Micheal K about user-defined
  schedule. \te{1 hour}
  
\item \tiny Mgmt:Spaces: empty trash of photos from Photo booth \te{10 minutes}
  
\item \tiny Mgmt:Spaces: move pictures from iPhone into folder. \te{10
  minutes}. 
  
\item \tiny Mgmt:Spaces: fix key set. \te{10 minutes}. 


\item \tiny Mgmt:Spaces: get citi bank account
  Mgmt:Spaces: get refund from AA  + Mgmt:Spaces: get the
  bumper bully +  Mgmt:Spaces: get replacement for Chase card. \te{1 hour}.
  
\item \tiny Work:admin(spaceSave): Goto MacStore and see if the following can be uninstalled and then
  re-installed if needed = Work:admin(spaceSave):
  a. GarageBand  + WOrk:admin(spaceSave):  b. iMovie +
  Work:admin(spaceSave): c. strip down Xcode +
  Work:admin(spaceSave): d. iPhoto 
  + WOrk:admin(spaceSave): 2. Check about MS office to see whether Microsoft Messenger and
  communicator can be deleted safely 
  + WOrk: admin(spaceSave): 3. Check that Omnigraffle can be
  deleted + WOrk:admin(spaceSave): See if PhotoBooth can be deleted +
  +Work:admin(SPaceSave): Empty photos from PhotoBooth. 
  + Work:admin(SpaceSave): see how to defrag Macbook Air.
  http://www.macworld.co.uk/how-to/mac/how-defrag-speed-up-mac-os-x-2016-3600241/

\comments{ 
      \begin{block}{Week Daily Schedule} %NOTE: must have a curly brace
                                %for blocks. 
        {\bf Sun:}  Comm: prep for talk, Comm: message to Asavi,
        \newline {\bf Mon:} 
        %NOTE: can't use newlines in macros easily 
        \newline {\bf Tues:}         
        \newline {\bf Wed:}
        \newline {\bf Thur:} 
        \newline {\bf Fri:} 
        \newline {\bf Sat:}
      \end{block} 
     } 
%TODO: consider adding weather command-line option here.  

\comments{
      \begin{block}{Week Daily Schedule}
        % howto: arrange items from running todo into the below
        % sheet management document. 
        
        \begin{columns}
          \begin{column}{0.14\textwidth}{\small \underline{\bf Mon}}

            {\small \bf weather: } 11/1 s \\ 
            {\small \bf todo}\\ 
            \begin{itemize}
              \tiny \item \tiny 
            \item \tiny  
            \item \tiny  
            \item \tiny 
            \end{itemize} 
                {\small  \bf schedule}\\
                \begin{enumerate} 
                  \tiny \item \tiny 8-9AM: Regular Routines 
                \end{enumerate}
          \end{column} 
          
          \begin{column}{0.14\textwidth}{\small \underline{\bf Tues}}
            {\small \bf weather: } 3/1 r \\ 
            {\small {\bf todo}}\\ 
            \begin{itemize}
              \tiny \item \tiny Work: do write-up 
            \item \tiny Work: do write-up for 
            \item \tiny Work: 
            \item \tiny Mgmt:wp: hbd to Vinod. 
            \item \tiny Mgmt:wp: hbd to Kavita. 
            \item \tiny Mgmt:wp: add picture of group on FB. 
            \item \tiny Mgmt:wp: add picture of Anu and Vivek on FB.  
            \item \tiny Comm: send Geeta Maushi a message with
              picture. 
            \item \tiny Comm: With Kishore Kaka, and with car. 
             
 
            \end{itemize} 
                {\small {\bf schedule}}
                \begin{enumerate} 
                  \tiny \item \tiny 8-9AM: Regular Routines 
                \end{enumerate} 
          \end{column}

          \begin{column}{0.14\textwidth}{\small \underline{\bf Wed}}
            {\small \bf weather: } 3/1 r \\ 
            \small{\bf todo}\\
            \begin{itemize}
              \tiny \item \tiny Add in schedule
            \item \tiny -
            \end{itemize} 
                {\small {\bf schedule}}\\
                \begin{enumerate} 
                  \tiny \item \tiny 8-9AM: Regular Routines 
                \end{enumerate} 
          \end{column}

          \begin{column}{0.14\textwidth}{\small \underline{\bf Thurs}}
            {\small \bf weather: } 1/-1 r \\ 
            {\small {\bf todo}} \\ 
            \begin{itemize}
              \tiny \item \tiny Add in schedule
            \item \tiny 
            \end{itemize} 
                {\small {\bf schedule}} \\
                \begin{enumerate} 
                  \tiny \item \tiny 8-9AM: Regular Routines 
                \end{enumerate}
          \end{column} 
          
          \begin{column}{0.14\textwidth}{\small \underline{\bf Fri}}
            {\small \bf weather: } 3/1 r \\ 
            {\small {\bf todo}} \\ 
            \begin{itemize}
              \tiny \item \tiny Add in schedule
            \item \tiny 
            \end{itemize} 
                {\small {\bf schedule}} \\
                \begin{enumerate} 
                  \tiny \item \tiny 8-9AM: Regular Routines 
                \end{enumerate}
          \end{column}

          \begin{column}{0.15\textwidth}{\small \underline{\bf Sat}}
            {\small \bf weather: } 11/1 .2r \\ 
            { \small {\bf todo}} \\ 
            \begin{itemize}
              \tiny \item \tiny Add in schedule
            \item \tiny 
            \end{itemize} 
                {\small {\bf schedule}} \\
                \begin{enumerate} 
                  \tiny \item \tiny 8-9AM: Regular Routines 
                \end{enumerate}
          \end{column}
          
          \begin{column}{0.15\textwidth}{\small \underline{\bf Sun}}
            {\small \bf weather: } 11/2 r \\ 
            {\small {\bf todo}}\\ 
            \begin{itemize}
              \tiny \item \tiny Add in schedule
            \end{itemize} 
                {\small {\bf schedule}}\\
                \begin{enumerate} 
                  \tiny \item \tiny 8-9AM: Regular Routines 
                \end{enumerate}
          \end{column}

        \end{columns}
      \end{block}

}
 

}
