%\def\PRES{1}
%\ifx{\PRES}

%\iftoggle{\PRES}
\begin{frame}{Running to do}
%\else 
%\fi 
\begin{enumerate}
\item \tiny Work(psm:nt): reply for journal. 
  \tiny \item[] \tiny \textbf{Curr} $\rightarrow$ 
\item \tiny Work:admin: update resume. 
  
\item \tiny Work: prep for discussion with OpenMP. 
\item \tiny Work:rel: send in application,
\item \tiny Work: ask about LLVM compiler to Michael Klemm. 
\item \tiny Work:admin: ask for vacation.\te{10 minutes} \dl{TuesNight} \pr{high}. 
\item \tiny Work: send in plan with slides.
\item \tiny Work: talk with Michael Klemm, 

\item \tiny Work: finish proposal slides   
\item \tiny  –Curr-> 

  \tiny \item \tiny Work: do review for journal paper. 
\item \tiny Work: write slides. 



\item \tiny Work: admin: send in receipts for SC17. 
\item \tiny Mgmt:Spaces: get pay stubs. 
\item \tiny Mgmt:Spaces: apply for jobs and cover letter = Mgmt:Spaces: LBNL cover letter + Mgmt:Spaces: other cover letter + Mgmt:Spaces: talk with Martin Kong. 
\item \tiny Work:admin: update resume.
\item \tiny Work: check about Intel KNL.  \url{https://www.bnl.gov/knlhackathon2018/} 
  
\item \tiny Mgmt:Spaces: finish flight booking. 
\item \tiny Mgmt:Spaces: get Virginia license and registration \pr{Urgent}.
\item \tiny Mgmt:Spaces: pay parking ticket from VA \te{1hour} \pr{U}. 
\item \tiny Mgmt:Spaces: pay parking ticket from VA \te{1hour} \pr{U}.
\item \tiny Work: finish slide. 
\item \tiny Work:admin: submit receipts for Bagel.
\item \tiny Work:admin: ask for vacation.\te{10 minutes} \dl{TuesNight} \pr{high}    
\item \tiny Work: update slides for OpenMPCon. 
\item \tiny Work: update website for  \url{bit.ly/udsomp}. 
\item \tiny Work:admin: fill out questionnaire for Health assessment.
\item \tiny Mgmt:Spaces: pay Mai T. Phan. 
  \seti
\end{enumerate}
  
% \ifx{\PRES}{1}
\end{frame}
% \else 
 % \fi
  
% \ifx{\PRES}{1}
\begin{frame}{Running To Do (2)} 
%  \fi 
  \begin{enumerate}
    \conti    
  \item[] \tiny  $\leftarrow$ \textbf{End Curr}
  \item \tiny Mgmt:Spaces: get citi bank account + Mgmt:Spaces: get refund from AA  + Mgmt:Spaces: get the bumper bully 
  \item \tiny Mgmt:Spaces: update software  in car\te{ 1 hour}. 
  \item \tiny  Mgmt:Spaces: consider new wheels 
  \item \tiny EI: Study materials from CBT.  \te{2 hours} \dl{Monday}.
  \item \tiny Work:comm: figure out whether to add Anshu \te{1 hr}.
  \end{enumerate}
  
  %\ifx{\PRES}{1}
 \end{frame}
%\fi
