%\def\PRES{1}
%\ifx{\PRES}

%\iftoggle{\PRES}
\begin{frame}{Running to do}
%\else 
%\fi 
\begin{enumerate} 
\item \tiny Work(psm:nt): reply for journal. 
  \tiny \item[] \tiny \textbf{Curr} $\rightarrow$ 
\doneTask{Work:admin: update resume}. 
\doneTask{Work: prep for discussion with OpenMP.}
\item Work:rel: send in application,
\doneTask{Work: ask about LLVM compiler to Michael Klemm.}
\item \tiny Work: talk with Michael Klemm, 
\item \tiny {\bf Curr} $\rightarrow$ 

\item \tiny Work: finish proposal slides.  

\item \tiny Work:rel: do cover letter for LLNL = Work: rel: explain
  reason for wanting to join LLNL + Work:rel:(cvl): explain your
  contributions + Work:rel:(cvl): 

\item \tiny WOrk:rel: do cover letter for BNL. 
\item \tiny Mgmt:Spaces: talk with Martin Kong. 
 
\item \tiny Work:rel: do application for HLFF = Work:rel: get degree
  certificate + Work:rel: add research statement + Work:rel: write
  letter of motivation. 

\item \tiny Work: admin: send in receipts for SC17. 

\item \tiny Mgmt:Spaces: get points on Southwest back.

\item \tiny Mgmt:Spaces: cancel order from LinkedIn premium. 

\item \tiny Mgmt:Spaces: finalize dinner with Bhavesh.

\item \tiny Mgmt:Spaces: look for apartments.

\item \tiny Work:admin: update resume.
\item \tiny Work: check about Intel KNL.  \url{https://www.bnl.gov/knlhackathon2018/}. 
  
\item \tiny Mgmt:Spaces: finish flight booking. 

\item \tiny Comm:rel: respond to Maithily Mane. 
\item \tiny Mgmt:Spaces: get Virginia license and registration \pr{Urgent}.
\item \tiny Mgmt:Spaces: pay parking ticket from VA \te{1hour} \pr{U}. 
\item \tiny Mgmt:Spaces: pay parking ticket from VA \te{1hour} \pr{U}.
\item \tiny Work: finish slide. 

\item \tiny Work: update slides for OpenMPCon. 
\item \tiny Work: update website for  \url{bit.ly/udsomp}. 
\item \tiny Mgmt:Spaces: pay Mai T. Phan. 
  \seti
\end{enumerate}

% \ifx{\PRES}{1}
\end{frame}
% \else 
 % \fi
  
% \ifx{\PRES}{1}
\begin{frame}{Running To Do (2)} 
%  \fi 
  \begin{enumerate}
    \conti    
  \item[] \tiny  $\leftarrow$ \textbf{End Curr}
  \item \tiny Mgmt:Spaces: get citi bank account + Mgmt:Spaces: get refund from AA  + Mgmt:Spaces: get the bumper bully 
  \item \tiny Mgmt:Spaces: update software  in car\te{ 1 hour}. 
  \item \tiny  Mgmt:Spaces: consider new wheels 
  \item \tiny EI: Study materials from CBT.  \te{2 hours} \dl{Monday}.
  \item \tiny Work:comm: figure out whether to add Anshu \te{1 hr}.
  \end{enumerate}
  
  %\ifx{\PRES}{1}
 \end{frame}

\ifdefined\POSTER
  \begin{columns}
    %-- Column 1 --------------------------------------------------- 
   \begin{column}{0.22\columnwidth}
      \begin{block}{Happiness Generation - must maintain every week.}
\else
 \underline{\bf Happiness Generation - must maintain every week.} 
\fi
        % explain happiness: show gratitude 
        \begin{itemize}
          \tiny \item \tiny happy that I have Atul to show me.  
        %\item \tiny Happy that I have normal life up to this point.  
        %\item \tiny Think about dad saying, I understand, and want
        %you to be happy.
          \item \tiny T 
        \end{itemize}
\ifdefined\POSTER
      \end{block}
\fi

\ifdefined\POSTER
    \begin{block}{Habits}
\else
 \underline{\bf \it Habits} 
\fi 
      \begin{itemize} 
        \tiny \item \tiny back straight + eye contact. 
      \item \tiny lips relaxed. 
      \item \tiny watch what happens when a hot girl talks to you. 
      \end{itemize}
\ifdefined\POSTER
    \end{block} 
  \end{column} %1
\fi

\ifdefined\POSTER
  \begin{column}{0.5\columnwidth}
    \begin{block}{10-year plan}   %-- Block 2-1 
\else 
 \underline{\bf 10-year plan}
\fi
      \begin{itemize}
      \item \small Make someone and dad proud.
      \end{itemize}
\ifdefined\POSTER
    \end{block}
\fi

\ifdefined\POSTER 
    \begin{block}{3-year plan}
\else
\underline{\bf 3-year plan} 
\fi
      \begin{itemize}
      \item \small find someone
      \item \small make 150K
      \item \small network
      \end{itemize}
\ifdefined\POSTER
    \end{block} 
\fi

\ifdefined\POSTER
    \begin{block}{6-month plan}
\else
\underline{\bf 6-month plan}
\fi
        \begin{itemize}
          \small \item \small results + thesis
          \item \small routine + worklife
          \item \small             
          \end{itemize}
\ifdefined\POSTER
    \end{block} 
\fi


\ifdefined\POSTER  
    \begin{block}{Month-by-month}
\else
\underline{\bf Month-by-month} 
\fi 
      %howto: This is most important, and should be re-visited every
      %month and definitely every three months(have fixed time within
      %4 times in the year to do this). 
      \begin{itemize} 
      %\item \small \textit{May:} Work: finish paper  + Work: comm:
      %  finish resume and cover letter.  
      %\item \small \textit{June:} Work: code org and plan + Work:
      %  finish code + worklife: org + worklife: finish emotional int +
      %  Comm: experiences + Comm: TM. 
      \item \small \textit{July:} Work: library, Work:comm: job
        introductions, Comm: meet people.
      \item \small \textit{August:} Work: library documentation and
      experimentation, Work: comm: resume prep + Work:comm:linkedIn +
      Work:comm: interviewing skills + Work:rel: get headstart o jobs (fb and dshaw) + Comm: stay in touch with girls. 
      \item \small \textit{September:} Work:library + Work: paper writing + Work:comm: interviewing. 
      \item \small \textit{October:} Work:paper +  Work:rel:interviewing + Comm: dating 
      \item \small \textit{November:} worklife: review , Work:paper, Comm: dating 
      \end{itemize}
\ifdefined\POSTER 
    \end{block}
\fi

\ifdefined\POSTER
\begin{block}{May goals}
\else
\underline{\bf May goals}\\
\fi 

\begin{enumerate} 
\item \small Work: finish writing goals
  \small \item \small Mgmt:Spaces: clean room 
\item \small worklife: practice implemented work to form habits 
\item \small Comm: meet people 
\end{enumerate}

\ifdefined\POSTER
\end{block}
\fi

\ifdefined\POSTER
\begin{block}{\small \bf Week of September $31^{st}$: job search}
\else
\underline{\bf Week of September $31^{st}$: job search}\\
\fi

\begin{enumerate}
\tiny \item \tiny Work: finish connecting with people regarding implementation. 
\item \tiny Mgmt:Spaces: take care of driver's license. 
\item \tiny 
\item \tiny Comm: meet people 
\end{enumerate}

\ifdefined\POSTER
\end{block}
\fi

\ifdefined\POSTER
\begin{block}{Weekend Plans - March $15^{th}$, 2017 to May $1^{st}$,2017} 
\else
{\underline{\bf Weekend Plans - March $15^{th}$, 2017 to May $1^{st}$,2017}}\\ 
\fi
\begin{itemize}
\item \tiny Weekend of March $17^{th}$: Visit New York City. Details:
\item \tiny Weekend of March $24^{th}$: Visit San Francisco. Details:
\item \tiny Weekend of March $31^{st}$: Visit San Francisco. Details:
\item \tiny Weekend of April $6^{th}$:  Dad is coming, cherry
  blossoms.
\item \tiny Weekend of April $13^{th}$: Visit India.
\item \tiny Weekend of April $20^{th}$: Go to New York.
\item \tiny Weekend of April $26^{th}$: Go to Los Angeles.
\end{itemize}

{\underline{\bf  Weekend plans for weekends between May $1^{st}$, 2017
    and June$1^{st}$, 2017}}\\
\begin{itemize}
\item \tiny Weekend of May $5^{th}$: Visit New York.
\item \tiny Weekend of May $12^{th}$:
\item \tiny Weekend of May $19^{th}$:
\item \tiny Weekend of May $27^{th}$:
\end{itemize}

\ifdefined\POSTER
\end{block}
\end{column}
\fi

%-- Column 3 --------------------------------------------- 

\ifdefined\POSTER
\begin{column}{0.28\linewidth}
\begin{block}{\small \bf Regular Routines}
\else
\underline{\bf Regular Routines}\\ 
\fi 

%\input{../../../ViveksLaptop2/life/workLifeMgr/regularRoutines}
\input{./content_regularRoutines_plan}

\ifdefined\POSTER
\end{block}
\end{column}%3
\fi

\ifdefined\POSTER
\end{columns}
\fi
\ifdefined\POSTER
\begin{block}{\small \bf Week of September $31^{st}$: job search}
\else
\underline{\bf Week of September $31^{st}$: job search}\\
\fi

\begin{enumerate}
\tiny \item \tiny Work: finish connecting with people regarding implementation. 
\item \tiny Mgmt:Spaces: take care of driver's license. 
\item \tiny 
\item \tiny Comm: meet people 
\end{enumerate}

\ifdefined\POSTER
\end{block}
\fi
\begin{minipage}{0.5\textwidth}
\begin{itemize}
\tiny \item \tiny do scheduling strategies.
\item \tiny work on job talk.
\item \tiny do travel.
\item \tiny social on facebook, catch up with Rishi.
\end{itemize}
\begin{itemize}
\item \tiny 2-month plan: May: finish documents.  June:  finish paper.
\item \tiny 2-month plan: July: paper, meet people  August: paper, meet people.
\item \tiny 2-month plan: September: paper, meet people  October: paper, meet people.
\end{itemize}
\end{minipage}

\begin{multicols}{4}
\begin{minipage}{\columnwidth}
\input{content_projects_psm}
\end{minipage}

%\begin{minipage}{\columnwidth} 
%\input{content_projects_sdh}
%\end{minipage}

\begin{minipage}{\columnwidth}
\input{content_projects_ocn}
\end{minipage}


\begin{minipage}{\columnwidth}
\input{content_projects_ckh} 
\end{minipage}

\begin{minipage}{\columnwidth}
\input{content_projects_ckhp}
\end{minipage}

\begin{minipage}{\columnwidth}
\input{content_projects_scp}
\end{minipage}

\begin{minipage}{\columnwidth}
\underline{\bf \tiny {Mgmt:Spaces: settle on your own}}
\begin{enumerate}
  \tiny \item \tiny Dentist + Get dentist appointment.
\item \tiny Doctor / Counselor + CBT.
  %TODO: organize and group the below. 
\item \tiny Work pay and holidays / hours. 
\item \tiny Flights: finish flight decision making notes, e.g.,
  justification for travel, money/airfare rules, award travel rules. 
\item \tiny Car city sticker.
\item \tiny Car: Get windows side checked + Get windows marking
  checked Ask about warranty.
\item \tiny Mgmt:Spaces(crp): check car tailpipe +
  Mgmt:Spaces(crp):Window \te{1 hour}.
\item \tiny Mgmt:Spaces(bfa): buy things for apartment =
Mgmt:Spaces(bfa): buy a whiteboard + Mgmt:Spaces(bfa): get a chair 
that adjusts height and folds \te{} \dl{} \pr{}.
\end{enumerate}
\end{minipage}

\samepage
\begin{minipage}{\columnwidth}
\underline{\bf \tiny {Project: awards}}\\
\begin{enumerate} 
\item \tiny Stay in touch with HLF - talk to Peter email:  \url{typos^@aol.com}
\item \tiny Do energy econ work with convergence. 
\item \tiny Go to whitehouse thing. 
\item \tiny Plan to be on Program Committee of .. 
\end{enumerate}
\tiny \textit{Schedule:} Looking ahead:\\ 
\end{minipage}
\samepage
\begin{minipage}{\columnwidth}
\underline{\bf \tiny {Worklife:read social intelligence}}
\begin{enumerate} 
\tiny \item \tiny -
\end{enumerate} 
{{\bf  \tiny {Schedule:}} Comm: read social intelligence first four chapters
and get a method to take in information ???? 5 hours. Comm: link comm
together, worklife: latex viewpoint. Looking ahead:} \\
\end{minipage}

\begin{minipage}{\columnwidth}
\underline{\bf Work:code: Project , Coding practice: p for interview.}
\begin{enumerate}
\tiny \item \tiny Work:code (cp.): go through C++, Work:code (cp.): go
through Java + Work:code (cp.): go through OOP. 
\item \tiny Work:code (cp.): code up problems.  ???? 1 week.
\item \tiny Work:code (cp.): integer problems + numerics   -- 1 week.
\item \tiny Work:code (cp.): practice mock interview problems. ???? 1  week.
\end{enumerate}
{{\bf \tiny {Schedule:}} Work:code (cp.): finish bit
  manipulation, Work(cp.): review brain teasers in book, Work(cp.):
  Work(cp.): go through C++.}\\
\end{minipage}
\end{multicols}


\comments{
\begin{columns}
\begin{column}{0.5\columnwidth}
%{\underline{\bf Work:code: Project for running ptychoLib }}
\begin{block}{Work:code: Project for running ptychoLib}
\begin{enumerate}
\tiny \item \tiny Work: download ptychoLib from Kaushik and copy to git repo.
\item \tiny Work: discuss work with A rittenbach + Work: download driver on GPU4.
\item \tiny work: integrate.
\item \tiny Work: do OpenMP 4.5 for ptypy and OpenACC.
\item \tiny Work: run with dataset from PSI.
\item \tiny Work: send message about research paper.
\item \tiny Work: get profiles for PtychoLib code.  
\end{enumerate}
\end{block}

\begin{block}{Worklife:read social intelligence } 
\begin{enumerate} 
\tiny \item \tiny -
\end{enumerate} 
\fbox{\tiny \textit{Schedule:} Comm: read social intelligence first four chapters
and get a method to take in information ???? 5 hours. Comm: link comm
together, worklife: latex viewpoint. Looking ahead:}\\ 
\end{block}

\begin{block}{Mgmt:Spaces: settle on your own}
\begin{enumerate}
  \tiny \item \tiny Dentist + Get dentist appointment.
\item \tiny Doctor / Counselor + CBT.
  %TODO: organize and group the below. 
\item \tiny Work pay and holidays / hours. 
\item \tiny 401k+retirement  + fidelity + bank (money owing).
\item \tiny Flights: finish flight decision making notes, e.g.,
  justification for travel, money/airfare rules, award travel rules.
\item \tiny Car city sticker.
\item \tiny Car: Get windows side checked + Get windows marking
  checked + Get tailpipe checked + Ask about warranty. 
\item \tiny Mgmt:Spaces(crp): check car tailpipe +
  Mgmt:Spaces(crp):Window \te{1 hour}.
\item \tiny Mgmt:Spaces(bfa): buy things for apartment =
  Mgmt:Spaces(bfa): buy a whiteboard + Mgmt:Spaces(bfa): get a chair
  that adjusts height and folds \te{} \dl{} \pr{}. 
\end{enumerate}
\end{block} 

\begin{block}{Mgmt:wp}
\begin{enumerate}
\item \tiny Mgmt:wp: I like Tesla cars and support the company's
  disruption to its industry. At the same time, I don????t think
  that the company will devalue instantaneously the engineering
  accumulated over 8 decades in a BMW.
  {I like cars by Tesla and am supportive of the company????s
    disruptiveness to industry. However, I can????t imagine
    that the company????s cars will make the eight decades of
    engineering that????s in my BMW engine become worthless.
    Tesla technology
    TODO:L3: intent: explain supportiveness of disruptve
    TODO:L3: outcome: people see what I????m about 
    TODO: L4: disruptiveness to industry VS disruption to industry 
    TODO: L4: I have a hard time VS I can????t imagine VS I
    don????t think VS
    TODO:L4: At the same time, VS However, 
    TODO:L4: truly VS [OMIT] 
    TODO:L4: I like VS I love}. 
\item \tiny Mgmt:Spaces: get car check engine light updated
  + Mgmt:Spaces: do car's registration. 
\item \tiny Mgmt:wp: post about Queen.
\item \tiny Mgmt:wp: post about Beckham. 

\item \tiny Mgmt:wp: post about Tesla's. 
\item \tiny Mgmt:wp: post about science on FB. 
\item \tiny Mgmt:wp: post about Queen.
\item \tiny Mgmt:wp: update fb with queen's picture. \te{10
  minutes}. 
\item \tiny Mgmt:wp: Write up on facebook.  
\end{enumerate}           
\end{block} 

\begin{block}{Worklife - Project ???? Comm:rel:}
\begin{enumerate} 
  \tiny \item \tiny Worklife: link management together.  
\item \tiny Worklife: link habits comm and Toastmasters. - done
\item \tiny Worklife: latex viewpoint. 
\item \tiny Comm: read social intelligence first four chapters.
\item \tiny Comm: link all comm together.
\item \tiny Worklife: get emails and texts to analyze.
\item \tiny Worklife: figure out how to book flights and trips quickly. 
\end{enumerate}
\fbox{\tiny \textit{Schedule:} Comm: read social intelligence first
  four chapters and get a method to take in information ???? 5
  hours. Comm: link comm together, worklife: latex viewpoint. Looking ahead:  }
\end{block} 

\begin{block}{Project: Comm}
\begin{enumerate}
\tiny \item \tiny Comm: consider view of girl on Shaadi. 
\item \tiny Comm: consider talking to Illina.
\item \tiny Comm: talk to friends from high school.
\item \tiny Mgmt:Spaces: plan trips. \te{-}.
\item \tiny Mgmt:webpresence: cancel FB friend request of Jocelyn + Mgmt:webpresence: check other friend requests
  sent requests. \te{-}. 
\item \tiny Mgmt:Spaces(GetThingsSpring2016): get Things =
  Mgmt:Spaces(getThings): get suit. \doneTask{Mgmt:webpresence: delete
    Anil Taneja from LinkedIn. \te{1 hour} \dl{Monday} \pr{UI}. - not
    needed since we met with Rishi+ Comm: may have not accepted + Mgmt:webpresence: bad to do so}
\end{enumerate}
{\fbox{\tiny {\it Schedule:} meet others over summer, meet girl over summer.}}\\
%TODO: figure out why this was the issue
\end{block}

\begin{block}{Project: Comm:rel}
\begin{enumerate} 
  \tiny \item \tiny Comm: consider what to do about Bhavna.
\item \tiny Comm: get caught up with Matrimony and Shaadi, Use match,
  make system for meeting. -done
\item \tiny Comm:rel: discuss with Mom and Dad. 
\end{enumerate}
\end{block}

\begin{block}{Work:rel: Project ???? interview with  Berkeley/MIT/industry} 
  \begin{enumerate}
    \tiny \item \tiny Business cards:  - use latex  -- 40 minutes. 
  \item \tiny Cover letter. 
  \item \tiny CV: + Research Summary:  -- 1 week.  - Talking about your
    research. 
  \item \tiny Work:rel: message to contacts about Microsoft \te{} \dl{} \pr{}. 
  \item \tiny Behavioral questions answers:    -- 1 week. 
  \item \tiny Structure in latex. 
  \end{enumerate}
{\small {\it Schedule:} Behavioral answers ???? 1 week, CV prep - 1 day,
  business cards, cover letter -1 hour. }\\ 
\end{block}
\end{column}

\begin{column}{0.5\columnwidth}
\begin{block}{Mgmt:Spaces}
\begin{enumerate} 
\item \tiny Mgmt:Spaces(GetThingsSpring2016): get Things = Mgmt:spaces: get suit
\item \tiny Mgmt:Spaces: get 1 TB disk drive. 
\item \tiny Mgmt:Spaces: finish transferring pictures + Mgmt:Spaces: figure out
how to delete photos from iPhoto + Mgmt:Spaces: figure out why size of
photo booth stays the same  Mgmt:Spaces: Figure out airplane photos
and put in proper album folder. Mgmt:Spaces: Organize photos in
folders + Mgmt:Spaces: Confirm pictures are placed properly and delete
from photos + Mgmt:Spaces: Compress photos into zip drive. +
Mgmt:Spaces: Move photos from folders into temporary disk / USB stick 
+ Mgmt:Spaces:Delete photos from iPhone.
\end{enumerate} 
\end{block}

\begin{block}{Work:comm: (can impact work):}
\begin{enumerate}
\tiny \item \tiny Work:rel: add Shikha.
\item \tiny Mgmt:webpresence: fb like to Lagha. 
\end{enumerate}
\end{block} 

\begin{block}{Work:rel: -  Project ???? Comm: rel:}
\begin{itemize} 
\item \tiny Comm:rel: meet others:  Sweta Kambaskadwar. + Mgmt:webpresence: fb
like of Shalaka????s. L3:past: she liked and suggested to come, lots of
time delayed. I didn????t like back.  Intent: show interest. Outcome:
stay alive with Rucha?
\item \tiny Mgmt:webpresence: take Xin Zhao off and remove anyone else that you
don????t want from work.
\item \tiny Mgmt:webpresence: consider deleting asdfjkl;  and making parts of facebook bmm 2006 public. 
\end{itemize}
\end{block}

\begin{block}{Interview preparing}
%\underline{\bf Work:code: Project , Coding practice: p for interview.}
\begin{enumerate}
\tiny \item \tiny Work:code (cp.): go through C++, Work:code (cp.): go
through Java + Work:code (cp.): go through OOP. 
\item \tiny Work:code (cp.): code up problems.  ???? 1 week.
\item \tiny Work:code (cp.): integer problems + numerics   -- 1 week.
\item \tiny Work:code (cp.): practice mock interview problems. ???? 1  week.
\end{enumerate}
{\tiny {\it {\tiny Schedule:}} Work:code (cp.): finish bit
  manipulation, Work(cp.): review brain teasers in book, Work(cp.):
  Work(cp.): go through C++.} \\
%{\underline{\bf Project: job talk prep}} 
{\tiny {\it {\tiny Schedule:}} Work:code (cp.): finish bit manipulation, Work(cp.): review brain teasers in book, Work(cp.): Work(cp.): go through C++.}\\
\end{block}

\end{column}

\end{columns}
}
\underline{\bf Morning}
\begin{itemize}
\tiny \item \tiny Brush Teeth \timeEst{4 mins}.
\item \tiny Mouthwash, Clean tongue - it helps with breath\timeEst{1mins}
\item \tiny Eating small breakfast.
\item \tiny Check your schedule for meetings / appointments for that
day: Is anything urgent? \timeEst{5 mins}.
\item \tiny Excercise: 1 hour ( Stretch for 10 mins, Treadmill for 30
mins , Lift weights or Yoga 1 hour, Meditation for 10 mins).
\item \tiny Shave (at least every other day) \timeEst{5 mins}.
\item \tiny Shower : (shampoo+conditioner, acne wash,  soap on
underarms/underbody) \timeEst{10 mins}
\item \tiny dry hair, dry face, arms, legs, back, stomach \timeEst{3
mins}
\item \tiny Clothing: belt, check collar, shirt not half-tucked,
matching socks \timeEst{5 mins}
\item \tiny Comb hair, hair gel optional \timeEst{ 1 min}
\item \tiny Check Keys/Wallet/Cell/Badge (get a bucket) \timeEst{1
min}
\item \tiny Open meds cabinet, get water, take medicines \timeEst{1
min}
\item \tiny Wear lenses and rinse out case \timeEst{ 2 mins}
\item \tiny Deodorant or cologne depending on the day \timeEst{1 min}
\item \tiny Wash your face with a face wash - it helps with
acne \timeEst{3 mins}
\item \tiny Moisturize - apply lotion \timeEst{ 2 min}
\item \tiny Neti pot / clean out sinuses - if you’re feeling
congested \timeEst{5 min}
\item \tiny clean out ears, nose \timeEst{5 mins}
\item \tiny Remember to lock door \timeEst{1 mins}
\end{itemize}

\underline{\bf Evening}
\begin{itemize}
\tiny \item \tiny Call family: 30 mins
\item \tiny meet friends: 20 mins
\item \tiny Cleaning dishes / cleaning house: 10 mins
\item \tiny Lay out clothes for the next day, iron if necessary
\item \tiny start laundry if needed: 10 mins,
\item \tiny Collect anything you’ll need for the next day (e.g. dry
cleaning to drop off): 5 mins,
\item \tiny Check Facebook/linkedin/google+: 10 mins, matrimony stuff:10 mins,
\item \tiny Food for lunch/dinner the next day: 10 mins
\end{itemize}
\underline{\bf Night before bed}
%TODO: why isn't enumerate working???
\begin{itemize}
\tiny \item \tiny Finish computer stuff \timeEst{5 mins}
\item \tiny Get into sleeping clothes \timeEst{1 mins}
\item \tiny Before sleeping: brush teeth, floss \timeEst{2 min} 
\item \tiny Properly wash and put away contacts \timeEst{2 mins}
\item \tiny Review the days good things \timeEst{10 min} 
\item \tiny Light Reading \timeEst{ 10 min}
\item \tiny Prayer \timeEst{10 mins}
\end{itemize}
\begin{block}{Jobs}
  \begin{itemize}
    \tiny \item \tiny cat1: D.E. Shaw | SUNY/BNL: applying . | IBM:
    applied,interviews.  | Sandia: applied and failed, Cray: applied and got offer, USC. 
  \item \tiny cat2: Intel: Applied and failed. Intel: re-application  completed, AMD: applied, Samsung, VMWare: Contacting Yavatkar Kaka. 
  \item \tiny cat3: Google. MongoDB: applied and failed, Facebook. 
  \item \tiny cat4: LLNL. 
  \end{itemize} 
\end{block} 

%TODO: check if below is needed. 
      %\item Friends: Amit, Sangita, Anchit, Kevin. 
      %Networking: 
  \begin{block}{Comm:friends} 
    \begin{itemize} 
    \item Palekar’s:  
      \begin{itemize}
      \item UP: 
      \item Rohun: 
      \end{itemize} 
    \item Bhagwat’s: 
    \item Kapoor’s: 
      \begin{itemize}
        \tiny \item \tiny Anchit: Interaction. Atul is smart. 
      \item \tiny Shuchi: 
      \end{itemize}
    \item Sudharshan’s: 
      \begin{itemize} 
        \tiny \item \tiny Amit:  
      \item \tiny Sangita:  
      \end{itemize}
    \item Kumar’s:
      \begin{itemize}
        \tiny \item \tiny Ashwin: 
      \item \tiny Shilpa: 
      \end{itemize}
    \item Saied’s: 
      \begin{itemize}
        \tiny \item \tiny Laila 
      \item \tiny Faisal 
      \item \tiny Ayesha
      \end{itemize} 
    \item Kukreti’s:
    \item Kumar’s:
    \item UIUC friends: 
      \begin{itemize} 
        \tiny \item \tiny Sadhna: 
      \item \tiny Rishi: 
      \item \tiny Amaeya: 
      \item \tiny Chris: 
      \item \tiny Brian: 
      \item \tiny Arif 
      \end{itemize}
    \item grad school friends 
      \begin{itemize} 
        \tiny \item \tiny  Karan: 
      \item \tiny Gopi: 
      \item \tiny Amanda:  
      \end{itemize}
    \end{itemize} 
  \end{block}
  
%  \begin{block}{Rel} 
%    \begin{itemize} 
%      \small \item \small Shwetha K/r
%    \item \small Shalaka 
%    \item \tiny DCK girl 
%    \item \tiny  Shikha Singhvi: initiated.  
%    \item \small Mamta
%    \item \small Avani 
%    \item \small SH05702678 Palo Alto - 
%    \item \small Sheila G -Sh93522198  
%    \item \small sonalisinha  s: 5103658167 and my email address is: \url{2sonalisinha@gmail.com}
%    \item \small Nandini  - 
%    \item \small Archana from San Jose. 
%    \item \small Im from DC  - B475435: parents initiated. 
%    \item \small Sruthi 
%    \item \small SH12825009 New York, New York - Finance Professional 
%    \item \small Navneet K  - 29 5'8" - SH88263211 
%    \item \small Girl from New York  -27 years
%    \item \small Shwetha Ravi 
%    \item \small Ruchira K ( SH34021888 )2-Way           
%    \item \small SH11680694 from San Francisco. 
%    \item \small Sandhya N. 22 Jun 2016 
%    \item \small Aarti S - 27 - 5' 9'' Charlotte.  
%    \item \small Anu M from Chicago, IL 
%    \item \small Pranati A from Cleveland, OH - 
%    \item \small Meghana K from New York - 
%    \item \small Ssd S - 28 , 5 5 , Boston, MA 
%    \item \small Anj B. - 30 yrs - SH13882555.
%    \end{itemize}
%  \end{block}
\begin{itemize}
          \tiny \item \tiny Monday: 
        \item \tiny Tuesday
        \item \tiny Wednesday
        \item \tiny Thursday
        \item \tiny Friday
        \item \tiny Saturday
        \end{itemize} 

{\underline{\bf Week Plan}  Work: send message to Prof. Gropp, Work: finish getting data set to work,
        Work: talk to Kristina, Mgmt:Spaces: take care of license
        plant + Mgmt:Spaces: take care of Virginia parking ticket,
        Comm: message to Kavita to send pictures}\\ 
      {\underline{\bf Weekend Plan:} Go to NYC, meet Ranjit, see BNL.}\\

%--- Page 2: Block 1-4 
      % howto:Recognize emotions / recognize (precisely) what you're worried about -> methods for eliminating worry. 
      % clean out old worries, put them in pastWorries doc.  
      % remember to define precisely 
      % order from top-to bottom
      \begin{itemize}
        \tiny \item \tiny Anger about UP -> think about the positive
        perspective, and the original
      \item \tiny Anger about Mr. Kapoor ->  leave it
      \item \tiny Anger about a b  -> ...
      \item \tiny Issue with USC : --> things get better. 
      \end{itemize}
\begin{minipage}{0.5\textwidth}
\begin{itemize}
\tiny \item \tiny do scheduling strategies.
\item \tiny work on job talk.
\item \tiny do travel.
\item \tiny social on facebook, catch up with Rishi.
\end{itemize}
\begin{itemize}
\item \tiny 2-month plan: May: finish documents.  June:  finish paper.
\item \tiny 2-month plan: July: paper, meet people  August: paper, meet people.
\item \tiny 2-month plan: September: paper, meet people  October:
  paper, meet people.
\end{itemize}
\end{minipage}

\begin{multicols}{4}
\begin{minipage}{\columnwidth}
\underline{\bf \tiny {Work:code: PRISMA}}
\begin{enumerate}
\item \tiny Work: fix Youssef's code.
\item \tiny Work: download ptychoLib from Kaushik and copy to git repo.
\item \tiny Work: run for Ptypy.
\item \tiny Work: figure out time to talk with Youssef.
\item \tiny Work: download ptychoLib from Kaushik and copy to git repo.

\item \tiny Work: discuss work with A rittenbach + Work: download
  driver on GPU4.

\item \tiny work: integrate.
\item \tiny Work: do OpenMP 4.5 for ptypy and OpenACC.
\item \tiny Work: run with dataset from PSI.
\item \tiny Work: send message about research paper.
\item \tiny Work: get profiles for PtychoLib code.
\item \tiny Work: write report for spec.
\item \tiny Work: ask for an increase in size for HPCC system.
\end{enumerate}
\end{minipage}

\begin{minipage}{\columnwidth}
\underline{\bf \tiny {Work: PRISMA pubs}}
\begin{enumerate}
\tiny \item \tiny Work: create a latex git repo for paper.
\item \tiny Work: find a conference.
\item \tiny Work: create an outline.
\item \tiny Work: get information about JIT compilation.
\end{enumerate}
\end{minipage}

\begin{minipage}{\columnwidth}
\underline{\bf \tiny {Work: Other work at ISI}}
\begin{enumerate}
\item \tiny Work: get information about JIT compilation.
\end{enumerate}
\end{minipage}

\begin{minipage}{\columnwidth}
\underline{\bf \tiny {Work: OpenMPCon submission}}
\begin{enumerate}
\tiny \item \tiny Work: create a latex git repo for paper.
\item \tiny Work: send Prof. Gropp a message.
\item \tiny Work: make notes on static/dynamic scheduling.
\item \tiny Work: make notes on user-defined scheduling.
\end{enumerate}
\end{minipage}

\begin{minipage}{\columnwidth}
\underline{\bf \tiny {Work: Charm++ +OpenMP}}
\begin{enumerate}
\tiny \item \tiny Work: send notes/tasks todo.
\item \tiny Work: do documentation of implementation.
\item \tiny Do Charm++ + OpenMP implementation.
\item \tiny Get GPU implementation of dotProd in Charm++.
\item \tiny Work: get access to Cori machine.
\item \tiny Work: Add notes about OpenMP.
\item \tiny Work: add explanation of dotProduct on OpenMP.
\end{enumerate}
\end{minipage}

\begin{minipage}{\columnwidth} 
\underline{\bf \tiny {Work: Charm++ +OpenMP}}
\begin{enumerate}
\item \tiny Mgmt:wp: post with friends from college. 
\item \tiny Mgmt:wp: update description.
\item \tiny Mgmt:wp: post about Queen.
\item \tiny Comm:rel: update pictures. \te{30 minutes}.
\end{enumerate}
\end{minipage}

\ifdefined\POSTER
  \begin{columns}
    %-- Column 1 ---------------------------------------------------  
   \begin{column}{0.22\columnwidth}
      \begin{block}{Happiness Generation - must maintain every week.}
\else
 \underline{\bf Happiness Generation - must maintain every week.}
\fi
        % explain happiness: show gratitude
\begin{itemize}
          \tiny \item \tiny happy that I have Atul to show me.
        %\item \tiny Happy that I have normal life up to this point. 
       %\item \tiny Think about dad saying, I understand, and want     
          %you to be happy.                             
          \item \tiny T
            \end{itemize}
\ifdefined\POSTER
      \end{block}
\fi

\ifdefined\POSTER
    \begin{block}{Habits}
\else
 \underline{\bf \it Habits}
\fi
      \begin{itemize}
        \tiny \item \tiny back straight + eye contact.
      \item \tiny lips relaxed.
      \item \tiny watch what happens when a hot girl talks to you.
      \end{itemize}
\ifdefined\POSTER
    \end{block}
  \end{column} %1 
\fi

\ifdefined\POSTER
  \begin{column}{0.5\columnwidth}
    \begin{block}{10-year plan}   %-- Block 2-1   
\else
 \underline{\bf 10-year plan}
\fi
      \begin{itemize}
      \item \small Make someone and dad proud.
      \end{itemize}
\ifdefined\POSTER
    \end{block}
\fi

\ifdefined\POSTER
    \begin{block}{3-year plan}
\else
\underline{\bf 3-year plan}
\fi
      \begin{itemize}
      \item \small find someone
      \item \small make 150K
      \item \small network
      \end{itemize}
\ifdefined\POSTER
   \end{block}
      \item \tiny watch what happens when a hot girl talks to you.
      \end{itemize}
\ifdefined\POSTER
    \end{block}
  \end{column} %1                                                                                           
\fi

\ifdefined\POSTER
  \begin{column}{0.5\columnwidth}
    \begin{block}{10-year plan}   %-- Block 2-1         
\else
 \underline{\bf 10-year plan}
\fi
      \begin{itemize}
      \item \small Make someone and dad proud.
      \end{itemize}
\ifdefined\POSTER
    \end{block}
\fi

\ifdefined\POSTER
    \begin{block}{3-year plan}
\else
\underline{\bf 3-year plan}
\fi
      \begin{itemize}
      \item \small find someone
      \item \small make 150K
      \item \small network
      \end{itemize}
\ifdefined\POSTER
    \end{block}
\fi

\ifdefined\POSTER
    \begin{block}{6-month plan}
\else
\underline{\bf 6-month plan}
\fi
        \begin{itemize}
          \small \item \small results + thesis
          \item \small routine + worklife
          \item \small
          \end{itemize}
\ifdefined\POSTER
    \end{block}
\fi

\ifdefined\POSTER
    \begin{block}{Month-by-month}
\else
\underline{\bf Month-by-month}
\fi
      %howto: This is most important, and should be re-visited every  
      %month and definitely every three months(have fixed time within  
      %4 times in the year to do this).     
      \begin{itemize}
      %\item \small \textit{May:} Work: finish paper  + Work: comm: 
      %  finish resume and cover letter. 

\ifdefined\POSTER
\begin{block}{May goals}
\else
\underline{\bf May goals}\\
\fi

\begin{enumerate}
\item \small Work: finish writing goals
  \small \item \small Mgmt:Spaces: clean room
\item \small worklife: practice implemented work to form habits
\item \small Comm: meet people
\end{enumerate}

\ifdefined\POSTER
\end{block}
\fi

\ifdefined\POSTER
\begin{block}{\small \bf Week of September $31^{st}$, 2017:}
\else
\underline{\bf Week of July $31^{st}$: }\\
\fi

\begin{enumerate}
\tiny \item \tiny Work: finish connecting with people regarding implementation.
\item \tiny Mgmt:Spaces: take care of driver's license.
\item \tiny Comm: meet people.
\end{enumerate}

\ifdefined\POSTER
\end{block}
\fi

\ifdefined\POSTER
\begin{block}{Weekend Plans - March $15^{th}$, 2017 to May $1^{st}$,2017}
\else
{\underline{\bf Weekend Plans - March $15^{th}$, 2017 to May $1^{st}$,2017}}\\
\fi

\input{plansForWeekend}

\begin{itemize}
\item \tiny Weekend of July $21^{st}$: Get car fixed. Visit NYC . Details: 
\item \tiny Weekend of July $28^{th}$: Visit Champaign  . Details:
\item \tiny Weekend of August $6^{th}$: Visit NYC Details:
\item \tiny Weekend of August $12^{th}$: Visit SFO?
\item \tiny Weekend of August $19^{th}$: Stay in D.C. - work on weekend.
\item \tiny Weekend of August $26^{th}$: Stay in D.C. - work on weekend.

\item \tiny Weekend of September $3^rd$: Go to San Francisco.

\item \tiny Weekend of September $26^{th}$: Go to New York City.
\item \tiny Weekend of September 
\end{itemize}

\end{itemize}

\ifdefined\POSTER
\end{block}
\fi 

\begin{minipage}{\columnwidth}
\begin{enumerate} 
 \item \tiny Mgmt:Spaces: look for apartment elsewhere. \te{1 hour}. 
\end{enumerate}
\end{minipage} 
\end{multicols}

\begin{columns}
  %-- Page 2: Column 1 --------------------------------------------------- 
  \begin{column}{0.20\linewidth}
    %{\textbf{\underline{Week Aspects(new name)}})
      %--- Page 2: Block 1-1 
    \begin{block}{Routines}
      { \tiny \underline{\bf Routines:} Morning: bfast, exercise/brush,
        floss, shower (hair, eyes, ears, underarms, feet), meds, belt,
        comb hair / dishes, clean kitchen floor. |  Night: running/ put
        away dishes, clean kitchen floor / brush teeth, charge phone,
        clothes for tomorrow, contacts off.}\\
      {\tiny \underline{\bf Sunday Routines:} Routines:
        Experiences,week plan.}\\ 
      {\tiny \underline{\bf Weekday Routines:}}\\
      %TODO: check if weekday routines overlaps into daily routines.
    \end{block} 
      %--- Page 2: Block 1-3
    \begin{block}{Local Happiness}
      % howto:Recognize emotions / recognize (precisely) what you're
      % worried about -> methods for eliminating worry. 
      % clean out old worries, put them in pastWorries doc.  
      % remember to define precisely 
      % order from top-to bottom
      \begin{itemize} 
        \tiny \item \tiny -
      \item \tiny Worrying about gal: think about talking to others.
      \end{itemize} 
    \end{block}
    %--- Page 2: Block 1-4 
    \begin{block}{AngersAndAnxieties}
      % howto:Recognize emotions / recognize (precisely) what you're worried about -> methods for eliminating worry. 
      % clean out old worries, put them in pastWorries doc.  
      % remember to define precisely 
      % order from top-to bottom
      \begin{itemize}
        \item \tiny Issue with USC : $\rightarrow$ things get better. 
        \tiny \item \tiny Anger about UP $\rightarrow$ think about the positive
        perspective, and the original
      \item \tiny Anger about Mr. Kapoor $\rightarrow$  leave it
      \item \tiny Anger about a b  $\rightarrow$ ...
      \end{itemize}
    \end{block}
      %-- Block 1-5
      \begin{block}{Life notes}
        \begin{itemize}
          \tiny \item \tiny Social Intelligence: 
        \end{itemize}
      \end{block}
      % howto:
      \begin{block}
        {\tiny {\bf Week lessons:}}
        \begin{enumerate}
%          \tiny \item \tiny Win Friends/ Influence People
%        \item \tiny Go through 7 habits.
        \item \tiny tm tips.
        \item \tiny Coding problem: 
        \item \tiny Chess tips: 
        \end{enumerate}
            {{\tiny {\tiny \bf  News:}} {\tiny  M: Uber board | S:
                Tony Award's| E: Fallon:  Kimmel:  Colbert: SNL:}}
            {{\tiny {\tiny \bf  Weather:}} {\tiny M: 1100 T: 1100 W:
                0110 R: 0100 F: 0110 Sa: 0110 Su: }}
      \end{block}
  \end{column}
  %-- Column 2 ---------------------------------------------
  \begin{column}{0.6\linewidth}
    \begin{block}{Week Summary} 
      {\underline {\bf Week Plan:} 
        Work: message to Youssef,
        Work: send out write up for git repo, Work: make plan for diffraction patterns, 
        Mgmt:Health: get dentist appointment, Mgmt:Spaces: xcel card,
        Mgmt:Spaces: call doctor for medicine appointment,
        Mgmt:Spaces: fix car tires, Mgmt:Spaces: flight for July,
        Mgmt:Spaces: look for apartment elsewhere,} \\

      {\underline{\bf Weekend Plan:} Meet Puja, Meet Srushti }\\
    \end{block} 
      \begin{block}{Running ToDo} % find a better name 
        \begin{enumerate} 
        \tiny \item \tiny \textbf{Curr} $\rightarrow$ 
      
     \item \tiny Work: put information on installing PtychoLib for Kaushik. 
     \item \tiny Mgmt:Health: get x-rays. 
     \item \tiny Mgmt:Health: call for dentist appointment at Virginia
       dental.
     \item \tiny Mgmt:Health: call about the counselor. 
     \item \tiny Work: run Youssef’s code with params.
     \item \tiny Mgmt:Spaces: book flight to California.
     \item \tiny Mgmt:Spaces: put up apartment for rent.
     \item \tiny Mgmt:Spaces: buy Kitchen magnet.
     \item \tiny Comm: message to Renata.
     \item \tiny EI: get the counselors taken care of in D.C. area. 
     \item \tiny Mgmt:Spaces: look for apartment elsewhere. 
     \item \tiny Work: do writeup for paper. \te{1 hour}. 
     \item \tiny Work: send message to Youssef about question about
       \texttt{nvprof}. \te{1 hour}.
     \item \tiny Mgmt:Spaces: book flight for trip in December. \te{1
       hour}.
     \item \tiny Comm: message to Rohina. 
     \item \tiny Work:rel: email to Renata. \te{10 minutes}. 
     \item \tiny worklife: read social intelligence. \te{2 hour}. 
     \item \tiny Comm: do review for Liberty Towers.
     \item \tiny \textbf{ <-- End Curr } 

     \item \tiny Work: IM system for LLNL.
=======

        \doneTask{Mgmt:Spaces: fix car tires.}


        \tiny \item \tiny \textbf{Curr} $\rightarrow$ 
        \item \tiny Work:admin: tell about reimbursements 
        \item \tiny  Mgmt:Spaces: look for apartment elsewhere. 

        \item \tiny Work: message to Youssef.   

        \item \tiny Work: email about schedule for work. 
        \item \tiny Work: email about git repository. 
        \item \tiny 

        \item \tiny Work: send out write up for git repo 
        \item \tiny Work: make plan for diffraction patterns
        \item \tiny Work: send message about optimizations to do for
          CkLoop. \te{1 hour} \dl{20 minutes}.
         
        \item \tiny Work:rel: email to Abid \te{1 hour}. 

        \item \tiny Mgmt:Health: get dentist appointment. 

        \item \tiny Mgmt:Spaces: flight for September. 
        \item \tiny Mgmt:Spaces: book flight for trip in July to Chicago . \te{1 hour}  
          
        \item \tiny Mgmt:Spaces: xcel card. 
        \item \tiny Mgmt:Spaces: call doctor for medicine appointment.

        \item \tiny Mgmt:Spaces: look for apartment elsewhere          

        \item \tiny Mgmt:Spaces: book flight for trip in December. \te{1 hour}.

        \item \tiny  Comm: prep to meet with Rohina. 
        \item \tiny Comm: message to Shalaka?
        \item \tiny Work:rel: email to Renata. \te{10 minutes}.
        \item \tiny worklife: read social intelligence. \te{2 hour}.           
          
        \item \tiny \textbf{ <-- End Curr } 
          
        \item \tiny Work: IM system for LLNL.
>>>>>>> f99874ec2397c111e47d40225e53c07d5693f7fd
        \end{enumerate}
      \end{block}
      
      % howto: the below is a routine based on the job I'm doing and the
      % circumstances I'm in. Note that this is different from routines
      % above, which is true for a long-term period of over 10 years. 
      \begin{block}{Weekly Meetings}
        \begin{itemize}
          \tiny \item \tiny IWOMP affinity meeting Thursday 7 AM PDT / 9 AM
          CDT call in: 805-639-779 pswd: places. \url{https://llnl.webex.com/llnl/j.php?MTID=m33950b76befb72c0cbc31ea2e3be720c}
        \item \tiny DEG group meeting.  
        \end{itemize}
      \end{block} 
      \begin{block}{Week Daily Schedule}
        % howto: arrange items from running todo into the below
        % sheet management document. 
        %NOTE: we don't use the table format because of fittting
        \begin{columns}
          \begin{column}{0.14\textwidth}{\small \underline{\bf Mon}}
            {\tiny \bf {\tiny weather:} } {\tiny 11/1 s} \\ 
            {\tiny \bf {\tiny todo}}\\ 
            \begin{itemize}
              \tiny \item \tiny Work: do experiments with multiple nodes. 
            \item \tiny Work: get experiments using real data.  
            \item \tiny 
            \end{itemize}
                {\small  \bf schedule}\\
                \begin{enumerate} 
                  \tiny \item \tiny 8-9AM: Regular Routines 
                \end{enumerate}
          \end{column}

          \begin{column}{0.14\textwidth}{\small \underline{\bf Tues}}
            {\bf {\tiny  weather:} } {\tiny 3/1 r} \\ 
            {\bf {\tiny todo}}\\ 
            \begin{itemize}
              \tiny \item \tiny Work: do write-up 
            \end{itemize} 
                {{\bf {\tiny  schedule}}}
                \begin{enumerate} 
                  \tiny \item \tiny 8-9AM: Regular Routines 
                \end{enumerate} 
          \end{column}
          \begin{column}{0.14\textwidth}{\small \underline{\bf Wed}}
            {\tiny \bf weather: } {\tiny 3/1 r} \\ 
            {\tiny {\bf todo}}\\
            \begin{itemize}
              \tiny \item \tiny Work: send email to Prof. Gropp. 
            \item \tiny 
            \item \tiny Comm: message to Anita. 
            \end{itemize}
                {\tiny \bf schedule}\\
                \begin{enumerate} 
                  \tiny \item \tiny 8-9AM: Regular Routines 
                \end{enumerate} 
          \end{column}

          \begin{column}{0.14\textwidth}{\small \underline{\bf Thurs}}
            {\tiny \bf weather: } {\tiny 1/-1 r }\\ 
            {\tiny \bf todo} \\ 
            \begin{itemize}
              \tiny \item \tiny Add in schedule
            \item \tiny 
            \end{itemize} 
                {\tiny {\bf schedule}} \\
                \begin{enumerate} 
                  \tiny \item \tiny 8-9AM: Regular Routines 
                \end{enumerate}
          \end{column} 
          
          \begin{column}{0.14\textwidth}{\small \underline{\bf Fri}}
            {\tiny \bf weather: } {\tiny 3/1 r} \\ 
            {\tiny \bf todo} \\ 
            \begin{itemize}
              \tiny \item \tiny Add in schedule
            \item \tiny 
            \end{itemize} 
                {\tiny \bf schedule} \\
                \begin{enumerate} 
                  \tiny \item \tiny 8-9AM: Regular Routines 
                \end{enumerate}
          \end{column}

          \begin{column}{0.15\textwidth}{\small \underline{\bf Sat}}
            {\tiny \bf weather: } {\tiny 11/1 .2r} \\ 
            { \tiny \bf todo} \\ 
            \begin{itemize}
              \tiny \item \tiny Add in schedule
            \item \tiny 
            \end{itemize} 
                {\tiny \bf schedule} \\
                \begin{enumerate} 
                  \tiny \item \tiny 8-9AM: Regular Routines 
                \end{enumerate}
          \end{column}
         
          \begin{column}{0.15\textwidth}{\small \underline{\bf Sun}}
            {\tiny {\bf weather:} } {\tiny 11/2 r} \\ 
            {\tiny {\bf todo}}\\
            \begin{itemize}
              \tiny \item \tiny Add in schedule
            \end{itemize} 
                {\tiny \bf schedule}\\
                \begin{enumerate} 
                  \tiny \item \tiny 8-9AM: Regular Routines 
                \end{enumerate}
          \end{column}
        \end{columns}
      \end{block}
\end{column}
    
    % ------ Page 2: Column 3
    \begin{column}{0.20\linewidth}
      % ------ Block 2.3.1 
      \begin{block}{Food Plan} 
        \begin{itemize}
          \tiny \item \tiny Google Express: DHDQQJQDRFTXDM95B
        \end{itemize}
      \end{block} 
      \begin{block}{Clothes plan} 
        \begin{itemize}
          \tiny \item \tiny Monday: 
        \item \tiny Tuesday
        \item \tiny Wednesday
        \item \tiny Thursday
        \item \tiny Friday
        \item \tiny Saturday
        \end{itemize} 
      \end{block} 
      
      %-- Block 3-3 
      \begin{block}{Situations}
        % Summary: the below are the situations that define one
        % another.
        % Howto: Put post notes of each situation from list of previous
        % week. Put high importance situations in situationslist. 
        % Put list of upcoming situations on Sunday morning with Pre. 
        \begin{itemize}
          \tiny \item \tiny 
        \item \tiny 
        \end{itemize}
      \end{block}
      % contingincies: 
      % Summary:
    \end{column}
\end{columns}
\ifdefined\POSTER
\begin{block}{Weekend Plans - October $29^{st}$, 2017 to December $31^{st}$, 2017} 
\else
{\underline{\bf Weekend Plans - October $29^{th}$, 2017 to December $31^{st}$, 2017}}\\ 
\fi
\begin{itemize}
\tiny \item \tiny \underline{Weekend of October $28^{th}$:} Visit Seattle. {\it Details:}
\item \tiny \underline{\bf Weekend of November $4^{th}$:} Stay in Washington, D.C. {\it Details:}
\item \tiny \underline{Weekend of November $11^{th}$:} Visit Denver. {\it Details:} Talk with Rayna
\item \tiny \underline{Weekend of November $17^{th}$:} Visit Denver/ L.A. {\it Details:} 
\item \tiny \underline{Weekend of November $24^{th}$:} Visit Champaign. {\it Details:} Talk with Brionna? Meet with friends from high school? 
\item \tiny \underline{Weekend of December $1^{st}$:} Holiday party. \textit{Details:} give RSVP. 1600 Duke Street in Old Town Alexandria, parking is free in the garage on the right of the restaurant.
\item \tiny \underline{Weekend of December $8^{th}$:} Go to San Francisco. \textit{Details:} stay at Atul's place. 

\end{itemize}

\ifdefined\POSTER
\end{block}
\end{column}
\fi





\ifdefined\POSTER
\begin{block}{Weekend Plans - October $29^{st}$, 2017 to December $31^{st}$, 2017} 
\else
{\underline{\bf Weekend Plans - October $29^{th}$, 2017 to December $31^{st}$, 2017}}\\ 

\begin{itemize}
\item \tiny 
\item \tiny 

\end{itemize}

\ifdefined\POSTER
\end{block}
\end{column}
\fi
\begin{columns}  %-- Page 2: Column 1 ---------------------------------------------------

\begin{column}{0.10\linewidth}

\begin{block}{Projects}
%Project superspace: mental health

% Project superspace: work 

% Project: Fundamental knowledge. 

% Project space: applications 

\underline{Computational Reqs} 
\underline{\textbf{Deadline:} January $29^{th}$, 2017} 
\begin{enumerate}
\pitem 
\pitem 
\end{enumerate}

\underline{Tomography Code} 
\underline{\textbf{Deadline:} February $4^{th}$, 2017} 
\begin{enumerate}
\pitem 
\pitem 
\end{enumerate}

\underline{Networking Infrastructure} 
\underline{\textbf{Deadline:} September $22^{nd}$, 2017} 
\begin{enumerate}
\pitem 
\pitem 
\end{enumerate}

\underline{Publication} 
\underline{\textbf{Deadline:} September $22^{nd}$, 2017} 
\begin{enumerate}
\pitem 
\pitem 
\end{enumerate}

% Project space: programming and systems

% -- Project: OpenMP 
\underline{OMP proposal} 
\underline{\textbf{Deadline:} September $22^{nd}$, 2017} 
\begin{enumerate}
\pitem 
\pitem 
\end{enumerate} 

% -- Project: CkLoopHyb paper 
\underline{CkLoopHyb paper}
\underline{\textbf{Deadline:} September $22^{nd}$, 2017}
\begin{enumerate}
\pitem Add template to git repository.
\pitem Add writeup for dot product results on Cori.
\pitem Get PIC results with Charm++-everywhere for BW.
\pitem Need a new application. 

\ptask Update the paper technique to be consistent with experiments.
 
\ptask Work: update paper .tex file with dot prod. \te{30 minutes}.

\ptask Add PAPI cache misses for problem statement.
\ptask Fix diagrams.
\ptask Figure out what to put at the top block of first quadrant.
\ptask Add content in extended paper.
\ptask Add code for PIC in bottom left quadrant.
\ptask Add projections results.
\ptask Add to related work.
\ptask Get PIC results with Charm++-everywhere, Charm++ + CkLoop for Cori.
\ptask Get results for Charm++ + CkLoop for missing data points.
\ptask Show results for dot product using Charm++ + OpenMP, and for
dot product with Charm++ + CkLoop.
%\doneTask{ Show code with Charm++ + OpenMP.}
\pitem Merge with git repository.
\pitem Send message to meet for results.
\pitem Work: message to Kathryn about poster.
\end{enumerate}

\underline{Schedule} \\ 
\begin{enumerate}
\pitem 
\end{enumerate} 
\end{block} 

%Project: interviewing 
\underline{Interviewing} 
\underline{\textbf{Deadline:}} 
\begin{enumerate}
\pitem 
\pitem 
\end{enumerate} 


%Project: extra-curricular

\begin{block}{Year Plan}
\begin{itemize}
\tiny \item \tiny January: Work: interview, application. , Mgmt:Spaces: get dl , Mgmt:Spaces: get cc, Comm: 
\item \tiny February: Work: proposal, Work: implementation, Mgmt:Spaces: 
\item \tiny March: Work: paper for IWOMP, Work: job talk prep.
\item \tiny April: Work: paper for IWOMP, Work: implementation  
\item \tiny May: Work: do paper, Work: Comm: 
\item \tiny June: Work: work on implementation with UDS 
\item \tiny July: Work: work on implementation with UDS Comm:  
\item \tiny August: Work: paper for IPDPS, 
\item \tiny September: Work: paper for IPDPS 
\item \tiny October: Work: paper for IPDPS  
\item \tiny November: Work: SC stuff, 
\item \tiny December: 
\end{itemize} 
\end{block}

\begin{block}{Month Plan}
\underline{Week of January $31^{st}$, 2018}
\begin{itemize}
\tiny \item \tiny Work: 
\item \tiny Mgmt:Spaces: 
\item \tiny Comm: 
\end{itemize}

\underline{Week of February $4^{th}$, 2018}
\begin{itemize}
\tiny \item \tiny Work: send in cover letter + Work: finish application.  
\item \tiny Mgmt:Spaces: 
\item \tiny Comm: 
\end{itemize}

\underline{Week of February $9^{th}$, 2018}
\begin{itemize}
\tiny \item \tiny Work: 
\item \tiny
\end{itemize}

\underline{Week of February $16^{th}$, 2018}
\begin{itemize}
\tiny \item \tiny 
\item \tiny
\end{itemize}
\end{block}

\end{column}
  \begin{column}{0.10\linewidth}
    %{\textbf{\underline{Week Aspects(new name)}})
      %--- Page 2: Block 1-1 
    \begin{block}{Routines}
      { \tiny \underline{\bf Routines:} Morning: bfast, exercise/brush,
        floss, shower (hair, eyes, ears, underarms, feet), meds, belt,
        comb hair / dishes, clean kitchen floor. |  Night: running/ put
        away dishes, clean kitchen floor / brush teeth, charge phone,
        clothes for tomorrow, contacts off.}\\
      {\tiny \underline{\bf Sunday Routines:} Routines:
        Experiences,week plan.}\\ 
      {\tiny \underline{\bf Weekday Routines:}}\\
      %TODO: check if weekday routines overlaps into daily routines.
    \end{block} 
      %--- Page 2: Block 1-3
    \begin{block}{Local Happiness}
      % howto:Recognize emotions / recognize (precisely) what you're
      % worried about -> methods for eliminating worry. 
      % clean out old worries, put them in pastWorries doc.  
      % remember to define precisely 
      % order from top-to bottom
      \begin{itemize} 
        \tiny \item \tiny -
      \item \tiny Worrying about gal: think about talking to others.
      \end{itemize} 
    \end{block}
    %--- Page 2: Block 1-4 
    \begin{block}{AngersAndAnxieties}
      % howto:Recognize emotions / recognize (precisely) what you're worried about -> methods for eliminating worry. 
      % clean out old worries, put them in pastWorries doc.  
      % remember to define precisely 
      % order from top-to bottom
      \begin{itemize}
        \item \tiny Issue with USC : $\rightarrow$ things get better. 
        \tiny \item \tiny Anger about UP $\rightarrow$ think about the positive
        perspective, and the original
      \item \tiny Anger about Mr. Kapoor $\rightarrow$  leave it
      \item \tiny Anger about a b  $\rightarrow$ ...
      \end{itemize}
    \end{block}
      %-- Block 1-5
      \begin{block}{Life notes}
        \begin{itemize}
          \tiny \item \tiny Social Intelligence: 
        \end{itemize}
      \end{block}
      % howto:
      \begin{block}
        {\tiny {\bf Week lessons:}}
        \begin{enumerate}
        \item \tiny tm tips. 
        \item \tiny Coding problem:
        \item \tiny Chess tips: 
        \end{enumerate}
            {{\tiny {\tiny \bf  News:}} {\tiny  M:  | S: 
                | E: Fallon:  Kimmel:  Colbert: SNL:}}
            {{\tiny {\tiny \bf  Weather:}} {\tiny M: 1100 T: 1100 W: 41/34 .1r 
                 R: 51/46 .60r F: 62/36 .7r a Sa: 42/20 .10r Su: 31/17 }}
           % \input{weather} 
      \end{block}
  \end{column}
  %-- Column 2 ---------------------------------------------
  \begin{column}{0.6\linewidth}
    \begin{block}{Week Summary}
      {\underline {\bf Week Plan:} 
        Work:rel: e-mail to LBL + Work:rel: meet with Crago, Work:rel: update LLNL jobs, Mgmt:Spaces: book flights, 
        Work: send e-mail to Prof. Gropp, Work: update job talk
      }\\

      {\underline{\bf Weekend Plan:} Go to SF } \\
  
    \end{block}
    \begin{block}{Running ToDo} % find a better name 
      \begin{enumerate}  
      \item \tiny \textbf{Curr} $\rightarrow$  
      \item \tiny worklife: update information on Work/rel with ref. letter information.  
        
      \item \tiny Work: add to job talk. 
      \item \tiny Work: send e-mail for accomplishments. 

      \item \tiny Work:rel: apply to other LLNL position. \te{1 hour} \dl{} 

      \item \tiny Work:rel: figure out OPenMP f2f at ISI = Work:rel:
        get session at ISI +  Work:rel: send Bronis an e-mail about
        getting a session at ISI.

        Hi Bronis and Michael,
        
        @Michael: Bronis and I spoke semi-casually in February about me hosting an OpenMP Face to Face at USC/ISI in Marina del Rey, California. 
        
        I’ve thought about this idea recently. I’d like to host or
        help host a meeting at USC/ISI at Marina del Rey,
        California. The TWiki for OpenMP shows a tentative location of
        Spring 2019 for a possibility of doing the event in Toronto. I
        think that the Spring 2019 will be best because students will
        be away and ISI is less busy around that time. 
        
        I looked into conference room availability for rooms through
        my calendar and with help with a receptionist that reserves
        these rooms. The receptionist and I found a schedule of room
        reservations that can work with events that have reservation
        for the rooms, that can get nice views of the ocean and that
        wouldn’t require moving between rooms much. We went far enough
        to put holds on two rooms during the week of May 21,
        2019. This entire set of holds can be shifted by a couple of
        weeks before and after as the events are recurring and the
        ones that aren’t should require small changes to the
        schedule. The set of holds could also potentially be shifted
        to Winter 2020. 

        Please let me know if this is of interest to you. 
        
        Vivek


      \item \tiny Work:rel(elb): follow-up email to LBL =
        Work:rel(elb): send e-mail with questions to LBL +
        Work:rel(elb): talk with Kaushik D. about positions.  +
        Work:rel(elb): talk with Steve Crago. 
        
      \item \tiny Work:rel: send e-mail to Prof. Gropp about ATPESC2018. \te{10 minutes} 

      \item \tiny Mgmt:Spaces: book flight to SF. 

      \item \tiny Mgmt:Spaces: get car serviced. 
      \item \tiny Mgmt:Spaces: get new meds. 
      \item \tiny Mgmt:wp: add pics on Instagram. 

      \item \tiny Work: prep for meeting.

      \item \tiny Work: update the charm++ stuff. 
      \item \tiny Work: read papers on Charm++ + OpenMP . 
      \item \tiny Work: do prep for OpenMP discussion.

      \item \tiny Work:admin: get the reimbursement for car’s warranty.  
          
      \item \tiny Mgmt:Spaces: Renew Vehicle Registration. 
      \item \tiny Mgmt:Spaces: get vehicle sticker for car. 
      \item \tiny Mgmt:Spaces: apply for cc. 

      \item \tiny Comm:rel: follow-up to Rathi? 
      \item \tiny Comm:rel: send dilmil message to Anushya = Hi, how
        are you doing? What's the picture 
      \item \tiny Comm: message to Aditi. 

      \item \tiny Comm: message to Renata.
      \item \tiny Comm:rel: email to Bhakti. 

      \item \tiny EI: get the counselors taken care of in D.C. area. 
       
      \item \tiny worklife: make projects list. 
      \item \tiny Mgmt:wp: add people to LinkedIn =  Mgmt:wp: add Andy
        Schmidt on LinkedIn. +  Mgmt:wp: add Mike Kumbera to LinkedIn +
        Mgmt:wp: add Marty. 

      \item \tiny Mgmt:Spaces: get contact lense cases. 
  
      \item \tiny Work:admin: submit receipts for Bagel. 

        \tiny \item[] \tiny \textbf{Curr} $\rightarrow$
    
      \item \tiny Work: finish proposal slides. 
      \item \tiny Work:rel: do cover letter for BNL + Mgmt:Spaces: talk with Martin Kong.
        
      \item \tiny Comm: photo upload. 
        
      \item \tiny Work: send in application to PNNL.
        
      \item \tiny Mgmt:wp: add profile.
      \item \tiny Mgmt:wp: add about me. 
        
      \item \tiny Mgmt:wp: add profile. 
\item \tiny Work:rel: email to Renata. \te{10 minutes} 
\item \tiny Comm: message to Sateja. 
  Hey, I followed you on LinkedIn. I think your work is really good. 
  Let me know if you want to grab coffee sometime in the city. 
  
\item \tiny Comm:rel: talk to Shweta.
\item \tiny Comm: talk with Toni. 
  
\item \tiny \textbf{ <-- End Curr }
\item \tiny Mgmt:wp: add photos from college. 
\item \tiny Comm: message to Rishi and Mike about meeting. 
\item \tiny worklife: read social intelligence. \te{2 hour} 
\item \tiny Mgmt:Spaces: get face scrub. 
\item \tiny worklife: practice posing in a picture.  
\item \tiny Work: IM system for LLNL.  
      \end{enumerate}
    \end{block} 


\begin{block}{DayPlans} 

  Sunday:   
  | Monday: 
  | Tuesday:  
  | Wednesday: 
  | Thursday: 
| Friday: 
| Saturday:  
\end{block}

\begin{block}{Alg for Mgmt}
Alg for Mgmt:Alg for Comm   L0:  L1:  L2:  L3:  Maps L4: L5: -> L0
TODO:  and prioritize . Use colors for levels Howto:  
\end{block} 

\begin{block}{Meeting Information}
BlueJeans meeting ID: 8562450706.
Webex MeetingID: 805639779  
\end{block} 

\begin{block}{Situations} 
\begin{enumerate}
\item Meet Steve: 
\end{enumerate} 
\end{block}

\begin{block}{Rel}
\underline{Rel-chat-short}: Bhakti J., Rath S, Vinita G. , Aishwarya , Madhura, Anushya, Aditi 

\underline{Rel-chat-like-toinitiate}: Sateja P. , Anuja D., Shilpa G., Sneha from NJ. 

\underline{Rel-chat}:  cat1:  Toni,, S Van., Bhakti, Shalaka/Rucha, Sateja P, Anuja
D. ,  Divya, cat2: sonal mukhi, Mamta, sapana/india, Avani, cat 3:
Shilpa Ghate, Renuka, Renata, 
\end{block}
  
  % howto: the below is a routine based on the job I'm doing and the
  % circumstances I'm in. Note that this is different from routines
  % above, which is true for a long-term period of over 10 years. 
  \begin{block}{Weekly Meetings}
    \begin{itemize}
      \tiny \item \tiny IWOMP affinity meeting Thursday 7 AM PDT / 9 AM
      CDT call in: 805-639-779 pswd: places. \url{https://llnl.webex.com/llnl/j.php?MTID=m33950b76befb72c0cbc31ea2e3be720c}
    \item \tiny DEG group meeting.          \end{itemize}
  \end{block} 

      \begin{block}{Week Daily Schedule}
        % howto: arrange items from running todo into the below
        % sheet management document. 
        %NOTE: we don't use the table format because of fittting
        \begin{columns}
          \begin{column}{0.14\textwidth}{\small \underline{\bf Mon}}
            {\tiny \bf {\tiny weather:} } {\tiny 11/1 s} \\ 
            {\tiny \bf {\tiny todo}}\\ 
            \begin{itemize}
              \tiny \item \tiny Work: do experiments with multiple nodes. 
            \item \tiny Work: get experiments using real data. 
          \item \tiny Mgmt:Spaces: get the Driver's License.  
      \item \tiny Mgmt:Spaces: cancel order from LinkedIn premium +
        Mgmt:Spaces:cancel order of Youtube Red.  
            \end{itemize}
                {\small  \bf schedule}\\
                \begin{enumerate} 
                  \tiny \item \tiny 8-9AM: Regular Routines 
                \end{enumerate}
          \end{column}

          \begin{column}{0.14\textwidth}{\small \underline{\bf Tues}}
            {\bf {\tiny  weather:} } {\tiny 3/1 r} \\ 
            {\bf {\tiny todo}}\\ 
            \begin{itemize}
              \tiny \item \tiny Work: do write-up 
            \end{itemize} 
                {{\bf {\tiny  schedule}}}
                \begin{enumerate} 
                  \tiny \item \tiny 8-9AM: Regular Routines 
                \end{enumerate} 
          \end{column}
          \begin{column}{0.14\textwidth}{\small \underline{\bf Wed}}
            {\tiny \bf weather: } {\tiny 3/1 r} \\ 
            {\tiny {\bf todo}}\\
            \begin{itemize}
              \tiny \item \tiny Work: send email to Prof. Gropp. 
            \item \tiny 
            \item \tiny Comm: message to Anita. 
            \end{itemize}
                {\tiny \bf schedule}\\
                \begin{enumerate} 
                  \tiny \item \tiny 8-9AM: Regular Routines 
                \end{enumerate} 
          \end{column}

          \begin{column}{0.14\textwidth}{\small \underline{\bf Thurs}}
            {\tiny \bf weather: } {\tiny 1/-1 r }\\ 
            {\tiny \bf todo} \\ 
            \begin{itemize}
              \tiny \item \tiny Add in schedule 
            \item \tiny Work:admin: get slide updated.  
              \item \tiny Work: admin: send cc statement. 

            \end{itemize} 
                {\tiny {\bf schedule}} \\
                \begin{enumerate} 
                  \tiny \item \tiny 8-9AM: Regular Routines 
                \end{enumerate}
          \end{column} 
          
          \begin{column}{0.14\textwidth}{\small \underline{\bf Fri}}
            {\tiny \bf weather: } {\tiny 3/1 r} \\ 
            {\tiny \bf todo} \\ 
            \begin{itemize} 
            \item \tiny Work:rel: cover letter for LLNL.
            \item \tiny Work: e-mail to JP and Steve about acheivements.
            \item \tiny Work: send e-mail. 
            \item \tiny Mgmt:Spaces: give back Internet box. 
            \item \tiny Mgmt:Spaces: get the Driver's License.  
      \item \tiny Mgmt:Spaces: cancel order from LinkedIn premium +
        Mgmt:Spaces:cancel order of Youtube Red. 
            \item \tiny Comm: reply on Coffee Meets Bagel.
            \item \tiny Comm: reply to Aishwarya
            \item \tiny Comm:rel: talk with Vinita. 
                
            \end{itemize} 
                {\tiny \bf schedule} \\
                \begin{enumerate} 
                  \tiny \item \tiny 8-9AM: Regular Routines 
                \end{enumerate}
          \end{column}

          \begin{column}{0.15\textwidth}{\small \underline{\bf Sat}}
            {\tiny \bf weather: } {\tiny 11/1 .2r} \\ 
            { \tiny \bf todo} \\ 
            \begin{itemize}
              \tiny \item \tiny Add in schedule
            \item \tiny 
            \end{itemize} 
                {\tiny \bf schedule} \\
                \begin{enumerate} 
                  \tiny \item \tiny 8-9AM: Regular Routines 
                \end{enumerate}
          \end{column}
         
          \begin{column}{0.15\textwidth}{\small \underline{\bf Sun}}
            {\tiny {\bf weather:} } {\tiny 11/2 r} \\ 
            {\tiny {\bf todo}}\\
            \begin{itemize}
              \tiny \item \tiny Add in schedule
            \end{itemize} 
                {\tiny \bf schedule}\\
                \begin{enumerate} 
                  \tiny \item \tiny 8-9AM: Regular Routines 
                \end{enumerate}
          \end{column}
        \end{columns}
      \end{block}
\end{column}
    
    % ------ Page 2: Column 3
    \begin{column}{0.20\linewidth}
      % ------ Block 2.3.1 
      \begin{block}{Food Plan} 
        \begin{itemize}
          \tiny \item \tiny Google Express: DHDQQJQDRFTXDM95B
        \end{itemize}
      \end{block} 
      \begin{block}{Clothes plan} 
        \begin{itemize}
          \tiny \item \tiny Monday: 
        \item \tiny Tuesday
        \item \tiny Wednesday
        \item \tiny Thursday
        \item \tiny Friday
        \item \tiny Saturday
        \end{itemize} 
      \end{block} 
      
      %-- Block 3-3 
      \begin{block}{Situations}
        % Summary: the below are the situations that define one
        % another.
        % Howto: Put post notes of each situation from list of previous
        % week. Put high importance situations in situationslist. 
        % Put list of upcoming situations on Sunday morning with Pre. 
        \begin{itemize}
          \tiny \item \tiny 
        \item \tiny 
        \end{itemize}
      \end{block}
      % contingincies: 
      % Summary:
    \end{column}
\end{columns}
