%Note:  consider weekly schedule template

%TODO : figure out how to schedule urgent and important tasks

{\huge{\underline{\textbf{Week of March 28th}}}} \\

\textbf{Summary:} This is the weekly planning document. To create
this, first look at weekly routines and make sure they are here. Then,
look at the yearWeekPlan doc, along with project plan doc, and iPhone
todo list, and divide tasks across days of the week. Then, put this
into the schedule.

After this is done, these items should be checked in the work and
work+life calendar, and verified through email.
Then, they should be put in the work + life
calendars. \\

\textbf{Clothing Prep: } \\
Note: think about making dress code for situations
\begin{enumerate}
\item \textbf{Monday}: standard tshirt + jeans
\item \textbf{Tuesday}: standard red polo shirt + jeans
\item \textbf{Wednesday}: simple  blue shirt + jeans
\item \textbf{Thursday}: Regular red + jeans
\item \textbf{Friday}: Full blue shirt , jeans
\item \textbf{Saturday}: formal wear
\item \textbf{Sunday}: lounging around wear
\end{enumerate}

\textbf{Worries to watch for} \\
\begin{enumerate}
\item seeing another person
\item ex-
\item New Years text
\item email to Vk
\item what will bronis say
\item stress about worklife
\item stress about Divya
\item stress about Sneha
\end{enumerate}

\textbf{Current habits: monthly}\\
\begin{itemize}
%\item dinner etiquette
%\item make sure eye contact not shifty
%\item avoid facebook / social media urge
%\item no cell phone
\item avoid bodily noises
%\item walk in straight line without feet scrubbing floor
%\item get reg routines down
%\item back straight.
%\item lips relaxed.
%\item avoid butt-dials.
\end{itemize}

\textbf{Practice Points}\\
\begin{itemize}
\item \textit{\textbf{Note:}} figure out how to organize and do this
\item go through goals from top down to get schedule
\item prioritization and time management
\item comparisons to general people (students)
\item comparisons to others
\end{itemize}

\textbf{Spaces Org: do this every Saturday }
\begin{itemize}
\item code folder
\item organization folder
\item email folder
\item iPhone items
\item desktop
\item backpack
\item clean up home directory
\item clean up downloads directory
\end{itemize}

\underline{\textbf{situations}} \\
\begin{enumerate}


\item Meet with Prof Gropp later: Pre-:  Post-:

\item Talk to Bronis and Todd about work stuff:  Pre-:  Post-:

\item Meet with Rishi and Chris: Pre-:  Post-:  check messages before-hand, good
to connect French toast(though make it more emotionally inspiring) ,
don't be late , when there is a change, see to assess situation on the
fly. Be sure to explain what you do carefully. Send a message to
follow-up right after.

\item Talk with Sneha: Pre- :Hang out, Plan time and meeting ;  Post-:
check with others what they think about what you should say to
 someone.

 \item Flight to SF:   Pre- :  get rental,  get boarding passes, charge
phone.  Post - : check for flight timings, see if there are
dependences for the travel, don't go anywhere away from terminal even
if there is a delay, get there earlier

\item Meet with Amanda:  Pre-: Check timing and location,
Post-: check for changes before the meeting,  logistics for airport,
be truthful with what's happening, tell things early and be a bit more
assertive.

\item Seibel Chair :  Pre-: meet with Prof Gropp, and talk to him ,
Post-: Know what to say before to Prof Gropp , good to plan pics,

\end{enumerate}

\underline{\textbf{\textit{Monday}}}\\
\underline{\textbf{todo}}\\
\begin{enumerate}
\item Finish writing the essay \timeEst{1 hour per day}
\item make quick notes on conversation skills \timeEst{10 mins}
\end{enumerate}

\underline{\textbf{schedule}}\\
\begin{itemize}
\regItem{7:00AM - 8:00AM: running}
\regItem{9:00AM - 10:00AM : regular routines for morning}
\regItem{5:00PM - 6:00PM : send out email to everyone on notes for meeting}
\regItem{9:00PM - 10:00PM : regular routines for night}
\end{itemize}

\underline{\textbf{\textit{Tuesday}}}\\
\underline{\textbf{todo}}\\
\begin{enumerate}
\item write up cost function, write up engineering design \priority{I}
\item write code for Amanda
\doneTask {check for VPN account access \timeEst{10 mins}}
\end{enumerate}

\textbf{Tuesday facebook post: } The actual innovation has already been done in Computer Science.
This doesn't solve an imminent problem in society. This generates controversy.
Controversy brings up attention. Attention makes people interested in trying it out.
And generating controversy is exactly how tech startups can stand tall in the face of tech giants.

This doesn't solve an imminent problem in society.
This generates controversy. And in this day, generating controversy is exactly how a small group of people can stand tall
in front of large corporations.

\underline{\textbf{schedule}}\\
\begin{itemize}
\regItem{7:00AM - 8:00AM: weights}
\regItem {8:00AM - 9:00AM: regular routines for morning}
\regItem {9:00AM - 10:00AM: meeting}
\regItem {9:30-10PM: fb social, linkedIn social}
\regItem {10:00PM - 10:30PM: regular routines for night}
\end{itemize}

\underline{\textbf{\textit{Wednesday}}}\\
\underline{\textbf{todo}}\\
\begin{enumerate}

\item Talk to Amanda (send code, send doc, work on code): (get struct working) \timeEst{10 mins} get \textit{vSchedLib\_demo} working and ensure low
overheads.

\item get infrastructure working with data collection, etc., and
\texttt{miniPthreadsCode.C}, systems issues, add pthreads \timeEst{1 hour}.

\item get a working technique that gives positive results (for
load-balanced codes). OR get a working technique that gives positive
results for load imbalanced codes. (get Barnes-Hut
working and try technique on that): (do perf. modeling) \priority{UI}.
\item talk to Bronis:

\item Rel: Email to Divya, email to Vk, call Sneha.

\item worklife: situations analysis, add situations. note to make sheet of excercises.

\item write down elements of style 1 chapter , read emotional
intelligence, get chapter's notes down \timeEst{10 mins}.

\item spaces clean (wallet, cellphone, backpack), desktop clean

\item excercise and yoga. (note to make sheet of excercises)

\end{enumerate}

\underline{\textbf{schedule}}\\
\begin{itemize}
\regItem{7:00AM - 8:00AM: running}
\regItem{8:00AM - 9:00AM: regular routines for morning}

\item 5PM - 6PM : excercise

\item 6:00PM - 6:30PM :

\item 6:30PM -7:00PM : email to Divya
\regItem{10:00PM - 10:30PM: regular routines for night}
\end{itemize}

\underline{\textbf{\textit{Thursday}}}\\
\underline{\textbf{todo}}\\
\begin{enumerate}
\item add dot Prod and other operations \timeEst{10 mins}  \priority{UI}

\item add PAPI counters \timeEst{1 hour}
\item get help on sched stuff \timeEst{20 mins}
\item software dev. \timeEst{10 mins}
\item integrate with \texttt{basicPthreads-handTuned.C}.

\item prep for tomorrow's meeting with Prof Gropp \timeEst{10 mins}
\item do related work ,  software spec  \timeEst{10 mins} \priority{U}

\item do a little lattice-boltzman prep \timeEst {10 mins} \priority{I}

\item write email to Vk \timeEst{30 mins} \priority{U}
\item write email to Divya \timeEst{1 hour} \priority{U}

\item spaces: order additional iPhone chargers \timeEst{10
mins} \priority{U}

\end{enumerate}


\underline{\textbf{schedule}}\\
\begin{itemize}
\regItem{7:00AM - 8:00AM: weights}
\regItem{8:00AM - 9:00AM: regular routines for morning}
\regItem {11AM - 11:30AM : work admin stuff}

\item 11AM - 12PM :
\item 1PM - 4PM: Amanda's code lookover
\item  11AM - 12PM : think about solution to problem

\item 11PM - 12PM: packing, checkin to flight
\regItem{10:00PM - 11:00PM: regular routines for night}
\end{itemize}

\underline{\textbf{\textit{Friday}}}\\
\underline{\textbf{todo}}\\
\begin{enumerate}
\item write down elements of style 1 chapter \timeEst{10 mins}
\item read emotional intelligence, get chapter's notes down \timeEst{10 mins}
\item talk with Amanda

\item look at Amanda's code briefly, fix the icrev part.  \timeEst{10 mins}  \priority{I}
\item send Amanda the code fixed, retrieve the new code from git. 
\item Fix additional parts of profiling, data output. 
\item send Amanda code and paper outline \timeEst{20 mins}

\item prep for meeting, figure out what to say to work done afterwards \timeEst{2 hours} \priority{UI}

\item write up to Vk \timeEst{2 hours}.

\item situations analysis \timeEst{20 mins}

\item do code implementation for meeting \timeEst{20 mins}
\item add in calendar event \timeEst{10 mins}
\item do code cleanup \timeEst{30 mins}
\end{enumerate}

\underline{\textbf{schedule}}\\
\begin{itemize}
\regItem{7:00AM - 8:00AM: running}
\regRoutineItem {8:00AM - 9:00AM: regular routines for morning}
\regItem{10AM - 11AM : HPC group meeting}
\item 6PM - 7PM : talk to Sneha
\regItem{9PM - 9:30PM :  situations analysis}
\regItem{9:30PM - 10PM :  lookup clothes for next week}
\regRoutineItem{10:00PM - 11:00PM: regular routines for night}
\end{itemize}

\underline{\textbf{\textit{Saturday}}}\\
\underline{\textbf{todo}}\\
\begin{enumerate}
\item read Emotional Intelligence \timeEst{10 mins}
\item fix Amanda's code \timEst{2hrs}
\item write up to Vk \timeEst{2 hours}
\item excercise
\item do re-imbursements
\item summarize the style guide, last part \timeEst{10 mins}

\item do analysis of win friends and influence people 1 chapter \timeEst{10 mins}
\item worklife cleanup , talk to Atul, situations, situations  analysis

 \item week clothes prep, food prep , situations prep
\item habits setup, stress relief (apply tactics to each stress)  \timeEst{10 mins}

\end{enumerate}

\underline{\textbf{schedule}}\\
\begin{itemize}
\regItem{7:00AM - 8:00AM: yoga sculpt}
\regRoutineItem {8:30AM - 9:30AM: regular routines for morning}
\regItem{9:30AM - 10:30AM: Spaces maintenance}
\situationItem 12PM - 1PM:
\item 6PM - 8:30PM:
\item 8:30PM - 9:30PM : dinner
\item 9:30PM - 10:30PM :
\regItem{10:00PM - 11:00PM: regular routines for night}
\end{itemize}

\underline{\textbf{\textit{Sunday}}}\\
\underline{\textbf{todo}}\\
\begin{enumerate}
\item summarize the style guide \timeEst{10 mins}
\item do analysis of win friends and influence people 2 chapters \timeEst{10 mins}
\end{enumerate}

\underline{\textbf{schedule}}\\
\begin{itemize}
\regItem{7:00AM - 8:00AM: weights + running + meditation }
\regRoutineItem {8:00AM - 9:00AM: regular routines for morning}
\item
\item 7-8PM: plan out refine yearweeksPlan for the next month
\regItem{8-9PM:  plan out week in week Plan curr}
\regRoutineItem{10:00PM - 11:00PM: regular routines for night}
\end{itemize}

\newpage

