\begin{columns}
    %-- Page 2: Column 1 --------------------------------------------------- 
    \begin{column}{0.25\linewidth}
      %{\textbf{\underline{Week Aspects(new name)}}}
      %TODO: check where this should go. -done  
      %--- Page 2: Block 1-1 
      \begin{block}{Routines}
        { \tiny \underline{\bf Routines:} Morning: bfast, exercise/brush,
          floss, shower (hair, eyes, ears, underarms, feet), meds, belt,
          comb hair / dishes, clean kitchen floor. |  Night: running/ put
          away dishes, clean kitchen floor / brush teeth, charge phone,
          clothes for tomorrow, contacts off.}\\
        {\tiny \underline{\bf Sunday Routines:} Routines: Experiences,week plan.}\\ 
        {\tiny \underline{\bf Weekday Routines:}}\\
        %TODO: check if weekday routines overlaps into daily routines.
      \end{block} 
      %--- Page 2: Block 1-3
      \begin{block}{Local Happiness}
        % howto:Recognize emotions / recognize (precisely) what you're
        % worried about -> methods for eliminating worry. 
        % clean out old worries, put them in pastWorries doc.  
        % remember to define precisely 
        % order from top-to bottom
        \begin{itemize} 
          \tiny \item \tiny Work: worrying about interviewing: just focus on the work. 
        \item \tiny Worrying about gal: think about talking to others. 
        \end{itemize}
      \end{block} 
      %--- Page 2: Block 1-4 
      \begin{block}{AngersAndAnxieties}
        % howto:Recognize emotions / recognize (precisely) what you're worried about -> methods for eliminating worry. 
        % clean out old worries, put them in pastWorries doc.  
        % remember to define precisely 
        % order from top-to bottom
        \begin{itemize}
          \tiny \item \tiny Anger about UP -> think about the positive
          perspective, and the original
        \item \tiny Anger about Mr. Kapoor ->  leave it
        \item \tiny Anger about a b  -> ...
        \item \tiny Issue with USC : --> things get better. 
        \end{itemize}
      \end{block}
      %-- Block 1-5
      \begin{block}{Life notes}
        \begin{itemize}
          \tiny \item \tiny Social Intelligence: 
        \end{itemize}
      \end{block}
      % howto:

      \begin{block}
      
      {\underline{\bf Day trip packing list:} charger for iPhone,
        charger for laptop, car keys, underwear, black socks, shoes,
        meds, halls meds, greyhound, boarding pass, flight pass, directions to
        venue?} \\ 
      {\tiny {\bf Week lessons:}} \\ 
      \begin{enumerate}
        \tiny \item \tiny Win Friends/ Influence People – no one
        likes to take direct orders.
      \item \tiny Go through 7 habits.
      \item \tiny Coding problem: 
      \item \tiny Chess tips: 
      \item \tiny tm tips.
      \end{enumerate}
          {{\tiny {\bf News:}} M:  | S:  Trump's wiretapping  | E:
            Fallon:   Kimmel:  Colbert: SNL:
            w: washdc: 
            {su: {48/35 s a}}  
            {m:{57/45 s a}} 
            {t: {62/40 .2r a}} 
            {w: {44/24 s a}} 
            {r: {47/32 s a}} 
            {f :{62/50 s a} }
            {sa: {71/48 s a}}} 
    \end{block}
    
  \end{column}     
  %-- Column 2 ---------------------------------------------
 
  \begin{column}{0.5\linewidth}
    \begin{block}{Week Summary} 
      {\underline {\bf Week Plan} Work: do runs with input data, Work:
        finish cworks, Mgmt:Spaces: take care of car, Mgmt:Spaces:
        decide on EWR to DCA trip, Mgmt:webpresence: fb like to Mamta
        + Comm:message to Shikha.}

      {\underline{\bf Week Plan}
        Work: do cworks work, Work: finish getting data set to work,
        Work: discuss transformations from CUDA to OpenMP, Work: talk
        to Kristina, Mgmt:Spaces: take care of Virginia parking ticket, Comm:
        message to Kavita to send pictures + Comm: message to Archana
        + Comm: message to girl from Philadelphia, Comm: message to
        Rishi. }\\ 

      {\underline{\bf Weekend Plan:} Go to NYC, meet Ranjit, see BNL.}\\

    \end{block}


      \begin{block}{Running ToDo} % find a better name 
        \begin{enumerate}
          \doneTask{ Work:admin: ask for vacation.} \te{10 minutes}\dl{TuesNight} \pr{high}
          \doneTask{Work: message to Prof. Gropp about plan.} \te{30 minutes} \dl{tonight} \pr{high}. 
          \doneTask{Work: admin: finish survey.} 

        \item \tiny Work:comm: figure out whether to add Anshu \te{1 hour}.
        \item \tiny \textbf{Curr} $\rightarrow$ 

Work: get to work on new data sets + Work: do run for problem size +
Work: do transformations from CUDA to OpenMP 4.5 + Work: discuss code
structure. TimeEst:1 hour. 
4.Work: finish report for review.


        \item \tiny Work: do transformations for CUDA + Work: try to
          get to work on new data sets + Work: look up parallelization
          of algorithms + Work: show errors  graph TimeEst \te{1 hour}
          Work: do run for problem size. \te{1 hour} 

        \item \tiny Work: do Cworks items = Get application with
          ckloop that’s load imbalanced Modify ckloop to ckloophybrid, where
          static section is not stolen by cores, i.e., cores do not steal
          work during execution of statically scheduled loop iterations +
          Consider additions: weighted static, locality-optimized. Bind
          cores, i.e., drone mode. Integrate with git.  \te{1 hour}
          \dl{tonight} \pr{high}.
 
        \item \tiny Work: send message to Micheal K about user-defined
          schedule. \te{1 hour}

        \item \tiny Mgmt:Spaces: empty trash of photos from Photo booth \te{10 minutes}

        \item \tiny Mgmt:Spaces: move pictures from iPhone into folder. \te{10 minutes}. 

        \item \tiny Mgmt:Spaces: fix key set. \te{10 minutes}. 

        \item \tiny Mgmt:Spaces: get citi bank account
          Mgmt:Spaces: get refund from AA  + Mgmt:Spaces: get the
          bumper bully +  Mgmt:Spaces: get replacement for Chase card. \te{1 hour}.

        \item \tiny Mgmt:Spaces: haircut \te{U} \dl{Wednesday} 

        \item \tiny Work:admin(spaceSave): Goto MacStore and see if the following can be uninstalled and then
          re-installed if needed = Work:admin(spaceSave):
          a. GarageBand  + WOrk:admin(spaceSave):  b. iMovie +
          Work:admin(spaceSave): c. strip down Xcode +
          Work:admin(spaceSave): d. iPhoto 
          + WOrk:admin(spaceSave): 2. Check about MS office to see whether Microsoft Messenger and
          communicator can be deleted safely 
          + WOrk: admin(spaceSave): 3. Check that Omnigraffle can be
          deleted + WOrk:admin(spaceSave): See if PhotoBooth can be deleted +
          +Work:admin(SPaceSave): Empty photos from PhotoBooth. 
          + Work:admin(SpaceSave): see how to defrag Macbook Air.
          http://www.macworld.co.uk/how-to/mac/how-defrag-speed-up-mac-os-x-2016-3600241/
          
        \item \tiny Mgmt:Spaces(call about car): car update = Mgmt:Spaces(car): get check engine light checked +
          Mgmt:Spaces: update software \te{ 1 hour}. 

        \item \tiny Mgmt:webpresence: fb unlike Kavita’s pictures + Mgmt:wb:
          fb like to Nishant's pictures +  Mgmt:wp: fb like to Joshua
          + Mgmt:wb:fb like to Leila's pics + Mgmt:webpresence: fb
          like to Tanuja + Mgmt:wp: have Kavita put picture up of Gary  + \doneTaskNoItem{Mgmt:wp:
          fb like Sapna's baby picture}.


        \item \tiny Comm: message to Rishi to meet up \te{Jan}.
        \item \tiny Comm: put a picture on Instagram with Atul and you on. 
        \item \tiny Mgmt:webpresence: put Chris's picture up. 

        \item \tiny  \textbf{End Curr} 

        \item \tiny  Mgmt:Spaces: consider new wheels.
        \item \tiny EI: Study materials from CBT.  \te{2 hours}
          \dl{Monday}.

        \item \tiny Mgmt:Spaces: get Virginia license and registration
          \pr{Urgent}. 

        \item \tiny Consider joining AAAS: \url{https://pubs.aaas.org/promo/Member/member_setup.asp}

        \item \tiny Work: admin: look at 401k plan. \te{1 hour}
        \item \tiny Work: send message about Whiteboard marker holder to
          Barbara\te{1 hour} = Work:admin(MH): Write draft +
          Work:admin(MH): talk to Forrest. 
        \item \tiny Mgmt:Spaces: get metromile car insurance.  \te{10
          minutes} \pr{IU}. 
        \item \tiny Work(setup): set up pictures for git repo +
          Work(setup): put up picture for slack. 

        \item \tiny Work: get MS office installed on laptop. 
        \item \tiny Work: IM system for LLNL. 

        \end{enumerate}
      \end{block}
 
      % howto: the below is a routine based on the job I'm doing and the
      % circumstances I'm in. Note that this is different from routines
      % above, which is true for a long-term period of over 10 years. 

      \begin{block}{Weekly Meetings}
        \begin{itemize}
          \tiny \item \tiny IWOMP affinity meeting Thursday 7 AM PDT / 9 AM
          CDT call in: 805-639-779 pswd: places. \url{https://llnl.webex.com/llnl/j.php?MTID=m33950b76befb72c0cbc31ea2e3be720c}
        \item \tiny DEG group meeting.  
        \end{itemize}
      \end{block} 
     
\comments{ 
      \begin{block}{Week Daily Schedule} %NOTE: must have a curly brace
                                %for blocks. 
        {\bf Sun:}  Comm: prep for talk, Comm: message to Asavi,
        \newline {\bf Mon:} 
        %NOTE: can't use newlines in macros easily 
        \newline {\bf Tues:}         
        \newline {\bf Wed:}
        \newline {\bf Thur:} 
        \newline {\bf Fri:} 
        \newline {\bf Sat:}
      \end{block} 
     } 
%TODO: consider adding weather command-line option here.  

\comments{
      \begin{block}{Week Daily Schedule}
        % howto: arrange items from running todo into the below
        % sheet management document. 
        
        \begin{columns}
          \begin{column}{0.14\textwidth}{\small \underline{\bf Mon}}

            {\small \bf weather: } 11/1 s \\ 
            {\small \bf todo}\\ 
            \begin{itemize}
              \tiny \item \tiny Work: message to Prof . Gropp 
            \item \tiny Work: ask about leave. 
            \item \tiny Work: talk to Kristina. 
            \item \tiny 
            \end{itemize} 
                {\small  \bf schedule}\\
                \begin{enumerate} 
                  \tiny \item \tiny 8-9AM: Regular Routines 
                \end{enumerate}
          \end{column} 
          
          \begin{column}{0.14\textwidth}{\small \underline{\bf Tues}}

            {\small \bf weather: } 3/1 r \\ 
            {\small {\bf todo}}\\ 
            \begin{itemize}
              \tiny \item \tiny Add in schedule
            \item \tiny -
            \end{itemize} 
                {\small {\bf schedule}}
                \begin{enumerate} 
                  \tiny \item \tiny 8-9AM: Regular Routines 
                \end{enumerate} 
          \end{column}

          \begin{column}{0.14\textwidth}{\small \underline{\bf Wed}}
            {\small \bf weather: } 3/1 r \\ 
            \small{\bf todo}\\
            \begin{itemize}
              \tiny \item \tiny Add in schedule
            \item \tiny -
            \end{itemize} 
                {\small {\bf schedule}}\\
                \begin{enumerate} 
                  \tiny \item \tiny 8-9AM: Regular Routines 
                \end{enumerate} 
          \end{column}

          \begin{column}{0.14\textwidth}{\small \underline{\bf Thurs}}
            {\small \bf weather: } 1/-1 r \\ 
            {\small {\bf todo}} \\ 
            \begin{itemize}
              \tiny \item \tiny Add in schedule
            \item \tiny 
            \end{itemize} 
                {\small {\bf schedule}} \\
                \begin{enumerate} 
                  \tiny \item \tiny 8-9AM: Regular Routines 
                \end{enumerate}
          \end{column} 
          
          \begin{column}{0.14\textwidth}{\small \underline{\bf Fri}}
            {\small \bf weather: } 3/1 r \\ 
            {\small {\bf todo}} \\ 
            \begin{itemize}
              \tiny \item \tiny Add in schedule
            \item \tiny 
            \end{itemize} 
                {\small {\bf schedule}} \\
                \begin{enumerate} 
                  \tiny \item \tiny 8-9AM: Regular Routines 
                \end{enumerate}
          \end{column}

          \begin{column}{0.15\textwidth}{\small \underline{\bf Sat}}
            {\small \bf weather: } 11/1 .2r \\ 
            { \small {\bf todo}} \\ 
            \begin{itemize}
              \tiny \item \tiny Add in schedule
            \item \tiny 
            \end{itemize} 
                {\small {\bf schedule}} \\
                \begin{enumerate} 
                  \tiny \item \tiny 8-9AM: Regular Routines 
                \end{enumerate}
          \end{column}
          
          \begin{column}{0.15\textwidth}{\small \underline{\bf Sun}}
            {\small \bf weather: } 11/2 r \\ 
            {\small {\bf todo}}\\ 
            \begin{itemize}
              \tiny \item \tiny Add in schedule
            \end{itemize} 
                {\small {\bf schedule}}\\
                \begin{enumerate} 
                  \tiny \item \tiny 8-9AM: Regular Routines 
                \end{enumerate}
          \end{column}

        \end{columns}
      \end{block}

}
 

\begin{table}[ht!]
\label{fig:calendar}
\begin{center}
\begin{tabular}
{ | c || c | c | c | c | c | c | c |}
\hline
  \textbf{\small content} & {\small \bf M} & {\small \bf T} & {\small
    \bf W} & {\small \bf R} & {\small \bf F} & {\small \bf Sa} &
         {\small \bf Su} \\
  \hline
  \small weat  &\tiny 2/3 r &\tiny 2/1 r &\tiny 2/-1 r &\tiny 11/2 s  &\tiny 11/4 s   &\tiny  11/4 s &\tiny 11/5 s \\
  \hline
  \small todo  &\small &\small &\small &\small &\small &\small
  &\small  \\
  \small       &\small &\small &\small &\small &\small &\small
  &\small  \\
  \small       &\small &\small &\small &\small &\small &\small
  &\small  \\
  \small       &\small &\small &\small &\small &\small &\small
  &\small  \\
  \small       &\small &\small &\small &\small &\small &\small
  &\small  \\
  \hline
  \small schd  &\small &\small &\small &\small &\small &\small &\small  \\
  \small     &\small &\small &\small &\small &\small &\small  &\small
  \\
  \small      &\small &\small &\small &\small &\small &\small  &\small
  \\
  \small    &\small &\small &\small &\small &\small &\small  &\small
  \\
  \small     &\small &\small &\small &\small &\small &\small &\small
  \\
  \hline
  %\bottomrule                                                                                                                                                                                                 
\end{tabular}
\end{center}
\end{table}

  \end{column}




    
    % ------ Page 2: Column 3
    \begin{column}{0.25\linewidth}
      % ------ Block 2.3.1 
      \begin{block}{Food Plan} 
        \begin{itemize}
          \tiny \item \tiny Google Express: DHDQQJQDRFTXDM95B
        \end{itemize}
      \end{block} 
      \begin{block}{Clothes plan} 
        \begin{itemize}
          \tiny \item \tiny Monday: 
        \item \tiny Tuesday
        \item \tiny Wednesday
        \item \tiny Thursday
        \item \tiny Friday
        \item \tiny Saturday
        \end{itemize} 
      \end{block} 
      
      %-- Block 3-3 
      \begin{block}{Situations}
        % Summary: the below are the situations that define one
        % another.
        % Howto: Put post notes of each situation from list of previous
        % week. Put high importance situations in situationslist. 
        % Put list of upcoming situations on Sunday morning with Pre. 
        \begin{itemize}
          \tiny \item \tiny Situation: meet With Kavita  Post-: More
          social awareness. More planning.
        \end{itemize}
      \end{block}
      % contingincies: 
      % Summary:

    \end{column} 
  \end{columns}
