\documentclass[11pt]{article}

\usepackage{ulem}
\usepackage{color}
\usepackage{xspace}
\newcommand{\bllt}{\item \small}
\newcommand{\doneTask}[1]{\item \sout{#1}}
\newcommand{\doneTaskHyp}[1]{\item \textcolor{blue} {\sout{#1}}}
\newcommand{\optTask}[1]{\item  \textcolor{green}{#1}}
\newcommand{\prioTask}[1]{\item  \textcolor{red}{#1}}
\newcommand{\timeEst}[1]{\textit{Time:} \textit{#1}}
\newcommand{\priority}[1]{\textit{Priority:} \textit{#1}}
\newcommand{\dueBy}[1]{\textit{Deadline:} \textit{#1}}
\newcommand{\MyName}{Vivek~Kale}
\newcommand{\fixme}[1]{\textcolor{blue}{[FIXME: #1]}}
\newcommand{\revision}[1]{\textcolor{blue}{[FIXME comment : #1]}}
\newcommand{\regItem}[1]{\item \textcolor{cyan}{#1}}
\newcommand{\regRoutineItem}[1]{\item \textcolor{green}{\textit{Reg. Routine:} #1}}
\newcommand{\situationItem}[1]{\item \textcolor{magenta}{\textit{Situation:} #1}}
%Note:  consider weekly schedule template


%TODO : figure out how to schedule urgent and important tasks


\begin{document}

{\huge{\underline{\textbf{Week of Feb. 2nd}}}} \\

\textbf{Summary:} This is the weekly planning document. To create
this, first look at weekly routines and make sure they are here. Then,
look at the yearWeekPlan doc, along with project plan doc, and iPhone
todo list, and divide tasks across days of the week. Then, put this
into the schedule.

After this is done, these items should be checked in the work and
work+life calendar, and verified through email.
Then, they should be put in the work + life
calendars. \\

\textbf{Worries to watch for} \\
\begin{enumerate}
\item seeing another person
\item ex-
\item New Years text
\item
\end{enumerate}

\textbf{Current habits}\\
\begin{itemize}
\item belt on, pants high
\item dinner etiquette
%\item avoid facebook / social media urge
%\item no cell phone
\end{itemize}

\underline{\textbf{situations}} \\
\begin{enumerate}
\item Toastmaster's eval. :  Pre-     Post: listen in the beginning, have a rough plan of structure, mark down words for eval.
\item Talk to Divya :  Pre: Think about three words to spark conversation    Post: don't go off on tangents
\item Talk to Nithya: Pre:  Post:  Talk less about things you've done, have a plan of what to say, and what to ask
\item Meet at Cocktails for Cause: Pre- ,  Post:
\item MBA event :   Pre:   Post:
\end{enumerate}

\underline{\textbf{\textit{Monday}}}\\
\underline{\textbf{todo}}\\
\begin{enumerate}
\item read style guide:  omit needles words, add notes in doc  \timeEst{1 hour}
\item summarize win friends and influence people, ch. 1 \timeEst{10 mins}
\item work on speech \timeEst{30 mins}
\end{enumerate}

\underline{\textbf{schedule}}\\
\begin{itemize}
\regItem{7:00AM - 8:00AM: running}
\regItem{9:00AM - 10:00AM : regular routines for morning}
\regItem{5:00PM - 6:00PM : send out email to everyone on notes for meeting}
\situationItem{ 5:30PM - 6:30PM : talk to Nithya} \timeEst{10 mins}
\regItem{9:00PM - 10:00PM : regular routines for night}
\end{itemize}

\underline{\textbf{\textit{Tuesday}}}\\
\underline{\textbf{todo}}\\
\begin{enumerate}
\item send message to Divya about time that works \timeEst{2 mins} \priority{U}
\item send Torsten email about results \timeEst{10 mins}   \priority{U}
\item update paper to have writing done \timeEst{3 hours} \priority{I}
\item discuss adding in cost model with dad \timeEst{10 mins}
\item figure out portland trip \timeEst{10 mins} \priority{UI}
\item get call with Amanda about the icrev for pthreads in lbm code  \timeEst{10 mins}
\doneTask{send Prof Gropp an email about semester plans} \timeEst{10 mins}
\item collections \timeEst{20 mins} \priority{UI}
\item register for MBA tour \timeEst{30 mins} \priority{U}
\item finish buying ticket  for cocktails for a cause \timeEst{10 mins} \priority{U}
\end{enumerate}

\underline{\textbf{schedule}}\\
\begin{itemize}
\regItem{7:00AM - 8:00AM: weights}
\regItem {8:00AM - 9:00AM: regular routines for morning}
\regItem {9:00AM - 10:00AM: meeting}
\item 11-12AM  :  summarize meeting, make plan for paper , prep for TM
\regItem {12:00PM - 1:00PM: Toastmasters}
\doneTask{ 1:00PM - 1:30PM : make notes on toastmasters}
\item 1:30PM-4PM :  work on paper
\item 4-4:30PM : send Prof Gropp plan for semester  get access to BW
\item 4:30PM-5:30PM  : work on Amanda's code
\doneTask{ 7PM - 8PM : talk to Atul about trip}
\item  fix the portland return trip.
\item 8-8:40PM :  do win friends influence people reviews
\item 8:45PM - 9:30PM: make notes on speech
\item 9:30PM -10PM : weekend planning
\regItem {10:00PM - 10:30PM: regular routines for night}
\end{itemize}



\underline{\textbf{\textit{Wednesday}}}\\
\underline{\textbf{todo}}\\
\begin{enumerate}
\item apply for Heidelberg Laureate forum \timeEst{3 hours}
\item work on speech \timeEst{30 mins}
\end{enumerate}
\underline{\textbf{schedule}}\\
\begin{itemize}
\regItem{7:00AM - 8:00AM: running}
\regItem{8:00AM - 9:00AM: regular routines for morning}
\item 1:30PM -2:30PM : talk on Faculty positions \timeEst{10 mins}
\item 5:30-6PM : prep for talking to Divya
\situationItem {6PM - 7PM: talk to Divya}
\regItem{10:00PM - 10:30PM: regular routines for night}

\end{itemize}

\underline{\textbf{\textit{Thursday}}}\\
\underline{\textbf{todo}}\\
\begin{enumerate}
\item send out email to everyone for updates on new paper, for revisions  \timeEst{30 mins}
\item send message to Prof Gropp about EuroMPI paper \timeEst{10 mins}
\item add in graphs for support in section 2 \timeEst{10 mins}

\item send out notes on contributions \timeEst{1 hour}
\item send message to everyone on updated paper \timeEst{20 mins}
\item send message to Arya \timeEst{10 mins}

\item add in code for pthreads in Amanda's code for stream \timeEst{2 hours}

\item do analysis of ``how to win friends and influence people'' 2 chapters \timeEst{30 mins}
\item work on speech \timeEst{30 mins}
\end{enumerate}

\underline{\textbf{schedule}}\\
\begin{itemize}
\regItem{7:00AM - 8:00AM: weights}
\regItem{8:00AM - 9:00AM: regular routines for morning}
\regItem {10AM -11AM : DEG meeting}
\item 10:00AM - 11AM : finish situation notes
\item 12PM - 1PM: update code
\item 1PM - 4PM: update paper
\item 3PM - 5PM: work on Amanda's code
\regItem{10:00PM - 11:00PM: regular routines for night}
\end{itemize}

\underline{\textbf{\textit{Friday}}}\\
\underline{\textbf{todo}}\\
\begin{enumerate}
\item get appt with Dr. Garrick \timeEst{10 mins}
\item paper revisions \timeEst{2 hours}
\item paper coding \timeEst{1 hour}
\item ask dad to talk to Pn \timeEst{20 mins}
\item watch hunger games \timeEst{3 hours}
\item summarize the style guide \timeEst{1 hour} \priority{UI}
\item do analysis of win friends and influence people, 2 chapters \timeEst{10 mins}  \priority{UI}
\item send Prof. Gropp note about EuroMPI \timeEst{10 mins}
\end{enumerate}

\underline{\textbf{schedule}}\\
\begin{itemize}
\regItem{7:00AM - 8:00AM: running}
\regRoutineItem {8:00AM - 9:00AM: regular routines for morning}
\regItem{10AM - 11AM : HPC group meeting}
\situationItem 7:30PM - 8:30PM: Post-doc outing
\regRoutineItem{10:00PM - 11:00PM: regular routines for night}
\end{itemize}

\underline{\textbf{\textit{Saturday}}}\\
\underline{\textbf{todo}}\\
\begin{enumerate}
\item excercise
\item do re-imbursements

\item summarize the style guide , first parts \timeEst{10 mins}
\item do analysis of win friends and influence people 2 chapters \timeEst{10 mins}

\end{enumerate}

\underline{\textbf{schedule}}\\
\begin{itemize}
\regItem{7:00AM - 8:00AM: yoga sculpt}
\regRoutineItem {8:30AM - 9:30AM: regular routines for morning}
\regItem{9:30AM - 10:30AM: Spaces maintenance}
\situationItem 12PM - 1PM :  meet with Amruta
\item 6PM - 8:30PM: work on Amanda's code, add shared mem. extensions
\item 8:30PM - 9:30PM : dinner
\item 9:30PM - 10:30PM : plan out weekend, tomorrow's sched.
\regItem{10:00PM - 11:00PM: regular routines for night}
\end{itemize}

\underline{\textbf{\textit{Sunday}}}\\
\underline{\textbf{todo}}\\
\begin{enumerate}
\item summarize the style guide \timeEst{10 mins}
\item do analysis of win friends and influence people 2 chapters \timeEst{10 mins}
\item  write up of speech 4 \timeEst{1.5 hours}
\end{enumerate}

\underline{\textbf{schedule}}\\
\begin{itemize}
\regItem{7:00AM - 8:00AM: weights + running + meditation }
\regRoutineItem {8:00AM - 9:00AM: regular routines for morning}
\item
\item 7-8PM: plan out /refine yearweeksPlan for the next month
\regItem{8-9PM:  plan out week in week Plan curr}
\regRoutineItem{10:00PM - 11:00PM: regular routines for night}
\end{itemize}


\newpage

\textbf{Regular Routines(for reference)}
\input{regularRoutines}

\end{document}
