\documentclass[serif, mathserif, final]{beamer}
\mode<presentation>{\usetheme{Lankton}} 
\usepackage[orientation=landscape,size=a0,scale=1.6, debug]{beamerposter}
%\usepackage[orientation=landscape,size=a0,scale=1.4,debug]{beamerposter}
%\usepackage[absolute,overlay]{textpos} % <-- can  use this to position text (solves problem of earlier yesterday with poster placement). 

%\documentclass[serif,mathserif,final]{beamer}
%\mode<poster>{\usetheme{RicePoster}}
\usepackage{amsmath,amsfonts,amssymb,pxfonts,xspace}

\usepackage{graphicx, ragged2e}
\usepackage{pgffor}
\usepackage{ulem}
\usepackage{caption}
\usepackage{courier}

\usepackage{verbatim}

%\usepackage[usenames,dvipsnames]{xcolor}    
\usepackage{listings}

\usepackage{float}
\usepackage{subfig}
\setbeamertemplate{caption}[numbered] 

\usepackage{calendar}
\usepackage{geometry}

%\graphicspath{{./figures/}}                                                   
%\usepackage{beamerposter}
%\graphicspath{{./figures/}} 
\newcommand{\bllt}{\item \small}
\newcommand{\doneTaskNoItem}[1]{\sout{#1}}
\newcommand{\doneTask}[1]{\tiny \item \tiny \sout{#1}}
\newcommand{\doneTaskHyp}[1]{\tiny \item \tiny \textcolor{blue} {\sout{#1}}}
\newcommand{\optTask}[1]{\tiny \item \tiny \textcolor{green}{#1}}
\newcommand{\prioTask}[1]{\tiny \item \tiny \textcolor{red}{#1}}
\newcommand{\timeEst}[1]{\textit{Time:} \textit{#1}}
\newcommand{\te}[1]{\textit{TimeEst:} \textit{#1}}
\newcommand{\priority}[1]{\textit{Priority:} \textit{#1}}
\newcommand{\pr}[1]{\textit{Priority:} \textit{#1}}
\newcommand{\prio}[1]{\textit{Priority:} \textit{#1}}
\newcommand{\dueBy}[1]{\textit{Deadline:} \textit{#1}}
\newcommand{\MyName}{Vivek~Kale}
\newcommand{\fixme}[1]{\textcolor{blue}{[FIXME: #1]}}
\newcommand{\revision}[1]{\textcolor{blue}{[FIXME comment : #1]}}
\newcommand{\regItem}[1]{\item \textcolor{cyan}{#1}}
\newcommand{\regRoutineItem}[1]{\item \textcolor{green}{\textit{Reg. Routine:} #1}}
\newcommand{\situationItem}[1]{\item \textcolor{magenta}{\textit{Situation:} #1}}
\newcommand{\deadline}[1]{#1}
\newcommand{\dl}[1]{#1}
\newcommand{\comments}[1]{}

%\graphicspath{{./figures/}}
%\usepackage[orientation=landscape,size=a0,scale=1.6,debug]{beamerposter}

%-- Header and footer information ----------------------------------
\newcommand{\footleft}{Mgmt-WorkLife-weekPlan} % figure what this should be 
\newcommand{\footright}{April 2015}

%------------------------------------------------------------------
%-- Main Document ------------------------------------------------- 
\title{Month-Week-Day Plan} 
\author{Vivek Kale$^1$}
\institute{$^1$ University of Illinois at Urbana-Champaign}  
\date{\today}

% TODO: make the below document neater 
% TODO: consider stretching center column 
% TODO: check how to fit week daily plan together .  

\begin{document}  

\comments{
\begin{frame}{} 
  \begin{columns}
    %-- Column 1 --------------------------------------------------- 
    \begin{column}{0.22\linewidth}
      \begin{block}{Happiness Generation - must maintain every week.} 
        % explain happiness: show gratitude
        % remember to show gratitude
        \begin{itemize}
          \tiny \item \tiny happy that I have Atul to show me.  
        \item \tiny Happy that I have normal life up to this point.  
        \item \tiny Thankful that I got a chance to do what I did on Saturday. 
        \item \tiny Think about Neha Jamb. 
        \item \tiny Think about dad saying, I understand, and want you to be happy. 
        \end{itemize}
      \end{block}

    \begin{block}{Habits} 
      \begin{itemize} 
        %\tiny \item \tiny move feet less, don't scrub on floor. 
        \tiny \item \tiny back straight + eye contact. 
      \item \tiny Reduce things. 
      \item \tiny lips relaxed. 
      \item \tiny watch what happens when a hot girl talks to you. 
      \end{itemize} 
    \end{block} 
  \end{column} %1

  \begin{column}{0.5\linewidth}
    %-- Block 2-1 
    \begin{block}{ 10-year plan }
      \begin{itemize}
      \item \small Make someone and dad proud.
      \end{itemize}
    \end{block}
    
    \begin{block}{ 3-year plan }
      \begin{itemize}
      \item \small find someone
      \item \small make 150K
      \item \small network
      \end{itemize}
    \end{block}

    \begin{block}{ 6-month plan}
      \begin{itemize}
        \small \item \small results + thesis
      \item \small routine + worklife
      \item \small 
      \end{itemize}
    \end{block} 

    \begin{block}{Month-by-month}
      \begin{itemize}
      \item \small Early December: finish slides for defense.
      \item \small Mid-december: put together things. 
      \item \small Late December: send out thesis to others 
      \item \small Late January: Defend.
      \item \small Mid-Feb: finish thesis, start looking for jobs. 
      \item \small Late feb: jobs+ and vacation. 
      \end{itemize}
    \end{block}

%TODO: prioritize
%\begin{column}{0.33\linewidth} {\textbf{\underline{Month Plan for August 2014}}}      %-- Block 1-1   
\begin{block}{\underline{\textbf{April goals}}}
\begin{enumerate}
\small \item \small 
\end{enumerate}
\end{block}

\begin{block}{\small \underline{\textbf{Week of April $17^{th}$}}}
\begin{enumerate}
\tiny \item \tiny 
\item \tiny 
\end{enumerate}
\end{block}
\end{column}

%-- Column 3 ---------------------------------------------


\begin{column}{0.28\linewidth}
\begin{block}{\small \textbf{\underline{Regular Routines}} }
\underline{\textbf{Morning}}
\begin{itemize}
\tiny \item \tiny Brush Teeth \timeEst{4 mins}. 
\item \tiny Mouthwash, Clean tongue - it helps with breath\timeEst{1mins} 
\item \tiny Eating small breakfast. 
\item \tiny Check your schedule for meetings / appointments for that day: Is anything urgent? \timeEst{5 mins}. 
\item \tiny Excercise: 1 hour ( Stretch for 10 mins, Treadmill for 30 mins , Lift weights or Yoga 1 hour, Meditation for 10 mins). 
\item \tiny Shave (at least every other day) \timeEst{5 mins}. 
\item \tiny Shower : (shampoo+conditioner, acne wash,  soap on underarms/underbody)
\timeEst{10 mins}
\item \tiny dry hair, dry face, arms, legs, back, stomach \timeEst{3 mins}
\item \tiny Clothing: belt, check collar, shirt not half-tucked, matching socks \timeEst{5 mins}
\item \tiny Comb hair, hair gel optional \timeEst{ 1 min}
\item \tiny Check Keys/Wallet/Cell/Badge (get a bucket) \timeEst{1 min}
\item \tiny Open meds cabinet, get water, take medicines \timeEst{1 min}
\item \tiny Wear lenses and rinse out case \timeEst{ 2 mins}
\item \tiny Deodorant or cologne depending on the day \timeEst{1 min}
\item \tiny Wash your face with a face wash - it helps with acne \timeEst{3 mins}
\item \tiny Moisturize - apply lotion \timeEst{ 2 min}
\item \tiny Neti pot / clean out sinuses - if you’re feeling congested \timeEst{5 min}
\item \tiny clean out ears, nose \timeEst{5 mins}
\item \tiny Remember to lock door \timeEst{1 mins}
\end{itemize} 

\underline{\textbf{Evening}}
\begin{itemize}
\tiny \item \tiny Call family: 30 mins
\item \tiny meet friends: 20 mins
\item \tiny Cleaning dishes / cleaning house: 10 mins
\item \tiny Lay out clothes for the next day, iron if necessary
\item \tiny start laundry if needed: 10 mins,
\item \tiny Collect anything you’ll need for the next day (e.g. dry cleaning to drop off): 5 mins,
\item \tiny Check Facebook/linkedin/google+: 10 mins, matrimony stuff: 10 mins,
\item \tiny Food for lunch/dinner the next day: 10 mins
\end{itemize}

\underline{\textbf{Night before bed}}
%TODO: why isn't enumerate working???
%\begin{enumerate}
\begin{itemize}
\tiny \item \tiny Finish computer stuff \timeEst{5 mins}
\item \tiny Get into sleeping clothes \timeEst{1 mins}
\item \tiny Before sleeping: brush teeth, floss \timeEst{ 2 min}
\item \tiny Properly wash and put away contacts \timeEst{ 2 mins}
\item \tiny Review the days good things \timeEst{ 10 min}
\item \tiny Light Reading \timeEst{ 10 min}
\item \tiny Prayer \timeEst{10 mins}
%\end{enumerate} 
\end{itemize}
\end{block} 
\end{column}%3 
\end{columns} 
\end{frame}
}

\begin{frame}{} 
  \begin{columns}
    %-- Column 1 --------------------------------------------------- 
    \begin{column}{0.25\linewidth} %{\textbf{\underline{Week
      %Aspects(new name)}}}
      \begin{block}{Habits}
        \begin{itemize}
          \tiny \item \tiny 
        \item \tiny 
        \item \tiny 
        \item \tiny 
        \end{itemize}
      \end{block}
      %-- Block 1-1 
      \begin{block}{Stresses}
        % Recognize emotions / recognize (precisely) what you're worried about -> methods for eliminating worry. 
        % clean out old worries, put them in pastWorries doc.  
        % remember to define precisely 
        % order from top-to bottom
        \begin{itemize}
          \tiny \item \tiny Worrying about thesis finish. Be sincere and work, we
          make mistakes with time. Get the facts about completion. Go
          find the path. If I can't get it done, then we'll do
          something else. 
          \tiny \item \tiny Work: worrying about interviewing: just
          focus on the work. 
        \item \tiny 
        \item \tiny 
          % \item \tiny Comm: worrying about situation at dinner.   stopworryingstartliving: spiritual(?): talk to someone, base: what's the worst? people will be better for a short time, but then you become better also, b/c you can.   
          % \item \tiny Comm: Worrying about not losing it (check this/ define this better) : work on sheet.  
          % \item \tiny Worrying about deep: forget her, because there's much more to be done.  She may not be interested because it's a brother. 
        \end{itemize} 
      \end{block} 
      
     \begin{block}{Real-time Confidence}
     \begin{itemize}
       \tiny \item \tiny if you do something sloppy, don't
       think about it and don't say sorry.
     \item \tiny don't think someone is trying to hurt you if
       they say something.
     \item \tiny know the paths of least stress.
     \item \tiny if mom does something, don't let that bite you.
     \end{itemize}
     \end{block}
     
     %-- Block 1-3
  \begin{block}{Life notes} 
    \begin{itemize} 
      \tiny \item \tiny Level 0+1: focus on finding Happiness. 
    \item \tiny Level 2: 
    \item \tiny Level 4.1: Writing: prefer standard to offbeat. 
    \item \tiny Level 4.2: Body Language: lips relaxed
    \item \tiny Level 4.3: Vocal Variety: shout. 
    \item \tiny TM: work on speech for submission to blog, increasing intentionality. 
    \item \tiny Mgmt/habits: finish chapter 1 reading notes and habits. 
    \end{itemize}     
  \end{block}
    \end{column} %2 
    
%-- Column 2 --------------------------------------------- 
\begin{column}{0.50\linewidth}
%{\textbf{\underline{Week TODO}}} 
% NOTE: Current policy is to comment out days as they come. 
  % TODO: put in the regular routines here for each day, in the schedule box. 
  %--- Block 2-1
  \begin{block}{Week Summary}
    \textbf{Weekend Plan:} Work: send message to Google, Work:comm:
    send Bronis message,  Work: finish project writing, Mgmt:Spaces:
    get keys checked,Comm:call Anu, Comm: do party updates \\

    \textbf{Week Plan:} Work:comm: send message to Prof. Gropp about
    HLF + send message about postdoc, Comm: call Anu, Comm: ohter
    invites +  Work: graduation stuff + Mgmt:spaces: keys , IWOMP paper 
    \\

    % Mgmt:Spaces:Southwest, 
%    \textbf{Week Plan:} Interview prep, Comm updates: invitation
%    letter, Mgmt: Spaces: Southwest + Passport pic, Project Notes +
%    Finish the thesis, Finish hw assignment + Review for
%    Interview. \\

  \end{block}

  \begin{block}{Running TODO} % find a better name 
    \begin{enumerate}
      \doneTask{ Work: finish work for course = Work: put in graphs  +
        Work: put in code change} \te{6 hour}. 
      \doneTask{Work: finish Homework 11} \te{1 hour}. 
    \doneTask{Work:comm: send message to Bronis to meet. }
    \doneTask{Work: comm: send message to Natasha from draft.} \te{1
      hour} \prio{doItSoonSinceItsAFace} 

    \doneTask{ Work: finish project writeup with more text fixed about
      the correlation.} \te{3
        hours}\prio{DoItByTonightSinceProfGroppMightReadItSoon}. 

    \doneTask{Comm: update fb pics}. \te{10
      mins}. \prio{ImportantToShowFace}     
    \doneTask{Comm: send email to Anu about keys} \te{20 mins}
      \prio{ sendSoon } \dl{eve}. 
      \doneTask{Comm: send email to Anu about fb.}\te{20 mins}
      \prio{}  \dl{SomeTimeBeforePrevEmail}


\item \tiny Work: give acceptance to postdoc \te{10
      mins}\prio{ImportantToKeepGoodRelationWithGropp}


      \item \tiny Mgmt: Spaces: license plate frame  + Mgmt:Spaces:
        keys taken care of \te{10 mins} + Mgmt: Spaces: wash
        Lexus + Work: admin: grad gown. \te{1 hr} \dl{Thursday} + \prio{DoItSoonToLookGood}  

     
    \doneTask{Work: finish getting reference} \te{1 hour}
      \prio{soonToGetRef}

%    \item \tiny Mgmt:Time: plan for week


      %    \item \tiny Work (hw9): Finish hw9 writeup = Work(hw9): finish hw9
      %    plots + Work(hw9): do hw9 writeup. 
      %  \item \tiny Mgmt:Spaces:(vulnerability): check tile. 
    \end{enumerate} 
  \end{block} 

  \begin{block}{Week Daily Schedule}
    \begin{columns} 
      \column{0.14\textwidth}{\textbf{\small \underline{Mon}}}
      \textbf{\small todo} \\ 
      \begin{itemize}
        \tiny \item \tiny Work: comm: 
        \tiny \item \tiny Work: comm: accept postdoc 

      \item \tiny Work: management of problems.
      \item \tiny Work: comm: send message about fellowship.
      \end{itemize} 
  \textbf{\small schedule} \\
  \begin{enumerate} 
    \tiny \item \tiny 8-9AM: Regular Routines 
  \end{enumerate} 

  \column{0.14\textwidth}{\textbf{\small \underline{Tue}}}
  \textbf{\small Todo} \\
  \begin{itemize} 
    \tiny \item \tiny Work: add'l practice problems 
     \item \tiny Comm: meditation. 
  \end{itemize}  
  \textbf{\small Schedule}\\ 
  \begin{enumerate} 
    \tiny \item \tiny Work: MPI-IO
  \item \tiny  Work: project - get runB and runC correlation coeffs on
    taub
    \item \tiny Work: write about the code in paper, and experimental
      app. 
      \item \tiny Work: write about the correlation coefficient.

  \end{enumerate} 

  \column{0.14\textwidth}{\textbf{\small {\underline{Wed}}}}
  \textbf{\small todo} \\
  \begin{itemize}
    \tiny \item \tiny Work: finish writing project. 
  \item \tiny Work: start homework. 
  \item \tiny worklife: do organization .  
  \item \tiny Mgmt:Spaces: . 
  \item \tiny Work:comm: send message to . 
  \item \tiny Work:comm: set up meeting time with Prof. Gropp. \te{10 mins}. 
  \item \tiny Comm: send message to Amit and Ritika \te{10 mins}. 
  \end{itemize}
  \textbf{\small schedule} \\
  \begin{enumerate}
    \tiny \item \tiny 8-9AM: Regular Routines 
  \end{enumerate}
  
  \column{0.14\textwidth}{\textbf{\small{\underline{Thu}}}}
  \textbf{\small todo}\\
  \begin{itemize} 
    \tiny \item \tiny
    \tiny \item \tiny Work: finish writing project. 
  \item \tiny Work: finish homework.  
  \end{itemize}
  \textbf{\small schedule}\\
  \begin{enumerate} 
    \tiny \item \tiny 8-9AM: Regular Routines 
  \end{enumerate} 
  
  \column{0.14\textwidth}{\textbf{\small{\underline{Fri}}}}
  \textbf{\small todo}\\ 
  \begin{itemize}
    \tiny \item \tiny -  \deadline{ }   \timeEst{}  \priority{} 
  \end{itemize}
  \textbf{\small schedule}\\
  \begin{enumerate}
    \tiny \item \tiny 8-9AM: Regular Routines 
  \end{enumerate}
  
  \column{0.14\textwidth}{\textbf{\small \underline{Sat}}}
  \textbf{\small todo}\\
  \begin{itemize}
    %  \tiny \item \tiny Work: comm: send message to Prof. Gropp. 
    % \item \tiny Work: do MPI-IO homework.

  \item \tiny Work: comm: send message to Natasha from draft \te{1 hour} \prio{doItSoonSinceItsAFace}

  \item \tiny Work: finish project writeup with more text fixed about
    the correlation. \te{3 hours} \prio{DoItByTonightSinceProfGroppMightReadItSoon}

  \item \tiny Work: give acceptance to postdoc \te{10 mins}\prio{ImportantToKeepGoodRelationWithGropp}
  \item \tiny Work: finish getting reference \te{1 hour} \prio{soonToGetRef}
  \end{itemize}
  \textbf{\small schedule}\\ 
  \begin{enumerate}
    \tiny \item \tiny 8-9AM: Regular Routines 
  \end{enumerate}
  
  \column{0.14\textwidth}{\textbf{\small \underline{Sun}}}
  \textbf{\small todo}\\
  \begin{itemize}
  \item \tiny Work: 
  \end{itemize}
  \textbf{\small schedule}\\
  \begin{enumerate} 
    \tiny \item \tiny 
  \end{enumerate} 
    \end{columns}
  \end{block}
\end{column}%2

%-- Column 3 --------------------------------------------------- 
\begin{column}{0.20\linewidth}
  %-- Block 3-1 
  % On Sunday morn, put a quick synopsis of top news items                  
  % here.  Categorize as Comm and Money.                                                                                          
  \begin{block}{News}
    \begin{itemize} 
      \tiny \item \tiny French Open
    \end{itemize}
  \end{block}
  \begin{block}{Weather} 
    \begin{itemize}
      \tiny \item \tiny Watch for Pollen.
    \item \tiny Rainy 
    \end{itemize}
  \end{block} 
  \begin{block}{Clothes plan} 
    \begin{itemize} 
      \tiny \item \tiny Saturday: wear polo 
    \item \tiny Saturday night: wear light blue dress shirt and jeans. (or maybe khakis and polo shirt). 
    \item \tiny Sunday: business casual shirt. 
    \item \tiny Wednesday : 
    \item \tiny Thursday: 
    \item \tiny Friday : 
    \item \tiny Saturday : Blue full shirt . 
    \item \tiny Sunday : Red shirt .
    \end{itemize} 
  \end{block}
  %-- Block 3-2

  %-- Block 3-3
  \begin{block}{Situations}
    \begin{itemize}
    \item \tiny \textit{BMW}: Pre-: clothes, clean car,figure out
      discussion with driver.  Post-:  check about questions for service. 
    \item \tiny \textit{Interview Tuesday}: Pre-: get all papers set
      up.  Review notes from last time. Post-: be more careful with
      organization in speech, even when you are nervous.  
    \item \tiny \textit{meet with Prof Gropp}: Pre-: clothes  Post-:
      Talk less in beginning, avoid saying "speaking of"
      graduation, then saying "on the topic" (wavers) 

    \item \tiny \textit{Email To Natasha:} Pre-:  Post-: 

    \end{itemize}
  \end{block}
\end{column}%3 
\end{columns}

\end{frame}
\end{document}
