\documentclass[serif,mathserif,final]{beamer}

\mode<presentation>{\usetheme{Lankton}} 
%\mode<presentation>{\usetheme{I6pd2}} 
%\mode<presentation>{\usetheme{RicePoster}} 
%%\mode<presentation>{\usetheme{ConfPoster}} 
\usepackage{amsmath,amsfonts,amssymb,pxfonts,eulervm,xspace}
\usepackage{graphicx, ragged2e}
\usepackage{pgffor}
\setbeamertemplate{caption}[numbered]

%\documentclass[11pt]{article}

\usepackage{ulem}
\usepackage{color}
\usepackage{xspace}
\newcommand{\bllt}{\item \small}
\newcommand{\doneTaskNoItem}[1]{\sout{#1}}
\newcommand{\doneTask}[1]{\item \sout{#1}}
\newcommand{\doneTaskHyp}[1]{\item \textcolor{blue} {\sout{#1}}}
\newcommand{\optTask}[1]{\item  \textcolor{green}{#1}}
\newcommand{\prioTask}[1]{\item  \textcolor{red}{#1}}
\newcommand{\timeEst}[1]{\textit{Time:} \textit{#1}}
\newcommand{\priority}[1]{\textit{Priority:} \textit{#1}}
\newcommand{\prio}[1]{\textit{Priority:} \textit{#1}}
\newcommand{\dueBy}[1]{\textit{Deadline:} \textit{#1}}
\newcommand{\MyName}{Vivek~Kale}
\newcommand{\fixme}[1]{\textcolor{blue}{[FIXME: #1]}}
\newcommand{\revision}[1]{\textcolor{blue}{[FIXME comment : #1]}}
\newcommand{\regItem}[1]{\item \textcolor{cyan}{#1}}
\newcommand{\regRoutineItem}[1]{\item \textcolor{green}{\textit{Reg. Routine:} #1}}
\newcommand{\situationItem}[1]{\item \textcolor{magenta}{\textit{Situation:} #1}}
\newcommand{\deadline}[1]{#1}
\newcommand{\comments}[1]{}

\graphicspath{{./figures/}}
\usepackage[orientation=landscape,size=a0,scale=1.6,debug]{beamerposter}

%-- Header and footer information ----------------------------------
\newcommand{\footleft}{Mgmt-WorkLife-weekPlan} % figure what this should be 
\newcommand{\footright}{June 2014}
\title{Month-Week-Day Plan} 
\author{Vivek Kale$^1$$^2$}
\institute{$^1$ University of Illinois at Urbana-Champaign \quad}  

%------------------------------------------------------------------
%-- Main Document ------------------------------------------------- 

\begin{document} 
\begin{frame}{}
  \begin{columns}[t]

    %-- Column 1 ---------------------------------------------------

%-- Column 1 ---------------------------------------------------  
\begin{column}{0.27\linewidth} {\textbf{\underline{Week Plan}}} 

  %-- Block 1-1
  \begin{block}{\textit Stresses} 
    % Recognize emotions / recognize what you're worried about -> eliminate worry
    \begin{itemize}
    \item \small EuroMPI paper : 
      \small \item \small Ridhima saying stuff about me. 
    \item \small related work:   
    \item \small Atul saying let's talk about this some other time. 
      % \item \small friends of Atul's better(?): 
      % \item \small email -done : 
      % \item \small anger that you are below parents 
      % \item \small [ find others ]
    \end{itemize} 
  \end{block} 
  %-- Block 1-2 

  %-- Block 1-3
  \begin{block}{\textit Habits } 
    \begin{itemize} 
      \small \item \small move feet less, don't scrub on floor. 
    \item \small back straight. 
    \item \small lips relaxed. 
    \end{itemize} 
  \end{block} 

  %-- Block 1-4
  \begin{block}{\textit Clothes plan } 
    \begin{itemize} 
      \small \item \small - 
    \item \small Saturday: wear polo shirt. 
    \item \small Saturday night: wear light blue dress shirt and jeans. (or maybe khakis and polo shirt ). 
    \item \small Sunday: business casual shirt. 
    \end{itemize} 
  \end{block} 

  %-- Block 1-5
  \begin{block}{\textit Food plan } 
    \begin{itemize} 
      \small \item \small Skip meals this week to take out fat from weekend. 
    \item \small Be very careful about food for Saturday night, along with Brunch for Sunday and dinner for Sunday. 
    \end{itemize} 
  \end{block} 

  \begin{block}{\textit Situations} 
    \begin{itemize} 
    \item \tiny Message to Prof. Gropp: Pre-: plan ahead of time  Post-: be careful with what you say, don't overthink.
    \item \tiny talk to George wardall on machine accts: Pre-: Post-: be less blaming, good to humour it, hold phone to ear after being angry will make other person want to criticize you more. 
    \item \tiny message to Amanda:  Pre-:     Post-: make quick points, don't worry about competition as much, find a way to balance brevity/ ``I got other stuff, don't want to be overbearing'' with ``yea, I'm paying attention to you''. 
    \item \tiny Atul Saturday morning (practice stuff): Pre-: check what to practice, make plan. Post-: don't say random things about pictures, (*) 
    \item \tiny Kelwan Saturday night: Pre-: wear nice clothes, be relaxed Post-: Talk with intention and don't talk about scotch complicated, know situation, get nice clothes earlier so you have time to plan other things, 
    \item \tiny Father's day brunch: Pre-: make sure to plan ahead what to say Post-: don't have to talk about nothing, be more intentional, make commentary about puzzles. 
\item \tiny Father's day shopping: Pre-:  Post-: don't talk about ``house'' - know what other person is saying, if someone says buy me anything then don't make it awkward, don't be overly angry if someone says something about you - just sit quiet. Good to say ``that's ok, I had my phone''.  
    \item \tiny Father's day dinner: Pre-: Greet everyone, don't talk too much (know what to say in certain situations)  Post-: know seating arrangements (will be important in wedding), be intentional when talking about something, 
    \item \tiny Toastmaster's: Pre-:  Post- : Come early, don't get upset by little things, don't talk too much if someone is getting confused / plan conversation earlier, figure out the awkward points early and prioritize/talk. 
    \end{itemize} 
  \end{block} 

\end{column} %2 
%-- Column 2 --------------------------------------------- 
\begin{column}{0.33\linewidth}{\textbf{\underline{Daily Plan}}} 

% NOTE: Current policy is to comment out days as they come. 
% TODO: put in the regular routines here for each day, in the schedule box. 
  %--- Block 2-1

\begin{block}{\small weekTODO} 

\begin{enumerate}

\item \tiny  Work: Do related work structure and motivation. 

\item \tiny Work: add code structure for data collection + Send message to Tanzima about PAPI + Find any other systems issues and take care of them + integrate the slack-conscious runtime/ MPI dot prod.  

\item \tiny Mgmt: Spaces:webpresence: change fb pic + change visibilities + choose and update matrimony pic + change website pic based on matrimony pic (or choose a separate one). 

\item \tiny Mgmt: Spaces: money: check sw old stuff; get the lamp; find iPad; update money;
\item \tiny \textbf{Mgmt: Spaces: Graduation: check for credit hours for the summer, get new ones if needed + check grad deadlines.  - got 6 hours,  need to register in fall for 1 S/U 500-level.  - checked the graduation/defense page, make sure your committee is in aggreement about the thesis. + Schedule defense in October / Do it early with checking Bronis's schedule / Be sure to go on Self-Service to apply for graduation before then. }
\item \tiny Mgmt: Spaces: Graduation: send messages on Post-docs. Princeton. / SUNY. / MIT. / Livermore. 

\item \tiny Mgmt: Spaces: get the taillight fixed, by buying this online. \timeEst{30 mins} 

\item \tiny \doneTask{workLife: Finish monthPlanCurr.} 
\item \tiny \doneTask{workLife: put situations in correct place.} 

\item \tiny workLife: finish emotional intelligence book, style guide, and winfriends. 
\item \tiny \doneTask{worklife: get cooking instructions down, get routine for running/excercise down, integrate other sheets.} 

\item \tiny Comm: structure Atul's speech + read vocal variety speech lessons, look at speech inspiration + sign up for week-after-next speech. 

\item \tiny \doneTask{Work: check with others about accounts at LLNL. }
\item \tiny \doneTask{Work: get environment setup, worklife: add in notes into environment}. 
\item \tiny Work: Figure out computer (cs-grad131), and check for files/images from CS525. 
\item \tiny GenKnowledge: get book on genKnowledge. 
\end{enumerate}

\end{block} 



\comments{ 
\begin{block}{\small Tuesday} 
\textbf{todo} \\
  \begin{itemize} 



\item \tiny worklife: revise spaces for comp: refine webpresence, put more details on work if possible. 

\item \tiny Mgmt:spaces: fix what's going on in ``work'' in ViveksLaptop directory. 
\item \tiny \doneTask{Work: check with others about accounts at LLNL. }
\item \tiny \doneTask{Work: reply to Amanda's email} 

\item \tiny Work: start adding code to collect data. \priority{IU}
\item \tiny Work: check about the application stuff for Amanda's code. 


  \item \tiny Work: figure whether we need to write  ``how to write a paper'', and could add this to comm guide   \timeEst{1 hour} 


\item \tiny Comm: Finish reading chapter for empathy. 
\item \tiny Comm: Read style guide and put all stuff in. 
\item \tiny Comm: Read How to win friends'' first parts and document / structure. 

\item \tiny Comm: start writing Atul's speech. 

  \item \tiny Code startup with PAPI, send message to Tanzima. \timeEst{3 hours} 
  \item \tiny Organization of code in repo. \timeEst{1 hour} \priority{IU, weighty} 
  \item \tiny Work: fix code, with graphs added \priority{quick} \timeEst{2 hours} 

  \item \tiny Mgmt: reg. routines: add in bathroom instructions again , with modifications to shower soap +  Mgmt: Spaces: Clean bathroom, organize spaces 
  \end{itemize} 
  
\underline{\textbf{schedule}}\\
\begin{itemize}
\regItem{7:00AM - 8:00AM: weights}
\regItem{8:00AM - 9:00AM: regular routines for morning}
\regItem{9:00AM - 10:00AM: meeting} 
\item \tiny 
\item \tiny 
\item \tiny 
\regItem{9:30-10PM: fb social, linkedIn social, read self-improvement/comm books}
\regItem{10:00PM - 10:30PM: regular routines for night} 
\end{itemize} 
\end{block} 

\begin{block} {\small Wednesday}
\textbf{todo} \\
  \begin{itemize} 
  \item \doneTask{\tiny worklife: go through goals again.}
  \item \doneTask{\tiny  Mgmt:Spaces:  Get the money stuff done for the RA work.} 
    
    
  \item \tiny Work: get data collection code done. \priority{quick} 
  \item \tiny Work: add related work bibs.  \priority{important} 
  \item \tiny Work: go through Amanda's code and see what needs to be done, do some planning. \priority{I} 

  \item \tiny Comm: write notes on Win Friends Influence People. \priority{important} 
  \item \tiny Comm: Note down Emotional Intelligence Empathy chapter. \priority{important} 

  \end{itemize} 

\textbf{schedule} \\
  \begin{enumerate} 
    \regItem{7:00AM - 8:00AM: weights}
    \regItem{8:00AM - 9:00AM: regular routines for morning}
  \item \tiny Mgmt: Health: write down excercise routine 
  \item \tiny Mgmt: Spaces: get clean laundry ironed
    \regItem{10:00PM - 10:30PM: regular routines for night}
  \end{enumerate} 
\end{block} 

\begin{block}{\small Thursday} 
\textbf{todo} \\
\begin{itemize} 

\item \tiny \doneTask{worklife: Write down macports setup in Environment folder. Add in bashrc, along with ssh login stuff \priority{quick}.} 
\item \tiny Work-Mgmt:Spaces get accounts back up, and environment setup. 
\item \tiny Mgmt: Money: Send message to Todi about lamp \priority {Urgent} 

\item \tiny Work: figure out conference to submit cloud to (BigData or EuroPar workshop - look for others) \timeEst{20 mins} \deadline{Wednesday}. 

\item \tiny Work: find other papers, and read related work. Need 100 citations or so., Add comparison to TBB (check about Barnes-Hut implementation in TBB for the last part). 

\item \tiny \doneTask{Work: get the \texttt{paper.tex} file for the cloud into the thesis, 
  add in citations from that into bibliography.bib. \priority{quick}.} 

\item \tiny Work: add in modeling stuff from IPDPS2010 paper, as Prof Gropp suggested. 

\item \tiny Work: put in system for integration of different parts of code. Add in slack-conscious runtime. 

\item \tiny Work: find systems issues and enumerate them, prioritize them, and make plan for fixing them. 

\item \tiny Work: go through Amanda's code.  

\item \tiny Comm: attend Toastmasters at 200 W. Green Street tonight, and during lunchtime. , Comm: make notes on TM 

\item \tiny Comm: do books (emo intelligence, winfriends, styleguide, 7habits as outer layer). 

\end{itemize} 

\textbf{schedule} \\
  \begin{enumerate} 
    \regItem{7:00AM - 8:00AM: weights}
    \regItem{8:00AM - 9:00AM: regular routines for morning}
  \item \tiny Mgmt: Health: write down excercise routine.  
  \item \tiny Mgmt: Spaces: get clean laundry ironed.     
  \item \tiny 5:30PM - 6PM = finish summary for meeting.  
  \item \tiny 6:15PM - 8:00PM = toastmasters 
  \item \tiny 8PM - 8:45PM = excercise     
  \item \tiny 9:30-11PM = send Prof. Gropp an email update. 
    \regItem{10:00PM - 10:30PM: regular routines for night}
  \end{enumerate}
\end{block}

\begin{block}{\small Friday} 
  \textbf{todo} 
  \begin{itemize} 
  \item \tiny 
  \item \tiny
  \end{itemize} 
  \textbf{schedule}
\begin{enumerate}   
  \regItem{\tiny 7:00AM - 8:00AM: weights}
  \regItem{\tiny 8:00AM - 9:00AM: regular routines for morning}
  \regItem{\tiny 8PM - 8:30PM : Situations analysis.} 
  \regItem{\tiny 8:30PM - 9PM : (Note: this could happen every other week):  workLife Doc improvement. } 
  \tiny \item \tiny 9:00PM - 9:30PM  =  update profile pic with brother, add jimmy john's post.  
   \item \tiny 11:20AM -11:35PM = get paper and update this into thesis \timeEst{15-20 mins} 
     
   \item \tiny 11:35PM - 12PM = send email to Bronis and Clea, with lc-support, to get accounts reactivated. \timeEst{30 mins} \priority{UI, HelpsToGetOtherThingsDone} \deadline{Friday 4PM}. 
   \item \tiny 12PM - 1PM  = related work organization finish, finish meeting summary, finish organization of thesis. 
   \item \tiny 1PM - 2:30PM = take notes on Hormozd's thesis
   \item \tiny 10:30PM - 11:30PM = go through modeling and update this in svn -- carries over to next day.
   \item \tiny 11:30PM - 12:30PM =  get code done (?) 
   \item \tiny 12:30PM - 1:30AM = organize tasks for the next week.
     
   \item \tiny 1:30AM - 2:30AM = Figure out any other worklife to be done. Make plan to finish self-improvement books on worklife(
     including making inferences, depth,etc), and to incorporate into worklife doc (along with practicing etc.) 

\end{enumerate} 
\end{block}

\begin{block}{\small Saturday } 
  \textbf{todo} 
  \begin{itemize} 
  \item \tiny 
  \item \tiny
\item \tiny Mgmt: Spaces: webpresence: choose linkedIn pic 
\item \tiny Mgmt: Spaces: webpresence: update website with various changes to pic. 
  \end{itemize} 

  \textbf{schedule} 
  \begin{enumerate} 
    \regItem{7:00AM - 8:00AM: weights}
    \regItem{8:00AM - 9:00AM: regular routines for morning} 

    \regItem{ \tiny  1:00PM - 2:00PM : Mgmt: Spaces: Spaces org} 
    \regItem{\tiny  2:00PM - 2:05PM : Mgmt: Spaces: clothes planning/ check weather for week} 
    \regItem{\tiny  2:05PM - 2:30PM : Mgmt: Spaces: clothes planning} 
    \regItem{ \tiny  2:30PM - 3:00PM :  Mgmt: Spaces: Money Management }
    \regItem{ \tiny  3:00PM - 3:30PM : Mgmt: Money: flights} 
    \regItem{10PM  - 10:30PM: regular routines for night}
  \end{enumerate} 

\end{block} 

\begin{block}{\small Sunday } 
  \textbf{todo} 
  \begin{itemize} 
  \item \tiny 
  \item \tiny
  \end{itemize} 

  \textbf{schedule} 
  \begin{enumerate} 
    \regItem{7:00AM - 8:00AM: weights}
    \regItem{8:00AM - 9:00AM: regular routines for morning}
  \item \tiny    
    \regItem{9:00AM - 10:00AM: GenKnowledge} 

    \regItem{7PM - 8PM: WeekPlanning} 
    \regItem{8PM - 8:30PM : (Note: this only happens every month) Month Planning} 
    
    \regItem{10PM  - 10:30PM: regular routines for night}
  \end{enumerate} 
  
\end{block} 

} %// end comments 

%Block 2-3

\begin{block}{\small \textbf{\underline{Regular Routines}} }
\underline{\textbf{Morning}}
\begin{itemize}
\item \tiny Brush Teeth \timeEst{4 mins}
\item \tiny Mouthwash, Clean tongue - it helps with breath\timeEst{1mins} 
\item \tiny Eating small breakfast
\item \tiny Check your schedule for meetings / appointments for that day: Is anything urgent? \timeEst{5 mins}
\item \tiny Excercise: 1 hour ( Stretch for 10 mins, Treadmill for 30 mins , Lift weights or Yoga 1 hour, Meditation for 10 mins)
\item \tiny Shave (at least every other day) \timeEst{5 mins}
\item \tiny Shower : (shampoo+conditioner, acne wash,  soap on underarms/underbody)
\timeEst{10 mins}
\item \tiny dry hair, dry face, arms, legs, back, stomach \timeEst{3 mins}
\item \tiny Clothing: belt, check collar, shirt not half-tucked, matching socks \timeEst{5 mins}
\item \tiny Comb hair, hair gel optional \timeEst{ 1 min}
\item \tiny Check Keys/Wallet/Cell/Badge (get a bucket) \timeEst{1 min}
\item \tiny Open meds cabinet, get water, take medicines \timeEst{1 min}
\item \tiny Wear lenses and rinse out case \timeEst{ 2 mins}
\item \tiny Deodorant or cologne depending on the day \timeEst{1 min}
\item \tiny Wash your face with a face wash - it helps with acne \timeEst{3 mins}
\item \tiny Moisturize - apply lotion \timeEst{ 2 min}
\item \tiny Neti pot / clean out sinuses - if you’re feeling congested \timeEst{5 min}
\item \tiny clean out ears, nose \timeEst{5 mins}
\item \tiny Remember to lock door \timeEst{1 mins}
\end{itemize}

\underline{\textbf{Evening}}

\begin{itemize}
\item \tiny Call family: 30 mins
\item \tiny meet friends: 20 mins
\item \tiny Cleaning dishes / cleaning house: 10 mins
\item \tiny Lay out clothes for the next day, iron if necessary
\item \tiny start laundry if needed: 10 mins,
\item \tiny Collect anything you’ll need for the next day (e.g. dry cleaning to drop off): 5 mins,
\item \tiny Check Facebook/linkedin/google+: 10 mins, matrimony stuff: 10 mins,
\item \tiny Food for lunch/dinner the next day: 10 mins
\end{itemize}

\underline{\textbf{Night before bed}}
%TODO: why isn't enumerate working???
%\begin{enumerate}
\begin{itemize}
\item \tiny Finish computer stuff \timeEst{5 mins}
\item \tiny Get into sleeping clothes \timeEst{1 mins}
\item \tiny Before sleeping: brush teeth, floss \timeEst{ 2 min}
\item \tiny Properly wash and put away contacts \timeEst{ 2 mins}
\item \tiny Review the days good things \timeEst{ 10 min}
\item \tiny Light Reading \timeEst{ 10 min}
\item \tiny Prayer \timeEst{10 mins}
%\end{enumerate} 
\end{itemize}
\end{block}

\end{column}%3 

\end{columns} 

\end{frame} 

\end{document}
