\documentclass[serif, mathserif, final]{beamer}
\mode<presentation>{\usetheme{Lankton}} 
\usepackage[orientation=landscape,size=a0,scale=1.6, debug]{beamerposter}
%\usepackage[orientation=landscape,size=a0,scale=1.4,debug]{beamerposter}
%\usepackage[absolute,overlay]{textpos} % <-- can  use this to position text (solves problem of earlier yesterday with poster placement). 

%\documentclass[serif,mathserif,final]{beamer}
%\mode<poster>{\usetheme{RicePoster}}
\usepackage{amsmath,amsfonts,amssymb,pxfonts,xspace}

\usepackage{graphicx, ragged2e}
\usepackage{pgffor}
\usepackage{ulem}
\usepackage{caption}
\usepackage{courier}

\usepackage{verbatim}

%\usepackage[usenames,dvipsnames]{xcolor}                                                                                                                            
\usepackage{listings}

\usepackage{float}
\usepackage{subfig}
\setbeamertemplate{caption}[numbered] 

%\graphicspath{{./figures/}}                                                                                              
%\usepackage{beamerposter}
%\graphicspath{{./figures/}} 
\newcommand{\bllt}{\item \small}
\newcommand{\doneTaskNoItem}[1]{\sout{#1}}
\newcommand{\doneTask}[1]{\item \sout{#1}}
\newcommand{\doneTaskHyp}[1]{\item \textcolor{blue} {\sout{#1}}}
\newcommand{\optTask}[1]{\item  \textcolor{green}{#1}}
\newcommand{\prioTask}[1]{\item  \textcolor{red}{#1}}
\newcommand{\timeEst}[1]{\textit{Time:} \textit{#1}}
\newcommand{\priority}[1]{\textit{Priority:} \textit{#1}}
\newcommand{\prio}[1]{\textit{Priority:} \textit{#1}}
\newcommand{\dueBy}[1]{\textit{Deadline:} \textit{#1}}
\newcommand{\MyName}{Vivek~Kale}
\newcommand{\fixme}[1]{\textcolor{blue}{[FIXME: #1]}}
\newcommand{\revision}[1]{\textcolor{blue}{[FIXME comment : #1]}}
\newcommand{\regItem}[1]{\item \textcolor{cyan}{#1}}
\newcommand{\regRoutineItem}[1]{\item \textcolor{green}{\textit{Reg. Routine:} #1}}
\newcommand{\situationItem}[1]{\item \textcolor{magenta}{\textit{Situation:} #1}}
\newcommand{\deadline}[1]{#1}
\newcommand{\comments}[1]{}

%\graphicspath{{./figures/}}
%\usepackage[orientation=landscape,size=a0,scale=1.6,debug]{beamerposter}

%-- Header and footer information ----------------------------------
\newcommand{\footleft}{Mgmt-WorkLife-weekPlan} % figure what this should be 
\newcommand{\footright}{August 2014}

%------------------------------------------------------------------
%-- Main Document ------------------------------------------------- 
\title{Month-Week-Day Plan} 
\author{Vivek Kale$^1$}
\institute{$^1$ University of Illinois at Urbana-Champaign}  
\date{\today}

% TODO: make the below document neater 
% TODO: consider stretching center column 
% TODO: check how to fit week daily plan together 

\begin{document} 
\begin{frame}{} 
  \begin{columns}
%-- Column 1 ---------------------------------------------------  
\begin{column}{0.25\linewidth} %{\textbf{\underline{Week Aspects(new name)}}}
  %-- Block 1-1
  \begin{block}{ Stresses} 
    % Recognize emotions / recognize what you're worried about -> eliminate worry
    \begin{itemize}
     % \tiny \item \tiny EuroMPI paper: 
     % \small \item \tiny Ridhima saying stuff about me. 
    %\item \tiny related work:   
      % \item \tiny Atul saying let's talk about this some other time. 
      % \item \small friends of Atul's better(?): 
      % \item \small email -done : 
      % \item \small anger that you are below parents 
      % \item \small [ find others ]
    %\item \tiny others at work. 
    %\item \tiny Comm: Talking to Amit - can bounce back, just close
    %  friends.
      %\item \tiny Comm: restricted profile - take it for face
      % value, probably because I'd get angry. 
    \tiny \item \tiny Comm: Frustration about Sneha - you still are you.
  %\item \tiny Comm: thinking about how Sat. went /general worries:
   %   don't worry and be conscious. 
  %  \item \tiny Comm: putting extra fb update - just did it for fun
  %    and whatever, if anything just local anxiety. 
    \item \tiny Comm: brother getting upset about laptop: 
 %   \item \tiny Comm: fb message to everyone: will go with time, was stressed about something, said Kaw later
    \item \tiny Comm: angry about weekend: she was too shy anyways

    \item \tiny Comm: remembering ab : it didn't work out for a reason 
    \item \tiny worrying about not losing it (check this/ define this better) : work on sheet. 
    \end{itemize} 
  \end{block} 
  %-- Block 1-2 
  
  %-- Block 1-3
  \begin{block}{ Habits } 
    \begin{itemize} 
      %\tiny \item \tiny move feet less, don't scrub on floor. 
    \tiny \item \tiny back straight. 
    \item \tiny lips relaxed. 
    \item \tiny watch what happens when a hot girl talks to you. 
    \end{itemize} 
  \end{block} 

  %-- Block 1-4
  \begin{block}{ Clothes plan } 
    \begin{itemize} 
    \tiny \item \tiny Saturday: wear polo shirt. 
    \item \tiny Saturday night: wear light blue dress shirt and jeans. (or maybe khakis and polo shirt). 
    \item \tiny Sunday: business casual shirt. 
    \item \tiny Wednesday : 
    \item \tiny Thursday: 
    \item \tiny Friday : 
    \item \tiny Saturday : Blue full shirt . 
    \item \tiny Sunday : Red shirt .
    \end{itemize} 
  \end{block} 
  %-- Block 1-5
  \begin{block}{ Food plan } 
    \begin{itemize} 
      \tiny \item \tiny Skip meals this week to take out fat from weekend. 
    \item \tiny Be very careful about food for Saturday night, along with Brunch for Sunday and dinner for Sunday. 
    \end{itemize} 
  \end{block} 
  \begin{block}{ Situations} 
    \begin{itemize} 
      
    \item \tiny \textit{Meet with Neha }: Pre-: Have all clothes ready well in
      advance, figure out the right place to go, plan topics of
      conversation(UIUC, what do I do, emotions on first date), square
      away logistics beforehand like parking/clean up car.  Post-:   
      
    \item \tiny Meet on Sunday : Pre-:  Post-:  
      
      - have entering / welcome figured out when you meet Pinky auntie. 
      
      - be sure to make others feel that you are in control. 
      - be aware of not saying ``Yea, I guess'' when someone says something empathetic. 
      - don't get too worked up about where to sit. - know arrangement before-hand. 
      
      - Mbe sure to be clean - bathroom, dinner table. 
      - good to show relaxation and joking about ``shotgun''.
      - bounce back after saying ``read harry potter''. Remember that Harry Potter is gen knowledge that you should know. 
      - good to have a rough point - wasn't too intense, esp. because you asked Ridhima about what it means for her. 
      - Comm: vocal variety: practice your laugh, and improve it; watch not to laugh too much. 
    \end{itemize}
  \end{block} 
\end{column} %2 
%-- Column 2 --------------------------------------------- 
\begin{column}{0.50\linewidth}
%{\textbf{\underline{Week TODO}}} 
% NOTE: Current policy is to comment out days as they come. 
% TODO: put in the regular routines here for each day, in the schedule box. 
  %--- Block 2-1

\begin{block}{ Week TODO} 

\begin{enumerate} 


\item \tiny Work: put in hypothesis for each of the applications.  + Work: put results sheet  + integrate it with allwork 1-page sheet.  \timeEst{3 hours}
\item \tiny Work: send Prof. Gropp message about transient vs. persistent load imbalance quantification. \priority{UI} - \timeEst{30 mins}. 
\item \tiny Work: send Prof. Gropp message to meet Friday at 2PM. \timeEst{20 mins} 
\item \tiny Work: get code on Blue Waters, and send update. \timeEst{10 mins} 
\item \tiny Work: identify miniFE code to change.  \priority{UI} \timeEst{30 mins}. 
\item \tiny Work: plan changes to miniFE code to change. \priority{UI}. \timeEst{30 mins}. 
\item \tiny Work: get metrics for load imbalance. 

\item \tiny Work: app code fix the problem with the per-thread lock for stealing / write-up 
\item \tiny Work: add error checks to code + Work: figure out timings. 
  for app, along with PAPI profile (dummy) and the dqIdle/time. + check flops. 
\item \tiny Work: Add code structure for data collection + Find any other systems issues and take care of them + integrate the
  slack-conscious runtime/MPI dot prod. 

\item \tiny Work: add OpenMP code transformation for different strategies ,e.g. figure out how to do staggered. 
\item \tiny Work: get timestep times. 

\tiny \item \tiny Work: clean up thesis tex file to have abstract/title. 
\tiny \item \tiny Work / Mgmt:Spaces: add in bibs from folder on MPI-shm . 

\item \tiny \doneTask{worklife: do full habits/infrastructure.} 
\item \tiny worklife: finish writeup of work infrastructure. 

\item \tiny Mgmt: Money: book sw travel for Atlanta 
\item \tiny Mgmt: Money: send check to Gary for $\$$35.35 
\item \tiny Mgmt: Money: send check to Ari for $\$$5.63 
\item \tiny Mgmt: spaces: make appt for fixing screen. \timeEst{10 mins}  
\item \tiny Mgmt: Spaces: return honda civic taillight and get new one \timeEst{10 mins}  + make notes on returning from Amazon + buying  (and returning/buying anywhere). 

\item \tiny worklife: situations for weekend travel 
\item \tiny worklife: situations for meeting Nitin Mama 
\item \tiny Work: make week plan for Aug. $18^{th}$ to August $30^{st}$ , and then Sept. $2^{nd}$ to Sept. $14^{th}$. \timeEst{1 hour} \priority{UI- partially done}.  
\item \tiny \doneTask{Mgmt: Spaces: buy laptop cover.} \timeEst{1 hour} 

\item \tiny Mgmt: Spaces: buy cover for iPhone. 


\item \tiny \doneTask{Mgmt: Spaces: order 10 iPhone 5s chargers.}
\item \tiny \doneTask{GenKnowledge: get book on genKnowledge OR read NYtimes, make habits to read .} 
\item \tiny Mgmt: Spaces: get rugs. 

\item \tiny Mgmt: Spaces: money: check sw old stuff; find iPad; update money; check money in bank. 
\item \tiny Mgmt: Spaces: Graduation: check get the Neur course checked. 

\item \tiny Work: Figure out computer (cs-grad131), and check for files/images from CS525. 



\item \tiny Work: check for sending paper to cloud computing conference/workshop. 
\item \tiny Work: (planning): look up conference for slack-conscious  - could do this later afterwards
\item \tiny Work: (planning): look up conference for vSched maybe. 
\item \tiny Work: reply to Tanzima telling her what she is saying does
  not make sense \priority{doItinAdayOrTwoButSoon} \timeEst{30 mins}.
\item \tiny Mgmt: Spaces: Graduation: send messages on Post-doc to
  Prof. Gropp about Princeton / other places + Work: check with Prof
  Gropp about the Princeton post-doc. 


\item \tiny Mgmt: money: livermore re-imbursements.

\end{enumerate}
\end{block} 

%\begin{columns}
%\begin{column}{0.5\columnwidth} 

\begin{block}{Week Daily Schedule} 
\textbf{\small \underline{Mon}}
\begin{enumerate} 
\tiny \item \tiny Mgmt: SPaces: clean-up. 
\item \tiny worklife+Comm: situations review.
\item \tiny Mgmt: time: plan out week, plan out day.  
\item  \tiny Work: go through results notes, prep for meeting. 
\item \tiny Work: perf. modeling maybe - check about impl first. 
\item \tiny worklife: get the habits right, including practice points. 
\item \tiny worklife: update spaces sheet (house) 
 
\item \tiny Comm: speech notes \timeEst{1 hour} 
\end{enumerate} 

\textbf{\small \underline{Tue}}
\begin{enumerate} 

\tiny \doneTask{Work: Add in vSched to PF3D} \timeEst{10 mins} \priority{UI}. 


\item \tiny Work: make speedup graphs for strong scaling for nbody. \priority{UI} \timeEst{25 mins.}

\item \tiny Work: add speedup graph for PF3D, with vSched. \priority{UI} \timeEst{20 mins.} 

\item \tiny \doneTask{Work: add in NAS CG code mod into poster.} \timeEst{10 mins}. 
\item \tiny Work: figure out how to get code to fit properly without showing whitespace. 

\item \tiny Work: put in write-up for results in poster write-up, structuring section \timeEst{10 mins}. 
\item \tiny Work: explain nbody in write-up. \timeEst{25 mins}. 
\item \tiny Work: add ``full'' for MPI+OpenMP snap, be sure to do comparison with full for nbody. \timeEst{10 mins}.
\item \tiny Work: Add in ``full'' to PF3D \timeEst{10 mins} \priority{UI}. 


\item \tiny \doneTask{Work: add in stencil diagram into poster.} + Work: figure out how to do stencil diagram \timeEst{10 mins}. 

\item \tiny Work: Figure out how vSched speedup scales for MPI+OpenMP nbody. \timeEst{10 mins} \priority{UI}. 
\item \tiny Work: Figure out how vSched scales for MPI+OpenMP snap - check result put in \timeEst{15 mins}. 

\item \tiny Work: create PF3D strong scale data. \timeEst{10 mins}. 
\item \tiny Work: explain CALU in write-up. \timeEst{30 mins}. 
\item \tiny \doneTask{Work: add in model for poster} \timeEst{10 mins}. 
\item \tiny \doneTask{Work: add in table for NAS benchmarks \timeEst{20 mins}} \priority{UI}. 
\item \tiny Work: add in class size S for NAS benchmarks. 
\item \tiny Work: make graph for NAS benchmarks data \timeEst{20 mins}. 
\item \tiny Work: figure out intro graphs to make in quadrant 1.  \timeEst{10 mins} 
\item \tiny \doneTask{Work: get content for strategies in quadrant 2}  \timeEst{10 mins}. 
\end{enumerate} 

\textbf{\small {\underline{Wed}}}
\begin{enumerate} 
\tiny \item \tiny Comm: Speech prep + habits. 
\item \tiny worklife: Add in spaces org 
\item \tiny work: Spaces org
\item \tiny Mgmt: search for flight 
\item \tiny Work(admin): find Prof Gropp's schedule 
\item \tiny Work: Prep for meeting 
\item \tiny Comm: Add in TM  
\end{enumerate} 

\textbf{\small{\underline{Thu}}}
\begin{enumerate} 
\tiny \doneTask{Mgmt:webpresence: check researchgate}
\item \tiny talk to ProfGropp about PACT
\item \tiny Comm: read 7 habits 1st chapter and summarize \timeEst{1 hour} . 

\item \tiny write down code snippet for each application: mini-FE, PF3D, lbm, 
\item \tiny organize all results on a page. 
\item \tiny finish mini-FE results writing for uSched, vSched, s-Sched, full 
\item \tiny finish summarizing PF3
\end{enumerate}
%\end{column}

%\begin{column}{0.5\columnwidth}

\textbf{\small {\underline{Fri}}} 
\begin{enumerate} 
\tiny \item \tiny worklife: update spaces sheets.

\item \tiny
\item \tiny Work: finish the code for NAS LU, CG
\item \tiny  Work: get it to work for HACC and other benchmarks. 
\item \tiny Work: finish related work, other stuff + Work: finish writing stuff for intro and related work. 
\end{enumerate}

\textbf{\small \underline{Sat}} 
\begin{enumerate} 

\item \tiny Work: finish going through experimentation 

\item \tiny Comm: finish with speech 

\item \tiny worklife: finish  organization, write todos 

\item \tiny worklife: Work: update Work in worklife cheatsheet. 

\item \tiny worklife: Work: update work in work page doc 

\item \tiny Mgmt: money : book hotel in Napa Valley 

\item \tiny Work: apply library code to GTC stencil 

\item \tiny Work: apply library code to Mesh 

\item \tiny Work: carefully write down model for load imbalance of reg. mesh. 


\item \tiny Work: send Prof Gropp update.\timeEst{30 mins}   + update guided sched results + 
Work: Send Simplice message and Laura a message \timeEst{20 mins} 
\item \tiny Work: create model based on results , connecting performance model to results \timeEst{1 hour} - generate rules. 
\item \tiny Work: check SNAP results \timeEst{20 mins}. 
\item \tiny Work: categorize the strategies better in the third quadrant. 
\item \tiny Work: 

\tiny \item \tiny Comm: send message to Shyunti. 
\item \tiny worklife: worklife cheat sheet update of experiences \timeEst{30 mins.} +  worklife: update practice points + worklife: update worklife implementation/habits +  worklife: finish emo intelligence notes on Empathy, and add into last part. 
\item \tiny Mgmt: Spaces: get laptop screen fixed. \priority{UI} 
\end{enumerate} 

\textbf{\small \underline{Sun}}
\begin{enumerate}
\tiny \item \tiny worklife: Time for next month 
\item \tiny Mgmt: webpresence: make final decision to delete ak from fb \timeEst{30 mins.} \priority{Urgent} 
\item \tiny Work: poster
\item \tiny Work: results:  Work: finish strong scaling for nbody \priority{UI}. +  Work: make graph (static, guided, uSched, vSched, sSched). 

\item \tiny Mgmt:webpresence: put blog post to blogger.com \timeEst{1 hr}.  
\item \tiny Mgmt: Money: California in mid-August. 
\item \tiny Mgmt: Money: figure out registration for NetIP.
\item \tiny Comm: get speech for vocal variety written up - MBA vs PhD\timeEst{1 hour}. 

\item \tiny Work: consider sending message to Prof. Grigori 
\end{enumerate} 

\end{block} 

%\end{column}
%\end{columns}

\end{column}%2 

\begin{column}{0.20\linewidth} 
%{\textbf{\underline{Reg. Routines}}} 

%Block 3-1
\begin{block}{\small \textbf{\underline{Regular Routines}} }
\underline{\textbf{Morning}}
\begin{itemize}
\tiny \item \tiny Brush Teeth \timeEst{4 mins}
\item \tiny Mouthwash, Clean tongue - it helps with breath\timeEst{1mins} 
\item \tiny Eating small breakfast
\item \tiny Check your schedule for meetings / appointments for that day: Is anything urgent? \timeEst{5 mins}
\item \tiny Excercise: 1 hour ( Stretch for 10 mins, Treadmill for 30 mins , Lift weights or Yoga 1 hour, Meditation for 10 mins)
\item \tiny Shave (at least every other day) \timeEst{5 mins}
\item \tiny Shower : (shampoo+conditioner, acne wash,  soap on underarms/underbody)
\timeEst{10 mins}
\item \tiny dry hair, dry face, arms, legs, back, stomach \timeEst{3 mins}
\item \tiny Clothing: belt, check collar, shirt not half-tucked, matching socks \timeEst{5 mins}
\item \tiny Comb hair, hair gel optional \timeEst{ 1 min}
\item \tiny Check Keys/Wallet/Cell/Badge (get a bucket) \timeEst{1 min}
\item \tiny Open meds cabinet, get water, take medicines \timeEst{1 min}
\item \tiny Wear lenses and rinse out case \timeEst{ 2 mins}
\item \tiny Deodorant or cologne depending on the day \timeEst{1 min}
\item \tiny Wash your face with a face wash - it helps with acne \timeEst{3 mins}
\item \tiny Moisturize - apply lotion \timeEst{ 2 min}
\item \tiny Neti pot / clean out sinuses - if you’re feeling congested \timeEst{5 min}
\item \tiny clean out ears, nose \timeEst{5 mins}
\item \tiny Remember to lock door \timeEst{1 mins}
\end{itemize}

\underline{\textbf{Evening}}

\begin{itemize}
\tiny \item \tiny Call family: 30 mins
\item \tiny meet friends: 20 mins
\item \tiny Cleaning dishes / cleaning house: 10 mins
\item \tiny Lay out clothes for the next day, iron if necessary
\item \tiny start laundry if needed: 10 mins,
\item \tiny Collect anything you’ll need for the next day (e.g. dry cleaning to drop off): 5 mins,
\item \tiny Check Facebook/linkedin/google+: 10 mins, matrimony stuff: 10 mins,
\item \tiny Food for lunch/dinner the next day: 10 mins
\end{itemize}

\underline{\textbf{Night before bed}}
%TODO: why isn't enumerate working???
%\begin{enumerate}
\begin{itemize}
\tiny \item \tiny Finish computer stuff \timeEst{5 mins}
\item \tiny Get into sleeping clothes \timeEst{1 mins}
\item \tiny Before sleeping: brush teeth, floss \timeEst{ 2 min}
\item \tiny Properly wash and put away contacts \timeEst{ 2 mins}
\item \tiny Review the days good things \timeEst{ 10 min}
\item \tiny Light Reading \timeEst{ 10 min}
\item \tiny Prayer \timeEst{10 mins}
%\end{enumerate} 
\end{itemize}
\end{block}

\end{column}%3 

\end{columns} 

\end{frame} 

\end{document}
