\documentclass[serif,mathserif,final]{beamer}

\mode<presentation>{\usetheme{Lankton}} 
\usepackage{amsmath,amsfonts,amssymb,pxfonts,eulervm,xspace}
\usepackage{graphicx, ragged2e}
\usepackage{pgffor}
\setbeamertemplate{caption}[numbered]

%\documentclass[11pt]{article}

\usepackage{ulem}
\usepackage{color}
\usepackage{xspace}
\newcommand{\bllt}{\item \small}
\newcommand{\doneTaskNoItem}[1]{\sout{#1}}
\newcommand{\doneTask}[1]{\item \sout{#1}}
\newcommand{\doneTaskHyp}[1]{\item \textcolor{blue} {\sout{#1}}}
\newcommand{\optTask}[1]{\item  \textcolor{green}{#1}}
\newcommand{\prioTask}[1]{\item  \textcolor{red}{#1}}
\newcommand{\timeEst}[1]{\textit{Time:} \textit{#1}}
\newcommand{\priority}[1]{\textit{Priority:} \textit{#1}}
\newcommand{\prio}[1]{\textit{Priority:} \textit{#1}}
\newcommand{\dueBy}[1]{\textit{Deadline:} \textit{#1}}
\newcommand{\MyName}{Vivek~Kale}
\newcommand{\fixme}[1]{\textcolor{blue}{[FIXME: #1]}}
\newcommand{\revision}[1]{\textcolor{blue}{[FIXME comment : #1]}}
\newcommand{\regItem}[1]{\item \textcolor{cyan}{#1}}
\newcommand{\regRoutineItem}[1]{\item \textcolor{green}{\textit{Reg. Routine:} #1}}
\newcommand{\situationItem}[1]{\item \textcolor{magenta}{\textit{Situation:} #1}}
\newcommand{\deadline}[1]{#1}
\newcommand{\comments}[1]{}

\graphicspath{{./figures/}}
\usepackage[orientation=landscape,size=a0,scale=1.6,debug]{beamerposter}

%-- Header and footer information ----------------------------------
\newcommand{\footleft}{Mgmt-WorkLife-weekPlan} % figure what this should be 
\newcommand{\footright}{June 2014}
\title{Month-Week-Day Plan} 
\author{Vivek Kale$^1$$^2$}
\institute{$^1$ University of Illinois at Urbana-Champaign \quad}  

%------------------------------------------------------------------
%-- Main Document ------------------------------------------------- 

\begin{document} 
\begin{frame}{}
  \begin{columns}[t]

    %-- Column 1 ---------------------------------------------------

% Question:  where should this be? Merged here or elsewhere? 
\comments{
    \begin{column}{0.33\linewidth} {\textbf{\underline{Month Plan for June 2014}}}
      %-- Block 1-1 
      \begin{block}{ \small Week 1: June 2 - June 9} 
        \begin{itemize} 
          \tiny \item \tiny Work: Amanda's code stuff: plan discussion with her, and do the coding.  
        \item \tiny Work: thesis organization.
        \item \tiny Work: software organization : PAPI, data sets.
        \item \tiny Mgmt: Spaces: finish off spaces from last week, make basic notes on avoiding ``generation of garbage''.  
        \end{itemize} 
      \end{block} 

      \begin{block}{ \small Week 2: June 10 - June 17 } 
        \begin{itemize} 
          \tiny \item \tiny
        \item \tiny 
          \tiny  \item \tiny Mgmt: Spaces:  make rules for reduction of garbage generation for closet spaces, reduction of garbage generation in general (might go under spaces vulnerability)
        \end{itemize} 
      \end{block} 
      
      \begin{block}{ \small Week 3: June 17 - June 24 } 
        \begin{itemize} 

        \item \tiny 
        \item \tiny 
         \item \tiny 
        \end{itemize} 
      \end{block} 
      
      \begin{block}{ \small Week 4: June 24 - July 1st } 
        \begin{itemize} 
       \tiny  \item \tiny 
        \item \tiny 
        \item \tiny 
        \end{itemize} 
      \end{block} 
    \end{column}%1 
}

%-- Column 1 ---------------------------------------------------  
\begin{column}{0.27\linewidth} {\textbf{\underline{Week Plan}}} 

  %-- Block 1-1
  \begin{block}{\textit Stresses} 
    \begin{itemize} 
      \small \item \small 
    \item \small friends of Atul's better(?)
    \item \small email -done  
 %  \item \small anger that you are below parents 
    \item \small [ find others ]
    \end{itemize} 
  \end{block} 

  %-- Block 1-2 
  \begin{block}{\textit Situations} 
    \begin{itemize} 
    \small \item \small Atul's b-party : Pre- :    Post- :   
    \item \small Hormozd's thesis defense : Pre-:  Post- : 
    \end{itemize} 
  \end{block} 

  %-- Block 1-3
  \begin{block}{\textit Habits } 
    \begin{itemize} 
    \small \item \small move feet less
    \item \small back straight 
    \item \small lips relaxed 
    \end{itemize} 
  \end{block} 

  %-- Block 1-4
  \begin{block}{\textit Clothes plan } 
    \begin{itemize} 
      \small \item \small - 
    \item \small Thursday: wear t-shirt 
    \item \small Friday: wear a blue polo shirt
    \end{itemize} 
  \end{block} 

  %-- Block 1-5
  \begin{block}{\textit Food plan } 
    \begin{itemize} 
      \small \item \small Skip meals this week to take out fat from weekend 
    \item \small Avoid snacks from Hormozd's thesis 
    \item \small don't eat too much if you go to chicago 


    \end{itemize} 
  \end{block} 

\end{column} %2 

%-- Column 2 --------------------------------------------- 
\begin{column}{0.27\linewidth}{\textbf{\underline{Daily Plan}}} 

% NOTE: Current policy is to comment out days as they come. 

% TODO: put in the regular routines here for each day, in the schedule box. 

  %--- Block 2-1

\comments{
\begin{block}{\small Monday } 
\textbf{todo} \\
  \begin{itemize} 
  \tiny \item \tiny Mgmt: Spaces: clean room 
  \item \tiny - 
  \item \tiny -
  \end{itemize} 

\textbf{schedule} 
  \begin{enumerate} 
 \tiny  \item \tiny
  \item \tiny -
  \item \tiny -
  \end{enumerate} 
\end{block} 

\begin{block} {\small Tuesday} 
\textbf{todo} \\
  \begin{itemize} 
  \item \tiny Discussion with Amanda \priority{U, quick} \timeEst{2 hours} 
  \item \tiny \doneTask{reply to Prof Gropp} \priority{U, quick} \timeEst{10 mins}  
  \item \tiny Code startup with PAPI, send message to Tanzima. \timeEst{3 hours} 
  \item \tiny Organization of code in repo. \timeEst{1 hour} \priority{IU, weighty} 
  \item \tiny Work: fix code, with graphs added \priority{quick} \timeEst{2 hours} 
  \item \tiny Mgmt: reg. routines: add in bathroom instructions again , with modifications to shower soap +  Mgmt: Spaces: Clean bathroom, organize spaces 
  \item \tiny Mgmt: Spaces: put in spaces for closet + Mgmt: Spaces: put up tags in Laundry + Mgmt: Spaces: fold laundry.  \priority{quick} \timeEst{20 mins} 
  \item \tiny Comm: send message to Divya \timeEst{30 mins} \priority{UI} 
  \end{itemize} 
  
\underline{\textbf{schedule}}\\
\begin{itemize}
\regItem{7:00AM - 8:00AM: weights}
\regItem{8:00AM - 9:00AM: regular routines for morning}
\regItem{9:00AM - 10:00AM: meeting} 
\item \tiny 
\item \tiny 
\item \tiny 
\regItem{9:30-10PM: fb social, linkedIn social, read self-improvement/comm books}
\regItem{10:00PM - 10:30PM: regular routines for night} 
\end{itemize} 
\end{block} 


\begin{block} {\small Wednesday}
\textbf{todo} \\
  \begin{itemize} 
  \item \tiny Work: Organization of code in repo \timeEst{1 hour} \priority{IU, weighty} 
  \item \tiny Work: add graphs generation to code  \priority{tedious} \timeEst{2 hours} 
    
  \item \tiny \doneTask{Work: get on BW} \timeEst{10 mins} \priority{quick} 
  \item \tiny Work: try to run a simple job on BW (need to get script) \timeEst{10 mins} 
  \item \tiny \doneTask{Work: get llnl accounts back up : talk to admins to do this, and then talk to others such as Karen, or try Tami} 
 
  \item \tiny Work: install macports (install xcode for dependency). \timeEst{20 mins} \priority{HardButMakesLifeMuchEasier} 
  \item \tiny Work: install git using macports \timeEst{10 mins} \priority{makesLifeMuchEasier} 

  \item \tiny \doneTask {Work: prep for tomorrow's meeting } 
  \item \tiny Comm: send message to Sumi 
  \end{itemize} 

\textbf{schedule} \\
  \begin{enumerate} 
    \regItem{7:00AM - 8:00AM: weights}
    \regItem{8:00AM - 9:00AM: regular routines for morning}
  \item \tiny Mgmt: Health: write down excercise routine 
  \item \tiny Mgmt: Spaces: get clean laundry ironed
    \regItem{10:00PM - 10:30PM: regular routines for night}
  \end{enumerate} 
\end{block} 



\begin{block}{\small Thursday} 
\textbf{todo} \\
\begin{itemize} 
  \item \tiny Mgmt: Spaces:webPresence: update profile pic with brother, make limited profile, add jimmy john's things \priority{U} \timeEst{30 mins}. 

  \item \tiny Work: send Prof. Gropp the notes post-meeting. \priority{U} \timeEst{1 hour} 

  \item \tiny send email to Bronis, Clea, and lc-support@llnl.gov to reactivate account. Include address, phone, affiliation. \timeEst{45 mins} \priority{IU}

  \item \tiny Work: look for post-docs (SUNY, Princeton(already looked through website of Professors), MIT, ORNL), and write on the thesis slides. \timeEst{1.5 hrs}  \priority{U, do this to show that you have a job to speed graduation up}  

  \item \tiny Work: finish related work organization \priority{UI} \timeEst{1.5 hours} 
  \item \tiny Work: find other papers, and read related work. Need 100 citations or so.  \timeEst{40 hours  - 1 week}     
  \item \tiny Work: add in modeling stuff from IPDPS2010 paper, as Prof Gropp suggested. 
  \item \tiny Work: discuss comparisons to guided. Add comparison to TBB. 

  \item \tiny Comm: attend Toastmasters at 200 W. Green Street tonight. 

  \item \tiny \doneTask{Work: get the paper .tex file for the cloud stuff. }
  \item \tiny Work: figure out conference to submit cloud to (BigData or EuroPar workshop - look for others) \timeEst{20 mins} \deadline{Wednesday} 

\end{itemize} 

\textbf{schedule} \\
  \begin{enumerate} 
    \regItem{7:00AM - 8:00AM: weights}
    \regItem{8:00AM - 9:00AM: regular routines for morning}
  \item \tiny Mgmt: Health: write down excercise routine 
  \item \tiny Mgmt: Spaces: get clean laundry ironed

\item \tiny 5:30PM - 6PM = finish summary for meeting 
\item \tiny 6:15PM - 8:00PM = toastmasters 
\item \tiny 8PM - 8:45PM = excercise 

\item \tiny 9:30-11PM = send Prof. Gropp an email update. 
\regItem{10:00PM - 10:30PM: regular routines for night}
  \end{enumerate}
\end{block}
} // end comments 
\begin{block} {\small Friday} 

\textbf{todo} 
\begin{itemize} 
\item \tiny 
\item \tiny
\end{itemize} 

\textbf{schedule}
\begin{enumerate} 
\tiny \item \tiny 9:00PM - 9:30PM  =  update profile pic with brother, add jimmy john's post.

\item \tiny 11:20AM -11:35PM = get paper and update this into thesis \timeEst{15-20 mins} 
\item 11:35PM - 12PM = send email to Bronis and Clea, with lc-support, to get accounts reactivated. \timeEst{30 mins} \priority{UI, HelpsToGetOtherThingsDone} \deadline{Friday 4PM}  

\item \tiny 12PM - 1PM  = related work organization finish, finish meeting summary, finish organization of thesis. 

\item 1PM - 2:30PM = take notes on Hormozd's thesis 

\item \tiny 10:30PM - 11:30PM = go through modeling and update this in svn -- carries over to next day.

\item 11:30PM - 12:30PM =  get code done (?) 

\item 12:30PM - 1:30AM = organize tasks for the next week.

\item 1:30AM - 2:30AM = Figure out any other worklife to be done. Make plan to finish self-improvement books on worklife(
including making inferences, depth,etc), and to incorporate into worklife doc (along with practicing etc.) 

\end{enumerate} 
\end{block}


%Block 2-3

\begin{block} {\small \textbf{\underline{Regular Routines}} }
\underline{\textbf{Morning}}
\begin{itemize}
\item \tiny Brush Teeth \timeEst{4 mins}
\item \tiny Mouthwash, Clean tongue - it helps with breath\timeEst{1mins} 
\item \tiny Eating small breakfast
\item \tiny Check your schedule for meetings / appointments for that day: Is anything urgent? \timeEst{5 mins}
\item \tiny Excercise: 1 hour ( Stretch for 10 mins, Treadmill for 30 mins , Lift weights or Yoga 1 hour, Meditation for 10 mins)
\item \tiny Shave (at least every other day) \timeEst{5 mins}
\item \tiny Shower : (shampoo+conditioner, acne wash,  soap on underarms/underbody)
\timeEst{10 mins}
\item \tiny dry hair, dry face, arms, legs, back, stomach \timeEst{3 mins}
\item \tiny Clothing: belt, check collar, shirt not half-tucked, matching socks \timeEst{5 mins}
\item \tiny Comb hair, hair gel optional \timeEst{ 1 min}
\item \tiny Check Keys/Wallet/Cell/Badge (get a bucket) \timeEst{1 min}
\item \tiny Open meds cabinet, get water, take medicines \timeEst{1 min}
\item \tiny Wear lenses and rinse out case \timeEst{ 2 mins}
\item \tiny Deodorant or cologne depending on the day \timeEst{1 min}
\item \tiny Wash your face with a face wash - it helps with acne \timeEst{3 mins}
\item \tiny Moisturize - apply lotion \timeEst{ 2 min}
\item \tiny Neti pot / clean out sinuses - if you’re feeling congested \timeEst{5 min}
\item \tiny clean out ears, nose \timeEst{5 mins}
\item \tiny Remember to lock door \timeEst{1 mins}
\end{itemize}

\underline{\textbf{Evening}}

\begin{enumerate}
\item \tiny Call family: 30 mins
\item \tiny meet friends: 20 mins
\item \tiny Cleaning dishes / cleaning house: 10 mins
\item \tiny Lay out clothes for the next day, iron if necessary
\item \tiny start laundry if needed: 10 mins,
\item \tiny Collect anything you’ll need for the next day (e.g. dry cleaning to drop off): 5 mins,
\item \tiny Check Facebook/linkedin/google+: 10 mins, matrimony stuff: 10 mins,
\item \tiny Food for lunch/dinner the next day: 10 mins
\end{enumerate}

\underline{\textbf{Night before bed}}
\begin{enumerate}
\item  \tiny Finish computer stuff \timeEst{5 mins}
\item  \tiny Get into sleeping clothes \timeEst{1 mins}
\item  \tiny Before sleeping: brush teeth, floss \timeEst{ 2 min}
\item  \tiny Properly wash and put away contacts \timeEst{ 2 mins}
\item  \tiny Review the days good things \timeEst{ 10 min}
\item  \tiny Light Reading \timeEst{ 10 min}
\item  \tiny Prayer \timeEst{10 mins}
\end{enumerate}

\end{block}

\end{column}%3 

\end{columns} 

\end{frame} 

\end{document}
