\documentclass[serif, mathserif, final]{beamer}
\mode<presentation>{\usetheme{Lankton}}
\usepackage[orientation=landscape,size=a0,scale=1.6, debug]{beamerposter}
\usepackage{amsmath,amsfonts,amssymb,pxfonts,xspace}
\usepackage{graphicx,ragged2e,pgffor}
\usepackage{hyperref}
\usepackage{ulem}
\usepackage{courier}
\usepackage{caption,verbatim,listings,float,subfig} %TODO: order these 
\setbeamertemplate{caption}[numbered] 
\usepackage{calendar}
\usepackage{geometry}

%TODO: remove unneeded items 
\newcommand{\bllt}{\item \small}
\newcommand{\doneTaskNoItem}[1]{\sout{#1}}
%TODO: consider changing the name of this macro to be what it's
%used for below
\newcommand{\doneTaskNoItemNewLine}[1]{\sout{#1}}

\newcommand{\doneTask}[1]{\tiny \item \tiny \sout{#1}}
\newcommand{\doneTaskHyp}[1]{\tiny \item \tiny \textcolor{blue} {\sout{#1}}}
\newcommand{\optTask}[1]{\tiny \item \tiny \textcolor{green}{#1}}
\newcommand{\prioTask}[1]{\tiny \item \tiny \textcolor{red}{#1}}

\newcommand{\timeEst}[1]{\textit{TimeEst:}\textit{#1}}
\newcommand{\te}[1]{\textit{TimeEst:}\textit{#1}}
%\newcommand{\t}[1]{\textit{TimeEst:}\textit{#1}} - command t already
%defined in latex, so we can't use the preceding command. 
\newcommand{\deadline}[1]{\textit{Deadline:}\textit{#1}}
\newcommand{\dueBy}[1]{\textit{Deadline:}\textit{#1}}
%\newcommand{\d}[1]{\textit{Deadline:}\textit{#1}}
\newcommand{\dl}[1]{\textit{Deadline:}\textit{#1}}
\newcommand{\priority}[1]{\textit{Priority:}\textit{#1}}
\newcommand{\prio}[1]{\textit{Priority:}\textit{#1}}
\newcommand{\pr}[1]{\textit{Priority:}\textit{#1}}
%\newcommand{\p}[1]{\textit{Priority:}\textit{#1}}

\newcommand{\MyName}{Vivek~Kale}
\newcommand{\fixme}[1]{\textcolor{blue}{[FIXME: #1]}}
\newcommand{\revision}[1]{\textcolor{blue}{[FIXME comment : #1]}}
\newcommand{\regItem}[1]{\item \textcolor{cyan}{#1}}
\newcommand{\regRoutineItem}[1]{\item \textcolor{green}{\textit{Reg. Routine:} #1}}
\newcommand{\situationItem}[1]{\item \textcolor{magenta}{\textit{Situation:} #1}}
\newcommand{\comments}[1]{}

%TODO: think of document as adding around ...
%TODO: consider changing the below so you only use the text in the
%document 
%TODO: change Week plans 

%TODO: consider putting making each frames have its own document. 
%TODO: decide where social intelligence goes. 
%TODO: decide how to separate work from life in social intelligence
%notes. 

\newcommand{\footleft}{Mgmt-WorkLife-weekPlan} % figure what this should be 
\newcommand{\footright}{Sept 2016}
%-- Main Document -------------------------------------------------
\title{Month-Week-Day Plan}\author{Vivek Kale$^1$}\institute{$^1$ University of Illinois at Urbana-Champaign}\date{\today}
%TODO: get rid of extra numbers below
\begin{document}

\begin{frame}
\begin{columns}

\begin{column}{0.5\textwidth}
\begin{block}{Projects}
%\underline{\bf Work:code: Project , Coding practice: p for interview.}
\begin{enumerate}
\tiny \item \tiny Work:code (cp.): go through C++, Work:code (cp.): go through Java + Work:code (cp.): go through OOP. 
\item \tiny Work:code (cp.): code up problems.  – 1 week.
\item \tiny Work:code (cp.): integer problems + numerics   -- 1 week. 
\item \tiny Work:code (cp.): practice mock interview problems. – 1 week. 
\end{enumerate}
{\it Schedule:} Work:code (cp.): finish bit manipulation,
%Work(cp.): review brain teasers in book, Work(cp.): Work(cp.): go
%through C++.\\ 

{\underline{\bf Project: job talk prep}}
\begin{enumerate} 
\item \tiny Mgmt:Spaces(crp): check car tailpipe +
  Mgmt:Spaces(crp):Window \te{1 hour}.
\item \tiny Mgmt:Spaces(bfa): buy things for apartment =
  Mgmt:Spaces(bfa): buy a whiteboard + Mgmt:Spaces(bfa): get a chair
  that adjusts height and folds \te{} \dl{} \pr{}. 
\end{enumerate}

{\underline{\bf Work:code: Project - Research Paper:}}
\begin{enumerate}
\tiny \item \tiny \url{http://mpp2016.ime.uerj.br}. 
\item \tiny \url{http://sbac-pad}  - registration is  500.
\item \tiny Put up latex.  
\item \tiny Gather all research. 
\item \tiny Gather project work. 
\item \tiny Write down introduction.
\item \tiny Gather data for OpenACC. 
\item \tiny Explain other details of setup. 
\item \tiny Note data for OpenMP. 
\end{enumerate} 
\textit{Schedule:} March 24th: do latex, March 2 \\
%\underline{\bf Work:rel: Project – interview with Berkeley/MIT/industry}
\begin{enumerate} 
\tiny \item \tiny Business cards:  - use latex  -- 40 minutes. 
\item \tiny Cover letter 
\item \tiny Jobs categorization for real jobs opportunities: 
Suny sb / suny sb / LLNL /  |  Intel, NVIDIA, Apple  Google/ms /
software companies, Database companies/Oracle, $\rightarrow$ real
companies. 
\item \tiny CV: + Research Summary:  -- 1 week.  - Talking about your research.
\item \tiny Work:rel: message to Yavatkar Kaka about VMWare +
  Work:rel: gather friends in network from friends about Google + Work:rel: message to contacts about Microsoft \te{} \dl{} \pr{}. 
\item \tiny Behavioral questions answers:    -- 1 week. 
\item \tiny Send emails – 1 day. 
\item \tiny Structure in latex. 
\end{enumerate}
%{\small {\it Schedule:} Behavioral answers – 1 week, CV prep - 1 day,
%business cards, cover letter -1 hour. }\\
%\underline{\bf Project: awards}
\begin{enumerate} 
\tiny \item \tiny Figure out write-up for Fulbright. 
\item \tiny Attend Fulbright : 
\item \tiny Stay in touch with HLF 
\item \tiny Do energy econ work with convergence. 
\item \tiny Go to whitehouse thing. 
\item \tiny Plan to be on Program Committee of .. 
\end{enumerate}
%{ \small \it Schedule:} April 15th: message to Stephen – 1 hour,
%Work:rel:Project – Awards: 
%\underline{\bf Mgmt:Spaces: settle on your own}
\begin{enumerate}
\tiny \item \tiny Dentist + Get dentist appointment.
\item \tiny Doctor / Counselor + CBT.
%TODO: organize and group the below 
\item \tiny Reimbursements.
\item \tiny Work pay and holidays / hours. 
\item \tiny 401k+retirement  + fidelity + bank (money owing). 
\item \tiny apartment + apartment sublease + apartment rent.
\item \tiny Flights: update flight information, e.g., credit card,
  emergency contact, passport number.
\item \tiny Flights: finish flight decision making notes, e.g.,
  justification for travel, money/airfare rules, award travel rules.
\item \tiny Change Chase address. 
\item \tiny apartment sublease. 
\item \tiny renter's insurance. 
\item \tiny xfinity and wifi accounts. 
\item \tiny ComEd. 
\item \tiny car insurance \doneTask{car parking} 
\item \tiny Car city sticker. \doneTask{Ventra card.}
\item \tiny Car: Get windows side checked + Get windows marking checked + Get tailpipe checked + Ask about warranty. 
\end{enumerate}

{\underline{\textbf{Worklife - Project – Comm:rel:}}}
\begin{enumerate} 
  \tiny \item \tiny Worklife: link management together.  
\item \tiny Worklife: link habits comm and Toastmasters. - done
\item \tiny Worklife: latex viewpoint. 
\item \tiny Comm: read social intelligence first four chapters.
\item \tiny Comm: link all comm together.
\item \tiny Worklife: get emails and texts to analyze. 
\item \tiny Worklife: figure out how to book flights and trips quickly. 
\end{enumerate}
\textit{Schedule:} Comm: read social intelligence first four chapters
and get a method to take in information – 5 hours. Comm: link comm together, worklife: latex viewpoint. Looking ahead:  \\
{\underline{\textbf{ Project: Comm}}}
\begin{enumerate}
  \tiny \item \tiny Comm: message to Mona and Leena \te{10 minutes} 
\item \tiny Comm: consider view of girl on Shaadi. 
\item \tiny Comm(ren): message to Michael :=  Comm(ren): message to
  Rishi and Chris and Amaeya about meeting. 

\item \tiny Comm: meet Gary and KD \te{10 minutes}.
  \doneTask{Comm: message to Kavita} 
\te{1 hour} \dl{Thursday} \pr{-}
      \item \tiny Comm: consider talking to Illina.
      \item \tiny Comm: talk to friends from high school.
      \item \tiny Mgmt:Spaces: plan trips. \te{-}.
      \item \tiny Mgmt:webpresence: cancel FB friend request of
        Jocelyn + Mgmt:webpresence: check other friend requests
        sent requests. \te{-}.
      \item \tiny Mgmt:Spaces(GetThingsSpring2016): get Things =
        Mgmt:Spaces(getThings): get suit. 
      \doneTask{Mgmt:webpresence: delete Anil Taneja from
        LinkedIn. \te{1 hour} \dl{Monday} \pr{UI}. - not needed since
        we met with Rishi  + Comm: may have not accepted +
        Mgmt:webpresence: bad to do so}
\end{enumerate}
{\it Schedule:} meet others over summer, meet girl over summer.\\
%TODO: figure out why this was the issue

{\underline{\textbf{Project: Comm:rel}}}
\begin{enumerate} 
  \tiny \item \tiny Comm: consider what to do about Bhavna.
\item \tiny Comm: get caught up with Matrimony and Shaadi, Use match,
  make system for meeting. 
\item \tiny Comm:rel: discuss with Mom and Dad. 
\end{enumerate} 
\end{block} 
\end{column} 

\begin{column}{0.5\textwidth}
\begin{block}{Planning} 
\comments{
{\underline{\textit{2-month plans}}}
{\underline{\textit{January and February:}}}
{\underline{\textit{March and April:}} }
{\underline{\textit{May and June:}}}
}

\begin{itemize}
\tiny \item \tiny do scheduling strategies. 
\item \tiny work on job talk. 
\item \tiny do travel. 
\item \tiny social on facebook, catch up with Rishi. 
\end{itemize} 
\begin{itemize} 
\tiny \item \tiny 2-Month Plan: December: code + worklife, January: study for interviews
\item \tiny 2-Month Plan: February: code | March:  code + interview review + finish coding work. 
\item \tiny 2-Month Plan: April: code, May: code paper review.
\item \tiny 2-month plan: June: relax July: adjust 
\item \tiny 2-month plan: August:  prep September: interview 
\end{itemize}

%\end{block}
%\begin{block}{Week-by-Week Plan}

\underline{{\bf Week of January $1^{st}$}}
\begin{itemize}
\small \item \small Charmworks:
\item \small modification to the CkLoop.  function for scheduler,
  Handler function on each PE.
\item \small staggered strategies, apply to a code.integration
\item \small EI: IOP - week 3: exposure, commitment, rumination.
\end{itemize} 

\underline{{\bf Week of January $8^{th}$:}} 
\begin{itemize} 
\small \item \small extension + more examples
\item \small IOP - week 4: exposure, exposure, rumination,   meet with
  Katie Riehman.
\end{itemize} 

\underline{{\bf Week of January $15^{th}$:}}
\begin{itemize} 
\small \item \small Work: figure out what the project is, setup accounts, etc.
\item \small Select insurance, select 401k,
\item \small Apartment hunting: - moving:
\end{itemize}

\underline{{\bf Week of January $22^{nd}$:}} 
\begin{itemize}
\small \item \small saving state.
\item \small adjust static fraction / make weights.
\item \small other
\item \small plan for someone to pick this up later.
\end{itemize}

\underline{{\bf Week of January $28^{th}$:}} 
\begin{itemize}
\small \item \small Work: finish report. 
\item \small Work: write code for cworks. 
\item \small Work:comm: message to OpenMP. 
\item \small Work: message to Prof. Gropp. 
\item \small Mgmt:Spaces: plan trip for HLF. 
\item \small Comm: message to others. 
\end{itemize}

\underline{{\bf Week of February $5^{th}$:}} 
\begin{itemize}
\small \item \small Work: do SHARP code runs + Work: make progress. 
\item \small Work: write code for cworks + WOrk: outline for paper.
\item \small Work:comm: message to OpenMP.
\item \small Work:comm: message to Prof. Gropp.
\item \small Comm: reply to people. 
\end{itemize}

\underline{{\bf Week of February $12^{th}$:}}
\begin{itemize}
\small \item \small Work: 
\item \small Work: write code for cworks.
\item \small Work:comm: message to OpenMP.
\item \small Work: message to Prof. Gropp. 
\item \small Comm: plan trip for HLF. 
\end{itemize}

\underline{{\bf Week of February $19^{th}$:}}
\begin{itemize}
\small \item \small Work: get results from SHARP. 
\item \small Work: results for code on CPU.
\item \small Work:comm: message to OpenMP. 
\item \small Work: message to Prof. Gropp. 
\item \small Comm: plan trip to meet. 
\end{itemize}

{\underline{\bf Weekend Plans:}} 
\begin{itemize}
\tiny \item \tiny Weekend of December $16^{th}$: fly to D.C., Ship car.
\item \tiny Weekend of December $23^{rd}$: meet friends in New York City.
\item \tiny Weekend of December $30^{th}$: come to Chicago. Meet Gary KD?
\item \tiny Weekend of January $3^{rd}$: I'll be in Boston.
\item \tiny Weekend of January $7^{th}$: I'll be in the D.C. Area. I'll move the remaining things from moving company.
\tiny \tiny Weekend of January $15^{th}$: I'll be in the
D.C. Area. Atul is visiting. Things from moving company will be
moved. Details: 
\begin{enumerate}
\tiny \item \tiny I'll pick Atul up from DCA. We'll stay at The W
Hotel at 515 15th St. NW in Washington, D.C. There is a banquet event
in Alexandria, VA that Atul will come with me to. I'll drop Atul to the airport on Sunday. 
\end{enumerate}

\item \tiny Weekend of January $22^{nd}$: I'll be in the D.C. Area watching the inauguration.
\item \tiny Weekend of January $27^{th}$: I may be in Marina del Rey, CA from Friday evening to Saturday evening. I'll be in D.C. from Sunday morning to Sunday evening.
\item \tiny Weekend of February $3^{rd}$: Visit San Francisco. 
\item \tiny Weekend of February $10^{th}$: Go out and meet friends again. 
\item \tiny Weekend of February $17^{th}$: Mom and Dad are coming. Visit Boston. 
\item \tiny Weekend of February $24^{th}$: 
\item \tiny Weekend of March $2^{nd}$: Stay in D.C. to work on paper. 
\item \tiny Weekend of March $7^{th}$: 
\end{itemize}

{\underline{\bf Weekend Plans:}} 
\begin{itemize}
\item \tiny Weekend of February $3^{rd}$: Visit Boston.- 
\item \tiny Weekend of February $10^{th}$: Visit New York/setup place. 
\item \tiny Weekend of February $17^{th}$: Mom and Dad are coming.-
\item \tiny Weekend of February $24^{th}$: Visit San Francisco.
\item \tiny Weekend of March $2^{nd}$: Stay in D.C. to work on paper. 
\item \tiny Weekend of March $7^{th}$:
\end{itemize}
\end{block}
\end{column} % end column f1 column 1 
\end{columns} 
% \item \tiny Mgmt:Spaces(afx): tell about the closet door.\te{}\dl{}
%   + Mgmt:Spaces(afx): tell about the bathroom. 
\end{frame} 
\begin{frame}
  \begin{columns}
    %-- Page 2: Column 1 --------------------------------------------------- 
    \begin{column}{0.25\linewidth}
      %{\textbf{\underline{Week Aspects(new name)}}}
      %TODO: check where this should go. -done  
      %--- Page 2: Block 1-1 
      \begin{block}{Routines}
        { \tiny \underline{\bf Routines:} Morning: bfast, exercise/brush,
          floss, shower (hair, eyes, ears, underarms, feet), meds, belt,
          comb hair / dishes, clean kitchen floor. |  Night: running/ put
          away dishes, clean kitchen floor / brush teeth, charge phone,
          clothes for tomorrow, contacts off.}\\
        {\tiny \underline{\bf Sunday Routines:} Routines: Experiences,week plan.}\\ 
        {\tiny \underline{\bf Weekday Routines:}}\\
        %TODO: check if weekday routines overlaps into daily routines.
      \end{block} 
      %--- Page 2: Block 1-3
      \begin{block}{Local Happiness}
        % howto:Recognize emotions / recognize (precisely) what you're
        % worried about -> methods for eliminating worry. 
        % clean out old worries, put them in pastWorries doc.  
        % remember to define precisely 
        % order from top-to bottom
        \begin{itemize} 
          \tiny \item \tiny Work: worrying about interviewing: just focus on the work. 
        \item \tiny Worrying about gal: think about talking to others. 
        \end{itemize}
      \end{block} 
      %--- Page 2: Block 1-4 
      \begin{block}{AngersAndAnxieties}
        % howto:Recognize emotions / recognize (precisely) what you're worried about -> methods for eliminating worry. 
        % clean out old worries, put them in pastWorries doc.  
        % remember to define precisely 
        % order from top-to bottom
        \begin{itemize}
          \tiny \item \tiny Anger about UP -> think about the positive
          perspective, and the original
        \item \tiny Anger about Mr. Kapoor ->  leave it
        \item \tiny Anger about a b  -> ...
        \item \tiny Issue with USC : --> things get better. 
        \end{itemize}
      \end{block}
      %-- Block 1-5
      \begin{block}{Life notes}
        \begin{itemize}
          \tiny \item \tiny Social Intelligence: 
        \end{itemize}
      \end{block}
      % howto:
    \end{column}

    %-- Column 2 --------------------------------------------- 
\begin{column}{0.5\linewidth}
  \begin{block}{Week Summary}
    {\tiny \underline{\bf Week Plan} Work: get code to run on HPCC
      systems, Work: transfer to laptop, Work:admin: discuss
      presentation, Mgmt:Spaces: get internet, 
      Work: send message to Sunita, Mgmt:webpresence: post to Sumi,
      Mgmt:webpresence: reply to Kavita, Mgmt:webpresence: reply to Comm: message to Asawari} 


    {\tiny \underline{\bf Weekend Plan:}} Get bed, Mgmt:Spaces: talk
    to Asawari, Comm: talk to
    Asawari, 

    {\underline{\bf Day trip packing list:} charger for iPhone,
      charger for laptop, car keys, underwear, black socks, shoes,
      meds, halls meds, greyhound, boarding pass, flight pass, directions to
      venue?}

    \begin{block}{Mgmt:webpresence}
      \begin{itemize} 
          \tiny \item \tiny Researchgate 
        \item \tiny LinkedIn 
        \item \tiny Twitter 
        \item \tiny website and google+ 
        \item \tiny Facebook + Whatsapp
        \item \tiny Skype.  Bluejeans. 
        \item \tiny Phone
        \end{itemize}
    \end{block}

    {\tiny {\bf Week lessons:}}
    \begin{enumerate}
      \tiny \item \tiny Win Friends/ Influence People – no one
      likes to take direct orders.
    \item \tiny Go through 7 habits.
    \item \tiny Coding problem: 
    \item \tiny Chess tips: 
    \item \tiny tm tips.
    \end{enumerate}
        {{\tiny {\bf News:}} M: dollar lower | S: 
          | E: Fallon: 
          w: washdc: {m: {43/41 s a}}  t:{ r a} {w: {21/17 s a}} {r:
            {3/-6 r a}} {f: {4/1 r a}} {sa :{15/9 r a} }
          {su: {22/9 s a  }}}
  \end{block} 

  \begin{block}{Running ToDo} % find a better name 
    \begin{enumerate} 

  \doneTask{Comm: message to Asawari := 
    Hi Asawari,
    My name is Vivek. My parents and I talked about you and they gave me
    your email address. How are you doing? Let me know if you’d like to
    chat by Skype this weekend, say Sunday at 10:00 AM Mumbai time.

    Vivek}
  
    {\bf Curr} $\rightarrow$ \\
    \tiny \item \tiny Work(setup): get git repo up + Work(setup): get
    machine access + Work(setup): get project access + Work(setup):
    set up pictures for git repo + Work(setup): put up picture for
    slack. +  Work:comm: send message about ptycholib.

  \item \tiny Work: do Cworks items = Get application with ckloop
    that’s load imbalanced Modify ckloop to ckloophybrid, where
    static section is not stolen by cores, i.e., cores do not steal
    work during execution of statically scheduled loop iterations +
    Consider additions: weighted static, locality-optimized. Bind
    cores, i.e., drone mode. Integrate with git.

  \item \tiny Work: send message about Whiteboard marker holder to
    Barbara\te{1 hour}. 

  \item \tiny Work: send message for presentation. 
  \item \tiny EI: call center in Georgetown for session. 
  \item \tiny Mgmt:Health: get ven meds from Walgreens. 
  \item \tiny Work: admin: paycheck. \te{10 minutes}. 

  \item \tiny Mgmt:webpresence: create an album for Kavita. \te{1 hour}.

  \item \tiny Mgmt:Spaces: get internet. 

\textbf{End Curr} 

  
\item \tiny Mgmt:webpresence: fb unlike Kavita’s pictures +
  Mgmt:webpresence: add pictures for Kavita + Mgmt:webpresence: fb
  like to Lagha + Mgmt:webpresence: fb like to Tanuja +
  Mgmt:webpresence: fb like to Mamta +
  \doneTaskNoItem{Mgmt:webpresence: fb like to Mugdha Joshi +
    Mgmt:webpresence: fb like to Neha Kul + Mgmt:webpresence: fb like
    to Mamta + Mgmt:webpresence: fb like to Alyssa + Comm: put a
    picture on Instagram + Mgmt:webpresence: add pictures of Kavita +
    Mgmt:webpresence: add picture of Feb. 4th dinner.  
\item \tiny Mgmt:webpresence: fb like to Shalaka. 
\item \tiny Work: message to Prof. Gropp about plan. \te{} \dl{}.
\item \tiny EI: Study materials from CBT.  \te{2 hours} \dl{Monday}.
\item \tiny Work:comm: figure out whether to add Anshu \te{1 hr}. 
  \doneTask{Comm: add Vinayak on Facebook.} 
  

    \end{enumerate}
  \end{block}
  
  % howto: the below is a routine based on the job I'm doing and the
  % circumstances I'm in. Note that this is different from routines
  % above, which is true for a long-term period of over 10 years. 
  \begin{block}{Weekly Meetings}
    \begin{itemize}
      \tiny \item \tiny IWOMP affinity meeting Thursday 7 AM PDT / 9 AM
      CDT call in: 805-639-779 pswd: places. \url{https://llnl.webex.com/llnl/j.php?MTID=m33950b76befb72c0cbc31ea2e3be720c}
    \item \tiny DEG group meeting.  
    \end{itemize}
  \end{block} 

  \begin{block}{Week Daily Schedule} %NOTE: must have a curly brace
                                %for blocks. 
    {\bf Sun:}  Comm: prep for talk, Comm: message to Asavi,
    \newline {\bf Mon:} \doneTaskNoItemNewLine{Comm: message to
      Mandar,} 
%NOTE: can't use newlines in macros easily
    \doneTaskNoItemNewLine{Comm: reply to Patricia.}
    \doneTaskNoItemNewLine{Comm: reply to Shalaka. No problem. Same here. Here's my
      phone number by the way: 217-369-7996. Feel free to WhatsApp or
      text me anytime. The weekend was good. Nice. Yeah, I like Arlington a lot. 
      I'm in Marina del Rey 
      TODO:L3: Here's my phone number by the way: 217-369-7996. Feel
      free to 8WhatsApp or text me anytime.
      TODO: L3: nice town  VS pleasant town 
    }
    \newline {\bf Tues:} Work: prep for meeting with JP, Mgmt:Spaces:
    write work, Comm: message to Asavi
    \newline {\bf Wed:}
    \newline {\bf Thur:} 
    \newline {\bf Fri:} 
    \newline {\bf Sat:}
  \end{block} 

  \begin{block}{Week Daily Schedule}
    % howto: arrange items from running todo into the below
        % sheet management document. 

    \begin{columns}
      \column{0.14\textwidth}{\small \underline{\bf Mon}}
         {\small \bf todo}\\ 
        \begin{itemize}
          \tiny \item \tiny Add in schedule
        \end{itemize} 
        \textbf{\small schedule}\\
        \begin{enumerate} 
          \tiny \item \tiny 8-9AM: Regular Routines 
        \end{enumerate}

        \column{0.14\textwidth}{\small \underline{\bf Tues}} 
        {\small \bf todo}\\ 
        \begin{itemize}
          \tiny \item \tiny Add in schedule
        \item \tiny -
        \end{itemize} 
        \textbf{\small schedule}\\
        \begin{enumerate} 
          \tiny \item \tiny 8-9AM: Regular Routines 
        \end{enumerate} 
     \column{0.14\textwidth}{\small \underline{\bf Wed}} 
        \small{\bf todo}\\ 
        \begin{itemize}
          \tiny \item \tiny Add in schedule
        \item \tiny -
        \end{itemize} 
        {\small \bf schedule}\\
        \begin{enumerate} 
          \tiny \item \tiny 8-9AM: Regular Routines 
        \end{enumerate} 

     \column{0.14\textwidth}{\small \underline{\bf Thurs}}
        {\small \bf todo} \\ 
        \begin{itemize}
          \tiny \item \tiny Add in schedule
        \item \tiny 
        \end{itemize} 
        {\small \bf schedule} \\
        \begin{enumerate} 
          \tiny \item \tiny 8-9AM: Regular Routines 
        \end{enumerate} 
     \column{0.14\textwidth}{\small \underline{\bf Fri}}
         {\small \bf todo} \\ 
        \begin{itemize}
          \tiny \item \tiny Add in schedule
        \item \tiny 
        \end{itemize} 
            {\small \bf schedule} \\
        \begin{enumerate} 
          \tiny \item \tiny 8-9AM: Regular Routines 
        \end{enumerate}
        \column{0.15\textwidth}{\small \underline{\bf Sat}}
        { \small \bf todo} \\ 
        \begin{itemize}
          \tiny \item \tiny Add in schedule
        \item \tiny 
        \end{itemize} 
        {\small \bf schedule} \\
        \begin{enumerate} 
          \tiny \item \tiny 8-9AM: Regular Routines 
        \end{enumerate}

 \column{0.15\textwidth}{\small \underline{\bf Sun}}
        {\small \bf todo}\\ 
        \begin{itemize}
          \tiny \item \tiny Add in schedule
        \end{itemize} 
            {\small \bf schedule}\\
        \begin{enumerate} 
          \tiny \item \tiny 8-9AM: Regular Routines 
        \end{enumerate}
    \end{columns}
  \end{block}
\end{column}

% ------ Page 2: Column 3
\begin{column}{0.25\linewidth}
  % ------ Block 2.3.1 
  \begin{block}{Food Plan} 
    \begin{itemize}
      \tiny \item \tiny Google Express: DHDQQJQDRFTXDM95B
    \end{itemize}
  \end{block} 
  \begin{block}{Clothes plan} 
    \begin{itemize}
      \tiny \item \tiny Monday: 
    \item \tiny Tuesday
    \item \tiny Wednesday
    \item \tiny Thursday
    \item \tiny Friday
    \item \tiny Saturday
    \end{itemize} 
  \end{block} 

  %-- Block 3-3 
  \begin{block}{Situations}
    % Summary: the below are the situations that define one
    % another.
    % Howto: Put post notes of each situation from list of previous
    % week. Put high importance situations in situationslist. 
    % Put list of upcoming situations on Sunday morning with Pre. 
    \begin{itemize}
      \tiny \item \tiny Situation: Talk with Surbhi Pre-:  Post-:   
      \item \tiny -
    \end{itemize} 
  \end{block} 
  % contingincies: 
  % Summary:
\end{column} 
  \end{columns}
\end{frame}

\begin{frame}[label=socialInt] % NOTE: Beamer poster allows labels
  \begin{block}{Jobs}
    \begin{itemize}
      \tiny \item \tiny cat1: D.E. Shaw | SUNY/BNL: applying . | IBM: applied,interviews.  | Sandia:
      applied and failed, Cray: applied and got offer, USC
    \item \tiny cat2: Intel: Applied and failed. Intel: re-application
      completed, AMD: applied, Samsung, VMWare: Contacting Yavatkar Kaka. 
    \item \tiny cat3: Google. MongoDB: applied and failed, Facebook. 
    \item \tiny cat4: LLNL 
    \end{itemize} 
  \end{block}


Demonstrate MPI scalability on ptycholib. 

Describe or publish contribution (IPDPS2018).  





































 

%TODO: check if below is needed. 
      %\item Friends: Amit, Sangita, Anchit, Kevin. 
      %Networking: 
      \begin{block}{Comm:friends} 
        \begin{itemize} 
        \item Palekar’s:  
          \begin{itemize}
          \item UP: 
          \item Rohun: 
          \end{itemize} 
        \item Bhagwat’s: 
        \item Kapoor’s: 
          \begin{itemize}
            \tiny \item \tiny Anchit: Interaction. Atul is smart. 
          \item \tiny Shuchi: 
          \end{itemize}
        \item Sudharshan’s: 
          \begin{itemize} 
          \tiny \item \tiny Amit:  
          \item \tiny Sangita:  
          \end{itemize}
        \item Kumar’s:
          \begin{itemize}
            \tiny \item \tiny Ashwin: 
          \item \tiny Shilpa: 
          \end{itemize}
        \item Saied’s: 
          \begin{itemize}
            \tiny \item \tiny Laila 
          \item \tiny Faisal 
          \item \tiny Ayesha
          \end{itemize} 
        \item Kukreti’s:
        \item Kumar’s:
        \item UIUC friends: 
          \begin{itemize} 
            \tiny \item \tiny Sadhna: 
          \item \tiny Rishi: 
          \item \tiny Amaeya: 
          \item \tiny Chris: 
          \item \tiny Brian: 
          \item \tiny Arif 
          \end{itemize}
        \item grad school friends 
          \begin{itemize} 
            \tiny \item \tiny  Karan: 
          \item \tiny Gopi: 
          \item \tiny Amanda:  
          \end{itemize}
        \end{itemize} 
      \end{block}
      
      \begin{block}{Rel} 
        \begin{itemize} 
          \small \item \small Shwetha K/r
        \item \small Shalaka 
        \item \tiny DCK girl -
        \item \small Mamta
        \item \small Avani 
        \item \small Sruthi 
          \item \small 
        \item \small SH11680694 from San Francisco. 
        \item \small Sandhya N. 22 Jun 2016 
        \item \small Aarti S - 27 - 5' 9'' Charlotte.       
        \item \small Anu M from Chicago, IL 
        \item \small Pranati A from Cleveland, OH - 
        \item \small Meghana K from New York - 
        \item \small Ssd S - 28 , 5 5 , Boston, MA 
        \item \small Anj B. - 30 yrs - SH13882555.
        \end{itemize}
      \end{block} 

\end{frame}

\end{document}
