\documentclass[12pt] {article} 
\usepackage{amsmath,amsfonts,amssymb,pxfonts,xspace}

\usepackage{graphicx, ragged2e}
\usepackage{pgffor}
\usepackage{ulem}
\usepackage{caption}
\usepackage{courier}

\usepackage{verbatim}

\usepackage[usenames,dvipsnames]{xcolor}        
\usepackage{listings}

\usepackage{float}
\usepackage{subfig}

%TODO: understand why doneTask can't have an item around it. 
%TODO: see if macros can create enumerate groups. 
%TODO: get parens to show .

\def \doneNewTask [#1][#2][#3][#4]{\small \item {\sout{\small ``#1''}\textit{TimeEst:}{``#2''}{\textit{Deadline:}{``#3''}}{\textit{Priority:}{``#4''}}}}

%\newcommand{\doneNewTask}[1][2][3][4]{\small \item 
%{\sout{\small{#1}}\textit{TimeEst:}{#2}{\textit{Deadline:}#3}{\textit{Priority:}#4}}

%\newcommand{\doneNewTask}[1][2][3][4]{\small \item
%  {\sout{\small{#1}}\textit{TimeEst:}{#2}{\textit{Deadline:}#3}{\textit{Priority:}#4}}

%\newcommand{\NewTask}[1][2][3][4]{\small \item \small {#1}\textit{TimeEst:}{#2}{\textit{Deadline:}#3}{\textit{Priority:}#4}} 

\newcommand{\bllt}{\item \small}
\newcommand{\doneTaskNoItem}[1]{\sout{#1}}
\newcommand{\doneTask}[1]{\sout{#1}}
\newcommand{\doneTaskHyp}[1]{\textcolor{blue}{\sout{#1}}}
\newcommand{\optTask}[1]{\item \textcolor{green}{#1}}
\newcommand{\prioTask}[1]{\item \textcolor{red}{#1}}
\newcommand{\timeEst}[1]{\textit{Time:} \textit{#1}}
\newcommand{\priority}[1]{\textit{Priority:} \textit{#1}}
\newcommand{\prio}[1]{\textit{Priority:} \textit{#1}}
\newcommand{\dueBy}[1]{\textit{Deadline:} \textit{#1}}
\newcommand{\MyName}{Vivek~Kale}
\newcommand{\fixme}[1]{\textcolor{blue}{[FIXME: #1]}}
\newcommand{\revision}[1]{\textcolor{blue}{[FIXME comment : #1]}}
\newcommand{\regItem}[1]{\item \textcolor{cyan}{#1}}
\newcommand{\regRoutineItem}[1]{\item \textcolor{green}{\textit{Reg. Routine:} #1}}
\newcommand{\situationItem}[1]{\item \textcolor{magenta}{\textit{Situation:} #1}}
\newcommand{\deadline}[1]{#1}
\newcommand{\comments}[1]{} 

\newcommand{\dl}[1]{\textit{Deadline:} \textit{#1}}
\newcommand{\te}[1]{\textit{TimeEst:} \textit{#1}}
\newcommand{\pr}[1]{\textit{Priority:} \textit{#1}} 

% model after a paper organization 
\begin{document} 

\underline{\textbf{ Current Work Todo}}\\
\begin{enumerate}
\tiny \item \tiny Finish last thesis chapter writing, and naming convention. 
\item \tiny Finish introduction portion in the slides. 
\item \tiny Get bw results for a single application  = ( run on machine + run on machine  + setup ). 
\item \tiny Message to Garzaran. 
\item \tiny Message to Padua. 
\item \tiny Message to Bronis. 
\end{enumerate}

\underline{\textbf{Work Todo}}\\
\begin{enumerate}
\tiny \item \tiny Finish last thesis chapter writing, and naming convention. \item \tiny Get bw results for a single application  = ( run on machine + run on machine  + setup ). 
\end{enumerate}

\underline{\textbf{Work:Mgmt Todo}}\\
\begin{enumerate} 
\item that's this page! 
\end{enumerate} 

\underline{\textbf{Work:Impl/ActiveDocs Todo}}\\
\begin{enumerate} 
\item \tiny \texttt{thesis/researchQuestionsAndData.tex}
\item \tiny \texttt{scheduleForThesis.tex}
\item \tiny \texttt{combinedScheduling/techniques.tex}
\item \tiny \texttt{combinedScheduling/results.tex}
\item \tiny \texttt{plots/nbody-craybw.dat}
\item \tiny \texttt{plots/Snap-craybw.dat}
\item \tiny \texttt{plots/fe-craybw.dat}
\item \tiny \texttt{plots/imb-final.tex}
\end{enumerate} 

% All tasks for work should go here 
% Break down each task into smaller tasks. Each small task should be
% 30 mins  
% Do each small task fully and to completion (don't leave behind any 
% parts) 
% Prioritize tasks (order based on urgent and important) 
% Have six tasks going each day
% break down into even smaller tasks in paper 
% add tasks that are generated from tasks here 

\underline{\textbf{Work:Pres Todo}}\\
\begin{enumerate}
\item fix transition at the beginning. \te{20 mins} \dl{by lunch} 
\item clean up transitions at the latter parts \te{} \dl{} 
\item \doneTask{Work: pres: Fix chapter 1 organization, make it
  clean.}  \te{1 hour} \dl{Sunday} \pr{U} 
\item \doneTask{Work: Make sure logical flow is maintained for chapter
  1.} \te{} \dl{} 
\item \doneTask{Work: finish thesis chapter 1 writing = Work: finish 
idle time calculations and graphs \te{1 hrs} \dl{}  +  Work: write the
outline. \te{1 hrs} \dl{-} + Work: do naming \te{2 hrs} \dl{} + Work: put in
figures properly \te{1 hrs} \dl{-}

\item \doneTask{Finish chapter 1 to check for remaining holes.} \te{}
  \dl{} \pr{} 
\item \doneTask{Work: add graphs for last chapter.} \te{4 hours}
\item \doneTask{Work: pres: Get synchronization overheads graphs.} 
\item \doneTask{Work: pres: update slides for Prof. Gropp.  = Work:pres: add 
load imbalance data at the end. + Work: pres: consider table at the end.} 
\te{1 hour} \dl{Christmas} \pr{UI}.

\item Work: pres: write out amplification explanation = ( work:pres:explanation of amplification connected to nbody / spmv  +  explanation of amplification in theory) \te{1 hour} \dl{1 hour} \pr{-}

\item Work: pres: refine the avg/max explanation by getting to the 
 point for thesis \dl{} \te{} \pr{}

\item Work: pres: finish fixing structure  \dl{} \te{} \pr{}
\item Work: pres: refine inevitability of problem for cache misses. =
  (Think about probability argument + Formalize better )  \te{} \dl{}
  \pr{}

\item Work: pres: show inevitability of problem for synchronization 
overheads = (Refine explanation of serialization overheads)  \te{} \dl{} \pr{}

\item \doneTask{Work: pres: show inevitability of problem for idle
  times = (Work: find example  for increasing idle time   + Work: find
  slack example)}  \te{1 hr} \dl{} \pr{-}. 

\item \doneTask{Work: pres: fix how to say it for the first chapter.}
  \dl{} \te{} \pr{}

\item \doneTask{Work: fix the last summary paragraph.} 
\item \textbf{curr $\rightarrow$} \\
\item \doneTask{Work: fix the transient vs persistent paragraph} \te{}
  \dl{} \pr{}
\item \doneTask{Work: add intro to last chapter \dl{Sat}
  \pr{SoonToGetACompleteProduct}} \te{1 hour}
\item \doneTask{Work: fix description in last chapter} \te{1 hour}
  \dl{Sat}\pr{lowerButImportantBeforeSendingOutSoNoOneGetsConfused}.

\item \doneTask{Work: (cm): get data sheet}
\item \doneTask{Work:(cm): and find cycle time}
\item \doneTask{Work:(cm): do calculation and find total data movement time \te{} \dl{}.}

\item \doneTask{Work:(cm): explain the parts that might be off.} \te{}\dl{}

\item Work:(cm): explain \textit{half} scheduling for nbody in terms of cache misses. 

\item Work:(Naslu): fix NASLU cache misses times.
\item Work:(NASLU): explain why original numbers were wrong.
\item Work:(NASLU): verify that measurements are correct with new cache
misses for NASLU. 
\item Work:(NASLU): go into cache miss table for NASLU and edit + Work:(NASLU): find way to get total cache misses for NASLU. 

\item Work:(cm): explain that more trials for n-body PAPI cache misses
 for dynamic scheduling may be needed to explain the differences also.

\item Work:(cm): explain that we should take the maximum instead of average
for n-body PAPI cache misses. 

\item Work: fix comments for chapter 2 \te{--} \dl{Sat} \pr{--} 

\item Work: bring in slack data in problem statement of hybrid 
scheduling, and don't repeat it. \te{} \dl{} \pr{}. 

\doneTask{Work:admin:/ Mgmt:Money: re-imbursements.}

\item Work: make descriptions in last chapter easy to read, 
i.e.,L3:howtosayit revision. \te{1 hour} \dl{Sun} 
\pr{lowerButImportantBeforeSendingOutSoNoOneGetsConfused}.

\item Work: check naming of terms = check for consistency + check for goodness 
  \te{} \dl{} \pr{}.

\item Work: make better title for last chapter \te{5mins}\dl{Mon}\pr{}

\item Work: Make sure naming of overhead and cost is consistent 
throughout last chapter and rest of thesis + Work: Make sure
distinction between noise event length vs. imbalance due to noise 
is consistent throughout last chapter and rest of thesis \dl{} \pr{}
\te{}.
\item Work: add graphs for last chapter (adg) = 
  Work:(adg): add graphs for rzuseq on nbody \te{} \dl{} + 
  Work (adg): add graphs for weighted scheduling for each 
  graph\te{} \dl{} \pr{}.
% may be needed
% for dynamic scheduling may be needed to explain the differences
% also. 
\item Work: put in data set for spatial locality to explain problem in
  staggered static/dynamic. 
\doneTask{Work: Comm: Send Padua message about defense} \te{10 mins}\dl{}\pr{EasyAndGetItDoneQuickly}.
\doneTask {Work: Comm: Send Bronis to let him know about the defense.} \te{20 mins} \dl{Sunday} \pr{IU}. 
\item Work: Comm: Contact for jobs. 

\item Work:(cme): explain cache misses to measurements for half for 
  n-body + Work(cme): explain cache misses to measurements \textit{besf} for n-body. 

\doneTask{ Work: add in slides for all tasklets.} \te{} \dl{} \pr{} 

\doneTask{Work: write slides for explaining skewed tasklets.} \te{} \dl{} \pr{}. 

\item Work: Make notes on figures for slack. \te{} \dl{} \pr{}. 

\item Work: Make notes on figures for spatial locality. \te{} \dl{} \pr{}. 

\item Work: finish writing the beginning of chapter 2 intro.  \te{} \dl{} \pr{}.  (Note:Break this down further).

\item Work: finish writing the explanation for figure about tasklet size \te{} \dl{} \pr{}

\doneTask{Work: do explanation for histograms scaling}  \te{} \dl{} \pr{}

\item Work: pres: write out amplification explanation = ( work:pres:explanation of amplification connected to nbody / spmv  + explanation of amplification in theory)\te{1 hour}\dl{1 hour}\pr{-}

\end{enumerate}

%\underline{\textbf{Work:should have}}\\ 
%\begin{enumerate} 
%\item Work: results: add in the result on topology \te{1 hours}  \pr{IU-ProfGroppExpectedThisAMonthBack}
%\end{enumerate} 

\underline{\textbf{Work:Nice To have}}\\
\begin{enumerate}
\optTask{do model for static fraction for persistent load imbalance, add
  this in the last chapter.} 
\item Work:Mgmt: update the schedule to show for yourself, and to show
  to Prof Gropp \te{} \dl{} \pr{}
\item Work: add relevant related work in intro and in literature 
survey to improve justification (arr) \te{30 mins} \dl{Wednesday}
\pr{ProfGroppToldToDoThisAndItHelpsToStrengthen}. 
\item Work:(arr): add STREAM benchmark citation when you mention the
bulk-synch code + Work:(arr): add STREAM benchmark. 
\item Work:(arr): add green work steal explanation in the
  conclusions. 
\item Work:(arr): discuss desktop computing benefits to improve
  Excel. 
\item Work:(arr):add senstrom citation when you mention coherence
  cache misses. 
\end{enumerate} 

\end{document} 
