%\def\PRES{1}
%\ifx{\PRES}
%\iftoggle{\PRES}

\begin{frame}{Week Plan} 
Work:cci: update code from taskq + Work:cci: review 11 code problems, Work:rsr: do paper writeup, Mgmt:Spaces: do travel expenses stuff, Work: rel: update LLNL research statement, Work:rel: bump email to Kathryn, Work:rel: send email to Olga, Work:rel: send email to Bronis and Kathryn, Work: review coding material, Comm: message to Toni, Comm: reply to Aditi about meetup. 
\end{frame} 
\begin{frame}{Running To Do - 1}
%\else
%\fi
\begin{enumerate}
\item \textbf{Curr} $\rightarrow$
 \item Work: finish draft paper for SC19. \te{1 hour} + [] Work: update lw-sched code to support Fortran. \te{30 minutes} + [] Work: do writing for IWOMP 19 paper problem statement and technique.
 \item Work: update startup draft. \te{50 minutes} 
 \item Work:comm: explain software contributions.
 \item Work: review software engineering course from Columbia.
 \item Work: explain knowledge of tools like git and cmake. 
 \item Work: rel: email to Bronis. +  [] Work: message to Tony Baylis. \te{10 minutes}. + [] Work: message to Olga about ParaDis + [] Work: message to Tony Baylis. 
\item Work:rel: update application for Rutgers. \te{20 minutes}. 
\item Work:rel: finish software overview in application. \te{30 minutes} + Work:rel: update for comments. 
\item Work: job talk update = Work: update task locality slides +  Work: add Work: add locality-sensitive scheduling to thesis part + Work: add cloud computing to thesis. 
\item Work: send message to Barry about merging adagio with slack trace.
\item Work: coding problems. 
\item Work: rel: send message to Tony to get access to HPC facilities. 
\item Mgmt:Spaces: get dentist appointment check. 
\item Mgmt:wp: update linkedIn with message about coding and github.
\seti 
\end{enumerate}
% \ifx{\PRES}{1}
\end{frame}
% \else 
 % \fi
 
% \ifx{\PRES}{1}
\begin{frame}{Running To Do (2)} 
%  \fi 
  \begin{enumerate}
    \conti
\item Mgmt:Spaces: get psychology sessions taken care of +  EI: Study materials from CBT.  \te{2 hours} \dl{Monday.}
\item Mgmt:Spaces: get the reimbursement for car's warranty. 
\item $\leftarrow$ \textbf{End Curr}
\item  Mgmt:Spaces: get citi bank account + Mgmt:Spaces: get refund from AA  + Mgmt:Spaces: get the bumper bully. 
  
\item Work:comm: figure out whether to add Anshu \te{1 hr}.
\item  Work: update book summary + Work: update movie summary. 
\item  Work: update website. 
  \end{enumerate}
  %\ifx{\PRES}{1}
\end{frame}
