%!TEX root = mgmtSlides.tex

%howto: this document contains the situations and mgmt infrastructure
%for each level.  

% link to wl-mgmt-slides 

% link to wl-cheatsheet: shows structure of each part, whereas
% wl-cheatsheet is showing L4 and some L3.   

% integrate tm here

% cube with different dimensions, including experiences : L2  

% situations list L0+ L1  


%TODO: fix the pdflatex compiler. 


%TODO: add slides on the regular routines 

% TODO: do regular routines timings 

% TODO: add notes on regular routines 

% TODO: add worries notes 

%TODO: add in stuff on dishwashing 


% TODO: add diagrams here 


% TODO:  add tm here 
% TODO: add experiences at bottom


%TODO: add notes on mgmt 


%TODO: Put in notes about social intelligence

%TODO: figure out where static goes 
 
%TODO: fix minima explanation 
%TODO: think about a new graph for static fraction 
%TODO: split explanations of graphs in first slides, into separate graphs 
%TODO: get different noise graphs. 
%TODO: figure out explanation for histogram graphs. 
%TODO: figure out rebound code that maps to heartbeat sim. and show that here.  
%TODO: make sure that rebound code works in terms of mapping to heartbeat  (check with someone) 
%TODO: ensure naming consistent besf.

%TODO: worklife: see how you can connect different levels ..


%Ridhima : honda cr-v 
% dad: acura rlx 
%vivek: bmw 3

\begin{frame}
\frametitle{Overview} 
\begin{enumerate} 
\item Work 
\item Mgmt
\item Comm 
\end{enumerate} 
\end{frame} 

\begin{frame} 
\frametitle{Mediums to Use to Do Slides}
\begin{itemize} 
\tiny \item \tiny  
\item \tiny 
\end{itemize} 
\end{frame}

\begin{frame}
\frametitle{Routines: Introduction}
\end{frame} 

\begin{frame}
\frametitle{Monthly Regular Routines \te{1 hour} } 
{ \small Change lightbulbs, change batteries of remote control, bills,
  medicines, clean car and oil change, haircut}
\end{frame}

\begin{frame} 
\frametitle{Change lightbulbs}
\te{20 minutes}
\begin{itemize} 
\small \item \small check available lightbulbs. \te{5 minutes}  
\item \small buy needed lights \te{10 minutes} 
\item \small Screw lightbulb \te{10 minutes} 
\end{itemize} 
\end{frame} 

\begin{frame} 
\frametitle{Clean Car} 
\te{1 hour 30 minutes} 
\begin{enumerate} 
\small \item \small Wheels \te{20 minutes} 
\item \small Outside: \te{45 minutes} 
\item \small Inside: \te{25 minutes} 
\end{enumerate}  
\end{frame} 

\begin{frame} 
\frametitle{Remote Control batteries}  
\end{frame} 

\begin{frame}
\frametitle{Weekly Regular Routines \te{1.5 hours}}
{\small Bring in Newspaper, Take out trash, clean fridge, clean microwave,
grocery, laundry, fold+iron clothes, fill gas, check wallet, water plants.}
\end{frame}

\begin{frame}
\frametitle{Grocery} 
{\small Time Estimate 1 hour}  
\begin{itemize}
\tiny \item \tiny Milk 
\item \tiny Bread 
\item \tiny Perrier water
\item \tiny Clif Bars 
\end{itemize} 

\end{frame} 

\begin{frame} 
\frametitle{Clean fridge} 
\te{5 minutes} 
\begin{itemize} 
\small \item \small clean door handles.
\item \small Clear out any ice. 
\item \small Organize shelves (make organization). 
\item \small Change filter. 
\end{itemize}
\end{frame}

\begin{frame} 
\frametitle{Clean microwave}
\te{5 minutes} 
\begin{enumerate} 
\small \item \small Clean buttons 
\item \small Clean front
\item \small Put water and microwave for five minutes. 
\item \small Take out plate
\item \small Clean top, left, right, bottom, inside of door.
\item \small Wash plate. 
\item \small put plate inside of microwave. 
\end{enumerate} 
\end{frame}

\begin{frame} 
\frametitle{Garbage} 
\te{10 minutes}  
\begin{itemize} 
\tiny \item \tiny Take garbage bags into trash can. \te{3 minutes} 
\item \tiny Put recycling into recycle bin (includes taking paper out)
  \te{3 minutes} 
\item \tiny Put garbage bin outside. \te{1 minute}
\item \tiny Put recycling bin outside. \te{1 minute} 
\item \tiny Put new garbage bags. \te{1 minute} 
\item \tiny Take garbage back in. \te{ 1 minute} 
\end{itemize} 
\end{frame} 

\begin{frame}
\frametitle{Laundry} 
\te{10 minutes} 
\end{frame}   

\begin{frame} 
\frametitle{Iron Clothes} 
\te{20 minutes} 
\end{frame}

\begin{frame}
\frametitle{Clean laptop and iPhone}
\te{10 minutes} 
\begin{enumerate} 
\small \item \small Clean laptop screen 
\item \small clean keyboard 
\item \small Clean outside of laptop 
\item \small clean out iPhone screen 
\end{enumerate} 
\end{frame}

\begin{frame}
\frametitle{Clean Room} 
\te{20 minutes} 
\begin{itemize} 
\item \tiny Vaccuum floor 
\item \tiny Dust desk 
\end{itemize} 
\end{frame}

\begin{frame}[label=routinesOverview]
\frametitle{Routines overview\te{1 hour} } 
{\small a. Morning: exercise | brush, floss, shower (hair, eyes, ears, neck,
underarms, feet), meds, belt, comb hair / dishes, clean kitchen
floor. | Night: running / put away dishes, clean kitchen floor /
brush teeth, charge phone, clothes for tomorrow, contacts off, situations. }
\end{frame} 

\begin{frame}[label=routinesBrush]
\frametitle{Teeth - 5  minutes}
           {\small When to do: Once in morning, once at night.\\}
           \begin{enumerate} 
             \small \item \small Brush (1 minute): do the following for 5 seconds.             
             \begin{itemize}
               \tiny \item \tiny Top front outer
             \item \tiny Bottom front outer
             \item \tiny Top left side outer 
             \item \tiny Bottom left side outer
             \item \tiny Top right side outer
             \item \tiny Bottom right side outer
               \tiny \item Top front inner
             \item \tiny Bottom front inner
             \item \tiny Top left side inner
             \item \tiny Bottom left side inner
             \item \tiny Top right side inner
             \item \tiny Bottom right side inner
             \end{itemize} 
           \item \small Floss (1 minute) 
           \item \small Mouth wash (20 seconds)
           \end{enumerate} 
\end{frame}

\begin{frame}
\frametitle{Health: allergies}
\textbf{Every morning:}
\begin{enumerate}
\small \item \small Gargle: 5 mins 
\item \small Neti pot: 10 mins 
\item \small Blow nose(with one finger): 10 mins 
\item \small Avoid sniffing: keep tissue with you. 
\item \small drink warm tea: 5 mins
\end{enumerate} 
\end{frame} 

\begin{frame} 
\frametitle{Breakfast and lunch prep} 
{\small Time Estimate: 20 minutes  
When: morning
How: don't overcook}
\begin{enumerate} 
\small \item \small Tea: WaterAndSugar:85/TeaBag:15/Milk:15 
\item \small Breakfast: Cereal , or Oatmeal
\item \small medicines 
\item \small watch boiling water. 
\item \small Put milk back in fridge 
\item \small wash dishes 
\end{enumerate}
\end{frame}

\begin{frame}
\frametitle{Fill DishWasher}
{\small Time Estimate: 10 minutes \\ 
When: clean at night , empty in morning \\
How: don't put too much soap, don't put dishes facing up, put plastics \\
on top, organize the plates to fit\\ } 
\begin{enumerate}
\small \item \small plates and bowls \te{2 minute}
\item \small bowls and mugs \te{2 minutes} 
\item \small Large cooking dishes \te{3 minutes} 
\item \small Spoons \te{3 minutes}
\end{enumerate}
\end{frame} 

\begin{frame} 
\frametitle{Empty Dishwasher} 
\te{7 minutes}
When: morning 
How: Ensure dishes are clean. 
\begin{itemize} 
\small \item \small Top dish .
\item \small Bottom dishes. 
\item \small silverware.
\end{itemize} 
\end{frame} 

\begin{frame}[label=kitchenClean ]  
\frametitle{Clean up kitchen} 
Time Estimate: 7 minutes  
When: morning 
How: Ensure dishes are clean. 
\begin{itemize} 
 \item \small Clean counter.
\item \small Sweep floor. 
\end{itemize}
\end{frame}

\begin{frame}[label=exercise] 
\frametitle{Exercise}
\begin{itemize} 
\tiny \item \tiny Time Estimate: 30 minutes  
\item \tiny When: morning 
 \item \tiny How: pushups and butt alternate days 
\end{itemize}

\begin{enumerate} 
\small \item \small Meditation. 
 \item \small Stretch. 
\item \small Pushups 
\item \small Running at night. 
\end{enumerate} 
\end{frame}

\begin{frame} 
\frametitle{Clean up room}
\te{2 minutes} 
\begin{itemize}
\small \item \small Make bed. 
\item \small Straighten pillows.  
\item \small Straighten sheets. 
\end{itemize} 
\end{frame}

\begin{frame}[label=shower] 
\frametitle{Shower} 
\te{12 minutes}
\begin{enumerate} 
\small \item \small Wet body. 
\small \item \small Put on shampoo.
\item \small Shaving cream + Shave(sides, under, chin, moustache, vuln: mouthsides, mouthtop, belowlip, underneck) 
\item \small Eyes + Ears + Neck 
\item \small Put body wash underarms 
\item \small Feet wash. 
\item \small Wash underarms again 
\item \small Conditioner. 
\item \small Put shaving stuff back. 
\item \small Clean out shower. 
\item \small Wipe the sink and counter. 
\end{enumerate} 
\end{frame} 

\begin{frame}
\frametitle{Dry yourself +Aftershower} 
\te{6 minutes} 
\begin{enumerate} 
\small \item \small Dry yourself. 
\item \small comb / hair spray. 
\item \small Iron clothes needed. 
\item \small socks. 
\item \small underwear. 
\item \small wallet and keys in left + cell right + belton+pantshigh. 
\item \small watch. 
\item \small lotion. 
\item \small concealer. 
\item \small undershirt / shirt / tuck shirt in / check collar/ check mirror. 
\item \small Tie shoes. 
\end{enumerate}
\end{frame}

\begin{frame} 
\frametitle{Emails + Planning} 
\te{20 minutes} 
\begin{itemize}
\item \tiny Read emails + send emails urgent.  
\item \tiny Make daily plan. 
\item \tiny Time Estimates, Prioritize and schedule day. 
\end{itemize}
\end{frame} 

\begin{frame}
\frametitle{Garage cleaning} 
\end{frame}

\begin{frame}[label=dinnerPrep]
\frametitle{Dinner}
\te{15 minutes}
\begin{itemize} 
\small \item \small Water, plates, bowl, spoons 
\item \small chew food while eating. 
\item \small table topics. 
\item \small clean up = put dishes in sink + rinse dishes 
\item \small find container for pots
\item \small put container in fridge, make sure fridge is closed. 
\item \small put pots in container. 
\item \small start dishwasher.  
\item \small clean table. 
\end{itemize} 
\end{frame} 

\begin{frame}
\frametitle{Before bed}
\te{20 minutes}
\begin{itemize} 
\small \item \small send any remaining less urgent emails 
\item \small Charge phone. 
\item \small Charge laptop.  
\item \small write down situations. 
\item \small read comm book. 
\end{itemize} 
\end{frame} 

\begin{frame}
\frametitle{Clean up office desk} 
\end{frame} 

%TODO: see in section is important  .  Could replace with proper
%intro. 
\begin{frame}
\frametitle{Car Maintenance records} 
\begin{itemize} 
\small \item \small Settings update, e.g., 
\item \small Other updates, e.g., 
\item \small Spark plugs change. 
\item \small Oil change. 
\end{itemize} 
\end{frame}

% TODO: add in stuff from implementation sheets in wl sheet into
% here. 

\begin{frame}[label=worryElimination]
\frametitle{AngersAndAnxieties}
\end{frame} 

\begin{frame}[label=CBTcomm] 
\frametitle{ CBT } 


From: \url{rshuster@chicagocbtcenter.com}
{\small I look forward to connecting with you. My direct contact (cell) is 812-219-5059. Will try giving you a call this evening. 
Hi Vivek,
Glad we were able to speak today. 
Here are my recommendations: } 

\begin{enumerate}
\tiny \item \tiny  DASC (Dr. Rodney Benson)
\url{http://www.dascchicago.com/Clinical-Staff.html}  Depression and
Anxiety Specialty Clinic of Chicago 3047 N. Lincoln Ave Suite 400 +
233 E. Erie St. Suite 706 Serving Lakeview Since 2005 773-494-5505
\item \tiny The Family Institute (Dr. Renay Gartner, if available)  \url{http://www.family-institute.org/affordable-counseling} 
\end{enumerate}

{\small Also, I've attached the paperwork I mentioned to help guide the
conversation re: insurance benefits. Can let me know if you have
questions. Warmly}

\end{frame} 

\begin{frame}
\frametitle{Ecological Intelligence} 
\end{frame} 

%\input{/Users/vivekkale/Desktop/ViveksLaptop/Work/pres/statdyn/thesis/content_researchQuestionsAndData}

\comments{
\begin{frame}
\frametitle{Overview: Work}
\begin{enumerate}
\item Work: code 
\begin{itemize}
\item  research
\item  Work: mathematics - computer science-engineering fundamentals
\end{itemize} 
\item Work: pres
\item Work: admin
\item Work: comm  
\end{enumerate}
\end{frame}
}

%NOTE: label can't have dash or underscore in it
\begin{frame}[label=ovviewGenknow]
\frametitle{Overview: Work, general knowledge}
\begin{enumerate} 
\small \item \small algorithms and data structures. 
\item \small logic and programming . AI
\item \small operating systems. 
\item \small machine structures . 
\item \small specialization. 
\end{enumerate}
\end{frame} 

\begin{frame}
\frametitle{ Writing a check }
{\small Routing number is one with :}  \\ 
{\small Account number is one with :- }
\begin{enumerate} 
\small \item \small Use the lines to guide writing of the check. 
\item \small Write the name in large letters 
\item \small Sign your name carefully, making sure it's smaller than recipient, but not too small. 
\item \small Write the date on the line, making sure it isn't different from the other parts. 
\item \small Write in small handwriting the memo.
\item \small Add account numbers at top. 
\item \small Put amount carefully 
\item \small Practice writing amount in english once, and then write
  it.  Make sure that line strike is neat, but a bit hasty is fine.

\item \small Generally, write quickly and confidently, while also trying to be smooth. 
\end{enumerate} 
\end{frame}
%TODO: think about which folder the fundamentals should go in - should
%it be in the content research questions and data? 
%\input{/Users/vivekkale/Desktop/ViveksLaptop/Work/pres/statdyn/thesis/content_researchQuestionsAndData} 

\input{/Users/vivekkale/Desktop/ViveksLaptop/Work/pres/fundamentals/content_fundamentals} 

\begin{frame}[label=cvrEPFL]
\frametitle{Cover Letter for EPFL}

\end{frame}

\begin{frame}[label=jobsList]
\frametitle{Jobs} 
{\small To get a prioritized list, we show from least feasible to most
  feasible and easiest to start from clean slate to hardest. It also
  prioritizes easiest to develop yourself to hardest.} 

\begin{itemize}
\tiny \item \tiny BNL: 
\item \tiny DBD
\begin{itemize} 
\tiny \item \tiny D.E. Shaw. 
\item \tiny Yahoo, GS, Salesforce. 
\item \tiny Google: 
\end{itemize}
\item \tiny broad national labs. 
\begin{itemize}
\tiny  \item \tiny PNNL or LBNL: 
\end{itemize}
\item \tiny Academia.
\begin{itemize} 
\tiny \item \tiny Stanford 
\item \tiny MIT Media 
\end{itemize}
\item \tiny Research focused jobs 
\begin{itemize}
\tiny \item \tiny  LLNL or Google
\item \tiny Palantir. 
\end{itemize}
%\end{enumerate}
\end{itemize}

\begin{itemize}
\tiny \item \tiny would be good to end up at LLNL long-term. 
\end{itemize}
\end{frame}

\begin{frame}[label=persVisionStatement]
\frametitle{Personal Vision Statement}
\begin{outline}[enumerate]
\tiny \1 {\tiny Identify past successes.}
\tiny \2 {\tiny Developed low-overhead loop scheduler. }
\tiny \1 {\tiny Identify Core values.}
\tiny \2 {\tiny Problem-solving.} 
\tiny \1 {\tiny Develop a list of attributes that you believe identify who
  you are and what your priorities are.  } 
\tiny \2 {\tiny decision-making.} 
\tiny \2 {\tiny friendly.}
\tiny \2 {\tiny outgoing.} 
\tiny \2 {\tiny positive.}  
\tiny \2 {\tiny family-oriented.}
\tiny \1 {\tiny Identify Contributions. }
\tiny \2 {\tiny Develop software, write code.} 
\tiny \2 {\tiny be good at programming.} 
\tiny \2 {\tiny teaching.}
%- to be a modern thinker. 
%- to lead by example and demonstrate how innovative and
%- problem-solving work. 
%- products can be both successful in terms of solving a problem and
% successful in terms of profitability and revenue generation for the
% organization.  
\tiny \1 {\tiny Identify Goals.}
\tiny \1 {\tiny Write Mission Statement. }
\tiny \2 {\tiny To learn continuously} 
\tiny \2 {\tiny To become better communicator. } 
\tiny \2 {\tiny To master coding skills} 
\end{outline}
\end{frame} 

\begin{frame}[label=groppUpdate]
\frametitle{Paper}
\begin{outline}
\tiny \1 {\tiny Intro:}
\tiny \1 {\tiny How are you doing?}
\tiny \1 {\tiny Harshitha and I submitted paper that I told you about
  in an email on March $24^{th}$.} 
\tiny \1 {\tiny Paper didn't get accepted.} 
\tiny \2 {\tiny Submitted paper.}
\tiny \1 {\tiny Results.}
\tiny \2 {\tiny Work on BW.} 
\tiny \1 {\tiny What's next}
\tiny  \2 {\tiny HiPC 2017} 
\end{outline} 
\end{frame}

\begin{frame}[label=groppUpdate] 

\begin{outline} 

\tiny \1 {\tiny Intro: } 
\tiny \1 {\tiny I'd like to add you as a co-author for the paper.} 
\tiny \1 {\tiny The paper will be about .. } 
\tiny \1 {\tiny The paper will be about.  } 
\tiny \1 {\tiny Would it be ok if I add you as co-author for this
  proposal? I'd like to get your input for the work.} 


\end{outline} 

\end{frame} 

\begin{frame} 


\begin{frame} 
\frametitle{} 

 Work: writeup with ecp.
Are you interested in making a big impression during the first 5 years
of your career? The Early Career Program is designed to equip
participants for significant contributions in their new careers by
building skills related to obtaining funding, identifying publishing
venues, establishing long-term mentor relationships, and effectively
managing their time. Sessions will be held in a workshop format on the
Monday before SC starts to allow participants to enjoy the full
technical program. In addition to formal presentations, there will be
time for peer mentoring, a chance to meet 4-5 potential long-term
senior mentors (called speed mentoring), and an organized lunch for
informal networking. Selected participants will be granted a workshop
pass in order to participate in the program. The peer mentoring, speed
mentoring, and networking lunch are only open to selected
participants. However, most of the sessions will be open to all SC
workshop attendees. The program is intended for people in their first
five years of a permanent position (assistant professors, and members
of the technical staff -MTS). Post-docs will be considered on a space
available basis. Members from nontraditional fields (i.e. art,
humanities, social science, etc.), women, underrepresented
racial/ethnic minorities, and persons with special needs are
particularly encouraged to apply.


\end{frame} 



\frametitle{Mission Statement} 

 To master coding skills, to become better
 communicator, and maintain friendships and relationships, and 
to learn continuously.
\end{frame} 

\begin{frame}
\frametitle{Pro/Con}
\url{http://www.forbes.com/sites/trudysteinfeld/2013/02/11/how-not-to-screw-up-a-job-offer/#4b7c55b9455d}
Ideal Job: 
Decision factors: 
Current advsisors: Bronis , Todd , Prof. Gropp,     Maria, Padua,
dad. 
Advice from advisors : gropp:  bnl   maria: usc    abid/claire:
crago: grant, \$130 k 
Columbia / Princeton 
Future: work in industry , be connected to science, work with gail
kaiser - professor /researcher.  
BNL:  
Chapman OpenMP -connected with Bronis   Ada Palatnik Abid 
Brookhaven - near IBM 
connected with others -
Pro:  
Con: 
- LLNL opinion about you if something goes wrong,

USC: 
connected to California , in D.C. , network with who?  
Pro: 

- less known  

Con: 
-   
Wake up in the morning:
\end{frame}  


%TODD: think of a better frame title here.
\begin{frame} 

\frametitle{Email to JP and Steve from ISI} 
Hi JP and Steve, 

The issue I have is that my belief that the work I've done
during my thesis shouldn't die off. I've spent a lot of time on the research and
feel people should pay attention to it. I think I should pay attention
to the research and make sure it goes in the right direction. 
The work at the national lab is with someone who is an expert in the
area of my research focus during my thesis. I have
an opportunity which I think is in that direction.  

On the other hand, I think there are several new opportunities at
ISI. 

I'm hesitant because I won't get to make my own direction and be supervised by
a direction.

Vivek

My advisor's urge made me want to do that.  

I feel that I'm letting go of such an opportunity right now.  

This is the issue I have right now. 
The reason that I asked for an extension is due to the time it took
for the labs to get back to me and the time. 



%At the same time, I'd like to be a good researcher, software
%developer, learn new things. 

% - and maybe forget about the research I've
%invested time in for a good career.  
%I feel that this job 

I'll need to do the work that's focused 
on the project and your direction.  

The issue has to do with the work that I'll be doing. 

I don't mind this actually. I think it's a good fit, but I'm giving up some of the research that
I'd like and want to do.  


At the same time, I want a job where I'll develop my skill set. 

I've also been talking to the people from National laboratories for some time. 

At the same time, my mind has shifted a bit in the last month or so to
doing something different than what I've done in the past and to
grow. 

I see that this position has many unknowns. This is something that
makes me uneasy. I'm open to taking on challenges like this, but the
other job

I'll need to write my own grants. 

\end{frame} 




\begin{frame} 

\frametitle{ Follow-up on an interview request} 





\end{frame} 



\begin{frame} 
\frametitle{Ask for a paper}

Dear Dr. Chandrasekaran,

I'm a PhD graduate. My dissertation involved OpenMP loop scheduling
strategies for scientific applications.

I saw the paper reference 

Rengan Xu, Sunita Chandrasekaran, Xiaonan Tian, Barbara Chapman, `An
Analytical Model-based Auto-tuning Framework for Locality-aware Loop
Scheduling', TO APPEAR - In Proceedings of the International
Supercomputing Conference (ISC), Frankfurt, Germany, 2016

on your faculty webpage while searching the web for other information.

I'd like to read the paper. I can't obtain a copy of the paper from
the web. Can you please send me a copy of the paper if possible?

Vivek

\end{frame} 
y
TODO:past: spoke to abid, no contact with Prof. Chapman, 

TODO:L3:intent: get contact   tell you  send me a copy 
TOdo:L3:outcome: meet , talks to Prof Chapman, sends a copy 



TODO:L3: subject: Copy of paper


TODO:L4->2.5: to understand the strategies used.  VS [OMIT] v  just:
say the relevance in opening -done 

TODO:L4->2.5: noticed an entry for VS noticed 

todo:l4: involved v vs workrd ib VS studied  just: keep it simple ,
low-key  -done 
TODO:L4 -> 2.5: other information v VS another topic  just: makes
sense because previous is information  -done 
todo:l4: if possible,  VS , if possible  just: avoid qualification,
keep logic  -done  
TODO:L5: Sunita VS Dr. Chandrasekaran v  just: be professional , -done 
TODO:L5: Hi VS Dear,v just:  formal setting, first time met,  -done  
TODO:L5: of Professor Gropp VS [OMIT] v  just: not needed for cred.   
TODO:L4-> 2.5: recent  VS [OMIT] v VS 2015 -done just: she can look me
up , not relevant to case for getting paper. 
TODO:L4->2.5: and dissertation  VS . My dissertation 

TODO:L4->2.5:  paper v VS publication  -done 
TODO:L4: copy of paper .   

TODO:L4: the web for other information v VS searching the web for
other information. just: follows 5 ws -done 


TODO:L4: saw v VS noticed  just: keep it simple -done 

TODO:L4: I'd seen VS I saw  just: past in one point in time  -done 


TODO:L4: entry for the paper VS copy of the paper VS reference  v 
just: reference is another  


curr->

TODO:L0: \decision/ : send or not.  
Pro:  
- get  attention 
- show confidence 
Con: 
-  unneeded attention   -- need
- can add awkwardness  -keep alive is important 

TODO:L3:intent: get back in the game  - get a paper 

TODO:L6/L0: I'm a former student of Professor Gropp.  


TODO:L0: I can't obtain the paper on the web. VS [OMIT] 




TODO:L4: send ... to me VS send me v  just: keep it simple, not  ,
follows 5 w's, checked online ,   send me object  -done 

TODO:L5: please VS [OMIT] just: be kind -done 
TODO:L5->L0: Thanks! VS [OMIT] 


TODO:L4: send in morning  VS send now v just: send now to get
attention for SC , 
TODO:L4: delete notes text -done 

\end{frame} 

\comments{
Hey, I'm back but 

Yeah.
I'm in Champaign-Urbana for the weekend.

TODO:L2: I'm in Vs  -newPara- I'm in v  -done 
TODO:L3: intent: 
TODO:L4: this VS for the v -doen 
TODO:L4/L5:  Yeah v v VS I'm back. -done 
TODO:L4 (L2/L3?): period VS no period  
}

\begin{frame}
  \frametitle{Work: admin for Graduation}
  \begin{itemize}
    \tiny \item \tiny Order regalia:  get waste measurements. 
  \item \tiny Register for commencement :  extra emails to confirm that you have registered. 
  \item \tiny Work:admin: Send email to Prof. Gropp about
    commencement-hooding, 
  \item \tiny Deposit thesis to department. 
  \item \tiny Deposit thesis to grad college. 
  \end{itemize}
\end{frame}  

\begin{frame}
  \frametitle{Emails to Companies}
  \begin{itemize}
    \tiny \item \tiny Google.
  \item \tiny Jump Labs. 
  \item \tiny Post-doc summer: 
  \end{itemize} 
\end{frame} 

\begin{frame} 
\frametitle{ } 

\end{frame} 

\begin{frame}[label=iw15papoutline]
\frametitle{Paper for IWOMP2015} 
\begin{outline}[enumerate]
\tiny \1 {\tiny -.} 
\tiny \2 {\tiny -.}
\tiny \2 {\tiny -.}

\tiny \1 {\tiny -.} 
\tiny \2 {\tiny -.} 

\end{outline}
\end{frame} 

%TODO: paper on load imbalance from class.
%TODO: look at low-overhead scheduling - over-decomposition idea.
%TODO: consider GPGPU fraction.

\begin{frame}
\frametitle{Paper on performance optimizations with GPUs}
\begin{outline}[enumerate]  
\tiny \1 {\tiny Need support for optimizing/porting CPU MPI
  code to GPU OpenACC code.} 
\tiny \2 {\tiny - .} 
\tiny \2 {\tiny - .}  
\tiny \1 {\tiny - Performance suffers when non-parallel optimizations
  not considered. } 
%Tools are necessary for performance optimization of
% code.  Performance model is needed. 
%TODO: break down into smaller pieces of experimental setup, etc. 
\tiny \1 {\tiny - Experimental setup.}
\tiny \2 {\tiny - Data set for functionized vs. non-functionized
  version of code for stencil on Keplar for stencil.} 
\tiny \2 {\tiny Data set for functionized vs. non-functionized on
  Keplar for full app.} 
\tiny \1 {\tiny -  Tools are necessary for performance optimization of
  code.} 
\tiny \2 {\tiny -  .} 
\tiny \2 {\tiny -  .} 
\end{outline}
\end{frame} 

\begin{frame}
\frametitle{Near-term goals essay}
\end{frame}


\begin{frame}
\frametitle{Heidelberg Laureate Forum Essay 2015}
{\tiny This defines the long-term goals, which is explained in the Heidelberg essay}.\\ 
\begin{outline}[enumerate]
\tiny \1 {\tiny Intro: Long term goals and how this forum helps. } 
\tiny \2 {\tiny Define Long term goal : offer a novel perspective or 
new exemplar technology in the area of mathematics or computer
science.} 
\tiny \2 {\tiny By being selected for the forum (and subsequently
  attending it), I will be able to better accomplish this goal in
  three ways.} 
\tiny \1 {\tiny I can learn from the experts about future trends in technology, which will help me navigate .} 
% Experts who know past trends, can help predict future
% trends and how areas of specialization will be affected.} 
\tiny \2 {\tiny Understanding of how future trends can impact what I am doing.}
\tiny \2 {\tiny Experts who know past trends. How will quantum
  computing impact?} 
\tiny \1 {\tiny Attending forum will help me strengthen basis of PhD 
  research (from which my career will follow). Mathematicians point of view. } 
\tiny \2 {\tiny New ways of formulating the problem will fill gaps (improve ? strengthen? collabs..), if any. %TODO: consider
                                %theoretical .. but is ok. 
}
\tiny \1  {\tiny Broader impact to field of computer science. } 
\tiny \2 {\tiny  Implications of Scheduling to Cloud?} 
\tiny \1 {\tiny Conclusions: Attending will give well-grounded ,
  well-rounded viewpoint to help me pursue(achieve) long-term goals.} 
\end{outline}  
\end{frame}


\begin{frame}
\frametitle{Heidelberg Laureate Forum Essay 2018}
{\tiny This defines the long-term goals, which is explained in the Heidelberg essay}.\\ 
\begin{outline}[enumerate]
\tiny \1 {\tiny Intro: Long term goals and how this forum helps. } 
\tiny \2 {\tiny Define Long term goal : offer a novel perspective or 
new exemplar technology in the area of mathematics or computer
science.} 
\tiny \2 {\tiny By being selected for the forum (and subsequently
  attending it), I will be able to better accomplish this goal in
  three ways.} 
\tiny \1 {\tiny I can learn from the experts about future trends in technology, which will help me navigate .} 
% Experts who know past trends, can help predict future
% trends and how areas of specialization will be affected.} 
\tiny \2 {\tiny Understanding of how future trends can impact what I am doing.}
\tiny \2 {\tiny Experts who know past trends. How will quantum
  computing impact?} 
\tiny \1 {\tiny Attending forum will help me strengthen basis of PhD 
  research (from which my career will follow). Mathematicians point of view. } 
\tiny \2 {\tiny New ways of formulating the problem will fill gaps (improve ? strengthen? collabs..), if any. %TODO: consider
                                %theoretical .. but is ok. 
}
\tiny \1  {\tiny Broader impact to field of computer science. } 
\tiny \2 {\tiny  Implications of Scheduling to Cloud?} 
\tiny \1 {\tiny Conclusions: Attending will give well-grounded ,
  well-rounded viewpoint to help me pursue(achieve) long-term goals.} 
\end{outline}  
\end{frame}


\begin{frame} 

\frametitle{ECP SC17} 

????Funding: understanding the agencies, funding instruments and
strategies for securing research funding;
????Publishing: understanding the landscape of conference, journal and
other publication venues including getting involved in conference
leadership or journal editorship;
????Mentorship: understanding the difference between a mentor and a
sponsor and establishing effective, long-term mentoring and sponsoring
relationships;
????Time management: striking a balance between our professional and
personal responsibilities and obligations.



I explain the long term goal and how this program benefits towards
meeting my long-term goal. 

\begin{outline}[enumerate]
  \tiny \1 {\tiny  Introduction} 
    \tiny \2 {\tiny In the next five years, I????d like to publish work in
      HPC, work with application programmers to improve performance of
      applications and fund a project, i.e., show that I can continue to
      do good work given skills and research from my PhD and knowledge.}  
    \tiny \2 {\tiny Being selected at the forum, I????ll be able to
      accomplish my five-year goal in three ways. } 
    \tiny \1 {\tiny First, I????ll learn about the state of the art in
      my field by learning about publishing. }
    \tiny \2 {\tiny For example, I'll understand the broader landscape
    of conferences outside my area that I haven't thought of before.} 
    \tiny \2 {\tiny For example, I'll understand how to find
      conferences for my research area that I haven't thought of by
      talking with presenters.} 
    \tiny \1 {\tiny Second, I????ll learn funding agencies relevant to my
      research.}
    \tiny \2 {\tiny For example, I'll learn the agencies that are
      interested in work that solves a particular problem, within
      which my HPC technique solves the problem.} 
    \tiny \2 {\tiny Relevant because I don't get this in a job.}
    \tiny \1 {\tiny Third, I'll learn about sponsorships and
      mentors.} 
    \tiny \2 {\tiny I've had mentors and want to make more based on my
    research.}
    \tiny \2 {\tiny I'd like to make sponsors.}
    
    \tiny \2 {\tiny For example, I could learn from lectures how to 
      find good sponsors and mentors.}
    \tiny \2 {\tiny I'd know who the right sponsors to look for are.}
    \tiny \2 {\tiny For example, talking about managing time by
      comparing notes will give assurance that I'll do things well.}
\end{outline}


\end{frame} 



\begin{frame}
\frametitle{Reference Letter for Heidelberg Forum by Gropp} 
\begin{enumerate} 
\tiny \item \tiny 
\item \tiny 
\end{enumerate} 
\end{frame} 


\begin{frame} 
\frametitle{SC17 ECP program} 

\begin{outline}[enumerate]
\tiny \1 {\tiny  } 
\tiny \1 {\tiny Good attendance at SC17. }
\tiny \1 {\tiny Clear that I want to continue with HPC. I want to maintain contacts. } 
\tiny \1 {\tiny The field of HPC has many programmers. I'd like to talk about tools that others use to solve problems quickly.} 
\tiny \1 {\tiny I'd like to have mentors in the field. Mentors with experience will be important. I'd like to work with people in labs in particular. } 
\tiny \1 {\tiny I'd like to learn how to publish continually. This may involve working with application programmers having a need to improve their code. }
\tiny \1 {\tiny I'd like to attend to develop myself and prepare myself for the next few years of productive career in HPC.}
\end{outline}


\end{frame} 


\begin{frame}
\frametitle{Reference Letter for Heidelberg Forum by Cappello}
\begin{outline}[enumerate]
\tiny \1 {\tiny Intro:}
\tiny \2 {\tiny Intent of Letter.}
\tiny \2 {\tiny Knowledge of Vivek and relationship to Vivek}
\tiny \2 {\tiny My credentials, and who I've worked with.}
\tiny \1 {\tiny Problem definition}
\tiny \2 {\tiny Just doing MPI+OpenMP process/thread not good enough}
\tiny \2 {\tiny Additionally, load imbalance problem across cores.}
\tiny \2 {\tiny Bulk-synchrony needed for applications to be correct.}
\tiny \2 {\tiny Many applications are loosely synchronous, so impact of solving this is high.}
\tiny \1 {\tiny Vivek worked on solving the problem for MPI+pthread
  reg. mesh code and CALU.} 
\tiny \1 {\tiny He then worked on additional techniques such as weighted. } 
\tiny \1 {\tiny With this, he was awarded a Lawrene Fellowship, where
  he worked on slack-conscious scheduling. } 
\tiny \1 {\tiny Recently, he returned to work with Simplice to show
  how combining scheduling techniques can be beneficial. This was
  published in SC} 
\tiny \1 {\tiny Conclusion}
\tiny \2 {\tiny Critical problem currently, and fundamental to
  computer science. Problem will remain as long we need supercomputing
  for advancements in science and engineering, and thus solution will
  still be relevant.}
\tiny \2 {\tiny Already established strong contacts; benefit from
  Heidelberg through interactions contribute to discussions}
\tiny \2 { My highest recommendations} 
\end{outline} 
\end{frame}

\begin{frame}
\frametitle{Cover Letter Outline} 
  \begin{outline}[enumerate] 
    \tiny \1 {\tiny Interested.}
    \tiny \1 {\tiny Long-term: patterns, teaching, research. I'd like teach.}
    \tiny \1 {\tiny I'm also interested in performance modeling and theoretical analysis. I'm aware of several good researchers a surrounding universities. This is why I'm inclined to takethe position or another position that comes up.}
    \tiny \1 {\tiny Applying to other places.}
    \tiny \1 {\tiny Let me know if you have updates.}
  \end{outline}  
\end{frame} 

\begin{frame}
\frametitle{Email to Jump Labs}
\end{frame}

\begin{frame} 
\frametitle{Email to Google} 
% Don't overpromise too much in the letter 
\begin{outline}[enumerate]
\tiny \1 {\tiny Lawrence Scholar.} 
\tiny \2 {\tiny What it was: Selective Fellowship, Had to work in
  California.}
\tiny \2 {\tiny What I did:} 
\tiny \3 {\tiny Worked on Software }
\tiny \3 {\tiny Worked with Senior Software Engineers}  
\tiny \3 {\tiny Talked to Scientists} 
\tiny \3 {\tiny Furthered my Research}
\tiny \2 {\tiny Why it's relevant:  } 
\tiny \3 {\tiny Formed basis for research}
\tiny \3 {\tiny Software Engineering Experience.}
%TODO: consider more on ... 
\tiny \1 {\tiny INRIA Saclay Visiting Research Position } 
\tiny \2 {\tiny What it was: }
\tiny \3 {\tiny Visited lab under supervision of expert in numerical
  linear algebra and guidance of my advisor, and worked with my
  collaborator. Sponsored by Jointlab at Illinois. (give more details
  on merits, what it is?).}
\tiny \2 {\tiny What I did:}
\tiny \3 {\tiny extended the research in terms of applying the method
  to make it work for other applications and other architectures.    } 
\tiny \3 {\tiny extended the research to in terms of theoretical
  analysis, to further improve the scheduler's performance. --} 
\tiny \2 {\tiny Why it's relevant:}
\tiny \2 {\tiny highlights the type of research I want to do.}
\tiny \2 {\tiny Performance Modeling and theoretical analysis can be
  applicable to and is relevant to the position I have applied to.} 
\end{outline}
\begin{itemize}
\tiny \item \tiny -
\item \tiny -
\end{itemize}
\end{frame} 

\begin{frame}
\frametitle{Email about DOE Positions}
\end{frame} 

\begin{frame}
\frametitle{Resume}
\end{frame}

\begin{frame}
\frametitle{Email to SUNY sb} 
\begin{itemize} 
\tiny \item \tiny 
\item \tiny 
\end{itemize} 
\end{frame} 

\begin{frame} 
\frametitle{Email to PNNL }
\end{frame} 

% Hold on to maturity dad stick mercedes.

\begin{frame}
\frametitle{Google Interview}
\begin{itemize} 
\tiny \item \tiny Go through the MPI+pthreads code, write down everything about
data structures from this (highlight data structures from the slack
code). 
\tiny \item \tiny Review Quals information. 
\item \tiny Review work from quals. 
\item \tiny Review google interview material. 
\item \tiny Work: comm: do coordination and setup for interview. +
  Work: mgmt: planning for before and after + Work: mgmt: planning for
  before and after. 
\end{itemize} 
\end{frame}


\begin{frame}[label=engPubs]
\frametitle{What engineering and computing publications do you read, if any?}
MIT Technology Review
HPCWire.com
\end{frame} 

\begin{frame} 
\frametitle{Follow-up email after not hearing back} 
 Interested.
 Long-term: patterns, teaching, research. I'd like to teach. 
          I'm also interested in performance modeling and theoretical
          analysis. I'm aware of several good researchers at
          surrounding universities. This is why I'm inclined to take
          the position or another position thatcomes up.
          Applying to other places.
          Let me know if you have updates.
\end{frame}


\begin{frame} 
\frametitle{Work}
Dear John,

I'm interested in knowing whether you have an update regarding my
application.

To review, I like the idea of using my experience with performance tuning 
for shared memory programs to the compiler-centric work in your
group. Broadly, I'm interested in a career involving performance improvement of
parallel programs, and this job fits well with that.

Please let me know the status when you can. 
Vivek

Long-term, the position will allow me to gain expertise in writing
production-level tools which can then be applied to a technical-heavy
position or a research position afterwards.
% I'd like to apply my work of hand-tuned loop transformation 
% performance tuning strategies. 
% Within production-level software. 
I would also incorporate other optimizations within the OpenMP
compiler.

I'm interested in knowing the outcome. 
Past: interview
Point: You should know i'm the one for the job.
Outcome: make a positive decision. 
\begin{itemize}
\tiny \item \tiny I found the work atmosphere challenging. I think
this challenging atmosphere can help to grow myself.
\tiny \item \tiny Background in research in HPC and scientific
computing, specifically scheduling for load imbalanced codes on 
clusters of SMPs. 
\item \tiny Apply my work of hand-tuned MPI+OpenMP performance tuning strategies within production-level software. I would also
  incorporate other optmizations within the OpenMP compiler.
\item \tiny The position also fits my objective of getting experience with
compilers rather than performance tuning for HPC workloads.
\item \tiny Experience in coding and software, but also not losing a
  foot in research. This position gives me these things. 
\end{itemize} 
Action Item: Please let me know if you have updates when you have a
chance. 
\end{frame} 

\begin{frame} %TODO: think of a better generic instantiation. 
\frametitle{Company ``x'' Cover Letter}
%Think win-win .
%explain what they have, then explain what you have. 
\begin{itemize}
\tiny \item \tiny Attended D.E. Shaw Research information session,
specifically learned about Anton and Molecular dynamics. 
\tiny \item \tiny Background in research in HPC and scientific
computing, specifically scheduling for load imbalanced codes on
clusters of SMPs.

\item \tiny Goal: apply my work in the context of molecular dynamics 
on specialized hardware. Also, write publications to develop myself,
where DE Shaw seems to be a good place for me to do so. 
\item \tiny Action Item: Please see my resume attached to get more
  information about my skills and experiences. 
%  I would be interested in a job that I can further
%  research in, write additional papers in, and learn more about. Given
%  D.E. Shaw's specialized hardware, I would be particularly interested
%  in applying my algorithmic strategies in the context of load
%  imbalanced codes such as molecular dynamics 
%apply my skills in. 
\end{itemize} 
\end{frame}
% Notes: don't give away too much about research.  

\begin{frame}
\frametitle{Company x Appl. Ques.: most sig. accomplishment}
{\tiny Please describe what you consider your most
significant accomplishment as a hardware/software architect, design
engineer, or researcher.}
\begin{enumerate}
\tiny \item \tiny CALU performance gains over DPLASMA codes and over a
highly optimized code. 
\item \tiny This was significant for my research since it showed the
  potential of our methods for bulk-sychronous codes. 
\item \tiny  This also was important because these are within a large
  class of applications. 
%\item \tiny Library was designed with the help of expert software
%  engineers. 
%\item \tiny It is a systematic methodology which allows for good
%  software development. 
\end{enumerate} 
\end{frame}

% TODO: 


\begin{frame}
\frametitle{Requesting time for access to accounts}
{\small Application for access to USC compute resources. }
\begin{outline}[enumerate]
\tiny \1 {\tiny Context and Goal} 

\tiny \2 {\tiny Context: need to better understand behavior of
  Integrated Circuits(IC)/computer chips technology to make
  advancements IC technology.} 
\tiny \2 {\tiny Goal: Construct an image to simulate operation of
  integrated circuit. } 
\tiny \3 {\tiny The following requirements for image reconstruction are needed: Real-time feedback during imaging, use of x-ray sources, establish highly reliable program.}
\tiny \1 {\tiny Project Methodology: How will you proceed? What kind of data or software will you use or install?} 
\tiny \2 {\tiny Use Ptychography technique to generate a 2D image and
  then use tomography to combine the 2D images to 3D images.}
\tiny \2 {\tiny Data and Software:}
\tiny \3 {\tiny software: Ptycholib for constructing ptycholib algorithms.}
\tiny \3 {\tiny For data for doing experimentation, we'll use Argonne's advanced photon source.}
\tiny \1 {\tiny Justification: (How will HPC use improve your results and help acheive your goals)}
\tiny \2 {\tiny Ptychography is computationally intensive with FFTs. }
\tiny \2 {\tiny GPU resources allow for throughput computing and will help improve 
efficiency of our simulations.}
\tiny \2 {\tiny interconnect network of cluster will help to improve
  efficiency of FFT algorithms.}
\tiny \2 {\tiny The improvements in efficency can help with doing more
  scientific calculations per second so as to allow for achieving high
  resolution images and satisfying the
  three requirements described in the response of the prompt Project
  Methology.} 
\end{outline} 
\end{frame} 

%TODO: make the below into 3 simple points , with strucutre 
\begin{frame}
\frametitle{Letter For Travel Research Support} 
\textbf{\small Explain what you Did for Graduate Studies}\\
{\tiny Goal: convince people to give money for travel, because you are
committed to research. }
\begin{enumerate}
  \tiny \item \tiny Problem: Load imbalance inhibits efficient
  execution of scientific applications on supercomputers. 
\item \tiny To correct this, across-node load balancing can be used.  
\item \tiny However, with the rise of multi-cores, within-node load balancing becomes
  particularly important. 
\item \tiny Within-node load balancing is challenging because doing so
  reduces data locality, which itself degrades performance.  
\item \tiny Worked to help scientists improve performance of their
  codes by using a low-overhead scheduling scheme, a type of load 
  balancing scheme. 
%\item \tiny Novel because across-node balancing exists, but not 
%  within-node imbalancing. In within-node load balancing, it's important to
%  maintain locality if one is to improve performance. 
%  This is challenging because of the contradictory goals of balancing
%  load across cores and maintaining data locality. 
\item \tiny Wrote paper to show benefits for CALU, tuning . 
\item \tiny Developed library for applicability to other
  applications such as Heartbeat simulations. 
\end{enumerate} 
\end{frame} 

\begin{frame}
\frametitle{Explanation of How Work Fits Workshop} 
\begin{outline}[enumerate] 
\tiny \1 {\tiny My research involves performance optimization of
  scientific applications on supercomputers. Unlike physics, 
  this research is done by few people around the world.}
\tiny \1 {\tiny Going to Shlosberg Helps for international
  collaboration to enrich my area of research.} 
\tiny \1 {\tiny Given the focus of both mathematics and computer
  science, this opportunity helps for collaborations with
  mathematicians, which are the primary domain experts of the
  technology that I build.}
\end{outline}
\end{frame} 


\begin{frame}
\frametitle{Summary of Work in Travel Grant}
{\tiny My thesis goal is to develop specialized dynamic multi-core
  scheduling strategies to improve scientific application performance.
  It's novel. This is challenging because of the contradictory goals
  of balancing load across cores and maintaining data locality. A
  basic technique I developed was called hybrid static/dynamic
  scheduling that combines the benefits of OpenMP static and OpenMP
  dynamic scheduling. We demonstrated benefits on CALU. I developed
  multiple scheduling strategies that are variants of this idea, which
  are useful in different contexts. The performance benefits of the
  strategies developed were demonstrated on supercomputers and
  clusters on up to tens of 1000s cores, to help improve performance
  of scientific applications.}
\end{frame} 

\begin{frame}
\frametitle{Job Talk Interview}
\textbf{Explain what you did for Graduate Studies}
{\tiny My thesis goal is to develop specialized dynamic multi-core scheduling
strategies to improve scientific application performance. This is
challenging because of the contradictory goals of balancing load
across cores and maintaining data locality. A basic technique I
developed was called hybrid static/dynamic scheduling that combines
the benefits of OpenMP static and OpenMP dynamic scheduling. I
developed multiple scheduling strategies that are variants of this
idea, which are useful in different contexts. The performance benefits
of the strategies developed were demonstrated on supercomputers and
clusters on up to tens of 1000s cores.}
\end{frame} 

\begin{frame} 
\frametitle{Code Experience}
C: 8 years :  40000 - grad school
C++:  3 years :  12000 - grad school 

Python: 2 :  2500 - school 

Perl:  1: 500  

VHDL: 0.5: 1000 - course 
Awards: 
\end{frame} 

\begin{frame}
\frametitle{Company x Application Question: Project Description}
{\tiny What were the sizes (in terms of number of lines of code, number of
gates, etc.) of the two to four largest designs you've worked on? If
the applications were group projects, what percent of each project was
your contribution? What programming languages were used? Briefly
describe the purpose and functionality of each project.}
\begin{enumerate}
\tiny \item \tiny uSchedFordmf: This was a project done in collaboration with
  INRIA-Saclay. We started on our own, and then worked together on the
  code.  
\begin{itemize}
\tiny \item \tiny 9000 lines of code. 
\item \tiny C.
\item \tiny Purpose: Provide a way to improve dense matrix
  factorizations, an important class of computation used in 
  simulations like the design of an airplane wing. It also was a way
  to show how numerical linear algebra computations, each used for
  different sets of applications, could be improved. 
\item \tiny Functionality: To obtain the performance gains, we provide a guide and instructions for creating
  scheduling strategies to help improve performance. The application
  programmer first parallelizes the code using pthreads. They then add
  schedulers directly to application code.  
\end{itemize}
\item \tiny OpenMP runtime. 
\begin{itemize} 
\tiny \item \tiny 30000 lines of code (and may grow further). 
\item \tiny C for runtime. 
\item \tiny It was a project led by my supervisor. 100\% of the
  project was my contribution.
\item \tiny Purpose: Helps to ultimately save money to do
  science, by improving performance of their code on large
  systems. This library was developed to help for a general class 
  of applications and not just for numerical linear algebra. 
\item \tiny Functionality: Improving performance is done by providing a
  library which consists of different within-node scheduling strategies to make
  their code handle a mixture of load imbalances during application 
  execution. The application programmer inserts one of 
  the scheduling strategies into their code. Using these directives
  provided by the library, the programmer combines different
  schedulers, and then experimentally tries different parameter values
  for the scheduling strategies to get the best performance. 
%Several scheduling strategies are in the library, and the user can insert
%  their own also. 
% The scheduling library allows for 
% This was developed as a standalone project,
% but actually sits as a component within the above runtime. 
\end{itemize} 
\item \tiny Slack-conscious low-overhead scheduling runtime. 
\begin{itemize} 
\tiny \item \tiny 40000 lines of code. 
\item \tiny C++ for runtime. python for plotting and to gather application performance statistics.
\item \tiny It was a group project. About 80\% of the project was my
  contribution. The remaining part was done with the help of Todd Gamblin,
  my mentor at Lawrence Livermore National Laboratory. 
\item \tiny Purpose: Provide a runtime for people to use my 
  low-overhead loop scheduling techniques. since manual tuning of is
  hard.
% runtime for people to use my
%  low-overhead scheduling techniques. 
\item \tiny Functionality: Obtaining performance gains is done through
  an initialization function of the application and performance 
  tuning for the initial parameters for the scheduling strategy used
  and 2. functions to predict the scheduler parameters during
  runtime.  The initialization of the scheduler parameters is done
  using a wrapper function within the MPI runtime. The ROSE compiler
  places these calls at appropriate places in
  the code. The user invokes a function call before the threaded 
  computation region of the code.
  %This predicts the best scheduler
  %parameters to use that will maximize performance of the invocation
  %of the threaded computation region. The user also must insert a
  %function at the end of the threaded computation region that - . 
  %Uses ROSE to automate compiler transformation.
  %TODO: make more clear. 
\end{itemize} 

TODO:L4: and reduces/eliminates programmer effort VS [OMIT] 
TODO:L4: ffdas
\end{enumerate}
\end{frame}

\begin{frame}
\frametitle{Company x Appl. Ques.: Areas of Interest} 
{\tiny A research or engineering position within DESRES can focus on
  any or all of a range of areas, from software design and algorithm
  analysis to computer architecture, chip design, and
  verification. What area or areas best match your expertise and
  interest?} 
\begin{itemize} 
\tiny \item \tiny Architecture. 
\item \tiny High-Performance Computing: 
\item \tiny Performance Modeling and Theoretical Analysis
\item \tiny Dense Matrix Factorizations 
\item \tiny Scientific Computing and Applications. 
\end{itemize}
\end{frame}


\begin{frame} 
\frametitle{Company x application question: Most significant
  accomplishment as a researcher}

My most significant accomplishment is improving performance of an
already optimized numerical linear algebra kernel run on a 48-core
node by 64\% by applying my lightweight loop scheduling techniques to
the kernel. The result is published at IPDPS 2011. The accomplishment
is significant because the numerical linear algebra kernel is
representative of kernels in many scientific applications. The
accomplishment is also significant for my research because it showed
the potential of our technique to benefit large bulk-synchronous
scientific MPI applications.

\end{frame} 


\begin{frame}
\frametitle{Reply to Girl after Rejection 2} 

Hi, 

I had a hard time opening and reading this this because of the pain
I was feeling in hearing in thinking about the possible replies that
you'd likely write. While there were several things going on, that's the reason behind the
e-mail to you with the subject line 'Your mail'. I thought again about
what I wrote during the week and decided I had to open and read the e-mail this
evening and reply in the best way that I can when I opened it. 

Thank you for your reply to my e-mail.

I understand the part of being dependable being involved. Maybe this
is me picking on something small, but I think it's a relevant
example. I was late by about 40 minutes for a brunch. 


I made a mistake of not keeping my phone charged when we met
in New York City. I did that more than a couple of
times then. I did that again when we met in Boston on Saturday
afternoon. I remember reading between the lines what I believe was
irritation in your text messages to me that day. Putting myself in
your perspective, I can only imagine that you were thinking that I
would have my phone turned off or be late for your birthday - you
might have even expected that, which annoyed me. 
If we were to be in a relationship again, or start over, I'd work hard
to do everything I can to make sure
that any method to communicate with you would be on for you all the
time so that you could know that you can depend on me if you need
something in any situation. 

I'll need to think on my own to answer this. 

I can't say much more at the moment since, frankly, I need to
to prepare for interviews. I have thought this through reasonably and
believe it's a reply that I may give when I'm less busy.

Vivek


Hi,

I had a hard time opening and reading this  because of the pain I was
feeling in thinking about the possible replies that you'd likely
write. I thought again about that and decided I had to open and read
the e-mail this evening.

Thank you for your detailed reply, which made me think further. I
understand the part of being dependable and being involved. I can see
these issues in the problems of being late at brunch in NYC and my
phone not being charged, which may be small examples. If we were to
start over, I'd work hard to make sure I'm dependable and in touch
with you all the time.

I won't say much more because of needing to prepare for
interviews. I'll let you know about my job search.

Vivek



%If were to start
%over, I'd do everything I could do have my method of communication be
%on all the time and that I read your texts. 
%And, if that ever happened again, which would happen rarely rather
%than a routine, I'd stop to tell
%you that I didn't mean for that to happen and show you things I'd do
%so you could feel you could depend on me. 

%I'd understand the situation of an event with your friends and make
%sure that you knew I'd have it on when in a big group of people when
%things can get complex and you need something from me. 

%These are things I'm aware of, know how to fix, 


% I tried to figure out what was wrong with the phone. 



%For me to do that in an entirely different
%context creates the impression. 


% have come into
% your office that day to tell you I need to figure out what's going
% on and have a conversation with you about the issues. 


%Personally, I think it's ok to be a little late to meeting. But that
%was more than just a bit late. 
%I wouldn't make you feel that being late is a habit.  


I'm in my own world for writing
 
This may be a simple example - you may have others - but from my perspective. 

I view the part about being involved is a superset of the element of
dependability. The part about being involved means that 

This is harder for me to answer right now. 




\end{frame} 



\begin{frame} 
\frametitle{Publications Read and Conferences Attended} 
\underline{\textbf{Conferences Attended/Presented}}\\
\begin{enumerate} 
\tiny \item \tiny SC'14, SC'13, SC'12, SC'11
\item \tiny IEEE IPDPS2010, IPDPS 2014 
\item \tiny SIAM PP10, SIAM PP14
\end{enumerate}
\underline{\textbf{Publications Read}}\\
\begin{enumerate}
\tiny \item \tiny SC conference series 
\tiny \item \tiny IEEE Transactions of Parallel and Distributed Computing 
\tiny \item \tiny SIAM PP and CSE conference series 
\end{enumerate} 
\end{frame}

\begin{frame}[label = atpesc]
\frametitle{ATPESC Training course acceptance} 
\textbf{Introduction}
\begin{itemize} 

\tiny \item \tiny MemHook: Use a watermark. 
%\item \tiny Action: I'd like you to read this and assess if I'm a fit for
%  your course. 

\item \tiny Action: I'm writing for admission to the ATPESC training
  course.  Application for admission to program . 

\item \tiny Perspective: I'm a student of Professor Gropp. I've recently 
graduated as a PhD at UIUC with a fellowship as Lawrence Scholar. 

\item \tiny St benefits: At the end of this, I hope you will see my
  qualifications and have a chance to evaluate  -- . I believe I can
  be a good student. Below I describe why I would be  
\end{itemize}

\textbf{Past Work} \\  
\begin{itemize} 
\tiny \item \tiny Worked on molecular dynamics simulation on
BlueWaters using MPI+OpenMP, using low-overhead scheduling + Worked on
PlasComCM OpenACC-ization along with a less complicated stencil
computation. - 
\begin{itemize} 
\tiny \item \tiny Worked to improve performance of code by using GPGPUs. 
\item \tiny Modified the OpenMP region MPI+OpenMP application to use
  low-overhead scheduling so as to improve performance. 
\end{itemize} 
\item \tiny Worked at LLNL with stencil computations on cab and BG/Q.  
\begin{itemize}
\tiny \item \tiny Did several transformations on simple codes 
\item \tiny Worked on transformations using ROSE.  
\item \tiny applied these transformations to application code,
  including a CORAl benchmark AMG2013. 
\end{itemize}
\tiny \item \tiny Took Bill Gropp's course recently on designing and
building applications for high-performance. 
\begin{itemize}
  \tiny \item \tiny This course gave strong grounding for designing
  and building applications, and practice with strategies to design
  and build numerical applications computations in a way that improves
  performance.  
\end{itemize}
\end{itemize}
\textbf{Plans}
\begin{itemize} 
\tiny \item \tiny Working on molecular dynamics simulations on BW
using my scheduling scheme. I would like to continue research to
finish my postdoc work. 
\begin{itemize}
\tiny \item \tiny 
\item \tiny 
\end{itemize}
\item \tiny Doing experimentation with GPGPUs for stencil-based
  codes to improve heart simulation and plascomcm on 1024 nodes. 
\begin{itemize} 
\tiny \item \tiny 
\item \tiny 
\end{itemize} 
\item \tiny Working to use my low-overhead
  scheduling scheme to improve heart simulation and plascomcm on 1024
  nodes.     
\begin{itemize} 
\tiny \item \tiny 
\item \tiny 
\end{itemize} 
\end{itemize} 

\textbf{Conclusion} 
\begin{itemize}  
\tiny \item \tiny Qualifications and background. I also believe I have
merit, given that I have publications.  
\item \tiny With these qualifications and experience, I believe I will
  be a good candidate for attending the ATPESC course. I also believe
  I can benefit from the course significantly. I may drift away from
  HPC in the future. 
\item \tiny  
\end{itemize} 
\end{frame} 


\begin{frame} 
\frametitle{Jobs}
{\tiny Everytime someone is hiring, they take a risk. LinkedIn. }
\begin{table}
\begin{tabular} 
cat1: 

D.E. Shaw money - positions | SUNY/BNL: money  applying other opinionsy | IBM: applied,interviews.  | Sandia:
applied and failed, Cray: applied and got offer, USC. 
 
cat2: 
  Intel: Applied and failed. Intel: re-application completed, AMD:
  applied, Samsung, VMWare: Contacting Yavatkar Kaka. 

cat3: 
  Google. MongoDB: applied and failed, Facebook.

cat4: LLNL - applied and didn't hear back.   

\end{tabular} 
\end{table} 

\begin{table} 
\begin{tabular}{ | c || c | c | c |}
  \hline
   \textbf{App} &  \textbf{Naive} &  \textbf{Collective} & \textbf{Callsite} \\
  \hline
  \tiny NASSP & \tiny 0.00615\%  & \tiny 0.0196\% & \tiny 0.301\% \\
  \hline
   NASBT & \tiny 0.00592\% & 0.0186\% & \tiny 0.294\% \\
  \hline
   NASLU & \tiny 0.00618\% &  \tiny 0.0204\% & \tiny 0.303\%  \\
  \hline
  \tiny AMG & \tiny 0.00675\% & \tiny 0.02064\% & \tiny 0.329\%  \\
  \hline
  \tiny PF3D & \tiny 0.006714\%  & \tiny 0.01995\% & \tiny 0.322\% \\
  \hline
\end{tabular}
\end{table} 

{\tiny BNL vs ISI :  think about the code, then think about the other
  things.} 
\end{frame} 

\begin{frame}[label=] 
\frametitle{Funding report for BNL} 
Funding report
https://www.youtube.com/watch?v=D1hfrtoVZDo
\end{frame} 

\begin{frame}[label=myProfile] 
\frametitle{What I do} 
%TODO: fix first sentence to be more general for scientific
%community. 

%TODO: simulation 

The performance of a scientific application intended to run on a cluster of SMP
nodes can degrade significantly with an increasing number of SMP nodes
due to node-local load imbalances. Although dynamic load balancing
within a node can mitigate such imbalances, such load balancing is
challenging because of its impact to data movement and synchronization
overhead. In this talk, I discuss a series of loop scheduling
strategies that mitigate node-local load imbalances without 
incurring high overhead. The scheme and methodology helps improve
performance of applications on a cluster of SMPs with minimal
application programmer intervention, and we expect these techniques to
be useful for future machines approaching exa-scale. 
Additionally, I discuss (1) work on performance
characterization of and a broad set of
performance optimizations for an application for x-ray imaging
intended to run on a cluster of a large number of SMP nodes each
having accelerator hardware, e.g., NVIDIA's Tesla K80 GPU, 
and (2) emerging node architectures that may resemble the
node architectures of future machines approaching exa-scale.

%TODO: fix this 
Finally, 


\end{frame}


\begin{frame}[label=contactswork]
\frametitle{Contacts from USC/ISI}
\begin{itemize}
\small \item \small Me: 703-812-3704
\item \small Steve Crago: 703-812-3729
\item \small JP Walters: 703-812-3706
\item \small Claire Jansa: 703-812-3731
\item \small Melissa Snearl-Smith: 310-448-9113 or 310-448-8270 
\item \small Kaushik Datta: 703-812-3722
\item \small Forrest Houston: 703-812-3726
\item \small Conf. Bridge: 703-248-6178 code: 546213 
\end{itemize}
\end{frame}

\begin{frame} 
\frametitle{ Prof. Chapman's work}  

OpenUH compiler : 

OpenMP directives: 


https://www.youtube.com/watch?v=OHx2G4a9JI0 

llvm : 
\end{frame}  


\begin{frame}
\frametitle{Operations} 

Facebook : 


BUSINESS OPERATIONS
Ken Koebel
Peter Boyle
Ziqiao
Guan
Shudong
Jin
Dimitrios Katramatos 
Kerstin Kleese van Dam
Lingda Li
Yuewei Lin
Jun Ma
Abid Malik
Remi Megret

COMPUTER SCIENCE AND MATHEMATICS 
HR 

BUSINESS PARTNER

Christel 
Colon
RESEARCH OPERATIONS
Linda Bowerman 
DIRECTORATE CHIEF
OPERATIONS 
OFFICER
Ann Emrick 
*Reports to Kerstin Kleese van Dam, Director of Computational
Science Initiative
ESH Coordinator 
????
Bob Colichio, Pat Carr
BARBARA CHAPMAN*
DIRECTOR
Gina Liles
Administrative Assistant

Approved: Barbara Chapman          Date: August 31, 2016
Minh Hoai Nguyen
Verinder Rana
Roman Samulyak
Wen Shih
Bo (Beth) Sun
B
\end{frame} 



\begin{frame}
\frametitle{ Apartment Decision}
\begin{itemize}
\item \small Ballston:
\begin{enumerate} 
\tiny \item \tiny Liberty towers
\item \tiny Virginia Sq.: 
\item \tiny Avalon: 
Pro: 
next to apt
Con: 
not great view 
\item \small  DuPont Circle: 
\end{enumerate} 


\begin{enumerate} 
\item \tiny  2500 
\end{enumerate} 
\end{itemize} 

\end{frame} 

\begin{frame}[label=jobApp] 
\frametitle{Job Application} 

{\tiny Sign In to access application status,
saved documents and Job Search Agents
Job Details
View Search Results
View Job Cart (0)
Send This Job to a Friend
View My Account
Assistant Scientist Compiler Directive
Job ID \#: 858 Job Category: Scientific Staff
Position Type: Full Time - Term Department: CC-Computational
Sci. Initiative
FLSA: Exempt  
Share: Share on Facebook! Facebook Share on LinkedIn! LinkedIn Share on Twitter! Twitter

Why Work at BNL?

Brookhaven National Laboratory is a multipurpose research institution
funded primarily by the U.S. Department of Energy????s Office of
Science. Located on the center of Long Island, New York, Brookhaven
Lab brings world-class facilities and expertise to the most exciting
and important questions in basic and applied science????from the birth of
our universe to the sustainable energy technology of tomorrow. We
operate cutting-edge large-scale facilities for studies in physics,
chemistry, biology, medicine, applied science, and a wide range of
advanced technologies. The Laboratory's almost 3,000 scientists,
engineers, and support staff are joined each year by more than 4,000
visiting researchers from around the world. Our award-winning history,
including seven Nobel Prizes, stretches back to 1947, and we continue
to unravel mysteries from the nanoscale to the cosmic scale, and
everything in between. Brookhaven is operated and managed by
Brookhaven Science Associates, which was founded by the Research
Foundation for the State University of New York on behalf of Stony
Brook University, and Battelle, a nonprofit applied science and
technology organization.

Organizational Overview

Building on its capabilities in computational science and data
management, the Computational Science Initiative (CSI -
\url{https://www.bnl.gov/compsci/}) at the U.S. Department of Energy's (DOE)
Brookhaven National Laboratory was established to integrate and
leverage computer science, computational science and applied
mathematics expertise and investments across multiple programs at the
Laboratory. In providing leading computational and data science
solutions for BNL????s flagship facilities ???? RHIC, LHC Atlas US Tier One
Center, NSLS II, CFN ????CSI is confirming Brookhaven as a leader in
tackling the ``big data'' challenges at the frontiers of scientific
discovery. CSI????s mission is to provide ????Leadership in Data Driven
Discovery????. We are pursuing this mission by engaging in research into
novel approaches and methods throughout the software stack to create
high performance analysis and interpretation capabilities for
experimental, observational and computational data, the provision of
data management and analysis facilities, and the practical application
of these resources to critical domain science challenges.

Position Description
 
The Computational Science Initiative (CSI -
\url{https://www.bnl.gov/compsci/}) of Brookhaven National Laboratory is
currently looking for an Assistant Computational Scientist with a
focus on designing and implementing compiler directives for parallel
computing. The post holder is expected to work closely with
Prof. Barbara Chapman, the lead of the BNL programming model and
compiler research effort.

Duties:
    Conduct research on directive-based parallel programming models
    for High Performance Computing, and their implementation, in order
    to increase their usefulness for large-scale computations
    Collaborate with scientific application developers to help them
    develop application codes that exploit the full potential of
    emerging high performance computing systems.
    Carry out research to enhance compiler technology in support of
    large-scale parallel computations
    Promote the research results through scholarly publications and
    presentations at leading conferences
    Participate in the development of related research proposals.

Position Requirements

Required Knowledge, Skills and Abilities:

    PhD in Computer Science, Computer Engineering or related
    discipline

    Research background in compilers, programming languages or
    libraries, or programming environments

    Experience in at least one aspect of compiler development
    Familiarity with overall compiler design
    Strong C / C++ programming skills and a passion for writing
    quality code.
    Publication in a refereed compiler conference/workshop.
    Good oral and written communication and teamwork skills.
    Moderate domestic and foreign travel. 
Preferred:

    Good understanding of modern computer architecture

    Experience working in multidisciplinary collaboration

    Research experience in High Performance Computing and/or
    familiarity with one ore more large-scale scientific applications

    Working knowledge of OpenMP and/or OpenACC.
    
    Experience working on LLVM/Clang a plus.
    
    Track record of producing high quality software on schedule.

We invite you to consider Brookhaven National Laboratory for
employment. To be considered for this position, please apply online at
BNL Careers and enter the job title into the Keyword Search.

Brookhaven National Laboratory (BNL) is an equal opportunity employer
committed to ensuring that all qualified applicants receive
consideration for employment and will not be discriminated against on
the basis of race, color, religion, sex, sexual orientation, gender
identity, national origin, age, status as a veteran, disability or any
other federal, state or local protected class.

BNL takes affirmative action in support of its policy and to advance
in employment individuals who are minorities, women, protected
veterans, and individuals with disabilities.

*VEVRAA Federal Contractor
}

\end{frame}


\begin{frame}
\frametitle{Intro to Management}
\end{frame}


\begin{frame}
\frametitle{Long-term goal}
Make an impact or illuminate a discovery in the area of computer science. 
\end{frame} 


\begin{frame}
\frametitle{Comm:}  
\begin{itemize}
\tiny \item \tiny review first 8 tm speeches + entertainment speech
\tiny \item \tiny finish readings 3.4-3.9  in win friends inf.  -  
\item \tiny Org. win friends inf. people. 
\item \tiny Finish notes on social intelligence + tm (speeches 9 and 10). \url{http://www.meetup.com/Michigan-Avenue-Toastmasters/about/comments/?op=all} 

\item \tiny Organize tm+social int into wlcheatsheet .  
\item \tiny Finish notes on 7 habits: goals, prioritization, 
public victory, win-win, listen, synergize,   
\item \tiny go through working with 7 habits . 
\item \tiny integrate into wl-cheatsheet.  
\item \tiny magazine articles categorization. 
\item \tiny impromptu speaking.
\end{itemize}
\end{frame} 
\begin{frame}
\frametitle{worklife todo} 
\begin{itemize} 
\item Finish organization in wl-cheatsheet. 
\item translate documents like resume to latex.  
\item integrate resume to worklife. 
\item create outline wl-cheatsheet  and extended outline of
  wl-cheatsheet. 
\item integrates slides into wl cheatsheet. 
\end{itemize}  
\end{frame}





\begin{frame} 

\frametitle{Meeting for PRISMA} 

\underline{\bf Join on computer} 

\begin{enumerate}
\small \item \small Dial: 199.48.152.152
\item \small Meeting ID: 8562450706
\end{enumerate}

\underline{\bf Join by phone} 
\begin{enumerate}
\small \item \small 408.740.7256 or 888.240.2560 
\item \small Meeting ID: 8562450706
\item \small Press \#
\end{enumerate}
\end{frame} 

\begin{frame}[label=omp_lang]
\frametitle{Meeting for OMP-lang} 

\underline{\bf Join WebEx meeting} 
\begin{itemize} 
\small \item \small  \url{https://llnl.webex.com/llnl/j.php?MTID=md575d91e6134ce9b0aaf14bc65c011eb}
\item \small Meeting number: 805 639 779
\item \small Meeting password: openmp
\end{itemize} 

\underline{\bf Join by phone} 
\begin{itemize} 
\small \item \small +1-415-655-0001 US TOLL
\item \small Access code: 805 639 779
\end{itemize} 

\end{frame} 


\begin{frame}[label=omp_affinity]
\frametitle{ Meeting for omp-affinity} 
\underline{\bf Join WebEx meeting} 
\begin{itemize} 
\small \item \small  \url{https://llnl.webex.com/llnl/j.php?MTID=md575d91e6134ce9b0aaf14bc65c011eb}
\item \small Meeting number: 805 639 779
\item \small Meeting password: places
\end{itemize} 

\underline{\bf Join by phone} 
\begin{itemize} 
\item +1-415-655-0001 US TOLL
\item Access code: 805 639 779
\end{itemize} 
\end{frame}

\begin{frame}[label=myInformation]
\frametitle{Mgmt:Spaces:information}  
      \begin{itemize}
      \tiny \item \tiny work ID
        \begin{enumerate} 
          \tiny \item \tiny UIUC UIN: 659743643 
        \item \tiny LLNL ID: 008983 
        \item \tiny USC ID: 910-1254-783
         \end{enumerate} 
\item \tiny Work equipment: 
\begin{enumerate} 
\tiny \item \tiny Model A1707
\tiny \item \tiny S/N: C02T30EZGTF1
\tiny \item \tiny Computer serial number: 
\tiny \item \tiny private159.east.isi.edu
\item \tiny IP address:  65.114.168.159 
\item \tiny Whole disk encryption? 
\end{enumerate}
      \item \tiny insurance number: 
        \begin{enumerate} 
          \tiny \item \tiny bcbs : user: vivekkale pass: qazxsw23
          memberID: QME9212849609  Group No.: IG2601.
        \item \tiny USC:  user:   pass: 
          \end{enumerate} 
      \item \tiny mycarle: vivekk112 password: carle 
      \item \tiny ppn:028361799  exp: 3-16-2025 driver's license:K400-8728-4051
        exp:2-20-18 
      \item \tiny Money: 
        \begin{itemize}
        \tiny \item \tiny CC1 num: CC2 num: Dbtnum: 
        \item \tiny Bank Account:   
          Name: JP Morgan Chase
          bank acct num: Nine Five
          Eight Six Thirty Sixteen Two
          IBAN/routing num: 3222 71627
          ABA-Fedwire No.: 021000021
        \item \tiny VIN:   License Plate: IL E61 2444 reg.exp:   Atul's lic: P84 VIN
        \item \tiny Parking location codes:   Parking signs: 
        \item \tiny VivekInternet????s FightingIllini  wifi pass:
          2173900374 WPA
        \item \tiny xfinity account number: 0149024144. /  vivek.lkale@gmail.com 
        \item \tiny ComEd account number: 0149024144. 
        \item \tiny Dominion Account Number: 4248285449
        \item \tiny Renter's Insurance Arlington, VA account number: 
        \item \tiny Hilton HHonors Number: 255506941. 
        \item \tiny Marriott Rewards number: 505951. 
        \item \tiny AAdvantage number: 847JJP0. password: 
        \item \tiny Southwest: vivek.k password: 
        \item \tiny Dad's AAdvantage number: BRU6630 Password:
          polarwind.
        \item \tiny Emerald Club number:  140294615   pass:
        \item \tiny Avis Wizard number: 
        \item \tiny Netflix user:  lvk2408@gmail.com  Netflix
          password: chitrapat.
        \item \tiny Sirius XM radio ID: 
          \item \tiny Sirius XM radio ID: 4D8CN0C1 acctend: 2076
        \end{itemize} 
\end{itemize}
\end{frame} 

\begin{frame}
\frametitle{Mgmt:webpresence}

\begin{enumerate} 
\small \item \small Researchgate.
\item \small LinkedIn.
\item \small Twitter.
\item \small website and google+.
\item \small Facebook.
\item \small Instagram. 
\item \small Whatsapp.
\item \small Skype.
\item \small Bluejeans.
\item \small Phone.
\end{enumerate}

\end{frame} 


\begin{frame} 
\frametitle{Work:codepractice:todo } 
\begin{itemize} 
\tiny \item \tiny Work:codepractice: Java lesson + Work:codepractice:
java problems  
\item \tiny Work:codepractice: finish bit manipulation problems. 
\item \tiny Work:codepractice: finish math/logic puzzles. 
\item \tiny Work:codepractice: Go through additional miscellaneous
  problems. 
\item \tiny Work:codepractice: go through dynamic programming
  problems. 
\item \tiny Work:codepractice: finish MIT algorithms lectures +
  Work:codepractice: quick review of other course material like eecs +
  integrate course material + Work: get compArch book.  
\end{itemize}
\end{frame}


\begin{frame}
\frametitle{Work:comm} 
\begin{itemize} 
\small \item \small talk to Prof. Gropp about ANL opportunity. 
\item \small talk to Stephen.
\item \small talk to Amanda. 
\item \small talk to Blaise. 
\end{itemize}
\end{frame} 

\begin{frame}
\frametitle{Work:code: todo} 
\begin{itemize}
\tiny \item \tiny create locality-aware tasklet scheduling library. 
\item \tiny make stencil with OpenACC. 
\item \tiny create configuration file for stencil with OpenACC. 
\item \tiny Work:code: make discussion of paper into latex 
\item \tiny 
\end{itemize} 
\end{frame}  

\begin{frame}
\frametitle{Comm Todo} 
\begin{itemize} 
\item \tiny  
\end{itemize} 
\end{frame}
 
\begin{frame} 
\frametitle{Work:admin information}

%TODO: categorize this further. 
\begin{itemize} 
\item Health insurance.
\item Retirement plan.
\item W-2 tax information. 
\item Travel. 
\item Keys and Clearance. 
\item ID. 
\item Machine accounts. 
pr1\$ma@1\$1
\end{itemize} 
\end{frame} 



\begin{frame}
\frametitle{6-month plan}
\begin{enumerate}
\tiny \item \tiny March: finish thesis writing + jobtalks +
organization of spaces. 
\item \tiny April: Code/ papers + books review 
\item \tiny May: books review    
\end{enumerate}
\end{frame}

\begin{frame}[label=schedule2016]
\frametitle{Schedule for March and April}
\begin{itemize} 
\tiny \item \tiny Work: paper + Work: code library +  Work: coding for
stencil.  
\item \tiny Work:comm: anl paper + Work:comm: talk to Amanda, Work:comm: talk to Stephen 
\item \tiny Coding excercises: 
\item \tiny finish wl  + finish comm: 
\item \tiny apply to places (interview later) : mit (consider being
  the only researcher), berkeley lab resume, intel resume 
\end{itemize} 
\end{frame} 

\begin{frame}[label=schedule2016]
\frametitle{Schedule for May and June}
\begin{itemize} 
\tiny \item \tiny Work: paper + Work: code library +  Work: coding for
stencil.  
\item \tiny Work:comm: anl paper + Work:comm: talk to Amanda, Work:comm: talk to Stephen 
\item \tiny Coding excercises: 
\item \tiny finish wl  + finish comm: 
\item \tiny apply to places (interview later) : mit (consider being
  the only researcher), berkeley lab resume, intel resume 
\end{itemize} 
\end{frame}  

\begin{frame} 
\frametitle{ Week by week for 2-month period} 
\begin{itemize}
\tiny \item \tiny Week1: 
\item \tiny 
\item \tiny 
\end{itemize} 
\end{frame}

\begin{frame}
\frametitle{Project: paper}
\end{frame}

\begin{frame}
\frametitle{Project: course project}
\begin{itemize} 
%TODO: re-word or integrate
\tiny \item \tiny many sources of within-node imbalances in
applications. Problem: Either due to imperfect partitioning of work to
threads or due to noise (or both).  
%TODO: re-word and integrate 
\item \tiny Research Question: What is the expected impact of within-node
imbalances to bulk-synchronous MPI application? 
\tiny \item \tiny Given: Load Imbalance Cost model for timestep: 
\item \tiny Extend to 3D reg. mesh computation, and then consider
  impact to different apps, e.g., Amanda's app or n-body simulation. 
\item \tiny By doing this, we hope to understand whether heartbeat sim
  is impacted by imbalances.
\end{itemize} 
\end{frame} 



\begin{frame}[label=fillOutForms ] 
\frametitle{Filling out forms} 
\begin{itemize} 
\tiny \item \tiny When asked to print, use capital letters
\item \tiny Banking transit number is one with :- 
\item \tiny 
\end{itemize}
\end{frame} 
  
\begin{frame}   
\frametitle{NATO Phonetic Alphabet when talking on phone} 

\textbf{First Name:} Victor India Victor Echo Kilo \\
\textbf{Middle Initial | (Name):} Lima | (Alfa Xray Mike India Kilo
Alfa November Tango) \\
\textbf{Last Name:} Kilo Alfa Lima Echo \\
\begin{table}
\begin{tabular}
  CHARACTER MORSECODE TELEPHONY PHONIC(PRONUNCIATION)
  A                    Alfa     (AL-FAH)     
  B                    Bravo    (BRAH-VOH)
  C                    Charlie  (CHAR-LEE) or(SHAR-LEE) 
  D                    Delta    (DELL-TAH)
  E                    Echo     (ECK-OH)
  F                    Foxtrot  (FOKS-TROT)
  G                    Golf     (GOLF) 
  H                    Hotel    (HOH-TEL)
  I                    India    (IN-DEE-AH)
  J                    Juliett  (JEW-LEE-ETT)
  K                    Kilo     (KEY-LOH)
  L                    Lima     (LEE-MAH) 
  M                    Mike     (MIKE) 
  N                    November (NO-VEM-BER) 
  O                    Oscar    (OSS-CAH ) 
  P                    Papa     (PAH-PAH)
  Q                    Quebec   (KEH-BECK)
  R                    Romeo    (ROW-ME-OH)
  S                    Sierra   (SEE-AIR-RAH)
  T                    Tango    (TANG-GO)
  U                    Uniform  (YOU-NEE-FORM)or(OO-NEE-FORM)
  V                    Victor   (VIK-TAH)
  W                    Whiskey  (WISS-KEY)
  X                    Xray     (ECKS-RAY)
  Y                    Yankee   (YANG-KEY)
  Z                    Zulu     (ZOO-LOO) 
  1                    One      (WUN)
  2                    Two      (TOO)
  3                    Three    (TREE)
  4                    Four     (FOW-ER)
  5                    Five     (FIFE) 
  6                    Six      (SIX)
  7                    Seven    (SEV-EN)
  8                    Eight    (AIT)
  9                    Nine     (NIN-ER)
  0                    Zero     (ZEE-RO)
\end{frame}

\begin{frame}
\frametitle{Cars Instances} 
{\tiny These are representative car instances that I think are suitable for me.} 
\begin{itemize} 
%TODO: add in 328i sport line (blk/grey color)
\small \item \small  2013 BMW 328i xDdrive. \$31,223. CPO. 24,340
mi. Colors: Blk Exterior/Tan interior/WoodGrain. VIN (for Carfax):
  WBA3B5G54DNS05235. Dealer ad: \url{http://www.cars.com/vehicledetail/detail/627013937/overview/.}
\item \small 2012 BMW 335i. \$34,998. Colors: Black/Black 32,003
  mi. CPO. M sport package. Tech package. Navigation. Heads up display. VIN(for
  Carfax):  WBA3A9C51CFX59924 \url{http://www.cars.com/vehicledetail/detail/628928072/overview/}. Phone: 
%\item \small 2010 BMW M3.  \$38,525. CPO. 29,144 mi.  VIN (for Carfax):
%WBSWD9C55AP363244. \url{http://www.cars.com/vehicledetail/detail/623505105/overview/} 
\end{itemize} 
\underline{\textbf{ Reviews }} \\
\begin{itemize} 
\small \item \small \url{www.carreviewsoup.com/which-bmw-3-is-best-it-just-doesnt-matter}
\end{itemize} 
\end{frame} 

\begin{frame} 
\frametitle{cars with most tickets} 
Cars with colors red: red cars go fast.  
Lexus ES 300 33
Nissan 350Z 33
Dodge Charger SE/SXT 32
Volkswagen Jetta GL31
Chevrolet Monte Carlo LS/LT 31
Mazda 3S 30
Volkswagen GTI 30
Dodge Stratus SXT30
Acura 3.0s 30
Toyota Tacoma 30
Mazda Tribute 30
Subaru Impreza WRX30
Lexus LS 400 Series30
Subaru Impreza 2.5I 30
Mercedes-Benz C300 4 Matic 30
Chevrolet Malibu 2LT29
Lincoln LS 29
Ford Fusion S 29
Mazda 3I 29
Chevrolet Tahoe K1500 29
\end{frame} 


\comments{
\documentclass[11pt,a4paper]{memoir}
\setstocksize{55mm}{85mm} % UK Stock size
\setpagecc{55mm}{85mm}{*}
\settypeblocksize{45mm}{75mm}{*}
\setulmargins{5mm}{*}{*}
\setlrmargins{5mm}{*}{*}
\usepackage{xcolor}
\setheadfoot{0.1pt}{0.1pt}
\setheaderspaces{1pt}{*}{*}
\usepackage{fontspec}
\setmainfont[]{EBGaramond12-Regular.ttf}
\checkandfixthelayout[fixed]
\pagestyle{empty}
\usepackage{pstricks}
\usepackage{auto-pst-pdf,pst-barcode}
\begin{document}
    \begin{Spacing}{0.75}%
    \noindent
    \textbf{Vivek Kale}\\
    \tiny Ph.D. \hfill {\color{gray}Postdoc, University of Illinois}\\ 
    \rule{74mm}{.3mm}\\
    \begin{minipage}[t]{33mm}
        \vspace{-0mm}%
        \begin{pspicture}(25mm,25mm)
            % The MECARD format is used to exchange contact
            % information. More information at:
            % http://www.nttdocomo.co.jp/english/service/imode/make/content/barcode/function/application/addressbook/index.html
          \psbarcode{MECARD:N:Last name, First
            Name;URL:https://fqdn;EMAIL:vivek.lkale@gmail.com;NOTE:GPG:
            ;;}{eclevel=L width=1 height=1}{qrcode}
        \end{pspicture}
    \end{minipage}
    \hspace{1mm}
    \begin{minipage}[t]{42mm}
        \vspace{-0mm}%
        \begin{flushleft}
        {\scriptsize
            \begin{Spacing}{1}%
            \textbf{Software Engineer}\\
            \hspace{5mm} Scientific Computing\\
            \hspace{5mm} Performance Tuning \\
            \hspace{5mm} Multi-core \vspace{2mm}\\
            \end{Spacing}
        }
        {\tiny
          \begin{tabular}{rl}
            {\color{gray}web} & https://vivek112.googlepages.com\\
            {\color{gray}email} & vivek@illinois.edu\\
            {\color{gray}email} & vivek.lkale@gmail.com\\
            {\color{gray}mobile} & +1 217 369 7996 \\
            \end{tabular}
            \vspace*{2mm}
        }
        \end{flushleft}
    \end{minipage}
    \rule{74mm}{0mm}\\
  %  \texttt{\fontsize{2.84mm}{3.55mm}\selectfont 425B 030A B8D2 0316
  %  CA1B 4709 CA83 5DDA EC31 CA56} % GPG KEY ID
    \end{Spacing}
\end{document}
}


\begin{frame}
  TM and habits 


\end{frame} 

\begin{frame} 
  \frametitle{Letter to Bronis for ref. letter} 
\end{frame} 

\begin{frame}
  \frametitle{Project Proposal : weighted imbalances}
\end{frame} 


\begin{frame}
  \frametitle{Overview: Comm}
  \begin{enumerate}
    \tiny \item \tiny 
  \end{enumerate}
\end{frame}

\begin{frame}
  \frametitle{Social notes}
  \comments{don't ask}
\end{frame}



\begin{frame}
  \frametitle{Toastmaster's Flow}
\end{frame}

\begin{frame}[label=webpresence] 
  \frametitle{Spaces : webpresence}
  \begin{itemize}
    \tiny \item \tiny 
  \item \tiny 
  \end{itemize} 
\end{frame}

\begin{frame}[label=spacescar]
  \frametitle{Spaces: Car}
  \begin{itemize}
    \tiny \item \tiny Glove compartment: insurance card
  \item \tiny Trunk: water, clif bars, shorts
  \item \tiny center console: earpiece, watch, sunglasses
  \item \tiny passenger underseat: maintenance papers
  \item \tiny driver underseat: checkbooks, receipts
  \item \tiny windshield wipers, windshield washer fluid
  \item \tiny tires check, oil change, maint req????d light
  \item \tiny gas, windshield cleaning 
  \item \tiny Interior cleaning: front-inside of windshield, front seats, floor
    mats, side windows, center console, instrument panels, rear-view
    mirror, inside door entry. 
  \item \tiny Exterior cleaning: wheels, hood, front sides, front door panels,
    rear door panels, trunk+bumper, roof.  
  \end{itemize}
\end{frame}




\begin{frame} 
\frametitle{ Apartment}

{\tiny Apartment sublease: }\\

{\tiny Title: \$2200 / 1br - 794ft2 - Lake View One Bedroom Sublet from 9/5
to 10/26 (Chicago) } \\

{\tiny Posting: I'm subleasing my one bedroom convertible apartment
  from September 5th, 2016 through the end of my lease on October 26th, 2016.

 The apartment has 10-foot-high ceilings, floor-to-ceiling windows and
a view of the lake and half of Chicago's skyline. Amenities include a
gym, a lounge and an outdoor patio with barbecue grills and
fireplaces. A security guard is on duty 24/7 at the building's lobby.

The location is a 5 minute walk to the Roosevelt CTA stop and Trader
Joe's and a 10 minute walk to Target and Whole Foods. } \\

Give Phone number of 217-369-7996. 

1BR / 1Ba 794ft2 available sep 05 
cats are OK - purrr
dogs are OK - wooof
no smoking
wheelchair accessible
private room
private bath
apartment
w/d in unit
attached garage. 

Pictures:  \\


Additional pictures: \\


Posting time: 7 days

\url{https://www.youtube.com/watch?v=-tzQclY43IA}

\end{frame}


\begin{frame}
\frametitle{Apartment} 
 \end{frame} 

\begin{frame} 
\frametitle{Apartment Sublease} 

\end{frame} 

\begin{frame}
\frametitle{Jean Pockets}
\begin{itemize}
\tiny \item \tiny Left pocket: Keys (RSA,car,house), cell phone (charger if
  needed) ???? unless it????s charging then remember to take it
 \item \tiny Right pocket: wallet (40 dollars, credit card, driver's
   license, school id)
\end{itemize} 
{\bf vuln} Treat your phone like its your baby !!! \\
{\bf vuln 2} Treat your wallet like its your baby 2 !!! 
{\bf vuln} Make sure to put in proper place:  right after coming
home from car, taking off jeans for the night, at a club 
\end{frame} 

\begin{frame}[label=backpack]
\frametitle{Backpack} 
\begin{itemize} 
\tiny \item \tiny main compartment: computer case (computer, computer charger)
\item \tiny side compartment: keys, checkbook, pens
\item \tiny left side outer: usb charger, outlet, usb memory stick 
\item \tiny right side outer: lotion
\item \tiny right side inner: glasses
\item \tiny left side inner: badge 
\end{itemize} 
\textbf{Vulnerability}: don????t put on floor of hotel or on bed/couch \\
\end{frame}

\begin{frame}[label=comp]
\frametitle{Spaces : Personal Computer}
\begin{itemize}
\tiny \item \tiny Webpresence, browser.
\tiny \item \tiny desktop layout1, desktop layout2
\item \tiny ViveksLaptop - Work: admin, fundamentals, code, pres, relatedPapers
\item \tiny Life: worklifemgr (thePast(speeches,   )),
  currPlanDoc.tex, myProfile. 
\item \tiny Environment: shell env. 
\end{itemize} 
\end{frame}

\begin{frame}[label=office] 
\frametitle{Office org}
\begin{itemize}
\tiny \item \tiny Left side: Fan, clock, phone, to file 
\item \tiny Right side: Food, tissue, papers, pens, hand sanitizer, tissue
\item \tiny Cabinet 1: Right: work docs + books, Left: life docs + books,
\item \tiny Center: Toiletries
\item \tiny Cabinet 2: Papers
\item \tiny Cabinet 3: Sleeping bag, pillow, misc., food
\item \tiny Center: Computer: --> 
\item \tiny Desktop: 
\item \tiny Docs: 
\item \tiny desktop background:  
\end{itemize} 
\end{frame}

\begin{frame}[label=garage]
\frametitle{Spaces: Garage/entrance/door/mailbox}
\begin{itemize}
\small \item \small  
\item \small 
\end{itemize} 
\end{frame} 

\begin{frame}[label=study]
\frametitle{Spaces: Study Room}
\begin{enumerate} 
\small \item \small desk with home computer. 
\small \item \small scanner. 
\item \small printer. 
\item \small clock.
\item \small couch.
\item \small left drawer: small.
\end{enumerate} 
\end{frame}

\begin{frame}[label=kitchen]
\frametitle{Mgmt:Spaces: Kitchen} 
\begin{itemize}
\small \item \small Freezer: ice cream, waffles, frozen meals.
\item \small Fridge: top: yogurt.
\item \small Fridge: middle: lunch/dinner, rice, lentils. 
\item \small Fridge: bottom: vegetables. 
\item \small Fridge: left side: condiments(chutney, sriracha)
\item \small Fridge: right side: dairy (butter, milk, jam) 
\item \small Pantry: top: maltomeal, rice.
\item \small Pantry: middle: tea, snacks, wine.
\item \small Pantry: olive oil, salt, sugar, spices. 
\item \small Pantry: floor: aluminum foil, plastic wrap, coasters, 
\item \small Cooking area: Microwave, toaster, stove, oven, coffee
  pot, rice cooker, sink, dishwasher.
\item \small dining table: placemats. 
\end{itemize}
\end{frame}

\begin{frame} 
\frametitle{Spaces: Bathroom}
\begin{itemize} 
\tiny \item \tiny Clean toilet bowl
\item \tiny Check clothes in towel bar
\item \tiny Watch for water on floor 
\item \tiny Clean sink area 
\item \tiny Check for hairs on bathtub. 
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Spaces: Bedroom}
\begin{itemize} 
\tiny \item \tiny center of room: bed: pillow, pillow covers, bed
sheet, blanket
\item \tiny left of bed: bedstand: top drawer:
\item \tiny right of bed:  desk: center: internet set and TV, left drawer, right drawer \\
\tiny \item closet: top shelves: sport shirts, undershirts, polos 
\item \tiny closet: bottom shelves: pajama, underwear, jeans
\item \tiny closet: low shelf: socks
\item \tiny closet: clothes rack: top: bottom: 
\item \tiny closet: floor: laundry. 
\end{itemize} 
\end{frame} 

\begin{frame}
\frametitle{Spaces: vuln}
\end{frame}

\begin{frame} 
\frametitle{Spaces: Vulnerabilities} 
\end{frame}



\begin{frame} 
\frametitle{Map}
\textit{\underline{\textbf{West Coast} }}
\underline{\textbf{San Francisco}} 

\underline{\textbf{Los Angeles}}
\underline{\textbf{Seattle}}
\underline{\textbf{Portland}} 
Local country map:
\textbf{\underline{\textit{Midwest}}}
\underline{\textbf{Minneapolis: }}

\underline{\textbf{Chicago:}}
West Loop: DRW office/ PT/\textbf{Metra Station},  \textbf{Union
  Station}
South Loop: Core Power Yoga, Target, 1401 S. State St.,
Streeterville Sheraton ,   McClurg Apartments, Round Table, Grand
Hyatt,

Michigan Avenue:

Lincoln Park:
Wicker Park:

Wrigleyville?

Surrounding areas:

\textit{North:} Northbrook/Evanston/Univ of Chicago/Hoffman Estates
\textit{East:} Indiana?

\textit{South:} Hyde Park, University of Chicago, \textbf{MDW}
\textit{West Suburbs:}
  North: Schaumburg, Bartlett, \textbf{ORD}
  South: Naperville, Aurora, Kankakee

\underline{\textbf{Urbana-Champaign:}} 

Campustown:
  North: Engineering:
  Main campus:
  Southside of campus:

Urbana:
Champaign:
Savoy:

\textbf{CMI}
\textbf{Illini Terminal}
Decatur/Springfield:
Tuscola/Mattoon:
Rantoul/Paxton:
St. Louis:
Indianapolis:


\underline{\textbf{East Coast:}} 
%\textit{\underline{\textbf{East Coast:}}}                                                                                                                                                                                                                        
Portland, Maine
\underline{\textbf{Cambridge/Boston}}
Providence
New Haven
\underline{\textbf{New York}}
Philadelphia
Wash D.C.

Southern cities:
Louisville,
Dallas, Nashville,
Atlanta,
Southeast US:
South Carolina,
Miami,
Orlando
\textit{\underline{\textbf{Europe}}} 
Northern Europe: 

United Kingdom: London 
Ireland: Dublin 

Sweden/Norway: 

Belgium: Brussels 

Dutch: Amsterdam: 

Germany/Austria/Swiss: 

- Cologne 
- Frankfurt/Heidelberg, Stuttgart
- Munich 
- Berlin 

Africa: 
- Cameroon
- Johannesburg

Southern Europe: 
   - Spain: Barcelona, Madrid
   - France: Paris, Lyon
   - Switzerland: Geneva/Lausanne, Zurich, 
   - Italy: Venice, Rome
   - Croatia: 
   - Greece: 
   
\underline{\textbf{Asia + Aussie }} 


Aussie: 

- Sydney

- Indonesia

- Tasmania

- Papa New Guinea



\end{frame}



\begin{frame}
\frametitle{Comm} 
\end{frame}

\begin{frame} 
\frametitle{Books} 
\begin{enumerate} 
\small \item \small 
\end{enumerate} 
\end{frame}

\begin{frame}
\frametitle{TM}
\todo{add TM in this area}
\end{frame}  

\begin{frame}[label=rulesofInt]
\frametitle{General rules of interaction} 
\begin{enumerate} 
\tiny \item \tiny Level 0+1: Think positively about interaction: No getting overworked
abt other????s remarks, stop beating yourself up, be humorous / Be
Honest, ethical to yourself and others | Act cozily | Reliability /
Consistency / Confidence /Shout. 
\item \tiny Level 2: Be logical, make sure you make sense / avoid random
thoughts that come to mind / structure thoughts and check for
non-sequitors.
\item \tiny Level 3: Be intentional / Think before you speak / integrate with
top-level point.
\item \tiny Level 4: send message in way that others will easily receive it:
howtosayit: grammar/picture errors, emphasize at the end, that
vs. which, check for gen. rules (don????t use abbreviations),
bodylanguage, vocalvariety.

Hi Kavita, let me know if you and Ashish can meet Friday evening. 

\item \tiny Level 5: persuasion, avoid I: a. give honest and sincere
appreciation b. don????t criticize, condemn, complain c. arouse in the
person and eager want: Be happy with others: Avoid mis-interpreting
others???? intentions / don????t get mad when someone doesn????t understand you
| avoid neg. thoughts | Identify common things | Listen to and Read
people (body language, facial expression) || empathy, wired to
connect: Situational awareness / Focus on one thing, and do that thing
/ Make eye contact / don????t be interested in random parties or
randomness outside / emotional intelligence | Give space, avoid being
over-intrusive.
\end{enumerate} 
\end{frame} 

\begin{frame}[label=specsettings] 
\frametitle{Specific Settings}
\begin{enumerate} 
\tiny \item \tiny Technical presentations: find ways to break ice and avoid
  nervousness/think of audience as rooting for you, organize speech
  (be linear), get to the point, how to say it, your body speaks,
  vocal variety, research your topic (know content), use visual  aids/materials (concrete?), persuade, inspire/connect, entertain/joke.
 \item \tiny Social gatherings/conventions (table topics): Be resilient to
  others words, think of words before speaking and making your point,
  punctuality, prep clothing, know schedules and email others in
  advance, know interactions that may come up, know what to go
  to/where to be, identify common ground in group and situational
  awareness, connect with the overall situation (mtg theme). 
  \item \tiny Meetings/hangout/interview (conversation): prep for what to say,
  avoid going into things that generate unneeded work. 
  \item \tiny Relationship setting: Be on lookout / think positively /
  icebreaker, Planning dates (make reservations, tell ahead of time
  what????s going on, don????t make things too complicated), Have something
  interesting + unique to say, show interest in specific things,
  Connecting (Find common ground, show compassion, show interest in
  the other person????s activities), Express emotions when you have them
  (when you like someone, tell them), connect about emotions. 
\end{enumerate} 
\end{frame} 

\begin{frame}
\frametitle{Social Intelligence} 
\end{frame}  

\begin{frame} 
\frametitle{Algorithm for Management - Monthly} 
\begin{enumerate} 
\tiny \item\tiny make6month plan.
\tiny \item \tiny make 2-month plan 
\item \tiny put in month week plan 
\item \tiny make notes on big conferences? 
\item \tiny put in weekend plans
\end{enumerate} 
\end{frame} 

\begin{frame}
\frametitle{Algorithm for Management - Weekly} 
\begin{enumerate}
\tiny \item \tiny Save as new file titled with Sunday beginning date. 
\item \tiny Save in old week plans. 
\item \tiny Put in worries list. 
\item \tiny Make week plan. 
\item \tiny Add in News. 
\item \tiny Add in situations. Write out the situations.  Put in pre
  and post. 
\item \tiny put in life notes. 
\item \tiny Add tasks to running todo based on week plan.
\item \tiny Breakdown tasks of running todo. 
\item \tiny Put identifiers on each todo. 
\item \tiny prioritize running todo. 
\item \tiny put into project sheet.  
\end{enumerate}
\end{frame} 

\begin{frame}[label=algsituationexp] 
\frametitle{Discussion of Situations} 
\begin{enumerate} 
\tiny \item \tiny Write down situation 
\item \tiny if/then. 
\item \tiny what was done well. 
\item \tiny vulnerabilities. 
\end{enumerate} 
\end{frame} 




\begin{frame} 
\frametitle{ Information}  
HealthAlliance:   940408859-01 HMO 1500a GOLD 866247-3296 tty 711
GeneSight: 866.757.9204  
Health Alliance password

Mycarle account: vivekk112 pword:  Misguided24
Busey Bank: 
Chase online:
CCnum:  banknum:  
VIN:  License plate: ill e61 2444   other cars: lexus:  VIN:  license:
Honda  |  Audi: VIN: 
Account number: 0149024144.
Atul????s FightingIllini  wifi pass:  2173900374 WPA. 
Southwest: 221040201

BICXZV 

\end{frame}

\begin{frame} 
\frametitle{Daily Schedule} 

\textbf{\underline{Weekday: }} \\
630 am: wake up, turn off alarm clock, brush teeth
645 am: eat breakfast
715 am: lift weights. 
730 am: look up weather, read emails. 
800 am: watch algorithms lectures, review programming problems 
11 am: research stuff. 
12 pm: eat lunch.
1 pm - 3 pm: programming. 
3 pm - 5 pm : applications/emails/meetings/phone calls. 
5 pm  - 6 pm : running.
6 pm  - 7:30 pm : dinner.
8 pm - 9 pm : talk to you and mom.
9 pm - 10:30 pm : finish emails.
10:30 pm - 11:30 pm : read books / articles on meditation or
self-help.


\underline{\textbf{Weekend: }} 
On Friday night: review situations. 
On Saturday morning, I take care of money, travel and bills. 
On Saturday afternoon, I take care of work I couldn't finish on the
weekday. 
On Saturday evening, I check LinkedIn for updates and I check Facebook
for updates and messages. I also check matrimony and prepare responses
to send on Sunday morning.
On Sunday morning, I watch news shows and read NYtimes. On Sunday
afternoon, I socialize and leave it open to do other things that help
me unwind. On Sunday evening, I plan for the week ahead, e.g., flights
checkins, emails to send. 

\end{frame} 

\begin{frame} [label=alg-daily]
\frametitle{Algorithm for Management - Daily} 
{\small \textbf{Summary:}  do night before, do after reg. routines} \\ 
\begin{enumerate} 
\tiny \item \tiny Extract three prime tasks from todo. 
\item \tiny put time est
\item \tiny make schedule. 
\end{enumerate} 
\end{frame} 

\begin{frame}[label=alg]
\frametitle{Algorithm for Comm}
\begin{enumerate}
\tiny \item \tiny L0:  think about the three key points you want to
say. Break into subpoints.  OR  Think about several points, and group
them into superponits. 
\item \tiny L1:  alleviate nervousness and don't hold back. 
\item \tiny L2: Create structure. Add content for introduction  
\item \tiny L3: Explain what you want the audience to get out of the 
  excercise. 
\item \tiny L4: write out what you're going to say as if you're 
talking to that person. Practice the text out loud. 
\item \tiny L4: Take care of logistics 
\item \tiny L5: Eliminate I in sentences. Focus on what the
  audience wants. 
\end{enumerate}  
\begin{enumerate}
\tiny \item \tiny write todos as you think of them.
\item \tiny reprioritize at each level. Some todos generate other
  todos. 
\item \tiny think big picture. %TODO: think about how to do this 
\item \tiny Do one level at a time. 
\item \tiny 
\end{enumerate}
\end{frame}

\begin{frame} 
\frametitle{Paper/pres} 
\end{frame} 

\begin{frame}[label=emails] 
\frametitle{Emails} 

%TODO: integrate email writing website here. 
 
\begin{enumerate}
\tiny \item \tiny Keep a happy face. Maintain reasons to be happy. 
\item \tiny Quick read of email. 
\item \tiny Write the immediate reaction: scratch. 
\item \tiny Read other person's email carefully = see whether they are
  showing interest, look at time sent, see which email, check cc's. 
\item \tiny Clear your mind: write three basic points based on facts +
Write down subpoints of three points to substantiate \te{20 minutes}. 
\item \tiny structure the body + write an introduction (tell them what
  you're going to tell them) + write conclusion(tell them what you
  told). \te{15 minutes}. 
\item \tiny Write down a call to action at the end.  \te{5 minutes}. 
\item \tiny Capture points into a single point. + make sure point
  pervades throughout email. (general and specific) \te{10 minutes}. 
\item \tiny Review how to say it. Thanks vs. Thank you. \te{2 minutes} 
\item \tiny Structure the body (check for unstated facts). \te{20 minutes} 
\item \tiny think of salutation.: Dear vs. Hi vs. none .  If a reply
  don't always need a salutation. \te{5 minutes} 
\item \tiny Think of subject line. \te{2 minutes}
\item \tiny Think about whether to send or not send \te{2 minutes} 
\end{enumerate} 
\begin{itemize} 
\tiny \item \tiny write quickly to a girl 
\item \tiny
\end{itemize}
\end{frame}


\begin{frame}[label=texts]
\frametitle{Texts\te{5 minutes}} 
\begin{enumerate}
\tiny \item \tiny L0: Shout.  
\item \tiny L1: Think about context. Think about emotional
  intelligence. Working with emotional intelligence.  
\item \tiny L2: Logic. Don't make assumptions. Follow.
\item \tiny L3: Intent. Past: Goal: Point: Outcome: 
\item \tiny L4: watch grammar, how to say it: short words, short
  sentences, be specific.
\item \tiny L5: not about you.   
\end{enumerate}
Examples:  
You text: 
Wanna meet up? 
Someone texts:  
\end{frame} 


\begin{frame}[label=fbposts]
\frametitle{Facebook posts} 
Fb posts: Happy Birthday! Happy Birthday [name]! to girl Happy
Birthday man! For travis tate  Happy Birthday, name! (if you don????t
know the person).  Happy Birthday, !  Congratulations! (on baby) Note
down bdays.  

\end{frame} 

\begin{frame}
\frametitle{FB likes} 
\end{frame} 

\begin{frame} 
\frametitle{Phone call} 
\end{frame}


\begin{frame}
\frametitle{Matrimony - source}

{\small \underline{\bf MM} } \\
\begin{itemize} 
\tiny \item \tiny San Jose 
\item \tiny Girl from Boston 
\item \tiny 
\item \tiny 
\end{itemize} 

{\small \underline{\bf SH}} \\
\begin{itemize} 
\tiny \item \tiny 
\item \tiny Girl from D.C.
\item \tiny 
\item \tiny 
\item \tiny 
\end{itemize} 

{\small \underline{\bf Encounters}} \\
\begin{itemize} 
\tiny \item \tiny Mamta 
\item \tiny
\item \tiny Avani
\item \tiny 
\end{itemize} 


\end{frame}


\begin{frame}[label=stateMachineDtng]
\frametitle{State Machine for Dating}
\begin{tikzpicture}[->,>=stealth',shorten >=1pt,auto,node
    distance=2.8cm,
                    semithick]
  \tikzstyle{every state}=[fill=red,draw=none,text=white]
  \node[initial,state] (A)                    {$q_a$};
  \node[state]         (B) [above right of=A] {$q_b$};
  \node[state]         (D) [below right of=A] {$q_d$};
  \node[state]         (C) [below right of=B] {$q_c$};
  \node[state]         (E) [below of=D]       {$q_e$};

  \path (A) edge              node {0,1,L} (B)
            edge              node {1,1,R} (C)
        (B) edge [loop above] node {1,1,L} (B)
            edge              node {0,1,L} (C)
        (C) edge              node {0,1,L} (D)
            edge [bend left]  node {1,0,R} (E)
        (D) edge [loop below] node {1,1,R} (D)
            edge              node {0,1,R} (A)
        (E) edge [bend left]  node {1,0,R} (A);
\end{tikzpicture} 
\end{frame} 

\begin{frame}
\frametitle{State Machine for dating} 

Introduction by text: 

talk by Phone: 

Talk by Skype: 

first date: 

second date: 

third date: 

decide: 

\end{frame}

\begin{frame}
\frametitle{Matrimony - priority}

{\small \underline{\bf Talking with} (July/August) } \\
\begin{itemize} 
\tiny \item \tiny Shikha. 
Hey Shikha, My week is going well. My boss is out of town this week. How
about you?

\item \tiny Bhakti.
\item \tiny Shwetha.
\item \tiny Shalaka.
\item \tiny Saloni 

\item \tiny Sonia Bhide 
\item \tiny Renuka. 

\item \tiny mamta. 

\item \tiny avani. 
\end{itemize}

{\small \underline{\bf cat 1} } \\
\begin{itemize} 
\tiny \item \tiny S. Van
\item \tiny Shalaka 
\item \tiny Sateja P. 
\item \tiny Divya 
\item \tiny San Jose 
\item \tiny Shilpa Ghate 
\end{itemize} 

{\small \underline{\bf cat 2}} \\
\begin{itemize} 
\tiny \item \tiny Mamta 
\item \tiny Asawari 
\item \tiny Avani
\item \tiny Girl from D.C.
\item \tiny Girl from Boston 
\end{itemize} 

{\small \underline{\bf cat3}} \\
\begin{itemize}
\tiny \item \tiny Surbhi 
\end{itemize}

\end{frame}



\begin{frame}
\frametitle {   Vivek <-> Asawari } 

\begin{enumerate} 
\tiny \item \tiny Sent email through parents. 
\item \tiny Sent email $\rightarrow$ No response. 

\end{enumerate} 

\end{frame} 




\begin{frame}[label=relMamta]
\frametitle{Vivek <-> Mamta} 
\begin{enumerate} 
\tiny \item \tiny Met for a date 
\item \tiny Tried to follow-up. 
\item \tiny Sent her a message. 
\item \tiny Sent a like. 
\end{enumerate} 
\end{frame} 

\begin{frame} 
\frametitle{ Vivek ->  Surbhi} 
\begin{enumerate} 

\item \tiny Contacted through Sumi 

\item \tiny Talked by phone. 

\item \tiny Met by date 

\item \tiny Phone call. 

\item \tiny No word afterwards.

\end{enumerate} 

\end{frame} 

\begin{frame}[label=pujaFriends]
\frametitle{ Friends with Puja} 

Enjoy your evening with Kevin! 

Perhaps we, including Kevin, can meet Thursday night?

\end{frame} 

\begin{frame}[label=mannerisms]
\frametitle{Mannerisms to have and to avoid} 
\begin{itemize} 
\tiny \item \tiny project voice
\item \tiny talk slowly
\item \tiny lips relaxed. 
\item \tiny smile. 
\item \tiny no frowning.
\item \tiny eyebrows up. 
\item \tiny relaxed hands, avoid
\item \tiny over-smiling
\item \tiny avoid moving arms
\item \tiny hands in pocket or to the side
\item \tiny avoid crossing arms
\item \tiny back straight.
\item \tiny walk with brisk pace.
\item \tiny don????t lean on places.
\item \tiny walk straight line without feet scrubbing floor
\item \tiny give hugs tightly.
\item \tiny shake hands thoroughly.
\item \tiny no looking at phone.
\item \tiny avoid bodily noises (no teeth clicks, no nose sneezes, no farts). 
\item \tiny don????t bump into people.
\item \tiny clean trash behind you.
\end{itemize} 
\end{frame}


\begin{frame} 


%to understand the strategies used.
\end{frame} 
\begin{frame}[label=experiences] 
\frametitle{Experiences/Evaluation} 
{\small emotional, social, general if/then, reliability,
maturity/practicepoints/positivepoints, rule-experience, specific
if/then, security, fault-correction, fault-tolerance. } 
\end{frame} 

\begin{frame}
\frametitle{Experiences List}
\end{frame}

% TODO: put experiences list and couple with experiences 
% TODO: move interview experiences before the weekend date experience. 
% TODO: put experiences list here 
% TODO: figure out whether the experience list should be in reverse 
% TODO: figure out whether experience list should be in reverse
