%\def\PRES{1}
%\ifx{\PRES}
%\iftoggle{\PRES}

%\begin{frame}[allowframebreaks]{Week Plan} 

%\begin{frame}[allowframebreaks]{Running To Do}

\begin{frame}[allowframebreaks]{Running To Do}
\begin{enumerate}
\item  $\rightarrow$ \textbf{Curr}
\item  Work:rel: send e-mail to Professor Chapman. \te{2 hours} 
\item  Work:rel: talk to James Beyer for getting GPU stuff. \dl{1 hour} 
\item  Work: draft letter for Michael. \te{1 hour} \dl{Tuesday} \pr{} 
\item  Talk with Helen. \te{} 
\item Work: admin: get password fixed. 
\item  Work: rel: send e-mail to Barry Rountree about
  talk. \te{25 minutes} \dl{Feb 8th} \pr{UI} 
\item \tiny Work: rel: send e-mail to Barry Rountree about slack-trace
  on github. \te{25 minutes} \pr{UI} 
\item  Work: rel: send message to Tony to get access to HPC
  facilities. \te{20 minutes} \dl{Feb 9th} 

\item  Mgmt:Spaces: read the letter from Carle. 
\item Mgmt:Health: get dentist appointment for filling. \te{1 hour}
\item Mgmt:Spaces: dentist appointment re-imbursement this week. \te{30 minutes} 
\item  Mgmt:Spaces: get glasses. \te{20 minutes}
\item Mgmt:Spaces: cancel appt.
\item Work:rel: email to Renata. \te{10 minutes} 

\item \tiny Work:rel: write draft letter for Michael Klemm.
\item \tiny Work: send follow-up e-mail to OpenMP committee. 
\item Work:rel: reply to Shantenu about references.
  
\item \tiny \textbf{ <-- End Curr }

\item \tiny Mgmt:wp: add people to LinkedIn =  Mgmt:wp: add Andy Schmidt on LinkedIn +  Mgmt:wp:add Marty.
\item \tiny Mgmt:Spaces: get the reimbursement for car's warranty.
\item \tiny Mgmt:Spaces: get citi bank account + Mgmt:Spaces: get
  refund from AA. 

\item \tiny Mgmt:Spaces: smart TV.
\item \tiny Work: update book summary.  
\item \tiny Work: update movie summary.

\end{enumerate}
\end{frame}

