%\def\PRES{1}
%\ifx{\PRES}
%\iftoggle{\PRES}
%\begin{frame}[allowframebreaks]{Week Plan} 
%\begin{frame}[allowframebreaks]{Running To Do}


\begin{frame} 
\begin{block}{Month Plan}
\underline{Week of February $2^{nd}$, 2018}
\begin{itemize}
\tiny \item \tiny Work: send in references 
\item \tiny Work: follow-up from OpenMP meeting. 
\item \tiny Mgmt:Spaces: get dentist taken care of. 
\item \tiny Comm: talk with Bhakti. 
\end{itemize}
\underline{Week of February $9^{th}$, 2018}
\begin{itemize}
\tiny \item \tiny Work:
\item \tiny
\end{itemize}
\underline{Week of February $16^{th}$, 2018}
\begin{itemize}
\tiny \item \tiny
\item \tiny
\end{itemize}
\underline{Week of February $23^{rd}$, 2018}
\begin{itemize}
\tiny \item \tiny
\item \tiny
\end{itemize}
\end{block}
\end{frame} 

\begin{frame}[allowframebreaks]{Running To Do}

\begin{block}{Week Plan}
Work: talk about RAJA, Work: coding problems, 
Work: send in references for schools and HLF,
Work: follow-up from OpenMP meeting with LBL, 
Mgmt:Spaces: get dentist taken care of, Comm: message
to Vinita, Comm: talk with Bhakti, Comm: talk with Aditi 

\end{block}

\begin{enumerate}
\doneTask{ Work: talk to James Beyer for getting GPU
  stuff}. \dl{Monday} \te{20 minutes} 

\doneTask{ Work:rel: send e-mail to Professor Chapman.} \te{2
  hours} \item \tiny $\rightarrow$ \textbf{Curr}

\item \tiny Work: rel: send e-mail to Barry Rountree about slack-trace
  on github. \te{25 minutes} \pr{UI} 

\item \tiny Work:(uds) socialize the idea of OpenMP loop schedules through
  draft e-mail to Michael and then e-mail to omp-lang comittee. 

\item \tiny Work:rel: apply to LLNL again. 

\item \tiny Work:rel:(hlf): HLF app = Work:rel:(hlf): send e-mail to
  Michael Klemm for HLF \te{1 hour} + Work:rel:(hlf): send e-mail to Michael Klemm
  for HLF + Work:rel:(hlf): write motivation statement +
  Work:rel(hlf): send out reference requests for Professor Crago +
  Work:rel(hlf): send reference requests for Professor Cappello +
  Work:rel(hlf): ask Professor Grigori for a recommendation letter for
  HLF 

\item \tiny Work: rel: send message to Tony to get access to HPC
  facilities. \te{20 minutes} \dl{Feb 9th}. 

\item \tiny Work:rel: get references taken care of for Rutgers
  Application \te{2 hours}. \dl{Monday}

\item \tiny Talk with Helen. \te{} 
\item \tiny Work:rel: follow-up e-mail to LBL Nick Wright and ... 
\item \tiny Work: figure out other universities to apply to \te{25
  minutes} 

\item \tiny Work: admin: get password fixed. 
\item \tiny Work:rel: send e-mail to Barry Rountree about
  talk. \te{25 minutes} \dl{Feb 8th} \pr{UI}

\item \tiny Mgmt:Spaces: read the letter from Carle. 
\item \tiny Mgmt:Health: get dentist appointment for filling. \te{1 hour}
\item \tiny Mgmt:Spaces: dentist appointment re-imbursement this
  week. \te{30 minutes}

\item \tiny Mgmt:Spaces: get glasses. \te{20 minutes}
\item \tiny Mgmt:Spaces: cancel appt.
\item \tiny Work:rel: email to Renata. \te{10 minutes}

\item \tiny Work:rel: make generic reference letter for Professor
  Cappello. \te{20 minutes} 
\item \tiny Work:rel: write draft letter for Michael Klemm.
\item \tiny Work: send follow-up e-mail to OpenMP committee. 
\item \tiny Work:rel: reply to Shantenu about references.  
\item \tiny \textbf{ <-- End Curr }

\item \tiny Mgmt:wp: add people to LinkedIn =  Mgmt:wp: add Andy  Schmidt on LinkedIn +  Mgmt:wp:add Marty.
\item \tiny Mgmt:Spaces: get the reimbursement for car's warranty.

\item \tiny Mgmt:Spaces: get citi bank account + Mgmt:Spaces: get
  refund from AA. 
\item \tiny Mgmt:Spaces: smart TV.
\item \tiny Work: update book summary.  
\item \tiny Work: update movie summary.
\end{enumerate}
\end{frame}

\begin{frame}[allowframebreaks]{Day Plans}
  \underline{\bf{Monday}:} 

  \underline{\bf{Tuesday}:} 
\item \tiny Work: rel: send e-mail to Barry Rountree about talk. \te{25 minutes}
\item \tiny Work: rel: send e-mail to Barry Rountree about slack-trace on github. \te{25 minutes}

  \underline{\bf{Wednesday}:}
\underline{todo}
\begin{itemize}
\item Work: Work: e-mail for RAJA.
\item Work: send Professor Chapman.
\item Work: draft letter to Michael.
\item Work: message to Martin Kong.
\item Mgmt:spaces: book abb. 
\item Mgmt:Spaces: open carle letter. 
\item Comm: talk with Sneha.
\end{itemize} 

\underline{schedule} 
\begin{itemize}
\item 
\item 
\item 
\end{itemize}

\underline{\bf{Thursday}:}

\underline{\bf{Friday}:}

\underline{todo}
\begin{itemize}
\item \tiny Work: reply to Professor Chapman. \te{15 minutes}.
\item \tiny Work: reply for PDT . 


\item \tiny Mgmt:Spaces: fix United Airlines name for first and middle merging.\te{15 minutes}
\item \tiny  Comm: send message to SnehaShinde.\te{20 minutes} 
\end{itemize} 

\underline{schedule}
\end{frame}
