\ifdefined\POSTER
  \begin{columns}
    %-- Column 1 --------------------------------------------------- 
   \begin{column}{0.22\columnwidth}
      \begin{block}{Happiness Generation - must maintain every week.}
\else
 \underline{\bf Happiness Generation - must maintain every week.} 
\fi
        % explain happiness: show gratitude 
        \begin{itemize}
          \tiny \item \tiny happy that I have Atul to show me.  
        %\item \tiny Happy that I have normal life up to this point.  
        %\item \tiny Think about dad saying, I understand, and want
        %you to be happy.
          \item \tiny T 
        \end{itemize}
\ifdefined\POSTER
      \end{block}
\fi

\ifdefined\POSTER
    \begin{block}{Habits}
\else
 \underline{\bf \it Habits} 
\fi 
      \begin{itemize} 
        \tiny \item \tiny back straight + eye contact. 
      \item \tiny lips relaxed. 
      \item \tiny watch what happens when a hot girl talks to you. 
      \end{itemize}
\ifdefined\POSTER
    \end{block} 
  \end{column} %1
\fi

\ifdefined\POSTER
  \begin{column}{0.5\columnwidth}
    \begin{block}{10-year plan}   %-- Block 2-1 
\else 
 \underline{\bf 10-year plan}
\fi
      \begin{itemize}
      \item \small Make someone and dad proud.
      \end{itemize}
\ifdefined\POSTER
    \end{block}
\fi

\ifdefined\POSTER 
    \begin{block}{3-year plan}
\else
\underline{\bf 3-year plan} 
\fi
      \begin{itemize}
      \item \small find someone
      \item \small make 150K
      \item \small network
      \end{itemize}
\ifdefined\POSTER
    \end{block} 
\fi

\ifdefined\POSTER
    \begin{block}{6-month plan}
\else
\underline{\bf 6-month plan}
\fi
        \begin{itemize}
          \small \item \small results + thesis
          \item \small routine + worklife
          \item \small             
          \end{itemize}
\ifdefined\POSTER
    \end{block} 
\fi


\ifdefined\POSTER  
    \begin{block}{Month-by-month}
\else
\underline{\bf Month-by-month} 
\fi 
      %howto: This is most important, and should be re-visited every
      %month and definitely every three months(have fixed time within
      %4 times in the year to do this). 
      \begin{itemize} 
      %\item \small \textit{May:} Work: finish paper  + Work: comm:
      %  finish resume and cover letter.  
      %\item \small \textit{June:} Work: code org and plan + Work:
      %  finish code + worklife: org + worklife: finish emotional int +
      %  Comm: experiences + Comm: TM. 
      \item \small \textit{July:} Work: library, Work:comm: job
        introductions, Comm: meet people.
      \item \small \textit{August:} Work: library documentation and
      experimentation, Work: comm: resume prep + Work:comm:linkedIn +
      Work:comm: interviewing skills + Work:rel: get headstart o jobs (fb and dshaw) + Comm: stay in touch with girls. 
      \item \small \textit{September:} Work:library + Work: paper writing + Work:comm: interviewing. 
      \item \small \textit{October:} Work:paper +  Work:rel:interviewing + Comm: dating 
      \item \small \textit{November:} worklife: review , Work:paper, Comm: dating 
      \end{itemize}
\ifdefined\POSTER 
    \end{block}
\fi

\ifdefined\POSTER
\begin{block}{May goals}
\else
\underline{\bf May goals}\\
\fi 

\begin{enumerate} 
\item \small Work: finish writing goals
  \small \item \small Mgmt:Spaces: clean room 
\item \small worklife: practice implemented work to form habits 
\item \small Comm: meet people 
\end{enumerate}

\ifdefined\POSTER
\end{block}
\fi

\ifdefined\POSTER
\begin{block}{\small \bf Week of September $31^{st}$: job search}
\else
\underline{\bf Week of September $31^{st}$: job search}\\
\fi

\begin{enumerate}
\tiny \item \tiny Work: finish connecting with people regarding implementation. 
\item \tiny Mgmt:Spaces: take care of driver's license. 
\item \tiny 
\item \tiny Comm: meet people 
\end{enumerate}

\ifdefined\POSTER
\end{block}
\fi

\ifdefined\POSTER
\begin{block}{Weekend Plans - March $15^{th}$, 2017 to May $1^{st}$,2017} 
\else
{\underline{\bf Weekend Plans - March $15^{th}$, 2017 to May $1^{st}$,2017}}\\ 
\fi
\begin{itemize}
\item \tiny Weekend of March $17^{th}$: Visit New York City. Details:
\item \tiny Weekend of March $24^{th}$: Visit San Francisco. Details:
\item \tiny Weekend of March $31^{st}$: Visit San Francisco. Details:
\item \tiny Weekend of April $6^{th}$:  Dad is coming, cherry
  blossoms.
\item \tiny Weekend of April $13^{th}$: Visit India.
\item \tiny Weekend of April $20^{th}$: Go to New York.
\item \tiny Weekend of April $26^{th}$: Go to Los Angeles.
\end{itemize}

{\underline{\bf  Weekend plans for weekends between May $1^{st}$, 2017
    and June$1^{st}$, 2017}}\\
\begin{itemize}
\item \tiny Weekend of May $5^{th}$: Visit New York.
\item \tiny Weekend of May $12^{th}$:
\item \tiny Weekend of May $19^{th}$:
\item \tiny Weekend of May $27^{th}$:
\end{itemize}

\ifdefined\POSTER
\end{block}
\end{column}
\fi

%-- Column 3 --------------------------------------------- 

\ifdefined\POSTER
\begin{column}{0.28\linewidth}
\begin{block}{\small \bf Regular Routines}
\else
\underline{\bf Regular Routines}\\ 
\fi 

\input{../../../ViveksLaptop2/life/workLifeMgr/content_regularRoutines_plan}
%\input{content_regularRoutines_plan}

\ifdefined\POSTER
\end{block}
\end{column}%3
\fi

\ifdefined\POSTER
\end{columns}
\fi
