\documentclass[11pt]{article}

\usepackage{ulem}
\usepackage{color}
\usepackage{xspace}
\newcommand{\bllt}{\item \small}
\newcommand{\doneTask}[1]{\item \sout{#1}}
\newcommand{\doneTaskHyp}[1]{\item \textcolor{blue} {\sout{#1}}} %finished a task, in theory
\newcommand{\doneTaskRev}[1]{\item \textcolor{yellow} {\sout{#1}}} % finished a task, but could use a revision
\newcommand{\optTask}[1]{\item  \textcolor{green}{#1}}
\newcommand{\prioTask}[1]{\item  \textcolor{red}{#1}}
\newcommand{\timeEst}[1]{\textit{#1}}
\newcommand{\dueBy}[1]{\textit{#1}}
\newcommand{\MyName}{Vivek~Kale}
\newcommand{\fixme}[1]{\textcolor{blue}{[FIXME: #1]}}
\newcommand{\revision}[1]{\textcolor{blue}{[FIXME comment : #1]}}
\newcommand{\todo}[1]{\textcolor{blue}{[TODO: #1]}}

\newcommand{\newSituation}[1]{\underline{\textbf{Situation:} #1} }
\newcommand{\newMiniSituation}[1]{\underline{\textbf{Mini-situation:}
    #1} }


% NOTE: these situations go into word  document 

% examples of such situations are interviews, conferences, weddings,
% dates, 
\newcommand{\newImportantSituation}[1]{\underline{\textbf{Important situation:} #1} }

\newcommand{\doneSituation}[1]{\sout{\underline{\textbf{Situation:} #1}} }

\begin{document}

\underline{\textbf{Summary:}} This document summarizes situations
that are upcoming, or have already past. Each event should have an approximate date. These
are drafts for those mapping to the actual calendar events.  Within
the calendar event details/notes is where the ``pre-notes'' and
``post-notes'' go. Also, the week plan curr should have the situation
noted after these situations have been added.  These situations should
be listed every week (and checked every night), so that pro-active
planning can take place. This list has the fairly big
situations. Smaller situations go in the weekly doc; they could be
integrated here too.  

%TODO: fix the below todos 
Be sure to connect the worklife cheat sheet experience  here. 

Add method to improve and learn from these situations. 

Discuss methods for error-correction, error-prevention, error-detection, and error-tolerance.

\todo{add experience/rule pair}  
\todo{define better what experience/rule pair is. }
\todo{add pre-post} 


\newMiniSituation{ }
\begin{itemize}
\item 
\item 
\item 
\end{itemize} 

\newSituation{Meet with Asm:} 
\begin{itemize} 
\item don't get stressed about something someone said about you.
\item talk to dad. 
\item don't hold in, and let out your feelings. 
\item articulate and speak more clearly through phone . 
\end{itemize} 

\newSituation{Shuchi's engagement party: Summer 2011} 
\begin{itemize}
\item
\item don't get mad about jacket 
\item
\end{itemize}

\newSituation{Meet with Neha Damle} 
\begin{itemize} 
\item avoid getting corny quickly  
\item if you get corny, don’t try to counter it 
\end{itemize} 

\newSituation{Holiday Party 2012}
\begin{itemize}
\item 
\item don't have to talk about drinking as much 
\end{itemize}

\newSituation{Meet with girls with Bariz - Dec. 2012} 
\begin{itemize} 
\item good with talking and writing down situations 
\item good clothes - helped her pick out from a crowd. 
\item 
\end{itemize} 

\newSituation{Meet with Pramod (first meeting):} 
\begin{itemize}
\item meet and talk about work less 
\item make fewer specific comments about work 
\end{itemize}

\newSituation{Meet with Rucha:} 
\begin{itemize} 
\item don't say ``I love you''. 
\item don't get mad just before going home . 
\item no need to get a mercedes. 
\end{itemize}

\newSituation{Meet with Pramod(second meeting):} 
\begin{itemize} 
\item don't talk about Rucha as much . 
\end{itemize} 

\newSituation{Talk with Sama:} 
\begin{itemize} 
\item don’t leave her hanging . 
\item be clear when you like someone, and also when you don’t (could be bad later)  . 
\end{itemize} 

\newSituation{Meet with Neha Joshi - Jan 2013} 
\begin{itemize} 
\item don’t say “yo yo no worries”. 
\item answer texts quickly without hesitation. 
\item good to say ``it would be good to meet you in person'' - jokingly, shows relaxation . 
\end{itemize} 

\newSituation{Meet with Mohini - 2013} 
\begin{itemize} 
\item be clear with a no answer, and no wavering - level 0. 
\item don’t take her for dinner, and instead talk about it. 
\end{itemize} 

\newSituation{Meet with Ajay Virkar and friends for birthday- april2013} 
\begin{itemize} 
\item don't be crazy while in line. Act normal 
\end{itemize} 

\newSituation{Atul's engagement}
\begin{itemize}
\item talk to Ankur.
\item be ready to dance.
\item good to be quiet next day.
\end{itemize} 

\newSituation{Shuchi's wedding} 
\begin{itemize} 
\item Don't talk to girl so much and tell her she is pretty. 
\item Don't talk to Shital and joke around about love either. 
\item Be less drunk maybe with tenn girl - could be less childish. 
\end{itemize} 

\newSituation{NetIP pre-event 1}
\begin{itemize}
\item -
\item - 
\item - 
\end{itemize}

\newSituation{BMM 2013} 
\begin{itemize} 
\item don't high-five. 
\item no need to say useless things about clothes.
\end{itemize} 

\newSituation{NetIP pre-event 2}
\begin{itemize}
\item don't have to talk about nothing to that girl - have a plan. 
\item 
\end{itemize} 

\newSituation{Meet at Mona Rishi's house: Aug 2013}
\begin{itemize}
\item don't get overstressed about meeting someone.
\item don't go overboard and be mechanical in love. 
\end{itemize} 

\newSituation{Meet with Arti:} 
\begin{itemize} 
\item Don’t get worked up about a text where she asks “oh I thought you live in Berkeley”  -- instead don’t answer. 
\end{itemize} 

\newSituation{NetIP:} 
\begin{itemize} 
\item intro: 
\item first night: 
\item second day: 
\item dinner: 
\item Sunday night: 
\item After-party on Monday: 
\end{itemize} 


\newSituation{Meet with Ssaswas} 
\begin{itemize} 
\item don’t act like a goofy and overly nice guy. 
\end{itemize} 

\newSituation{Meet with Archana}
\begin{itemize} 
\item good to be fun and open 
\item don't get nervous when asking what you think about us 
\item manage a bit better , don't do out of the blue things 
\item maybe try a bit harder to get with her at the top of the mountain 
\end{itemize} 

\newSituation{Anchit's  wedding - Nov 2013}
\begin{itemize}
\item don't have to ask about clothes to wear - shows that it's about you only, which it's not 
\item don't bring up archana 
\item don't have to say ``you look young''  in to Deepa auntie 
\item -
\end{itemize}

\newSituation{Bariz's wedding} 
\begin{itemize} 
\item good to be enthusiastic during toast 
\item don't be too negative about dropping someone 
\item don't have to be funny about someone crossing the road. Make it clear whether you are joking or serious. 
\end{itemize} 

\newSituation{Bariz’s reception - November  2013} 
\begin{itemize} 
\item be careful about lying , ppl can pick it up. 
\item good to have hair gel. 
\item don't say weird sexual jokes , not needed .
\end{itemize}

\newSituation{Holiday Party 2013}
\begin{itemize}
\item Good to take breaks. 
\item watch for people that are unexpected. 
\item watch for bumping into someone's car - be very careful right afterwards and go a longer route- don't text and drive (esp. if there is something going on). 
\end{itemize} 

\newSituation{Meet with Abhi1:}
\begin{itemize} 
\item good job on first date, and that you joked around a lot and talked about natural things. 
\end{itemize} 

\newSituation{Meet with Bronis }
\textit{Pre-notes}
\begin{itemize}
\item make notes on what to say before hand
\item schedule meeting when to have it.
\end{itemize}

\newSituation{Coding Session with Amanda}
\begin{itemize}
\item know airport better, prep for management of spaces 
\item talk less loudly. 
\item be clear about what your work plan is. 
\end{itemize} 

\newSituation{Meetup with Deeptha:} 
\begin{itemize} 
\item be clear in texts , leave no room for ambiguity
\item don’t get worked up about a text saying I thought you were in Chicago
\end{itemize} 

\newSituation{Meet with Abhi2:}
\begin{itemize} 
\item don't need to be crazy about being fat
\end{itemize} 

\newSituation{Meet at John BarleyCorn} 
\begin{itemize} 
\item Watch for saying ``how tall are you'' . 
\item Contain nervousness that came from awkwardness . 
\item Listen to Ridhima about not stressing about problem . 
\end{itemize} 

\newSituation{Meet with Divya} 
\begin{itemize} 
\item look at whether email was needed, avoid getting upset/nervous 
\item be less nervous, be ready to bring up tough subjects in front `` what do you think about us'' 
\item don't talk about BMW too much 
\end{itemize} 

\newSituation{Meet with Rishi with Sadhana for breakfast} 
\begin{itemize} 
\item don't talk about french toast too much 
\item be early to meeting
\end{itemize} 

\newSituation{Email about quitting}
\textit{Pre-notes}
\begin{itemize}
\item get timing right, see if you can spend less time (but perhaps ok)
\item don't get nervous afterwards and send an email about something else to Prof. Gropp. 
\end{itemize}

\newSituation{Meet at Dinner for invitation} 
\begin{itemize} 
\item don't yell at Aryav - carry a conversation with Atul, Ridhima  
\end{itemize} 

\newSituation{meet with Bronis} 
\begin{itemize} 
\item maintain truth, sincerity 
\item when someone says something, maybe get angry, but don't keep it 
\end{itemize} 

\newSituation{Rishi's bday}
\begin{itemize} 
\item don't get crazy about photos 
\item make sure to not get awkward with girl at end 
\item make sure to not talk too much once a girl approaches you 
\item be ready to talk in a group, esp. with Sadhna and you by yourself 
\end{itemize}

\newSituation{Dinner at Ritika's}  
\begin{itemize}
\item don't have to talk as much about how Atul and Ridhima met with dad 
\item can sit elsewhere away from crowd. 
\item tell waiter about cup, be less intrusive.
\end{itemize}

\newSituation{Pooja}  
\begin{itemize} 
\item don't worry about pics with Rashmi aunty -next time 
\item avoid nervousness , or nervousness about being nervous 
\end{itemize} 



\newSituation{Sangeet}   
\begin{itemize}
\item don't give drink , be careful here, know where to stand roughly 
\item don't talk too much and go deep into something. 
\item ask about seating arrangements , careful with drinking, don't bring obvious stuff up, 
\item don't talk too much with mom to act like something is going on. 
\end{itemize}


\newSituation{Fourth of July Lunch} 
\begin{itemize} 
\item don't bring up politics 
\item good to save it with coming back 
\end{itemize}


\newSituation{Wedding} 
\begin{itemize}
\item careful about saying groomslady 
\item don't say congrats randomly 
\item have plan when talking about shoes 
\item don't say anything about fake hair 
\end{itemize}

\newSituation{Reception} 
\begin{itemize}
\item  know whether to meet others or not 
\item know what to say about getting a drink  
\item  don't say boring things to Kavita 
\item good to be humble after reception 
\end{itemize} 


\newSituation{Casino} 
\begin{itemize}
\item be less crazy, even if it's late 
\end{itemize}


\newSituation{meet with Atul's high friends} 
\begin{itemize}
\item be less talkative, but it's ok 
\item be open to card games 
\item be sure when someone asks ``what do you do?''
\end{itemize}

\newSituation{meetup at Irazu's} 
\begin{itemize}
\item don't talk about motorcycle as much. 
\item maybe can fill awkward silences, but seems ok. 
\item good to have people to talk to on side. 
\item avoid conversation with Divya regarding Atul and Ridhima are too close - shows stress. 
\item avoid stress conversation with Naren about work 
\item maybe don't say you don't know how to dance. 
\end{itemize} 


\newSituation{Meetup with Family: home eat dosai}
\begin{enumerate}
\item Be less upfront about shoes problem with Amit  : talk positively, rather than negatively. 
\item Know when to say ``you sit down and eat''. 
\item Be more intentional, e.g. with photo. 
\item Say what you want about Gary quickly, no hesitation. 
\item talk less about ``does Aryav get lost?'' - good save 
with getting lost in our house - though better if it's less long-winded of a point. 
\end{enumerate} 

\newSituation{Meetup with Family: 301 mongolia}
\begin{enumerate}
\item Be careful about food / mongolian bbq  + Know how to sit and eat at a restaurant. 
\item Say things quickly in a big group: avoid saying delayed gratification. Need more intention. 
\item Can be a bit more intentional with meeting about food. 
\end{enumerate} 

\newSituation{Meetup with Family 3}
\begin{enumerate}
\item Don't bring up new orleans (ok, and how am I supposed to know this???- by experience and this sheet) 
\item Know about your work/research, be ready to answer specific questions about work/research. Answers should be concise!!
\item mostly good on relaxing. 
\end{enumerate} 

\newSituation{Text to Sneha}
\begin{enumerate} 
\item check the stress before you send. 
\item make sure you are not repeating yourself from previous conversations. 
\item check motivation/intention for sending
\end{enumerate} 

\newSituation{Meet with Prof. Gropp - 7/22}
\begin{enumerate}
\item be sure to check for logistics. 
\item practice opening when you come into office. 
\item good to make detailed notes, but just practice before-hand. 
\item notes on what not to say. 

\end{enumerate} 

\newSituation{Toastmasters TableTopics} 
\begin{enumerate} 
\item Practice beginning part multiple times (that's where we mess up and get nervous)
\item Make better transitions. 
\item Write down (-..? -)
\end{enumerate}

\newSituation{Meet at Ankur's in group}
\begin{enumerate} 
\item Don't talk too much about blog Actuary to Ridhima 
\item Be more intentional about boat 
\item \textit{maybe} don't second-guess if you've said something awkward, maybe  - could leave it alone and say something good?
\item know about timing of when to leave.
\end{enumerate}


\newSituation{Meet with Shyunti 1}
\begin{enumerate} 
\item don't have to back yourself if you are saying something disagreeable. 
\item be cautious about saying stock things like ``see anything you like'' 
\item be sure to manage and find the car in time 
\item be sure to check the city and logistics. 
\item could avoid generic conversation about cities - be sure to have a point here. 
\item good to show interest about Big Bowl ginger 
\item don't necessarily have to butter-coat something like ``can't find parking'' - did good here
\end{enumerate}

\newSituation{Meet with Shyunti 2}
\begin{enumerate} 
\item don't have to say too much about Barrington , and parking garage 
\item don't be too defensive about going to LA 
\item Specific Experiential Note: (\textit{Maybe} ) Remember stuff you said previously about where you'll be , to help keep it consistent!
\item good to say ``boutique shop was nice'' 
\end{enumerate} 

\newSituation{Meet at Ankur's house 2}
\begin{enumerate} 
\item make planning, and explain plan clearly - ask others what to do. 
\item don't have to say too much about Ankur's clothes, should be fine. 
\end{enumerate} 

\newSituation{Meet at Ankur's house 3}
\begin{enumerate} 
\item could bring fewer negatives about spicy mac and cheese  - topic is overdone. 
\item could be less awkward about pointing attention to Ankur. 
\end{enumerate} 

\newSituation{Meet at Kukreti's}
\begin{enumerate} 
\item  don't say ``neglected''
\item  watch laughter
\item  know what to do when Rakesh uncle comes (script) but is ok.
\end{enumerate}


\newSituation{Meet with Prof Gropp} 
\begin{itemize} 
\item work on not saying extra things (to generate extra work), 
\item prep the main points, esp. beginnning in advance, prioritize (like was done for last meeting)
\item Did good on ``not saying extra'' towards the end. 
\end{itemize} 

\newSituation{Chinmay coming over} 
\begin{enumerate} 
\item don't have to always talk 
\item smile and say funny things to ease tension quickly , break ice .  Then can stop talking . 
\end{enumerate}

\newSituation{Meet with Prof Gropp - day of deadline}
\begin{enumerate} 
\item try to have quick plan for meeting , in time crunch 
\item get out notepad before hand 
\item good to be natural 
\end{enumerate} 

\newSituation{SC poster} 
\begin{itemize}
\item  come up with the results model more quickly.  Do full results earlier, to avoid questions later.
\item Do writing based on what Prof Gropp says to do, can figure this out later (put less priority).
\item  make sure the mechanics of latex get solved earlier,
beforehand. Have a list of notes for latex somewhere for quick fixes:
beamer poster style files, alignment of text with textpos, figures
referencing in another document,  minipages, code listings, logo at
top, title movement. For tex file, know the general ideas for the
different formats (IEEE, bib, etc).
\item Time management: rough schedule before submission.

\item Process for managing:  1. Excercise(shorter/frequent) + happiness + worry recognition
and elimination   2. define tasks, break down tasks quickly, then
group) and 3. time estimation and prioritize in your head. Recognize
when you need to do this (should be every 2-3 hour
chunks). 4. Communicate results/thoughts + Presentation
skills. (figure out where this goes)

\item Prioritize for deadlines ,      .
\item  plan quick frequent communication with advisor to show progress
before deadline  -
\item  be sure to be near office when Prof. Gropp around to show working .

\item  make sure to show that you understood what your advisor said
quickly , by implementing or saying, yes that makes sense I'll put it
in at this time.

\end{itemize}


\newSituation{Wedding re-enactment} 

\begin{itemize} 
\item have entering / welcome figured out when you meet Pinky auntie.
\item be sure to make others feel that you are in control.

\item  be aware of not saying ``Yea, I guess'' when someone says something empathetic.
\item don't get too worked up about where to sit. - know arrangement
  before-hand. 


\item Mbe sure to be clean - bathroom, dinner table. 
\item good to show relaxation and joking about ``shotgun''.


\item bounce back after saying ``read harry potter''. Remember
  thatHarry Potter isgen knowledge that you should know. 
\item good to have a rough point - wasn't too intense, esp. because you asked Ridhima about what it means for her.
\item Comm: vocal variety: practice your laugh, and improve it; watch not to laugh too much.
\end{itemize} 


\newSituation{Planning trip for California} 

\begin{itemize} 
\item call early before wasting time to try stuff. 
\item could take notes to help understand trip/flights. 
\item spend less time looking for stuff - put a time limit on decisions. 

\end{itemize} 

 \newSituation{Meet with Neha }

\begin{itemize}
\item Pre-: Have all clothes ready well in
      advance, figure out the right place to go, plan topics of
      conversation(UIUC, what do I do, emotions on first date), square
      away logistics beforehand like parking/clean up car.  

\item Post-:  don't order Pesto, have plan on which place to go and what you'll do. The conversation should be easier.
\item plan out a couple of words to talk about. Talking about Prom was good, but could be less hesitant at places - watch for points dying down. 

\item Maybe joke a little less , and talk about mature topics. - but this is ok

\item Know in advance what to say where you stay - standard questions -- this should help to make things more smooth - but this is ok

\end{itemize} 

\newSituation{Meet with Nitin Mama}
\begin{itemize} 
\item  Post: don't have to be too surprised ,  know when to say no,  come earlier to avoid uncertainty, make plan earlier (people want to know plans).
\end{itemize} 

\newSituation{TM role of grammarian} 
\begin{itemize} 
\item manage time to prep more
\item  when you aren't prepped, just remember worklife cheatsheet
\item  good to be short and concise, be sure to
 have a brief prep note for each role. 
\item Shout to be less hesitant.  

\item For table topics, need to rehearse based on theme  (think about words that are important)

\end{itemize} 

\newSituation{Trip planning for Atlanta} 
\begin{itemize} 
\item find way to book even earlier. 
\item check for flights connecting through Atlanta to see if you can get a better fare - check such things and make notes on them. 
\item packing takes about 1.5 hours for going. Be sure to take black formal shoes in addition to brown shoes (avoid the situation where you have to buy something). 
\item money allocation 
\item 
\end{itemize} 

\underline{\textbf{Atlanta trip netip}} 
\newSituation{meet at hotel lobby} 
\begin{itemize} 
\item 
\item 
\end{itemize} 

\newSituation{Party at tongue and groove} 
\begin{itemize} 
\tiny \item find location earlier, and figure out parking sooner 
\tiny \item meet Chicago girl was good, just talk less to the guy and talk to the girl. Note how the girl talked to you afterwards. 
\end{itemize}

\newSituation{Lunch at true foods}
\begin{itemize} 
\item good to be chill to start. 
\item avoid being negative about work, e.g., I'm a software engineer - be proud!!  Make yourself stand out! 
\item good to ask about where you live, shows you have interest. 
\item Good to have intentional points, see if you can get them earlier. 
\item ask about if we can meet up early -- see how you can get a number. 
\item jaywalking reaction was relaxed.  Might have been a bit bland, but not wrong. Could just increase on intentional, but was ok. 
\item I'm meeting some friends - see if you could spice it up? Honesty, but also happiness.  But was good, since you were honest. 
\end{itemize} 

\newSituation{Speed date} 
\begin{itemize} 
\item plan ahead of time , get details on whether it's good - shouldn't be surprised at the last minute. 
\item watch for boring conversation with vanessa, watch her twitch - (and adjust on the fly! maybe)
\item watch for the weird conversation with uma and do NOT keep going if it gets weird - avoid charity case. 
\item know how to talk about wine - don't talk too much  .  Make sure others are engaged - not about you. 
\end{itemize}  

\newSituation{Meet at Buckhead Theatre} 
\begin{itemize} 
\item planning for arrival could have been better. 
\item be careful with Purvi. 
\item be ready to dance with girls you like, if needed. Be sure to know where to dance. 
\item good to just be chill. 
\item know how to make quick conversation. 
\item good to talk to Uma afterwards  , but don't let guy keep saying you are good guy. 
\end{itemize} 

\newSituation{Saturday After party in lobby} 
\begin{itemize} 
\item talk to purvi about number - it's ok 
\item ask red-haired girl for number - you look nice - avoid the intensity maybe (level 6/0  (? does  that work?) , level 4  ).  
\item be less desperate about food, but maybe it's ok  (level 4 : not about you )  
\item watch when someone else is talking to someone  -  further, could read body language (listen , then send ) 
\item 
\end{itemize}


\newSituation{  Sunday brunch} 
\begin{itemize} 
\item don't have to be planning too ahead - though it's ok , since you joked it off and didn't react more - that's what made it fine. 
\item 
\end{itemize} 

\newSituation{Sunday sessions} 
\begin{itemize} 
\item Good to talk to girl giving  cookies , be happy generally . Interesting Challenge: see if you can change this into a more intimate conversation. 
\item Be sure to present well with name tag
\item Figure out how girl said hi - (you can call me ``kale'').  Be sure to get names!!!  Have good memory!  Train/practice the name game. 
\item - 
\end{itemize} 



\newSituation{Purvi to bar} 
\begin{itemize} 
\item Don't get caught up on stalker. 
\item (Following the follower a bit nerdy. - just keep mouth shut. 
\item make sure you make sense. (level 2). Did you drive. 
\item Be sure to manage drinks better. 
\item 
\end{itemize} 

\newSituation{Banquet} 
\begin{itemize} 
\item good to talk 
\item ok to forget doctor about vanessa, could maybe close better at the end with a point.
\item good conversation about gulab jamun. 
\item watch for dancing periods. 
 
\item good to talk about buckeyes: Challenge: make it spicier. 

\item watch for ``assembly language'' hesitation. Be confident about what you are saying makes sense. 

\item good to make conversation about ``what's near alabama''. Challenge: how to keep it going? 
\item good to talk to Purvi at end. - though don't be too harsh. 

\end{itemize} 

\newSituation{Banquet after-party} 
\begin{itemize} 
\item talk with more intention to girl about dance 
\item know card games in social situation - blackjack/poker . 
\item Talk to Natasha : be sure to have intent about coming.  Keep inspiring/interesting. 

\item talk less about guys aren't crazy - could have more common/inspiring - seemed ok, watch for points.  
\item Get the girl's number!!! 
\end{itemize} 

\newSituation{Monday Lunch} 
\begin{itemize} 
\item computer software joke - seemed good , stick to it. 
\item narcissitic joke pick-up line: watch for level 6/0 - 
\item 
\end{itemize}  


\newSituation{Talk to Tower Research} 
\begin{itemize} 
\item get resume prepped. 
\item don't get let down by others .  Be resilient to happiness when the guy says life is like x, and when you see Microsoft interviewing ppl on the spot. 
\end{itemize} 

\newSituation{Meet with Atul and Ridhima} 
\begin{itemize} 
\item Avoid over-thinking things about shoes. --> Think a bit more carefully, but more importantly, keep a calm mind and think habits. 
\item Silence is ok.  Could think about sub-situations when situation arises. 
\item Good to joke and relax at the end. 
\end{itemize} 

\newSituation{Fashion Show} 
\begin{itemize} 
\item Could think about some sub-situations when situation arises , like talking to Sadhna's sister. 
\item Think more about entrance, think about parking/logistics/   .  Prioritize a bit more .  Keep card/ money to avoid. 
\item Have more of a habits/picture of yourself. 
\item know the city, and wander less. Know: airports, subway, ground/highway, streets/directions, 
\item Have full process: Comm, work, dotlink, habitsSummary, habits , experience-feedback. 
\end{itemize}

\newSituation{Car dealer} 
\begin{itemize} 
\item be less hesitant to say no. 
\end{itemize} 


\newSituation{Meeting 1} 
\begin{itemize} 
\item be less goofy
\item don't say ``that was the weirdest eww'' 
\item know when you are nervous, and stop yourself from saying extra things. 
\item stop yourself from saying stuff when not needed, like ``now that you three are here''. When people are gathering together, don't have to say anything. 
\end{itemize} 


\newSituation{Engagement party} 
\begin{itemize} 
\item Speak clearly.
\item Know when to not talk too much. 
\item 
\end{itemize} 


\newSituation{Brunch} 
\begin{itemize} 
\item Good to explain to Ridhima how going elsewhere is good. If there is a chance to go and make a point about life, do it . People will think of it ..
\item 
\end{itemize} 

\newSituation{Meet with Rupali} 
\begin{itemize} 
\item if there is something controversial, don't say anything too contentious. Think win-win. 
\item if there is a signal, good to try to kiss. Don't go further though afterwards. 
\end{itemize}

\newSituation{Meeting 2} 
\begin{itemize} 
\item Don't get nervous about the water. 
\item Good to not say anything after ``..but we have a GPS''. 
\end{itemize} 

\newSituation{SC poster session} 
\begin{itemize} 
\item Prepare for the session, to ensure you have a flow of what to say. 
\item If someone asks a personal question, don't get too upset, and calm down and answer carefully. 
\item Maintain consistency of loud voice, and lips relaxed. 
\item If you get someone that knows your work, explain the parts they don't know , and make sure they know you are doing good work 
(good explanation during Todd's visit). 
\end{itemize} 

\newSituation{Cray party}
\begin{itemize} 
\item When you are being funny, watch out for being childish. 
\item If you are being random, you may induce negative thoughts about beer (even when it's random). Randomness can cause negative thoughts to come out. 
\item If there is something that you connect on an emotional level, use that to ice-break.  (Good to talk about Tony).  
\end{itemize} 

\newSituation{Conversations at SC}
\begin{itemize} 
\item Talking to .. 
\item Talking to PNNL. 
\item 
\end{itemize} 

\newSituation{Party }
\begin{itemize} 
\item Good to keep a conversation going with French. Have a positive topic to talk about. If you do, people should be readily talk about themselves. 
\item If at a party, keep the body language up (notice how girl recognized you). People come out of nowhere. 
\item 
\end{itemize} 

\newSituation{Diwali dinner} 

\begin{itemize} 
\item If there is something exciting about a girl, watch for getting out of control and talking about it. <--- key point : we tend to lose our listening skills, when we do this. 
\item Think before speaking. Be more intentional about the ICS dinner. 
\item If you see some flyer, and you remember from childhood and want to tell, stop to think carefully what you want to say. 
\end{itemize} 

\newSituation{Meet with Rupali} 
\begin{itemize} 
\item \textit{Experience:} Rupali didn't know what to say after you explained.  \textit{Rule:} If you are going to say something, be intentional. 
\item Know what to say that can make someone hurt. 
\item Watch for signals where you are too intense, esp. if you are by yourself. 
\item If someone is thinking something(leaving tomorrow) , listen carefully to emotions. 
\item Don't make eye contact when getting intimate. 
\end{itemize} 

\newSituation{Airport MDW->MSY} 
\textbf{Pre-:}
\begin{itemize} 
\item 
\end{itemize} 
\textbf{Post-:}
\begin{itemize} 
\item \textit{Experience:} Get rental gas helps. \textit{Rule:} Get things that save time at the airport. 
\item \textit{Experience:} Checked in bags for \$ 60.00 \textit{Rule:} if tempted to buy extra, think about other ways to make convenient (and how we can cope without it). 
\end{itemize} 

\newSituation{poster session} 
\begin{itemize}
\item could benefit from prep time. Need to add time for prep, since this is equally important as the  content 
\item don't be defensive to guy asking you tough questions
\item - 
\end{itemize} 

\newSituation{Cray Party} 
\begin{itemize}
\item could benefit from prep time. Need to add time for prep, since this is equally important as the  content 
\item don't be defensive to guy asking you tough questions
\item - 
\end{itemize} 

\newSituation{Banquet} 
\begin{itemize}
\item 
\item - 
\end{itemize} 

\newSituation{Airport MSY->MDW} 
\begin{itemize} 
\item \textit{Experience:} Have all trip taken care of 3 nights before (since travel it is difficult do). \textit{Rule:} 
\item \textit{Experience:} If there are changes, talk to mom and dad about the trip in advance. Maybe let them know changes. \textit{Rule:} 
\item getting to airport: be sure to check rental car or other transport, and book in advance. 
\item booking flight: double-check flight time before booking. 
\item Take time out 1 night before (10 mins) to do check-in, think about vulnerabilities. 
\item Be calm at the ticketing counter. If missed flight, be calm and explain situation clearly. (People don't like stressed out people). 
\item Be prepared at security to look good. 
\item airport gate: watch for sniffling, respect others space. 
\item in airplane: avoid looking at other people's magazines. Watch personal space. 
\end{itemize} 

\newSituation{TM speech} 
\begin{itemize} 
\item talking to evaluator: think about question for reacting to eval. before asking it. Be sure not to get too defensive. 
\item during speech: See how maintain consistency of body language throughout. 
\item Talking to girl after speech: don't go deep into programming. If someone asks, immediately know what to say. 
\end{itemize} 

\newSituation{ Aryav's bday party  } 
\begin{itemize} 
\item \textit{Experience:} Saying ``wow'' about cake. \textit{Rule:} If silence with Ridhima, then it's ok. 
\item \textit{Experience:} Watch for long explanations to Amit's mom. \textit{Rule}Have stock answers memorized. Just like introductions are pre-written in TM.  Before going to party, know common interactions and prep for them. 
\end{itemize} 

\newSituation{Meet with Prof. Gropp}
\begin{itemize} 
\item could improve beginning part by coming early. 
\item could reduce distraction by taking care of computer screen 
\item good to prepare what to say beforehand briefly
\end{itemize} 

\newSituation{TM dinner} 
\begin{itemize} 
\item dinner 
\end{itemize} 

\newSituation{Meet Rupali4  $\rightarrow$ Date} 
\begin{itemize}
\item plan a bit more in advance to reduce money. Avoid cities for dates because it adds more. 
\item Remember past topics, and see if you can avoid talking about them. 
\item don't talk about friends too much - friend zone. 
\item If Rupali doesn't understand something, don't get stressed about it. 
\item Extra credit: if a weird topic comes up, slowly back out of it. Change the subject in style. 
\end{itemize}

\newSituation{Eye Doctor visit $rightarrow$ one-on-one meeting }
\begin{itemize}
\item Don't be too hesitant if you think someone is accusign you of not wearing contacts. Again, think and plan ahead , esp. in terms of  if/then .
\end{itemize}

\newSituation{VZW wireless store $\rightarrow$ one-on-one meeting } 
\begin{itemize}
\item notice the body language and vocal variety diff. 
\item avoid trying to break silence. Don't try to ask question about cases just to show that you'll care.  (Know business a bit, beforehand)
\end{itemize}

 \newSituation{ Meet for Aryav's bday $\rightarrow$ gathering}
 \begin{itemize} 
  \item  Be intentional, be more careful. 
  \item  Watch for talking about you, when watching Aryav's pictures. 
Have a point when you talk. When there is silence, don't worry too much (silence is fine). Did silence ever kill a friendship? No. Why? It's those funny moments that did.... 
%\item \tiny  \textit{Situation:} Car dealership: 
\end{itemize} 

%TODO: make general template with three levels: practice points + generalizations + positive points/static rules throughout, experience-rule pair (static to real time), things to watch out for
\newSituation{Christmas Dinner $\rightarrow$ House meeting } 
\begin{itemize} 
\item \textit{Practice Points:} When is your PhD done? When is your work done?  --- Be sure not to talk too much about yourself.  
\item \textit{Positive Points:} made a joke about the scent.
\item \textit{Things to do before situation:} 
\item \textit{Experience:} saying this is a good Christmas dinner.  \textit{Rule:} If you are alone with someone, don't say anything extra like ``this is a good Christmas dinner''. Why? That comes out as forced. 
\item \textit{Experience:}  \textit{Rule:} 
\item \textit{Error-prevention:}  ---  Things that didn't happen but could have, and how you would prevent them. 
\item \textit{Error-tolerance:} -- Things that didn't happen, but could have, and if they did, how you would tolerate them - generalize. 
\end{itemize}




\newSituation{Talk to Rupali $\rightarrow$ Skype Date} 
\begin{itemize}
\item Good to ask Ridhima beforehand in non-intrusive way in front of everyone. Could spend more time thinking about it. But you shouted, so that was good. 
\item Learning to say no, assertively.  
\item Don't waffle around when there is a silence. 
\end{itemize} 

\newSituation{Talk to Prof. Gropp for slides}
\begin{itemize} 
\tiny \item \tiny Be less wavering once he says something (don't have
to follow up too much) 
\item \textit{Positive Points:} 
\item
\end{itemize} 

\newSituation{Aryav's bday} 
\begin{itemize} 
\item  %  \tiny \item \tiny \textit{Situation:} Meet for Aryav's bday.  \
\textit{Pre-:} Be intentional, be more careful. \textit{Post:} Watch
for talking about you, when watching Aryav's pictures. Have a point when you
talk. When there is silence, don't worry too much (silence is
fine). Did silence ever kill a friendship? No. Why? It's those funny moments that did.... 
\end{itemize} 

\newSituation{New Year's Eve 2014 $\rightarrow$ House Party}
\begin{itemize} 
\item Be sure to have a point, when asking again about the restaurant. 
\end{itemize}

\newSituation{Defense} 
\begin{itemize} 
\item Be sure to listen to advisor. Not listening sticks out.
\item Be prepared for afterward, even simple note is fine. (Sometimes,
  after a big event, there could be other smaller events). 
\item Find ways to reduce nervousness. 
\item Good to keep it short. 
\end{itemize} 

\newSituation{Breakfast Feb 27th} 
\begin{itemize} 
\item Clean dishes after
\item Open the silverware container, rather than putting it on the
  island. 
\item 
\end{itemize}

\newSituation {meet for Dinner}
\begin{itemize} 
\item Be relaxed - blue/gray socks. 
\item 
\end{itemize}

\newSituation{Meet with Anu}
\begin{itemize}
\item \textit{Practice Points:} Could improve on shirt humour. 
\item \textit{Positive Points:} did good work at beginning with
  humour. stopped to think about stuff . 
\item \textit{Things to do before situation:} 
\item \textit{Experience:} overthinking at coffee :   \textit{Rule:}
  if there is discussion about social situation, don't ask about rules
  about ``how should this be done''.  
\item \textit{Experience:}  \textit{Rule:} 
\item \textit{Error-prevention:}  ---  Things that didn't happen but
  could have, and how you would prevent them. 
\item \textit{Error-tolerance:} -- Things that didn't happen, but
  could have, and if they did, how you would tolerate them - generalize. 
\end{itemize}

\newSituation{Interview} 
\begin{itemize}
\item Shout. 
\item I work on performance tuning scientific applications like
  weather simulation using low-overhead dynamic multi-core scheduling
  strategies. 
\end{itemize} 

\newSituation{Interview at XPACC} 
\begin{itemize} 
\item 
\item 
\end{itemize}  
\item \tiny \textit{BMM Travel planning:} Post: planning hotel , use experience from before to plan current.   
\item \tiny \textit{Travel planning:} 
\newSituation{Graduate Get-together $\rightarrow$ get-together} 
\begin{itemize}
\item \textit{Things to do before situation:} figure out events that
  have people and be ready. 

\item  \textit{Experience:} see someone nice \textit{Rule}: if see
  someone nice, smile. 
\item \textit{Experience:} spoke unclear about wine \textit{Rule:} if
  someone says about wine, don't have to explain yourself. 
\item \textit{Experience:} saw woodley   \textit{Rule:} good to not
  avoid. 
\item \textit{Error-prevention:}  -- meet nice person - smile. 
\item \textit{Dress code} earrings, boots, cross t-shirt. 
\end{itemize} 


\newSituation{Mem. Day Atul and Ridhima} Pre-: 
\item \tiny \textit{Graduation:} Pre-:   Post-:
\item \tiny \textit{Party } Pre-:  Post-:


\newSituation{\textit{BMM2015(Wedding)}}
Pre-: registration
packet, if meet w/ vk, stand straight no smile, and walk.
Post-: Fine to smile.

\newSituation{{Mixer Thursday:}
  Pre-: Clothes ready
  Post-: Good to be calm in beginning, don't say negative
  things. 
  
  \newSituation{\textit{Cruise:}}
  Pre-:  Post-: don't have to make random conversation with Ruchi.

\newSituation{Speed Dating:}
Pre-:  Post-:  Good to be
energetic, don't have to point out the problem with app
(too nerdy). 

\newSituation{Club Nite at Fire N Ice}: 
Pre-:  Post-:
don't have to be too open with Sameer. Know how to dance at
these things (have a dance move).   

\newSituation{SnehaBandhan} 
Pre-: Post-: 


\newSituation{Meet Mona and Leena in August}
Pre-: Confirm time, leave by 7PM, wear business clothes,
rent a car? Discuss
savv0ddude , talk about girl, explain what you are
doing(rehearse). 
have closing for meeting next, take picture and put post on FB.
Post-: Can suggest a new time, explain time when you meet,
Good to keep back straight and lips relaxed, Don't take glasses off,
don't lose confidence when Mona leaves to get water. 

{Practice Points:} When is your PhD done? When is your work done? 
-- Be sure not to talk too much about yourself.

\begin{itemize}
\item \textit{Positive Points:} made a joke about the scent.
\item \textit{Things to do before situation:}
\item \textit{Experience:} saying this is a good Christmas dinner.
  \textit{Rule:} If you are alone with someone, don't say anything extra like
  ``this is a good Christmas dinner''. Why? That comes out as forced.
\item \textit{Experience:}  \textit{Rule:}
\item \textit{Error-prevention:}  ---  Things that didn't happen but
  could have, and how you would prevent them.
\item \textit{Error-tolerance:} -- Things that didn't happen, but
  could have, and if they did, how you would tolerate them -
  generalize. 
\end{itemize} 

\newSituation{Talk with Sruthi}
Pre-: check connection, Find where to talk, figure out things to talk
and center conversation around. Post-: be less apologetic about not
making your points.
\begin{itemize} 
\tiny \item \tiny 
\end{itemize} 


\newSituation{Google Interview $rightarrow$ one-on-one work date} 
\begin{itemize} 
\tiny \item \tiny 
\end{itemize} 

\newSituation{Google Interview follow-up} 
\begin{itemize} 
\item 
\item 
\end{itemize}

\newSituation{Meet with Udatta Kaka} 
\begin{itemize} 
\item 
\item 
\end{itemize}

\newSituation{Meeting with Professor Gropp} 
\begin{itemize} 
\item 
\item 
\end{itemize}

\newSituation{Toastmasters - General Evaluator $\rightarrow$} 

\newImportantSituation{Meet for Interview} 
\begin{itemize} 
Pre-:  shoe shine, makeup, check area, look up people, full review
Post-: be less angry when asked about clearance, good to watch for
points, keep it simple 
\end{itemize} 

\newSituation{ Meet with Sruthi}
\begin{itemize} 
\item \tiny Pre-: print directions from hotel to
\item \tiny place, talk little + intent, back straight.   Post-: Note that when
you paused, she asked a question. 
\item \textit{Positive Points:} made a joke about the scent.
\item \textit{Things to do before situation:}
\item \textit{Experience:} saying this is a good Christmas dinner.
  \textit{Rule:} If you are alone with someone, don't say anything
  extra like
  ``this is a good Christmas dinner''. Why? That comes out as forced.
\item \textit{Experience:}  \textit{Rule:}
\item \textit{Error-prevention:}  ---  Things that didn't happen but
  could have, and how you would prevent them.
\item \textit{Error-tolerance:} -- Things that didn't happen, but
  could have, and if they did, how you would tolerate t
\end{itemize} 

\newImportantSituation{Meet for Sangita's wedding.} 
\begin{itemize} 
\tiny \item \tiny  Pre-:  
Post-: get sandals ahead of time, avoid scripting too much.  .. 
\tiny \item \tiny 
\end{itemize} 


          %\tiny \item \tiny Situation: Meet Mom and Dad:  coord:               
          %Pre-:  Post-: have topics to discuss, talk about plan                
          %beforehand- see time comittment, mention the work you need           
          %to do.                                                               


\newImportantSituation{Interview with BNL} 

\begin{itemize} 
\tiny \item \tiny 
\item \tiny 
\end{itemize} 

\newImportantSituation{Interview with USC/ISI} 
\begin{itemize} 
\tiny \item \tiny 
\item \tiny 
\end{itemize} 

\end{itemize} 
\newSituation{Situation: Talk to Anu:} 
\begin{itemize} 
\item \tiny 
\item \tiny Pre-:   
\item \tiny Post-:  talk
\end{itemize} 
          % less      
          %  about you, don't have to make statements that are logical

%\tiny \item \tiny \textit{Toastmasters} Post-: L2: 

%\tiny \item \tiny \textit{Talk to Anita} Pre-: get ready for
%phone call by looking good. Post-: laugh less (watch for
%``interesting'' diversions.

%\item \tiny \item  \textit{Shwaytha dinner:} Pre-: 1. Talk to
%  Udatta Palekar (distance yourself). 2. Talk to Shwaytha about
%  how she has been doing

\newSituation{TM} 
\begin{itemize} 
\tiny \item \tiny good to prep in advance, but prep even more. L1:
Watch for changing at the last minute.
\tiny \item \tiny L3: good to stay consistent L4: say thank you
instead of thanks.
\item \tiny 
\end{itemize} 

\newSituation{Wedding} 
\begin{itemize}
\item \tiny watch for getting in people's way.
\item \tiny Prep more.
\item \tiny Good to smile.
\end{itemize} 

\newSituation{HLF} 
\begin{itemize} 
\tiny \item \tiny Stay consistent with back straight. 
\item \tiny Keep intentionality in mind. 
\end{itemize}

\newSituation{IWOMP}
\begin{itemize}
\item \tiny 
\item \tiny
\end{itemize} 

\newSituation{Meet Udatta Kaka 2} 
\begin{itemize} 
\end{itemize} 

\newSituation{Interviews} 
\begin{itemize} 
\tiny \item \tiny 
\end{itemize}  


\newSituation{Business Career Fair} 
\begin{itemize}
\tiny \item \tiny 
\item \tiny 
\end{itemize}


\newSituation{Dinner at Pandharipande} 
\begin{itemize} 
\item \tiny don't show anger to people 
\item \tiny 
\end{itemize} 

\newSituation{Dinner with Anita} 
\begin{itemize}  
\item \tiny Don't get too angry quickly  - 
\tiny \item \tiny Make it quick - 
\end{itemize}   

\newSituation{NetIP}
\begin{itemize}
\tiny \item \tiny Mgmt:Spaces: 
\tiny \item \tiny Comm: 
\tiny \item \tiny Comm: 
\end{itemize} 

\newSituation{SC} 
\begin{itemize} 
\item \tiny 
\item \tiny 
\end{itemize} 

\newSituation{Sandia Interview} 
\begin{itemize}  
\item \tiny 
\item \tiny 
\end{itemize} 


\newSituation{Meet with Saroj 1} 
\begin{itemize} 
\tiny \item \tiny 
\item \tiny 
\end{itemize} 

\newSituation{Meet with Saroj 2}

\begin{itemize}

\tiny \item 
\end{itemize} 

\newSituation{Meet with Saroj 3} 
\begin{itemize}
\tiny \item \tiny 
\item \tiny 
\end{itemize} 

\newSituation{Meet at end of Job} 
\begin{itemize} 
\tiny \item \tiny 
\tiny \item \tiny 
\end{itemize} 

\newSituation{Meet for Xmas} 
\begin{itemize} 
\item \tiny Avoid Donald trump reference. 
\item \tiny Give gifts. 
\end{itemize}  




\newSituation{Meet with Saroj 4}
\begin{itemize}
\tiny \item \tiny Don't say too many complicated things about city
being small.  
\item \tiny If you made plans, don't change them last minute. 
\item \tiny Don't get too into someone's space. 
\end{itemize}

\newSituation{Facebook Phone Interview} 
\begin{itemize}
\item Interview -:   Post-: Don’t say you too at the end, write the
  code cleanly, good to write hello world in the text box, Know how to
  end the conversation, get headset. 
\item 
\item
\end{itemize}


\newSituation{Meet with Manjula 1} 
\begin{itemize} 
\tiny \item \tiny Smile less often. Back straight. 
\item \tiny Don't assume the worst in people. 
\item \tiny Could be upfront earlier.  
\end{itemize} 


\newSituation{Meet Mom and Dad} 
\begin{itemize}
\item \tiny  coord: 
Pre-:  Post-: have topics to discuss, talk about plan beforehand- see time comittment, mention the work you need to do.
\end{itemize} 


\newSituation{Situation:} Talk to Anu: 
\begin{itemize} 
\item \tiny Pre-:   Post-:  talk less about you, don't have to make statements that are logical. 
\end{itemize}



\newSession{IOP - exposure 0:} 
\begin{itemize}
\item \tiny 
\tiny \item \tiny formulate plan to talk about specific situation and
analyzed and understand the regret. 
\item \tiny journaled 
\end{itemize}

\newSession{IOP - general 1} 
\begin{itemize}
\item \tiny 
\tiny \item \tiny formulate plan to talk about specific situation and
analyzed and understand the regret. 
\item \tiny journaled 
\end{itemize}


\newSession{IOP - rumination} 
\begin{itemize}
\item \tiny 
\tiny \item \tiny formulate plan to talk about specific situation and
analyzed and understand the regret. 
\item \tiny journaled 
\end{itemize}

\newSession{IOP - DBT } 
\begin{itemize}
\item \tiny 
\tiny \item \tiny formulate plan to talk about specific situation and
analyzed and understand the regret. 
\item \tiny journaled 
\end{itemize}

\newSession{IOP - mindfulness } 
\begin{itemize}
\item \tiny 
\tiny \item \tiny formulate plan to talk about specific situation and
analyzed and understand the regret. 
\item \tiny journaled 
\end{itemize}

\newSession{IOP - exposure 1:} 
\begin{itemize}
\item \tiny 
\tiny \item \tiny formulate plan to talk about specific situation and
analyzed and understand the regret. 
\item \tiny journaled 
\end{itemize}




\newSession{IOP - exposure 2:}
\begin{itemize}
\tiny \item \tiny Person discusses life decisions. 

\item \tiny wrote down pros  list and what I won't ruminate about. 
\item \tiny Should thinkin about live with the worst-case scenario -
  cons list. 
\item \tiny Got very down because I thought about something else. 




\item \tiny divorce 
\item \tiny feeling tired 

\item \tiny emotions 
\item \tiny both options are good, not believing  

\item \tiny feeling vulnerable because you told someone something that
  you though to hide. 


\end{itemize}



\newSession{IOP - exposure 3:}
\begin{itemize}
\tiny \item \tiny buying a plane ticket 
\end{itemize}


\newSituation{Baby Shower:} 





\newSituation{NYE party with Rishi:} 

\newSituation{Meetup at Kapoor’s house} 

\newSituation{Meeting at Nitin Mama’ s house:}  


\newpage 

\underline{\textbf{ Common Situations}}
\newSituation{ Meeting with Prof Gropp: } 
-don’t get worked up about something specific, if it’s about you


\newSituation{ HPC group meeting:} 
-don’t get worked up about something specific, if it’s about you

\newSituation{CASC Group lunch:}
-avoid conversations where you are the center of attention
-it’s not about you

\newSituation{CASC division meeting:}
-don’t eat donuts before hand
-avoid coming late
-be prepped to answer questions

\newSituation{ Yoga classes:} 

\newSituation{Bhangra classes:} 

\newSituation{Presentations: } 

\newSituation{Speeches/Toasts:} 

\newSituation{Coding:} 

\newSituation{Results:} 

\newSituation{Paper writing:} 


% ---- Attic -----
\newpage 


\comments{
       The possibility of a 1-year restriction if you don't make it
        must be put up front.
        I feel that put up front the possibility of a 1-year
        restriction on reapplying if you don't make the interview.
        As an interviewee coming out of Graduate school and not
        knowing about the interview process, knowing this would makes
        planning easier.
        I wanted to know the possibility of a 1-year restriction on
        re-applying if you don't makethe interview.

        Please let graduating PhD 
             I feel that, for graduating PhD students, the first email
        sent for an interview request needs to state up front the
        possibility of a 1-year time frame
        for re-applying.
I feel that, for graduating PhD students, the first email sent for an
interview request needs to state the possibility of a 1-year time
frame for re-applying. The reason is that knowing this possibility
could better help to manage time for the current interview as well as
to help for near-term career planning.

While there were a lot of study materials given at once, each of the
study materials were helpful for preparing for the interview. I also
liked that the main recruiter gave me specific advice to help prepare
for my second-round interview.

        %Knowing this possibility could help to plan                                                                                                                                                                               
        %the current interview and for near-term career planning.                                                                                                                                                                 
        I did not know about the 1-year time frame within which one
        canno.

        apply again to a position at Google. If I had known this, I
        would have
        interviewed at a better time, for example, after my coursework
        was
        done and my dissertation was deposited.

        Goal: give feedback/inform
        Specific Goal: tell what could be improved,

        1. What: tell us possibility of the 1-year restriction to
        re-apply before we start the process!
        2. Why this is important to help improve the process
          a. I really want a good job right after graduation, and I
          want to do the best I can now for you. To find the best
          match, this is the right time to find a connecction, but
          you didn't.

          b. It did not feel right. This did simply did not feel
          right. I felt I was an adversary,
          rather than working with you to make a connection.

        3. Conclusion: Tell us everything for time management.
        It helps to do the best we can, now, and makes it easier to
        re-apply in the future.

        I expect that the top company like Google would show
        understanding.
        While there were a lot of materials given all at once, the
        study materials were really helpful for preparing for the
        interview. I also liked that the interviewers gave specific
        advice to help prepare for the interview.
}


\newSituation{Cocktails for a cause -feb 9th }
\textit{Pre-notes}
\begin{itemize}
\item get tickets in advance
\item check who is coming
\item spend half-hour deciding on clothes
\item running before hand
\end{itemize}

\newSituation{MBA tour - feb 9th}
\textit{Pre-notes}
\begin{itemize}
\item find good business clothes.
\item go with resumes, in case someone asks.
\item Find parking quickly.
\item Know your story, don't get sucked into anything
\end{itemize}

\newSituation{Feb. meetup }
\begin{itemize}
\item Get location of place to go. Talk to Atul.
\item Know people, invite others
\item Keep it simple
\end{itemize}


\newSituation{Atul's Wedding}
\textit{Pre-notes}
\begin{itemize}
\item clothing for each day
\item know who is coming , invite list
\item do what Ridhima says
\end{itemize} 

\newSituation{Dinner with Amanda}
\begin{itemize}
\item 
\item  
\item 
\item 
\end{itemize}


\newSituation{Post-doc lunch} 
\underline{\textit{Pre-notes}}
\begin{itemize}
\item Wear white and brown shoes
\item comb hair before going
\item 
\end{itemize}

\underline{\textit{Post-notes}} 
\begin{itemize} 
\item 
\item 
\item  
\end{itemize}



\end{document}
