\begin{frame} 
\frametitle{Outreach(channels)}
\begin{enumerate} 

\item \small --

\end{enumerate} 
\end{frame} 


\begin{frame} 
\frametitle{Outreach(substantiated)}
\begin{enumerate} 
\item Send AK message about plans for next weekend and in San Francisco. 
\item Get in touch with Kopal 
\item Nisha Puntambekar
\item Talk to Sita 
\item Talk to Payal
\item Talk with ND?
\item Nandu kaka's friends
\item Srishti Srivastava 
\end{enumerate} 
\end{frame} 



\begin{frame} 
\frametitle{Ladies-AK schedule}
\begin{enumerate} 
\item \textbf{July 23}: send message about meeting
\item \textbf{July 28}: meet up maybe with friends
\item \textbf{August 5}: lunch/dinner plans
\item \textbf{August 8th}:  meet up with parents 
\item \textbf{August 15th}: Hang out 
\item \textbf{Sept 15th}: Hang out 
\item \textbf{sept 30th}: actually start thinking about this girl
\item \textbf{oct 30th}: actually start thinking about doing stuff
\end{enumerate} 
\end{frame} 

\begin{frame} 
\frametitle{Ladies-AK, Topics for discussion}
\begin{itemize} 
\bllt parents resemblance to our conversations
\bllt late night work 
\bllt ak 2 
\bllt Mom should come to dinner
\bllt Awesome that you listen and read all the emails. 
\bllt going to India 
\end{itemize} 
\end{frame}




\begin{frame} 
\frametitle{\textit{Steps to meeting someone}}
\begin{enumerate} 
\bllt seek through channels. 
\bllt have a face-to-face meeting with that person.
\bllt start talking online 
\bllt start talking through gchat 
\bllt talk on the phone
\bllt meet up in person, possibly with friends
\bllt meet up in person by yourselves 
\bllt tell her you like her.
\bllt meet on a date
\bllt chat +  meet again
\end{enumerate} 
\end{frame} 

\begin{frame} 
\frametitle{Asking on a date}
\begin{itemize} 
\bllt 
\bllt 
\bllt 
\end{itemize} 
\end{frame} 





\begin{frame} 
\frametitle{Describe yourself}
\begin{itemize} 
\bllt relaxed and confident
\bllt calm, naive
\bllt logical
\bllt no sense of humor, just simple 
\bllt fit, and well-built
\bllt smile 
\bllt caring about others
\end{itemize} 
\end{frame}

\begin{frame} 
\frametitle{On the date}
\begin{itemize} 
\bllt stay on topic, don't digress
\bllt talk about common interests. 
\bllt discuss work. 
\bllt talk about the people you are rooming with.
\bllt ask about where she is 
\end{itemize} 
\end{frame}

\begin{frame} 
\frametitle{Flirting}
\begin{itemize} 
\bllt work, weather, small things that are connected, 
\bllt how fast do you drive?
\bllt how often do you work out?  What work-out do you do? 
\end{itemize} 
\end{frame}




\begin{frame} 
\frametitle{ Questions / Topics }
\begin{itemize} 
\bllt What is your favorite movie? Contact ,   movies with a deep message, 
\bllt What is your favorite restaurant in Berkeley? south berkeley, salvadorean 
\bllt What TV shows do you like? Office
\bllt What Music do you like? Trance 
\bllt Where is your favorite place to hang out? embarcadero 
\bllt What is your favorite drink?  ginger ale
\bllt What is your favorite place to eat?  Crepes place in Berkeley
\bllt What books do you read?  Pride and Predujice, Thomas Friedman, Catch-22, 
\bllt What is your work on?  Computational science and engineering, Using risk analysis and game theory to improve computation 
\bllt 
\end{itemize} 
\end{frame}




