\begin{frame} 
\frametitle{Room Shape} 
\begin{enumerate}
\item \small Make bed
\item \small all stuff is off coffee table
\item \small Medicines are in place
\item \small put meds in container every Sunday, put in backpack
\item \small charge cell phone every night, put in charger. 
\item \small put books away 
\item \small clean bathroom 
\item \small make sure clothes are folded properly
\item \small ensure bed is clean.
\item \small vacuum floor. 
\end{enumerate}
\end{frame} 

\begin{frame} 
\frametitle{Kitchen Shape} 
\begin{enumerate}
\item \small ensure dishes are clean
\item \small put mail in bag
\item \small sweep floor. 
\item \small make sure counter top is clean
\item \small make sure door is locked. 
\end{enumerate}
\end{frame} 

\begin{frame} 
\frametitle{Living Room Shape} 
\begin{enumerate}
\item \small make sure that no belt is lying 
around, no clothes are on couch. 
\item \small sweep floor. 
\item \small make sure counter top is clean. 
\item \small make sure door is locked. 
\end{enumerate}
\end{frame} 

\begin{frame} 
\frametitle{Car Shape} 
\begin{enumerate}
\item \small Fuel should be at full every week
\item \small Oil change every 5000 miles from Art's automotive 
\item \small Make sure no papers are in passenger's seat 
\item \small Trunk should be clear of clothes. 
\end{enumerate}
\end{frame} 

\begin{frame} 
\frametitle{Wallet Shape} 
\begin{enumerate}
\item \small All flaps should not be torn
\item \small Need at least 40 dollars
\item \small Put drivers license, credit card in the proper place.
\end{enumerate}
\end{frame} 

\begin{frame} 
\frametitle{Apartment External Shape} 
\begin{enumerate}
\item \small Check Parking tag 
\item \small Go to roofdeck every weekend
\item \small Check mail 
\item \small pay rent at on the 27th of every month (use proper chase check)
\item \small lock door every day. 
\end{enumerate}
\end{frame} 

\begin{frame} 
\frametitle{Personal Grooming Shape} 
\begin{enumerate}
\item \small Haircut
\item \small Nails cut
\item \small Clean shirt
\item \small Cologne 
\item \small Eliminate Blemishes
\item \small shave
\item \small make sure contact lenses are on
\item \small take meds in the morning (zoloft + concerta)
\item \small wear belt
\item \small matching socks, socks should not be torn
\item \small jeans should be waist-high
\item \small breath shouldn't smell, teeth should be clean. 
\item \small make sure jeans don't have stains on them
\item \small zip up pants
\item \small wear good shoes 
\end{enumerate}
\end{frame}

\begin{frame} 
\frametitle{Body Shape} 
\begin{enumerate}
\item \small teeth (floss + brush morning and evening)
\item \small calves (bounces , 50 reps in morning)  
\item \small biceps (curls, 35 reps in afternoon) 
\item \small thighs ( squats, 50 reps in afternoon ) 
\item \small wrists ( 50 reps in evening )
\item \small abs  (100 reps)
\item \small pecs (75 pushups)
\item \small stretches (15 mins)
\item \small meditation (10 mins)
\end{enumerate}
\end{frame} 

\begin{frame} 
\frametitle{Diet Shape} 
\begin{enumerate}
\item \small Instead of sweet cereal, eat corn flakes
\item \small Have heavier breakfast, and light lunch. 
\item \small Do running in afternoon 
\end{enumerate}
\end{frame} 



\begin{frame} 
\frametitle{Eating Shape} 
\begin{enumerate}
\item \small Food eaten without spilling on side of plate. 
\item \small Make sure food does not touch shirt. 
\item \small Ensure that drink does not drop on floor. 
\item \small Don't touch food with hands. 
\item \small Keep food all in one area of plate.  
\item \small Drink water without spilling. 
\end{enumerate}
\end{frame} 

\begin{frame} 
\frametitle{Desktop Shape} 
\begin{enumerate} 
\item \small -
\item \small -
\item \small -
\item \small -
\end{enumerate}
\end{frame} 

\begin{frame} 
\frametitle{Communication Shape} 
\begin{enumerate} 
\item \small speak clearly and coherently 
\item \small understand the social situation
\item \small dress well to make an impression on others, groom well
\item \small think before you speak
\item \small don't react defensively
\item \small answer questions calmly 
\end{enumerate}
\end{frame} 

\begin{frame} 
\frametitle{1. Speaking skills Shape} 
\begin{enumerate} 
\item \small don't stop mid-sentence and switch topics 
\item \small enunciate 
\item \small keep your tone flowing, emphasize on the correct syllable
\item \small don't say useless things 
\item \small use correct grammar 
\item \small don't click your teeth 
\item \small avoid jumping from topic to topic(if something is on your mind that leads to something else, don't jump to that)
\end{enumerate}
\end{frame} 

\begin{frame} 
\frametitle{2. Gestures Shape} 
\begin{enumerate} 
\item \small When explaining,  don't move your hands around
\item \small make eye contact with the person you are talking to
\item \small don't put your hands in your pockets
\item \small don't smile too much 
\item \small don't bite your lip 
\end{enumerate} 
\end{frame} 

\begin{frame} 
\frametitle{3. Posture Shape} 
\begin{enumerate} 
\item \small Walk with back straight
\item \small Don't flail when walking
\item \small Keep arms swinging by side
\item \small Keep head up 
\item \small Shoulders straight 
\end{enumerate}
\end{frame}


\begin{frame} 
\frametitle{4. Social Structure Understanding Shape} 
\begin{enumerate} 
\item \small relationship
\item \small friends
\item \small co-workers
\item \small apartment 
\item \small roommate
\item \small grocery stores 
\end{enumerate}
\end{frame} 

\begin{frame} 
\frametitle{5. Answering questions Shape} 
\begin{enumerate} 
\item \small Know answers to common questions
\item \small be able to impromptu by finding the right answer roughly 
\end{enumerate}
\end{frame} 

