\begin{frame}
\frametitle{Contents Life Notes}
\tableofcontents[part=1]
\end{frame}

\subsection{Priorities}
\begin{frame}
\frametitle{Priorities}
\begin{enumerate}
\item \small Work
\item \small Health
\item \small meeting fe
\item \small Activities/involvement
\item \small Parties + friends
\end{enumerate} 
\end{frame}

\subsection{Organization}
\begin{frame}
\frametitle{Organization}
\begin{enumerate}
\item \tiny Receipts should be in one place
\item \tiny Backpack should contain everything needed
\item \tiny Car should have adequate supplies
\item \tiny Throw all little pieces of paper in the garbage
\item \tiny Clean kitchen every weekend
\item \tiny Make bed 
\item \tiny Laundry every weekend 
\end{enumerate} 
\end{frame}

\subsection{Social}
\begin{frame} 
\frametitle{Social}
\begin{enumerate} 
\item \tiny Go to parties sponsored by organizations
\item \tiny Find through fb the parties that others are going to. 
\item \tiny Go to events that are of interest to you (cloud computing) 
\item \tiny Go to yoga classes
\item \tiny Attend non-profit work through Asha
\item \tiny Attend Tennis club
\end{enumerate} 
\end{frame} 

\subsection{Getting a date}
\begin{frame}
\frametitle{Getting a Date}
\begin{enumerate}
\item \small \url{ http://www.wikihow.com/Category:Getting-a-Date}
\item \tiny
\end{enumerate}
\end{frame}


\subsection{Communication}
\begin{frame} 
\frametitle{Communication}
\begin{enumerate} 
\item --
\item --
\end{enumerate}
\url{http://www.wikihow.com/Category:Conversation-Skills}
\url{http://www.wikihow.com/Communicate-Effectively}
\end{frame}

\subsection{Presentations}
\begin{frame} 
\frametitle{Presentations}
\begin{enumerate} 
\item \tiny Put website up. 
\item \tiny Do presentations. 
\item \tiny If someone asks, what is the work that you do, have memorized what 
you do: ``I work on optimization of HPC applications such as human heartbeat simulation to run in half the time it originally would. This optimization allows
for more science per hour, increasing efficiency and progress of scientific discovery. It also makes code that might have run in a lifetime into code that can run 
in just a few days. `` 
\item \tiny If someone asks, what is your role at work, say: ``I work as a Lawrence Scholar at LLNL, completing my PhD . Hoping to be done in a year or so. ''
\end{enumerate} 
\end{frame} 

\subsection{Work}
\begin{frame} 
\frametitle{Work}
\begin{enumerate} 
\item \tiny Do weekly status updates. 
\item \tiny Check for papers. 
\item \tiny Submit work to conferences. 
\end{enumerate} 
\end{frame} 

\subsection{Appearance}
\begin{frame} 
\frametitle{Appearance}
\begin{enumerate} 
\item \tiny Hair combing.
\item \tiny Halath for blisters.
\item \tiny Cut nails once a week.
\item \tiny Deodorant.
\item \tiny Facial: 
\begin{itemize}
\item Teeth whitening.
\item Clean zits by washing face daily.
\item Shaving.  
\item Flossing.
\end{itemize}
\end{enumerate}  

More info: \url{  } 

\end{frame} 


\subsection{Handling Rejection}
\begin{frame}
\frametitle{Getting over someone's rejection}
\begin{enumerate}
\item \tiny  Learn from all  the mistakes that you made. 
\item \tiny  Think that they are just your friends
\item \tiny  They are rejecting the concept of you and her together, not you as a person. 
\item \tiny \textit{ The thought of someone else replacing you is meaningless, because you are not the same as that other person}. 
\item \tiny \textit{The feeling that she will come back for you can be left open.} 
\item \tiny Think that she's gonna come back and talk to you eventually.  
\end{enumerate}
\item \small \url{ http://www.wikihow.com/Category:Getting-a-Date}
\end{frame}
