\begin{frame}
\frametitle{Coding Table of Contents}
\tableofcontents[part=1]
\end{frame} 

\subsection{Scheduler Runtime}
\subsubsection{Scheduler Runtime: Must have} 
\begin{frame}
\frametitle{$\mu$-Scheduler runtime: Must Have}
\begin{enumerate} 
\bllt \sout{create interface}
\bllt Consider usage in context of MPI shared memory extensions.
\bllt Testing infrastructure for correctness. 
\begin{itemize} 
\item \tiny Check answer of Dot Product. Can use norms. 
\item \tiny Check all threads are running and doing work. 
\item \tiny Check for lock and unlock (no data races). 
\item \tiny Check total work done, regardless of sched. (no tasks should be left behind) 
\item \tiny Check locality state info is getting updated. 
\end{itemize}
\bllt Incorporate state information in scheduler. 
\begin{itemize}
\item \tiny Add integrate MPI slack-conscious sched. 
\item \tiny Add in thread slack-conscious sched. 
\item \tiny Add in tasklet locality tags. 
\end{itemize}
\end{enumerate} 
\end{frame} 

\subsubsection{Sched Runtime Should have}
\begin{frame}
\frametitle{Sched Runtime: Should Have}
\begin{enumerate} 
\bllt Create separate files for schedulers(?). 
\bllt See if we can get an OpenMP like interface. 
\bllt make proper output, and redirect to file. 
\bllt use gnuplot scripts to get data from output file. 
\bllt package into ar and shared library. 
\end{enumerate}
\end{frame}

\subsubsection{Sched Runtime : Nice to have}
\begin{frame}
\frametitle{Sched Runtime: Nice to have}
\begin{enumerate} 
\bllt put in proper timers for slack-conscious scheduling
\bllt get profiling to measure dequeue overhead 
\end{enumerate} 
\end{frame} 

\subsubsection{Post-processing data}
\begin{frame}
\frametitle{Plotting data}
\begin{enumerate} 
\bllt Plotting for num processes versus perf 
\bllt Transpose
\bllt Runtime overheads for different tuned versions
\bllt output parsing scripts 
\end{enumerate} 
\end{frame} 

\begin{frame}
\frametitle{Output post-processing}
\begin{enumerate} 
\bllt Memorize the code needed for file I/O. Consider C++ file I/O. 
\bllt Have a standard table for printing the output through a set of parameters.
\bllt Learn python to post-process the output from an application. 
\end{enumerate} 
\end{frame} 

\begin{frame}
\frametitle{Plotting}
\begin{enumerate} 
\bllt Understand how to create a histogram 
\bllt Know how to label axes and graph title. 
\end{enumerate} 
\end{frame} 

\subsubsection{Git Repo}
\begin{frame}
\frametitle{Git Repo}
\begin{enumerate} 
\bllt Make sure everything compiles before checking in. 
\bllt Check how to do branches in git. 
\bllt Do frequent check-ins. 
\bllt Know what to do in the event of a conflict. 
\end{enumerate} 
\end{frame} 

\subsubsection{Git Repo}
\begin{frame}
\frametitle{Git Repo}
\begin{enumerate} 
\bllt Make sure everything compiles before checking in. 
\bllt Check how to do branches in git. 
\bllt Do frequent check-ins. 
\bllt Know what to do in the event of a conflict. 
\end{enumerate} 
\end{frame} 

\subsubsection{SSH login guide}
\begin{frame}
\frametitle{SSH login guide}
\begin{enumerate} 
\bllt Fix \texttt{known\_hosts} if login creates a problem. 
\bllt Make sure there is an easy way to login without the RSA key.
\end{enumerate} 
\end{frame} 

\subsubsection{Benchmark tests}
\begin{frame}
\frametitle{Tests}
\begin{enumerate} 
\bllt Benchmark tests for load imbalance across cores \texttt{ld} is the linker.
\bllt test for variation across Iteration timesteps
\bllt test for variation across different MPI procs 
\bllt test for variation of dequeue overheads, for one particular thread. 
\bllt test for non-uniformity of dequeue overhead, across threads. 
\end{enumerate} 
\end{frame} 

\subsubsection{Work Improvement}
\begin{frame}
\frametitle{ }
\begin{enumerate} 
\bllt Send email on tasks/habits on Monday
\bllt Add tasks in JIRA 
\bllt finish cases for theoretical analysis + send this out
\bllt finish writing of theoretical analysis. 
\end{enumerate} 
\end{frame} 
