% Question:  What are the role of computer technology in society today ? Do we really need computers?
% Question: Do we really need computers?


\begin{frame}
\frametitle{Committee} 
\begin{itemize}

\end{itemize} 
\end{frame} 

\begin{frame} 
\frametitle{Comm Org} 

\begin{itemize} 
\item Meeting Time 
\item Meeting Place
\end{itemize}

\end{frame} 


\begin{frame}
\frametitle{Speech Projects} 
\end{frame} 


\begin{frame}
\frametitle{Management Projects}
\end{frame}



\begin{frame}
\frametitle{Toastmaster} 
\begin{enumerate} 
\tiny \item \tiny 
\end{enumerate} 
\end{frame} 

\begin{frame} 
\frametitle{Theme} 
\end{frame} 

\begin{frame}
\frametitle{Introductions}
\end{frame} 

\begin{frame}
\frametitle{Speakers}
\begin{itemize} 
\item Introduction
\item Talk to Evaluation
\end{itemize} 
\end{frame} 

\begin{frame}
\frametitle{Speech Evaluator} 
\begin{itemize} 
\item Listening 
\end{itemize}
\end{frame} 

\begin{frame} 
\frametitle{Feedback Sheets} 
\begin{itemize}
\item gives feedback to Speakers. 
\item 
\end{itemize}
\end{frame}


\begin{frame} 
\frametitle{Table Topics}
\end{frame}


\begin{frame} 
\frametitle{Table Topics Master} 
\end{frame} 

\begin{frame} 
\frametitle{Timer} 
\end{frame} 

\begin{frame} 
\frametitle{Word of the day}
\end{frame} 

\begin{frame} 
\frametitle{Grammarian} 
\end{frame} 

\begin{frame} 
\frametitle{General Evaluator} 
\begin{enumerate} 
\tiny \item \tiny 
\item \tiny 
\end{enumerate} 
\end{frame}


\comments{

\begin{frame}
\frametitle{Engineer, Mathematician ,Phycist Fire}

{\small A physicist, an engineer and a mathematician were all in a hotel
sleeping when a fire broke out in their respective rooms.} 
\end{frame} 

\begin{frame}
\frametitle{ Phycist} 

\begin{enumerate} 
\small \item \small The physicist woke up, saw the fire. 
\item \small  ran over to his desk, 
\item \small pulled out his CRC, and began working out all sorts of fluid dynamics
equations. 
\item \small After a couple minutes, he threw down his pencil, got
a graduated cylinder out of his suitcase, and measured out a
precise amount of water. 
\item \small He threw it on the fire, extinguishing
it, with not a drop wasted, and went back to sleep.
\end{enumerate}
\end{frame}

\begin{frame}
\frametitle{Engineer} 
\begin{enumerate} 
\small \item \small The engineer woke up, saw the fire
\item \small ran into the bathroom
\item \small turned on the faucets full-blast,
\item \small flooding out the entire apartment, which put out the
  fire, and then went back to sleep.
\end{enumerate}
\end{frame}

\begin{frame} 
\frametitle{Mathematician}
\begin{enumerate}
\small \item \small The mathematician woke up, saw the fire, 
\item \small Ran over to his desk
\item \small began working through theorems,
  lemmas, hypotheses , you -name-it. 
\item \small and after a few minutes, put down his pencil triumphantly
  and exclaimed, ``I have \textbf{proven} that I \textbf{can} put the fire
  out!''... , and THEN went back to sleep. 
\end{enumerate} 
\end{frame}

}

%\begin{frame}
%\frametitle{Family}
%\begin{itemize}
%\item How close should you be to family? 
%\item Are your parent's always your best mentors? Can we learn things we didn't learn about before through people that aren't parents? 
%\item People say that she's like a sister to me. 
%\end{itemize} 
%\end{frame}


\begin{frame}
\frametitle{General guidelines} 
\begin{itemize} 
\item 
\item 
\item 
\end{itemize} 
\end{frame} 



