\begin{frame}
\frametitle{Opening}
\begin{itemize}
\item Shake hands 
\item Ladies and Gentleman, Distinguished Members and Guests 
\end{itemize}
\end{frame} 

\begin{frame}
\frametitle{Introduction}
\begin{itemize}
\item \small Tennis is one of the world's major sports, w/ 4 grand
  slam events (the largest being Wimbledon). 
\item \small Hi, my name is Vivek and  I am going to tell you about my passion for tennis. 
\item \small I believe it has played an important role in my life. 
\item \small After this talk, I hope you will get to know how exactly tennis has shaped my mind and my view of life. 
\end{itemize} 
\end{frame} 

\begin{frame} 
\frametitle{My Perspective of Tennis Basics}
\begin{itemize} 
\item \small serve
\item \small forehand  
\item \small backhand  
\item \small volley
\item \small run to get to ball
\item \small most importantly, don't smash racket at end of point. 
\item \small To play a point in a match, you need to be able to put these all together.  \\
\end{itemize}  
\end{frame} 

\begin{frame} 
\frametitle{ Styles of Play (Everyone's has different skills that they are stronger/weaker at, and one should play a style that capitalize on strengths)  }

\begin{enumerate} 
%\item \small \textbf{Roger Federer:}
%  \begin{itemize}
%    \item \tiny has a well-balanced strategic game, and likes to serve and volley. 
%    \item \tiny Can't run as hard for long periods of time, so gets a bit offset in long matches.   
%  \item \tiny
%  \end{itemize}

%\item \small \textbf{Rafael Nadal: }
%\begin{itemize}
%  \item \tiny plays a defensive game from the baseline. 
%  \item \tiny Runs very hard, which allows him to win long matches. 
%\end{itemize}
\item \small \textbf{My Style} 
\begin{itemize}
\item \tiny Earlier on, I tried to run around a lot, as I had more time to work out. I didn't play with as much strategy through, as I was inexperienced. 
\item \tiny Now, I don't run around as much and play a  bit more offensive, as I don't have as much time to work out. I  play more strategy, as I am more experienced.  
\end{itemize} 
\end{enumerate}
\end{frame} 

\begin{frame}
\frametitle{Matches played} 
\begin{enumerate}
\item \small \textbf{7 hours match:}
\begin{itemize}
\item \tiny played defensive game, with each point lasting what seemed to be a lifetime. 
\item \tiny I amazingly won, as I simply outdid my opponent in terms of skills.
\item \tiny This taught me how important it is to know the fundamentals. One mis-hit, and I would lose the point. 
\end{itemize} 

\item \small \textbf{2 hour match:}
\begin{itemize}
\item \tiny Lost match easily to someone who was much better than me. 
\item \tiny Points were short, with me failing at several points, and the other person pinning me down at my weaknesses and using smart strategies to win.  
\item \tiny Learned that it's important to keep some good strategies to really be competitive, and not simply have good skills. 
\end{itemize}
\item \small \textbf{3.5 hour match:}
\begin{itemize} 
\item \tiny I was losing badly in first set. 
\item \tiny I then changed up my strategy,  and found some weaknesses in my opponents game. 
\item \tiny I went on to win that match.  I learned that one shouldn't just play to one's strengths, but also play with the other person's weaknesses in mind. 
% staying calm and keeping a good attitude is helpful to get out of bad situations. 
\end{itemize}
\end{enumerate}
\end{frame}

\begin{frame} 
\frametitle{Tennis is a lot like life} 
\begin{itemize}  
\item \small Trying to win a tennis match is similar to accomplishing one's goals in life.
\item \small One example of a recurring goal in my life is publishing research papers.   
\item \small Just like in a tennis match: know several basic skills. 
%For publishing a CS conference, we should know about
%  experimentation and data analysis. 

\item \small As in a tennis match, there are several working styles we might have in achieving these goals, and we chose our styles based on our strengths. 
% goals, and each style is different based on the
%  individual. 
%When we write our papers, we focus more on theory if
%that is our strength, and focus more on experimentation if that is
%our strength.  
\item \small Just like in a tennis match: experience with reaching goals
builds our ability to achieve future goals. 
% We may not publish some papers, but we learn through experience how
% to publish. 

\item \small I watched a grand slam tennis match a few days ago. It got me motivated to achieve 
a new goal, which is becoming better at public speaking. I may have ups and downs, but 
I'm hoping I can achieve this goal in the next few months. 
\end{itemize} 
\end{frame}

\begin{frame}
\frametitle{Closing}
\begin{itemize}
\item Shake hands 
\item Sit back down.
\end{itemize}
\end{frame} 

\begin{frame}
\frametitle{Delivery Notes}
\begin{enumerate}
\item \small Make sure points are all logically connected.  Ensure that each point is part of bigger picture.
\item \small memorize speech intro.
\item \small memorize speech conclusion.
\item \small rehearse transitions
\item \small memorize points in speech. 
\item \small practice delivery
\begin{itemize}
\item \tiny don't be afraid to pause after each point (helps avoid restarts)
\item \tiny \textbf{shout}  
\item \tiny don't look down
\item \tiny avoid moving hands. 
\item \tiny don't pace. 
\end{itemize}
\end{enumerate}
\end{frame} 


\begin{frame}  
\frametitle{Verbal: Intro} 
Tennis is one of the \textbf{major sports of the world}, with
\textbf{4 grand slam} events each year.  \textbf{Hi my name Vivek, and
  today} I want to tell you a bit about \textbf{my interest in
  tennis}. I believe it has \textbf{been an important part of my life}.
At the end of this talk, I hope you'll get to know how tennis has \textbf{shaped my mind}
and \textbf{my view of life}. 

\end{frame}




\begin{frame}
\frametitle{Verbal: Conclusion}

Playing a tennis match  is a \textbf{lot like trying to achieve one's
  goals} in life. One example of a goal in my life is \textbf{writing
  research papers}. Just like a tennis match, it's important to know
\textbf{basic skills such as theory, experimental analysis, and
  computer programming}.  Just like in a tennis match, it's important
to \textbf{chose your research style based on your strengths}. Just
like a tennis match, it's important to \textbf{learn from results in
  past research paper submissions to get a better chance of publishing
  in upcoming conferences}.  I \textbf{watched} a grand slam tennis
match a few days ago. It got me motivated to \textbf{achieve a new
  goal} -- getting better at public speaking. I may have \textbf{ups
  and downs} like in a tennis match, but I'm hoping that \textbf{I can
  learn from my mistakes} and achieve this goal in the \textbf{next
  few months}. 


\end{frame}
