% Question:  What are the role of computer technology in society today ? Do we really need computers?

%Question: Do we really need computers?

\begin{frame}
\frametitle{Introduction to Table Topics }
\begin{itemize} 
\item explain background 
\item formulate theme
\item 
\end{itemize} 
\end{frame} 

\begin{frame}
\frametitle{Marriage} 
\begin{itemize} 
\item 
\item 
\item 
\end{itemize} 
\end{frame} 

\begin{frame}
\frametitle{Wedding}
\begin{itemize}
\item What would you focus on most during the ceremony: reception, actual ceremony, or the events leading to the wedding? 
\item How much is too much to spend on a wedding? 
\item Is it ok to do a wedding with no one invited? 
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Money vs. Happiness}
\begin{itemize}
\item 
\item 
\item 
\end{itemize}
\end{frame} 


\begin{frame} 
\frametitle {Friendships introduction} 

\begin{itemize}
\item Friends made at all times 
\item 
\end{itemize} 

\end{frame} 
\begin{frame}
\frametitle{Meaning of Friendships}
\begin{itemize}

\item What defines a good friend? Someone who (always) agrees with your viewpoints?  Or someone whose (always) been there in the tough times and helped you out?  

\item Can you call someone a good friend, even if you haven't talked to them in several years? 

\item Can a good friend be someone you've never seen in person before, and only be connected digitally? 

\item Is it possible to become good friend with your boss/co-workers? 

\item What do you think about working for a good friend? Working with a good friend? 

\item Does having too many friends dilute each friendship? Or does having too many friends make each friendship stronger?  TODO: fix this 


%How many good friends is too many? Can you have too many good friends? Can you have too few good friends?

\end{itemize} 
\end{frame} 


\begin{frame}
\frametitle{Family}
\begin{itemize}
\item How close should you be to family? 
\item Are your parent's always your best mentors? Can we learn things we didn't learn about before through people that aren't parents? 
\item People say that she's like a sister to me. 
\end{itemize} 
\end{frame}

\begin{frame}
\frametitle{Summer}
\begin{itemize}
\tiny \item \tiny 
\item \tiny 
\item \tiny 
\item \tiny 
\end{itemize}
\end{frame}


\begin{frame}
\frametitle{General guidelines} 
\begin{itemize} 
\item 
\item 
\item 
\end{itemize} 
\end{frame} 



