\documentclass[11pt]{article}

\usepackage{ulem}
\usepackage{color}
\usepackage{xspace}
\newcommand{\bllt}{\item \small}
\newcommand{\doneTask}[1]{\item \sout{#1}}
\newcommand{\doneTaskHyp}[1]{\item \textcolor{blue} {\sout{#1}}} %finished a task, in theory
\newcommand{\doneTaskRev}[1]{\item \textcolor{yellow} {\sout{#1}}} % finished a task, but could use a revision
\newcommand{\optTask}[1]{\item  \textcolor{green}{#1}}
\newcommand{\prioTask}[1]{\item  \textcolor{red}{#1}}
\newcommand{\timeEst}[1]{\textit{#1}}
\newcommand{\dueBy}[1]{\textit{#1}}
\newcommand{\MyName}{Vivek~Kale}
\newcommand{\fixme}[1]{\textcolor{blue}{[FIXME: #1]}}
\newcommand{\revision}[1]{\textcolor{blue}{[FIXME comment : #1]}}
\newcommand{\todo}[1]{\textcolor{blue}{[TODO: #1]}}

\newcommand{\newSituation}[1]{\underline{\textbf{Situation:} #1} }
\newcommand{\newMiniSituation}[1]{\underline{\textbf{Mini-situation:} #1} }

\newcommand{\doneSituation}[1]{\sout{\underline{\textbf{Situation:} #1}} } 
\begin{document}

\underline{\textbf{Summary:}} This document summarizes situations that
are upcoming, or have already past. Each event should have an
approximate date. These are drafts for those mapping to the actual calendar events.  Within
the calendar event details/notes is where the ``pre-notes'' and
``post-notes'' go. Also, the week plan curr should have the situation
noted after these situations have been added.  These situations should
be listed every week (and checked every night), so that pro-active planning can take place.
This list has the fairly big situations. Smaller situations go in the
weekly doc; they could be integrated here too. 

%TODO: fix the below todos 
Be sure to connect the worklife cheat sheet experience here. 

Add method to improve and learn from these situations. 

Discuss methods for error-correction, error-prevention,
error-detection, and error-tolerance.  

\todo{add experience/rule pair}  
\todo{define better what experience/rule pair is. }
\todo{add pre-post} 













Social Intelligence: 


Prologue


\begin{enumerate} 
\tiny \item \tiny Unveiling a New Science 
\begin{itemize} 
\tiny \item \tiny Read annotate
\item \tiny Examples
\item \tiny connect to related
\end{itemize}

\tiny \item \tiny The Sociable Brain 

\begin{itemize} 
\tiny \item \tiny Read annotate
\item \tiny Examples
\item \tiny connect to related 
\end{itemize} 

\item \tiny Social Corrosion
\begin{itemize} 
\item \tiny Read annotate
\item \tiny Examples
\item \tiny connect to related
\end{itemize} 

\item \tiny Creeping Disconnection
a.Read annotate
b.Examples
c.connect to related

\item \tiny Social Neuroscience
a.Read annotate
b.Examples
c.connect to related

\item \tiny Acting Wisely
a.Read annotate
b.Examples
c.connect to related

d.Integrate into wl-cheat
e.Listen 

\item \tiny Emotional Economy: 
1.Low Road: contagion central 
2.Mood Drivers: 
3.Catching Emotions 
4.Radar for insincerity 
5.CasaNova’s downfall 
6.Love, Power, and Empathy 
Recipe for Rapport 
1.A phsychotherapy session is well under way
2.Glow of simpatico 
3.In synch 
4.Inner timekeepers
5. Protoconversation 
6.Neural Wifi 
7.Neural Mirrors
8.Meme wars 
9.Madness of crowds 

\item \tiny Instinct for altruism 
1.When attention must be paid 
2.Fine-Tuning 
3.Instinctive compassion 
4.Angel on earth 
5.Ancient debate 
6.Neuroanatomy of a kiss 
7.Low-road velocity 
8.What he saw her see 
9.High-road choices 
10.Economic Road Rage 
11.No to Impulse 
12.On second thought
13.Reengineering the Low Road

\item \tiny What is Social Intelligence? 

1.Social Awareness  
2.Social Facility 
3.Primal Empathy 
4.Attunement 
5.Empathic Accuracy 
6.Social Cognition 
7.Synchrony 
8.Self-presentation 
9.Influence 
10.Concern 
11.Educating the Low Road 
12.Social Intelligence Reconsidered 

Part Two: Broken Bonds 

\item \tiny You and It
1.I-you 
2.Feeling Felt
3.Utility of IT
4.Pain of rejection 
5.Empathy or projection? 

\item \tiny Dark Triad 
1.Narcissist: Dreams of Glory 
2.Dark side of Loyalty 
3.Narcissist’s Motto 
4.The Machiavellian: my ends justify the means 
5.Psychopath: other as object
6. Moral Prods 

\item \tiny Mindblind
1.Mean monkey
2.Male Brain 
3.Making Sense of People 
\end{enumerate} 

\end{document}
