\underline{\bf \it Happiness Generation - must maintain every week.}
        % explain happiness: show gratitude
        \begin{itemize}
          \tiny \item \tiny happy that I have Atul to show me.  
        %\item \tiny Happy that I have normal life up to this point.  
        %\item \tiny Think about dad saying, I understand, and want
        %you to be happy.
          \item \tiny Th
        \end{itemize}

    \underline{\bf \it Habits}
      \begin{itemize} 
        \tiny \item \tiny back straight + eye contact. 
      \item \tiny lips relaxed. 
      \item \tiny watch what happens when a hot girl talks to you. 
      \end{itemize} 



    \underline{\it \bf 10-year plan}   %-- Block 2-1 
      \begin{itemize}
      \item \small Make someone and dad proud.
      \end{itemize}

 
    \underline{\it \bf 3-year plan}
      \begin{itemize}
      \item \small find someone
      \item \small make 150K
      \item \small network
      \end{itemize}


    \underline{\it \bf 6-month plan}
      \begin{itemize}
        \small \item \small results + thesis
      \item \small routine + worklife
      \item \small 
      \end{itemize}

    
    \underline{\it \bf Month-by-month}
      %howto: This is most important, and should be re-visited every
      %month and definitely every three months(have fixed time within
      %4 times in the year to do this). 
      \begin{itemize} 
      %\item \small \textit{May:} Work: finish paper  + Work: comm:
      %  finish resume and cover letter.  
      %\item \small \textit{June:} Work: code org and plan + Work:
      %  finish code + worklife: org + worklife: finish emotional int +
      %  Comm: experiences + Comm: TM. 
      \item \small \textit{July:} Work: library, Work:comm: job
        introductions, Comm: meet people.
      \item \small \textit{August:} Work: library documentation and
        experimentation, Work: comm: resume prep + Work:comm:linkedIn
        + Work:comm: interviewing skills + Work:rel: get headstart on
        jobs (fb and dshaw) + Comm: stay in touch with girls. 
      \item \small \textit{September:} Work:library + Work: paper
        writing + Work:comm: interviewing. 
      \item \small \textit{October:} Work:paper +
        Work:rel:interviewing + Comm: dating 
      \item \small \textit{November:} worklife: review , Work:paper, Comm: dating 
 %     \item \small \textit{December:} 

      \end{itemize}

\underline{\it \bf March goals}
\begin{enumerate} 
\item \small Work: finish writing goals
  \small \item \small Mgmt:Spaces: clean room 
\item \small worklife: practice implemented work to form habits 
\item \small Comm: meet people 
\end{enumerate}

\begin{block}{\small \bf Week of September $31^{st}$: job search}
  \begin{enumerate}
\tiny \item \tiny Work: finish connecting with people regarding
implementation. 
\item \tiny Mgmt:Spaces: take care of driver's license. 
\item \tiny 
\item \tiny 
\item \tiny Comm: meet people 
\end{enumerate}
\end{block}

\begin{block}

{\underline{\bf Weekend Plans - March $15^{th}$, 2017 to May $1^{st}$,
    2017}}\\
\begin{itemize}
\item \tiny Weekend of March $17^{th}$: Visit New York City. Details:
\item \tiny Weekend of March $24^{th}$: Visit San Francisco. Details:
\item \tiny Weekend of March $31^{st}$: Visit San Francisco. Details:
\item \tiny Weekend of April $6^{th}$:  Dad is coming, cherry
  blossoms.
\item \tiny Weekend of April $13^{th}$: Visit India.
\item \tiny Weekend of April $20^{th}$: Go to New York.
\item \tiny Weekend of April $26^{th}$: Go to Los Angeles.
\end{itemize}

{\underline{\bf  Weekend plans for weekends between May $1^{st}$, 2017
    and June$1^{st}$, 2017}}\\
\begin{itemize}
\item \tiny Weekend of May $5^{th}$: Visit New York.
\item \tiny Weekend of May $12^{th}$:
\item \tiny Weekend of May $19^{th}$:
\item \tiny Weekend of May $27^{th}$:
\end{itemize}

\end{block}
\end{column}

%-- Column 3 --------------------------------------------- 



\begin{column}{0.28\linewidth}
\begin{block}{\small \bf Regular Routines}
%\input{../../../ViveksLaptop2/life/workLifeMgr/regularRoutines}
\input{./content_regularRoutines_plan}
\end{block}
\end{column}%3

\end{columns}
