\underline{\bf \it Jobs} 
    \begin{itemize}
      \tiny \item \tiny cat1: D.E. Shaw | SUNY/BNL: applying . | IBM:
      applied,interviews.  | Sandia: applied and failed, Cray: applied and got offer, USC. 
    \item \tiny cat2: Intel: Applied and failed. Intel: re-application  completed, AMD: applied, Samsung, VMWare: Contacting Yavatkar Kaka. 
    \item \tiny cat3: Google. MongoDB: applied and failed, Facebook. 
    \item \tiny cat4: LLNL. 
    \end{itemize} 


%TODO: check if below is needed. 
      %\item Friends: Amit, Sangita, Anchit, Kevin. 
      %Networking: 
  \underline{\bf \it Comm:friends}
    \begin{itemize} 
    \item Palekar’s:  
      \begin{itemize}
      \item UP: 
      \item Rohun: 
      \end{itemize} 
    \item Bhagwat’s: 
    \item Kapoor’s: 
      \begin{itemize}
        \tiny \item \tiny Anchit: Interaction. Atul is smart. 
      \item \tiny Shuchi: 
      \end{itemize}
    \item Sudharshan’s: 
      \begin{itemize} 
        \tiny \item \tiny Amit:  
      \item \tiny Sangita:  
      \end{itemize}
    \item Kumar’s:
      \begin{itemize}
        \tiny \item \tiny Ashwin: 
      \item \tiny Shilpa: 
      \end{itemize}
    \item Saied’s: 
      \begin{itemize}
        \tiny \item \tiny Laila 
      \item \tiny Faisal 
      \item \tiny Ayesha
      \end{itemize} 
    \item Kukreti’s:
    \item Kumar’s:
    \item UIUC friends: 
      \begin{itemize} 
        \tiny \item \tiny Sadhna: 
      \item \tiny Rishi: 
      \item \tiny Amaeya: 
      \item \tiny Chris: 
      \item \tiny Brian: 
      \item \tiny Arif 
      \end{itemize}
    \item grad school friends 
      \begin{itemize} 
        \tiny \item \tiny  Karan: 
      \item \tiny Gopi: 
      \item \tiny Amanda:  
      \end{itemize}
    \end{itemize} 

  
\underline{\bf \it Rel}
    \begin{itemize} 
      \small \item \small Shwetha K/r
    \item \small Shalaka 
    \item \tiny DCK girl 
    \item \tiny  Shikha Singhvi: initiated.  
    \item \small Mamta
    \item \small Avani 
    \item \small SH05702678 Palo Alto - 
    \item \small Sheila G -Sh93522198  
    \item \small sonalisinha  s: 5103658167 and my email address is: \url{2sonalisinha@gmail.com}
    \item \small Nandini  - 
    \item \small Archana from San Jose. 
    \item \small Im from DC  - B475435: parents initiated. 
    \item \small Sruthi 
    \item \small SH12825009 New York, New York - Finance Professional 
    \item \small Navneet K  - 29 5'8" - SH88263211 
    \item \small Girl from New York  -27 years
    \item \small Shwetha Ravi 
    \item \small Ruchira K ( SH34021888 )2-Way           
    \item \small SH11680694 from San Francisco. 
    \item \small Sandhya N. 22 Jun 2016 
    \item \small Aarti S - 27 - 5' 9'' Charlotte.  
    \item \small Anu M from Chicago, IL 
    \item \small Pranati A from Cleveland, OH - 
    \item \small Meghana K from New York - 
    \item \small Ssd S - 28 , 5 5 , Boston, MA 
    \item \small Anj B. - 30 yrs - SH13882555.
    \end{itemize}
