\begin{block}{Planning} 
\comments{
{\underline{\textit{2-month plans}}}
{\underline{\textit{January and February:}}}
{\underline{\textit{March and April:}} }
{\underline{\textit{May and June:}}}
}

\begin{itemize}
\tiny \item \tiny do scheduling strategies. 
\item \tiny work on job talk. 
\item \tiny do travel. 
\item \tiny social on facebook, catch up with Rishi. 
\end{itemize} 
\begin{itemize} 
\item \tiny 2-month plan: May:  June:  
\item \tiny 2-month plan: August:  prep September: interview. 
\end{itemize}
\end{block}

\begin{columns}
\begin{column}{0.333\columnwidth}
\begin{block}{Project1}
%\underline{\bf Work:code: Project , Coding practice: p for interview.}
\begin{enumerate}
\tiny \item \tiny Work:code (cp.): go through C++, Work:code (cp.): go
through Java + Work:code (cp.): go through OOP. 
\item \tiny Work:code (cp.): code up problems.  – 1 week.
\item \tiny Work:code (cp.): integer problems + numerics   -- 1 week.
\item \tiny Work:code (cp.): practice mock interview problems. – 1 week.
\end{enumerate}
{\tiny {\it {\tiny Schedule:}} Work:code (cp.): finish bit
  manipulation, Work(cp.): review brain teasers in book, Work(cp.):
  Work(cp.): go through C++.} \\
{\underline{\bf Project: job talk prep}} 
{\tiny {\it {\tiny Schedule:}} Work:code (cp.): finish bit manipulation,
Work(cp.): review brain teasers in book, Work(cp.): Work(cp.): go
through C++.} \\

{\underline{\bf Work:code: Project}}
\begin{enumerate}
\tiny \item \tiny Work: download ptychoLib from Kaushik and copy to git repo.
\item \tiny Work: discuss work with A rittenbach + Work: download driver on GPU4.
\item \tiny work: integrate.
\item \tiny Work: do OpenMP 4.5 for ptypy and OpenACC.
\item \tiny Work: run with dataset from PSI.
\item \tiny Work: send message about research paper. 
\end{enumerate}

{\underline{\bf Work:code: Project - Research Paper:}}
\begin{enumerate}
\tiny \item \tiny \url{http://mpp2016.ime.uerj.br}. 
\item \tiny \url{http://sbac-pad}  - registration is  500.

\item \tiny Work: add 
\item \tiny Put up latex.  
\item \tiny Gather all research. 
\item \tiny Gather project work. 
\item \tiny Write down introduction.
\item \tiny Gather data for OpenACC. 
\item \tiny Explain other details of setup. 
\item \tiny Note data for OpenMP. 
\item \tiny Work: discuss ideas with Michael Klemm. 
\end{enumerate}
{\tiny {\textit{Schedule:} March 24th: do latex, March 2}}\\

%\underline{\bf Work:rel: Project – interview with Berkeley/MIT/industry}
\begin{enumerate}
\tiny \item \tiny Business cards:  - use latex  -- 40 minutes. 
\item \tiny Cover letter. 
\item \tiny Jobs categorization for real jobs opportunities: Suny sb /
  suny sb / LLNL /  |  Intel, NVIDIA, Apple  Google/ms / software
  companies, Database companies/Oracle, $\rightarrow$ real companies. 
\item \tiny CV: + Research Summary:  -- 1 week.  - Talking about your research.
\item \tiny Work:rel: message to Yavatkar Kaka about VMWare +
  Work:rel: gather friends in network from friends about Google +
  Work:rel: message to contacts about Microsoft \te{} \dl{} \pr{}. 
\item \tiny Behavioral questions answers:    -- 1 week. 
\item \tiny Send emails – 1 day. 
\item \tiny Structure in latex. 
\end{enumerate}
%{\small {\it Schedule:} Behavioral answers – 1 week, CV prep - 1 day,
%business cards, cover letter -1 hour. }\\
%\underline{\bf Project: awards}
\begin{enumerate} 
\tiny \item \tiny Figure out write-up for Fulbright. 
\item \tiny Attend Fulbright : 
\item \tiny Stay in touch with HLF 
\item \tiny Do energy econ work with convergence. 
\item \tiny Go to whitehouse thing. 
\item \tiny Plan to be on Program Committee of .. 
\end{enumerate}
%{ \small \it Schedule:} April 15th: message to Stephen – 1 hour,
%Work:rel:Project – Awards: 
%\underline{\bf Mgmt:Spaces: settle on your own}
\begin{enumerate}
\tiny \item \tiny Dentist + Get dentist appointment.
\item \tiny Doctor / Counselor + CBT.
%TODO: organize and group the below
\item \tiny Reimbursements.
\item \tiny Work pay and holidays / hours.
\item \tiny 401k+retirement  + fidelity + bank (money owing).
\item \tiny apartment + apartment sublease + apartment rent.
\item \tiny Flights: update flight information, e.g., credit card,
  emergency contact, passport number.
\item \tiny Flights: finish flight decision making notes, e.g.,
  justification for travel, money/airfare rules, award travel rules. 
\item \tiny apartment sublease. 
\item \tiny Car city sticker.
\item \tiny Car: Get windows side checked + Get windows marking
  checked + Get tailpipe checked + Ask about warranty. 
\item \tiny Mgmt:Spaces(crp): check car tailpipe +
  Mgmt:Spaces(crp):Window \te{1 hour}.
\item \tiny Mgmt:Spaces(bfa): buy things for apartment =
  Mgmt:Spaces(bfa): buy a whiteboard + Mgmt:Spaces(bfa): get a chair
  that adjusts height and folds \te{} \dl{} \pr{}. 
\end{enumerate}
\end{enumerate}

{\underline{\textbf{Worklife - Project – Comm:rel:}}}
\begin{enumerate} 
  \tiny \item \tiny Worklife: link management together.  
\item \tiny Worklife: link habits comm and Toastmasters. - done
\item \tiny Worklife: latex viewpoint. 
\item \tiny Comm: read social intelligence first four chapters.
\item \tiny Comm: link all comm together.
\item \tiny Worklife: get emails and texts to analyze. 
\item \tiny Worklife: figure out how to book flights and trips
  quickly. 
\textit{Schedule:} Comm: read social intelligence first four chapters
and get a method to take in information – 5 hours. Comm: link comm
together, worklife: latex viewpoint. Looking ahead:  \\

{\underline{\bf Project: Comm}}
\begin{enumerate}
\item \tiny Comm: consider view of girl on Shaadi. 
\item \tiny Comm: consider talking to Illina.
\item \tiny Comm: talk to friends from high school.
\item \tiny Mgmt:Spaces: plan trips. \te{-}.
\item \tiny Mgmt:webpresence: cancel FB friend request of
  Jocelyn + Mgmt:webpresence: check other friend requests
  sent requests. \te{-}. 
\item \tiny Mgmt:Spaces(GetThingsSpring2016): get Things =
  Mgmt:Spaces(getThings): get suit.
  \doneTask{Mgmt:webpresence: delete Anil Taneja from LinkedIn. \te{1
      hour} \dl{Monday} \pr{UI}. - not needed since we met with Rishi
    + Comm: may have not accepted + Mgmt:webpresence: bad to do so}
\end{enumerate}
{\it Schedule:} meet others over summer, meet girl over summer.\\
%TODO: figure out why this was the issue

{\underline{\bf Project: Comm:rel}}
\begin{enumerate} 
  \tiny \item \tiny Comm: consider what to do about Bhavna.
\item \tiny Comm: get caught up with Matrimony and Shaadi, Use match,
  make system for meeting. 
\item \tiny Comm:rel: discuss with Mom and Dad. 
\end{enumerate} 

{\underline{\bf Mgmt:Spaces}}\\
\begin{enumerate} 
\item \tiny Mgmt:Spaces(GetThingsSpring2016): get Things = Mgmt:spaces: get suit
+ Mgmt:Spaces: buy calendar 
\item \tiny Mgmt:Spaces: get voicemail fixed  - ‘Hi, you have reached Vivek’s
phone. I’ll call you back as soon as possible.’ + Mgmt:Spaces: delete
voicemails’ 
\item \tiny Mgmt:Spaces: get 1 TB disk drive. 
\item \tiny Mgmt:Spaces: finish transferring pictures + Mgmt:Spaces: figure out
how to delete photos from iPhoto + Mgmt:Spaces: figure out why size of
photo booth stays the same  Mgmt:Spaces: Figure out airplane photos
and put in proper album folder. Mgmt:Spaces: Organize photos in
folders + Mgmt:Spaces: Confirm pictures are placed properly and delete
from photos + Mgmt:Spaces: Compress photos into zip drive. +
Mgmt:Spaces: Move photos from folders into temporary disk / USB stick 
+ Mgmt:Spaces:Delete photos from iPhone.
\end{enumerate} 

{\underline{\bf Work:comm: (can impact work):}}
\begin{enumerate}
\item \tiny Work:rel: add Shikha.
\item \tiny Mgmt:webpresence: fb like to Lagha. 
\end{enumerate}

\underline{\bf Work:rel: -  Project – Comm: rel:} 
\begin{itemize} 
\item \tiny Comm:rel: meet others:  Sweta Kambaskadwar. + Mgmt:webpresence: fb
like of Shalaka’s. L3:past: she liked and suggested to come, lots of
time delayed. I didn’t like back.  Intent: show interest. Outcome:
stay alive with Rucha?
\item \tiny Mgmt:webpresence: fb like to Tanuja
\item \tiny Mgmt:webpresence: take Xin Zhao off and remove anyone else that you
don’t want from work.
\item \tiny Mgmt:webpresence: update location on linkedIn +  Mgmt:webpresence: update.
\item \tiny Mgmt:webpresence: consider deleting asdfjkl;  and making parts of facebook bmm 2006 public. 
\end{itemize}

\end{block}



%          \item \tiny Work: talk to Prem about an office in SF
  \begin{columns}
    %-- Page 2: Column 1 --------------------------------------------------- 
    \begin{column}{0.20\linewidth}
      %{\textbf{\underline{Week Aspects(new name)}})
      %--- Page 2: Block 1-1 
      \begin{block}{Routines}
        { \tiny \underline{\bf Routines:} Morning: bfast, exercise/brush,
          floss, shower (hair, eyes, ears, underarms, feet), meds, belt,
          comb hair / dishes, clean kitchen floor. |  Night: running/ put
          away dishes, clean kitchen floor / brush teeth, charge phone,
          clothes for tomorrow, contacts off.}\\
        {\tiny \underline{\bf Sunday Routines:} Routines:
          Experiences,week plan.}\\ 
        {\tiny \underline{\bf Weekday Routines:}}\\
        %TODO: check if weekday routines overlaps into daily routines.
      \end{block} 
      %--- Page 2: Block 1-3
      \begin{block}{Local Happiness}
        % howto:Recognize emotions / recognize (precisely) what you're
        % worried about -> methods for eliminating worry. 
        % clean out old worries, put them in pastWorries doc.  
        % remember to define precisely 
        % order from top-to bottom
        \begin{itemize} 
          \tiny \item \tiny
        \item \tiny Worrying about gal: think about talking to others.
        \end{itemize} 
      \end{block}
      %--- Page 2: Block 1-4 
      \begin{block}{AngersAndAnxieties}
        % howto:Recognize emotions / recognize (precisely) what you're worried about -> methods for eliminating worry. 
        % clean out old worries, put them in pastWorries doc.  
        % remember to define precisely 
        % order from top-to bottom
        \begin{itemize}
          \tiny \item \tiny Anger about UP -> think about the positive
          perspective, and the original
        \item \tiny Anger about Mr. Kapoor ->  leave it
        \item \tiny Anger about a b  -> ...
        \item \tiny Issue with USC : --> things get better. 
        \end{itemize}
      \end{block}
      %-- Block 1-5
      \begin{block}{Life notes}
        \begin{itemize}
          \tiny \item \tiny Social Intelligence: 
        \end{itemize}
      \end{block}

      % howto:
      \begin{block}
        {\tiny {\bf Week lessons:}}
        \begin{enumerate}
          \tiny \item \tiny Win Friends/ Influence People
        \item \tiny Go through 7 habits.
        \item \tiny Coding problem: 
        \item \tiny Chess tips: 
        \item \tiny tm tips.
        \end{enumerate}
            {{\tiny {\tiny \bf  News:}} {\tiny  M: | S: France's election | E:
              Fallon:   Kimmel:  Colbert: SNL:}}
      \end{block}
    \end{column}
  %-- Column 2 ---------------------------------------------
  \begin{column}{0.6\linewidth}
    \begin{block}{Week Summary} 
      {\underline {\bf Week Plan:}
        Work: run dataset to scale on HPC cluster, Work: make slide
        for ptycholib, Comm: send message to Nitin Mama, Comm: reply
        on  WhatsApp group. } \\

      {\underline{\bf Weekend Plan:} }\\
    \end{block}

      \begin{block}{Running ToDo} % find a better name 
        \begin{enumerate} 
          \item \tiny \textbf{Curr} $\rightarrow$
          \item \tiny Work: fix Youssef's code.
          \item \tiny Work: do \texttt{ ln -s} for paper subdirectory
            in bitbucket git repository.
          \item \tiny Work: download ptychoLib from Kaushik and copy
            to git repo.
          \item \tiny Work: discuss work with A rittenbach + Work: download driver on GPU4. 
           
          \item \tiny Work: kakadu software. 

          \item \tiny Work: run with real dataset if possible. 
          \item \tiny Work: figure out time to talk with Youssef.

          \item \tiny Mgmt:Spaces: get car check engine light updated
            + Mgmt:Spaces: do car's registration + Mgmt:Spaces: get
            reimbursements done. 

          \item \tiny Mgmt:Spaces: plan trip  to California. =
            Mgmt:Spaces: talk to Ashwin saying that works.  +
            Mgmt:Spaces: send message to Gopi + 
            Mgmt:Spaces: ask Dad for getting miles + Mgmt:Spaces:
            message to Nitin Mama.

           \item \tiny Mgmt:wp: post about Tesla's. 

            \item \tiny Mgmt:wp: post about net neutrality. 

            The Internet was incepted with the assumption of network
            neutrality. Let's stick to tradition and keep the Internet
            that way. Support the cause.

            TODO:L4: assumption of network neutrality VS assuming net
            net neutrality.  -done 
            TODO:L4: stick to v VS maintain  -done 

            TODO:L4: and keep the internet that way. 

            TODO:L3: website VS full


%http://time.com/4770205/john-oliver-fcc-net-neutrality/


The Internet was incepted with the assumption of network neutrality. Let's
stick to tradition and keep the Internet that way. Support the cause.

http://time.com/4770205/john-oliver-fcc-net-neutrality/


for network  neutrality.

I support network neutrality.

Support the cause. 


Let's make sure that it stick to 

            I understand that companies need to make money, but
            there's absolutely no argument against blocking out
            smaller 
            tradition.  Net neutrality. exactly what we need to fight
            for.
 
           \item \tiny Mgmt:wp: post about science on FB. 
           \item \tiny Mgmt:wp: post about Queen. 

           \item \tiny Mgmt:wp: Write up on facebook.
           \item \tiny Mgmt:wp: I like Tesla cars and support the company's
            disruption to its industry. At the same time, I don’t think
            that the company will devalue instantaneously the engineering
            accumulated over 8 decades in a BMW.
            {I like cars by Tesla and am supportive of the company’s
              disruptiveness to industry. However, I can’t imagine
              that the company’s cars will make the eight decades of
              engineering that’s in my BMW engine become worthless.
             Tesla technology
             TODO:L3: intent: explain supportiveness of disruptve
             TODO:L3: outcome: people see what I’m about 
             TODO: L4: disruptiveness to industry VS disruption to industry 
             TODO: L4: I have a hard time VS I can’t imagine VS I don’t think  VS 
             TODO:L4: At the same time, VS However, 
             TODO:L4: truly VS [OMIT] 
             TODO:L4: I like VS I love} 

           \item \tiny Comm: message to Nitin Mama about meeting his
             father with a picture.

          \item \tiny Comm: do review for Liberty Towers. 
          \item \tiny \textbf{ <-- End Curr } 
          \item \tiny Work: IM system for LLNL.
        \end{enumerate}
      \end{block}
 
      % howto: the below is a routine based on the job I'm doing and the
      % circumstances I'm in. Note that this is different from routines
      % above, which is true for a long-term period of over 10 years. 

      \begin{block}{Weekly Meetings}
        \begin{itemize}
          \tiny \item \tiny IWOMP affinity meeting Thursday 7 AM PDT / 9 AM
          CDT call in: 805-639-779 pswd: places. \url{https://llnl.webex.com/llnl/j.php?MTID=m33950b76befb72c0cbc31ea2e3be720c}
        \item \tiny DEG group meeting.  
        \end{itemize}
      \end{block} 

\comments{
\begin{block}
\begin{table}[ht!]
\label{fig:calendar}
\begin{center}
\begin{tabular}
{ | c || c | c | c | c | c | c | c |}
\hline
  \textbf{\small content} & {\small \bf M} & {\small \bf T} & {\small
    \bf W} & \
{\small \bf R} & {\small \bf F} & {\small \bf Sa} & {\small \bf Su} \\
  \hline
  \small weat  &\tiny 2/3 r &\tiny 2/1 r &\tiny 2/-1 r &\tiny 11/2 s
  &\tiny 11/4 s   &\tiny  11/4 s &\tiny 11/5 s \\
  \hline
  \small todo  &\small exps on a node &\small &\small &\small &\small &\small
  &\small  \\
  \small       &\small &\small &\small &\small &\small &\small
  &\small  \\
  \small       &\small &\small &\small &\small &\small &\small
  &\small  \\
  \small       &\small &\small &\small &\small &\small &\small
  &\small  \\
  \small       &\small &\small &\small &\small &\small &\small
  &\small  \\
  \hline
  \small schd  &\small &\small &\small &\small &\small &\small
  &\small  \\
  \small     &\small &\small &\small &\small &\small &\small  &\small
  \\
  \small      &\small &\small &\small &\small &\small &\small  &\small
  \\
  \small    &\small &\small &\small &\small &\small &\small  &\small
  \\
  \small     &\small &\small &\small &\small &\small &\small &\small
  \\
  \hline
%\bottomrule                                                                    
\end{tabular}
\end{center}
\end{table}

\end{block}
}

      \begin{block}{Week Daily Schedule}
        % howto: arrange items from running todo into the below
        % sheet management document. 
        %NOTE: we don't use the table format because of fittting

        \begin{columns}
          \begin{column}{0.14\textwidth}{\small \underline{\bf Mon}}
            {\tiny \bf {\tiny weather:} } {\tiny 11/1 s} \\ 
            {\tiny \bf {\tiny todo}}\\ 
            \begin{itemize}
              \tiny \item \tiny Work: do experiments with multiple
              nodes. 
            \item \tiny Work: get experiments using real data.  
            \item \tiny 
            \end{itemize}
                {\small  \bf schedule}\\
                \begin{enumerate} 
                  \tiny \item \tiny 8-9AM: Regular Routines 
                \end{enumerate}
          \end{column}

          \begin{column}{0.14\textwidth}{\small \underline{\bf Tues}}
            {\bf {\tiny  weather:} } {\tiny 3/1 r} \\ 
            {\bf {\tiny todo}}\\ 
            \begin{itemize}
              \tiny \item \tiny Work: do write-up  
            \end{itemize} 
                {{\bf {\tiny  schedule}}}
                \begin{enumerate} 
                  \tiny \item \tiny 8-9AM: Regular Routines 
                \end{enumerate} 
          \end{column}

          \begin{column}{0.14\textwidth}{\small \underline{\bf Wed}}
            {\tiny \bf weather: } {\tiny 3/1 r} \\ 
            {\tiny {\bf todo}}\\
            \begin{itemize}
              \tiny \item \tiny Add in schedule
            \item \tiny -
            \end{itemize} 
                {\tiny \bf schedule}\\
                \begin{enumerate} 
                  \tiny \item \tiny 8-9AM: Regular Routines 
                \end{enumerate} 
          \end{column}

          \begin{column}{0.14\textwidth}{\small \underline{\bf Thurs}}
            {\tiny \bf weather: } {\tiny 1/-1 r }\\ 
            {\tiny \bf todo} \\ 
            \begin{itemize}
              \tiny \item \tiny Add in schedule
            \item \tiny 
            \end{itemize} 
                {\tiny {\bf schedule}} \\
                \begin{enumerate} 
                  \tiny \item \tiny 8-9AM: Regular Routines 
                \end{enumerate}
          \end{column} 
          
          \begin{column}{0.14\textwidth}{\small \underline{\bf Fri}}
            {\tiny \bf weather: } {\tiny 3/1 r} \\ 
            {\tiny \bf todo} \\ 
            \begin{itemize}
              \tiny \item \tiny Add in schedule
            \item \tiny 
            \end{itemize} 
                {\tiny \bf schedule} \\
                \begin{enumerate} 
                  \tiny \item \tiny 8-9AM: Regular Routines 
                \end{enumerate}
          \end{column}

          \begin{column}{0.15\textwidth}{\small \underline{\bf Sat}}
            {\tiny \bf weather: } {\tiny 11/1 .2r} \\ 
            { \tiny \bf todo} \\ 
            \begin{itemize}
              \tiny \item \tiny Add in schedule
            \item \tiny 
            \end{itemize} 
                {\tiny \bf schedule} \\
                \begin{enumerate} 
                  \tiny \item \tiny 8-9AM: Regular Routines 
                \end{enumerate}
          \end{column}
          
          \begin{column}{0.15\textwidth}{\small \underline{\bf Sun}}
            {\tiny {\bf weather:} } {\tiny 11/2 r} \\ 
            {\tiny {\bf todo}}\\
            \begin{itemize}
              \tiny \item \tiny Add in schedule
            \end{itemize} 
                {\tiny \bf schedule}\\
                \begin{enumerate} 
                  \tiny \item \tiny 8-9AM: Regular Routines 
                \end{enumerate}
          \end{column}
        \end{columns}
      \end{block}

\end{column}
    
    % ------ Page 2: Column 3
    \begin{column}{0.20\linewidth}
      % ------ Block 2.3.1 
      \begin{block}{Food Plan} 
        \begin{itemize}
          \tiny \item \tiny Google Express: DHDQQJQDRFTXDM95B
        \end{itemize}
      \end{block} 
      \begin{block}{Clothes plan} 
        \begin{itemize}
          \tiny \item \tiny Monday: 
        \item \tiny Tuesday
        \item \tiny Wednesday
        \item \tiny Thursday
        \item \tiny Friday
        \item \tiny Saturday
        \end{itemize} 
      \end{block} 
      
      %-- Block 3-3 
      \begin{block}{Situations}
        % Summary: the below are the situations that define one
        % another.
        % Howto: Put post notes of each situation from list of previous
        % week. Put high importance situations in situationslist. 
        % Put list of upcoming situations on Sunday morning with Pre. 
        \begin{itemize}
          \tiny \item \tiny Meet with Ashwin. Pre-: dress red, talk
          about life. Post-:
        \end{itemize}
      \end{block}
      % contingincies: 
      % Summary:
    \end{column}
\end{columns}
