\begin{block}{Planning} 
\comments{
{\underline{\textit{2-month plans}}}
{\underline{\textit{January and February:}}}
{\underline{\textit{March and April:}} }
{\underline{\textit{May and June:}}}
}

\begin{itemize}
\tiny \item \tiny do scheduling strategies. 
\item \tiny work on job talk. 
\item \tiny do travel. 
\item \tiny social on facebook, catch up with Rishi. 
\end{itemize} 
\begin{itemize} 
\tiny \item \tiny 2-Month Plan: December: code + worklife, January: study for interviews
\item \tiny 2-Month Plan: February: code | March:  code + interview review + finish coding work. 
\item \tiny 2-Month Plan: April: code, May: code paper review.
\item \tiny 2-month plan: June: relax July: adjust 
\item \tiny 2-month plan: August:  prep September: interview 
\end{itemize} 

\end{block}

\begin{block}{Projects}
%\underline{\bf Work:code: Project , Coding practice: p for interview.}
\begin{enumerate}
\tiny \item \tiny Work:code (cp.): go through C++, Work:code (cp.): go through Java + Work:code (cp.): go through OOP. 
\item \tiny Work:code (cp.): code up problems.  – 1 week.
\item \tiny Work:code (cp.): integer problems + numerics   -- 1 week. 
\item \tiny Work:code (cp.): practice mock interview problems. – 1 week. 
\end{enumerate}
{\it Schedule:} Work:code (cp.): finish bit manipulation,
%Work(cp.): review brain teasers in book, Work(cp.): Work(cp.): go
%through C++.\\ 

{\underline{\bf Project: job talk prep}}
\begin{enumerate} 
\item \tiny Mgmt:Spaces(crp): check car tailpipe +
  Mgmt:Spaces(crp):Window \te{1 hour}.
\item \tiny Mgmt:Spaces(bfa): buy things for apartment =
  Mgmt:Spaces(bfa): buy a whiteboard + Mgmt:Spaces(bfa): get a chair
  that adjusts height and folds \te{} \dl{} \pr{}. 
\end{enumerate}

{\underline{\bf Work:code: Project - Research Paper:}}
\begin{enumerate}
\tiny \item \tiny \url{http://mpp2016.ime.uerj.br}. 
\item \tiny \url{http://sbac-pad}  - registration is  500.
\item \tiny Put up latex.  
\item \tiny Gather all research. 
\item \tiny Gather project work. 
\item \tiny Write down introduction.
\item \tiny Gather data for OpenACC. 
\item \tiny Explain other details of setup. 
\item \tiny Note data for OpenMP. 
\item \tiny Work: discuss ideas with Michael Klemm. 
\end{enumerate} 
\textit{Schedule:} March 24th: do latex, March 2 \\
%\underline{\bf Work:rel: Project – interview with Berkeley/MIT/industry}
\begin{enumerate} 
\tiny \item \tiny Business cards:  - use latex  -- 40 minutes. 
\item \tiny Cover letter 
\item \tiny Jobs categorization for real jobs opportunities: 
Suny sb / suny sb / LLNL /  |  Intel, NVIDIA, Apple  Google/ms /
software companies, Database companies/Oracle, $\rightarrow$ real
companies. 
\item \tiny CV: + Research Summary:  -- 1 week.  - Talking about your research.
\item \tiny Work:rel: message to Yavatkar Kaka about VMWare +
  Work:rel: gather friends in network from friends about Google + Work:rel: message to contacts about Microsoft \te{} \dl{} \pr{}. 
\item \tiny Behavioral questions answers:    -- 1 week. 
\item \tiny Send emails – 1 day. 
\item \tiny Structure in latex. 
\end{enumerate}
%{\small {\it Schedule:} Behavioral answers – 1 week, CV prep - 1 day,
%business cards, cover letter -1 hour. }\\
%\underline{\bf Project: awards}
\begin{enumerate} 
\tiny \item \tiny Figure out write-up for Fulbright. 
\item \tiny Attend Fulbright : 
\item \tiny Stay in touch with HLF 
\item \tiny Do energy econ work with convergence. 
\item \tiny Go to whitehouse thing. 
\item \tiny Plan to be on Program Committee of .. 
\end{enumerate}
%{ \small \it Schedule:} April 15th: message to Stephen – 1 hour,
%Work:rel:Project – Awards: 
%\underline{\bf Mgmt:Spaces: settle on your own}
\begin{enumerate}
\tiny \item \tiny Dentist + Get dentist appointment.
\item \tiny Doctor / Counselor + CBT.
%TODO: organize and group the below 
\item \tiny Reimbursements.
\item \tiny Work pay and holidays / hours. 
\item \tiny 401k+retirement  + fidelity + bank (money owing). 
\item \tiny apartment + apartment sublease + apartment rent.
\item \tiny Flights: update flight information, e.g., credit card,
  emergency contact, passport number.
\item \tiny Flights: finish flight decision making notes, e.g.,
  justification for travel, money/airfare rules, award travel rules.
\item \tiny Change Chase address. 
\item \tiny apartment sublease. 
\item \tiny renter's insurance. 
\item \tiny xfinity and wifi accounts. 
\item \tiny ComEd. 
\item \tiny car insurance \doneTask{car parking} 
\item \tiny Car city sticker. \doneTask{Ventra card.}
\item \tiny Car: Get windows side checked + Get windows marking checked + Get tailpipe checked + Ask about warranty. 
\end{enumerate}

{\underline{\textbf{Worklife - Project – Comm:rel:}}}
\begin{enumerate} 
  \tiny \item \tiny Worklife: link management together.  
\item \tiny Worklife: link habits comm and Toastmasters. - done
\item \tiny Worklife: latex viewpoint. 
\item \tiny Comm: read social intelligence first four chapters.
\item \tiny Comm: link all comm together.
\item \tiny Worklife: get emails and texts to analyze. 
\item \tiny Worklife: figure out how to book flights and trips quickly. 
\end{enumerate}
\textit{Schedule:} Comm: read social intelligence first four chapters
and get a method to take in information – 5 hours. Comm: link comm
together, worklife: latex viewpoint. Looking ahead:  \\

{\underline{\bf Project: Comm}}
\begin{enumerate}
  \tiny \item \tiny Comm: message to Mona and Leena \te{10 minutes} 
\item \tiny Comm: consider view of girl on Shaadi. 
\item \tiny Comm(ren): message to Michael :=  Comm(ren): message to
  Rishi and Chris and Amaeya about meeting. 
\item \tiny Comm: meet Gary and KD \te{10 minutes}.
  \doneTask{Comm: message to Kavita} 
\te{1 hour} \dl{Thursday} \pr{-}
\item \tiny Comm: consider talking to Illina.
\item \tiny Comm: talk to friends from high school.
\item \tiny Mgmt:Spaces: plan trips. \te{-}.
\item \tiny Mgmt:webpresence: cancel FB friend request of
  Jocelyn + Mgmt:webpresence: check other friend requests
  sent requests. \te{-}.
\item \tiny Mgmt:Spaces(GetThingsSpring2016): get Things =
  Mgmt:Spaces(getThings): get suit. 
  \doneTask{Mgmt:webpresence: delete Anil Taneja from
    LinkedIn. \te{1 hour} \dl{Monday} \pr{UI}. - not needed since
    we met with Rishi  + Comm: may have not accepted +
    Mgmt:webpresence: bad to do so}

\end{enumerate}
{\it Schedule:} meet others over summer, meet girl over summer.\\
%TODO: figure out why this was the issue

{\underline{\bf Project: Comm:rel}}
\begin{enumerate} 
  \tiny \item \tiny Comm: consider what to do about Bhavna.
\item \tiny Comm: get caught up with Matrimony and Shaadi, Use match,
  make system for meeting. 
\item \tiny Comm:rel: discuss with Mom and Dad. 
\end{enumerate} 

{\underline{\bf Mgmt:Spaces}}\\
\begin{enumerate} 
\item \tiny Mgmt:Spaces(GetThingsSpring2016): get Things = Mgmt:spaces: get suit
+ Mgmt:Spaces: buy calendar 
\item \tiny Mgmt:Spaces: get voicemail fixed  - ‘Hi, you have reached Vivek’s
phone. I’ll call you back as soon as possible.’ + Mgmt:Spaces: delete
voicemails’ 
\item \tiny Mgmt:Spaces: get 1 TB disk drive. 
\item \tiny Mgmt:Spaces: finish transferring pictures + Mgmt:Spaces: figure out
how to delete photos from iPhoto + Mgmt:Spaces: figure out why size of
photo booth stays the same  Mgmt:Spaces: Figure out airplane photos
and put in proper album folder. Mgmt:Spaces: Organize photos in
folders + Mgmt:Spaces: Confirm pictures are placed properly and delete
from photos + Mgmt:Spaces: Compress photos into zip drive. +
Mgmt:Spaces: Move photos from folders into temporary disk / USB stick 
+ Mgmt:Spaces:Delete photos from iPhone.
\end{enumerate} 

{\underline{\bf Work:comm: (can impact work):}}
\begin{enumerate}
\item \tiny Work:rel: add Hirve Kaka. 
\item \tiny Work:rel: add Shikha.
\item \tiny Work:rel: add Dele. 
\item \tiny Mgmt:webpresence: fb like to Lagha
\end{enumerate}

\underline{\bf Work:rel: -  Project – Comm: rel:} 
\begin{itemize} 
\item \tiny Comm:rel: meet others:  Sweta Kambaskadwar. + Mgmt:webpresence: fb
like of Shalaka’s. L3:past: she liked and suggested to come, lots of
time delayed. I didn’t like back.  Intent: show interest. Outcome:
stay alive with Rucha?
\item \tiny Respond to Vinayak. 
\item \tiny Comm: Message to Labonee about moving.
\item \tiny Mgmt:webpresence: fb like to Tanuja
\item \tiny Mgmt:webpresence: take Xin Zhao off and remove anyone else that you
don’t want from work.
\item \tiny Comm: message to Rayna about re-union. 
\item \tiny Mgmt:webpresence: update location on linkedIn + Mgmt:webpresence:
update.
\item \tiny Mgmt:webpresence: consider deleting asdfjkl;  and making
parts of facebook bmm 2006 public. 
\end{itemize}

\end{block}
