Week of December 6th, 2015: 
1.Work: finish gpu code + Work: mesh code
2.Work: finish documentation  
3.  Work:rel: interviewing with algo-logic  + Work:rel: interview
arrangements with fb 
4.  Comm: talk to girl from Maryland

Week of December 13th, 2015: 

1.Work: finish documentation 
2.Work: consider 
3.Work:theory: prep for interviews 
4.Comm: 


%TODO: make outer file containing this file for compilation 
\begin{frame}
  \begin{columns}
    %-- Column 1 --------------------------------------------------- 
    \begin{column}{0.25\linewidth} %{\textbf{\underline{Week Aspects(new name)}}}
      \begin{block}{Local Happiness}
        % howto:Recognize emotions / recognize (precisely) what you're worried about -> methods for eliminating worry. 
        % clean out old worries, put them in pastWorries doc.  
        % remember to define precisely 
        % order from top-to bottom 
        \begin{itemize}
          \tiny \item \tiny Work: worrying about interviewing: just focus on the work. 
        \item \tiny Worrying about gal: think about talking to others. 
        \end{itemize}
      \end{block}
      \begin{block}{Stresses}
        % howto:Recognize emotions / recognize (precisely) what you're worried about -> methods for eliminating worry. 
        % clean out old worries, put them in pastWorries doc.  
        % remember to define precisely 
        % order from top-to bottom
        \begin{itemize}
          \tiny \item \tiny Work 
          \item \tiny Anger about a b  -> ...
          \item \tiny Anger about UP -> think about the positive
            perspective, and the original
          \item \tiny Anger about dad saying things 
        \end{itemize}
      \end{block} 
      %-- Block 1-3 
      \begin{block}{Life notes}
        \begin{itemize}
        \item \tiny TM: look at last chapter of emotional
          intelligence.  
        \item \tiny Problem: implement game of mastermind. 
        \end{itemize}
      \end{block}
    \end{column} %2 

    %-- Column 2 --------------------------------------------- 
    \begin{column}{0.50\linewidth}
      %--- Block 2-1

      \begin{block}{Routines}
        Morning: exercise, brush, \underline{floss}, shower (hair, eyes, ears,
        underarms, feet), meds, belt, comb hair, Night: brush teeth, charge
        phone, clothes for tomorrow, contacts off.  
      \end{block}

      \begin{block}{Week Summary}
        {\tiny \textbf{Week Plan:}  Work:   , Work: admin: send message to Prof. Gropp, Work: finish code for stencil, Work:comm: send emails to Prof. Gropp
          about meeting, Mgmt:Spaces: eye doctor appt, Comm: talk to
          Manjula, Comm: finish code for stencil, 
        } 

        {\tiny \textbf{Weekend Plan:} Mgmt:Spaces: pay tickets, Work: finish code, Comm: catch up with people} 

      \end{block} 


Not a problem 

Please do let me know soon though

not a problem 



          %infiniti / mercedes / acura / lexus 

      \begin{block}{Running TODO} % find a better name 
        \begin{enumerate}

          % --> curr  
     \item \tiny Work(GPUcode): get code done for OpenACC = 
       Work: Test code for PlasComCM + 
       Work(GPUcode): run code on xpacc cluster + 
       Work(GPUcode): check cluster access 

     \item \tiny Work(GPUcode): get code done for OpenACC =
       Work(GPUcode): get code done for OpenACC = Work(GPUcode):
       figure out control flow of all of code + Work(GPUcode): write
       down time estimates + Work(GPUcode): get code to compile on
       xpacc-clust GPU + Work(GPUcode): update git repo to have OpenMP
       and OpenACC in separate branches. 

     \item \tiny Work: comm: talk to Prof. Gropp. 

     \doneTask{ Work: comm: send message to Jon Freund} \pr{high} \te{10
       minutes} \dl{tonight} 

     \item \tiny Work: send message to Prof. Gropp. \te{10 minutes} 

     \item \tiny Work(documentation): add documentation =
       Work(documentation): make grid for machines  

     \item \tiny Work:comm/admin: message to Jill  +  Work: comm: talk
       to admin office. 

     \item \tiny Work: comm: send note to Prof. Gropp - 30 minutes 
       \tiny \item \tiny Work: call for suit \te{30 minutes} 
     \item \tiny Mgmt:Spaces: pay tickets \te{10 minutes}
        \end{enumerate}
      \end{block} 

      \begin{block}{Work:rel}
        \begin{itemize} 
        \item \tiny Intel 
        \item \tiny Facebook
        \item \tiny Oracle
          \tiny \item \tiny Sandia, LLNL, Postdoc at UIUC  
        \end{itemize}
      \end{block} 

      \begin{block}{Week Daily Schedule} 
        % howto: arrange items from running todo into the below
        % sheet management document. 
        {\small \textbf{Sun:} Work on code, worklife: experiences  }
        {\small \textbf{Mon:} Prep for presentation. \small
          \textbf{Tues:} experiences sheet\small
          \textbf{Wed:} Work: ... , Work: work on code, Work:rel: send
          in things for LBL,  Work:rel: send message to catch up on
          phone, Work: revise the presentation for technical stuff, Work: send
          message about . 

          \small \textbf{Thurs:} 

          \small \textbf{Fri:}  Work: finish runs setup, Work: talk to
          Matt about tests, Work: talk to Matt about configuration
          file, Work: figure out the llnl systems, Work: make notes on
          running systems, Work: add in
          research questions, Mgmt:Spaces: pay tickets, Work: git repo
          addition, Comm: message to girl from Chicago, Comm: accept
          the matrimony site picture. 
          \textbf{Sat:} \small Work: finish writing summary, Work: add
          OpenMP into code, Work: finish experimentation ,  Work: get
          code to run on BW with Cray compiler, 
          Work: put up script for running plascomm on xpacc, Work: 
          Mgmt:Spaces: tickets, Comm: do shaadi  } 

    %-- Column 3 --------------------------------------------------- 
    \begin{column}{0.20\linewidth}
      %-- Block 3-1 
      % On Sunday morn, put a quick synopsis of top news items           
      % here.  Categorize as Comm and Money.      
      \begin{block}{News}
        \begin{itemize} 
          \tiny \item \tiny San Berdardino shootings 
          \tiny \item \tiny Bomb from Egypt aircraft 
        \item \tiny Debates 
        \item \tiny Donald Trump on SNL 
        \item \tiny VW 
        \item \tiny Lufthansa strike  
        \end{itemize}
      \end{block}
      
      \begin{block}{Weather} 
        \begin{itemize}
          \tiny \item \tiny 
        \item \tiny 
        \end{itemize}
      \end{block}  

      \begin{block}{Clothes plan} 
        \begin{itemize}
          \tiny \item \tiny Monday
        \item \tiny Tuesday 
        \item \tiny Wednesday
        \item \tiny Thursday
        \item \tiny Friday 
        \end{itemize} 
      \end{block}

      %-- Block 3-3
      \begin{block}{Situations}
        % Howto: the below are the situations that define one another
        %WeeklySunTimeEst: 10 minutes
        \begin{itemize} 
        \item \tiny \textit{Situation: Sandia Interview} Pre-: Post-:
          get logistics down 
          \item \tiny \textit{Situation: Atul coming over} Pre-:
            Post-: 
        \end{itemize} 
      \end{block}

\begin{block}{Rel}
  \begin{itemize} 
    \small \item \small Girl from SF 
    %\small \item \small Meghan Joshi 
    \small \item \small Mamta 
    \small \item \small Girl from L.A.     
    \small \item \small Girl coming to SF. 
  \item \small Australian girl
    \small \item \small Chicago girl 
    \small \item \small Girl you got the number from 
    \small \item \small Rekha 
    \small \item Girl teaching 2nd grade     
  \item \small Smita kammath  
  \item \small Girl doing dentistry 
  %\small \item \small Ruchi 
  %\small \item \small Neha Jambhekar 
  %\small \item \small Vinita Ghate 
  \end{itemize}
\end{block} 
\end{column}%3 
      \end{columns}

\comments{
        \begin{columns} 
          \column{0.14\textwidth}{\textbf{\small \underline{Mon}}}
          \textbf{\small todo} \\ 
          \begin{itemize}
            \tiny \item \tiny Work: finish coding for GPGPU to ask
            Wen-mei. \te{20 minutes}. 
          \item \tiny Work: send mails for meetings. 
          \item \tiny Work: prep for this week. 
          \item \tiny Work: make slides for next week and this week 

            \tiny \item \tiny Work:rel: send message to IBM 

          \item \tiny worklife: experience writing 

          \item \tiny Pay tickets 
          \item \tiny 

          \end{itemize} 

          \textbf{\small schedule} \\
          \begin{enumerate} 
            \tiny \item \tiny 8-9AM: Regular Routines 

            \tiny \item \tiny 10AM - 11AM =  letter to wdg
          \item \tiny 11AM - 12PM = IBM 
              \tiny \item \tiny 1PM - 4PM = prep for presentation + finish code + Makefile 
              \tiny \item \tiny 4PM - 5PM = experience sheet +
              planning 
              \tiny \item \tiny 5 PM - 9 PM = meet people at exhibit hall 
          \end{enumerate} 
          
          \column{0.14\textwidth}{\textbf{\small \underline{Tue}}}
          \textbf{\small todo} \\
          \begin{itemize}
            \tiny \item \tiny Work: make project sheet \te{10 minutes} 
          \item \tiny  \te{10 minutes} 
          \end{itemize}  
          \textbf{\small schedule} 
          \begin{enumerate}
            \tiny \item \tiny 11AM - 12PM = IBM letter 

          \item \tiny 12 PM - 1 PM = prep for presentation 
          \item \tiny 1 PM - 2 PM = 
            \tiny \item \tiny 2PM - 3PM = 
          \item \tiny 6PM - 10PM = 
          \end{enumerate}  
          
          \column{0.14\textwidth}{\textbf{\small {\underline{Wed}}}}
          \textbf{\small todo} \\
          \begin{itemize}
            \tiny \item \tiny Work: finish slides   
          \item \tiny Mgmt: Spaces: update fb 
          \item \tiny Comm: 
          \end{itemize}
          \textbf{\small schedule} \\
          \begin{enumerate}
            \tiny \item \tiny 8-9AM: Regular Routines 
          \item \tiny 9AM - 10AM: Send message 
            \item \tiny 6:30PM - 7:30PM = 
          \end{enumerate} 
          \column{0.14\textwidth}{\textbf{\small{\underline{Thu}}}}
          \textbf{\small todo}\\
          \begin{itemize}  
            \tiny \item \tiny Work: finish slides 
            \item \tiny Mgmt:Spaces: 
            \item \tiny Comm: 

          \end{itemize} 

          \textbf{\small schedule}\\
          \begin{enumerate} 
            \tiny \item \tiny 8-9AM = Regular Routines 
            \item \tiny 12-1PM = 
            \item \tiny 3:30PM - 4:30PM = group meeting 
            \item \tiny 6PM - 9PM = revise emot. int. chapter and
              structure wl-cheat based on it 
          \end{enumerate} 
          
          \column{0.14\textwidth}{\textbf{\small{\underline{Fri}}}}
          \textbf{\small todo}\\ 
          \begin{itemize}
            \tiny \item \tiny Work: updates on GPU \dl{} \te{} \prio{}

            \tiny \item \tiny Mgmt:Spaces: Haircut \te{10 minutes} 

            
          \item \tiny \te{1 hour} 
          \end{itemize}
          \textbf{\small schedule}\\
          \begin{enumerate}
            \tiny \item \tiny 8-9AM: Regular Routines            
          \item \tiny 10AM - 11AM  = haircut 
            \tiny \item \tiny 11AM - 12PM = meet with Prof. Gropp at
            SC 4313  
          \item \tiny 5:30 PM - 7:00 PM = meet with Ruchi at 106
            N. Walnut Street (Esquire Lounge) 
          
          \end{enumerate}
          
          \column{0.14\textwidth}{\textbf{\small \underline{Sat}}}
          \textbf{\small todo}\\
          \begin{itemize} 
            \tiny \item \tiny
          \end{itemize}
          \textbf{\small schedule}\\ 
          \begin{enumerate}
            \tiny \item \tiny 7-7:30PM = food + organize.  
            \tiny \item \tiny 7:30PM -8PM = 
            \tiny \item \tiny 8PM -9PM = 
            \tiny \item \tiny 9:45PM - 10:30PM = go out 
            \tiny \item \tiny 2AM -3AM =  message Samir + add people
          \end{enumerate}
          
          \column{0.14\textwidth}{\textbf{\small \underline{Sun}}}
          \textbf{\small todo}\\
          \begin{itemize} 
           \tiny \item \tiny 
          \end{itemize}

          \textbf{\small schedule}\\
          \begin{enumerate} 
            \tiny \item \tiny 3PM - 4PM  =
          \item \tiny 5-7PM = Comm work 
          \item \tiny 8PM - 10PM = worklife work. 
          \end{enumerate} 
        \end{columns}
      \end{block}
    \end{column}%2     
}
\end{frame}  



%    \item \small Mgmt:Spaces(pk): Packing = 
%      Mgmt:Spaces(pk): charger +Mgmt:Spaces(pk): adapter 
%      + Mgmt:Spaces(pk): shoes  + 
%      Mgmt:Spaces(pk): belt + 
%      Mgmt:Spaces(pk):undershirts  =
%      (Mgmt:Spaces(pk):two black + Mgmt:Spaces(pk):two white) 
%      \doneTaskNoItem{Mgmt:Spaces(pk): Passport}
%      + \doneTaskNoItem{Mgmt:Spaces(pk): 6 underwear} +
%      \doneTaskNoItem{Mgmt:Spaces(pk): 8 socks} +
%      \doneTaskNoItem{Mgmt:Spaces: 4 shirts} + Mgmt:Spaces(pk): 4 

%   print boarding pass ,  print bus pass  

%   at airport:  

%  find the terminal to go to  

%  at security: 


% show boarding pass and get ID out 

% Put wallet in left compartment, and ID in right compartment. 

% Laptop in separate case 

% belt off, put in case with other things 

% shoes off 

% go into security 

% put laptop in case, and then in backpack.

% grab shoes and belt. 

% put cases away. 



% put backpack on. 
% grab other bag. 

% put shoes and belt on off to side 


% check gate on phone and go to gate

% check with flight staff about window, find a place to sit 

% email 
