%Note:  figure how to make items small automatically 
\underline{\textbf{October goals}}\\
\begin{enumerate}
\item Work: results finish and integrate. 
\item Work: thesis completion: research questions + writing 
\item Mgmt: Health: increase muscle: 
\item Mgmt: Health: increase dentist visits 
\item worklife: Habits + empathy + social intelligence. 
\item habits: lips relaxed, back straight, no teeth clicking/body noises, feet quiet. 
\end{enumerate}

\underline{\textbf{Week of Sept $22^{nd}$}} \\

\begin{enumerate}

\item Work: finish research questions. 2 hours +  Work: get slides done. 

\item Work: get weak scaling results for SNAP on BW - 2 hours. 
\item Work: get strong scaling for n-body on BG/Q. 1 hours.
\item Work: get weak scaling for n-body on BG/Q. 1 hours.
\item Work: get strong scaling for SNAP on BG/Q. 1 hours.
\item Work: get weak scaling for SNAP on BG/Q. 1 hours. 

\item Comm: finish empathy part of emotional intelligence, and take notes. - 1hr. 
\item Comm: finish TM speech. - 20 mins. 
\item Comm: practice vocal variety. - 30 mins. 
\end{enumerate}

\underline{\textbf{Week of October $1^{st}$}} \\
\begin{enumerate}
\item Work: problem size variation for NAS benchmarks on BG/Q, cab and BW. 30 mins. 
\item Work: start writing and organizing in thesis. 

\item Comm: practice vocal variety. 
\item worklife: read habits and update for notes. 
\end{enumerate} 

\underline{\textbf{Week of October $7^{th}$}} \\
\begin{enumerate} 
\item Work: start communicating /scheduling defense to committee. 
\item Work: organize results with research questions. 
\item Work: practice vocal variety. 
\item Comm: read social intelligence to help with social life. 
\end{enumerate}

\underline{\textbf{Week of October $13^{th}$}} \\
\begin{enumerate}
\item Work: write the thesis and organize  
\item Work: gather additional results 
\item worklife: read habits chapters interdependence. 
\end{enumerate}

\underline{\textbf{Week of October $20^{th}$}} \\
\begin{enumerate}
\item Work: write thesis defense and organize
\item Work: poster for EuroMPI + revisions in that chapter to finish off. 
\end{enumerate}

\underline{\textbf{Week of October $28^{th}$}} \\
\begin{enumerate}
\item Work: 
 \item Work: poster for EuroMPI + revisions in that chapter  to finish off
\end{enumerate}
