%\def\PRES{1}
%\ifx{\PRES}
%\iftoggle{\PRES}

%\begin{frame}[allowframebreaks]{Week Plan} 
%Work: send message to Barry about merging adagio with slack trace, Mgmt:Spaces: update facebook, Work: do work for cworks, 
%\end{frame}
%\begin{frame}[allowframebreaks]{Running To Do}

\begin{frame}[allowframebreaks]{Running To Do}
\begin{enumerate}

\item \tiny Work: talk with Professor Chapman. \te{30 minutes}.
\item \tiny Work: send e-mail to Florina. \te{45 minutes}
\item \tiny Work: approve pull requests of RAJA. \te{10 minutes}
\item \tiny Work: rel: send e-mail to Barry Rountree about talk. \te{25 minutes}
\item \tiny Work: rel: send e-mail to Barry Rountree about slack-trace on github. \te{25 minutes}
\item \tiny Work: rel: make generic reference letter for Professor Cappello. \te{20 minutes}
\item \tiny Work: book flight to San Francisco January 26th. \te{1 hour}
\item \tiny Mgmt:Spaces: dentist appointment this week. \te{30 minutes}
\item \tiny Mgmt:Spaces: get glasses. \te{20 minutes}
\item \tiny Mgmt:Spaces: get phone fixed through insurance assurex. \te{30 minutes}
\item \tiny Mgmt:Spaces: get sweatshirt from Travelodge by calling or e-mailing them. \te{10 minutes}
\item \tiny Mgmt:wp: update Facebook profile photo to show only face. \te{5 minutes}
\item \tiny Comm: text message to Bhakti. \te{30 minutes}.
\item \tiny Work:rel: email to Renata. \te{10 minutes}
  
\item \tiny \textbf{ <-- End Curr }
  
\item \tiny Work: rel: send message to Tony to get access to HPC facilities. 
\item \tiny Mgmt:wp: add people to LinkedIn =  Mgmt:wp: add Andy Schmidt on LinkedIn +  Mgmt:wp:add Marty. 
\item \tiny Mgmt:Spaces: get the reimbursement for car's warranty. 
\item \tiny Mgmt:Spaces: get citi bank account + Mgmt:Spaces: get refund from AA
\item \tiny Mgmt:Spaces: smart TV. 
\item \tiny Work: update book summary.  
\item \tiny Work: update movie summary. 
\end{enumerate}
\end{frame}


\begin{frame}{Day Plans}
  \underline{\bf{Monday}:}
  \underline{\bf{Thursday}:}
\end{frame} 
